### 2018-02-01 stats/mcc_pilot.Rmd
Adding revised version of informativeness and anonymized stats

---
title: "MCC_pilot"
author: "Manuel Bohn"
date: "26 1 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data
d <- bind_rows(read_csv(file="pref.data.csv"),
               read_csv(file="novel.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

Sanity checks.
```{r sanity checks}

## sanity checks
d %>%
  group_by(trial_type, condition) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)

```
Plot condition and speaker change with 95%CI
```{r plot}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, condition, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = change, y = mean, fill = change, frame = condition)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_wrap(~ condition,
             labeller = as_labeller(c(`novelty`="Novelty", `preference`="Preference")))+ 
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

Conditions by trial.
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, condition, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~ condition) + 
  theme_few() + 
  scale_colour_solarized()
```
Conditions by agents. Unequal distribution of agents across condition and change combinations leads to seemingly strange patterns for some agents. However, these strange results are always those with very few data points (e.g. Tiger novelty speaker change is only one data point). For those cells with more than five data points, the pattern is very similar to the overall pattern. 
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change, condition) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(change, condition, choiceAgent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = choiceAgent, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~ condition) + 
  theme_few() + 
  scale_colour_solarized()
```

T-tests against chance for each condition*change combination
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(change, condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change,condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(condition,change,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

```

Model testing for interaction between change and condition. No interaction between change and condition, and no effect of condition suggesting that speaker change manipualtion is similar in novelty and preference.
```{r}
## model
library(lme4)

data_cg <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))

lm <- glmer(correct ~ change * condition + trial +
              (change + trial|id) + (1|choiceAgent), 
            data = data_cg, family = binomial, control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))

summary(lm)

```

### 2018-02-01 experiments/informativeness_pilot/mcc_informativeness.js

@@ -32,7 +32,7 @@ function choiceAgent(id) {
   // Hide all slides
 	$(".agent").hide();
 	// Show just the agent we want to show
-	$("#"+id+"_choice").show();
+	$("#"+id+"_straight").show();
 }
 
 function sourceRightFruit(a) {
@@ -252,7 +252,8 @@ var experiment = {
   leftFruit: leftFruit,
   inf: inf,
   data: [],
-    
+  fruitPosition: [],
+  fruitPosition2: [],
 // end of the experiment
   end: function() {
     // Show the finish slide.
@@ -279,15 +280,43 @@ var experiment = {
     // get time for reaction time
     var endTime = (new Date()).getTime();    
     // select correct object
-    var corrFruit = $(".fruit_"+inf[0][0]).attr("src");
+    //var corrFruit = $(".fruit_"+inf[0][0]).attr("src");
+    if (inf[0]=="left") {
+        var corrFruit = leftFruit[0];
+    } else {
+        var corrFruit = rightFruit[0]
+        };
     // select chosen object  
     var pick = event.target.src;
+    // record position of objects on each table
+    var innerRight = $(".fruit_r").attr('src')
+    var outerRight = $(".fruit_r2").attr('src')
+    var innerLeft = $(".fruit_l").attr('src')
+    var outerLeft = $(".fruit_l2").attr('src')
     // Code correct: does name of chosen object contain the name of the correct object
     if (pick.indexOf(corrFruit) > -1) {
         var correct =1
         } else {
         var correct = 0
         };
+    //Code location of correct object (inner or outer one on the respective table)
+       
+    if (experiment.inf[0] == "left"){
+            if (innerLeft.indexOf(corrFruit) > -1) {
+                var tablePositionCorr = "inner"
+            } else {
+                var tablePositionCorr = "outer"
+            };
+    } else {
+            if (innerRight.indexOf(corrFruit) > -1) {
+                var tablePositionCorr = "inner"
+            } else {
+                var tablePositionCorr = "outer"
+            };
+    };
+   
+        
+       
       
     // data collected  
       data = {
@@ -297,6 +326,7 @@ var experiment = {
         agent: agents[0],
         leftFruit: leftFruit[0],
         rightFruit: rightFruit[0],
+        tablePositionCorr: tablePositionCorr,
         inf: inf[0],
         pick: pick,
         correct: correct,
@@ -332,6 +362,8 @@ var experiment = {
     experiment.control[0].shift();
     experiment.rightFruit.shift();
[…]

### 2018-02-01 stats/data_preprocessing.R

@@ -1,0 +1,115 @@
+install.packages("stringr")
+library(rjson)
+library(tidyr)
+library(stringr)
+library(dplyr)
+library(data.table)
+library("stringr")
+
+
+##
+setwd("~/Work/MCC/git-mcc/mcc/stats/")
+
+############################
+######## novelty ###########
+################################################################################################################
+
+
+# select all files from individual workers
+files <- dir("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results")
+
+#combine files into one dataframe
+raw <- data.frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- data.frame(workerid = jd$WorkerId, 
+                   data = jd$answers$data$data
+)
+  raw <- bind_rows(raw, id)
+}
+
+# convert into short format, drop unnecessary columns, rename variables and sort by id
+novel.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
+names(novel.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+novel.data$pick= str_sub(novel.data$pick,73,str_length(novel.data$pick)-4)
+novel.data = novel.data[!duplicated(novel.data), ]
+novel.data = novel.data[order(id)]
+novel.data$id = paste(novel.data$id,novel.data$condition,sep="_")
+# check resulting datafile
+str(novel.data)
+head(novel.data)
+# write csv file for further analysis
+write.csv(novel.data, file="novel.data.csv")
+
+################################################################################################################
+
+
+############################
+######## preference ###########
+################################################################################################################
+
+files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
+
+#combine files into one dataframe
+raw <- data.frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/cosub_preference/anonymized-results/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- data.frame(workerid = jd$WorkerId, 
+                   data = jd$answers$data$data
+)
+  raw <- bind_rows(raw, id)
[…]

### 2018-02-01 stats/mcc_pilot_cg_plots.R

@@ -1,0 +1,57 @@
+
+library("ggplot2")
+library("ggthemes")
+library("viridis")
+library("ggpubr")
+
+
+## importing data
+#pref.data.full =read.csv(file="~/Work/MCC/stats/pref.data.csv", header=T, sep=",")
+#novel.data.full =read.csv(file="~/Work/MCC/stats/novel.data.csv", header=T, sep=",")
+
+load("mcc_pilot.RData")
+
+## sanity checks
+# number of participants in each experiment
+unique(pref.data.full$id)
+unique(novel.data.full$id)
+
+# select training trials
+# check performance in training trials
+novel.training=subset(novel.data.full, novel.data.full$trial=="train")
+table(novel.training$id,novel.training$correct)
+
+pref.training=subset(pref.data.full, pref.data.full$trial=="train")
+table(pref.training$id,pref.training$correct)
+
+## remove training trials for plotting
+novel.data=subset(novel.data.full, trial!="train")
+pref.data=subset(pref.data.full, trial!="train")
+
+### merging datasets
+cg.data=rbind(pref.data,novel.data)
+
+#plot for two common ground conditions
+ggplot(cg.data, 
+       aes(x = change, y = correct, fill = change, frame = condition))+
+  stat_summary_bin(aes(y = correct), fun.y = "mean", geom = "bar")+
+  stat_summary(fun.data = "mean_cl_normal", colour = "black", size = 1, width = .1, geom = "errorbar", show.legend = FALSE)+
+  facet_wrap(~ condition,
+             labeller = as_labeller(c(`novelty`="Novelty", `preference`="Preference")))+
+  geom_hline(yintercept = 0.5, size = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  ylim(0,1.05)+
+  guides(fill = guide_legend(keywidth = 2, keyheight = 2))+
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_fill_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))+
+  #scale_fill_viridis(discrete=TRUE,name="Speaker Change",
+  #                     breaks=c("false", "true"),
+  #                     labels=c("No", "Yes"))+
+  theme_few(base_size = 12)+
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
+
+save.image("mcc_pilot.RData")
+
+

### 2018-02-02 stats/mcc_pilot.Rmd
training trial options for inforamtiveness and updated model

@@
 
-Model testing for interaction between change and condition.
-No interaction between change and condition, and no effect of condition suggesting that speaker change manipualtion is similar in novelty and preference.
+ChoiceAgent can be seen as an approximation for "item".
+Model below converges, however, the random effects for choiceAgent are highly correlated suggesting that there is not enough data to estimate them independently (makes sense in light of table above).
+Therefore I would remove the random slopes within choiceAgent (AIC looks better when they are removed).
+What would you do with non-significant interaction?
+I put it in there just to check.
+We did not hypothesize that there would be an interaction, therefore I would remove it.
+Model 2 reflects what I would suggest.
+Result (independent of model): No interaction between change and condition, effect of change and no effect of condition suggesting that speaker change manipualtion is similar in novelty and preference.
 ```{r}
@@
 
-lm <- glmer(correct ~ change * condition + trial +
-              (change + trial|id) + (1|choiceAgent), 
-            data = data_cg, family = binomial, control=glmerControl(optimizer="bobyqa",
-                            optCtrl=list(maxfun=2e5)))
+# maximal converging model
+lm <- glmer(correct ~ change * condition +
+              (condition + change + trial|id) + (0 + condition + change + trial |choiceAgent), 
+              data = data_cg, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
 
@@
 
+# alternative model
+lm2 <- glmer(correct ~ change + condition +
+              (condition + change + trial|id) + (1|choiceAgent), 
+              data = data_cg, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lm2)
+
 ```

### 2018-02-02 experiments/informativeness_pilot/mcc_informativeness.js

@@ -195,7 +195,7 @@ $.ajax({
 
 // Variables and randomization for the experiment
 
-var trial = ["train","train","finTrain",1,2,3,4,5,6]
+var trial = ["train1","train2","finTrain",1,2,3,4,5,6]
 // agent order for training
 var trainAgents = ["Elephant","Pig"]
 var allAgents = ["Frog","Mouse","Monkey","Bunny","Dog","Bear","Tiger","Cat","Sheep"];
@@ -389,13 +389,28 @@ var experiment = {
     $("#text3").text(agents[0]+" is here")  
     
     // specify what is shown on the tables depending on training and test condition
-    if (experiment.trial[0] == "train"){
-        showAgent(agents[0],"choice");
+    if (experiment.trial[0] == "train1"){
+        showAgent(agents[0],"point_l");
         choiceLeftFruit("images/"+leftFruit[0]+".png");
-        choiceLeftFruit2("images/empty.png");
+        choiceLeftFruit2("images/"+rightFruit[0]+".png");
+        //choiceLeftFruit2("images/empty.png");
       
-        choiceRightFruit("images/"+rightFruit[0]+".png");     
+        choiceRightFruit("images/empty.png");
+        //choiceRightFruit("images/"+rightFruit[0]+".png");     
         choiceRightFruit2("images/empty.png");
+        
+        $("#choiceFruit_l").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
+                    $("#choiceFruit_l").animate({width: "250px",opacity: '1', queue: false, duration: 1000});
+                    $("#choiceFruit_l2").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
+                    $("#choiceFruit_l2").animate({width: "250px",opacity: '1', queue: false, duration: 1000});
+        
+        } else if (experiment.trial[0] == "train2"){
+        showAgent(agents[0],"choice");
+        choiceLeftFruit("images/empty.png");
+        choiceLeftFruit2("images/"+leftFruit[0]+".png");
+      
+        choiceRightFruit("images/empty.png");     
+        choiceRightFruit2("images/"+rightFruit[0]+".png");
         
         } else {
             if (experiment.control[0][0] == "true"){
@@ -512,13 +527,27 @@ var experiment = {
      
     // display obejcts on table depending on training and test condition
 
-    if (experiment.trial[0] == "train"){
+    if (experiment.trial[0] == "train1"){
[…]

### 2018-02-02 stats/mcc_pilot.Rmd
updating analysis for novelty and preference

@@
 For those cells with more than five data points, the pattern is very similar to the overall pattern.
+Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment.
+This causes the unequal distribution.
 ```{r trials per condition and agent}
@@
 ChoiceAgent can be seen as an approximation for "item".
-Model below converges, however, the random effects for choiceAgent are highly correlated suggesting that there is not enough data to estimate them independently (makes sense in light of table above).
+First model below converges, however, the random effects for choiceAgent are highly correlated suggesting that there is not enough data to estimate them independently (makes sense in light of plot/table above).
 Therefore I would remove the random slopes within choiceAgent (AIC looks better when they are removed).
-What would you do with non-significant interaction?
+What would you do with the non-significant interaction?
 I put it in there just to check.
-We did not hypothesize that there would be an interaction, therefore I would remove it.
+I did not hypothesize that there would be an interaction, therefore I would remove it.
 Model 2 reflects what I would suggest.
@@
 summary(lm)
+```
 
+```{r}
 # alternative model

### 2018-02-06 stats/mcc_pilot.Rmd
updating informativeness

@@
 ```{r}
-# alternative model
+#  final model
+#  removing random effects for trial as there seems to be no evidence for a trial effect
 lm2 <- glmer(correct ~ change + condition +
-              (condition + change + trial|id) + (1|choiceAgent), 
+              (condition + change |id) + (1|choiceAgent), 
               data = data_cg, family = binomial, 

### 2018-02-06 experiments/informativeness_pilot/mcc_informativeness.js

@@ -211,12 +211,12 @@ var control = trainControl.concat(testControl);
 // objects on tables in training and test (fruits = toys)
 var trainFruitLeft = ["car","duck"];
 var trainFruitRight = ["bear","ball"];
-var fruits = ["t1","t2","t3","t18","t5","t6","t7","t8","t17","t10", "t11","t12","t13","t15","t16"];
+var fruits = ["t1","t2","t3","t4","t5","t7","t8","t17","t10", "t11","t12","t15","t16"];
 // randomizing order and combiantion of test objects
-var testRightFruit = fruits.sort(() => .5 - Math.random()).slice(0,8);
+var testRightFruit = fruits.sort(() => .5 - Math.random()).slice(0,6);
 var remainingFruits = $.grep(fruits, function(value) {
     return $.inArray(value, testRightFruit) < 0;});
-var testLeftFruit = remainingFruits.sort(() => .5 - Math.random()).slice(0,8);
+var testLeftFruit = remainingFruits.sort(() => .5 - Math.random()).slice(0,6);
 var leftFruit = trainFruitLeft.concat(testLeftFruit);
 var rightFruit = trainFruitRight.concat(testRightFruit);
 
@@ -390,19 +390,12 @@ var experiment = {
     
     // specify what is shown on the tables depending on training and test condition
     if (experiment.trial[0] == "train1"){
-        showAgent(agents[0],"point_l");
+        showAgent(agents[0],"choice");
         choiceLeftFruit("images/"+leftFruit[0]+".png");
-        choiceLeftFruit2("images/"+rightFruit[0]+".png");
-        //choiceLeftFruit2("images/empty.png");
+        choiceLeftFruit2("images/empty.png");
       
-        choiceRightFruit("images/empty.png");
-        //choiceRightFruit("images/"+rightFruit[0]+".png");     
+        choiceRightFruit("images/"+rightFruit[0]+".png");     
         choiceRightFruit2("images/empty.png");
-        
-        $("#choiceFruit_l").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
-                    $("#choiceFruit_l").animate({width: "250px",opacity: '1', queue: false, duration: 1000});
-                    $("#choiceFruit_l2").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
-                    $("#choiceFruit_l2").animate({width: "250px",opacity: '1', queue: false, duration: 1000});
         
[…]

### 2018-02-07 stats/mcc_inf.Rmd
informativeness results

---
title: "MCC_Informativeness"
author: "Manuel Bohn"
date: "7 2 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data
d <- read_csv(file="inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

Sanity checks.
```{r training performance}
## performance in training and test
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 3)

```

Plot for test vs control with 95%CI
```{r plot}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = control, y = mean, fill = control)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Trial Type",
                     breaks=c("false", "true"),
                     labels=c("Test", "Control"))
```

Effect of target object location on table. Inner = closer to the agent, outer = further away. 
For test this does not seem to matter. For control: If they had a tendency to pick the one closer to the agent, they should be above chance for inner and below chance for outer. Only the latter seems to be the case. Not sure why, could also be just noise. 
```{r inner vs outer location}
## performance in training and test
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(targetOnTable,control, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = control, y = mean, fill = control,frame = targetOnTable)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~ targetOnTable) +
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) +
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Trial Type",
                     breaks=c("false", "true"),
                     labels=c("Test", "Control"))

```

Conditions by trial.
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = control)) +
  geom_line(aes(group= control)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Conditions by agents.
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  group_by(agent,control) %>%
  summarise(n = length(agent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

Agent effect. Dog seems a little strange (despite enough data) but no idea what to make of this.
```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, agent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = agent, y = mean, col = control)) +
  geom_line(aes(group= control)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

T-tests against chance test and control
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(control, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(control) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(control,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

```

Agent can be seen as an approximation for "item".

```{r}
## model
library(lme4)

data_inf <- d%>%
  filter(trial_type == "test")%>%
  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))

# registered  model
lm <- glmer(correct ~ control +
              (control |id) + (control |agent), 
              data = data_inf, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)
```

### 2018-02-07 stats/mcc_pref.Rmd
informativeness results

---
title: "MCC_Preference"
author: "Manuel Bohn"
date: "26 1 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data
d <- read_csv(file="pref.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

Sanity checks.
```{r sanity checks}

## sanity checks
d %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)

```

Plot for speaker change with 95%CI
```{r plot}

ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = change, y = mean, fill = change)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

Conditions by trial.
```{r plot trials}
ms <- d %>%
  filter(trial_type == "test") %>%
  group_by(change, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Conditions by agents. Unequal distribution of agents across change leads to seemingly strange patterns for some agents. However, these strange results are always those with very few data points (e.g. Tiger novelty speaker change is only one data point). For those cells with more than five data points, the pattern is very similar to the overall pattern. Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment. This causes the unequal distribution.
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

```{r plot agents}
ms <- d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(change, choiceAgent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = choiceAgent, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

T-tests against chance for each speaker change conditions
```{r}
## t tests against chance
d %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(change,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

```

ChoiceAgent can be seen as an approximation for "item".

```{r}
## model
library(lme4)

data_cg <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))

# maximal converging model
lm <- glmer(correct ~ change +
              (1 |id) + (1 |choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)
```

### 2018-02-07 stats/data_preprocessing.R

@@ -82,12 +82,12 @@ write.csv(pref.data, file="pref.data.csv")
 ######## informativeness ###########
 ################################################################################################################
 
-files <- dir("~/Work/MCC/git-mcc/cosub_informativeness/sandbox-results")
+files <- dir("~/Work/MCC/git-mcc/cosub_informativeness/anonymized-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/cosub_informativeness/sandbox-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/cosub_informativeness/anonymized-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -96,12 +96,14 @@ for (f in files) {
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-inf.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.leftFruit","^data.rightFruit","^data.pick","^data.inf","^data.trial","^data.control","^data.rt", "^data.correct"))
-names(inf.data) = c("id","alltrial","condition","agent","leftObject","rightObject","pick","target","trial","control","rt","correct") 
+inf.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.leftFruit","^data.rightFruit","^data.tablePositionCorr","^data.pick","^data.inf","^data.trial","^data.control","^data.rt", "^data.correct"))
+names(inf.data) = c("id","alltrial","condition","agent","leftObject","rightObject","targetOnTable","pick","target","trial","control","rt","correct") 
 inf.data $pick= str_sub(inf.data $pick,81,str_length(inf.data $pick)-4)
 inf.data = inf.data[!duplicated(inf.data), ]
 inf.data = inf.data[order(id)]
 inf.data $id = paste(inf.data $id, inf.data $condition,sep="_")
+inf.data$trial[inf.data$trial=="train1"]="train"
+inf.data$trial[inf.data$trial=="train2"]="train"
 # check resulting datafile
 str(inf.data)
 head(inf.data)

### 2018-02-07 stats/mcc_pilot_cg_plots.R

@@ -1,57 +1,0 @@
-
-library("ggplot2")
-library("ggthemes")
-library("viridis")
-library("ggpubr")
-
-
-## importing data
-#pref.data.full =read.csv(file="~/Work/MCC/stats/pref.data.csv", header=T, sep=",")
-#novel.data.full =read.csv(file="~/Work/MCC/stats/novel.data.csv", header=T, sep=",")
-
-load("mcc_pilot.RData")
-
-## sanity checks
-# number of participants in each experiment
-unique(pref.data.full$id)
-unique(novel.data.full$id)
-
-# select training trials
-# check performance in training trials
-novel.training=subset(novel.data.full, novel.data.full$trial=="train")
-table(novel.training$id,novel.training$correct)
-
-pref.training=subset(pref.data.full, pref.data.full$trial=="train")
-table(pref.training$id,pref.training$correct)
-
-## remove training trials for plotting
-novel.data=subset(novel.data.full, trial!="train")
-pref.data=subset(pref.data.full, trial!="train")
-
-### merging datasets
-cg.data=rbind(pref.data,novel.data)
-
-#plot for two common ground conditions
-ggplot(cg.data, 
-       aes(x = change, y = correct, fill = change, frame = condition))+
-  stat_summary_bin(aes(y = correct), fun.y = "mean", geom = "bar")+
-  stat_summary(fun.data = "mean_cl_normal", colour = "black", size = 1, width = .1, geom = "errorbar", show.legend = FALSE)+
-  facet_wrap(~ condition,
-             labeller = as_labeller(c(`novelty`="Novelty", `preference`="Preference")))+
-  geom_hline(yintercept = 0.5, size = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  ylim(0,1.05)+
-  guides(fill = guide_legend(keywidth = 2, keyheight = 2))+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))+
-  #scale_fill_viridis(discrete=TRUE,name="Speaker Change",
-  #                     breaks=c("false", "true"),
-  #                     labels=c("No", "Yes"))+
-  theme_few(base_size = 12)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
-
-save.image("mcc_pilot.RData")
-
-

### 2018-02-16 stats/simulations/mcc_simulations.Rmd
data simulation for modeling 1.0

---
title: "MCC Simulations"
author: "Manuel Bohn"
date: "10 2 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(ggpubr)
library(lme4)

```

```{r}
conditions <- read.csv("condition_means.csv", sep=";")

generate_data <- function(condition_df, n_subs = 40, n_trials = 3) {
  tibble(count = condition_df$count,
         speaker = condition_df$speaker, 
         prior = condition_df$prior,
         info = condition_df$info, 
         experiment = condition_df$experiment,
         correct = rbinom( n_subs * n_trials, 1,
                          condition_df$correct_add),
         correct2 = rbinom( n_subs * n_trials, 1,
                          condition_df$correct_cg),
         correct3 = rbinom( n_subs * n_trials, 1,
                          condition_df$correct_inf),
         correct4 = rbinom( n_subs * n_trials, 1,
                          condition_df$correct_seq),
         subid = rep(1:n_subs, n_trials))
}

participant_data <- conditions %>%
  mutate(index = 1:n()) %>%
  split(.$index) %>%
  map_df(generate_data) %>%
  mutate(subid=paste(subid,speaker,prior,info,sep=""))%>%
  mutate(prior = relevel(prior, ref="cntl"),
         info = relevel(info, ref="neutral"))

  #mutate(correct=correct+rnorm(n=length(subid), mean=0, sd=0.05*(as.numeric(as.factor(subid)))/length(subid)))%>%
  #mutate(correct = ifelse(correct < 0.5, 0,1))

```

```{r}

library('grid')

ms <- participant_data %>%
  group_by(count,experiment,speaker, prior, info) %>%
  summarise(correct = mean(correct),
            correct2 = mean(correct2),
            correct3 = mean(correct3),
            correct4 = mean(correct4))

mp <- ggplot(ms, 
       aes(x = prior, y = correct, fill = prior)) +
  geom_bar(stat="identity") + 
  facet_grid(~speaker*info,scales = "free_x", space = "free_x")+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  theme_few(base_size = 6) + 
  ylim(0,1)+
  ggtitle("1: mean(info+prior)")+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

cgp <- ggplot(ms, 
       aes(x = prior, y = correct2, fill = prior)) +
  geom_bar(stat="identity") + 
  facet_grid(~speaker*info,scales = "free_x", space = "free_x")+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  theme_few(base_size = 6) + 
  ylim(0,1)+
  ggtitle("2: prior > info")+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

ip <- ggplot(ms, 
       aes(x = prior, y = correct3, fill = prior)) +
  geom_bar(stat="identity") + 
  facet_grid(~speaker*info,scales = "free_x", space = "free_x")+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  theme_few(base_size = 6) + 
  ylim(0,1)+
  ggtitle("3: info > prior")+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

seq <- ggplot(ms, 
       aes(x = prior, y = correct4, fill = prior)) +
  geom_bar(stat="identity") + 
  facet_grid(~speaker*info, scales = "free_x", space = "free_x")+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  theme_few(base_size = 6) + 
  ylim(0,1)+
  ggtitle("4: if (info = prior, max(prior,info), mean(prior,info)")+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

sum= ggarrange(mp,ip, cgp,seq,
          ncol = 1, nrow = 4,
          common.legend=TRUE)
```
```{r fig3, fig.asp = 1.2}
sum
```

```{r}

## Sometimes models for different predictions (correct - correct4) do not converge - probably due to data structure, as this changes when data are newly simulated.

lm <- glmer(correct ~ speaker * prior * info+ (1|subid), 
      data = participant_data,
      family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)
drop1(lm, test = "Chisq")

```

### 2018-02-16 stats/data_preprocessing_kids.R

@@ -23,19 +23,18 @@ raw <- data.frame()
 for (f in files) {
   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(id = f, 
+  id <- data.frame(
                    data = jd$data$data
 )
   raw <- bind_rows(raw, id)
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,73,str_length(novel.data$pick)-4)
+novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
+names(novel.data) = c("alltrial","id","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+novel.data$pick= str_sub(novel.data$pick,72,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(id)]
-novel.data$id = paste(novel.data$id,novel.data$condition,sep="_")
 # check resulting datafile
 str(novel.data)
 head(novel.data)
@@ -56,19 +55,18 @@ raw <- data.frame()
 for (f in files) {
   jf <- paste("~/Work/MCC/git-mcc/kids_pref_data/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(id = f, 
+  id <- data.frame(
                    data = jd$data$data
 )
   raw <- bind_rows(raw, id)
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
[…]

### 2018-02-16 stats/simulations/power_analysis.r

@@ -1,0 +1,197 @@
+library(lme4)
+source("X:/Statistics/R scripts/Roger/intercept_optimization.r")
+n.children=c(12, 18, 24, 32, 40)
+subj.contrib=c(0.1, 0.2, 0.4, 0.8, 1.6)
+conds=as.factor(c("ton", "geste", "both"))
+ages=as.factor(c(18, 24))
+trial.effect=0.1
+trial.RS=0.05
+age.cond.probs=c(0.5, 0.6, 0.7, 0.6, 0.7, 0.8)
+logit.age.cond.probs=log(age.cond.probs/(1-age.cond.probs))
+
+do.all<-function(index, nc, sc){
+	keepWarnings<-function(expr){
+		localWarnings <- list()
+		value <- withCallingHandlers(expr,
+			warning = function(w) {
+				localWarnings[[length(localWarnings)+1]] <<- w
+				invokeRestart("muffleWarning")
+			}
+		)
+		list(value=value, warnings=localWarnings)
+	}
+	N=n.children[nc]*length(conds)*length(ages)
+	xdata=data.frame(expand.grid(conds, ages))
+	colnames(xdata)=c("cond", "age")
+	xdata$cond=factor(xdata$cond, levels=c("ton", "geste", "both"))
+	xdata=xdata[rep(x=1:nrow(xdata), each=n.children[nc]), ]
+	xdata$subject=as.factor(1:N)
+	n.trials=sample(1:4, N, replace=T, prob=c(0.4, 0.3, 0.2, 0.1))
+	xdata=xdata[rep(x=1:nrow(xdata), times=n.trials), ]
+	xdata$trial.nr=unlist(lapply(X=n.trials, FUN=function(input){1:input}))
+	xdata$z.trial.nr=as.vector(scale(xdata$trial.nr))
+	both.fac=as.factor(paste(xdata$age, xdata$cond, sep="_"))
+	both.fac=factor(both.fac, levels(both.fac)[c(3, 2, 1, 6, 5, 4)])
+	
+	resp=logit.age.cond.probs[as.numeric(both.fac)]+
+		xdata$z.trial.nr*(trial.effect+rnorm(n=N, mean=0, sd=trial.RS)[as.numeric(xdata$subject)])+
+		rnorm(n=N, mean=0, sd=subj.contrib[sc])[as.numeric(xdata$subject)]
+	resp=rbinom(n=nrow(xdata), size=1, prob=exp(resp)/(1+exp(resp)))
[…]

### 2018-02-20 stats/simulations/mcc_simulations.Rmd
minor adjustment layout novel + pref

@@
 
-sum= ggarrange(mp,ip, cgp,seq,
+sum= ggarrange(mp, cgp,ip,seq,
           ncol = 1, nrow = 4,
@@
 
-lm <- glmer(correct ~ speaker * prior * info+ (1|subid), 
+lm <- glmer(correct3 ~ speaker * prior * info+ (1|subid), 
       data = participant_data,

### 2018-03-09 stats/simulations/mcc_kids_simulations.Rmd
kids data sim

---
title: "MCC Simulations"
author: "Manuel Bohn"
date: "10 2 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(ggpubr)
library(lme4)

```

```{r}
conditions <- read.csv("kids_condition_means.csv", sep=";")

generate_data <- function(condition_df, n_subs = 16, n_trials = 3) {
  tibble(count = condition_df$count,
         condition = condition_df$condition,
         age = condition_df$age,
         type = condition_df$type,
         correct = rbinom( n_subs * n_trials, 1,
                          condition_df$correct),
         subid = rep(1:n_subs, n_trials))
}

participant_data <- conditions %>%
  mutate(index = 1:n()) %>%
  split(.$index) %>%
  map_df(generate_data)%>%
  mutate(subid=paste(subid,age,condition,sep="_"))%>%
  arrange(condition, subid)

 participant_data %>%
  group_by(condition,age,type,subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct") %>%
  mutate(ciw = ci_upper-ci_lower) %>%
  group_by() %>%
  summarise(ciw = mean(ciw))%>%
  knitr::kable(digits = 3)

```

```{r}

ms <- participant_data %>%
  group_by(condition,age,type,subid) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = type, y = mean, fill = type)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  facet_grid(age~ condition)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

```{r}

#
md <- participant_data %>%
  filter(condition == "novel")

lm <- glmer(correct ~ age * type + (1|subid), 
      data = md,
      family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)
drop1(lm, test = "Chisq")

```

### 2018-03-09 experiments/kids_informativeness/mcc_informativeness.js

@@ -160,77 +160,7 @@ function playSound() {
        }, time); 
     };
 
-// disabling next button in preview mode
 
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-      showSlide("instructions");
-      alert("Please accept HIT to view");
-    } else {
-      showSlide('training')
-    }
-});
-
-// Progress bar
-
-$("#progressbar").progressbar();
-$("#progressbar").progressbar( "option", "max", 9);
-
-// move progress bar
-
-function move() {
-	$("#progressbar").progressbar("option", "value", 
-        ($("#progressbar").progressbar( "option", "value")+1));
-}
-
-// preloading images and sounds
-// images
-
-/*
-var folder = "images/";
-
-$.ajax({
-    url : folder,
-    success: function (data) {
-        $(data).find("a").attr("href", function (i, val) {
-            if( val.match(/\.(png)$/) ) { 
-                $("preload").append( "<img src='"+ folder + val +"'>" );
-            } 
-        });
-    }
-});
-
-// sound
-
-var folder2 = "sound/";
-
-$.ajax({
-    url : folder2,
-    success: function (data) {
-        $(data).find("a").attr("href", function (i, val) {
-            if( val.match(/\.(mp3)$/) ) { 
-                $("preload").append( "<audio src='"+ folder2 + val +"'>" );
-            } 
-        });
-    }
-});
-
-var folder3 = "dots/";
-
-$.ajax({
-    url : folder3,
-    success: function (data) {
-        $(data).find("a").attr("href", function (i, val) {
-            if( val.match(/\.(jpg)$/) ) { 
-                $("preload").append( "<img src='"+ folder3 + val +"'>" );
-            } 
-        });
-    }
-});
-
-
-*/
 
 
 // Variables and randomization for the experiment
@@ -305,9 +235,15 @@ var experiment = {
 			$("#checkMessage").html('<font color="red">You must input a subject ID</font>');
 			return;
 		}
+        if (document.getElementById("subjectAge").value.length < 1) {
+			$("#checkMessage").html('<font color="red">You must input a subject age</font>');
+			return;
+		}
 		experiment.subid = document.getElementById("subjectID").value
+        experiment.subage = document.getElementById("subjectAge").value
         experiment.trainingDot()
-      },    
+      }, 
+    
 // end of the experiment
   end: function() {
     // Show the finish slide.
[…]

### 2018-03-09 experiments/kids_novelty/mcc_novelty.js

@@ -135,18 +135,6 @@ function playSound() {
        }, time); 
     };
 
-// disabling next button in preview mode
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-      showSlide("instructions");
-      alert("Please accept HIT to view");
-    } else {
-      showSlide('training')
-    }
-});
-
 
 // Variables and randomization for the experiment
 
@@ -228,15 +216,20 @@ var experiment = {
 			$("#checkMessage").html('<font color="red">You must input a subject ID</font>');
 			return;
 		}
+        if (document.getElementById("subjectAge").value.length < 1) {
+			$("#checkMessage").html('<font color="red">You must input a subject age</font>');
+			return;
+		}
 		experiment.subid = document.getElementById("subjectID").value
+        experiment.subage = document.getElementById("subjectAge").value
         experiment.trainingDot()
-      },    
+      },     
     
 // end of the experiment
   end: function() {
     // Show the finish slide.
     showSlide("finished");
-    setTimeout(function() { turk.submit(experiment) }, 8000);
+    setTimeout(function() { turk.submit(experiment) }, 2000);
   },
  
 // end of training
@@ -256,6 +249,9 @@ var experiment = {
     sourceSound("sound/end.mp3");
     playSound();
     
+    $(".fruit_r").unbind("click");
+    $(".fruit_l").unbind("click");   
+       
     // get time for reaction time    
     var endTime = (new Date()).getTime();    
     // select correct object
@@ -268,10 +264,13 @@ var experiment = {
         } else {
         var correct = 0
         };
-    var subid = experiment.subid;  
-    // data collected 
+       
+    var subid = experiment.subid;
+    var subage = experiment.subage;    
+    // data collected  
       data = {
         subid: subid,
+        subage: subage,
         condition: "novelty",
         trial: trial[0],
         speakerChange: speakerChange[0][0],
@@ -304,8 +303,8 @@ var experiment = {
         showEat(agents[0])
     };
    
-    $("#continue").text("Touch the animal to continue")
-    $(".agent_eat").bind("click", experiment.newtrial);     
+   
+    $(".agent_eat").click(experiment.newtrial);     
   
 },       
 // unbind and shif variables between trials     
@@ -317,11 +316,8 @@ newtrial: function() {
     
     
[…]

### 2018-03-09 experiments/kids_preference/mcc_preference.js

@@ -135,17 +135,6 @@ function playSound() {
        }, time); 
     };
 
-// disabling next button in preview mode
-
-$("#button").click(function() {
-    //disable accept button if in turk preview mode
-    if (turk.previewMode) {
-      showSlide("instructions");
-      alert("Please accept HIT to view");
-    } else {
-      showSlide('training')
-    }
-});
 
 
 // Variables and randomization for the experiment
@@ -229,7 +218,12 @@ checkInput: function() {
 			$("#checkMessage").html('<font color="red">You must input a subject ID</font>');
 			return;
 		}
+        if (document.getElementById("subjectAge").value.length < 1) {
+			$("#checkMessage").html('<font color="red">You must input a subject age</font>');
+			return;
+		}
 		experiment.subid = document.getElementById("subjectID").value
+        experiment.subage = document.getElementById("subjectAge").value
         experiment.trainingDot()
       },    
     
@@ -237,7 +231,7 @@ checkInput: function() {
   end: function() {
     // Show the finish slide.
     showSlide("finished");
-    setTimeout(function() { turk.submit(experiment) }, 8000);
+    setTimeout(function() { turk.submit(experiment) }, 2000);
   },
     
 // end of training  
@@ -249,7 +243,10 @@ checkInput: function() {
     eat: function(event) {
 
     setTimeout(function() {experiment.eat2() }, 1500);
-       
+     
+    $(".fruit_r").unbind("click");
+    $(".fruit_l").unbind("click");    
+        
     showSlide("choice");  
        
     event.target.style.border = '5px solid blue';
@@ -271,10 +268,12 @@ checkInput: function() {
         var correct = 0
         };
       
-    var subid = experiment.subid; 
+    var subid = experiment.subid;
+    var subage = experiment.subage;    
     // data collected  
       data = {
         subid: subid,
+        subage: subage,
         condition: "preference",
         trial: trial[0],
         speakerChange: speakerChange[0][0],
@@ -307,8 +306,7 @@ checkInput: function() {
         showEat(agents[0])
     };
    
-    $("#continue").text("Touch the animal to continue")
-    $(".agent_eat").bind("click", experiment.newtrial);     
+    $(".agent_eat").click(experiment.newtrial);     
   
 },     
  // unbind and shif variables between trials       
[…]

### 2018-03-09 stats/data_preprocessing_kids.R

@@ -30,9 +30,9 @@ for (f in files) {
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("alltrial","id","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,72,str_length(novel.data$pick)-4)
+novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
+names(novel.data) = c("alltrial","id","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+novel.data$pick= str_sub(novel.data$pick,115,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(id)]
 # check resulting datafile
@@ -62,9 +62,9 @@ for (f in files) {
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-pref.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.pref","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(pref.data) = c("alltrial","id","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-pref.data$pick= str_sub(pref.data$pick,75,str_length(pref.data$pick)-4)
+pref.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.pref","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
[…]

### 2018-03-10 stats/simulations/mcc_kids_simulations.Rmd
kids data sim

@@
 ```{r}
-conditions <- read.csv("kids_condition_means.csv", sep=";")
+
+### condition means based on adult data with slightly smaller effect for younger kids
+
+conditions <- tibble (
+  age = c(rep(c(2,2,4,4),3)),
+  condition = c(rep(c("pref"),4),rep(c("novel"),4),rep(c("inf"),4)),
+  type = c(rep(c("test","ctrl"),6)),
+  correct = c(0.8666667,0.5416667,0.9666667,0.6416667,0.7333333,0.4916667,0.8333333,0.5916667,0.6716667,0.5,0.7416667,0.4583333)
+)
 
 generate_data <- function(condition_df, n_subs = 16, n_trials = 3) {
-  tibble(count = condition_df$count,
-         condition = condition_df$condition,
+  tibble(condition = condition_df$condition,
          age = condition_df$age,
@@
 
-participant_data <- conditions %>%
+### Average CI width across all condition, type and agegroup combinations.
+### For adults (n = 40), this average CI width 0.172
+### Average CI width as function of n kids: 12 = 0.261; 16 = 0.231; 24 = 0.192; 30 = 0.174; 40 = 0.150
+
+for (i in 1:100) {
+x[i] = conditions %>%
   mutate(index = 1:n()) %>%
@@
   mutate(subid=paste(subid,age,condition,sep="_"))%>%
-  arrange(condition, subid)
-
- participant_data %>%
+  arrange(condition, subid) %>%
   group_by(condition,age,type,subid) %>%
@@
   summarise(ciw = mean(ciw))%>%
-  knitr::kable(digits = 3)
+  pull()
+}
+
+mean(unlist(x))
 
@@
 ```{r}
+
+participant_data <- conditions %>%
+  mutate(index = 1:n()) %>%
+  split(.$index) %>%
+  map_df(generate_data)%>%
+  mutate(subid=paste(subid,age,condition,sep="_"))
 
@@
 summary(lm)
-drop1(lm, test = "Chisq")
 

### 2018-03-15 cue_strength/informativeness_point/mcc_informativeness_point_label.js
adding cue strength

@@ -1,0 +1,606 @@
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+  // Hide all slides
+	$(".agent").hide();
+	// Show just the agent we want to show
+	$("#"+id+"_straight").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
[…]

### 2018-03-15 cue_strength/informativeness_point/mcc_informativeness_point_only.js

@@ -1,0 +1,608 @@
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+  // Hide all slides
+	$(".agent").hide();
+	// Show just the agent we want to show
+	$("#"+id+"_straight").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
[…]

### 2018-04-12 models/predictions.Rmd
updating Ex3 and model and predictions

---
title: "MCC Predictions"
author: "Manuel Bohn"
date: "9 4 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
```

# Modeling Informativeness

Speaker optimality parameter of 2.25 produces model predictions that match out empirical results. The following predictions therefore use this parameter.

Prior = measured proportion this type of object is being chosen.

## "Dampening"" model

### Preference inconcgruent
ObjectPrior = Categorical({vs: all_objects, ps: [0.9666667, 0.9666667, 0.0333333] })

### Preference congruent
ObjectPrior = Categorical({vs: all_objects, ps: [0.0333333, 0.0333333, 0.9666667] })

### Novelty inconcgruent
var ObjectPrior = Categorical({vs: all_objects, ps: [0.8333333, 0.8333333, 0.1666667] })

### Novelty concgruent
var ObjectPrior = Categorical({vs: all_objects, ps: [0.1666667, 0.1666667, 0.8333333] })

```{r , echo=FALSE}

pred <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Model = c("Full model","Full model","Full model","Full model","Full model","Full model","Full model","Full model","No prior","No prior","No prior","No prior","No prior","No prior","No prior","No prior", "Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only"),
  corr = c(0.9999672744165804,0.03460862921907267,0.9083230583454356,0.5090645649737232,0.9930727540990627,0.20045767964927574,0.8603373265403738,0.594975610001643,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.967,0.033,0.642,0.358,0.833,0.167,0.592,0.408))

pred %>%
  knitr::kable(digits = 3)

ggplot(pred, 
       aes(x = Model, y = corr, fill = Model)) +
  geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Change*Alignment)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.x=element_blank())+
  ylim(0,1)

```

At what ratio does it flip back to more informative?

```{r , echo=FALSE}

pred <- data.frame(
  Prior = c("90/10","80/20","70/30","60/40","50/50"),
  corr = c(0.1118794400899893,0.24897738407515466,0.40911964439987003,0.5807810413750243,0.74)
)

ggplot(pred, 
       aes(x = Prior, y = corr, fill = Prior)) +
  geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Choosing More Informative")+
  theme_few(base_size = 12) +
  scale_fill_discrete(name = "Prior: less inf / more inf")+
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

```

### 2018-04-12 experiments/Ex3/Ex3_novel.js

@@ -263,7 +263,7 @@ var trainCond = [
     ["train2","same","right","right"]];
 var testCond = shuffle([
     ["sameSpInfLNovelL","same","left","left"],
-    ["difSpInfLNovelL","diff","left","left"],
+    ["diffSpInfLNovelL","diff","left","left"],
     ["sameSpInfRNovelL","same","right","left"],
     ["diffSpInfRNovelL","diff","right","left"],
     ["sameSpInfRNovelR","same","right","right"],
@@ -297,7 +297,7 @@ var experiment = {
   end: function() {
     // Show the finish slide.
     showSlide("finished");
-    setTimeout(function() { turk.submit(experiment) }, 8000);
+    setTimeout(function() { turk.submit(experiment) }, 5000);
   },
     
 // end of training  
@@ -326,22 +326,31 @@ var experiment = {
     var endTime = (new Date()).getTime();    
     // select correct object from info and novel perspective
        
-    if (experiment.cond[0][2]=="left") {
-        if (experiment.cond[0][3]=="left"){
-            var corrFruit_inf = experiment.fruitPosition[1]
-            var corrFruit_novel = experiment.fruitPosition[1];
-        } else {
-            var corrFruit_inf = experiment.fruitPosition[0]
-            var corrFruit_novel = experiment.fruitPosition[1];
-        };
+    if (experiment.cond[0][0] == "train1"){
+        var corrFruit_inf = "car";
+        var corrFruit_novel = "car";
+    } else if (experiment.cond[0][0] == "train2"){
+        var corrFruit_inf = "ball";
+        var corrFruit_novel = "ball";
     } else {
-        if (experiment.cond[0][3]=="left"){
-            var corrFruit_inf = experiment.fruitPosition[0]
-            var corrFruit_novel = experiment.fruitPosition[1];
-        } else {
-            var corrFruit_inf = experiment.fruitPosition[1]
-            var corrFruit_novel = experiment.fruitPosition[1];
-        };  
+       
+        if (experiment.cond[0][2]=="left") {
+            if (experiment.cond[0][3]=="left"){
+                var corrFruit_inf = experiment.fruitPosition[1];
+                var corrFruit_novel = experiment.fruitPosition[1];
+            } else {
+                var corrFruit_inf = experiment.fruitPosition[0]
+                var corrFruit_novel = experiment.fruitPosition[1];
+            };
+        } else if (experiment.cond[0][2]=="right"){
+            if (experiment.cond[0][3]=="left"){
[…]

### 2018-04-12 experiments/Ex3/Ex3_pref.js

@@ -240,10 +240,12 @@ var agentOrientations = [
 var agentOrient = shuffle(agentOrientations);
 
 
-var trainCond = [["train1"],["train2"]];
+var trainCond = [
+    ["train1","same","left","left"],
+    ["train2","same","right","right"]];
 var testCond = shuffle([
     ["sameSpInfLPrefL","same","left","left"],
-    ["difSpInfLPrefL","diff","left","left"],
+    ["diffSpInfLPrefL","diff","left","left"],
     ["sameSpInfRPrefL","same","right","left"],
     ["diffSpInfRPrefL","diff","right","left"],
     ["sameSpInfRPrefR","same","right","right"],
@@ -278,7 +280,7 @@ var experiment = {
   end: function() {
     // Show the finish slide.
     showSlide("finished");
-    setTimeout(function() { turk.submit(experiment) }, 8000);
+    setTimeout(function() { turk.submit(experiment) }, 5000);
   },
     
 // end of training  
@@ -304,8 +306,17 @@ var experiment = {
    
     $("#continue").text("Click on the animal to continue")
    // get time for reaction time       
-    var endTime = (new Date()).getTime();    
+    var endTime = (new Date()).getTime();   
+       
     // select correct object from info perspective
+       
+    if (experiment.cond[0][0] == "train1"){
+        var corrFruit_inf = "car";
+        var corrFruit_pref = "car";
+    } else if (experiment.cond[0][0] == "train2"){
+        var corrFruit_inf = "ball";
+        var corrFruit_pref = "ball";
+    } else {
     if (experiment.cond[0][2]=="left") {
             var corrFruit_inf = leftFruit[0];
         } else {
@@ -316,7 +327,8 @@ var experiment = {
             var corrFruit_pref = leftFruit[0];
         } else {
             var corrFruit_pref = rightFruit[0]
-            };   
+            };  
+    }
        
     // select chosen object    
     var pick = event.target.src;
@@ -331,7 +343,14 @@ var experiment = {
         } else {
         var correct_inf = 0
         };
-      
+    
+  // congruent or incongruent trial       
+    if (experiment.cond[0][2] == experiment.cond[0][3]){
+        var alignment = "congruent";
+    }   else {
+        var alignment = "incongruent";
+    };
+       
     // check if picked object is correct from info perspective
     if (pick.indexOf(corrFruit_pref) > -1) {
         var correct_pref =1
@@ -344,12 +363,15 @@ var experiment = {
[…]

### 2018-04-12 experiments/Ex3/Ex3_pref.js
fixing bug in Ex3 pref

@@ -429,7 +429,7 @@ var experiment = {
     
       
      // specify what happens depending on test condition
-    if (experiment.cond[0] == "train1"){
+    if (experiment.cond[0][0] == "train1"){
         showAgent(agents[0],"choice");
         
         $("#text3").text(agents[0]+" is here");
@@ -442,7 +442,7 @@ var experiment = {
         choiceRightFruit("images/"+rightFruit[0]+".png");     
         choiceRightFruit2("images/empty.png");
         
-        } else if (experiment.cond[0] == "train2"){
+        } else if (experiment.cond[0][0] == "train2"){
         showAgent(agents[0],"choice");
             
         $("#text3").text(agents[0]+" is here");

### 2018-04-20 models/predictions.Rmd
results from ex3

@@
 date: "9 4 2018"
-output: word_document
+output: html_document
 ---
@@
 
-```{r , echo=FALSE}
+```{r data}
 
@@
 
-pred %>%
-  knitr::kable(digits = 3)
+```
+
+```{r plot}
+#pred %>%
+#  knitr::kable(digits = 3)
 
 ggplot(pred, 
-       aes(x = Model, y = corr, fill = Model)) +
-  geom_bar(stat="identity") + 
+       aes(x = Change, y = corr, fill = Model)) +
+  geom_bar(stat="identity",position = position_dodge()) + 
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Change*Alignment)+
+  facet_grid(Experiment ~ Alignment)+
   theme_few(base_size = 12) + 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.x=element_blank())+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
   ylim(0,1)
+```
 
+```{r MH}
+# MH?
+ggplot(pred, 
+       aes(x = Change, y = corr, fill = Alignment)) +
+  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x=" ",y="Proportion Choosing More Informative")+
+  facet_grid(Experiment ~ Model)+
+  theme_few(base_size = 12) + 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  ylim(0,1)
 ```

### 2018-04-20 stats/ex3_comparisons.Rmd
results from ex3

---
title: "MCC Predictions"
author: "Manuel Bohn"
date: "9 4 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
```

# Modeling Informativeness

Speaker optimality parameter of 2.25 produces model predictions that match our empirical results. The following predictions therefore use this parameter.

Prior = measured proportion this type of object is being chosen.

## "Dampening"" model

### Preference inconcgruent
ObjectPrior = Categorical({vs: all_objects, ps: [0.9666667, 0.9666667, 0.0333333] })

### Preference congruent
ObjectPrior = Categorical({vs: all_objects, ps: [0.0333333, 0.0333333, 0.9666667] })

### Novelty inconcgruent
var ObjectPrior = Categorical({vs: all_objects, ps: [0.8333333, 0.8333333, 0.1666667] })

### Novelty concgruent
var ObjectPrior = Categorical({vs: all_objects, ps: [0.1666667, 0.1666667, 0.8333333] })

```{r data}
dat <- bind_rows(read_csv(file="ex3.novel.data.csv"),
               read_csv(file="ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
```

```{r sanity checks}
# check if there are incongruent trials in which informativeness and prior yield the same results
# is not the case, that's good
dat %>%
  filter(alignment == "incongruent") %>%
  filter(correct_inf == correct_prior)

# check if someone needs to be excluded because wrong in training
# no one, that's good
dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct_inf = mean(correct_inf)) %>%
  filter(correct_inf == 0)

# check if someone did both experiments
x <- dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct_inf)) %>%
  filter(n > 2)

# exclude those who dod both experiments
data <- dat %>%
  filter(id != x$id) %>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"))

```

```{r plot data}

p1 <- data %>%
  filter(trial_type == "test") %>%
  group_by(Change ,Experiment,Alignment, id) %>%
  summarise(correct = mean(correct_inf))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = Alignment, y = correct, col = Alignment, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = Alignment, y = mean, col = Alignment,ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_grid(Experiment ~ Change , scales = "free_x", space = "free_x" ) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized()

```

```{r comparisons to chance}
data %>%  
  filter(trial_type == "test") %>%
  group_by(change ,experiment,alignment, id) %>%
  summarise(correct_inf = mean(correct_inf)) %>%
  summarize(correct_inf = list(correct_inf)) %>%
  group_by(change ,experiment,alignment) %>%
  mutate(mean = mean(unlist(correct_inf)),
         stat = wilcox.exact(unlist(correct_inf), mu = 0.5)$statistic,
         p_value = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
  select(change ,experiment,alignment,mean,stat,p_value)%>%
  knitr::kable(digits = 3)
```

```{r model}
library(lme4)

m.data <- data %>%
  mutate(item = ifelse( change == "false", agent, altAgent))

lm <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change*Alignment|agent), 
              data = m.data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)

```

```{r model predictions}
predictions <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Model = c("Full model","Full model","Full model","Full model","Full model","Full model","Full model","Full model","No prior","No prior","No prior","No prior","No prior","No prior","No prior","No prior", "Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only"),
  corr = c(0.9999672744165804,0.03460862921907267,0.9083230583454356,0.5090645649737232,0.9930727540990627,0.20045767964927574,0.8603373265403738,0.594975610001643,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.967,0.033,0.642,0.358,0.833,0.167,0.592,0.408))

pred <- predictions %>%
  group_by(Model,Experiment,Change,Alignment)%>%
  multi_boot_standard(col = "corr")

```

```{r joining files}

da <- data %>%
  filter(trial_type=="test")%>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
         Model = "Data") %>%
  group_by(Model,Experiment,Change,Alignment,id)%>%
  summarise(correct_inf = mean(correct_inf)) %>%
  multi_boot_standard(col = "correct_inf")

pd <- rbind(pred,da)

```

```{r plot models and data}
ggplot(pd, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Model)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```
```{r plot comparing models}

library(ggpubr)

plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot1) = c("Experiment","Data","Model","Comp")
plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot2) = c("Experiment","Data","Model","Comp")
plot3 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot3) = c("Experiment","Data","Model","Comp")
plot4 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot4) = c("Experiment","Data","Model","Comp")

plot <- rbind(plot3,plot4,plot1,plot2)

ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
  geom_point()+
  facet_grid(Experiment~Comp)+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black")+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

```

At what ratio does it flip back to more informative?

```{r , echo=FALSE}

pred <- data.frame(
  Prior = c("90/10","80/20","70/30","60/40","50/50"),
  corr = c(0.1118794400899893,0.24897738407515466,0.40911964439987003,0.5807810413750243,0.74)
)

ggplot(pred, 
       aes(x = Prior, y = corr, fill = Prior)) +
  geom_bar(stat="identity") + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Choosing More Informative")+
  theme_few(base_size = 12) +
  scale_fill_discrete(name = "Prior: less inf / more inf")+
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

```

### 2018-04-20 stats/data_preprocessing_Ex3.R

@@ -16,13 +16,14 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 
 # select all files from individual workers
-files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/sandbox-results")
+#files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/sandbox-results")
+files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results/",f,sep="")
-  
+  #jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/sandbox-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -31,17 +32,21 @@ for (f in files) {
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,73,str_length(novel.data$pick)-4)
+novel.data= melt(setDT(raw), measure = patterns( "^data.experiment","^data.agent","^data.altAgent","^data.rightFruit","^data.leftFruit","^data.corrFruit_inf","^data.corrFruit_novel","^data.pick","^data.novel","^data.inf","^data.trial","^data.alignment","^data.speaker","^data.rt", "^data.correct_inf","^data.correct_novel"))
+names(novel.data) = c("id","alltrial","experiment","agent","altAgent","rightFruit","leftFruit","corObjInf","corObjPrior","pick","prior","inf","trial","alignment","change","rt","correct_inf","correct_prior") 
[…]

### 2018-04-24 stats/ex3_comparisons.Rmd
adding weak prior experiments

@@
 library(ggthemes)
+library(langcog)
 ```
@@
 # check if someone did both experiments
+# yes, two people
 x <- dat %>%
@@
 
-# exclude those who dod both experiments
+# exclude those who did both experiments
 data <- dat %>%
-  filter(id != x$id) %>%
+  filter(!id %in% x$id) %>%
+  filter(trial_type != "train") %>%
   mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
@@
 
+data %>%
+  group_by(experiment,alignment,change) %>%
+  summarise(n = length(id))
 ```
@@
 ```{r comparisons to chance}
+library(exactRankTests)
+
 data %>%  
@@
 
-lm <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change*Alignment|agent), 
+lm <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change+Alignment|agent), 
               data = m.data, family = binomial, 
@@
 ```{r plot models and data}
+
 ggplot(pd, 
@@
   ylim(0,1)
+
 ```
@@
 
+```{r rsaUtils}
+library(rwebppl)
+
+rsaUtils <- '
+var all_objects = [
+{ shape: "triangle", id:1, location: 1},  
+{ shape: "triangle", id:2, location: 2},
+{ shape: "circle", id:1, location: 2}
+]
+
+var labels = ["dax","wug"]
+
+var lexicon1 = function(utterance, obj){
+utterance.label == "dax" ? obj.shape == "triangle" :
+utterance.label == "wug" ? obj.shape == "circle" : 
+true
+}
+
+var lexicon2 = function(utterance, obj){
+utterance.label == "dax" ? obj.shape == "circle" :
+utterance.label == "wug" ? obj.shape == "triangle" : 
+true
+}
+
+var lexiconObjects = {
+"dax = triangle": {
+triangle: "dax", circle: "wug"
+},
+"dax = circle": {
+triangle: "wug", circle: "dax"
+},
+}
+
+var lexiconObject = {
+"dax = triangle": lexicon1,
+"dax = circle" : lexicon2
+}
+
+var point = function(utterance, obj){
+return obj.location == utterance.point
+}
+
+var utterancePrior = function(obj, lexiconName){
+var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
+var point = uniformDraw(locationsWithShape)
+var label = lexiconObjects[lexiconName][obj.shape]
+return {label: label, point: point}
+}
+
+var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
+'
+```
+
+```{r rsaModel}
+rsaModel <- 'var ObjectPrior = Categorical({vs: all_objects, ps: priorProbs })
+
+var pragmaticListener = function(utterance){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior);
+var obj = sample(ObjectPrior);
+var S1 = speaker(obj, lexiconName);
+observe(S1, utterance)
+return {lexicon: lexiconName, obj: obj.shape}
+}})
+}
+
+var speakerOptimality = 2.25;
+
+var speaker = function(obj, lexiconName){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+}
+
+var literalListener = function(utterance){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior); 
+var lexicon = lexiconObject[lexiconName];
+var obj = sample(ObjectPrior);
+if ("label" in utterance) {
+ var truthValue = lexicon(utterance, obj);
+ condition(truthValue)
+}
+if (utterance.point) {
+ var truthValuePoint = point(utterance, obj);
+ condition(truthValuePoint)
+}
+return obj.shape 
+}})
+}
+
+pragmaticListener({label: "dax", point: 2 })
+'
+```
+
+```{r}
+priorProbsFromR <- list(
+  "pref_inf_same_congruent" =  c(0.0333333, 0.033333, 0.9666667),
+  "pref_inf_same_incongruent" = c(0.9666667, 0.9666667, 0.0333333),
+  "pref_inf_diff_congruent" =  c(0.3583333, 0.3583333, 0.6416667),
+  "pref_inf_diff_incongruent" = c(0.6416667, 0.6416667, 0.3583333),
+  "novel_inf_same_congruent" =  c(0.1666667, 0.1666667, 0.8333333),
+  "novel_inf_same_incongruent" = c(0.8333333, 0.8333333, 0.1666667),
+  "novel_inf_diff_congruent" =  c(0.4083333, 0.4083333, 0.5916667),
+  "novel_inf_diff_incongruent" = c(0.5916667, 0.5916667, 0.4083333)
+)
+
+# get model predictions from webppl
+wp.rs.all <- data.frame()
+for (conditionName in names(priorProbsFromR)) {
+
+  priorProbs <- priorProbsFromR[[conditionName]]
+  rs.wp <- webppl(
+    program_code = paste(rsaUtils, rsaModel, sep='\n'),
+    data = priorProbs,
+    data_var = "priorProbs"
+  )
+  wp.rs.all <- bind_rows(
+    wp.rs.all, 
+    rs.wp %>% 
+      mutate(condition = conditionName,
+             Model = "Full model")
+  )
+}
+
+# common confition names to join by
+con <- c("pref_inf_same_congruent",
+  "pref_inf_same_incongruent",
+  "pref_inf_diff_congruent",
+  "pref_inf_diff_incongruent",
+  "novel_inf_same_congruent",
+  "novel_inf_same_incongruent",
+  "novel_inf_diff_congruent",
+  "novel_inf_diff_incongruent")
+
+#Model predictions from prior only model
+prior_only <- predictions %>%
+  filter(Model == "Prior only")%>%
+  mutate(condition = con)
+
+#Model predictions from no prior model
+no_prior <- predictions %>%
+  filter(Model == "No prior")%>%
+  mutate(condition = con)
+
+# summarizing the data
+data.summary <- data %>%
+  mutate(condition = paste(experiment,change, alignment, sep = "_")) %>%
+  group_by(condition) %>%
+  summarize(n= n(),
+            k = sum(correct_inf))
+
+# joining model predictions and data
+model_comparison <- rbind(
+  left_join(
+  wp.rs.all %>% filter(obj == "circle")%>%mutate(exp = substr(condition,1,4)) %>%select(condition,exp,Model,prob),
+  data.summary),
+  left_join(
+  no_prior%>%mutate(prob = corr, exp = substr(condition,1,4))%>%select(condition,exp,Model,prob),
+  data.summary),
+  left_join(
+  prior_only%>%mutate(prob = corr, exp = substr(condition,1,4))%>%select(condition,exp,Model,prob),
+  data.summary)
+  )
+
+# calculate how well model predicts data
+comp_model<- model_comparison%>%
+  mutate(p_data_given_model = dbinom(size = n, p = prob, x = k, log = T)) %>%
+  group_by(Model) %>%
+  summarize(log_p_data_given_model = sum(p_data_given_model))
+
+comp_model
+
+## log p (data | model)
+## bayes factor_1,2 = p (data | model_1) / p (data | model_2)
+## log bf = log p (data | model_1) - log p (data | model_2)
+
+# Bayes factors full vs other models
+bf_full_no_prior <- exp((comp_model[1,2] - comp_model[2,2]))
+bf_full_no_prior
+
+bf_full_prior_only <- exp((comp_model[1,2] - comp_model[3,2]))
+bf_full_prior_only
+
+# model comparison by experiment
+comp_model_by_exp<- model_comparison%>%
+  mutate(p_data_given_model = dbinom(size = n, p = prob, x = k, log = T)) %>%
+  group_by(Model,exp) %>%
+  summarize(log_p_data_given_model = sum(p_data_given_model))
+
+# Bayes factors full - prior only
+pref_bf_full_prior_only <- exp(comp_model_by_exp[2,3] - comp_model_by_exp[6,3])
+pref_bf_full_prior_only
+
+novel_bf_full_prior_only <- exp(comp_model_by_exp[1,3] - comp_model_by_exp[5,3])
+novel_bf_full_prior_only
+
+```
+
 At what ratio does it flip back to more informative?

### 2018-04-24 experiments/Ex3_weak/Ex3_novel_weak.js

@@ -1,0 +1,1163 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-04-24 experiments/Ex3_weak/Ex3_pref_weak.js

@@ -1,0 +1,832 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-04-24 experiments/novelty_pilot/mcc_novelty_weak.js

@@ -1,0 +1,595 @@
+
+// ## Helper functions
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function getTime1() {
+    return startTime = (new Date()).getTime();
+};
+
+// Get a random integer less than n.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+};
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+};
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+
+function sourceSound(c) {
+        document.getElementById("sound").src=c;
+    };
+function playSound() {
+    document.getElementById("sound").play();
+      };
+
+
[…]

### 2018-04-24 experiments/preference_pilot/mcc_preference_weak.js

@@ -1,0 +1,526 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function getTime1() {
+    return startTime = (new Date()).getTime();
+};
+
+// Get a random integer less than n.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+};
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+};
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+
+function sourceSound(c) {
+        document.getElementById("sound").src=c;
+    };
+function playSound() {
+    document.getElementById("sound").play();
+      };
[…]

### 2018-04-27 stats/mcc_pref.weak.Rmd
novelty weak 2 second exp

--- 2018-02-07 stats/mcc_pref.Rmd
@@
 ---
-title: "MCC_Preference"
+title: "MCC_Preference_Weak"
 author: "Manuel Bohn"
-date: "26 1 2018"
+date: "26 4 2018"
 output: html_document
@@
 ## importing data
-d <- read_csv(file="pref.data.csv") %>%
+d <- read_csv(file="pref.weak.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 
+# check if someone needs to be excluded because wrong in training
+# no one
+d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(correct = mean(correct)) %>%
+  filter(correct == 0)
+
 ```
@@
 
-ms <- d %>%
+p1 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change, id) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+T-tests against chance for each speaker change conditions
+```{r}
+## t tests against chance
+d %>%
   filter(trial_type == "test") %>%
@@
   summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
+  summarise(correct = list(correct)) %>%
+  group_by(change) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(change,df,t_value,p_value) %>%
+  knitr::kable(digits = 2)
 
-ggplot(ms, 
-       aes(x = change, y = mean, fill = change)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few(base_size = 12) + 
-  ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+```
+
+ChoiceAgent can be seen as an approximation for "item".
+
+```{r}
+## model
+library(lme4)
+
+data_cg <- d%>%
+  filter(trial_type == "test")%>%
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
+  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
+
+# maximal converging model
+lm <- glmer(correct ~ change + (change |id) + (change |choiceAgent), 
+              data = data_cg, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lm)
 ```
@@
 ```
-
-T-tests against chance for each speaker change conditions
-```{r}
-## t tests against chance
-d %>%
-  filter(trial_type == "test") %>%
-  group_by(change, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(change) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(change,df,t_value,p_value) %>%
-  knitr::kable(digits = 2)
-
-```
-
-ChoiceAgent can be seen as an approximation for "item".
-
-```{r}
-## model
-library(lme4)
-
-data_cg <- d%>%
-  filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
-
-# maximal converging model
-lm <- glmer(correct ~ change +
-              (1 |id) + (1 |choiceAgent), 
-              data = data_cg, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-summary(lm)
-```

### 2018-04-27 experiments/novelty_pilot/mcc_novelty_weak.js

@@ -123,7 +123,7 @@ $("#button").click(function() {
 // Progress bar
 
 $("#progressbar").progressbar();
-$("#progressbar").progressbar( "option", "max", 10);
+$("#progressbar").progressbar( "option", "max", 12);
 
 // move progress bar
 
@@ -167,29 +167,29 @@ $.ajax({
 
 // Variables and randomization for the experiment
 
-var trial = ["train","train","finTrain",1,2,3,4,5,6]
+var trial = ["train","train","finTrain",1,2,3,4,5,6,7,8]
 
 // agents for training and test
 var trainAgents = ["Elephant","Pig"]
-var allAgents = ["Mouse","Dog","Tiger","Cat","Sheep","Bear","Monkey","Frog","Bunny"];
+var allAgents = ["Elephant","Pig","Frog","Mouse","Monkey","Bunny","Dog","Bear","Tiger","Cat","Sheep","Beaver"];
 
 // randomization of agent and speaker change agent order for test trials
-var testAgents = allAgents.sort(() => .5 - Math.random()).slice(0,6);
+var testAgents = allAgents.sort(() => .5 - Math.random()).slice(0,8);
 var remainingAgent = $.grep(allAgents, function(value) {
     return $.inArray(value, testAgents) < 0;});
-var testAltAgent = remainingAgent.sort(() => .5 - Math.random()).slice(0,3);
+var testAltAgent = remainingAgent.sort(() => .5 - Math.random()).slice(0,4);
 var agents = trainAgents.concat(testAgents);
 var altAgents = testAltAgent;
 
 // randomizing order of speaker change
 var trainSpeakerChange = [["false","false"]];
-var testSpeakerChange = shuffle([shuffle(["true","false"]),shuffle(["false","true"]),shuffle(["false","true"])]);
+var testSpeakerChange = shuffle([shuffle(["true","false"]),shuffle(["false","true"]),shuffle(["false","true"]),shuffle(["false","true"])]);
 var speakerChange = trainSpeakerChange.concat(testSpeakerChange);
 
 // objects on tables in training and test (fruits = toys)
 var trainFruitLeft = ["car","duck"];
 var trainFruitRight = ["bear","ball"];
-var fruits = ["t1","t2","t3","t18","t5","t6","t7","t8","t17","t10", "t11","t12","t13","t15","t16"];
[…]

### 2018-04-27 stats/data_preprocessing.R

@@ -1,4 +1,4 @@
-install.packages("stringr")
+
 library(rjson)
 library(tidyr)
 library(stringr)
@@ -16,12 +16,13 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 
 # select all files from individual workers
-files <- dir("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results")
+#files <- dir("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak/production-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_novelty_weak/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -35,12 +36,12 @@ names(novel.data) = c("id","alltrial","condition","agent","altAgent","leftObject
 novel.data$pick= str_sub(novel.data$pick,73,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(id)]
-novel.data$id = paste(novel.data$id,novel.data$condition,sep="_")
+#novel.data$id = paste(novel.data$id,novel.data$condition,sep="_")
 # check resulting datafile
 str(novel.data)
 head(novel.data)
 # write csv file for further analysis
-write.csv(novel.data, file="novel.data.csv")
+write.csv(novel.data, file="novel.weak.data.csv")
 
 ################################################################################################################
 
@@ -49,12 +50,13 @@ write.csv(novel.data, file="novel.data.csv")
 ######## preference ###########
 ################################################################################################################
 
-files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
+#files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/cosub_preference/anonymized-results/",f,sep="")
[…]

### 2018-05-01 stats/ex3_comparisons.Rmd
starting with bda

@@
 
+```{r rsa model2}
+rsaModel2 <- 'var ObjectPrior = Categorical({vs: all_objects, ps: [0.1666667, 0.1666667, 0.8333333] })
+
+var pragmaticListener = function(utterance){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior);
+var obj = sample(ObjectPrior);
+var S1 = speaker(obj, lexiconName);
+observe(S1, utterance)
+return {lexicon: lexiconName, obj: obj.shape}
+}})
+}
+
+var speakerOptimality = 2.25;
+
+var speaker = function(obj, lexiconName){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+}
+
+var literalListener = function(utterance){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior); 
+var lexicon = lexiconObject[lexiconName];
+var obj = sample(ObjectPrior);
+if ("label" in utterance) {
+ var truthValue = lexicon(utterance, obj);
+ condition(truthValue)
+}
+if (utterance.point) {
+ var truthValuePoint = point(utterance, obj);
+ condition(truthValuePoint)
+}
+return obj.shape 
+}})
+}
+
+// pragmaticListener({label: "dax", point: 2 })
+
+var addNoise = function(dist, noiseParam){
+   Infer({model: function(){ 
+      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
+    }
+   })
+}
+
+var model = function(){
+   var noise = uniform(0, 1)
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 })
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+   map(data, function(d){ 
+      observe(noisyModelPredictions, d)
+    } )
+  return [noise, modelPredictions]
+}
+
+model() 
+'
+```
+
+```{r}
+
+obs_data <- data %>% filter (Change == "Same speaker", Alignment == "Congruent", Experiment =="Novelty") %>% select(correct_inf)
+
+bda <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
+  data = obs_data,
+  data_var = "data"
+)
+
+```
+
 ```{r}

### 2018-05-01 stats/mcc_priors_overview.Rmd
starting with bda

---
title: "MCC Prior Overview"
author: "Manuel Bohn"
date: "9 4 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
```

```{r data}
d1 <- read_csv(file="novel.weak.data2.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "2_medium")

x <- d1 %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct)) %>%
  filter(n > 2)

d1 <- d1 %>%
  filter(!id %in% x$id)

d2 <- read_csv(file="novel.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "1_weak")

d3 <- read_csv(file="novel.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

d4 <-read_csv(file="pref.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

d5 <-read_csv(file="pref.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "2_medium")

d <- bind_rows(d1,d2,d3,d4,d5)
```

```{r plot data}

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(strength,condition,change, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(p1, 
       aes(x = change, y = mean, fill = change)) +
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 12) + 
  facet_grid(condition ~ strength , scales = "free_x", space = "free_x" ) +
  ylim(0,1)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

```

### 2018-05-01 stats/data_preprocessing.R

@@ -17,12 +17,13 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 # select all files from individual workers
 #files <- dir("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak2/production-results")
+#files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak2/sandbox-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_novelty_weak/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_novelty_weak2/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -41,7 +42,7 @@ novel.data = novel.data[order(id)]
 str(novel.data)
 head(novel.data)
 # write csv file for further analysis
-write.csv(novel.data, file="novel.weak.data.csv")
+write.csv(novel.data, file="novel.weak.data2.csv")
 
 ################################################################################################################
 

### 2018-05-02 stats/ex3_comparisons.Rmd
noisy model predictions

--- 2018-04-24 stats/ex3_comparisons.Rmd
@@
 
+```{r rsa model2}
+rsaModel2 <- '
+
+var pragmaticListener = function(utterance, priorProbs){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior);
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+var S1 = speaker(obj, lexiconName, priorProbs);
+observe(S1, utterance)
+return {lexicon: lexiconName, obj: obj.shape == "circle" ? 1 : 0}
+}})
+}
+
+var speakerOptimality = 2.25;
+
+var speaker = function(obj, lexiconName, priorProbs){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance, priorProbs);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+}
+
+var literalListener = function(utterance, priorProbs){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior); 
+var lexicon = lexiconObject[lexiconName];
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+if ("label" in utterance) {
+ var truthValue = lexicon(utterance, obj);
+ condition(truthValue)
+}
+if (utterance.point) {
+ var truthValuePoint = point(utterance, obj);
+ condition(truthValuePoint)
+}
+return obj.shape 
+}})
+}
+
+var addNoise = function(dist, noiseParam){
+   Infer({model: function(){ 
+      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
+    }
+   })
+}
+
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = uniform(0, 1)
+
+  var conditionOutput = map(function(conditionInfo){
+
+    var conditionSpecificData =  _.filter(allData, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors.priorProbs)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return {noisyModelPred: Math.exp(noisyModelPredictions.score(1)), noise: noise, Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment}
+
+}, allConditions)
+
+ return conditionOutput
+}
+
+Infer({model: model, method: "MCMC", samples: 10})
+'
+```
+
+```{r}
+
+allConditions <- data %>%
+  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
+         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
+         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty")) %>%
+  group_by(Experiment,Change,Alignment)%>%
+  summarise(correct_inf = mean(correct_inf)) %>%
+  select(Change, Alignment,Experiment)
+
+allPriorProbs <- data.frame(
+  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+
+allPriorProbs$priorProbs = list(
+    c(0.0333333, 0.033333, 0.9666667), 
+    c(0.9666667, 0.9666667, 0.0333333),
+    c(0.3583333, 0.3583333, 0.6416667),
+    c(0.6416667, 0.6416667, 0.3583333),
+    c(0.1666667, 0.1666667, 0.8333333),
+    c(0.8333333, 0.8333333, 0.1666667),
+    c(0.4083333, 0.4083333, 0.5916667),
+    c(0.5916667, 0.5916667, 0.4083333))
+
+bda <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR"
+)
+
+jsonlite::toJSON(priorProbs, pretty = T)
+
+```
+
 ```{r}

### 2018-05-02 stats/data_preprocessing_kids.R

@@ -71,7 +71,7 @@ pref.data = pref.data[order(id)]
 str(pref.data)
 head(pref.data)
 # write csv file for further analysis
-write.csv(pref.data, file="kids_pref.data.csv")
+write.csv(pref.data, file="kids_pref_handcoding.data.csv")
 
 ################################################################################################################
 

### 2018-05-02 stats/ex3_comparisons.Rmd
noisy model predictions

@@
 
-    var conditionSpecificData =  _.filter(allData, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})
+    var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
 
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Experiment: conditionInfo.Experiment})
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
 
@@
 
-jsonlite::toJSON(priorProbs, pretty = T)
+jsonlite::toJSON(allConditions, pretty = T)
+
+jsonlite::toJSON(allPriorProbs, pretty = T)
 

### 2018-05-03 stats/ex3_comparisons.Rmd
weaker preference version

@@
 observe(S1, utterance)
-return {lexicon: lexiconName, obj: obj.shape == "circle" ? 1 : 0}
+return obj.shape == "circle" ? 1 : 0
 }})
@@
 
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors.priorProbs)
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
    var noisyModelPredictions = addNoise(modelPredictions, noise)
@@
    map(function(d){ 
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
       observe(noisyModelPredictions, d.correct_inf)
@@
 
-  return {noisyModelPred: Math.exp(noisyModelPredictions.score(1)), noise: noise, Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment}
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
 
@@
 
- return conditionOutput
+ return extend(_.fromPairs(conditionOutput), {noise: noise})
 }
-
-Infer({model: model, method: "MCMC", samples: 10})
 '
@@
   data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR"
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T)
 )
 
-jsonlite::toJSON(allConditions, pretty = T)
+jsonlite::toJSON(data, pretty = T)
 
 jsonlite::toJSON(allPriorProbs, pretty = T)
+
+filter(bda, Iteration == 1)
+
+posterior.noise <- bda %>%
+  filter(Parameter == "noise")%>%
+  summarise(noise = mean(value))
+
+posterior.predictive = bda %>%
+  filter(Parameter != "noise") %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2)
+
+noisy.model <- posterior.predictive %>%
+  mutate(Model="Noisy Model")%>%
+  group_by(Model,Experiment,Change,Alignment)%>%
+  multi_boot_standard(col = "value")
+
+p.com <- bind_rows(noisy.model,pd)
+
+ggplot(p.com, 
+       aes(x = Change, y = mean, fill = Alignment)) +
+  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
+  labs(x=" ",y="Proportion Choosing More Informative")+
+  facet_grid(Experiment ~ Model)+
+  theme_few(base_size = 12) + 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  ylim(0,1)
 

### 2018-05-03 experiments/preference_pilot/mcc_preference_weak2.js

@@ -1,0 +1,526 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function getTime1() {
+    return startTime = (new Date()).getTime();
+};
+
+// Get a random integer less than n.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+};
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+};
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+
+function sourceSound(c) {
+        document.getElementById("sound").src=c;
+    };
+function playSound() {
+    document.getElementById("sound").play();
+      };
[…]

### 2018-05-08 stats/ex3_comparisons.Rmd
adding noisy model predictions and weaker priors

@@
   summarise(n = length(id))
+
 ```
@@
 names(plot2) = c("Experiment","Data","Model","Comp")
+plot5 <- data.frame(noisy.model$Experiment,pd$mean[pd$Model=="Data"],noisy.model$mean,rep("Data vs Noisy Model",8))
+names(plot5) = c("Experiment","Data","Model","Comp")
+
 plot3 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
@@
 
-plot <- rbind(plot3,plot4,plot1,plot2)
+plot <- rbind(plot1,plot2,plot5)
 
@@
   geom_point()+
-  facet_grid(Experiment~Comp)+
+  facet_grid(~Comp)+
   stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
@@
 
+## check one iteration
+filter(bda, Iteration == 1)
+
 jsonlite::toJSON(data, pretty = T)
@@
 
-filter(bda, Iteration == 1)
+## distribution of noise
+posterior.noise <- bda %>%
+  filter(Parameter == "noise")
 
-posterior.noise <- bda %>%
-  filter(Parameter == "noise")%>%
-  summarise(noise = mean(value))
+ggplot(posterior.noise, aes(x = value))+
+  geom_histogram()
 
+## distribution of model predictions
 posterior.predictive = bda %>%
@@
   geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2)
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 
@@
   mutate(Model="Noisy Model")%>%
-  group_by(Model,Experiment,Change,Alignment)%>%
-  multi_boot_standard(col = "value")
+  group_by(Model,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
 
+## joining noisy model predictions with other predictions
 p.com <- bind_rows(noisy.model,pd)

### 2018-05-08 stats/mcc_pref.weak2.Rmd
adding noisy model predictions and weaker priors

--- 2018-04-27 stats/mcc_pref.weak.Rmd
@@
 ## importing data
-d <- read_csv(file="pref.weak.data.csv") %>%
+d <- read_csv(file="pref.weak.data2.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 # maximal converging model
-lm <- glmer(correct ~ change + (change |id) + (change |choiceAgent), 
+lm <- glmer(correct ~ change + (change |id) + (change || choiceAgent), 
               data = data_cg, family = binomial, 
@@
 
-Conditions by agents.
-Unequal distribution of agents across change leads to seemingly strange patterns for some agents.
-However, these strange results are always those with very few data points (e.g.
-Tiger novelty speaker change is only one data point).
-For those cells with more than five data points, the pattern is very similar to the overall pattern.
-Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment.
-This causes the unequal distribution.
-```{r trials per condition and agent}
-d %>%
-  filter(trial_type == "test") %>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  group_by(choiceAgent,change) %>%
-  summarise(n = length(choiceAgent), 
-            correct = mean(correct)) %>%
-  knitr::kable(digits = 2)
-```
-
 ```{r plot agents}

### 2018-05-08 stats/data_preprocessing.R

@@ -4,7 +4,6 @@ library(tidyr)
 library(stringr)
 library(dplyr)
 library(data.table)
-library("stringr")
 
 
 ##
@@ -52,12 +51,14 @@ write.csv(novel.data, file="novel.weak.data2.csv")
 ################################################################################################################
 
 #files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
+#files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak2/production-results")
+
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak2/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -76,7 +77,7 @@ pref.data = pref.data[order(id)]
 str(pref.data)
 head(pref.data)
 # write csv file for further analysis
-write.csv(pref.data, file="pref.weak.data.csv")
+write.csv(pref.data, file="pref.weak.data2.csv")
 
 ################################################################################################################
 

### 2018-05-08 stats/ex3_comparisons.Rmd
adding noisy model predictions and weaker priors

@@
 names(plot2) = c("Experiment","Data","Model","Comp")
-plot5 <- data.frame(noisy.model$Experiment,pd$mean[pd$Model=="Data"],noisy.model$mean,rep("Data vs Noisy Model",8))
-names(plot5) = c("Experiment","Data","Model","Comp")
 
-plot3 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
-names(plot3) = c("Experiment","Data","Model","Comp")
-plot4 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
-names(plot4) = c("Experiment","Data","Model","Comp")
-
-plot <- rbind(plot1,plot2,plot5)
+plot <- rbind(plot1,plot2)
 
@@
 
-```{r}
+```{r noisy model}
 
@@
 
+## check what things look like in JSON format
 jsonlite::toJSON(data, pretty = T)
@@
 
+## correlations for model comparisons
+
+plot3 <- data.frame(noisy.model$Experiment,pd$mean[pd$Model=="Data"],noisy.model$mean,rep("Data vs Noisy Model",8))
+names(plot3) = c("Experiment","Data","Model","Comp")
+
+plot_noise <- rbind(plot,plot3)
+
+ggplot(data = plot_noise,aes(x = Model, y = Data, col = Comp)) +
+  geom_point()+
+  facet_grid(~Comp)+
+  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
+  geom_smooth(method = "lm", se = F, col = "black")+
+  theme_few() + 
+  guides(col = F)+
+  scale_colour_solarized()
+
 ```
 
-```{r}
+```{r simple BF model comparisons}
 priorProbsFromR <- list(

### 2018-05-10 stats/mcc_priors_overview.Rmd
adding noisy model predictions and weaker priors
add weaker prior dis-preference

@@
 ```{r data}
-d1 <- read_csv(file="novel.weak.data2.csv") %>%
+d3 <- read_csv(file="novel.weak.data2.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-x <- d1 %>%
-  filter(trial_type == "train") %>%
-  group_by(id)%>%
-  summarise(n = length(correct)) %>%
-  filter(n > 2)
-
-d1 <- d1 %>%
-  filter(!id %in% x$id)
-
-d2 <- read_csv(file="novel.weak.data.csv") %>%
+d4 <- read_csv(file="novel.weak.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d3 <- read_csv(file="novel.data.csv") %>%
+d1 <- read_csv(file="novel.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d4 <-read_csv(file="pref.data.csv") %>%
+d2 <-read_csv(file="pref.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d <- bind_rows(d1,d2,d3,d4,d5)
+d6 <-read_csv(file="pref.weak.data3.csv") %>%
+  mutate(trial_type = ifelse(trial == "train", "train", "test"),
+         strength = "1_weak")
+
+d <- bind_rows(d1,d2,d3,d4,d5,d6)
+
+# check if someone got both training trials wrong
+d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(sum = sum(correct)) %>%
+  filter(sum == 0)
+
+# check if someone did multiple experiments
+# yes, six people
+d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(n = length(correct)) %>%
+  filter(n > 2)
+
+# exclude those who did both experiments
+# keep first time they participated
+
+d <- d %>% 
+  distinct(id, alltrial, .keep_all = TRUE)
 ```

### 2018-05-10 experiments/preference_pilot/mcc_preference_weak4.js

@@ -1,0 +1,526 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function getTime1() {
+    return startTime = (new Date()).getTime();
+};
+
+// Get a random integer less than n.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+};
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+};
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+
+function sourceSound(c) {
+        document.getElementById("sound").src=c;
+    };
+function playSound() {
+    document.getElementById("sound").play();
+      };
[…]

### 2018-05-10 experiments/preference_pilot/mcc_preference_weak5.js

@@ -1,0 +1,564 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function getTime1() {
+    return startTime = (new Date()).getTime();
+};
+
+// Get a random integer less than n.
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+};
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+};
+
+function shuffle(array) {
+    for (var i = array.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = array[i];
+        array[i] = array[j];
+        array[j] = temp;
+    }
+    return array;
+}
+
+
+function sourceSound(c) {
+        document.getElementById("sound").src=c;
+    };
+function playSound() {
+    document.getElementById("sound").play();
+      };
[…]

### 2018-05-10 stats/data_preprocessing.R

@@ -52,13 +52,13 @@ write.csv(novel.data, file="novel.weak.data2.csv")
 
 #files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
 #files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak2/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak3/production-results")
 
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak2/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak3/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -77,7 +77,7 @@ pref.data = pref.data[order(id)]
 str(pref.data)
 head(pref.data)
 # write csv file for further analysis
-write.csv(pref.data, file="pref.weak.data2.csv")
+write.csv(pref.data, file="pref.weak.data3.csv")
 
 ################################################################################################################
 

### 2018-05-10 experiments/preference_pilot/mcc_preference_weak5.js
add weaker prior dis-preference

@@ -402,7 +402,7 @@ var experiment = {
     setTimeout(function() {      
     $(".fruit_r").bind("click", experiment.eat);
     $(".fruit_l").bind("click", experiment.eat);
-}, 000);
+}, 7000);
   
   },
  // sequence of events during training exposure

### 2018-05-15 stats/ex3_comparisons.Rmd
add regularized prior bda models, prior only noise model

@@
 rsaModel2 <- '
-
 var pragmaticListener = function(utterance, priorProbs){
@@
 }
+'
+```
 
+```{r bda model rsa noise}
+bdaModel.rsa.noise <-'
 var allConditions = dataFromR.allConditions
@@
 var model = function(){
-   var noise = uniform(0, 1)
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
 
@@
  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r bda model prior noise}
+bdaModel.prior.noise <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
+
+   map(function(d){ 
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r bda model rsa regularizedPrior noise}
+bdaModel.rsa.regularizedPrior.noise <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {noise: noise, priorExponent: priorExponent})
+}
+'
+```
+
+```{r bda model rsa regularizedPrior}
+bdaModel.rsa.regularizedPrior <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+
+   map(function(d){ 
+     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
+      observe(modelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
 }
@@
 bda <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, sep='\n'),
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
+  #program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
   data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
@@
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 5000, burn = 2500, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
 )
@@
 posterior.noise <- bda %>%
-  filter(Parameter == "noise")
+  filter(Parameter %in% c("noise", "priorExponent"))
 
 ggplot(posterior.noise, aes(x = value))+
-  geom_histogram()
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
 
@@
 posterior.predictive = bda %>%
-  filter(Parameter != "noise") %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
   separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
@@
 ggplot(data = plot_noise,aes(x = Model, y = Data, col = Comp)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
   geom_point()+
   facet_grid(~Comp)+
-  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
-  geom_smooth(method = "lm", se = F, col = "black")+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  #stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
+  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
   theme_few() + 

### 2018-05-15 stats/ex3_comparisons.Rmd
add sketchy marg likelihood calc model

@@
       observe(modelPredictions, d.correct_inf)
+      // factor(modelPredictions.score(d.correct_inf))
     }, conditionSpecificData)
@@
 '
+```
+
+```{r}
+bdaModel.rsa.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+
+   var loglike = sum(map(function(d){ 
+      return modelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(loglike)
+}
+'
+
 ```

### 2018-05-16 stats/ex1_2_overview.Rmd
noisy / regularized models

---
title: "MCC Ex 1 and 2 overview"
author: "Manuel Bohn"
date: "9 4 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
```

```{r data}
d1 <- bind_rows(read_csv(file="novel.data.csv"),
               read_csv(file="pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         control = ifelse(change == "true", "true" , "false"))

d2 <- read_csv(file="inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

d <- bind_rows(d1,d2) %>%
  mutate(condition = ifelse(condition == "preference", 2, ifelse(condition == "novelty", 3,1)))

```

```{r plot data}

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition ,control, id) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Info."))) +
  theme_few(base_size = 14) + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized(name="Condition",
                     breaks=c("false", "true"),
                     labels=c("Test", "Control"))+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

```

### 2018-05-16 stats/ex3_comparisons.Rmd
noisy / regularized models

@@
 
+```{r bda model rsa regularizedPrior}
+bdaModel.rsa.regularizedPrior <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+
+   map(function(d){ 
+     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
+      observe(modelPredictions, d.correct_inf)
+      // factor(modelPredictions.score(d.correct_inf))
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
+}
+'
+```
+
+```{r bda model prior regularizedPrior}
+bdaModel.prior.regularizedPrior <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+    var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   map(function(d){ 
+     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
+      observe(modelPredictions, d.correct_inf)
+      // factor(modelPredictions.score(d.correct_inf))
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
+}
+'
+```
+
 ```{r bda model rsa regularizedPrior noise}
@@
 
-```{r bda model rsa regularizedPrior}
-bdaModel.rsa.regularizedPrior <-'
+```{r bda model prior regularizedPrior noise}
+bdaModel.prior.regularizedPrior.noise <-'
 var allConditions = dataFromR.allConditions
@@
    var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
 
@@
 
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
 
    map(function(d){ 
-     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
-      observe(modelPredictions, d.correct_inf)
-      // factor(modelPredictions.score(d.correct_inf))
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
+      observe(noisyModelPredictions, d.correct_inf)
     }, conditionSpecificData)
 
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
 
@@
 
- return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
+ return extend(_.fromPairs(conditionOutput), {noise: noise, priorExponent: priorExponent})
 }
@@
 
-```{r}
-bdaModel.rsa.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
-
-   var loglike = sum(map(function(d){ 
-      return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(loglike)
-}
-'
-
-```
-
-```{r noisy model}
+```{r model setup}
 
@@
     c(0.5916667, 0.5916667, 0.4083333))
+```
 
+```{r predictions rsa noise}
 bda <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
-  #program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
   data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
@@
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 1000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
 )
-
-## check one iteration
-filter(bda, Iteration == 1)
-
-## check what things look like in JSON format
-jsonlite::toJSON(data, pretty = T)
-
-jsonlite::toJSON(allPriorProbs, pretty = T)
 
@@
 
-noisy.model <- posterior.predictive %>%
-  mutate(Model="Noisy Model")%>%
-  group_by(Model,Experiment,Change,Alignment) %>%
+noisy.rsa.model <- posterior.predictive %>%
+  mutate(Model="Noisy RSA Model",
+         Adjustment = "Noise",
+         Type = "RSA")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
   summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
 
+```
+
+```{r predictions prior noise}
+bda1 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise1 <- bda1 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise1, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive1 = bda1 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive1, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
+noisy.prior.model <- posterior.predictive1 %>%
+  mutate(Model="Noisy Prior Model",
+         Adjustment = "Noise",
+         Type = "Prior only")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r predictions rsa regularized prior}
+bda2 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise2 <- bda2 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise2, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive2 = bda2 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive2, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
+regPrior.rsa.model <- posterior.predictive2 %>%
+  mutate(Model="Regularized RSA Model",
+         Adjustment = "Regularized Prior",
+         Type = "RSA")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r predictions prior regularized prior}
+bda3 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise3 <- bda3 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise3, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive3 = bda3 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive3, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
+regPrior.prior.model <- posterior.predictive3 %>%
+  mutate(Model="Regularized Prior Model",
+         Adjustment = "Regularized Prior",
+         Type = "Prior only")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r predictions rsa noise regularized prior}
+bda4 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise4 <- bda4 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise4, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive4 = bda4 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive4, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
+noisy.regPrior.rsa.model <- posterior.predictive4 %>%
+  mutate(Model="Noisy Regularized RSA Model",
+         Adjustment = "Noise & Regularized Prior",
+         Type = "RSA")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r predictions prior noise regularized prior}
+bda5 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise5 <- bda5 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise5, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive5 = bda5 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive5, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+## Bayesian credible intervals
+
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
+
+noisy.regPrior.prior.model <- posterior.predictive5 %>%
+  mutate(Model="Noisy Regularized Prior Model",
+         Adjustment = "Noise & Regularized Prior",
+         Type = "Prior only")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r}
 ## joining noisy model predictions with other predictions
-p.com <- bind_rows(noisy.model,pd)
+no.adj.models <- pd %>%
+  mutate(Type = ifelse(Model == "Full model" | Model == "No prior","RSA",ifelse(Model == "Data","Data","Prior only")),
+         Adjustment = "None")
+
+p.com <- bind_rows(
+  noisy.rsa.model,
+  noisy.prior.model,
+  regPrior.rsa.model,
+  regPrior.prior.model,
+  noisy.regPrior.rsa.model,
+  noisy.regPrior.prior.model,
+  no.adj.models
+  )
 
@@
   labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Model)+
+  facet_grid(Experiment ~ Model, labeller = label_wrap_gen(width=5))+
   theme_few(base_size = 12) + 
@@
 
+```
+
+```{r}
 ## correlations for model comparisons
 
-plot3 <- data.frame(noisy.model$Experiment,pd$mean[pd$Model=="Data"],noisy.model$mean,rep("Data vs Noisy Model",8))
-names(plot3) = c("Experiment","Data","Model","Comp")
+p.com$Data = rep(pd$mean[pd$Model=="Data"],10)
 
-plot_noise <- rbind(plot,plot3)
+plot.model <- p.com %>%
+  filter(Model != "Data", Model != "No prior" )
 
-ggplot(data = plot_noise,aes(x = Model, y = Data, col = Comp)) +
+ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
   geom_point()+
-  facet_grid(~Comp)+
+  facet_grid(Type~Adjustment)+
   coord_fixed()+
   xlim(0,1)+ylim(0,1)+
-  #stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
+  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
   geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
@@
   scale_colour_solarized()
+
+```
+
+```{r model rsa loglikelihood}
+bdaModel.rsa.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+
+   var loglike = sum(map(function(d){
+
+  // display(JSON.stringify(modelPredictions.score(d.correct_inf)))
+
+  return modelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(loglike)
+}
+'
+```
+
+```{r rsa loglikelihood}
+llh <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 100, verbose = T)
+)
 

### 2018-05-16 stats/mcc_pref.kids.Rmd
noisy / regularized models

--- 2018-02-07 stats/mcc_pref.Rmd
@@
 ---
-title: "MCC_Preference"
+title: "MCC PRefere"
 author: "Manuel Bohn"
-date: "26 1 2018"
+date: "26 4 2018"
 output: html_document
@@
 ## importing data
-d <- read_csv(file="pref.data.csv") %>%
+
+d <- bind_rows(read_csv(file="kids_pref.data.csv"),
+              read.csv(file="kids_pref_handcoding.data.csv", sep = ";")) %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
+
+# children who need to be dropped
+drop <- c("Dryrun","180426_3_pref","180502_1_pref","180503_1_pref","180503_2_pref","180504_1_pref","180511_2_pref","180511_1_pref")
+
+d <- d %>%
+  filter(!id %in% drop)
 
@@
 
+# check if someone needs to be excluded because wrong in training
+# no one
+d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(correct = mean(correct)) %>%
+  filter(correct == 0)
+```
+```{r kids per age group}
+
+d %>%
+  group_by(age)%>%
+  summarise(n = length(unique(id)))%>%
+  knitr::kable(digits = 2)
 ```
@@
 
-ms <- d %>%
+p1 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change,age, id) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~age)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+T-tests against chance for each speaker change conditions
+```{r}
+## t tests against chance
+d %>%
   filter(trial_type == "test") %>%
@@
   summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
+  summarise(correct = list(correct)) %>%
+  group_by(change) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(change,df,t_value,p_value) %>%
+  knitr::kable(digits = 2)
 
-ggplot(ms, 
-       aes(x = change, y = mean, fill = change)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few(base_size = 12) + 
-  ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+```
+
+ChoiceAgent can be seen as an approximation for "item".
+
+```{r}
+## model
+library(lme4)
+
+data_cg <- d%>%
+  filter(trial_type == "test")%>%
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))
+
+# maximal converging model
+lm <- glmer(correct ~ age + change + (age * change |id) + (age * change |choiceAgent), 
+              data = data_cg, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lm)
 ```

### 2018-05-16 stats/mcc_pref.weak4.Rmd
noisy / regularized models

--- 2018-05-08 stats/mcc_pref.weak2.Rmd
@@
 ---
-title: "MCC_Preference_Weak"
+title: "MCC_Preference_Weak_Dispref"
 author: "Manuel Bohn"
-date: "26 4 2018"
+date: "10 5 2018"
 output: html_document
@@
 ## importing data
-d <- read_csv(file="pref.weak.data2.csv") %>%
+d <- read_csv(file="pref.weak.data4.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 # check if someone needs to be excluded because wrong in training
+# one person
+x <- d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(correct = mean(correct)) %>%
+  filter(correct == 0)
+
+# check if someone participated twice
 # no one
@@
   group_by(id)%>%
-  summarise(correct = mean(correct)) %>%
-  filter(correct == 0)
+  summarise(n = length(correct)) %>%
+  filter(n > 2)
+
+d <- d %>%
+  filter(!id %in% x$id)
 
@@
   filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))
 
 # maximal converging model
-lm <- glmer(correct ~ change + (change |id) + (change || choiceAgent), 
+lm <- glmer(correct ~ change + (change |id) + (change | choiceAgent), 
               data = data_cg, family = binomial, 

### 2018-05-16 stats/mcc_pref.weak5.Rmd
noisy / regularized models

--- 2018-05-16 stats/mcc_pref.weak4.Rmd
@@
 ---
-title: "MCC_Preference_Weak_Dispref"
+title: "MCC_Preference_Weak_Pref/Dispref"
 author: "Manuel Bohn"
-date: "10 5 2018"
+date: "26 4 2018"
 output: html_document
@@
 ## importing data
-d <- read_csv(file="pref.weak.data4.csv") %>%
+d <- read_csv(file="pref.weak.data5.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 # check if someone needs to be excluded because wrong in training
-# one person
+
 x <- d %>%
@@
   filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
+  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
 
@@
 summary(lm)
+```
+
+# Analysis by emotion
+```{r plot by emotion}
+
+p1 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change,emotion, id) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  facet_wrap(~emotion) +
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+```{r by emotion}
+## model
+library(lme4)
+
+data_emo <- d%>%
+  filter(trial_type == "test")%>%
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
+  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
+
+# maximal converging model
+lemo <- glmer(correct ~ change * emotion + (change |id) + (change | choiceAgent), 
+              data = data_emo, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lemo)
 ```

### 2018-05-16 experiments/preference_pilot/mcc_preference.js

@@ -502,15 +502,15 @@ var experiment = {
     // animate object when visible and pointed at 
       if (experiment.agentOrient[0][0] == "point_r") {
         setTimeout(function() {
-            $("#fruit_r").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
-            $("#fruit_r").animate({width: "250px",opacity: '1', queue: false, duration: 1000})
+            $("#fruit_r").animate({width: "180px",opacity: '0.3', queue: false, duration: 1000});
+            $("#fruit_r").animate({width: "130px",opacity: '1', queue: false, duration: 1000})
         }, 2500)
     }; 
       
     if (experiment.agentOrient[0][0] == "point_l") {
         setTimeout(function() {
-            $("#fruit_l").animate({width: "300px",opacity: '0.3', queue: false, duration: 1000});
-            $("#fruit_l").animate({width: "250px",opacity: '1', queue: false, duration: 1000})
+            $("#fruit_l").animate({width: "180px",opacity: '0.3', queue: false, duration: 1000});
+            $("#fruit_l").animate({width: "130px",opacity: '1', queue: false, duration: 1000})
         }, 2500)
     }; 
     

### 2018-05-16 stats/data_preprocessing.R

@@ -52,13 +52,13 @@ write.csv(novel.data, file="novel.weak.data2.csv")
 
 #files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
 #files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak3/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak5/production-results")
 
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak3/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_preference_weak5/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -67,8 +67,8 @@ for (f in files) {
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
-pref.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.pref","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(pref.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+pref.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.pref","^data.emo","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
+names(pref.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","emotion","trial","change","rt","correct") 
 pref.data$pick= str_sub(pref.data$pick,76,str_length(pref.data$pick)-4)
 pref.data = pref.data[!duplicated(pref.data), ]
 pref.data = pref.data[order(id)]
@@ -77,7 +77,7 @@ pref.data = pref.data[order(id)]
 str(pref.data)
 head(pref.data)
 # write csv file for further analysis
-write.csv(pref.data, file="pref.weak.data3.csv")
+write.csv(pref.data, file="pref.weak.data5.csv")
 
 ################################################################################################################
 

### 2018-05-16 stats/data_preprocessing_kids.R

@@ -4,7 +4,7 @@ library(tidyr)
 library(stringr)
 library(dplyr)
 library(data.table)
-library("stringr")
+
 
 
 ##
@@ -71,7 +71,7 @@ pref.data = pref.data[order(id)]
 str(pref.data)
 head(pref.data)
 # write csv file for further analysis
-write.csv(pref.data, file="kids_pref_handcoding.data.csv")
+write.csv(pref.data, file="kids_pref.data.csv")
 
 ################################################################################################################
 

### 2018-05-16 stats/ex3_comparisons.Rmd
working models: noise + regularized priors

@@
 ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
   geom_point()+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
   facet_grid(~Comp)+
@@
     var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
       return obj.shape == "circle" ? 1 : 0
@@
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
       return obj.shape == "circle" ? 1 : 0
@@
   xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
   stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
@@
 
-  // display(JSON.stringify(modelPredictions.score(d.correct_inf)))
+  //display(JSON.stringify(modelPredictions.score(d.correct_inf)))
+  //display(JSON.stringify(conditionSpecificData))
 

### 2018-05-18 stats/ex3_comparisons.Rmd
continuing model comparisons

@@
 library(langcog)
+library(rwebppl)
 ```
@@
 
-```{r model predictions}
+```{r model predictions, include = FALSE}
 predictions <- data.frame(
@@
 
-```{r joining files}
+```{r joining files, include = FALSE}
 
@@
 
-```{r rsaUtils}
-library(rwebppl)
-
+```{r rsaUtils, include = FALSE}
 rsaUtils <- '
@@
 
-```{r rsa model2}
+```{r rsa model2, include = FALSE}
 rsaModel2 <- '
@@
 
-```{r bda model rsa noise}
+```{r bda model rsa noise, include = FALSE}
 bdaModel.rsa.noise <-'
@@
 
-```{r bda model prior noise}
+```{r bda model prior noise, include = FALSE}
 bdaModel.prior.noise <-'
@@
 
-```{r bda model rsa regularizedPrior}
+```{r bda model rsa regularizedPrior, include = FALSE}
 bdaModel.rsa.regularizedPrior <-'
@@
 
-```{r bda model prior regularizedPrior}
+```{r bda model prior regularizedPrior, include = FALSE}
 bdaModel.prior.regularizedPrior <-'
@@
 
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
     var modelPredictions = Infer({method: "enumerate", model: function(){
@@
    map(function(d){ 
-     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
       observe(modelPredictions, d.correct_inf)
-      // factor(modelPredictions.score(d.correct_inf))
     }, conditionSpecificData)
@@
 
-```{r bda model rsa regularizedPrior noise}
+```{r bda model rsa regularizedPrior noise, include = FALSE}
 bdaModel.rsa.regularizedPrior.noise <-'
@@
 
-```{r bda model prior regularizedPrior noise}
+```{r bda model prior regularizedPrior noise, include = FALSE}
 bdaModel.prior.regularizedPrior.noise <-'
@@
 
-```{r model setup}
+```{r model setup, include = FALSE}
 
@@
 
-```{r predictions rsa noise}
+```{r predictions rsa noise, include = FALSE}
 bda <- webppl(
@@
 
-```{r predictions prior noise}
+```{r predictions prior noise, include = FALSE}
 bda1 <- webppl(
@@
 
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
 noisy.prior.model <- posterior.predictive1 %>%
@@
 
-```{r predictions rsa regularized prior}
+```{r predictions rsa regularized prior, include = FALSE}
 bda2 <- webppl(
@@
 
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
 regPrior.rsa.model <- posterior.predictive2 %>%
@@
 
-```{r predictions prior regularized prior}
+```{r predictions prior regularized prior, include = FALSE}
 bda3 <- webppl(
@@
 
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
 regPrior.prior.model <- posterior.predictive3 %>%
@@
 
-```{r predictions rsa noise regularized prior}
+```{r predictions rsa noise regularized prior, include = FALSE}
 bda4 <- webppl(
@@
 
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
 noisy.regPrior.rsa.model <- posterior.predictive4 %>%
@@
   summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
-```
-
-```{r predictions prior noise regularized prior}
+```
+
+```{r predictions prior noise regularized prior, include = FALSE}
 bda5 <- webppl(
@@
 
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
 noisy.regPrior.prior.model <- posterior.predictive5 %>%
@@
 no.adj.models <- pd %>%
-  mutate(Type = ifelse(Model == "Full model" | Model == "No prior","RSA",ifelse(Model == "Data","Data","Prior only")),
+  mutate(Type = ifelse(Model == "Full model","RSA",ifelse(Model == "Data","Data",ifelse(Model == "No prior","No Prior","Prior only"))),
          Adjustment = "None")
@@
 
+p.com$Adjustment <- ordered(p.com$Adjustment, levels = c("None","Noise","Regularized Prior","Noise & Regularized Prior"))
+
 ggplot(p.com, 
@@
   labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Model, labeller = label_wrap_gen(width=5))+
+  facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
   theme_few(base_size = 12) + 
@@
 plot.model <- p.com %>%
-  filter(Model != "Data", Model != "No prior" )
+  filter(Model != "Data", Model != "No prior")
+
+plot.model$Adjustment <- ordered(plot.model$Adjustment, levels = c("None","Noise","Regularized Prior","Noise & Regularized Prior"))
 
@@
 ```{r model rsa loglikelihood}
-bdaModel.rsa.loglikelihood <-'
+rsa.loglikelihood <-'
 var allConditions = dataFromR.allConditions
@@
 
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
+
+  var loglike = sum(map(function(d){
+
+  return modelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model prior loglikelihood}
+prior.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   var loglike = sum(map(function(d){
+
+  return priorOnlyPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model rsa noise loglikelihood}
+rsa.noise.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+  var loglike = sum(map(function(d){
+
+  return noisyModelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model prior noise loglikelihood}
+prior.noise.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
+
+   var loglike = sum(map(function(d){
+
+  return noisyModelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model rsa regularized prior loglikelihood}
+rsa.regPrior.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
@@
 
-  //display(JSON.stringify(modelPredictions.score(d.correct_inf)))
-  //display(JSON.stringify(conditionSpecificData))
-
   return modelPredictions.score(d.correct_inf)
@@
 
- return sum(loglike)
-}
-'
-```
-
-```{r rsa loglikelihood}
-llh <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.loglikelihood, sep='\n'),
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model prior regularized prior loglikelihood}
+prior.regPrior.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+   var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var loglike = sum(map(function(d){
+
+  return modelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model rsa regularizedPrior noise loglikelihood}
+rsa.regularizedPrior.noise.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+  var loglike = sum(map(function(d){
+
+  return noisyModelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model prior regularizedPrior noise loglikelihood}
+prior.regularizedPrior.noise.likelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
+        conditionSpecificPriors[0].priorProbs))
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+  var loglike = sum(map(function(d){
+
+  return noisyModelPredictions.score(d.correct_inf)
+    }, conditionSpecificData))
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model loglikelihoods}
+
+llh.rsa <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
   data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 100, verbose = T)
-)
-
+  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "RSA")
+
+llh.prior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "Prior only")
+
+llh.rsa.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "RSA Noisy")
+
+llh.prior.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "Prior only Noisy")
+
+llh.prior.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "Prior only Regularized")
+
+llh.rsa.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "RSA Regularized")
+
+llh.rsa.noise.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+)%>%
+  mutate(Model = "RSA Noisy Regularized")
+
+llh.prior.noise.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+) %>%
+  mutate(Model = "Prior only Noisy Regularized")
+
+```
+
+```{r}
+
+likelihood_overview <- bind_rows(
+  llh.rsa,
+  llh.prior,
+  llh.rsa.noise,
+  llh.prior.noise,
+  llh.prior.regPrior,
+  llh.rsa.regPrior,
+  llh.rsa.noise.regPrior,
+  llh.prior.noise.regPrior)
+
+ggplot(likelihood_overview, aes(x = value))+
+  geom_histogram()+
+  xlim(-700,-500)+
+  facet_wrap(~Model, nrow = 2)
+
+```
+
+```{r logsum summary}
+library(matrixStats)
+
+llh.plot <- likelihood_overview %>%
+  group_by(Model)%>%
+  summarize(logSumExp = logSumExp(value))%>%
+  mutate(Model = reorder(Model,logSumExp))
+
+ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
+  geom_bar(stat="identity", color = "black")+
+  ggtitle("logsumexp per model")+
+  theme_few()+ 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+
+save.image(file="model.comparisons.RData")
 ```

### 2018-05-18 stats/summary_model_predictions.Rmd
continuing model comparisons

---
title: "MCC model predictions overview"
author: "Manuel Bohn"
date: "17 5 2018"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo=FALSE)
knitr::opts_chunk$set(warning=FALSE)
```

```{r, include = FALSE}
load("model.comparisons.RData")

library(tidyverse)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(coda)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

## All model predictions and data

```{r, include = FALSE}
a <- ggplot(p.com, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)+
  theme(legend.position="bottom")
```

```{r}
a
```

## Correlations between mocel predictions and data

```{r, include = FALSE}
b <-ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  facet_grid(Type~Adjustment)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()
```

```{r}
b
```

## Prior only Model with Noise
Mean noise parameter with 95% Credible Interval: `r round(mean(posterior.noise1$value),2)` [`r round(hdi_lower(posterior.noise1$value),2)` : `r round(hdi_upper(posterior.noise1$value),2)`].

Model predictions: Very squashed (less extreme) compared to no adjustment predictions due to high noise parameter.

Qualitatively, predictions change for different speaker - congruent (from above chance to chance).

## RSA Model with Noise
Noise parameter: `r round(mean(posterior.noise$value),2)` [`r round(hdi_lower(posterior.noise$value),2)` : `r round(hdi_upper(posterior.noise$value),2)`]

Model predictions: Slightly squashed compared to no adjustment predictions.

Qualitatively predictions do not change.

## Prior only Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise3$value),2)` [`r round(hdi_lower(posterior.noise3$value),2)` : `r round(hdi_upper(posterior.noise3$value),2)`].

Model predictions: Again, very squashed (less extreme) compared to no adjustment predictions. Prior exponent parameter shows that priors are pulled towards uniform (and therefore to chance level).

Qualitatively, predictions change again for different speaker - congruent (from above chance to below chance).

## RSA Model with regularized Priors
Prior Exponent: `r round(mean(posterior.noise2$value),2)` [`r round(hdi_lower(posterior.noise2$value),2)` : `r round(hdi_upper(posterior.noise2$value),2)`]

Model predictions: Pulled strongly towards no prior model because priors are made more uniform.

Qualitatively, predictions change for same speaker incongruent in novelty (from below chance to chance) and for different speaker incongruent preference (at chance to above chance).

## Prior only Model with Noise and regularized Priors
Noise parameter: `r round(mean(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)`].

Prior Exponent: `r round(mean(posterior.noise5$value[posterior.noise5$Parameter =="priorExponent"]),2)` [`r round(hdi_lower(posterior.noise5$value[posterior.noise5$Parameter =="priorExponent"]),2)` : `r round(hdi_upper(posterior.noise5$value[posterior.noise5$Parameter =="priorExponent"]),2)`].

Model predictions: Slightly squashed (less extreme). More noise compared to model with noise only adjustment. Prior exponent suggests that priors are made more extreme - probably due to high noise parameter.

No qualitative change.

## RSA Model with Noise and regularized Priors
Mean noise parameter with 95% CrI: `r round(mean(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)`].

Mean priorExponent with 95% CrI: `r round(mean(posterior.noise4$value[posterior.noise4$Parameter =="priorExponent"]),2)` [`r round(hdi_lower(posterior.noise4$value[posterior.noise4$Parameter =="priorExponent"]),2)` : `r round(hdi_upper(posterior.noise4$value[posterior.noise4$Parameter =="priorExponent"]),2)`].

Model predictions: Slightly squashed (less extreme). A little less noisy compared to model with only noise adjustment. Prior adjustment is also less strongly towards uniform.

No qualitative change.

## Comparing models
```{r model predictions log likelihood, include = FALSE}
c <- ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("logsumexp per model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

```{r}
llh.plot%>%
  knitr::kable(digits = 3)
```

```{r}
c
```

### 2018-05-18 stats/ex3_comparisons.Rmd
overview model comparisons

@@
 
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
     var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
@@
    map(function(d){ 
-     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
       observe(noisyModelPredictions, d.correct_inf)
@@
   group_by(Model)%>%
-  summarize(logSumExp = logSumExp(value))%>%
+  summarize(logSumExp = logSumExp(value),
+            max = max(value))%>%
   mutate(Model = reorder(Model,logSumExp))

### 2018-05-18 stats/summary_model_predictions.Rmd
overview model comparisons

@@
   facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
-  theme_few(base_size = 12) + 
+  theme_few(base_size = 8) + 
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
@@
 
-## Correlations between mocel predictions and data
+## Correlations between model predictions and data
 
@@
   xlab("Model")+
-  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
+  stat_cor(method = "pearson", label.x = 0.3, label.y = 0.9)+
   geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
@@
 
-## Prior only Model with Noise
+## Model descriptions
+
+### Prior only Model with Noise
 Mean noise parameter with 95% Credible Interval: `r round(mean(posterior.noise1$value),2)` [`r round(hdi_lower(posterior.noise1$value),2)` : `r round(hdi_upper(posterior.noise1$value),2)`].
@@
 
-Qualitatively, predictions change for different speaker - congruent (from above chance to chance).
+Qualitatively, predictions change compared to no adjustment predictions for different speaker - congruent (from above chance to chance).
 
-## RSA Model with Noise
+4/8 predictions are qualitatively correct.
+
+### RSA Model with Noise
 Noise parameter: `r round(mean(posterior.noise$value),2)` [`r round(hdi_lower(posterior.noise$value),2)` : `r round(hdi_upper(posterior.noise$value),2)`]
@@
 
-## Prior only Model with regularized Priors
+8/8 predictions are qualitatively correct.
+
+### Prior only Model with regularized Priors
 Prior Exponent: `r round(mean(posterior.noise3$value),2)` [`r round(hdi_lower(posterior.noise3$value),2)` : `r round(hdi_upper(posterior.noise3$value),2)`].
@@
 Qualitatively, predictions change again for different speaker - congruent (from above chance to below chance).
+This is somehow strange as the uniform prior prediction in this case would be chance.
+Why is the prediction pushed below chance?
+This doesn't really make sense.
 
-## RSA Model with regularized Priors
+4/8 predictions are qualitatively correct.
+
+### RSA Model with regularized Priors
 Prior Exponent: `r round(mean(posterior.noise2$value),2)` [`r round(hdi_lower(posterior.noise2$value),2)` : `r round(hdi_upper(posterior.noise2$value),2)`]
@@
 
-## Prior only Model with Noise and regularized Priors
+6/8 predictions are qualitatively correct.
+
+### Prior only Model with Noise and regularized Priors
 Noise parameter: `r round(mean(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise5$value[posterior.noise5$Parameter =="noise"]),2)`].
@@
 
-## RSA Model with Noise and regularized Priors
+6/8 predictions are qualitatively correct.
+
+### RSA Model with Noise and regularized Priors
 Mean noise parameter with 95% CrI: `r round(mean(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` [`r round(hdi_lower(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)` : `r round(hdi_upper(posterior.noise4$value[posterior.noise4$Parameter =="noise"]),2)`].
@@
 
+8/8 predictions are qualitatively correct.
+
 ## Comparing models
+
+Order of parameterized models makes sense when looking at the correlations and model predictions.
+However, the predictions from the non-parameterized models do not fit in.
+First, the Prior only model provided a better fit based on the previous
+
 ```{r model predictions log likelihood, include = FALSE}
@@
 ```{r}
-llh.plot%>%
-  knitr::kable(digits = 3)
+c
 ```
 
+Log probabilities given the data for all models (except no prior model), computed via webppl.
+
 ```{r}
-c
+llh.plot%>%
+  knitr::kable(digits = 2)
 ```
+
+Log probabilities given the data for non-parameterized models based on binomial distribution (full model = RSA).
+
+```{r}
+comp_model%>%
+  knitr::kable(digits = 2)
+```

### 2018-05-31 stats/mcc_pref.kids.Rmd
model comparisons update

@@
   filter(trial_type == "test") %>%
-  group_by(change,age, id) %>%
+  group_by(change, id) %>%
   summarise(correct = mean(correct))
@@
   filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
+         age = scale(age))
 

### 2018-06-19 stats/ex3_comparisons.Rmd
model comparisons update
updating model comparisons

@@
 ```
+
 ```{r plot comparing models}
@@
 
+var two_objects = [
+{ shape: "triangle", id:1, location: 1},  
+{ shape: "circle", id:1, location: 2}
+]
+
 var labels = ["dax","wug"]
@@
 
+```{r bda model prior, include = FALSE}
+bdaModel.prior <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = 0
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
+
+   map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
 ```{r bda model rsa noise, include = FALSE}
@@
     c(0.5916667, 0.5916667, 0.4083333))
+
+allPriorProbs2 <- allPriorProbs
+
+allPriorProbs2$priorProbs = list(
+    c(0.0333333, 0.9666667), 
+    c(0.9666667, 0.0333333),
+    c(0.3583333, 0.6416667),
+    c(0.6416667, 0.3583333),
+    c(0.1666667, 0.8333333),
+    c(0.8333333, 0.1666667),
+    c(0.4083333, 0.5916667),
+    c(0.5916667, 0.4083333))
+
+```
+
+```{r predictions prior, include = FALSE}
+bda0 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.noise1 <- bda1 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise1, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+## distribution of model predictions
+posterior.predictive1 = bda0 %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
+
+ggplot(posterior.predictive1, aes(x = value))+
+  geom_histogram(binwidth = .01)+
+  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
+
+prior.model <- posterior.predictive1 %>%
+  mutate(Model="Prior Model",
+         Adjustment = "Noise",
+         Type = "Prior only")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value))
+
 ```
@@
 
-  var loglike = sum(map(function(d){
-
-  return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+var loglike = Binomial({
+        p: Math.exp(modelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 
-   var loglike = sum(map(function(d){
-
-  return priorOnlyPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+var loglike = Binomial({
+        p: Math.exp(priorOnlyPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 
-  var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 
-   var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 
-   var loglike = sum(map(function(d){
-
-  return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+var loglike = Binomial({
+        p: Math.exp(modelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 
-  var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
+  var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
 
@@
 ```{r model loglikelihoods}
+###################
+# RSA Models
+###################
 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
 )%>%
   mutate(Model = "RSA")
+
+llh.rsa.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy")
+
+llh.rsa.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Regularized")
+
+llh.rsa.noise.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy Regularized")
+
+###################
+# Prior only models
+###################
 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
 )%>%
   mutate(Model = "Prior only")
-
-llh.rsa.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Noisy")
 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
 )%>%
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
 )%>%
   mutate(Model = "Prior only Regularized")
-
-llh.rsa.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Regularized")
-
-llh.rsa.noise.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Noisy Regularized")
 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
 ) %>%
@@
   llh.prior.regPrior,
-  llh.rsa.regPrior,
+  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
   llh.rsa.noise.regPrior,
@@
 save.image(file="model.comparisons.RData")
+
 ```

### 2018-06-19 stats/model_predictions_variable_priors.Rmd
updating model comparisons

--- 2018-05-18 stats/ex3_comparisons.Rmd
@@
 ---
-title: "MCC Predictions"
+title: "MCC Model Predictions"
 author: "Manuel Bohn"
-date: "9 4 2018"
+date: "15 6 2018"
 output: html_document
@@
 library(rwebppl)
-```
+library(coda)
 
-# Modeling Informativeness
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
 
-Speaker optimality parameter of 2.25 produces model predictions that match our empirical results. The following predictions therefore use this parameter.
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
 
-Prior = measured proportion this type of object is being chosen.
-
-## "Dampening"" model
-
-### Preference inconcgruent
-ObjectPrior = Categorical({vs: all_objects, ps: [0.9666667, 0.9666667, 0.0333333] })
-
-### Preference congruent
-ObjectPrior = Categorical({vs: all_objects, ps: [0.0333333, 0.0333333, 0.9666667] })
-
-### Novelty inconcgruent
-var ObjectPrior = Categorical({vs: all_objects, ps: [0.8333333, 0.8333333, 0.1666667] })
-
-### Novelty concgruent
-var ObjectPrior = Categorical({vs: all_objects, ps: [0.1666667, 0.1666667, 0.8333333] })
-
-```{r data}
-dat <- bind_rows(read_csv(file="ex3.novel.data.csv"),
-               read_csv(file="ex3.pref.data.csv")) %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
-```
-
-```{r sanity checks}
-# check if there are incongruent trials in which informativeness and prior yield the same results
-# is not the case, that's good
-dat %>%
-  filter(alignment == "incongruent") %>%
-  filter(correct_inf == correct_prior)
-
-# check if someone needs to be excluded because wrong in training
-# no one, that's good
-dat %>%
-  filter(trial_type == "train") %>%
-  group_by(id)%>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  filter(correct_inf == 0)
-
-# check if someone did both experiments
-# yes, two people
-x <- dat %>%
-  filter(trial_type == "train") %>%
-  group_by(id)%>%
-  summarise(n = length(correct_inf)) %>%
-  filter(n > 2)
-
-# exclude those who did both experiments
-data <- dat %>%
-  filter(!id %in% x$id) %>%
-  filter(trial_type != "train") %>%
-  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"))
-
-data %>%
-  group_by(experiment,alignment,change) %>%
-  summarise(n = length(id))
-
-```
-
-```{r plot data}
-
-p1 <- data %>%
-  filter(trial_type == "test") %>%
-  group_by(Change ,Experiment,Alignment, id) %>%
-  summarise(correct = mean(correct_inf))
-
-p2 <- p1 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p1, aes(x = Alignment, y = correct, col = Alignment, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = Alignment, y = mean, col = Alignment,ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  facet_grid(Experiment ~ Change , scales = "free_x", space = "free_x" ) +
-  theme_few() + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_colour_solarized()
-
-```
-
-```{r comparisons to chance}
-library(exactRankTests)
-
-data %>%  
-  filter(trial_type == "test") %>%
-  group_by(change ,experiment,alignment, id) %>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  summarize(correct_inf = list(correct_inf)) %>%
-  group_by(change ,experiment,alignment) %>%
-  mutate(mean = mean(unlist(correct_inf)),
-         stat = wilcox.exact(unlist(correct_inf), mu = 0.5)$statistic,
-         p_value = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
-  select(change ,experiment,alignment,mean,stat,p_value)%>%
-  knitr::kable(digits = 3)
-```
-
-```{r model}
-library(lme4)
-
-m.data <- data %>%
-  mutate(item = ifelse( change == "false", agent, altAgent))
-
-lm <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change+Alignment|agent), 
-              data = m.data, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-summary(lm)
-
-```
-
-```{r model predictions, include = FALSE}
-predictions <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty","Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
-  Model = c("Full model","Full model","Full model","Full model","Full model","Full model","Full model","Full model","No prior","No prior","No prior","No prior","No prior","No prior","No prior","No prior", "Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only","Prior only"),
-  corr = c(0.9999672744165804,0.03460862921907267,0.9083230583454356,0.5090645649737232,0.9930727540990627,0.20045767964927574,0.8603373265403738,0.594975610001643,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.742,0.967,0.033,0.642,0.358,0.833,0.167,0.592,0.408))
-
-pred <- predictions %>%
-  group_by(Model,Experiment,Change,Alignment)%>%
-  multi_boot_standard(col = "corr")
-
-```
-
-```{r joining files, include = FALSE}
-
-da <- data %>%
-  filter(trial_type=="test")%>%
-  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
-         Model = "Data") %>%
-  group_by(Model,Experiment,Change,Alignment,id)%>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  multi_boot_standard(col = "correct_inf")
-
-pd <- rbind(pred,da)
-
-```
-
-```{r plot models and data}
-
-ggplot(pd, 
-       aes(x = Change, y = mean, fill = Alignment)) +
-  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
-  labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Model)+
-  theme_few(base_size = 12) + 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  ylim(0,1)
-
-```
-```{r plot comparing models}
-
-library(ggpubr)
-
-plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
-names(plot1) = c("Experiment","Data","Model","Comp")
-plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
-names(plot2) = c("Experiment","Data","Model","Comp")
-
-plot <- rbind(plot1,plot2)
-
-ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
-  geom_point()+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  facet_grid(~Comp)+
-  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
-  geom_smooth(method = "lm", se = F, col = "black")+
-  theme_few() + 
-  guides(col = F)+
-  scale_colour_solarized()
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 
@@
 { shape: "triangle", id:2, location: 2},
+{ shape: "circle", id:1, location: 2}
+]
+
+var two_objects = [
+{ shape: "triangle", id:1, location: 1},  
 { shape: "circle", id:1, location: 2}
@@
 ```{r bda model rsa noise, include = FALSE}
-bdaModel.rsa.noise <-'
+predictions.rsa.noise <-'
 var allConditions = dataFromR.allConditions
@@
 var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+   var noise = 0.28
 
@@
 
- return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r bda model prior noise, include = FALSE}
-bdaModel.prior.noise <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-    }})
-
-   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
- return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r bda model rsa regularizedPrior, include = FALSE}
-bdaModel.rsa.regularizedPrior <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
-
-   map(function(d){ 
-     // display(JSON.stringify(modelPredictions) + JSON.stringify(d.correct_inf))
-      observe(modelPredictions, d.correct_inf)
-      // factor(modelPredictions.score(d.correct_inf))
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
-
-}, allConditions)
-
- return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
-}
-'
-```
-
-```{r bda model prior regularizedPrior, include = FALSE}
-bdaModel.prior.regularizedPrior <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-    var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
-      return obj.shape == "circle" ? 1 : 0
-    }})
-
-   map(function(d){ 
-      observe(modelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
-
-}, allConditions)
-
- return extend(_.fromPairs(conditionOutput), {priorExponent: priorExponent})
-}
-'
-```
-
-```{r bda model rsa regularizedPrior noise, include = FALSE}
-bdaModel.rsa.regularizedPrior.noise <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
- return extend(_.fromPairs(conditionOutput), {noise: noise, priorExponent: priorExponent})
-}
-'
-```
-
-```{r bda model prior regularizedPrior noise, include = FALSE}
-bdaModel.prior.regularizedPrior.noise <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
- return extend(_.fromPairs(conditionOutput), {noise: noise, priorExponent: priorExponent})
+ return extend(_.fromPairs(conditionOutput))
 }
@@
 
-allConditions <- data %>%
-  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty")) %>%
-  group_by(Experiment,Change,Alignment)%>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  select(Change, Alignment,Experiment)
-
-allPriorProbs <- data.frame(
+strongPriorProbs <- data.frame(
   Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
@@
 
-allPriorProbs$priorProbs = list(
+strongPriorProbs$priorProbs = list(
     c(0.0333333, 0.033333, 0.9666667), 
@@
     c(0.5916667, 0.5916667, 0.4083333))
+
+mediumPriorProbs <- data.frame(
+  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+
+mediumPriorProbs$priorProbs = list(
+    c(0.1465517, 0.1465517, 0.8534483), 
+    c(0.8534483, 0.8534483, 0.1465517),
+    c(0.4137931, 0.4137931, 0.5862069),
+    c(0.5862069, 0.5862069, 0.4137931),
+    c(0.2983871, 0.2983871, 0.7016129),
+    c(0.7016129, 0.7016129, 0.2983871),
+    c(0.4137931, 0.4137931, 0.5862069),
+    c(0.5862069, 0.5862069, 0.4137931))
+
+weakPriorProbs <- data.frame(
+  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+
+weakPriorProbs$priorProbs = list(
+    c(0.1428571, 0.1428571, 0.8571429),
+    c(0.8571429, 0.8571429, 0.1428571),
+    c(0.4107143, 0.4107143, 0.5892857),
+    c(0.5892857, 0.5892857, 0.4107143),
+    c(0.4166667, 0.4166667, 0.5833333), 
+    c(0.5833333, 0.5833333, 0.4166667),
+    c(0.475, 0.475, 0.5250000),
+    c(0.5250000, 0.5250000, 0.475))
 ```
 
-```{r predictions rsa noise, include = FALSE}
+```{r predictions rsa noise strong prior, include = FALSE}
 bda <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = strongPriorProbs), 
   data_var = "dataFromR",
@@
 
-## distribution of noise
-posterior.noise <- bda %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
+# model predictions
 
-ggplot(posterior.noise, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive = bda %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
-
-noisy.rsa.model <- posterior.predictive %>%
-  mutate(Model="Noisy RSA Model",
+noisy.rsa.model.strong <- bda%>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
+  mutate(Model="Noisy RSA Model - Strong Prior",
+         Prior = "Strong",
          Adjustment = "Noise",
@@
 
-```{r predictions prior noise, include = FALSE}
-bda1 <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+```{r predictions rsa noise medium prior, include = FALSE}
+bda <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = mediumPriorProbs), 
   data_var = "dataFromR",
@@
 
-## distribution of noise
-posterior.noise1 <- bda1 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
+# model predictions
 
-ggplot(posterior.noise1, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive1 = bda1 %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive1, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-noisy.prior.model <- posterior.predictive1 %>%
-  mutate(Model="Noisy Prior Model",
+noisy.rsa.model.medium <- bda%>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
+  mutate(Model="Noisy RSA Model - Medium Prior",
+         Prior = "Medium",
          Adjustment = "Noise",
-         Type = "Prior only")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
-```
-
-```{r predictions rsa regularized prior, include = FALSE}
-bda2 <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-## distribution of noise
-posterior.noise2 <- bda2 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
-
-ggplot(posterior.noise2, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive2 = bda2 %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive2, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-regPrior.rsa.model <- posterior.predictive2 %>%
-  mutate(Model="Regularized RSA Model",
-         Adjustment = "Regularized Prior",
          Type = "RSA")%>%
@@
 
-```{r predictions prior regularized prior, include = FALSE}
-bda3 <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+```{r predictions rsa noise weak prior, include = FALSE}
+bda <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = weakPriorProbs), 
   data_var = "dataFromR",
@@
 
-## distribution of noise
-posterior.noise3 <- bda3 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
+# model predictions
 
-ggplot(posterior.noise3, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive3 = bda3 %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive3, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-regPrior.prior.model <- posterior.predictive3 %>%
-  mutate(Model="Regularized Prior Model",
-         Adjustment = "Regularized Prior",
-         Type = "Prior only")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
-```
-
-```{r predictions rsa noise regularized prior, include = FALSE}
-bda4 <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa.regularizedPrior.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-## distribution of noise
-posterior.noise4 <- bda4 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
-
-ggplot(posterior.noise4, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive4 = bda4 %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive4, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-noisy.regPrior.rsa.model <- posterior.predictive4 %>%
-  mutate(Model="Noisy Regularized RSA Model",
-         Adjustment = "Noise & Regularized Prior",
+noisy.rsa.model.weak <- bda%>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
+  mutate(Model="Noisy RSA Model - Weak Prior",
+         Prior = "Weak",
+         Adjustment = "Noise",
          Type = "RSA")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-```
-
-```{r predictions prior noise regularized prior, include = FALSE}
-bda5 <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior.regularizedPrior.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-## distribution of noise
-posterior.noise5 <- bda5 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
-
-ggplot(posterior.noise5, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive5 = bda5 %>%
-  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive5, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-noisy.regPrior.prior.model <- posterior.predictive5 %>%
-  mutate(Model="Noisy Regularized Prior Model",
-         Adjustment = "Noise & Regularized Prior",
-         Type = "Prior only")%>%
   group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
@@
 ```{r}
-## joining noisy model predictions with other predictions
-no.adj.models <- pd %>%
-  mutate(Type = ifelse(Model == "Full model","RSA",ifelse(Model == "Data","Data",ifelse(Model == "No prior","No Prior","Prior only"))),
-         Adjustment = "None")
 
-p.com <- bind_rows(
-  noisy.rsa.model,
-  noisy.prior.model,
-  regPrior.rsa.model,
-  regPrior.prior.model,
-  noisy.regPrior.rsa.model,
-  noisy.regPrior.prior.model,
-  no.adj.models
-  )
+pred <- bind_rows(
+  noisy.rsa.model.strong,
+  noisy.rsa.model.medium,
+  noisy.rsa.model.weak
+) %>% 
+  ungroup() %>%
+  mutate(Model = relevel(as.factor(Model), ref = "Noisy RSA Model - Weak Prior"))
 
-p.com$Adjustment <- ordered(p.com$Adjustment, levels = c("None","Noise","Regularized Prior","Noise & Regularized Prior"))
-
-ggplot(p.com, 
+ggplot(pred, 
        aes(x = Change, y = mean, fill = Alignment)) +
@@
   labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Adjustment*Type, labeller = label_wrap_gen(width=5))+
+  facet_grid(Experiment ~ Model)+
   theme_few(base_size = 12) + 
@@
   ylim(0,1)
-
 ```
-
-```{r}
-## correlations for model comparisons
-
-p.com$Data = rep(pd$mean[pd$Model=="Data"],10)
-
-plot.model <- p.com %>%
-  filter(Model != "Data", Model != "No prior")
-
-plot.model$Adjustment <- ordered(plot.model$Adjustment, levels = c("None","Noise","Regularized Prior","Noise & Regularized Prior"))
-
-ggplot(data = plot.model,aes(x = mean, y = Data, col = Model)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
-  geom_point()+
-  facet_grid(Type~Adjustment)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
-  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
-  theme_few() + 
-  guides(col = F)+
-  scale_colour_solarized()
-
-```
-
-```{r model rsa loglikelihood}
-rsa.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
-
-  var loglike = sum(map(function(d){
-
-  return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model prior loglikelihood}
-prior.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-    }})
-
-   var loglike = sum(map(function(d){
-
-  return priorOnlyPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model rsa noise loglikelihood}
-rsa.noise.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-  var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model prior noise loglikelihood}
-prior.noise.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, 
-        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-    }})
-
-   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
-
-   var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model rsa regularized prior loglikelihood}
-rsa.regPrior.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-
-  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
-
-   var loglike = sum(map(function(d){
-
-  return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model prior regularized prior loglikelihood}
-prior.regPrior.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-
-  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var loglike = sum(map(function(d){
-
-  return modelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model rsa regularizedPrior noise loglikelihood}
-rsa.regularizedPrior.noise.loglikelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, regularizedPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-  var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model prior regularizedPrior noise loglikelihood}
-prior.regularizedPrior.noise.likelihood <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
-
-var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  var regularizedPriors = normalize(map(function(i){ return Math.pow(i, priorExponent) },
-        conditionSpecificPriors[0].priorProbs))
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: regularizedPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-  var loglike = sum(map(function(d){
-
-  return noisyModelPredictions.score(d.correct_inf)
-    }, conditionSpecificData))
-
-  return  loglike
-}, allConditions)
-
- return sum(conditionOutput)
-}
-'
-```
-
-```{r model loglikelihoods}
-
-llh.rsa <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA")
-
-llh.prior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "Prior only")
-
-llh.rsa.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Noisy")
-
-llh.prior.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "Prior only Noisy")
-
-llh.prior.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "Prior only Regularized")
-
-llh.rsa.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Regularized")
-
-llh.rsa.noise.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-)%>%
-  mutate(Model = "RSA Noisy Regularized")
-
-llh.prior.noise.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
-) %>%
-  mutate(Model = "Prior only Noisy Regularized")
-
-```
-
-```{r}
-
-likelihood_overview <- bind_rows(
-  llh.rsa,
-  llh.prior,
-  llh.rsa.noise,
-  llh.prior.noise,
-  llh.prior.regPrior,
-  llh.rsa.regPrior,
-  llh.rsa.noise.regPrior,
-  llh.prior.noise.regPrior)
-
-ggplot(likelihood_overview, aes(x = value))+
-  geom_histogram()+
-  xlim(-700,-500)+
-  facet_wrap(~Model, nrow = 2)
-
-```
-
-```{r logsum summary}
-library(matrixStats)
-
-llh.plot <- likelihood_overview %>%
-  group_by(Model)%>%
-  summarize(logSumExp = logSumExp(value),
-            max = max(value))%>%
-  mutate(Model = reorder(Model,logSumExp))
-
-ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
-  geom_bar(stat="identity", color = "black")+
-  ggtitle("logsumexp per model")+
-  theme_few()+ 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
-
-save.image(file="model.comparisons.RData")
-```
-
-```{r simple BF model comparisons}
-priorProbsFromR <- list(
-  "pref_inf_same_congruent" =  c(0.0333333, 0.033333, 0.9666667),
-  "pref_inf_same_incongruent" = c(0.9666667, 0.9666667, 0.0333333),
-  "pref_inf_diff_congruent" =  c(0.3583333, 0.3583333, 0.6416667),
-  "pref_inf_diff_incongruent" = c(0.6416667, 0.6416667, 0.3583333),
-  "novel_inf_same_congruent" =  c(0.1666667, 0.1666667, 0.8333333),
-  "novel_inf_same_incongruent" = c(0.8333333, 0.8333333, 0.1666667),
-  "novel_inf_diff_congruent" =  c(0.4083333, 0.4083333, 0.5916667),
-  "novel_inf_diff_incongruent" = c(0.5916667, 0.5916667, 0.4083333)
-)
-
-# get model predictions from webppl
-wp.rs.all <- data.frame()
-for (conditionName in names(priorProbsFromR)) {
-
-  priorProbs <- priorProbsFromR[[conditionName]]
-  rs.wp <- webppl(
-    program_code = paste(rsaUtils, rsaModel, sep='\n'),
-    data = priorProbs,
-    data_var = "priorProbs"
-  )
-  wp.rs.all <- bind_rows(
-    wp.rs.all, 
-    rs.wp %>% 
-      mutate(condition = conditionName,
-             Model = "Full model")
-  )
-}
-
-# common confition names to join by
-con <- c("pref_inf_same_congruent",
-  "pref_inf_same_incongruent",
-  "pref_inf_diff_congruent",
-  "pref_inf_diff_incongruent",
-  "novel_inf_same_congruent",
-  "novel_inf_same_incongruent",
-  "novel_inf_diff_congruent",
-  "novel_inf_diff_incongruent")
-
-#Model predictions from prior only model
-prior_only <- predictions %>%
-  filter(Model == "Prior only")%>%
-  mutate(condition = con)
-
-#Model predictions from no prior model
-no_prior <- predictions %>%
-  filter(Model == "No prior")%>%
-  mutate(condition = con)
-
-# summarizing the data
-data.summary <- data %>%
-  mutate(condition = paste(experiment,change, alignment, sep = "_")) %>%
-  group_by(condition) %>%
-  summarize(n= n(),
-            k = sum(correct_inf))
-
-# joining model predictions and data
-model_comparison <- rbind(
-  left_join(
-  wp.rs.all %>% filter(obj == "circle")%>%mutate(exp = substr(condition,1,4)) %>%select(condition,exp,Model,prob),
-  data.summary),
-  left_join(
-  no_prior%>%mutate(prob = corr, exp = substr(condition,1,4))%>%select(condition,exp,Model,prob),
-  data.summary),
-  left_join(
-  prior_only%>%mutate(prob = corr, exp = substr(condition,1,4))%>%select(condition,exp,Model,prob),
-  data.summary)
-  )
-
-# calculate how well model predicts data
-comp_model<- model_comparison%>%
-  mutate(p_data_given_model = dbinom(size = n, p = prob, x = k, log = T)) %>%
-  group_by(Model) %>%
-  summarize(log_p_data_given_model = sum(p_data_given_model))
-
-comp_model
-
-## log p (data | model)
-## bayes factor_1,2 = p (data | model_1) / p (data | model_2)
-## log bf = log p (data | model_1) - log p (data | model_2)
-
-# Bayes factors full vs other models
-bf_full_no_prior <- exp((comp_model[1,2] - comp_model[2,2]))
-bf_full_no_prior
-
-bf_full_prior_only <- exp((comp_model[1,2] - comp_model[3,2]))
-bf_full_prior_only
-
-# model comparison by experiment
-comp_model_by_exp<- model_comparison%>%
-  mutate(p_data_given_model = dbinom(size = n, p = prob, x = k, log = T)) %>%
-  group_by(Model,exp) %>%
-  summarize(log_p_data_given_model = sum(p_data_given_model))
-
-# Bayes factors full - prior only
-pref_bf_full_prior_only <- exp(comp_model_by_exp[2,3] - comp_model_by_exp[6,3])
-pref_bf_full_prior_only
-
-novel_bf_full_prior_only <- exp(comp_model_by_exp[1,3] - comp_model_by_exp[5,3])
-novel_bf_full_prior_only
-
-```
-
-At what ratio does it flip back to more informative?
-
-```{r , echo=FALSE}
-
-pred <- data.frame(
-  Prior = c("90/10","80/20","70/30","60/40","50/50"),
-  corr = c(0.1118794400899893,0.24897738407515466,0.40911964439987003,0.5807810413750243,0.74)
-)
-
-ggplot(pred, 
-       aes(x = Prior, y = corr, fill = Prior)) +
-  geom_bar(stat="identity") + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Choosing More Informative")+
-  theme_few(base_size = 12) +
-  scale_fill_discrete(name = "Prior: less inf / more inf")+
-  ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
-
-```

### 2018-06-19 stats/ex3_comparisons.Rmd
updating model predictions

@@
 
+```{r model prior2 loglikelihood}
+prior.loglikelihood2 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: two_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+var loglike = Binomial({
+        p: Math.exp(priorOnlyPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
 ```{r model rsa noise loglikelihood}
@@
       var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+    }})
+
+   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
+
+var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model prior noise loglikelihood}
+prior.noise.loglikelihood2 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, 
+        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: two_objects, ps: conditionSpecificPriors[0].priorProbs}));
       return obj.shape == "circle" ? 1 : 0
@@
 
+llh.prior2 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood2, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs2), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "Prior only - non normalized")
+
 llh.prior.noise <- webppl(
@@
 
+llh.prior.noise2 <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood2, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs2), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 5000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "Prior only Noisy - non normalized")
+
 llh.prior.regPrior <- webppl(
@@
   llh.prior,
+  llh.prior2,
   llh.rsa.noise,
   llh.prior.noise,
+  llh.prior.noise2,
   llh.prior.regPrior,
@@
 
+getmode <- function(v) {
+   uniqv <- unique(v)
+   uniqv[which.max(tabulate(match(v, uniqv)))]
+}
+
 llh.plot <- likelihood_overview %>%
   group_by(Model)%>%
-  summarize(logSumExp = logSumExp(value),
-            max = max(value))%>%
-  mutate(Model = reorder(Model,logSumExp))
-
-ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
+  summarize(logP = max(value))%>%
+  mutate(Model = reorder(Model,logP))
+
+ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
   geom_bar(stat="identity", color = "black")+
@@
   theme_few()+ 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = F)
 

### 2018-06-23 stats/ex3_comparisons.Rmd
updating model predictions
updating model comparison and predictions

--- 2018-06-19 stats/ex3_comparisons.Rmd
@@
 
+load("model.comparisons.RData")
+
 library(tidyverse)
@@
 library(rwebppl)
+library(matrixStats)
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 ```
@@
 
-pred <- predictions %>%
+pred2 <- predictions %>%
   group_by(Model,Experiment,Change,Alignment)%>%
@@
 
-```{r plot models and data}
-
-ggplot(pd, 
-       aes(x = Change, y = mean, fill = Alignment)) +
-  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
-  labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Model)+
-  theme_few(base_size = 12) + 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  ylim(0,1)
-
-```
-
-```{r plot comparing models}
-
-library(ggpubr)
-
-plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
-names(plot1) = c("Experiment","Data","Model","Comp")
-plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
-names(plot2) = c("Experiment","Data","Model","Comp")
-
-plot <- rbind(plot1,plot2)
-
-ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
-  geom_point()+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  facet_grid(~Comp)+
-  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
-  geom_smooth(method = "lm", se = F, col = "black")+
-  theme_few() + 
-  guides(col = F)+
-  scale_colour_solarized()
-
-```
-
 ```{r rsaUtils, include = FALSE}
@@
 { shape: "triangle", id:2, location: 2},
-{ shape: "circle", id:1, location: 2}
-]
-
-var two_objects = [
-{ shape: "triangle", id:1, location: 1},  
 { shape: "circle", id:1, location: 2}
@@
 var model = function(){
-   var noise = 0
 
@@
 
-   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(priorOnlyPredictions.score(1))]
 
@@
 
- return extend(_.fromPairs(conditionOutput), {noise: noise})
+ return extend(_.fromPairs(conditionOutput))
+}
+'
+```
+
+```{r bda model rsa, include = FALSE}
+bdaModel.rsa <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(modelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput))
 }
@@
 var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})
 
@@
 var model = function(){
-   var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+   var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})
    var noise = uniformDrift({a: 0, b:1, width: 0.1})
@@
 
-allPriorProbs2 <- allPriorProbs
-
-allPriorProbs2$priorProbs = list(
-    c(0.0333333, 0.9666667), 
-    c(0.9666667, 0.0333333),
-    c(0.3583333, 0.6416667),
-    c(0.6416667, 0.3583333),
-    c(0.1666667, 0.8333333),
-    c(0.8333333, 0.1666667),
-    c(0.4083333, 0.5916667),
-    c(0.5916667, 0.4083333))
-
 ```
@@
 ```{r predictions prior, include = FALSE}
-bda0 <- webppl(
+bda_priorOnly <- webppl(
   program_code = paste(rsaUtils, rsaModel2, bdaModel.prior, sep='\n'),
@@
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-## distribution of noise
-posterior.noise1 <- bda1 %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
-
-ggplot(posterior.noise1, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-## distribution of model predictions
-posterior.predictive1 = bda0 %>%
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
+)
+
+prior.model <- bda_priorOnly %>%
   filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")
-
-ggplot(posterior.predictive1, aes(x = value))+
-  geom_histogram(binwidth = .01)+
-  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-prior.model <- posterior.predictive1 %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
   mutate(Model="Prior Model",
-         Adjustment = "Noise",
+         Adjustment = "None",
          Type = "Prior only")%>%
@@
 
+```{r predictions rsa, include = FALSE}
+bda_rsa <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, bdaModel.rsa, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
+)
+
+rsa.model <- bda_rsa %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_") %>%
+  mutate(Model="RSA Model",
+         Adjustment = "None",
+         Type = "RSA")%>%
+  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value))
+
+```
+
 ```{r predictions rsa noise, include = FALSE}
@@
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
 )
@@
   facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')
-
-## Bayesian credible intervals
-
-library(coda)
-
-estimate_mode <- function(s) {
-  d <- density(s)
-  return(d$x[which.max(d$y)])
-}
-
-hdi_upper<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","upper"])
-}
-
-hdi_lower<- function(s){
-  m <- HPDinterval(mcmc(s))
-  return(m["var1","lower"])
-}
 
@@
 no.adj.models <- pd %>%
+  filter(Model != "Full model", Model != "Prior only")%>%
   mutate(Type = ifelse(Model == "Full model","RSA",ifelse(Model == "Data","Data",ifelse(Model == "No prior","No Prior","Prior only"))),
@@
 p.com <- bind_rows(
+  prior.model,
+  rsa.model,
   noisy.rsa.model,
@@
 p.com$Data = rep(pd$mean[pd$Model=="Data"],10)
+p.com$Data_ci_low = rep(pd$ci_lower[pd$Model=="Data"],10)
+p.com$Data_ci_up = rep(pd$ci_upper[pd$Model=="Data"],10)
 
@@
   geom_point()+
+  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0)+
   facet_grid(Type~Adjustment)+
@@
 
-  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+  var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})
+
+  var pe = []
 
@@
     )
+
+loglike == -Infinity ? display(priorExponent) : null
 
@@
 
-  var priorExponent = uniformDrift({a: 0, b:5, width: 0.1})
+  var priorExponent = uniformDrift({a: 0, b:3, width: 0.1})
 
@@
   model_var = "model",
-  inference_opts = list(method = "forward", samples = 5000),
+  inference_opts = list(method = "forward", samples = 10000),
   chains = 3, cores = 3
@@
   llh.prior.noise,
+  llh.rsa.regPrior,
   llh.prior.regPrior,
-  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
   llh.rsa.noise.regPrior,
@@
   geom_histogram()+
-  xlim(-700,-500)+
-  facet_wrap(~Model, nrow = 2)
+  xlim(-200,0)+
+  facet_wrap(~Model, nrow = 2, scales = "free")
 
@@
 ```{r logsum summary}
-library(matrixStats)
-
 llh.plot <- likelihood_overview %>%
   group_by(Model)%>%
-  summarize(logSumExp = logSumExp(value),
-            max = max(value))%>%
-  mutate(Model = reorder(Model,logSumExp))
-
-ggplot(llh.plot, aes(x = Model, y = logSumExp, fill = Model))+
+  summarize(logP = logSumExp(value))%>%
+  mutate(Model = reorder(Model,logP))
+
+ggplot(llh.plot, aes(x = Model, y = logP, fill = Model))+
   geom_bar(stat="identity", color = "black")+
@@
   theme_few()+ 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = F)
 
 save.image(file="model.comparisons.RData")
+
+```
+
+```{r more iterations on rsa models}
+
+llh.n.10k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy 10k")
+
+llh.n.20k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 20000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy 20k")
+
+llh.n.50k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 50000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy 50k")
+
+llh.nr.10k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy Regularized 10k")
+
+llh.nr.20k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 20000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy Regularized 20k")
+
+llh.nr.50k <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 50000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy Regularized 50k")
+
+```
+
+```{r}
+rsa_overview <- bind_rows(
+  llh.n.10k,
+  llh.n.20k,
+  llh.n.50k,
+  llh.nr.10k,
+  llh.nr.20k,
+  llh.nr.50k)
+
+rsa.llh.plot <- rsa_overview %>%
+  group_by(Model)%>%
+  summarize(logP = logSumExp(value))%>%
+  mutate(Model = reorder(Model,logP))
+
+ggplot(rsa.llh.plot, aes(x = Model, y = logP, fill = Model))+
+  geom_bar(stat="identity", color = "black")+
+  ggtitle("logsumexp by number of samples")+
+  theme_few()+ 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(fill = F)
 
@@
 ```
-
-At what ratio does it flip back to more informative?
-
-```{r , echo=FALSE}
-
-pred <- data.frame(
-  Prior = c("90/10","80/20","70/30","60/40","50/50"),
-  corr = c(0.1118794400899893,0.24897738407515466,0.40911964439987003,0.5807810413750243,0.74)
-)
-
-ggplot(pred, 
-       aes(x = Prior, y = corr, fill = Prior)) +
-  geom_bar(stat="identity") + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Choosing More Informative")+
-  theme_few(base_size = 12) +
-  scale_fill_discrete(name = "Prior: less inf / more inf")+
-  ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
-
-```

### 2018-06-23 stats/model_predictions_variable_priors.Rmd
updating model comparison and predictions

@@
 knitr::opts_chunk$set(echo = TRUE)
+
+load("model.predictions.RData")
 
@@
 
-```{r bda model rsa noise, include = FALSE}
+```{r predictions rsa noise, include = FALSE}
 predictions.rsa.noise <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.allPriorProbs
+var allConditions = dataFromR.newConditions
+var allData = dataFromR.predData
+var allPriorProbs = dataFromR.predPriorProbs
 
 var model = function(){
-   var noise = 0.28
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
 
@@
 
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
 
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
-
-  //display(JSON.stringify(conditionSpecificData[0].correct_inf))
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
 
@@
 
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment+ "_" + conditionInfo.Prior, Math.exp(noisyModelPredictions.score(1))]
 
@@
 
- return extend(_.fromPairs(conditionOutput))
+ // return extend(_.fromPairs(conditionOutput), {noise: noise})
+
+// generate predictions for new conditions
+
+   var newPredictions = map(function(conditionInfo){
+
+    var newSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior: conditionInfo.Prior})
+
+    var newModelPredictions = pragmaticListener({label: "dax", point: 2 }, newSpecificPriors[0].priorProbs)
+    var newNoisyModelPredictions = addNoise(newModelPredictions, noise)
+
+    return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment + "_" + conditionInfo.Prior, Math.exp(newNoisyModelPredictions.score(1))]
+
+  }, allConditions)
+
+  return extend(_.fromPairs(newPredictions), {noise: noise})
+
 }
@@
   Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Strong",8))
 
@@
   Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Medium",8))
 
@@
 weakPriorProbs <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"))
+  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Weak",4))
 
 weakPriorProbs$priorProbs = list(
-    c(0.1428571, 0.1428571, 0.8571429),
-    c(0.8571429, 0.8571429, 0.1428571),
-    c(0.4107143, 0.4107143, 0.5892857),
-    c(0.5892857, 0.5892857, 0.4107143),
   c(0.4166667, 0.4166667, 0.5833333), 
@@
   c(0.5250000, 0.5250000, 0.475))
+
+predPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)
+
+allPriorProbs <- strongPriorProbs %>%
+  select(-Prior)
+
+allConditions <- predPriorProbs %>%
+  filter(Prior == "Strong")%>%
+  select(-priorProbs, -Prior)
+
+newConditions <- predPriorProbs %>%
+  select(-priorProbs)
+
+predData <- data %>%
+  mutate(Prior = "Strong")
 ```
 
-```{r predictions rsa noise strong prior, include = FALSE}
-bda <- webppl(
+```{r predictions rsa noise, include = FALSE}
+bda.pred.noise <- webppl(
   program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = strongPriorProbs), 
+  data = list(allData = data, newConditions = newConditions, predPriorProbs = predPriorProbs, predData = predData), 
   data_var = "dataFromR",
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
 )
+
+## distribution of noise
+posterior.noise.pred <- bda.pred.noise %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise.pred, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
 
@@
 
-noisy.rsa.model.strong <- bda%>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
-  mutate(Model="Noisy RSA Model - Strong Prior",
-         Prior = "Strong",
+noisy.rsa.pred <- bda.pred.noise %>%
+  filter(!(Parameter %in% c("noise", "priorExponent")))  %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment", "Prior"), sep="_")%>%
+  mutate(Model="Noisy RSA Model",
          Adjustment = "Noise",
-         Type = "RSA")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
-```
-
-```{r predictions rsa noise medium prior, include = FALSE}
-bda <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = mediumPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-# model predictions
-
-noisy.rsa.model.medium <- bda%>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
-  mutate(Model="Noisy RSA Model - Medium Prior",
-         Prior = "Medium",
-         Adjustment = "Noise",
-         Type = "RSA")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
-```
-
-```{r predictions rsa noise weak prior, include = FALSE}
-bda <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = weakPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-)
-
-# model predictions
-
-noisy.rsa.model.weak <- bda%>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")%>%
-  mutate(Model="Noisy RSA Model - Weak Prior",
-         Prior = "Weak",
-         Adjustment = "Noise",
-         Type = "RSA")%>%
-  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
+         Type = "RSA",
+         Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
+  group_by(Model,Prior,Adjustment,Type,Experiment,Change,Alignment) %>%
   summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
@@
 
-pred <- bind_rows(
-  noisy.rsa.model.strong,
-  noisy.rsa.model.medium,
-  noisy.rsa.model.weak
-) %>% 
-  ungroup() %>%
-  mutate(Model = relevel(as.factor(Model), ref = "Noisy RSA Model - Weak Prior"))
-
-ggplot(pred, 
+ggplot(noisy.rsa.pred, 
        aes(x = Change, y = mean, fill = Alignment)) +
@@
   labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Model)+
+  facet_grid(Experiment ~ Prior)+
   theme_few(base_size = 12) + 
@@
 ```
+
+```{r}
+save.image(file="model.predictions.RData")
+```

### 2018-06-25 experiments/Ex3_2/Ex3_novel_medium.js
variable prior exp and model predictions

@@ -1,0 +1,1147 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-06-25 experiments/Ex3_2/Ex3_novel_weak.js

@@ -1,0 +1,1131 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-06-25 experiments/Ex3_2/Ex3_pref_medium.js

@@ -1,0 +1,839 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-06-25 experiments/Ex3_2/_layout/custom.js

@@ -1,0 +1,31 @@
+setTimeout(function() {
+
+  var getLineHeight = function(el) {
+    return parseInt(document
+                    .defaultView
+                    .getComputedStyle(el, null)["line-height"]
+                    .replace("px",""));
+  }
+  
+  $("li:has(.content) > .annotation")
+    .filter(function(i, a) {
+      var p = $(a).find("p")[0];
+      if (!p) {
+        return false;
+      }
+      
+      var c = $(this).parent().find(".content")[0];
+      return $(p).height() > $(c).outerHeight();
+    })
+    .addClass("folded")
+    .prepend($("<span class='ellipsis'>+</span>").click(function(e) {
+      $(this).parent().toggleClass("folded");
+
+      if ($(this).text() == "+") {
+        $(this).text("-")
+      } else {
+        $(this).text("+")
+      }
+    }))
+
+}, 200);

### 2018-06-25 experiments/Ex3_weak/Ex3_novel_weak.js

@@ -1,1163 +1,0 @@
-
-// ## Helper functions
-
-
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-	$(".text").hide();
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-    $(".look_agent_l").hide();
-    $(".look_agent_r").hide();
-	$("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-	$(".agent").hide();
-}
-
-
-function choiceAgent(id) {
-	$(".agent").hide();
-	$("#"+id+"_choice").show();
-}
-
-function sourceRightFruit(a) {
-        document.getElementById("fruit_r").src=a;
-    };
-
-function sourceRightFruit2(a) {
-        document.getElementById("fruit_r2").src=a;
-    };
-
-function sourceLeftFruit(b) {
-        document.getElementById("fruit_l").src=b;
-    };
-
-function sourceLeftFruit2(b) {
-        document.getElementById("fruit_l2").src=b;
-    };
-
-function showRightFruit() {
-    document.getElementById('fruit_r').style.visibility='visible';
-      };
-
-function showRightFruit2() {
-    document.getElementById('fruit_r2').style.visibility='visible';
-      };
-
-function hideRightFruit() {
-    document.getElementById('fruit_r').style.visibility='hidden';
-      };
-
-function showLeftFruit() {
-    document.getElementById('fruit_l').style.visibility='visible';
-      };
-
-function showLeftFruit2() {
-    document.getElementById('fruit_l2').style.visibility='visible';
-      };
-
-function hideLeftFruit() {
-    document.getElementById('fruit_l').style.visibility='hidden';
-      };
-
-function showEat(id) {
-	$(".agent_eat").hide();
-	$("#"+id+"_eat").show();
-};
-
-function choiceLeftFruit(a) {
-        document.getElementById("choiceFruit_l").src=a;
-    };
-
-function choiceLeftFruit2(a) {
-        document.getElementById("choiceFruit_l2").src=a;
-    };
-
-function choiceRightFruit(a) {
-        document.getElementById("choiceFruit_r").src=a;
-    };
-
-function choiceRightFruit2(a) {
[…]

### 2018-06-25 experiments/Ex3_weak/Ex3_pref_weak.js

@@ -1,832 +1,0 @@
-
-// ## Helper functions
-
-
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-	$(".text").hide();
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-    $(".look_agent_l").hide();
-    $(".look_agent_r").hide();
-	$("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-	$(".agent").hide();
-}
-
-
-function choiceAgent(id) {
-	$(".agent").hide();
-	$("#"+id+"_choice").show();
-}
-
-function sourceRightFruit(a) {
-        document.getElementById("fruit_r").src=a;
-    };
-
-function sourceRightFruit2(a) {
-        document.getElementById("fruit_r2").src=a;
-    };
-
-function sourceLeftFruit(b) {
-        document.getElementById("fruit_l").src=b;
-    };
-
-function sourceLeftFruit2(b) {
-        document.getElementById("fruit_l2").src=b;
-    };
-
-function showRightFruit() {
-    document.getElementById('fruit_r').style.visibility='visible';
-      };
-
-function showRightFruit2() {
-    document.getElementById('fruit_r2').style.visibility='visible';
-      };
-
-function hideRightFruit() {
-    document.getElementById('fruit_r').style.visibility='hidden';
-      };
-
-function showLeftFruit() {
-    document.getElementById('fruit_l').style.visibility='visible';
-      };
-
-function showLeftFruit2() {
-    document.getElementById('fruit_l2').style.visibility='visible';
-      };
-
-function hideLeftFruit() {
-    document.getElementById('fruit_l').style.visibility='hidden';
-      };
-
-function showEat(id) {
-	$(".agent_eat").hide();
-	$("#"+id+"_eat").show();
-};
-
-function choiceLeftFruit(a) {
-        document.getElementById("choiceFruit_l").src=a;
-    };
-
-function choiceLeftFruit2(a) {
-        document.getElementById("choiceFruit_l2").src=a;
-    };
-
-function choiceRightFruit(a) {
-        document.getElementById("choiceFruit_r").src=a;
-    };
-
-function choiceRightFruit2(a) {
[…]

### 2018-06-28 stats/ex3_comparisons.Rmd
updating exp variable priors

@@
 library(coda)
+library(ggpubr)
 
@@
 
-pred2 <- predictions %>%
+pred <- predictions %>%
   group_by(Model,Experiment,Change,Alignment)%>%
@@
 
+da2 <- data %>%
+  filter(trial_type=="test")%>%
+  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
+         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
+         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
+         Model = "Data") %>%
+  group_by(Model,Experiment,Change,Alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
 pd <- rbind(pred,da)
+
+pd2 <- bind_rows(pred,da2)
 
@@
 
+noisy.rsa.params <- bda %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+noisy.rsa.params100k <- bda2 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
 ## distribution of model predictions
@@
 
+noisy.prior.params <- bda1 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
 ## distribution of model predictions
@@
 ## joining noisy model predictions with other predictions
-no.adj.models <- pd %>%
+no.adj.models <- pd2 %>%
   filter(Model != "Full model", Model != "Prior only")%>%
@@
 
-p.com$Data = rep(pd$mean[pd$Model=="Data"],10)
-p.com$Data_ci_low = rep(pd$ci_lower[pd$Model=="Data"],10)
-p.com$Data_ci_up = rep(pd$ci_upper[pd$Model=="Data"],10)
+p.com$Data = rep(pd2$mean[pd2$Model=="Data"],10)
+p.com$Data_ci_low = rep(pd2$ci_lower[pd2$Model=="Data"],10)
+p.com$Data_ci_up = rep(pd2$ci_upper[pd2$Model=="Data"],10)
 

### 2018-06-28 stats/mcc_pref.kids.Rmd
updating exp variable priors

@@
 # children who need to be dropped
-drop <- c("Dryrun","180426_3_pref","180502_1_pref","180503_1_pref","180503_2_pref","180504_1_pref","180511_2_pref","180511_1_pref")
+drop <- c("Dryrun",
+"180426_3_pref",
+"180427_2_pref",
+"180427_3_pref",
+"180427_4_pref",
+"180502_1_pref",
+"180503_1_pref",
+"180503_2_pref",
+"180504_1_pref",
+"180511_1_pref",
+"180511_2_pref")
 
@@
 
+unique(d$id)
 ```
@@
   filter(trial_type == "test") %>%
-  group_by(change, id) %>%
+  group_by(change,age, id) %>%
   summarise(correct = mean(correct))
@@
 # maximal converging model
-lm <- glmer(correct ~ age + change + (age * change |id) + (age * change |choiceAgent), 
+lm <- glmer(correct ~ age * change + (age * change |id) + (age * change |choiceAgent), 
               data = data_cg, family = binomial, 

### 2018-06-28 stats/model_predictions_variable_priors.Rmd
variable prior exp and model predictions
updating exp variable priors

@@
 
-```{r predictions rsa noise, include = FALSE}
+```{r model setup, include = FALSE}
+
+strongPriorProbs <- data.frame(
+  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Strong",8))
+
+strongPriorProbs$priorProbs = list(
+    c(0.0333333, 0.033333, 0.9666667), 
+    c(0.9666667, 0.9666667, 0.0333333),
+    c(0.3583333, 0.3583333, 0.6416667),
+    c(0.6416667, 0.6416667, 0.3583333),
+    c(0.1666667, 0.1666667, 0.8333333),
+    c(0.8333333, 0.8333333, 0.1666667),
+    c(0.4083333, 0.4083333, 0.5916667),
+    c(0.5916667, 0.5916667, 0.4083333))
+
+mediumPriorProbs <- data.frame(
+  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Medium",8))
+
+mediumPriorProbs$priorProbs = list(
+    c(0.1465517, 0.1465517, 0.8534483), 
+    c(0.8534483, 0.8534483, 0.1465517),
+    c(0.4137931, 0.4137931, 0.5862069),
+    c(0.5862069, 0.5862069, 0.4137931),
+    c(0.2983871, 0.2983871, 0.7016129),
+    c(0.7016129, 0.7016129, 0.2983871),
+    c(0.4274194, 0.4274194, 0.5725806),
+    c(0.5725806, 0.5725806, 0.4274194))
+
+weakPriorProbs <- data.frame(
+  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
+  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
+  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
+  Prior = rep("Weak",4))
+
+weakPriorProbs$priorProbs = list(
+  c(0.4166667, 0.4166667, 0.5833333), 
+  c(0.5833333, 0.5833333, 0.4166667),
+  c(0.475, 0.475, 0.5250000),
+  c(0.5250000, 0.5250000, 0.475))
+
+predPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)
+
+allPriorProbs <- strongPriorProbs %>%
+  select(-Prior)
+
+allConditions <- predPriorProbs %>%
+  filter(Prior == "Strong")%>%
+  select(-priorProbs, -Prior)
+
+newConditions <- predPriorProbs %>%
+  select(-priorProbs)
+
+predData <- data %>%
+  mutate(Prior = "Strong")
+```
+
+```{r model rsa noise, include = FALSE}
 predictions.rsa.noise <-'
@@
 
-```{r model setup, include = FALSE}
-
-strongPriorProbs <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Strong",8))
-
-strongPriorProbs$priorProbs = list(
-    c(0.0333333, 0.033333, 0.9666667), 
-    c(0.9666667, 0.9666667, 0.0333333),
-    c(0.3583333, 0.3583333, 0.6416667),
-    c(0.6416667, 0.6416667, 0.3583333),
-    c(0.1666667, 0.1666667, 0.8333333),
-    c(0.8333333, 0.8333333, 0.1666667),
-    c(0.4083333, 0.4083333, 0.5916667),
-    c(0.5916667, 0.5916667, 0.4083333))
-
-mediumPriorProbs <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Medium",8))
-
-mediumPriorProbs$priorProbs = list(
-    c(0.1465517, 0.1465517, 0.8534483), 
-    c(0.8534483, 0.8534483, 0.1465517),
-    c(0.4137931, 0.4137931, 0.5862069),
-    c(0.5862069, 0.5862069, 0.4137931),
-    c(0.2983871, 0.2983871, 0.7016129),
-    c(0.7016129, 0.7016129, 0.2983871),
-    c(0.4137931, 0.4137931, 0.5862069),
-    c(0.5862069, 0.5862069, 0.4137931))
-
-weakPriorProbs <- data.frame(
-  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Weak",4))
-
-weakPriorProbs$priorProbs = list(
-  c(0.4166667, 0.4166667, 0.5833333), 
-  c(0.5833333, 0.5833333, 0.4166667),
-  c(0.475, 0.475, 0.5250000),
-  c(0.5250000, 0.5250000, 0.475))
-
-predPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)
-
-allPriorProbs <- strongPriorProbs %>%
-  select(-Prior)
-
-allConditions <- predPriorProbs %>%
-  filter(Prior == "Strong")%>%
-  select(-priorProbs, -Prior)
-
-newConditions <- predPriorProbs %>%
-  select(-priorProbs)
-
-predData <- data %>%
-  mutate(Prior = "Strong")
-```
-
 ```{r predictions rsa noise, include = FALSE}
@@
 
+#bda.pred.noise2 has 100k samples
+
 ## distribution of noise
@@
   facet_wrap(~Parameter, scales = 'free')
+
+noisy.rsa.params.pred <- bda.pred.noise %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+noisy.rsa.params.pred100k <- bda.pred.noise2 %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
 
@@
 
-```{r}
+```{r plot rsa noise pred}
 
@@
 
+```{r model prior only noise , include = FALSE}
+predictions.prior.noise <-'
+var allConditions = dataFromR.newConditions
+var allData = dataFromR.predData
+var allPriorProbs = dataFromR.predPriorProbs
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+ // return extend(_.fromPairs(conditionOutput), {noise: noise})
+
+// generate predictions for new conditions
+
+   var newPredictions = map(function(conditionInfo){
+
+    var newSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior: conditionInfo.Prior})
+
+    var newModelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: newSpecificPriors[0].priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+  var newNoisyModelPredictions = addNoise(newModelPredictions, noise)
+
+    return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment + "_" + conditionInfo.Prior, Math.exp(newNoisyModelPredictions.score(1))]
+
+  }, allConditions)
+
+  return extend(_.fromPairs(newPredictions), {noise: noise})
+
+}
+'
+```
+
+```{r predictions prior only noise, include = FALSE}
+bda.pred.prior.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, predictions.prior.noise, sep='\n'),
+  data = list(allData = data, newConditions = newConditions, predPriorProbs = predPriorProbs, predData = predData), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
+)
+
+## distribution of noise
+posterior.prior.noise.pred <- bda.pred.prior.noise %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.prior.noise.pred, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+noisy.prior.params.pred <- bda.pred.prior.noise %>%
+  filter(Parameter %in% c("noise", "priorExponent"))  %>%
+  group_by(Parameter) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+# model predictions
+
+prior.noise.pred <- bda.pred.prior.noise %>%
+  filter(!(Parameter %in% c("noise", "priorExponent")))  %>%
+  separate(Parameter, into = c("Experiment", "Change", "Alignment", "Prior"), sep="_")%>%
+  mutate(Model="Noisy Prior only Model",
+         Adjustment = "Noise",
+         Type = "Prior only",
+         Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
+  group_by(Adjustment,Model,Prior,Type,Experiment,Change,Alignment) %>%
+  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
+
+```
+
+```{r plot prior only noise regularized}
+
+ggplot(prior.noise.pred, 
+       aes(x = Change, y = mean, fill = Alignment)) +
+  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
+  labs(x=" ",y="Proportion Choosing More Informative")+
+  facet_grid(Experiment ~ Prior)+
+  theme_few(base_size = 12) + 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  ylim(0,1)
+```
+
+```{r}
+pred.plot <- bind_rows(prior.noise.pred,noisy.rsa.pred)
+
+ggplot(pred.plot, 
+       aes(x = Change, y = mean, fill = Alignment)) +
+  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
+  labs(x=" ",y="Proportion Choosing More Informative")+
+  facet_grid(Experiment ~ Prior*Type)+
+  theme_few(base_size = 12) + 
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  ylim(0,1)
+
+```
+
 ```{r}

### 2018-06-28 experiments/Ex3_2/Ex3_pref_strong.js

@@ -1,0 +1,872 @@
+
+// ## Helper functions
+
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+	$(".text").hide();
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+    $(".look_agent_l").hide();
+    $(".look_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+	$(".agent").hide();
+}
+
+
+function choiceAgent(id) {
+	$(".agent").hide();
+	$("#"+id+"_choice").show();
+}
+
+function sourceRightFruit(a) {
+        document.getElementById("fruit_r").src=a;
+    };
+
+function sourceRightFruit2(a) {
+        document.getElementById("fruit_r2").src=a;
+    };
+
+function sourceLeftFruit(b) {
+        document.getElementById("fruit_l").src=b;
+    };
+
+function sourceLeftFruit2(b) {
+        document.getElementById("fruit_l2").src=b;
+    };
+
+function showRightFruit() {
+    document.getElementById('fruit_r').style.visibility='visible';
+      };
+
+function showRightFruit2() {
+    document.getElementById('fruit_r2').style.visibility='visible';
+      };
+
+function hideRightFruit() {
+    document.getElementById('fruit_r').style.visibility='hidden';
+      };
+
+function showLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='visible';
+      };
+
+function showLeftFruit2() {
+    document.getElementById('fruit_l2').style.visibility='visible';
+      };
+
+function hideLeftFruit() {
+    document.getElementById('fruit_l').style.visibility='hidden';
+      };
+
+function showEat(id) {
+	$(".agent_eat").hide();
+	$("#"+id+"_eat").show();
+};
+
+function choiceLeftFruit(a) {
+        document.getElementById("choiceFruit_l").src=a;
+    };
+
+function choiceLeftFruit2(a) {
+        document.getElementById("choiceFruit_l2").src=a;
+    };
+
+function choiceRightFruit(a) {
+        document.getElementById("choiceFruit_r").src=a;
+    };
+
+function choiceRightFruit2(a) {
[…]

### 2018-06-28 experiments/Ex3_2/Ex3_pref_medium.js
updating exp variable priors

@@ -622,7 +622,7 @@ var experiment = {
                 $(".fruit_r2").bind("click", experiment.eat);
             };
         };
-}, 000);
+}, 7000);
   
   },
  // sequence of events during training exposure

### 2018-06-28 experiments/Ex3_2/Ex3_novel_weak.js
updating exp variable priors

@@ -367,7 +367,7 @@ var experiment = {
        
     // data collected  
       data = {
-        experiment: "novel_inf",
+        experiment: "novel_weak",
         trial: trial[0],
         speaker: experiment.cond[0][1],
         alignment: alignment,

### 2018-06-28 experiments/Ex3_2/Ex3_pref_strong.js

@@ -368,7 +368,7 @@ var experiment = {
        
     // data collected  
       data = {
-        experiment: "pref_inf",
+        experiment: "pref_strong",
         trial: trial[0],
         speaker: experiment.cond[0][1],
         alignment: alignment,

### 2018-06-29 stats/ex3_comparisons.Rmd
fixing bug in exp 3 novel med and weak

@@
 
+```{r model no prior loglikelihood}
+no.prior.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+
+var loglike = Binomial({
+        p: Math.exp(modelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
 ```{r model rsa loglikelihood}
@@
 
+llh.no.prior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, no.prior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "No Prior")
+
 llh.rsa <- webppl(
@@
 likelihood_overview <- bind_rows(
+  llh.no.prior,
   llh.rsa,

### 2018-06-29 experiments/Ex3_2/Ex3_novel_medium.js

@@ -916,7 +916,7 @@ if (experiment.cond[0][2] == "right"){
   
    
 // animate object when visible and pointed at  
-    if (experiment.agentOrient[0][0].slice(0,-1) == "point_r") {
+    if (experiment.agentOrient[0][0] == "point_r") {
         setTimeout(function() {
             $("#fruit_r").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
             $("#fruit_r").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
@@ -925,7 +925,7 @@ if (experiment.cond[0][2] == "right"){
         }, 1500)
     }; 
       
-    if (experiment.agentOrient[0][0].slice(0,-1) == "point_l") {
+    if (experiment.agentOrient[0][0] == "point_l") {
         setTimeout(function() {
             $("#fruit_l").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
             $("#fruit_l").animate({width: "130px",opacity: '1', queue: false, duration: 1000});

### 2018-06-29 experiments/Ex3_2/Ex3_novel_weak.js

@@ -915,24 +915,21 @@ if (experiment.cond[0][2] == "right"){
   
    
 // animate object when visible and pointed at  
-    if (experiment.agentOrient[0][0].slice(0,-1) == "point_r") {
+    if (experiment.agentOrient[0][0] == "point") {
         setTimeout(function() {
             $("#fruit_r").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
             $("#fruit_r").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
-            $("#fruit_r2").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
-            $("#fruit_r2").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
-        }, 1500)
-    }; 
-      
-    if (experiment.agentOrient[0][0].slice(0,-1) == "point_l") {
-        setTimeout(function() {
+            
             $("#fruit_l").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
             $("#fruit_l").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
+            
+            $("#fruit_r2").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
+            $("#fruit_r2").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
+            
             $("#fruit_l2").animate({width: "200px",opacity: '0.3', queue: false, duration: 1000});
             $("#fruit_l2").animate({width: "130px",opacity: '1', queue: false, duration: 1000});
         }, 1500)
-    };       
-      
+    }; 
       
     // play sound depending on agent orientation 
     // agent says hello  

### 2018-06-29 stats/data_preprocessing_Ex3.R

@@ -1,4 +1,4 @@
-install.packages("stringr")
+
 library(rjson)
 library(tidyr)
 library(stringr)
@@ -16,14 +16,14 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 
 # select all files from individual workers
-#files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/sandbox-results")
-files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/sandbox-results")
+#files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  #jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/sandbox-results/",f,sep="")
-  jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/sandbox-results/",f,sep="")
+  #jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -34,19 +34,19 @@ for (f in files) {
 # convert into short format, drop unnecessary columns, rename variables and sort by id
 novel.data= melt(setDT(raw), measure = patterns( "^data.experiment","^data.agent","^data.altAgent","^data.rightFruit","^data.leftFruit","^data.corrFruit_inf","^data.corrFruit_novel","^data.pick","^data.novel","^data.inf","^data.trial","^data.alignment","^data.speaker","^data.rt", "^data.correct_inf","^data.correct_novel"))
 names(novel.data) = c("id","alltrial","experiment","agent","altAgent","rightFruit","leftFruit","corObjInf","corObjPrior","pick","prior","inf","trial","alignment","change","rt","correct_inf","correct_prior") 
-novel.data$pick= str_sub(novel.data$pick,63,str_length(novel.data$pick)-4)
+novel.data$pick= str_sub(novel.data$pick,65,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(id)]
[…]

### 2018-07-26 stats/ex3_2_variable_priors_comparison.Rmd
new kids informativeness version

---
title: "MCC Ex3 Variable Priors"
author: "Manuel Bohn"
date: "30 6 2018"
output: 
  html_document:
  toc: true
  toc_float: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
library(ggpubr)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

# Overview of the data

```{r data, include= FALSE}

dat <- bind_rows(read_csv(file="ex3.2.novel.strong.data.csv"),
               read_csv(file="ex3.2.novel.medium.data.csv"),
               read_csv(file="ex3.2.novel.weak.data.csv"),
               read_csv(file="ex3.2.pref.strong.data.csv"),
               read_csv(file="ex3.2.pref.medium.data.csv")
               ) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
```

```{r sanity checks, include= FALSE}
# check if there are incongruent trials in which informativeness and prior yield the same results
# is not the case, that's good
dat %>%
  filter(alignment == "incongruent") %>%
  filter(correct_inf == correct_prior)

# check if someone needs to be excluded because wrong in training
# no one, that's good
y <- dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct_inf = mean(correct_inf)) %>%
  filter(correct_inf == 0)

# check if someone did both experiments

dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct_inf)) %>%
  filter(n > 2)

# exclude those who failed in training and did both experiments
data <- dat %>%
  filter(!id %in% y$id)%>% 
  distinct(id, alltrial, .keep_all = TRUE) %>%
  filter(trial_type != "train") %>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(grepl("pref",experiment), "Preference", "Novelty"),
         Prior = ifelse(prior == "weak", "Weak", ifelse(prior == "medium", "Medium", "Strong"))
         )

data %>%
  group_by(Prior,Experiment,Change,Alignment) %>%
  summarise(n = length(id))

```

```{r plot data, echo = FALSE}

p1 <- data %>%
  filter(trial_type == "test") %>%
  mutate(Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
  group_by(Prior,Change ,Experiment,Alignment, id) %>%
  summarise(correct = mean(correct_inf)) %>%
  multi_boot_standard(col = "correct")

ggplot(p1, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Prior)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)

```

```{r comparisons to chance, include= FALSE}
library(exactRankTests)

data %>%  
  filter(trial_type == "test") %>%
  group_by(change ,experiment,alignment, id) %>%
  summarise(correct_inf = mean(correct_inf)) %>%
  summarize(correct_inf = list(correct_inf)) %>%
  group_by(change ,experiment,alignment) %>%
  mutate(mean = mean(unlist(correct_inf)),
         stat = wilcox.exact(unlist(correct_inf), mu = 0.5)$statistic,
         p_value = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
  select(change ,experiment,alignment,mean,stat,p_value)%>%
  knitr::kable(digits = 3)
```

## Comparing data from Time 1 and 2

The strong prior manipulations in Time 2 are a replication of the first round of data collection. In general the results are very similar. Preference, different speaker, incongruent differs the most. 
```{r comparing data to first round of data collection, include = FALSE}
# getting data from time 1
dat.t1 <- bind_rows(read_csv(file="ex3.novel.data.csv"),
               read_csv(file="ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))%>%
  filter(trial_type != "train") %>%
  distinct(id, alltrial, .keep_all = TRUE) %>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
         Time = "Time 1")

# joining data files
d.comp <- bind_rows(data%>%filter(Prior == "Strong")%>%mutate(Time = "Time 2"),dat.t1)

p.comp <- d.comp%>%
  group_by(Change,Experiment,Alignment,Time, id) %>%
  summarise(correct = mean(correct_inf)) %>%
  multi_boot_standard(col = "correct")

```

Barplot for Time 1 and 2.

```{r, echo= FALSE}
# plot

ggplot(p.comp, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Time)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```

```{r correlation time 1 and 2, include = FALSE, warning = FALSE}
# correlation
p.cor.comp <- data.frame(Time1 = p.comp$mean[p.comp$Time == "Time 1"],
                         Time2 = p.comp$mean[p.comp$Time == "Time 2"],
                         ci_low1 = p.comp$ci_lower[p.comp$Time == "Time 1"],
                         ci_low2 = p.comp$ci_lower[p.comp$Time == "Time 2"],
                         ci_up1 = p.comp$ci_upper[p.comp$Time == "Time 1"],
                         ci_up2 = p.comp$ci_upper[p.comp$Time == "Time 2"])

```

Correlation between Time 1 and 2.

```{r, echo= FALSE, warning = FALSE}

ggplot(data = p.cor.comp,aes(x = Time1, y = Time2)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  coord_fixed()+
  geom_errorbar(aes(ymin = ci_low2, ymax = ci_up2),width = 0)+
  geom_errorbarh(aes(xmin = ci_low1, xmax = ci_up1), height = 0)+
  xlim(0,1)+ylim(0,1)+
  stat_cor(method = "pearson", label.x = 0.3, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()
```

# GLMMs

Frequentist analysis: GLMMs for each level of prior strength. For "strong" and "medium" we find the interaction between speaker change and incongruent like in the first round of data collection. This suggests that participants differentiate between congruent and incongruent trials when it is the same speaker. The effect is considerably weaker in "medium". For "weak", this interaction is gone. This pattern makes sense and suggests that the experimental manipulations work.

## GLMM strong

```{r glmm strong, cache = TRUE, echo = FALSE}
library(lme4)

m.data.strong <- data %>%
  filter(Prior == "Strong") %>%
  mutate(item = ifelse( change == "false", agent, altAgent))

lm.strong <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change+Alignment|agent), 
              data = m.data.strong, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm.strong)
```

## GLMM medium

```{r glmm medium, cache = TRUE, echo = FALSE}

m.data.medium <- data %>%
  filter(Prior == "Medium") %>%
  mutate(item = ifelse( change == "false", agent, altAgent))

lm.medium <- glmer(correct_inf ~ Experiment*Change*Alignment + (Change*Alignment|id) + (Change+Alignment|agent), 
              data = m.data.medium, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm.medium)
```

## GLMM weak (novelty only)

```{r glmm weak, cache = TRUE, echo = FALSE}

m.data.weak <- data %>%
  filter(Prior == "Weak") %>%
  mutate(item = ifelse( change == "false", agent, altAgent))

lm.weak <- glmer(correct_inf ~ Change*Alignment + (Change*Alignment|id) + (Change+Alignment|agent), 
              data = m.data.weak, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm.weak)

```

# Comparing data to model predictions

```{r joining with predictions, include = FALSE}
da <- data %>%
  mutate(Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
  filter(trial_type=="test")%>%
  mutate(Model = "Data") %>%
  group_by(Model,Prior,Experiment,Change,Alignment)%>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         ci_lower  = qbeta(.025, a, b),
         ci_upper = qbeta(.975, a, b),
         mean = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

pred.ex3 <- read_csv(file = "predictions.ex3.csv")

vp.pd <- bind_rows(pred.ex3,da)

```

Plots for models and predictions. I did not plot the no prior model because it predicts the same for all conditions. The predictions are the ones we pre-registered. The noise parameter is therefore estimated based on the data from the first round.

```{r comparing to predictions barplot, echo = FALSE,fig.width = 10}

vp.pd <- vp.pd%>%
  mutate(Prior = relevel(as.factor(Prior), ref = "Weak"),
         Model = ifelse(Model =="Noisy RSA Model", "RSA",ifelse(Model =="Data", "Data","Prior Only")))

ggplot(vp.pd, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Prior*Model)+
  theme_few() + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)

```

## Correlation between predictions and data

```{r comparing to predictions correlation overall, echo = FALSE, warning= FALSE}
## correlations for model comparisons

pred.ex3$Data = rep(da$mean,2)
pred.ex3$Data_ci_low = rep(da$ci_lower,2)
pred.ex3$Data_ci_up = rep(da$ci_upper,2)

pred.ex3 <- pred.ex3%>%
  mutate(Prior = relevel(as.factor(Prior), ref = "Weak"))

ggplot(data = pred.ex3,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0)+
  facet_grid(~Type)+
  #facet_grid(Type~Prior)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.3, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  scale_colour_solarized()

```

## Correlation between predictions and data seperate for each level of prior strengths

Correlation for weak prior is low because the conditions are so close to one another (see also GLMM).

```{r comparing to predictions correlation, echo = FALSE, warning= FALSE, fig.width=12}
ggplot(data = pred.ex3,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.3)+
  geom_point()+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0)+
  #facet_grid(~Type)+
  facet_grid(Type~Prior)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  stat_cor(method = "pearson", label.x = 0.3, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F)+
  geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few() + 
  scale_colour_solarized()

```

# BDA

All models, including the no prior model, comprise a noise parameter. Surprisingly, the no prior model does better than the prior only model here. This was not the case in the previous round with only the strong priors.

```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

var labels = ["dax","wug"]

var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

var lexicon2 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "circle" :
utterance.label == "wug" ? obj.shape == "triangle" : 
true
}

var lexiconObjects = {
"dax = triangle": {
triangle: "dax", circle: "wug"
},
"dax = circle": {
triangle: "wug", circle: "dax"
},
}

var lexiconObject = {
"dax = triangle": lexicon1,
"dax = circle" : lexicon2
}

var point = function(utterance, obj){
return obj.location == utterance.point
}

var utterancePrior = function(obj, lexiconName){
var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
var point = uniformDraw(locationsWithShape)
var label = lexiconObjects[lexiconName][obj.shape]
return {label: label, point: point}
}

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
'
```

```{r rsaModel, include = FALSE}
rsaModel <- 'var ObjectPrior = Categorical({vs: all_objects, ps: priorProbs })

var pragmaticListener = function(utterance){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample(ObjectPrior);
var S1 = speaker(obj, lexiconName);
observe(S1, utterance)
return {lexicon: lexiconName, obj: obj.shape}
}})
}

var speakerOptimality = 2.25;

var speaker = function(obj, lexiconName){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample(ObjectPrior);
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}

pragmaticListener({label: "dax", point: 2 })
'
```

```{r rsa model2, include = FALSE}
rsaModel2 <- '
var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speakerOptimality = 2.25;

var speaker = function(obj, lexiconName, priorProbs){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}
'
```

```{r model setup, include = FALSE}

strongPriorProbs <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Strong",8))

strongPriorProbs$priorProbs = list(
    c(0.0333333, 0.033333, 0.9666667), 
    c(0.9666667, 0.9666667, 0.0333333),
    c(0.3583333, 0.3583333, 0.6416667),
    c(0.6416667, 0.6416667, 0.3583333),
    c(0.1666667, 0.1666667, 0.8333333),
    c(0.8333333, 0.8333333, 0.1666667),
    c(0.4083333, 0.4083333, 0.5916667),
    c(0.5916667, 0.5916667, 0.4083333))

mediumPriorProbs <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Medium",8))

mediumPriorProbs$priorProbs = list(
    c(0.1465517, 0.1465517, 0.8534483), 
    c(0.8534483, 0.8534483, 0.1465517),
    c(0.4137931, 0.4137931, 0.5862069),
    c(0.5862069, 0.5862069, 0.4137931),
    c(0.2983871, 0.2983871, 0.7016129),
    c(0.7016129, 0.7016129, 0.2983871),
    c(0.4274194, 0.4274194, 0.5725806),
    c(0.5725806, 0.5725806, 0.4274194))

weakPriorProbs <- data.frame(
  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Weak",4))

weakPriorProbs$priorProbs = list(
  c(0.4166667, 0.4166667, 0.5833333), 
  c(0.5833333, 0.5833333, 0.4166667),
  c(0.475, 0.475, 0.5250000),
  c(0.5250000, 0.5250000, 0.475))

vpPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)

vpAllConditions <- vpPriorProbs %>%
  select(-priorProbs)

```

```{r model no prior noise loglikelihood, include = FALSE}
vp.no.prior.noise.loglikelihood <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

var model = function(){
  var noise = uniformDrift({a: 0, b:1, width: 0.1})
  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior : conditionInfo.Prior})

   var conditionSpecificPriors = [.5, .5, .5]

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike
}, allConditions)

 return sum(conditionOutput)
}
'
```

```{r model rsa noise loglikelihood, include = FALSE}
vp.rsa.noise.loglikelihood <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior : conditionInfo.Prior})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior : conditionInfo.Prior})

// display(JSON.stringify(conditionSpecificData))

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike
}, allConditions)

 return sum(conditionOutput)
}
'
```

```{r model prior noise loglikelihood, include = FALSE}
vp.prior.noise.loglikelihood <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, 
        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior : conditionInfo.Prior})

   var conditionSpecificPriors =  _.filter(allPriorProbs, 
        {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior : conditionInfo.Prior})

    var priorOnlyPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
      return obj.shape == "circle" ? 1 : 0
    }})

   var noisyModelPredictions = addNoise(priorOnlyPredictions, noise)

var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

  return  loglike
}, allConditions)

 return sum(conditionOutput)
}
'
```

```{r model loglikelihoods, include = FALSE, cache = TRUE}
###################
# RSA Models
###################

vp.llh.no.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.no.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = vpAllConditions, allPriorProbs = vpPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "No Prior")

vp.llh.rsa.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = vpAllConditions, allPriorProbs = vpPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Pragmatic")

###################
# Prior only models
###################

vp.llh.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = vpAllConditions, allPriorProbs = vpPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior Only")

```

```{r, include = FALSE, include = FALSE}

vp.likelihood_overview <- bind_rows(
  vp.llh.no.prior.noise,
  vp.llh.rsa.noise,
  vp.llh.prior.noise)

ggplot(vp.likelihood_overview, aes(x = value))+
  geom_histogram()+
  xlim(-700,0)+
  facet_wrap(~Model, nrow = 2, scales = "free")

```

## Comparing models

```{r logsum summary, echo = FALSE}
vp.llh.plot <- vp.likelihood_overview %>%
  group_by(Model)%>%
  summarize(logP = logSumExp(value))%>%
  mutate(Model = reorder(Model,logP))

ggplot(vp.llh.plot, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("Log Likelihood per Model")+
  theme_few()+ 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)
```

## Bayes Factors

```{r bayes factors, echo = FALSE}

bf <- data.frame(
  Comparison = c("Pragmatic vs. Prior only","Pragmatic vs. No prior", "No Prior vs. Prior only"),
  BayesFactor = c(
    exp(vp.llh.plot$logP[vp.llh.plot$Model== "Pragmatic"] - vp.llh.plot$logP[vp.llh.plot$Model== "Prior Only"]),
    exp(vp.llh.plot$logP[vp.llh.plot$Model== "Pragmatic"] - vp.llh.plot$logP[vp.llh.plot$Model== "No Prior"]),
    exp(vp.llh.plot$logP[vp.llh.plot$Model== "No Prior"] - vp.llh.plot$logP[vp.llh.plot$Model== "Prior Only"]))
)

bf%>%
  kable(digits = 2)
```

## Model comparison by level of prior strength

```{r model loglikelihoods by prior level, include = FALSE, cache = TRUE}
###################
# No Prior
###################

vp.llh.no.prior.noise.strong <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.no.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Strong"), allConditions = vpAllConditions%>%filter(Prior == "Strong"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Strong")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "No Prior",
         Prior = "Strong")

vp.llh.no.prior.noise.medium <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.no.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Medium"), allConditions = vpAllConditions%>%filter(Prior == "Medium"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Medium")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "No Prior",
         Prior = "Medium")

vp.llh.no.prior.noise.weak <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.no.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Weak"), allConditions = vpAllConditions%>%filter(Prior == "Weak"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Weak")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "No Prior",
         Prior = "Weak")

###################
# RSA Model
###################

vp.llh.rsa.noise.strong <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Strong"), allConditions = vpAllConditions%>%filter(Prior == "Strong"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Strong")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Pragmatic",
         Prior = "Strong")

vp.llh.rsa.noise.medium <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Medium"), allConditions = vpAllConditions%>%filter(Prior == "Medium"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Medium")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Pragmatic",
         Prior = "Medium")

vp.llh.rsa.noise.weak <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Weak"), allConditions = vpAllConditions%>%filter(Prior == "Weak"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Weak")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Pragmatic",
         Prior = "Weak")

###################
# Prior only models
###################

vp.llh.prior.noise.strong <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Strong"), allConditions = vpAllConditions%>%filter(Prior == "Strong"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Strong")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior Only",
         Prior = "Strong")

vp.llh.prior.noise.medium <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Medium"), allConditions = vpAllConditions%>%filter(Prior == "Medium"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Medium")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior Only",
         Prior = "Medium")

vp.llh.prior.noise.weak <- webppl(
  program_code = paste(rsaUtils, rsaModel2, vp.prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data%>%filter(Prior == "Weak"), allConditions = vpAllConditions%>%filter(Prior == "Weak"), allPriorProbs = vpPriorProbs%>%filter(Prior == "Weak")), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior Only",
         Prior = "Weak")

```

```{r, echo = FALSE}

vp.likelihood_overview.variable <- bind_rows(
  vp.llh.no.prior.noise.strong,
  vp.llh.no.prior.noise.medium,
  vp.llh.no.prior.noise.weak,
  vp.llh.rsa.noise.strong,
  vp.llh.rsa.noise.medium,
  vp.llh.rsa.noise.weak,
  vp.llh.prior.noise.strong,
  vp.llh.prior.noise.medium,
  vp.llh.prior.noise.weak)%>%
  mutate(Prior = relevel(as.factor(Prior), ref = "Weak"),
         Model = relevel(as.factor(Model), ref = "Prior Only"))

p.llh.plot.variable <- vp.likelihood_overview.variable %>%
  group_by(Prior, Model)%>%
  summarize(logP = logSumExp(value))

ggplot(p.llh.plot.variable, aes(x = Model, y = logP, fill = Model))+
  geom_bar(stat="identity", color = "black")+
  ggtitle("Log Likelihood per Model and Prior Level")+
  theme_few()+ 
  facet_wrap(~Prior)+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(fill = F)

```

Interestingly the No Prior model does better than the RSA model with weak priors, although the difference is not huge (BF = `r round(exp(p.llh.plot.variable$logP[p.llh.plot.variable$Model== "No Prior" & p.llh.plot.variable$Prior == "Weak"] - p.llh.plot.variable$logP[p.llh.plot.variable$Model== "Pragmatic" & p.llh.plot.variable$Prior == "Weak" ]),2)`).

```{r, include = FALSE}

save.image("mcc_model_comparison.RData")
```

### 2018-07-26 stats/ex3_comparisons.Rmd
new kids informativeness version

--- 2018-06-28 stats/ex3_comparisons.Rmd
@@
 
-load("model.comparisons.RData")
+load("mcc_model_comparisons.RData")
 
@@
 
+```{r model no prior noise loglikelihood}
+no.prior.noise.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+  var noise = uniformDrift({a: 0, b:1, width: 0.1})
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+  var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
 ```{r model rsa noise loglikelihood}
@@
 
+llh.no.prior.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, no.prior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "No Prior")
+
 llh.rsa <- webppl(
@@
 likelihood_overview <- bind_rows(
-  llh.rsa,
-  llh.prior,
+  llh.no.prior.noise,
   llh.rsa.noise,
-  llh.prior.noise,
-  llh.rsa.regPrior,
-  llh.prior.regPrior,
-  llh.rsa.noise.regPrior,
-  llh.prior.noise.regPrior)
+  llh.prior.noise)
 
@@
   guides(fill = F)
-
-save.image(file="model.comparisons.RData")
 
@@
 ```
+
+```{r}
+save.image("mcc_model_comparison.RData")
+```

### 2018-07-26 stats/mcc_inf.Rmd
new kids informativeness version

@@
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
+
+d%>%
+  mutate(pick_position = ifelse(targetOnTable == "inner" & correct == 1, "inner", 
+                             ifelse(targetOnTable == "outer" & correct == 1, "outer",
+                                    ifelse(targetOnTable == "inner" & correct == 0, "outer",
+                                           ifelse(targetOnTable == "outer" & correct == 0, "inner",NA)))))%>%
+  group_by(control)%>%
+  summarise(pick_inner = sum(pick_position == "inner")/length(pick_position))
 

### 2018-07-26 stats/mcc_inf.kids.Rmd
new kids informativeness version

---
title: "MCC Informativeness Kids"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

```{r setup, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data

d <- read_csv(file="kids_inf.data.csv")%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

# Sample size per age bin

We reached the pre-registered sample size for 3yo, that's why I took another look at the data. See below the nr. of subjects we have so far.

```{r kids per age group,echo = F }

d %>%
  group_by(age)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

# Plot overall

We can ignore this plot for now and go straight to the plot by age bin as we are primarily interested in the 3yo.

```{r plot across age, echo = F }
p3 <- d %>%
  filter(trial_type == "test") %>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

p4 <- p3 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p4, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

```

# Plot by age group

Here it seems like there is absolutely nothing for the 3yo. No difference between conditions and no performance above chance. That's bad news, especially since we have good reasons to believe that they are able to do this by that age. So it's reasonable to ask what's wrong with our setup? the next graph might give an answer to that

```{r plot by age, echo= FALSE}
p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(control,age, subid) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~age)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot for object picked based on position on table

There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases). This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field. For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice. The plot below shows the proportion of trials in which they picked the inner object. If position would not matter, this should be at chance in each condition.

This bias seems to be absent in 4yo, so my prediction would be that we will see the effect in the full sample, whereas in the 2yo it is more likely to go away.

```{r plot for pick, echo = F }

p5 <- d%>%
  mutate(pick_position = ifelse(targetOnTable == "inner" & correct == 1, "inner", 
                             ifelse(targetOnTable == "outer" & correct == 1, "outer",
                                    ifelse(targetOnTable == "inner" & correct == 0, "outer",
                                           ifelse(targetOnTable == "outer" & correct == 0, "inner",NA)))),
         age = factor(age),
         control = ifelse(control == "true", "control", "test"))%>%
  group_by(age,control)%>%
  summarise(pick_inner = sum(pick_position == "inner")/length(pick_position))

ggplot(p5, aes(x = control, y = pick_inner, fill = age))+
  geom_bar(stat="identity", color = "black")+
  ylim(-0.05,1.05)+
  facet_wrap(~age)+
  theme_few() +
  geom_hline(yintercept = 0.5, lty=2)+
  scale_colour_solarized()

```

### 2018-07-26 stats/mcc_pref.kids.Rmd
new kids informativeness version

--- 2018-05-16 stats/mcc_pref.kids.Rmd
@@
 ---
-title: "MCC PRefere"
+title: "MCC Preference Kids"
 author: "Manuel Bohn"
-date: "26 4 2018"
+date: "23 7 2018"
 output: html_document
@@
 
-```{r setup}
+```{r setup, include= FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 ###
@@
 
-d <- bind_rows(read_csv(file="kids_pref.data.csv"),
-              read.csv(file="kids_pref_handcoding.data.csv", sep = ";")) %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+d_ipad <- read_csv(file="kids_pref.data.csv")
 
-# children who need to be dropped
-drop <- c("Dryrun","180426_3_pref","180502_1_pref","180503_1_pref","180503_2_pref","180504_1_pref","180511_2_pref","180511_1_pref")
+d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
+  mutate(age_num = as.numeric(as.character(age_num)))
 
-d <- d %>%
-  filter(!id %in% drop)
-
-```
-
-Sanity checks.
-```{r sanity checks}
-
-## sanity checks
-d %>%
-  group_by(trial_type) %>%
-  summarise(n = length(unique(id)), 
-            correct = mean(correct)) %>%
-  knitr::kable(digits = 2)
+d <- bind_rows(d_ipad,d_hand_code)%>%
+  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
+  filter(subid != "200718_8_pref")
 
@@
   filter(trial_type == "train") %>%
-  group_by(id)%>%
+  group_by(subid)%>%
   summarise(correct = mean(correct)) %>%
   filter(correct == 0)
+
 ```
-```{r kids per age group}
+
+# Subjects
+
+There was one additional 4yo in the data set, whom I excluded to get the pre-registered sample size of 45 total.
+For the modeling we might want to include her as that gives us a tiny bit more precision.
+
+## Overall
+
+All training trials were answered correctly, suggesting that children generally understood the procedure.
+Sex is not included in the data set but the sex ration is fairly balances across age bins (47 to 60% girls).
+
+```{r sanity checks, echo = FALSE,warning = FALSE, message = FALSE}
+
+## sanity checks
+d %>%
+  group_by(trial_type) %>%
+  summarise(n = length(unique(subid)), 
+            correct = mean(correct)) %>%
+  knitr::kable(digits = 2)
+
+```
+
+## By age bin
+
+Just to check if we got the planned sample size of 15 per bin.
+
+```{r kids per age group,echo = FALSE}
 
@@
   group_by(age)%>%
-  summarise(n = length(unique(id)))%>%
+  summarise(n = length(unique(subid)),
+            age_num = mean(age_num))%>%
   knitr::kable(digits = 2)
@@
 
-Plot for speaker change with 95%CI
-```{r plot}
+# Plots
 
+## Plot across age bins
+
+Medium overall effect of speaker change.
+
+```{r plot across age}
+p3 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change, subid) %>%
+  summarise(correct = mean(correct))
+
+p4 <- p3 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p3, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p4, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+## Plot by age bin
+
+The following two plots suggest some sort of linear developmental trajectory.
+
+```{r plot by age}
 p1 <- d %>%
   filter(trial_type == "test") %>%
-  group_by(change,age, id) %>%
+  group_by(change,age, subid) %>%
   summarise(correct = mean(correct))
@@
 
-T-tests against chance for each speaker change conditions
+## Plot with age as continuous variable
+
+```{r plot by numerical age}
+p5 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change,age_num, subid) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
+  geom_smooth(method = "loess", se = T)+
+  geom_jitter( alpha = .5, height = 0.04)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Inference
+
+## T-tests against chance across age bins
 ```{r}
@@
   filter(trial_type == "test") %>%
-  group_by(change, id) %>%
+  group_by(change, subid) %>%
   summarise(correct = mean(correct)) %>%
@@
   select(change,df,t_value,p_value) %>%
-  knitr::kable(digits = 2)
+  knitr::kable(digits = 3)
 
@@
 
-ChoiceAgent can be seen as an approximation for "item".
+## T-tests against chance per age bin
+```{r}
+## t tests against chance
+d %>%
+  filter(trial_type == "test") %>%
+  group_by(age,change, subid) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(age,change) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(age,change,df,t_value,p_value) %>%
+  knitr::kable(digits = 3)
+
+```
+
+## GLMM
+
+With age as continuous variable.
+We pre-registered the model with an interaction between age and change as a random slope for subject: `(change * age| subid)`.
+However, including age here seems unnecessary since each subject has only one age.
+I therefore took the interaction out in the model below.
+
+Results mirror what we see in the plots above: increasing effect of speaker change across development.
 
@@
 
-data_cg <- d%>%
+lm_data <- d%>%
   filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
+         age_num = scale(age_num, center = TRUE, scale = TRUE))
 
 # maximal converging model
-lm <- glmer(correct ~ age + change + (age * change |id) + (age * change |choiceAgent), 
-              data = data_cg, family = binomial, 
+lm <- glmer(correct ~ age_num * change + (change | subid) + (age_num * change | choiceAgent), 
+              data = lm_data, family = binomial, 
               control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
@@
 summary(lm)
+
 ```
 
-Conditions by trial.
+# Additional plots
+
+To check for trial and item effects.
+
+## Conditions by trial
 ```{r plot trials}
@@
   filter(trial_type == "test") %>%
-  group_by(change, trial, id) %>%
+  group_by(change, trial, subid) %>%
   summarise(correct = mean(correct)) %>%
@@
 
-Conditions by agents.
-Unequal distribution of agents across change leads to seemingly strange patterns for some agents.
-However, these strange results are always those with very few data points (e.g.
-Tiger novelty speaker change is only one data point).
-For those cells with more than five data points, the pattern is very similar to the overall pattern.
-Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment.
-This causes the unequal distribution.
-```{r trials per condition and agent}
-d %>%
-  filter(trial_type == "test") %>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  group_by(choiceAgent,change) %>%
-  summarise(n = length(choiceAgent), 
-            correct = mean(correct)) %>%
-  knitr::kable(digits = 2)
-```
-
+## By agent
 ```{r plot agents}
@@
   mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  group_by(change, choiceAgent, id) %>%
+  group_by(change, choiceAgent, subid) %>%
   summarise(correct = mean(correct)) %>%

### 2018-07-26 experiments/kids_informativeness/mcc_informativeness.js

@@ -5,6 +5,7 @@ var images = new Array();
 for (i = 0; i < preFruits.length; i++) {
 	images[i] = new Image();
 	images[i].src = "images/" + preFruits[i];
+    images[i].id = preFruits[i];
 }
 
 

### 2018-07-26 experiments/kids_informativeness/mcc_informativeness2.js

@@ -1,0 +1,676 @@
+// preload
+var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preFruits.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preFruits[i];
+    images[i].id = preFruits[i];
+}
+
+
+var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
+	$("#"+id+"_"+orient).show();
+}
+
+function hideAgent() {
+  // Hide all slides
+	$(".agent").hide();
+}
+
[…]

### 2018-07-26 stats/data_preprocessing_Ex3.R

@@ -16,14 +16,19 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 
 # select all files from individual workers
-files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/sandbox-results")
-#files <- dir("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results")
+#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/sandbox-results")
+#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/production-results")
+#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_medium/production-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/production-results")
+
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/sandbox-results/",f,sep="")
-  #jf <- paste("~/Work/MCC/git-mcc/cosub_Ex3_novel/production-results/",f,sep="")
+  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/sandbox-results/",f,sep="")
+  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/production-results/",f,sep="")
+  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_medium/production-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -41,12 +46,14 @@ novel.data = novel.data[order(id)]
 novel.data <- novel.data %>%
   mutate(correct_inf = ifelse(pick == corObjInf,1,0),
          correct_prior = ifelse(pick == corObjPrior,1,0),
-         Prior = substr(experiment,7,12))
+         prior = substr(experiment,7,12))
 # check resulting datafile
 str(novel.data)
 head(novel.data)
 # write csv file for further analysis
-write.csv(novel.data, file="ex3.2.novel.strong.data.csv")
[…]

### 2018-07-26 stats/data_preprocessing_kids.R

@@ -4,7 +4,8 @@ library(tidyr)
 library(stringr)
 library(dplyr)
 library(data.table)
-
+library(readxl)
+library(lubridate)
 
 
 ##
@@ -24,8 +25,8 @@ for (f in files) {
   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(
-                   data = jd$data$data
-)
+    data = jd$data$data
+  )
   raw <- bind_rows(raw, id)
 }
 
@@ -55,18 +56,63 @@ raw <- data.frame()
 for (f in files) {
   jf <- paste("~/Work/MCC/git-mcc/kids_pref_data/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(
+  id <- data.frame(test_date= jf,
                    data = jd$data$data
-)
+  )
   raw <- bind_rows(raw, id)
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
 pref.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.pref","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(pref.data) = c("alltrial","id","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+names(pref.data) = c("test_date","alltrial","subid","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
 pref.data$pick= str_sub(pref.data$pick,118,str_length(pref.data$pick)-4)
 pref.data = pref.data[!duplicated(pref.data), ]
-pref.data = pref.data[order(id)]
+pref.data = pref.data[order(subid)]
+
+# calculating age
+pref.data $test_date = as.Date(str_sub(pref.data $test_date,43,str_length(pref.data $test_date)-11))
+
+
+
+# change subid for subjects so that they match the subject log file
+pref.data <- pref.data%>%
+  filter(subid != "Dryrun")%>%
+  mutate(subid = ifelse(subid == "190718_9_pref" & age == 2,"190718_8_pref", subid),
+         subid = ifelse(subid == "120503_2_pref","180503_2_pref", subid),
[…]

### 2018-07-27 stats/mcc_inf.kids.Rmd
updating kids novelty

@@
 There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases).
-This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field.
+This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field (see below).
+
+![Setup as is.](../../../setup_inf.png)
+
 For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice.

### 2018-07-27 stats/mcc_novel.kids.Rmd
updating kids novelty

--- 2018-07-26 stats/mcc_pref.kids.Rmd
@@
 ---
-title: "MCC Preference Kids"
+title: "MCC Novelty Kids"
 author: "Manuel Bohn"
@@
 
-d_ipad <- read_csv(file="kids_pref.data.csv")
-
-d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
-  mutate(age_num = as.numeric(as.character(age_num)))
-
-d <- bind_rows(d_ipad,d_hand_code)%>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
-  filter(subid != "200718_8_pref")
+d<- read_csv(file="kids_novel.data.csv")%>%
+  mutate(trial_type = ifelse(trial == "train", "train", "test"))
 
@@
 
-There was one additional 4yo in the data set, whom I excluded to get the pre-registered sample size of 45 total.
-For the modeling we might want to include her as that gives us a tiny bit more precision.
-
 ## Overall
-
-All training trials were answered correctly, suggesting that children generally understood the procedure.
-Sex is not included in the data set but the sex ration is fairly balances across age bins (47 to 60% girls).
 
@@
 
-Just to check if we got the planned sample size of 15 per bin.
-
 ```{r kids per age group,echo = FALSE}
@@
 ## Plot across age bins
-
-Medium overall effect of speaker change.
 
@@
 
-With age as continuous variable.
-We pre-registered the model with an interaction between age and change as a random slope for subject: `(change * age| subid)`.
-However, including age here seems unnecessary since each subject has only one age.
-I therefore took the interaction out in the model below.
-
-Results mirror what we see in the plots above: increasing effect of speaker change across development.
-
 ```{r}

### 2018-07-27 experiments/kids_novelty/mcc_novelty.js

@@ -138,35 +138,35 @@ function playSound() {
 
 // Variables and randomization for the experiment
 
-var trial = ["train","train","finTrain",1,2,3,4,5,6]
+var trial = ["train","train","finTrain",1,2,3,4,5,6,7,8]
 
 // agents for training and test
 var trainAgents = ["Elephant","Pig"]
-var allAgents = ["Mouse","Dog","Tiger","Cat","Sheep","Bear","Monkey","Frog","Bunny"];
+var allAgents = ["Elephant","Pig","Frog","Mouse","Monkey","Bunny","Dog","Bear","Tiger","Cat","Sheep","Beaver"];
 
 // randomization of agent and speaker change agent order for test trials
-var testAgents = allAgents.sort(() => .5 - Math.random()).slice(0,6);
+var testAgents = allAgents.sort(() => .5 - Math.random()).slice(0,8);
 var remainingAgent = $.grep(allAgents, function(value) {
     return $.inArray(value, testAgents) < 0;});
-var testAltAgent = remainingAgent.sort(() => .5 - Math.random()).slice(0,3);
+var testAltAgent = remainingAgent.sort(() => .5 - Math.random()).slice(0,4);
 var agents = trainAgents.concat(testAgents);
 var altAgents = testAltAgent;
 
 // randomizing order of speaker change
 var trainSpeakerChange = [["false","false"]];
-var testSpeakerChange = shuffle([shuffle(["true","false"]),shuffle(["false","true"]),shuffle(["false","true"])]);
+var testSpeakerChange = shuffle([shuffle(["true","false"]),shuffle(["false","true"]),shuffle(["false","true"]),shuffle(["false","true"])]);
 var speakerChange = trainSpeakerChange.concat(testSpeakerChange);
 
 // objects on tables in training and test (fruits = toys)
 var trainFruitLeft = ["car","duck"];
 var trainFruitRight = ["bear","ball"];
-var fruits = ["t1","t2","t3","t4","t5","t7","t8","t17","t10", "t11","t12","t15","t16"];
+var fruits = ["t1","t2","t3","t4","t5","t6","t7","t8","t9","t10","t11","t12","t14","t15","t16","t17"];
 
 // randomizing order and combiantion of test objects
-var testRightFruit = fruits.sort(() => .5 - Math.random()).slice(0,6);
+var testRightFruit = fruits.sort(() => .5 - Math.random()).slice(0,8);
 var remainingFruits = $.grep(fruits, function(value) {
[…]

### 2018-07-27 experiments/kids_preference/mcc_preference.js

@@ -181,7 +181,7 @@ var agentOrientations = [
     ["straight","point_r", "point_l","disappear","down"],
     ["straight","point_l", "point_r","disappear","down"],
     ["straight","point_r", "point_l","disappear","down"],
-    ["straight","point_r", "point_l","disappear","down"],
+    ["straight","point_l", "point_r","disappear","down"],
     ["straight","point_r", "point_l","disappear","down"]];
 
 // randomize agent orientations 

### 2018-07-27 stats/data_preprocessing_kids.R

@@ -24,18 +24,55 @@ raw <- data.frame()
 for (f in files) {
   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(
-    data = jd$data$data
+  id <- data.frame(test_date= jf,
+                   data = jd$data$data
   )
   raw <- bind_rows(raw, id)
 }
 
 # convert into short format, drop unnecessary columns, rename variables and sort by id
 novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("alltrial","id","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
+names(novel.data) = c("test_date","alltrial","subid","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
 novel.data$pick= str_sub(novel.data$pick,115,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
-novel.data = novel.data[order(id)]
+novel.data = novel.data[order(subid)]
+
+# calculating age
+novel.data $test_date = as.Date(str_sub(novel.data $test_date,44,str_length(novel.data $test_date)-11))
+
+
+# change subid for subjects so that they match the subject log file
+# also chnage age group for one child to match dob
+novel.data <- novel.data%>%
+  mutate(targetObj = ifelse(target == "left",leftObject, rightObject),
+         subid = ifelse(subid == "180725_9_inf","180725_9_nov", subid),
+         correct = ifelse(pick == targetObj, 1, 0))
+
+# load subject log file
+log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "nov")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+# koin datasets
+novel.data <- left_join(novel.data,log, by = "subid")
+
+# calcualte numerical age at test
+novel.data <- novel.data %>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
[…]

### 2018-07-27 experiments/kids_informativeness/mcc_informativeness2.js
add new info exp version

@@ -1,5 +1,5 @@
 // preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
+var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png","fence.png"];
 //for critical trials and fillers
 var images = new Array();
 for (i = 0; i < preFruits.length; i++) {
@@ -9,12 +9,13 @@ for (i = 0; i < preFruits.length; i++) {
 }
 
 
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
[…]

### 2018-07-27 experiments/kids_novelty/mcc_novelty.js

@@ -379,7 +379,7 @@ newtrial: function() {
     
     // play choice sound only in training
     if (experiment.trial[0] == "train"){
-        sourceSound("sound/"+agents[0]+"_choice.mp3");
+        sourceSound("sound/"+agents[0]+"_train.mp3");
         playSound();
     } else { 
    // play hello/return sound and choice depending on speaker chnage condition in test trials 

### 2018-07-27 stats/data_preprocessing_kids.R

@@ -205,7 +205,7 @@ inf.data <- inf.data%>%
          subid = ifelse(subid == "180726_7_inf" & age == 4,"180726_6_inf_2", subid),
          age = ifelse(subid == "200718_4_inf",2, age),
          age = ifelse(subid == "180725_1_inf",4, age),
-         targetObj = ifelse(target == "left",leftObject, rightObject),
+         targetObj = ifelse(target == "right",rightObject, leftObject),
          correct = ifelse(pick == targetObj, 1, 0))
 
 # load subject log file

### 2018-07-27 experiments/kids_informativeness/mcc_informativeness2.js
disableing preview button in preview

@@ -165,6 +165,17 @@ function playSound() {
 
 
 
+$("#button").click(function() {
+    //disable accept button if in turk preview mode
+    if (turk.previewMode) {
+      showSlide("instructions");
+      alert("Please accept HIT to view");
+    } else {
+      showSlide('training')
+    }
+});
+
+
 // Variables and randomization for the experiment
 
 var trial = ["train1","train2","finTrain",1,2,3,4,5,6,7,8]

### 2018-07-27 experiments/kids_informativeness/mcc_informativeness2.js
disableing preview button in preview

@@ -424,6 +424,7 @@ eat2: function(event) {
     
     background2("images/back"+back[0]+".jpg");
 
+    setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);
       
     // specify what is shown on the tables depending on training and test condition
     if (experiment.trial[0] == "train1"){

### 2018-07-27 experiments/kids_informativeness/mcc_informativeness2.js
adding text

@@ -424,7 +424,8 @@ eat2: function(event) {
     
     background2("images/back"+back[0]+".jpg");
 
-    setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);
+      $("#text2").text(""); 
+      setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);
       
     // specify what is shown on the tables depending on training and test condition
     if (experiment.trial[0] == "train1"){
@@ -547,7 +548,9 @@ eat2: function(event) {
     };  
     
     showSlide("stage");  
-     
+    
+  
+      
     background("images/back"+back[0]+".jpg")
       
     // show agent

### 2018-07-30 stats/mcc_inf.kids.Rmd
add new info exp version
adding new kids inforamtiveness experiment

@@
 
-We reached the pre-registered sample size for 3yo, that's why I took another look at the data. See below the nr. of subjects we have so far.
-
 ```{r kids per age group,echo = F }
@@
   knitr::kable(digits = 2)
+
 ```
@@
 # Plot overall
-
-We can ignore this plot for now and go straight to the plot by age bin as we are primarily interested in the 3yo.
 

### 2018-07-30 experiments/kids_informativeness/mcc_informativeness2.js

@@ -424,8 +424,8 @@ eat2: function(event) {
     
     background2("images/back"+back[0]+".jpg");
 
-      $("#text2").text(""); 
-      setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);
+     /* $("#text2").text(""); 
+      setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);*/
       
     // specify what is shown on the tables depending on training and test condition
     if (experiment.trial[0] == "train1"){
@@ -449,7 +449,9 @@ eat2: function(event) {
                 if (experiment.inf[0] == "left") {
                     showAgent(agents[0],"choice")
                    
-                    $("#"+agents[0]+"_choice").animate({left: 0, bottom: 145, queue: false},1000);
+                    $("#"+agents[0]+"_choice").animate({left: -5, bottom: 185, queue: false},1000);
+                    
+                    $("#"+agents[0]+"_choice").animate({left: -10, bottom: 145, width: 350, queue: true},500);
                     
                     choiceLeftFruit("images/"+experiment.fruitPosition[0]+".png");
                     choiceLeftFruit2("images/"+experiment.fruitPosition.filter(function(x) { return x !== experiment.fruitPosition[0]; })+".png");
@@ -461,7 +463,9 @@ eat2: function(event) {
                 } else { 
                     showAgent(agents[0],"choice")
                    
-                    $("#"+agents[0]+"_choice").animate({left: 630, bottom: 145, queue: false},1000)
+                    $("#"+agents[0]+"_choice").animate({left: 635, bottom: 185, queue: false},1000)
+                   
+                    $("#"+agents[0]+"_choice").animate({left: 640, bottom: 145, width: 350, queue: true},500);
                     choiceLeftFruit("images/"+experiment.fruitPosition[0]+".png");
                     choiceLeftFruit2("images/"+experiment.fruitPosition.filter(function(x) { return x !== experiment.fruitPosition[0]; })+".png");
       
@@ -475,7 +479,9 @@ eat2: function(event) {
                     showAgent(agents[0],"choice")
                    
                     
-                    $("#"+agents[0]+"_choice").animate({left: 0, bottom: 145, queue: false},1000);
+                    $("#"+agents[0]+"_choice").animate({left: -5, bottom: 185, queue: false},1000);
+                    
+                    $("#"+agents[0]+"_choice").animate({left: -10, bottom: 145, width: 350, queue: true},500);
[…]

### 2018-07-30 stats/data_preprocessing.R

@@ -87,11 +87,12 @@ write.csv(pref.data, file="pref.weak.data5.csv")
 ################################################################################################################
 
 files <- dir("~/Work/MCC/git-mcc/cosub_informativeness/anonymized-results")
+files <- dir("~/Work/MCC/git-mcc/nosub_informativeness2/production-results")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/cosub_informativeness/anonymized-results/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/nosub_informativeness2/production-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
                    data = jd$answers$data$data
@@ -102,17 +103,23 @@ for (f in files) {
 # convert into short format, drop unnecessary columns, rename variables and sort by id
 inf.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.leftFruit","^data.rightFruit","^data.tablePositionCorr","^data.pick","^data.inf","^data.trial","^data.control","^data.rt", "^data.correct"))
 names(inf.data) = c("id","alltrial","condition","agent","leftObject","rightObject","targetOnTable","pick","target","trial","control","rt","correct") 
-inf.data $pick= str_sub(inf.data $pick,81,str_length(inf.data $pick)-4)
+inf.data $pick= str_sub(inf.data $pick,80,str_length(inf.data $pick)-4)
 inf.data = inf.data[!duplicated(inf.data), ]
 inf.data = inf.data[order(id)]
-inf.data $id = paste(inf.data $id, inf.data $condition,sep="_")
 inf.data$trial[inf.data$trial=="train1"]="train"
 inf.data$trial[inf.data$trial=="train2"]="train"
+
+
+inf.data <- inf.data%>%
+  mutate(targetObj = ifelse(target == "right",rightObject, leftObject),
+         correct = ifelse(pick == targetObj, 1, 0))
+
+
 # check resulting datafile
 str(inf.data)
 head(inf.data)
 # write csv file for further analysis
-write.csv(inf.data, file="inf.data.csv")
+write.csv(inf.data, file="inf.2.data.csv")
 
 ################################################################################################################
 

### 2018-07-30 experiments/kids_informativeness/mcc_informativeness2.js
update agent trajectory kids inf

@@ -463,7 +463,7 @@ eat2: function(event) {
                 } else { 
                     showAgent(agents[0],"choice")
                    
-                    $("#"+agents[0]+"_choice").animate({left: 635, bottom: 185, queue: false},1000)
+                    $("#"+agents[0]+"_choice").animate({left: 645, bottom: 185, queue: false},1000)
                    
                     $("#"+agents[0]+"_choice").animate({left: 640, bottom: 145, width: 350, queue: true},500);
                     choiceLeftFruit("images/"+experiment.fruitPosition[0]+".png");
@@ -492,7 +492,7 @@ eat2: function(event) {
             } else { 
                     showAgent(agents[0],"choice")
                     
-                   $("#"+agents[0]+"_choice").animate({left: 635, bottom: 185, queue: false},1000)
+                   $("#"+agents[0]+"_choice").animate({left: 645, bottom: 185, queue: false},1000)
                    
                     $("#"+agents[0]+"_choice").animate({left: 640, bottom: 145, width: 350, queue: true},500);
             
@@ -532,7 +532,7 @@ eat2: function(event) {
                 $(".fruit_r2").click(experiment.eat);
             };
         };
-}, 7000);
+}, 000);
   },
         
 // moving on within a trial

### 2018-07-30 experiments/kids_informativeness/mcc_informativeness2.js
update agent trajectory kids inf

@@ -532,7 +532,7 @@ eat2: function(event) {
                 $(".fruit_r2").click(experiment.eat);
             };
         };
-}, 000);
+}, 7000);
   },
         
 // moving on within a trial

### 2018-08-03 stats/mcc_inf_pilot_kids.Rmd
kids info with turning and moving agent

--- 2018-02-07 stats/mcc_inf.Rmd
@@
 ---
-title: "MCC_Informativeness"
+title: "MCC Informativeness - moving agent pilots kids"
 author: "Manuel Bohn"
@@
 ## importing data
-d <- read_csv(file="inf.data.csv") %>%
+d <- inf.data %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
   group_by(trial_type) %>%
-  summarise(n = length(unique(id)), 
+  summarise(n = length(unique(subid)), 
             correct = mean(correct)) %>%
@@
 
-Plot for test vs control with 95%CI
+# Plot with 95%CI
 ```{r plot}
 
-ms <- d %>%
+p <- d %>%
   filter(trial_type == "test") %>%
-  group_by(control, id) %>%
-  summarise(correct = mean(correct)) %>%
+  group_by(control, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
   multi_boot_standard(col = "correct")
 
-ggplot(ms, 
-       aes(x = control, y = mean, fill = control)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Proportion Expected Choice")+
-  theme_few(base_size = 12) + 
-  ylim(0,1)+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
   theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Trial Type",
+  scale_colour_solarized(name="Control",
                      breaks=c("false", "true"),
-                     labels=c("Test", "Control"))
+                     labels=c("No", "Yes"))
 ```
@@
   filter(trial_type == "test") %>%
-  group_by(targetOnTable,control, id) %>%
+  group_by(targetOnTable, id) %>%
   summarise(correct = mean(correct)) %>%
@@
 ggplot(ms, 
-       aes(x = control, y = mean, fill = control,frame = targetOnTable)) +
+       aes(x = targetOnTable, y = mean, fill = targetOnTable)) +
   geom_bar(stat="identity") + 
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  facet_wrap(~ targetOnTable) +
   labs(x="",y="Proportion Expected Choice")+
@@
   ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_fill_solarized(name="Trial Type",
@@
   select(control,df,t_value,p_value) %>%
-  knitr::kable(digits = 2)
+  knitr::kable(digits = 3)
 
@@
 # registered  model
-lm <- glmer(correct ~ control +
-              (control |id) + (control |agent), 
+lm <- glmer(correct ~ 1 +
+              (1 |id) + (1 |agent), 
               data = data_inf, family = binomial, 

### 2018-08-03 experiments/kids_informativeness/mcc_informativeness2.js

@@ -476,12 +476,35 @@ eat2: function(event) {
             } else {
                
                 if (experiment.inf[0] == "left") {
-                    showAgent(agents[0],"choice")
+                    
+                    showAgent(agents[0],"point_r")
+                    
+                    
+                    setTimeout(function() {
+            
+                    showAgent(agents[0],"point_l")
+                        
+                    }, 1000);
+                     
+                    
+                    setTimeout(function() {
+            
                    
+                             
+                    $("#"+agents[0]+"_point_l").animate({left: -5, bottom: 185, queue: false},1000);
+                        
+                    }, 2000);
                     
-                    $("#"+agents[0]+"_choice").animate({left: -5, bottom: 185, queue: false},1000);
+                     setTimeout(function() {
                     
+                    showAgent(agents[0],"choice")
+                         
+                    $("#"+agents[0]+"_choice").css({left: -5, bottom: 185} );
+                         
+                         
                     $("#"+agents[0]+"_choice").animate({left: -10, bottom: 145, width: 350, queue: true},500);
+                         
+                    }, 3000)
                     choiceLeftFruit("images/"+experiment.fruitPosition[0]+".png");
                     choiceLeftFruit2("images/"+experiment.fruitPosition.filter(function(x) { return x !== experiment.fruitPosition[0]; })+".png");
                     
@@ -490,12 +513,38 @@ eat2: function(event) {
                     
                     choiceRightFruit("images/"+rightFruit[0]+".png"); choiceRightFruit2("images/empty.png");
             } else { 
-                    showAgent(agents[0],"choice")
                     
-                   $("#"+agents[0]+"_choice").animate({left: 645, bottom: 185, queue: false},1000)
-                   
+                
+                showAgent(agents[0],"point_l")
+                    
+                    
+                setTimeout(function() {
+                         
+                    showAgent(agents[0],"point_r")
+                    
+                    
+                }, 1000)
+                
+        
+                
+            setTimeout(function() {
+                
+                
+                   $("#"+agents[0]+"_point_r").animate({left: 645, bottom: 185, queue: false},1000)
+            
+            }, 2000)
+                
+                setTimeout(function() {
+                         
+                    showAgent(agents[0],"choice")
+    
+                                  
+                $("#"+agents[0]+"_choice").css({left: 645, bottom: 185 });
+                    
[…]

### 2018-08-03 stats/data_preprocessing_kids.R

@@ -163,12 +163,13 @@ write.csv(pref.data, file="kids_pref.data.csv")
 ######## informativeness ###########
 ################################################################################################################
 
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent")
 files <- dir("~/Work/MCC/git-mcc/kids_info_data")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(test_date= jf, 
                    data = jd$data$data
@@ -187,7 +188,9 @@ inf.data$trial[inf.data$trial=="train2"]="train"
 
 
 inf.data <- inf.data%>%
-  mutate(pick = ifelse(subid == "180405_2_inf" | subid == "180718", str_sub(pick,123,str_length(pick)-4) , str_sub(pick,51,str_length(pick)-4)))
+  mutate(pick = ifelse(subid == "180405_2_inf" | subid == "180718", str_sub(pick,123,str_length(pick)-4) , str_sub(pick,51,str_length(pick)-4)),
+         targetObj = ifelse(target == "right",rightObject, leftObject),
+         correct = ifelse(pick == targetObj, 1, 0))
 
 
 # calculating age

### 2018-08-03 experiments/kids_informativeness/mcc_informativeness2.js
update kids info with turning and moveing agent

@@ -489,17 +489,17 @@ eat2: function(event) {
                     
                     setTimeout(function() {
             
-                   
+                   showAgent(agents[0],"choice")
                              
-                    $("#"+agents[0]+"_point_l").animate({left: -5, bottom: 185, queue: false},1000);
+                    $("#"+agents[0]+"_choice").animate({left: -5, bottom: 185, queue: false},1000);
                         
-                    }, 2000);
+                    }, 2100);
                     
                      setTimeout(function() {
                     
-                    showAgent(agents[0],"choice")
+                    
                          
-                    $("#"+agents[0]+"_choice").css({left: -5, bottom: 185} );
+                   // $("#"+agents[0]+"_choice").css({left: -5, bottom: 185} );
                          
                          
                     $("#"+agents[0]+"_choice").animate({left: -10, bottom: 145, width: 350, queue: true},500);
@@ -529,17 +529,17 @@ eat2: function(event) {
                 
             setTimeout(function() {
                 
-                
-                   $("#"+agents[0]+"_point_r").animate({left: 645, bottom: 185, queue: false},1000)
+                showAgent(agents[0],"choice") 
+                   $("#"+agents[0]+"_choice").animate({left: 645, bottom: 185, queue: false},1000)
             
-            }, 2000)
+            }, 2100)
                 
                 setTimeout(function() {
                          
-                    showAgent(agents[0],"choice")
+                   
     
                                   
-                $("#"+agents[0]+"_choice").css({left: 645, bottom: 185 });
+               // $("#"+agents[0]+"_choice").css({left: 645, bottom: 185 });
                     
                     $("#"+agents[0]+"_choice").animate({left: 640, bottom: 145, width: 350, queue: true},500);
             
@@ -562,7 +562,7 @@ eat2: function(event) {
     } else {
         setTimeout(function() {
             sound.find(function (obj){return obj.id == agents[0]+"_choice.mp3"}).play()
-            }, 1800)
+            }, 1500)
         };
       
     // choice can be made by clicking the objects after - possible after 8s

### 2018-08-03 experiments/kids_informativeness/mcc_informativeness2.js
update kids info with turning and moveing agent

@@ -581,7 +581,7 @@ eat2: function(event) {
                 $(".fruit_r2").click(experiment.eat);
             };
         };
-}, 000);
+}, 7000);
   },
         
 // moving on within a trial

### 2018-08-06 stats/mcc_novel_pilot_kids.Rmd
fix bug in novel kids 2

--- 2018-08-03 stats/mcc_inf_pilot_kids.Rmd
@@
 d %>%
-  group_by(trial_type) %>%
+  group_by(age,trial_type) %>%
   summarise(n = length(unique(subid)), 

### 2018-08-06 experiments/kids_novelty/mcc_novelty2.js

@@ -256,13 +256,18 @@ var experiment = {
            sound.find(function (obj){return obj.id == agents[0]+"_train.mp3"}).pause();
         sound.find(function (obj){return obj.id == "end.mp3"}).play()
         
-       } else {
-       
-           sound.find(function (obj){return obj.id ==  altAgents[0]+"_choice.mp3"}).pause();
-           sound.find(function (obj){return obj.id ==  agents[0]+"_choice.mp3"}).pause();
-           sound.find(function (obj){return obj.id == "end.mp3"}).play()
-
-       }
+     } else {
+    
+         if (speakerChange[0][0] == "true"){
+             sound.find(function (obj){return obj.id ==  altAgents[0]+"_choice.mp3"}).pause();
+             
+             sound.find(function (obj){return obj.id == "end.mp3"}).play()
+         } else {
+             sound.find(function (obj){return obj.id ==  agents[0]+"_choice.mp3"}).pause();
+             sound.find(function (obj){return obj.id == "end.mp3"}).play()
+         };
+        
+     }
     
     $(".fruit_r").unbind("click");
     $(".fruit_l").unbind("click");   
@@ -416,20 +421,20 @@ newtrial: function() {
      
     } else { 
    // play hello/return sound and choice depending on speaker chnage condition in test trials 
-    if (experiment.speakerChange[0][0] == "true"){
-        setTimeout(function() {
-              sound.find(function (obj){return obj.id == altAgents[0]+"_hello.mp3"}).play()
-      }, 0);
-       setTimeout(function() {
-        sound.find(function (obj){return obj.id == altAgents[0]+"_choice.mp3"}).play();}, 4000);
-    } else {
-        setTimeout(function() {
-       sound.find(function (obj){return obj.id == agents[0]+"_return.mp3"}).play()
-            ;}, 0);
-       setTimeout(function() {
-              sound.find(function (obj){return obj.id == agents[0]+"_choice.mp3"}).play()
-       ;}, 4000);
-            }; 
+        if (experiment.speakerChange[0][0] == "true"){
+            setTimeout(function() {
+                sound.find(function (obj){return obj.id == altAgents[0]+"_hello.mp3"}).play()
+            }, 0);
+            setTimeout(function() {
+                sound.find(function (obj){return obj.id == altAgents[0]+"_choice.mp3"}).play();}, 4000);
+        } else {
+            setTimeout(function() {
+                sound.find(function (obj){return obj.id == agents[0]+"_return.mp3"}).play()
[…]

### 2018-08-08 stats/mcc_inf_pilot_kids.Rmd
new pilot of inforamtiveness and new version of novelty, both kids

@@
 ## importing data
-d <- inf.data %>%
+d2 <- inf.data %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 d %>%
-  group_by(trial_type) %>%
-  summarise(n = length(unique(subid)), 
-            correct = mean(correct)) %>%
+  group_by(age) %>%
+  summarise(n = length(unique(subid))) %>%
+  knitr::kable(digits = 3)
+
+d2 %>%
+  group_by(age) %>%
+  summarise(n = length(unique(subid))) %>%
   knitr::kable(digits = 3)
@@
 p <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(control, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+```{r plot}
+
+p <- d2 %>%
   filter(trial_type == "test") %>%

### 2018-08-08 stats/mcc_novel_pilot_kids.Rmd
new pilot of inforamtiveness and new version of novelty, both kids

--- 2018-08-03 stats/mcc_inf_pilot_kids.Rmd
@@
 ## importing data
-d <- inf.data %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+d <- novel.data %>%
+  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
+  filter(trial != "7", trial != "8")
 
@@
 d %>%
-  group_by(trial_type) %>%
+  group_by(age,change,trial_type) %>%
   summarise(n = length(unique(subid)), 
@@
 p <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(control, subid) %>%
+  filter(trial != "train") %>%
+  group_by(change, subid) %>%
   summarise(correct = mean(correct))
@@
 ggplot() +
-  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .01)+
+  geom_pointrange(data = p1, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+

### 2018-08-08 experiments/kids_informativeness/mcc_informativeness3_text.js

@@ -9,14 +9,14 @@ for (i = 0; i < preFruits.length; i++) {
 }
 
 
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Elephant_train.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3"];
+/*var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Elephant_train.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3"];
 //for critical trials and fillers
 var sound = new Array();
 for (i = 0; i < preSounds.length; i++) {
 	sound[i] = new Audio();
 	sound[i].src = "sound/" + preSounds[i];
     sound[i].id = preSounds[i];
-}
+}*/
 
 // ## Helper functions
 function showSlide(id) {
@@ -228,6 +228,14 @@ var inf = trainInf.concat(testInf)
 
 var back = shuffle([1,2,3,4,5,6,7,8,9,10]);
 
+var trainWord = ["car","ball"]
+
+var testWord = shuffle( ["ticon","kepel", "glipsa","zubi","oscot","toma","zoyar","wiso"]);
+
+var word = trainWord.concat(testWord);
+
[…]

### 2018-08-08 experiments/kids_novelty/mcc_novelty2.js

@@ -291,7 +291,7 @@ var experiment = {
       data = {
         subid: subid,
         subage: subage,
-        condition: "novelty",
+        condition: "novelty new",
         trial: trial[0],
         speakerChange: speakerChange[0][0],
         agent: agents[0],
@@ -345,7 +345,7 @@ newtrial: function() {
     
     $(".agent_eat").unbind("click"); 
    
-    $("#text3").text("");
+
      
     sourceRightFruit("images/empty.png");
     showRightFruit();
@@ -393,16 +393,7 @@ newtrial: function() {
     };
     
    
-    if (experiment.trial[0] == "train"){
-        $("#text3").text("")
-    } else {  
-         if (speakerChange[0][0] == "true") {
-             $("#text3").text(agents[0]+" is gone ... now "+altAgents[0]+" is here");
-         }else {
-             choiceAgent(agents[0]);
-             $("#text3").text(agents[0]+" is back");
-         };  
-    };
+
       
       
     // animate agent in test trials
@@ -426,14 +417,14 @@ newtrial: function() {
                 sound.find(function (obj){return obj.id == altAgents[0]+"_hello.mp3"}).play()
             }, 0);
             setTimeout(function() {
-                sound.find(function (obj){return obj.id == altAgents[0]+"_choice.mp3"}).play();}, 4000);
+                sound.find(function (obj){return obj.id == altAgents[0]+"_choice.mp3"}).play();}, 2500);
         } else {
             setTimeout(function() {
                 sound.find(function (obj){return obj.id == agents[0]+"_return.mp3"}).play()
                 ;}, 0);
             setTimeout(function() {
                 sound.find(function (obj){return obj.id == agents[0]+"_choice.mp3"}).play()
-                ;}, 4000);
+                ;}, 2500);
         }; 
     }
       
@@ -441,7 +432,7 @@ newtrial: function() {
     setTimeout(function() {      
     $(".fruit_r").click(experiment.eat);
     $(".fruit_l").click(experiment.eat);
-}, 9000);
+}, 8000);
   },
   
 // sequence of events during training exposure
@@ -511,7 +502,7 @@ newtrial: function() {
    // play sound depending on agent orientation 
 // agent says hello
     if (experiment.agentOrient[0][0] == "straight") { 
-        pause("next",3000); 
+        pause("next",2000); 
   sound.find(function (obj){return obj.id == agents[0]+"_hello.mp3"}).play()
     };  
 // agent says hello when returning    
@@ -523,33 +514,33 @@ newtrial: function() {
[…]

### 2018-08-08 stats/data_preprocessing_kids.R

@@ -19,10 +19,12 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 # select all files from individual workers
 files <- dir("~/Work/MCC/git-mcc/kids_novel_data")
 
+files <- dir("~/Work/MCC/git-mcc/kids_novel_pilot")
+
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_novel_pilot/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(test_date= jf,
                    data = jd$data$data
@@ -36,6 +38,8 @@ names(novel.data) = c("test_date","alltrial","subid","age","condition","agent","
 novel.data$pick= str_sub(novel.data$pick,115,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(subid)]
+
+
 
 # calculating age
 novel.data $test_date = as.Date(str_sub(novel.data $test_date,44,str_length(novel.data $test_date)-11))
@@ -171,13 +175,18 @@ write.csv(pref.data, file="kids_pref.data.csv")
 ######## informativeness ###########
 ################################################################################################################
 
-files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_turning")
+
 files <- dir("~/Work/MCC/git-mcc/kids_info_data")
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/filler")
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_turning")
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent")
+
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/moving_turning/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/filler/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(test_date= jf, 
                    data = jd$data$data
@@ -193,6 +202,8 @@ inf.data = inf.data[!duplicated(inf.data), ]
[…]

### 2018-08-08 experiments/kids_informativeness/mcc_informativeness3_text.js
fix timing info kids 3

@@ -667,7 +667,7 @@ eat2: function(event) {
                 $(".fruit_r2").click(experiment.eat);
             };
         };
-}, 000);
+}, 6000);
   },
         
 // moving on within a trial

### 2018-08-08 experiments/kids_informativeness/mcc_informativeness3_text.js
change trial names kids inf 3

@@ -178,7 +178,7 @@ $("#button").click(function() {
 
 // Variables and randomization for the experiment
 
-var trial = ["train1","train2","finTrain","train3",1,2,3,"train4",4,5,6]
+var trial = ["train1","train2","finTrain","filler1",1,2,3,"filler2",4,5,6]
 // agent order for training
 var trainAgents = ["Elephant","Pig"]
 var allAgents = ["Elephant","Pig","Frog","Mouse","Monkey","Bunny","Dog","Bear","Tiger","Cat","Sheep","Beaver"];
@@ -456,7 +456,7 @@ eat2: function(event) {
       setTimeout(function() {$("#text2").text("Click on the toy")}, 10000);*/
       
     // specify what is shown on the tables depending on training and test condition
-    if (experiment.trial[0] == "train1" || experiment.trial[0] == "train3"){
+    if (experiment.trial[0] == "train1" || experiment.trial[0] == "filler1"){
            showAgent(agents[0],"point_r")
                     
                     
@@ -491,7 +491,7 @@ eat2: function(event) {
         choiceRightFruit("images/"+rightFruit[0]+".png");     
         choiceRightFruit2("images/empty.png");
         
-        } else if (experiment.trial[0] == "train2" || experiment.trial[0] == "train4"){
+        } else if (experiment.trial[0] == "train2" || experiment.trial[0] == "filler2"){
             
           showAgent(agents[0],"point_l")
                     
@@ -653,7 +653,7 @@ eat2: function(event) {
       
     // choice can be made by clicking the objects after - possible after 8s
     setTimeout(function() {
-        if (experiment.trial[0] == "train1" || experiment.trial[0] == "train2" || experiment.trial[0] == "train3" || experiment.trial[0] == "train4") {
+        if (experiment.trial[0] == "train1" || experiment.trial[0] == "train2" || experiment.trial[0] == "filler1" || experiment.trial[0] == "filler1") {
             $(".fruit_l").click(experiment.eat);
             $(".fruit_l2").click(experiment.eat);
             $(".fruit_r").click(experiment.eat);
@@ -726,7 +726,7 @@ eat2: function(event) {
         showRightFruit();
         sourceRightFruit2("images/"+rightFruit[0]+".png");
         showRightFruit2(); 
-    } else  if (experiment.trial[0] == "train3"){
+    } else  if (experiment.trial[0] == "filler1"){
[…]

### 2018-08-08 stats/data_preprocessing_kids.R

@@ -186,7 +186,7 @@ files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent")
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/filler/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(test_date= jf, 
                    data = jd$data$data
@@ -202,8 +202,8 @@ inf.data = inf.data[!duplicated(inf.data), ]
 inf.data = inf.data[order(subid)]
 inf.data$trial[inf.data$trial=="train1"]="train"
 inf.data$trial[inf.data$trial=="train2"]="train"
-inf.data$trial[inf.data$trial=="train3"]="train"
-inf.data$trial[inf.data$trial=="train4"]="train"
+inf.data$trial[inf.data$trial=="filler1"]="filler"
+inf.data$trial[inf.data$trial=="filler2"]="filler"
 
 
 inf.data <- inf.data%>%

### 2018-08-08 experiments/kids_informativeness/mcc_informativeness3_text.js
change trial names kids inf 3

@@ -653,7 +653,7 @@ eat2: function(event) {
       
     // choice can be made by clicking the objects after - possible after 8s
     setTimeout(function() {
-        if (experiment.trial[0] == "train1" || experiment.trial[0] == "train2" || experiment.trial[0] == "filler1" || experiment.trial[0] == "filler1") {
+        if (experiment.trial[0] == "train1" || experiment.trial[0] == "train2" || experiment.trial[0] == "filler1" || experiment.trial[0] == "filler2") {
             $(".fruit_l").click(experiment.eat);
             $(".fruit_l2").click(experiment.eat);
             $(".fruit_r").click(experiment.eat);
@@ -735,7 +735,7 @@ eat2: function(event) {
         showRightFruit();
         sourceRightFruit2("images/empty.png");
         showRightFruit2(); 
-    } else  if (experiment.trial[0] == "train2"){
+    } else  if (experiment.trial[0] == "filler2"){
         sourceLeftFruit("images/empty.png");
         showLeftFruit(); 
         sourceLeftFruit2("images/"+leftFruit[0]+".png");

### 2018-08-08 experiments/kids_informativeness/mcc_informativeness3_text.js
change trial names kids inf 3

@@ -449,7 +449,7 @@ eat2: function(event) {
     
       setTimeout(function() {  
           $("#text2").text("Here is a table with a "+experiment.word[0]+", how "+experiment.filler[0]+", a table with a "+experiment.word[0]+". Can you give "+experiment.agents[0]+" the "+experiment.word[0]+"?")
-      }, 3000)
+      }, 0)
 
 
      /* $("#text2").text(""); 

### 2018-10-29 stats/kids_Ex3_pref.Rmd
adding kids exp 3

---
title: "MCC Informativeness Kids 2"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,45,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_raw <-raw_data %>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         experiment = "mcc_kids_inf_2")

unique(d$subid)

log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf")%>%
  select(subid,experimenter,keep_drop,sex,dob)

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

```

# Sample size per age bin

```{r kids per age group,echo = F }

d %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

```

# Plot filler by age

```{r plot by age, echo= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

pf2 <- pf1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pf1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = pf2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot by age group

```{r plot by age, echo= FALSE}

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot overall test

```{r plot across age, echo = F }
p3 <- d %>%
  filter(trial != "filler1",
  trial != "filler2")%>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

p4 <- p3 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p4, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

```

### 2018-10-29 stats/mcc_inf_pilot_kids.Rmd
adding kids exp 3

--- 2018-08-03 stats/mcc_inf_pilot_kids.Rmd
@@
 ---
-title: "MCC Informativeness - moving agent pilots kids"
+title: "MCC Informativeness - Pilot with Kids"
 author: "Manuel Bohn"
-date: "7 2 2018"
 output: html_document
@@
 
-```{r setup}
+```{r setup, include = F}
 ###
@@
 library(ggthemes)
+library(jsonlite)
 
 ## importing data
-d <- inf.data %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees")
 
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$data$data)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_trees <- raw_data %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$data$data)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_robots <- raw_data %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  id <- as_data_frame(jd$data$data)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_trees_left_right <- raw_data %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")
 ```
 
-Sanity checks.
-```{r training performance}
-## performance in training and test
-d %>%
-  group_by(trial_type) %>%
-  summarise(n = length(unique(subid)), 
-            correct = mean(correct)) %>%
+# Sample
+
+## Trees
+
+```{r sample trees, echo = F}
+
+d_trees %>%
+  group_by(subage) %>%
+  summarise(n = length(unique(subid))) %>%
   knitr::kable(digits = 3)
-
 ```
 
-# Plot with 95%CI
-```{r plot}
+## Robots
 
-p <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(control, subid) %>%
+```{r sample robots, echo = F}
+
+d_robots %>%
+  group_by(subage) %>%
+  summarise(n = length(unique(subid))) %>%
+  knitr::kable(digits = 3)
+```
+
+## Trees left right
+
+```{r sample trees left right, echo = F}
+d_trees_left_right %>%
+  group_by(subage) %>%
+  summarise(n = length(unique(subid))) %>%
+  knitr::kable(digits = 3)
+```
+
+# Results overall
+
+## Trees
+
+Experiment: [Tree Setup](https://langcog.stanford.edu/expts/cue/exp/kids/kids_cue_barrier7_tree.html)
+
+```{r , echo = F}
+
+p <- d_trees %>%
+  group_by(control,subid) %>%
   summarise(correct = mean(correct))
@@
 
-Effect of target object location on table. Inner = closer to the agent, outer = further away. 
-For test this does not seem to matter.
-For control: If they had a tendency to pick the one closer to the agent, they should be above chance for inner and below chance for outer.
-Only the latter seems to be the case.
-Not sure why, could also be just noise.
-```{r inner vs outer location}
-## performance in training and test
-ms <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(targetOnTable, id) %>%
-  summarise(correct = mean(correct)) %>%
+## Robots
+
+Experiment: [Robot Setup](https://langcog.stanford.edu/expts/cue/exp/kids/kids_cue_barrier6.html)
+
+```{r, echo = F}
+
+p <- d_robots %>%
+  group_by(control,subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
   multi_boot_standard(col = "correct")
 
-ggplot(ms, 
-       aes(x = targetOnTable, y = mean, fill = targetOnTable)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Proportion Expected Choice")+
-  theme_few(base_size = 12) +
-  ylim(0,1)+
-  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Trial Type",
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
                      breaks=c("false", "true"),
-                     labels=c("Test", "Control"))
+                     labels=c("No", "Yes"))
+```
+
+## Trees left right
+
+Experiment: [Trees with objects left and right](https://langcog.stanford.edu/expts/cue/exp/kids/kids_cue_barrier8_tree_left_right.html)
+
+```{r, echo = F}
+
+p <- d_trees_left_right %>%
+  group_by(control,subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Results by age
+
+## Trees
+
+```{r , echo = F}
+
+p <- d_trees %>%
+  group_by( subage, control, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+## Robots
+
+```{r , echo = F}
+
+p <- d_robots %>%
+  group_by( subage, control, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+## Trees left right
+
+```{r , echo = F}
+
+p <- d_trees_left_right %>%
+  group_by( subage, control, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Positioning bias (top vs. bottom object more informative)
+
+## Trees
+```{r , echo = F}
+
+p <- d_trees %>%
+  group_by( subage, targetPosition, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+## Robots
+
+```{r , echo = F}
+
+p <- d_robots %>%
+  group_by( subage, targetPosition, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+## Trees left right (here it is inner vs outer object)
+
+```{r , echo = F}
+
+p <- d_trees_left_right %>%
+  group_by( subage, targetPosition, subid) %>%
+  summarise(correct = mean(correct))
+
+p1 <- p %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p1, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+```{r}
+# power analysis for cue barrier
+
+xx <- bind_rows(d_trees,
+d_trees_left_right,
+d_robots)%>%
+  filter(subage != "2")
+
+ power_data <- xx %>%
+  group_by(subage,subid) %>%
+  summarise(correct = mean(correct))
+
+library("lsr")
+
+library("pwr")
+
+d_robots %>%
+  group_by(subage, subid) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(subage) %>%
+  mutate(mean = mean(unlist(correct)),
+        df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
+        d = cohensD(unlist(correct), mu = 0.5)) %>%
+  select(subage,mean,df,t_value,p_value,d) %>%
+  knitr::kable(digits = 3)
+
+cohensD(power_data$correct,mu = 0.5)
+
+pwr.t.test(d = 0.65, power = 0.8, type = "one.sample")
+
+pwr.t.test(d = 0.8, power = 0.8, type = "one.sample")
+
+pwr.t.test(d = 1.05, power = 0.8, type = "one.sample")
 
 ```
-
-Conditions by trial.
-```{r plot trials}
-ms <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(control, trial, id) %>%
-  summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
-
-ggplot(ms, 
-       aes(x = trial, y = mean, col = control)) +
-  geom_line(aes(group= control)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  theme_few() + 
-  scale_colour_solarized()
-```
-
-Conditions by agents.
-```{r trials per condition and agent}
-d %>%
-  filter(trial_type == "test") %>%
-  group_by(agent,control) %>%
-  summarise(n = length(agent), 
-            correct = mean(correct)) %>%
-  knitr::kable(digits = 2)
-```
-
-Agent effect. Dog seems a little strange (despite enough data) but no idea what to make of this.
-```{r plot agents}
-ms <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(control, agent, id) %>%
-  summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
-
-ggplot(ms, 
-       aes(x = agent, y = mean, col = control)) +
-  geom_line(aes(group= control)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  theme_few() + 
-  scale_colour_solarized()
-```
-
-T-tests against chance test and control
-```{r}
-## t tests against chance
-d %>%
-  filter(trial_type == "test") %>%
-  group_by(control, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(control) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(control,df,t_value,p_value) %>%
-  knitr::kable(digits = 3)
-
-```
-
-Agent can be seen as an approximation for "item".
-
-```{r}
-## model
-library(lme4)
-
-data_inf <- d%>%
-  filter(trial_type == "test")%>%
-  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
-
-# registered  model
-lm <- glmer(correct ~ 1 +
-              (1 |id) + (1 |agent), 
-              data = data_inf, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-summary(lm)
-```

### 2018-10-29 stats/mcc_novel.kids.Rmd
adding kids exp 3

@@
 
-d<- read_csv(file="kids_novel.data.csv")%>%
+d_new <- read_csv(file="kids_novel.data.csv")%>%
+  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+
+d_old <- read_csv(file="kids_novel.data.round1.csv")%>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 # no one
-d %>%
+d_new %>%
   filter(trial_type == "train") %>%
@@
   filter(correct == 0)
+
+d_old %>%
+  filter(trial_type == "train") %>%
+  group_by(subid)%>%
+  summarise(correct = mean(correct)) %>%
+  filter(correct == 0)
+
+d <- bind_rows(d_new,d_old)
 
@@
 d %>%
-  group_by(trial_type) %>%
+  group_by(condition,trial_type) %>%
   summarise(n = length(unique(subid)), 
@@
 d %>%
-  group_by(age)%>%
+  group_by(condition,age)%>%
   summarise(n = length(unique(subid)),
@@
   filter(trial_type == "test") %>%
-  group_by(change, subid) %>%
+  group_by(condition,change, subid) %>%
   summarise(correct = mean(correct))
@@
   labs(x="",y="Proportion Expected Choice")+
+  facet_grid(condition ~.)+
   theme_few() +
@@
 
-The following two plots suggest some sort of linear developmental trajectory.
-
 ```{r plot by age}
@@
   filter(trial_type == "test") %>%
-  group_by(change,age, subid) %>%
+  group_by(condition,change,age, subid) %>%
   summarise(correct = mean(correct))
@@
   theme_few() +
-  facet_wrap(~age)+
+  facet_wrap(condition~age)+
   ylim(-0.05,1.05)+
@@
   filter(trial_type == "test") %>%
-  group_by(change,age_num, subid) %>%
+  group_by(condition,change,age_num, subid) %>%
   summarise(correct = mean(correct))
@@
   theme_few() +
+   facet_grid(condition ~.)+
   ylim(-0.05,1.05)+

### 2018-10-29 stats/mcc_summary_inf_pilot_kids.Rmd
adding kids exp 3

---
title: "MCC Informativeness - summary pilots kids"
author: "Manuel Bohn"
date: "7 2 2018"
output: html_document
---

```{r setup, include = FALSE}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)

## round 1 adult design
d_round_1 <- read_csv(file="kids_inf.data.csv")%>%
  filter(trial != "train", control == "false")%>%
  mutate(setup = "table",
         move = "no_move",
         turn = "no_turn",
         wording = "there_is_a_dax",
         filler = "no_filler",
         choice = "object",
         subage = age,
         experiment = "1_round1",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

## introducing filler trials
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/filler")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/filler/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_filler <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "train3",
         trial != "train4")%>%
  mutate(setup = "table",
         move = "no_move",
         turn = "no_turn",
         wording = "there_is_a_dax",
         filler = "filler",
         choice = "object",
         experiment = "2_filler",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

## moving agent
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/moving_agent/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_move_agent <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "train3",
         trial != "train4")%>%
  mutate(setup = "table",
         move = "move",
         turn = "no_turn",
         wording = "there_is_a_dax",
         filler = "no_filler",
         choice = "object",
         experiment = "3_move_agent",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)%>%
  mutate(subage = ifelse(subage == "3 ", "3", subage))

## moving agent, turning before starting to move
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/moving_turning")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/moving_turning/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_move_turn <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "train3",
         trial != "train4")%>%
  mutate(setup = "table",
         move = "move",
         turn = "turn",
         wording = "there_is_a_dax",
         filler = "no_filler",
         choice = "object",
         experiment = "4_move_turn",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

## introduce new wording, spoken by experimenter
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/new_wording")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/new_wording/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_new_wording <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(setup = "table",
         move = "move",
         turn = "turn",
         wording = "Here_is_a_table_with_a_dax",
         filler = "filler",
         choice = "object",
         experiment = "5_new_wording",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)%>%
  filter(subid != "Test")

## introducing robots, agent is looking, experimenter reads text
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_look_1")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_look_1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)%>%
    mutate(subid = jd$data$subid,
           subage = jd$data$subage)
  raw_data <- bind_rows(raw_data, id)
}

d_robot_look <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(setup = "robot",
         move = "no_move",
         turn = "no_turn",
         wording = "Here_is_a_table_with_a_dax",
         filler = "filler",
         choice = "object",
         experiment = "6_robot_look",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)%>%
  filter(subid != "Test")

## robots, agent is pointing
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_1")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_1/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_robot_point <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(setup = "robot",
         move = "no_move",
         turn = "no_turn",
         wording = "Here_is_a_table_with_a_dax",
         filler = "filler",
         choice = "object",
         experiment = "7_robot_point",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

## robots talk themselves
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_3_sound")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_3_sound/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_robot_talk <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(setup = "robot",
         move = "no_move",
         turn = "no_turn",
         wording = "Here_is_a_table_with_a_dax",
         filler = "filler",
         choice = "object",
         experiment = "8_robot_point_talk",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

## robots map onto container
files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$data$data)
  raw_data <- bind_rows(raw_data, id)
}

d_robot_map_container <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(setup = "robot",
         move = "no_move",
         turn = "no_turn",
         wording = "Here_is_a_table_with_a_dax",
         filler = "filler",
         choice = "container",
         experiment = "9_robot_map_container",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

pilot_data <- bind_rows(
  d_round_1,
  d_filler,
  d_move_agent,
  d_move_turn,
  d_new_wording,
  d_robot_look,
  d_robot_point,
  d_robot_talk,
  d_robot_map_container
)

```

# Descriptives

```{r}

```

# Overview by experiment

## Experiment descriptions

* 1_round1: Table setup (like adults) including control trials (4 objects)
* 2_filler: Table setup without control trials but with filler trials
* 3_move_agent: Table setup with agent moving in front of table before asking
* 4_move_turn: Table setup with agent turning to the other table before moving to the target table and requesting
* 5_new_wording: Table setup with experimenter reading out prompts. Wording changed to "Here is a table with a dax".
* 6_robot_look: Robot setup with experimenter reading prompts. Agent looks to robot when making request. Wording (from here onwards): "This is a robot with a dax".
* 7_robot_point: Robot setup, experimenter reading prompts. Agent points twice while labeling and before requesting.
* 8_robot_point_talk: Robot setup, recorded request. Pointing twice to target robot before requesting.
* 9_robot_map_container: Robot setup, recorded request. Pointing twice during labeling. Children pick container instead of object directly.

```{r plot, echo = FALSE, warning = FALSE, fig.width=12}

p <- pilot_data %>%
  group_by(experiment,subage, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(subage~experiment)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

```{r plot, echo = FALSE, warning = FALSE}

p <- pilot_data %>%
  filter(subage != "2")%>%
  group_by(experiment, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = experiment, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(.~experiment)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

# Model across experiments
```{r model, cache = TRUE, warning = FALSE}
library(lme4)

lm <- glmer(correct ~ subage * setup + subage * move + subage * turn + subage * wording + subage * filler + subage * choice + (subage  | agent) + (subage | experiment) + (1 | subid), 
              data = pilot_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm)

```

# Indivudal variations

## Setup

```{r, echo=FALSE}
p <- pilot_data %>%
  group_by(setup,subage, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(setup~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

## Wording

```{r, echo=FALSE}
p <- pilot_data %>%
  group_by(wording,subage, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(wording~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

## Move (only table setup)

```{r, echo=FALSE}
p <- pilot_data %>%
  filter(setup == "table")%>%
  group_by(move,subage, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(move~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

## Filler

```{r, echo=FALSE}
p <- pilot_data %>%
  group_by(filler,subage, subid) %>%
  summarise(correct = mean(correct))

p1 <- p %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(filler~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

### 2018-10-29 stats/visualizations.Rmd
adding kids exp 3

---
title: "MCC Visualizations"
author: "Manuel Bohn"
date: "23 10 2018"
output: html_document
---

```{r setup, include=FALSE}
load("mcc_model_comparison.RData")

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
library(ggpubr)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r}
# data ex 1 and ex 2 adults

d1 <- bind_rows(read_csv(file="novel.data.csv"),
               read_csv(file="pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         control = ifelse(change == "true", "true" , "false"))

d2 <- read_csv(file="inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

d <- bind_rows(d1,d2) %>%
  mutate(condition = ifelse(condition == "preference", 2, ifelse(condition == "novelty", 3,1)))

```

```{r}
# plot ex 1 and 2 adults

## pointrange plot
p1 <- d %>%
  filter(trial_type == "test") %>%
  mutate(control = ifelse(control == "true", "Control", "Test")) %>%
  group_by(condition ,control, id) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct") %>%
  ungroup()%>%
  mutate(condition = as.character(condition))

exp1 <- ggplot() +
  geom_rect(data = p2%>%filter(condition == "1"), aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1%>%filter(condition == "1"), aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2%>%filter(condition == "1"), aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness"))) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F)+ 
  scale_color_manual(name="Condition",
                     breaks=c("Control","Test"),
                     values= c("#657b83","black"))+
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#dc322f","#268bd2","#268bd2"))+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),
        panel.border = element_rect(color = "#dc322f", fill = NA, size = 6))

exp2 <- ggplot() +
  geom_rect(data = p2%>%filter(condition == "2"), aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1%>%filter(condition == "2"), aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2%>%filter(condition == "2"), aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness"))) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F)+ 
  scale_color_manual(name="Condition",
                     breaks=c("Control","Test"),
                     values= c("#839496","black"))+
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#dc322f","#268bd2","#268bd2"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
       axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.border = element_rect(color = "#268bd2", fill = NA, size = 6))

exp3 <- ggplot() +
  geom_rect(data = p2%>%filter(condition == "3"), aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1%>%filter(condition == "3"), aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2%>%filter(condition == "3"), aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness"))) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F)+ 
  scale_color_manual(name="Condition",
                     breaks=c("Control","Test"),
                     values= c("#839496","black"))+
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#dc322f","#268bd2","#268bd2"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.border = element_rect(color = "#268bd2", fill = NA, size = 6))

exp12 <- ggplot() +
  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness"))) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F)+ 
  scale_color_manual(name="Condition",
                     breaks=c("Control","Test"),
                     values= c("#657b83","black"))+
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#dc322f","#268bd2","#268bd2"))+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),
        panel.border = element_rect(color = "#268bd2", fill = NA, size = 6))

```

```{r}
ggsave("graphs/ex1_2.png", width = 6.5, height = 2, scale = 1.8)
```

```{r}
# barplots
p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(condition ,control, id) %>%
  summarise(correct = mean(correct))  %>%
  multi_boot_standard(col = "correct")

ggplot(p1, 
       aes(x = control, y = mean, fill = control)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x="",y="Proportion Expected Choice")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Info."))) +
  theme_few(base_size = 14) + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_fill_solarized(name="Condition",
                     breaks=c("false", "true"),
                     labels=c("Test", "Control"))+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())

```

```{r}
ggsave("graphs/ex1_2.png", width = 6.5, height = 2, scale = 1.5)
```

```{r}
## kids preference data

d_ipad <- read_csv(file="kids_pref.data.csv")

d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
  mutate(age_num = as.numeric(as.character(age_num)))

d <- bind_rows(d_ipad,d_hand_code)%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
  filter(subid != "200718_8_pref")

# check if someone needs to be excluded because wrong in training
# no one
d %>%
  filter(trial_type == "train") %>%
  group_by(subid)%>%
  summarise(correct = mean(correct)) %>%
  filter(correct == 0)
```

```{r}
# kids pref plot

p1 <- d %>%
  filter(trial_type == "test") %>%
  group_by(change,age, subid) %>%
  summarise(correct = mean(correct))%>%
  multi_boot_standard(col = "correct")

ggplot(p1, 
       aes(x = change, y = mean, fill = change)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x="",y="Proportion Expected Choice")+
  facet_wrap( ~ age, labeller = as_labeller(c(`2`="2-year-olds", `3`="3-year-olds", `4`="4-year-olds"))) +
  theme_few(base_size = 14) + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_fill_solarized(name="Condition",
                     breaks=c("false", "true"),
                     labels=c("Test", "Control"))

## pointrange plot
p1 <- d %>%
  filter(trial_type == "test") %>%
  mutate(change = ifelse(change == "true", "Control", "Test")) %>%
  group_by(age ,change, subid) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct") %>%
  ungroup()%>%
  mutate(age = as.character(age))

exp2k <- ggplot() +
  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1, aes(x = change, y = correct, col = change), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean,ymin = ci_lower, ymax = ci_upper, col = change),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  facet_wrap( ~ age, labeller = as_labeller(c(`2`="2-year-olds", `3`="3-year-olds", `4`="4-year-olds"))) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F)+ 
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#268bd2","#268bd2","#268bd2"))+
  scale_color_manual(name="Condition",
                     breaks=c("Control","Test"),
                     values= c("#839496","black"))+
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.border = element_rect(color = "#268bd2", fill = NA, size = 6))

```

```{r}
ggarrange(exp12, exp2k, ncol = 1, nrow = 2, legend = "bottom", common.legend = T)
```

```{r}
ggsave("graphs/ex12_kids.pdf", width = 6.5, height = 4, scale = 1.5)
```

```{r}
# data ex 3 first round

dat <- bind_rows(read_csv(file="ex3.novel.data.csv"),
               read_csv(file="ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

dat %>%
  filter(alignment == "incongruent") %>%
  filter(correct_inf == correct_prior)

# check if someone needs to be excluded because wrong in training
# no one, that's good
dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct_inf = mean(correct_inf)) %>%
  filter(correct_inf == 0)

# check if someone did both experiments
# yes, two people
x <- dat %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct_inf)) %>%
  filter(n > 2)

# exclude those who did both experiments
data <- dat %>%
  filter(!id %in% x$id) %>%
  filter(trial_type != "train") %>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(experiment == "pref_inf", "Preference", "Novelty"))

data %>%
  group_by(experiment,alignment,change) %>%
  summarise(n = length(id))

```

```{r}
# plot data Ex3 first round

p1 <- data %>%
  filter(trial_type == "test") %>%
  group_by(Experiment,Change ,Alignment, id) %>%
  summarise(correct = mean(correct_inf)) %>%
  multi_boot_standard(col = "correct")

ggplot(p1, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid( ~ Experiment)+
  theme_few(base_size = 12) + 
  scale_fill_brewer(type = "qual")+
  theme(axis.text.x=element_text(angle = 0, vjust = 0.5, hjust = 0.5))+
  ylim(0,1)

## pointrange plot
p1 <- data %>%
  filter(trial_type == "test") %>%
  group_by(Experiment,Change ,Alignment, id) %>%
  summarise(correct = mean(correct_inf))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p1, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = 1)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( ~ Experiment + Change) +
  theme_few(base_size = 20) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#859900","#859900","#859900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
        panel.border = element_rect(color = "#859900", fill = NA, size = 6))

```

```{r}
ggsave("graphs/data_ex3_round1.pdf", width = 6.5, height = 3, scale = 1.8)
```

```{r}
## correlation round 1

pc1 <- plot.model%>%
  filter(Model == "Noisy RSA Model")%>%
  mutate(Prior = "Strong")

c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ggtitle("Experiment 3")+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F, size = 6)+
  #geom_smooth(method = "lm", se = F, col = "black", size =1)+
  theme_few(base_size = 20) + 
  guides(col = F)+
  scale_colour_viridis_d()
```

```{r}
ggsave("graphs/model_critique_ex3_round1.png", width = 4, height = 4, scale = 1)
```

```{r}
## correlation round 2

pc2 <- pred.ex3%>%
  filter(Model == "Noisy RSA Model")

c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = 1 )+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ggtitle("Replication/Extension")+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F, size = 6)+
  #geom_smooth(method = "lm", se = F, col = "black", size =0.4)+
  theme_few(base_size = 20) + 
  scale_colour_manual(values = rev(viridis::viridis(3)))
```

```{r}
ggarrange(c1, c2, ncol = 2, nrow = 1, legend = "right", common.legend = T)
```

```{r}
ggsave("graphs/model_critique_ex3_round1_2.pdf", width = 10, height = 4, scale = 1.2)
```

### 2018-10-29 experiments/kids_EX3/Ex3_kids_pref.js

@@ -1,0 +1,1740 @@
+// preload
+var preImages = ["back1.jpg",
+"back2.jpg",
+"back3.jpg",
+"back4.jpg",
+"back6.jpg",
+"back10.jpg",
+"Bear_disappear.png",
+"Bear_eat.png",
+"Bear_look_l.png",
+"Bear_look_r.png",
+"Bear_point_l_straight_n.png",
+"Bear_point_l_straight_p.png",
+"Bear_point_l_up_n.png",
+"Bear_point_l_up_p.png",
+"Bear_point_l.png",
+"Bear_point_r_straight_n.png",
+"Bear_point_r_straight_p.png",
+"Bear_point_r_up_n.png",
+"Bear_point_r_up_p.png",
+"Bear_point_r.png",
+"Bear_straight.png",
+"Beaver_disappear.png",
+"Beaver_eat.png",
+"Beaver_look_l.png",
+"Beaver_look_r.png",
+"Beaver_point_l_straight_n.png",
+"Beaver_point_l_straight_p.png",
+"Beaver_point_l_up_n.png",
+"Beaver_point_l_up_p.png",
+"Beaver_point_l.png",
+"Beaver_point_r_straight_n.png",
+"Beaver_point_r_straight_p.png",
+"Beaver_point_r_up_n.png",
+"Beaver_point_r_up_p.png",
+"Beaver_point_r.png",
+"Beaver_straight.png",
+"Bunny_disappear.png",
+"Bunny_eat.png",
+"Bunny_look_l.png",
+"Bunny_look_r.png",
+"Bunny_point_l_straight_n.png",
+"Bunny_point_l_straight_p.png",
+"Bunny_point_l_up_n.png",
+"Bunny_point_l_up_p.png",
+"Bunny_point_l.png",
+"Bunny_point_r_straight_n.png",
+"Bunny_point_r_straight_p.png",
+"Bunny_point_r_up_n.png",
+"Bunny_point_r_up_p.png",
+"Bunny_point_r.png",
+"Bunny_straight.png",
+"button-gradient.png",
+"Cat_disappear.png",
+"Cat_eat.png",
+"Cat_look_l.png",
+"Cat_look_r.png",
+"Cat_point_l_straight_n.png",
+"Cat_point_l_straight_p.png",
+"Cat_point_l_up_n.png",
+"Cat_point_l_up_p.png",
+"Cat_point_l.png",
+"Cat_point_r_straight_n.png",
[…]

### 2018-10-29 experiments/kids_EX3/mmturkey_mcc_kids_ex3.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2018-10-29 experiments/kids_informativeness/mcc_informativeness4_text.js

@@ -1,0 +1,863 @@
+// preload
+var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png","fence.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preFruits.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preFruits[i];
+    images[i].id = preFruits[i];
+}
+
+
+/*var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Elephant_train.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+    sound[i].id = preSounds[i];
+}*/
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+
+function showAgent(id, orient) {
+	$(".agent").hide();
+    $(".point_agent_l").hide();
+    $(".point_agent_r").hide();
[…]

### 2018-10-29 stats/data_preprocessing_kids.R

@@ -17,14 +17,13 @@ setwd("~/Work/MCC/git-mcc/mcc/stats/")
 
 
 # select all files from individual workers
-files <- dir("~/Work/MCC/git-mcc/kids_novel_data")
+files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round1/")
 
-files <- dir("~/Work/MCC/git-mcc/kids_novel_pilot")
 
 #combine files into one dataframe
 raw <- data.frame()
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_novel_pilot/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round1/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(test_date= jf,
                    data = jd$data$data
@@ -35,26 +34,23 @@ for (f in files) {
 # convert into short format, drop unnecessary columns, rename variables and sort by id
 novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
 names(novel.data) = c("test_date","alltrial","subid","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,115,str_length(novel.data$pick)-4)
+novel.data$pick= str_sub(novel.data$pick,72,str_length(novel.data$pick)-4)
 novel.data = novel.data[!duplicated(novel.data), ]
 novel.data = novel.data[order(subid)]
 
 
 
 # calculating age
-novel.data $test_date = as.Date(str_sub(novel.data $test_date,44,str_length(novel.data $test_date)-11))
+novel.data $test_date = as.Date(str_sub(novel.data $test_date,51,str_length(novel.data $test_date)-11))
 
 
 # change subid for subjects so that they match the subject log file
 # also chnage age group for one child to match dob
 novel.data <- novel.data%>%
   mutate(targetObj = ifelse(target == "left",leftObject, rightObject),
-         subid = ifelse(subid == "180725_9_inf","180725_9_nov", subid),
-         subid = ifelse(subid == "180727_11_inf","180727_11_nov", subid),
[…]

### 2018-10-31 stats/kids_Ex3_pref.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

@@
 ---
-title: "MCC Informativeness Kids 2"
+title: "MCC Ex3 Preference Kids"
 author: "Manuel Bohn"
@@
 ## importing data
-files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
+files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
 
@@
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
@@
 
-d_raw <-raw_data %>%
-  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
-         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
-         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
-         experiment = "mcc_kids_inf_2")
+d_raw <-raw_data
 
-unique(d$subid)
-
-log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "inf")%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-d <- left_join(d_raw,log, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"),
-         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+d_raw
 

### 2018-10-31 stats/mcc_inf.kids.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

@@
 ---
-title: "MCC Informativeness Kids"
+title: "MCC Informativeness Kids 2"
 author: "Manuel Bohn"
-date: "26 4 2018"
 output: html_document
@@
 
-```{r setup, include = F}
+```{r import data, include = F}
 ###
@@
 library(ggthemes)
+library(jsonlite)
+library(readxl)
 
 ## importing data
+files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
 
-d <- read_csv(file="kids_inf.data.csv")%>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,45,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_raw <-raw_data %>%
+  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
+         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
+         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
+         experiment = "mcc_kids_inf_2")
+
+log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "inf")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+d <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
+         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
 
@@
 d %>%
-  group_by(age)%>%
+  group_by(subage)%>%
   summarise(n = length(unique(subid)))%>%
@@
 
-# Plot overall
+# Plot filler by age
+
+```{r plot by age, echo= FALSE}
+pf1 <- d %>%
+      filter(trial == "filler1" | trial == "filler2")%>%
+  group_by(control,subage, subid) %>%
+  summarise(correct = mean(correct))
+
+pf2 <- pf1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Plot by age group
+
+```{r plot by age, echo= FALSE}
+
+p1 <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(control,subage, subid) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Performance by trial
+```{r plot trials}
+ms <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  group_by(subage, trial, subid) %>%
+  summarise(correct = mean(correct)) %>%
+  multi_boot_standard(col = "correct")
+
+ggplot(ms, 
+       aes(x = trial, y = mean, col = subage)) +
+  geom_line(aes(group= subage)) + 
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
+                  position = position_dodge(width = .1)) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  theme_few() + 
+  scale_colour_solarized()
+```
+
+## Plot with age as continuous variable
+
+```{r plot by numerical age}
+p5 <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  group_by(age_num, subid) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p5, aes(x = age_num, y = correct)) +
+  geom_smooth(method = "loess", se = T)+
+  geom_jitter( alpha = .5, height = 0.04)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Plot overall test
 
@@
 p3 <- d %>%
-  filter(trial_type == "test") %>%
+  filter(trial != "filler1",
+  trial != "filler2")%>%
   group_by(control, subid) %>%
@@
 ```
-
-# Plot by age group
-
-Here it seems like there is absolutely nothing for the 3yo.
-No difference between conditions and no performance above chance.
-That's bad news, especially since we have good reasons to believe that they are able to do this by that age.
-So it's reasonable to ask what's wrong with our setup?
-the next graph might give an answer to that
-
-```{r plot by age, echo= FALSE}
-p1 <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(control,age, subid) %>%
-  summarise(correct = mean(correct))
-
-p2 <- p1 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_wrap(~age)+
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
-
-# Plot for object picked based on position on table
-
-There was a small tendency in the adult data to pick the inner object in the control condition (55% of cases).
-This is understandable as the agent is closer to that object and after turning it is the one that is closer in the agent's visual field (see below).
-
-![Setup as is.](../../../setup_inf.png)
-
-For the 3yo, it seems like the tendency to pick the object closer to the agent is much stronger and is in fact driving their choice.
-The plot below shows the proportion of trials in which they picked the inner object.
-If position would not matter, this should be at chance in each condition.
-
-This bias seems to be absent in 4yo, so my prediction would be that we will see the effect in the full sample, whereas in the 2yo it is more likely to go away.
-
-```{r plot for pick, echo = F }
-
-p5 <- d%>%
-  mutate(pick_position = ifelse(targetOnTable == "inner" & correct == 1, "inner", 
-                             ifelse(targetOnTable == "outer" & correct == 1, "outer",
-                                    ifelse(targetOnTable == "inner" & correct == 0, "outer",
-                                           ifelse(targetOnTable == "outer" & correct == 0, "inner",NA)))),
-         age = factor(age),
-         control = ifelse(control == "true", "control", "test"))%>%
-  group_by(age,control)%>%
-  summarise(pick_inner = sum(pick_position == "inner")/length(pick_position))
-
-ggplot(p5, aes(x = control, y = pick_inner, fill = age))+
-  geom_bar(stat="identity", color = "black")+
-  ylim(-0.05,1.05)+
-  facet_wrap(~age)+
-  theme_few() +
-  geom_hline(yintercept = 0.5, lty=2)+
-  scale_colour_solarized()
-
-```

### 2018-10-31 stats/mcc_inf_pilot_kids.Rmd
updating kids experiment - sam trial types in both halfs of exp 3 pref

@@
          subage != "Test")
+
+d_3 <- bind_rows(d_trees,d_trees_left_right,d_robots)
 ```
@@
   group_by( subage, control, subid) %>%
-  summarise(correct = mean(correct))
+  summarise(correct = mean(correct))%>%
+  ungroup()%>%
+  add_row(subage = "2", control = "no", correct = 0, subid = "none")
 
 p1 <- p %>%
+  group_by(subage, control)%>%
   multi_boot_standard(col = "correct")

### 2018-10-31 experiments/kids_EX3/Ex3_kids_pref.js

@@ -622,22 +622,31 @@ var testAgentOrientations = shuffle([
 var agentOrient = trainAgentOrientations.concat(testAgentOrientations)
 
 
-
-
 var trainCond = [
     ["train1","same","left","left"],
     ["train2","same","right","right"]];
-var testCond = shuffle([
+var testCond1 = shuffle([
     ["sameSpInfLPrefL","same","left","left"],
-    ["diffSpInfLPrefL","diff","left","left"],
-    ["sameSpInfRPrefL","same","right","left"],
-    ["diffSpInfRPrefL","diff","right","left"],
-    ["sameSpInfRPrefR","same","right","right"],
     ["diffSpInfRPrefR","diff","right","right"],
+    ["sameSpInfRPrefL","same","right","left"],
+    ["diffSpInfLPrefR","diff","left","right"]])
+    
+var testCond2 = shuffle([    
+    ["sameSpInfRPrefR","same","right","right"],
+    ["diffSpInfLPrefL","diff","left","left"],
     ["sameSpInfLPrefR","same","left","right"],
-    ["diffSpInfLPrefR","diff","left","right"]]);
+    ["diffSpInfRPrefL","diff","right","left"]]);
 
-var cond = trainCond.concat(testCond)
+if (shuffle([1,2])[0] == 1){
+    
+    var cond = trainCond.concat(testCond1.concat(testCond2))
+        
+} else {
+    
+    var cond = trainCond.concat(testCond2.concat(testCond1))
+    
+}
+
 
 // randomizing location of target object (i.e. single object)
 

### 2018-11-07 stats/mcc_inf.kids.Rmd
elaborating on instructions for kids ex 3

@@
          subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
+         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
          test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),

### 2018-11-07 experiments/kids_EX3/Ex3_kids_pref.js

@@ -593,7 +593,7 @@ var targetSwitch = trainTargetSwitch.concat(testTargetSwitch)
 
 
 
-var fruits = shuffle(["t01","t02","t03","t04","t05","t06","t07","t08","t09","t10", "t11","t12","t13","t14","t15","t16","t17","t18","t19","t20","t21","t22"]);
+var fruits = shuffle(["t01","t02","t03","t04","t05","t07","t08","t09","t10", "t11","t12","t13","t14","t16","t17","t18","t19","t20","t21","t22"]);
 // randomizing order and combiantion of test objects
 var rightFruit = fruits.sort(() => .5 - Math.random()).slice(0,10);
 var remainingFruits = $.grep(fruits, function(value) {

### 2018-11-08 stats/mcc_inf.kids.Rmd
update intro message!

--- 2018-10-31 stats/mcc_inf.kids.Rmd
@@
          subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
+         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
          test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
+         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
          experiment = "mcc_kids_inf_2")
@@
          check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+
+pf1 %>%
+  filter(correct == 0)
 
@@
 
-```{r plot by age, echo= FALSE}
+```{r filler by age, echo= FALSE, warning= FALSE}
 pf1 <- d %>%
@@
 
-# Plot by age group
+# Plot test trials by age bin
 
@@
 
-# Performance by trial
-```{r plot trials}
+# Plot with age as continuous variable
+
+```{r plot by numerical age, echo = F}
+p5 <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  group_by(age_num, subid) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p5, aes(x = age_num, y = correct)) +
+  geom_smooth(method = "lm", se = T)+
+  geom_jitter( alpha = .5, height = 0.04)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Performance by trial and age bin
+
+```{r plot trials, echo = F}
 ms <- d %>%
@@
 
-## Plot with age as continuous variable
+## T-tests against chance per age bin
+```{r, echo = F}
+## t tests against chance
+d %>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  group_by(subage, subid) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(subage) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(subage,df,t_value,p_value) %>%
+  knitr::kable(digits = 3)
 
-```{r plot by numerical age}
+```
+
+## GLMM
+
+```{r, include=F}
+## model
+library(lme4)
+
+lm_data <- d%>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# maximal converging model
+lm <- glmer(correct ~ age_num + (1 | subid), 
+              data = lm_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+```
+
+```{r, echo = F}
+summary(lm)
+```
+
+# Effect of target position
+
+Target was either the closer (inner) or further away (outer) object.
+
+```{r, echo = F}
 p5 <- d %>%
   filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(age_num, subid) %>%
+         trial != "filler2")%>%
+  group_by( subage, targetPosition, subid) %>%
   summarise(correct = mean(correct))
 
-ggplot(data = p5, aes(x = age_num, y = correct)) +
-  geom_smooth(method = "loess", se = T)+
-  geom_jitter( alpha = .5, height = 0.04)+
+p6 <- p5 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p5, aes(x = targetPosition, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p6, aes(x = targetPosition, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
+  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
   guides(alpha = F)+ 
-  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Speaker Change",
+  scale_colour_solarized(name="Control",
                      breaks=c("false", "true"),
@@
 
-# Plot overall test
+# Target switch
 
-```{r plot across age, echo = F }
-p3 <- d %>%
+In half of the trials, the target switched sides from exposure to test.
+
+```{r, echo = F}
+p7 <- d %>%
   filter(trial != "filler1",
          trial != "filler2")%>%
-  group_by(control, subid) %>%
+  group_by( subage, targetSwitch, subid) %>%
   summarise(correct = mean(correct))
 
-p4 <- p3 %>%
+p8 <- p7 %>%
   multi_boot_standard(col = "correct")
@@
 ggplot() +
-  geom_jitter(data = p3, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p7, aes(x = targetSwitch, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p8, aes(x = targetSwitch, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
+  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
   guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_colour_solarized(name="Control",
@@
                      labels=c("No", "Yes"))
-
 ```

### 2018-11-23 stats/kids_Ex3_pref.Rmd
start working on kids model predictions

@@
 
-d_raw <-raw_data
-
-d_raw
+d <-raw_data
 
@@
       filter(trial == "filler1" | trial == "filler2")%>%
-  group_by(control,subage, subid) %>%
-  summarise(correct = mean(correct))
+  group_by(subage, subid) %>%
+  summarise(correct = mean(correct_inf))
 
@@
 ggplot() +
-  geom_jitter(data = pf1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = pf2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = pf1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
+  geom_pointrange(data = pf2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
-  facet_wrap(~subage)+
   ylim(-0.05,1.05)+
   guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
 ```
@@
          trial != "filler2")%>%
-  group_by(control,subage, subid) %>%
-  summarise(correct = mean(correct))
+  group_by(speaker, alignment ,subage, subid) %>%
+  summarise(correct = mean(correct_inf))
 
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p1, aes(x = alignment, y = correct, col = alignment, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = alignment, y = mean, col = alignment, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
-  facet_wrap(~subage)+
+  facet_grid(subage~speaker)+
   ylim(-0.05,1.05)+
   guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
   scale_colour_solarized(name="Control",
@@
 ```
-
-# Plot overall test
-
-```{r plot across age, echo = F }
-p3 <- d %>%
-  filter(trial != "filler1",
-  trial != "filler2")%>%
-  group_by(control, subid) %>%
-  summarise(correct = mean(correct))
-
-p4 <- p3 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p3, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-
-```

### 2018-11-23 stats/kids_model_predictions.Rmd
start working on kids model predictions

--- 2018-06-23 stats/model_predictions_variable_priors.Rmd
@@
 ---
-title: "MCC Model Predictions"
+title: "MCC Kids Model Predictions"
 author: "Manuel Bohn"
-date: "15 6 2018"
 output: html_document
@@
 
+```{r}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-
-load("model.predictions.RData")
-
 library(tidyverse)
@@
 ```
+# Pretest
 
+Loading data
+
+```{r pretest data}
+
+pref_data <- read_csv(file="data/kids_pref_data.csv")%>%
+  filter(age != "2",
+         trial_type != "train")%>%
+  mutate(age_bin = factor(age),
+         experiment = "preference_pretest",
+         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
+         agent = ifelse( change == "false", agent, altAgent))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)
+
+inf_data <- read_csv(file="data/kids_inf_data.csv")%>%
+  filter(subage != "2",
+         trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = factor(subage),
+         experiment = "informativeness_pretest",
+         condition = ifelse(control == "no", "test", "control"))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)
+
+pre_data <- bind_rows(pref_data,
+                      inf_data)
+
+```
+
+# Pretest results
+
+```{r pretest plot}
+
+pre_p1 <- pre_data %>%
+  group_by(experiment,condition,age_num,subid)%>%
+  summarise(correct = mean(correct))
+
+ggplot(data = pre_p1, aes(x = age_num, y = correct, col = condition)) +
+  geom_smooth(method = "lm", se = F)+
+  geom_jitter(alpha = .5, height = 0, width = 0)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  facet_wrap(~experiment)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_colour_solarized()
+
+```
+
+# Model predictions
+
+## Pretest slopes
 ```{r rsaUtils, include = FALSE}
@@
 
-```{r rsaModel}
-rsaModel <- 'var ObjectPrior = Categorical({vs: all_objects, ps: priorProbs })
+```{r rsa model, include = FALSE}
 
-var pragmaticListener = function(utterance){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior);
-var obj = sample(ObjectPrior);
-var S1 = speaker(obj, lexiconName);
-observe(S1, utterance)
-return {lexicon: lexiconName, obj: obj.shape}
-}})
-}
+rsaModel <- '
 
-var speakerOptimality = 2.25;
-
-var speaker = function(obj, lexiconName){
-Infer({method: "enumerate", model: function(){
-var utterance = utterancePrior(obj, lexiconName);
-var L0 = literalListener(utterance);
- factor(speakerOptimality * L0.score(obj.shape))
-return utterance
-}})
-}
-
-var literalListener = function(utterance){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior); 
-var lexicon = lexiconObject[lexiconName];
-var obj = sample(ObjectPrior);
-if ("label" in utterance) {
- var truthValue = lexicon(utterance, obj);
- condition(truthValue)
-}
-if (utterance.point) {
- var truthValuePoint = point(utterance, obj);
- condition(truthValuePoint)
-}
-return obj.shape 
-}})
-}
-
-pragmaticListener({label: "dax", point: 2 })
-'
-```
-
-```{r rsa model2, include = FALSE}
-rsaModel2 <- '
 var pragmaticListener = function(utterance, priorProbs){
@@
 }
-
-var speakerOptimality = 2.25;
 
@@
 
-```{r predictions rsa noise, include = FALSE}
-predictions.rsa.noise <-'
-var allConditions = dataFromR.newConditions
-var allData = dataFromR.predData
-var allPriorProbs = dataFromR.predPriorProbs
+```{r speaker optimality slope}
+soSlopeWebppl <- '
+
+var infData = dataFromR.infData
+var priorProbs = [.5, .5, .5]
 
 var model  = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
 
-  var conditionOutput = map(function(conditionInfo){
+  var so_slope = uniform(-5, 5)
+  var so_int = uniform(0, 20)
 
-  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
+    map(function(age){
 
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})
+      var speakerOptimality = so_int  + so_slope * (age - infData.minage)
+      var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs)
 
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
+      observe(rsaPredictions, infData.correct)
 
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
+      return  [infData.experiment + "_" + infData.age_num, Math.exp(model.score(1))]
 
-  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment+ "_" + conditionInfo.Prior, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
- // return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-// generate predictions for new conditions
-
-   var newPredictions = map(function(conditionInfo){
-
-    var newSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior: conditionInfo.Prior})
-
-    var newModelPredictions = pragmaticListener({label: "dax", point: 2 }, newSpecificPriors[0].priorProbs)
-    var newNoisyModelPredictions = addNoise(newModelPredictions, noise)
-
-    return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment + "_" + conditionInfo.Prior, Math.exp(newNoisyModelPredictions.score(1))]
-
-  }, allConditions)
-
-  return extend(_.fromPairs(newPredictions), {noise: noise})
+    }, infData.age_num)
 
@@
 
-```{r model setup, include = FALSE}
-
-strongPriorProbs <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Strong",8))
-
-strongPriorProbs$priorProbs = list(
-    c(0.0333333, 0.033333, 0.9666667), 
-    c(0.9666667, 0.9666667, 0.0333333),
-    c(0.3583333, 0.3583333, 0.6416667),
-    c(0.6416667, 0.6416667, 0.3583333),
-    c(0.1666667, 0.1666667, 0.8333333),
-    c(0.8333333, 0.8333333, 0.1666667),
-    c(0.4083333, 0.4083333, 0.5916667),
-    c(0.5916667, 0.5916667, 0.4083333))
-
-mediumPriorProbs <- data.frame(
-  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Medium",8))
-
-mediumPriorProbs$priorProbs = list(
-    c(0.1465517, 0.1465517, 0.8534483), 
-    c(0.8534483, 0.8534483, 0.1465517),
-    c(0.4137931, 0.4137931, 0.5862069),
-    c(0.5862069, 0.5862069, 0.4137931),
-    c(0.2983871, 0.2983871, 0.7016129),
-    c(0.7016129, 0.7016129, 0.2983871),
-    c(0.4137931, 0.4137931, 0.5862069),
-    c(0.5862069, 0.5862069, 0.4137931))
-
-weakPriorProbs <- data.frame(
-  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
-  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
-  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
-  Prior = rep("Weak",4))
-
-weakPriorProbs$priorProbs = list(
-  c(0.4166667, 0.4166667, 0.5833333), 
-  c(0.5833333, 0.5833333, 0.4166667),
-  c(0.475, 0.475, 0.5250000),
-  c(0.5250000, 0.5250000, 0.475))
-
-predPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)
-
-allPriorProbs <- strongPriorProbs %>%
-  select(-Prior)
-
-allConditions <- predPriorProbs %>%
-  filter(Prior == "Strong")%>%
-  select(-priorProbs, -Prior)
-
-newConditions <- predPriorProbs %>%
-  select(-priorProbs)
-
-predData <- data %>%
-  mutate(Prior = "Strong")
-```
-
-```{r predictions rsa noise, include = FALSE}
-bda.pred.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
-  data = list(allData = data, newConditions = newConditions, predPriorProbs = predPriorProbs, predData = predData), 
+```{r}
+soSlope <- webppl(
+  program_code = paste(rsaUtils, rsaModel, soSlopeWebppl , sep='\n'),
+  data = list(infData = inf_data%>%mutate(minage = min(age_num))), 
   data_var = "dataFromR",
   model_var = "model",
-  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
 )
-
-## distribution of noise
-posterior.noise.pred <- bda.pred.noise %>%
-  filter(Parameter %in% c("noise", "priorExponent"))
-
-ggplot(posterior.noise.pred, aes(x = value))+
-  geom_histogram()+
-  facet_wrap(~Parameter, scales = 'free')
-
-# model predictions
-
-noisy.rsa.pred <- bda.pred.noise %>%
-  filter(!(Parameter %in% c("noise", "priorExponent")))  %>%
-  separate(Parameter, into = c("Experiment", "Change", "Alignment", "Prior"), sep="_")%>%
-  mutate(Model="Noisy RSA Model",
-         Adjustment = "Noise",
-         Type = "RSA",
-         Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
-  group_by(Model,Prior,Adjustment,Type,Experiment,Change,Alignment) %>%
-  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))
-
 ```
@@
 ```{r}
-
-ggplot(noisy.rsa.pred, 
-       aes(x = Change, y = mean, fill = Alignment)) +
-  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
-  labs(x=" ",y="Proportion Choosing More Informative")+
-  facet_grid(Experiment ~ Prior)+
-  theme_few(base_size = 12) + 
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  ylim(0,1)
+save.image(file="kids_ex3_predictions.RData")
 ```
-
-```{r}
-save.image(file="model.predictions.RData")
-```

### 2018-11-23 stats/kids_pref.Rmd
start working on kids model predictions

--- 2018-07-26 stats/mcc_pref.kids.Rmd
@@
 
-d_ipad <- read_csv(file="kids_pref.data.csv")
+# d_ipad <- read_csv(file="kids_pref.data.csv")
+# 
+# d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
+#   mutate(age_num = as.numeric(as.character(age_num)))
+# 
+# d <- bind_rows(d_ipad,d_hand_code)%>%
+#   mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
+#   filter(subid != "200718_8_pref")
+# 
+# 
+# # check if someone needs to be excluded because wrong in training
+# # no one
+# d %>%
+#   filter(trial_type == "train") %>%
+#   group_by(subid)%>%
+#   summarise(correct = mean(correct)) %>%
+#   filter(correct == 0)
 
-d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
-  mutate(age_num = as.numeric(as.character(age_num)))
-
-d <- bind_rows(d_ipad,d_hand_code)%>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
-  filter(subid != "200718_8_pref")
-
-# check if someone needs to be excluded because wrong in training
-# no one
-d %>%
-  filter(trial_type == "train") %>%
-  group_by(subid)%>%
-  summarise(correct = mean(correct)) %>%
-  filter(correct == 0)
+d <- read_csv(file="data/kids_pref_data.csv")
 

### 2018-11-23 experiments/kids_EX3/Ex3_kids_pref.js

@@ -236,32 +236,32 @@ var preImages = ["back1.jpg",
 //for critical trials and fillers
 var images = new Array();
 for (i = 0; i < preImages.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preImages[i];
+    images[i] = new Image();
+    images[i].src = "images/" + preImages[i];
     images[i].id = preImages[i];
 }
 
 
 
 function showLeftFriend(id) {
-	$(".tree_l").hide();
-	$("#"+id+"_l").show();
+    $(".tree_l").hide();
+    $("#" + id + "_l").show();
 }
 
 function showRightFriend(id) {
-	$(".tree_r").hide();
-	$("#"+id+"_r").show();
+    $(".tree_r").hide();
+    $("#" + id + "_r").show();
 }
 
 
 function showLeftChoiceFriend(id) {
     $(".tree_l").hide();
-	$("#"+id+"_l_c").show();
+    $("#" + id + "_l_c").show();
 }
 
 function showRightChoiceFriend(id) {
-	$(".tree_r").hide();
-	$("#"+id+"_r_c").show();
+    $(".tree_r").hide();
+    $("#" + id + "_r_c").show();
 }
 
 var preSounds = ["Bear_hello.mp3",
@@ -377,29 +377,29 @@ var preSounds = ["Bear_hello.mp3",
 //for critical trials and fillers
 var sound = new Array();
 for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
+    sound[i] = new Audio();
+    sound[i].src = "sound/" + preSounds[i];
     sound[i].id = preSounds[i];
 }
 
 // ## Helper functions
 function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
+    // Hide all slides
+    $(".slide").hide();
+    // Show just the slide we want to show
+    $("#" + id).show();
 }
 
 function showText(id) {
-  // Hide all slides
-	$(".text").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
+    // Hide all slides
+    $(".text").hide();
+    // Show just the slide we want to show
+    $("#" + id).show();
 }
 
 
 function showAgent(id, orient) {
-	$(".agent").hide();
+    $(".agent").hide();
     $(".point_agent_l").hide();
[…]

### 2018-11-28 stats/adults/ex3_comparisons.Rmd
add kids so and pref models

--- 2018-07-26 stats/ex3_comparisons.Rmd
@@
 
-load("mcc_model_comparisons.RData")
+load("mcc_model_comparison.RData")
 
@@
 likelihood_overview <- bind_rows(
-  llh.no.prior.noise,
-  llh.rsa.noise,
-  llh.prior.noise)
+  llh.no.prior.noise %>% mutate(Model = "No Prior"),
+  llh.rsa.noise %>% mutate(Model = "Pragmatic"),
+  llh.prior.noise %>% mutate(Model = "Prior only"))
 
@@
   geom_bar(stat="identity", color = "black")+
-  ggtitle("logsumexp per model")+
+  ggtitle("Log Likelihood per Model")+
   theme_few()+ 

### 2018-11-28 stats/adults/mcc_inf2.Rmd
add kids so and pref models

--- 2018-08-03 stats/mcc_inf_pilot_kids.Rmd
@@
 ---
-title: "MCC Informativeness - moving agent pilots kids"
+title: "MCC Informativeness - moving agent"
 author: "Manuel Bohn"
@@
 ## importing data
-d <- inf.data %>%
+d <- read_csv(file="inf.2.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
   group_by(trial_type) %>%
-  summarise(n = length(unique(subid)), 
+  summarise(n = length(unique(id)), 
             correct = mean(correct)) %>%
@@
   filter(trial_type == "test") %>%
-  group_by(control, subid) %>%
+  group_by(control, id) %>%
   summarise(correct = mean(correct))

### 2018-11-28 stats/adults/mcc_novel.Rmd
add kids so and pref models

--- 2018-02-07 stats/mcc_pref.Rmd
@@
 ---
-title: "MCC_Preference"
+title: "MCC_Novelty"
 author: "Manuel Bohn"
@@
 ## importing data
-d <- read_csv(file="pref.data.csv") %>%
+d <- read_csv(file="novel.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 Conditions by agents.
-Unequal distribution of agents across change leads to seemingly strange patterns for some agents.
+Unequal distribution of agents across change combinations leads to seemingly strange patterns for some agents.
 However, these strange results are always those with very few data points (e.g.
@@
 
-T-tests against chance for each speaker change conditions
+T-tests against chance for each change conditions
 ```{r}
@@
 lm <- glmer(correct ~ change +
-              (1 |id) + (1 |choiceAgent), 
+              (change |id) + (change |choiceAgent), 
               data = data_cg, family = binomial, 

### 2018-11-28 stats/adults/mcc_novel.weak.Rmd
add kids so and pref models

--- 2018-11-28 stats/adults/mcc_novel.Rmd
@@
 ---
-title: "MCC_Novelty"
+title: "MCC_Novelty_Weak"
 author: "Manuel Bohn"
-date: "26 1 2018"
+date: "26 4 2018"
 output: html_document
@@
 ## importing data
-d <- read_csv(file="novel.data.csv") %>%
+d <- read_csv(file="novel.weak.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
 
-ms <- d %>%
+p1 <- d %>%
+  filter(trial_type == "test") %>%
+  group_by(change, id) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+
+```
+
+T-tests against chance for each change conditions
+```{r}
+## t tests against chance
+d %>%
   filter(trial_type == "test") %>%
@@
   summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
+  summarise(correct = list(correct)) %>%
+  group_by(change) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(change,df,t_value,p_value) %>%
+  knitr::kable(digits = 2)
 
-ggplot(ms, 
-       aes(x = change, y = mean, fill = change)) +
-  geom_bar(stat="identity") + 
-  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few(base_size = 12) + 
-  ylim(0,1)+
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_fill_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+```
+
+ChoiceAgent can be seen as an approximation for "item".
+
+```{r}
+## model
+library(lme4)
+
+data_cg <- d%>%
+  filter(trial_type == "test")%>%
+  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
+  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
+
+# maximal converging model
+lm <- glmer(correct ~ change +
+              (change |id) + (change |choiceAgent), 
+              data = data_cg, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lm)
 ```
@@
 ```
-
-T-tests against chance for each change conditions
-```{r}
-## t tests against chance
-d %>%
-  filter(trial_type == "test") %>%
-  group_by(change, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(change) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(change,df,t_value,p_value) %>%
-  knitr::kable(digits = 2)
-
-```
-
-ChoiceAgent can be seen as an approximation for "item".
-
-```{r}
-## model
-library(lme4)
-
-data_cg <- d%>%
-  filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  mutate(trial = scale(as.numeric(trial), center = TRUE, scale=FALSE))
-
-# maximal converging model
-lm <- glmer(correct ~ change +
-              (change |id) + (change |choiceAgent), 
-              data = data_cg, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-summary(lm)
-```

### 2018-11-28 stats/adults/mcc_novel.weak2.Rmd
add kids so and pref models

---
title: "MCC_Novelty_Weak2"
author: "Manuel Bohn"
date: "26 4 2018"
output: html_document
---

```{r setup}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)

## importing data
d <- read_csv(file="novel.weak.data2.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

```

Sanity checks.
```{r sanity checks}
# Check if someone participated twice (some issues with nosub made that possible).
## Yes, one person did. 
## Remove (and replace) that person
x <- d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct)) %>%
  filter(n > 2)

# check if someone needs to be excluded because wrong in training
## no one
d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct = mean(correct)) %>%
  filter(correct == 0)

## sanity checks
d %>%
  filter(!id %in% x$id) %>%
  group_by(trial_type) %>%
  summarise(n = length(unique(id)), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)

```

Plot for speaker change with 95%CI
```{r plot}

p1 <- d %>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

```

T-tests against chance for each change conditions
```{r}
## t tests against chance
d %>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test") %>%
  group_by(change, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(change) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(change,df,t_value,p_value) %>%
  knitr::kable(digits = 2)

```

ChoiceAgent can be seen as an approximation for "item".

```{r}
## model
library(lme4)

data_cg <- d%>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent))

# maximal converging model
lm <- glmer(correct ~ change + 
              (change |id) + (change |choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(lm)
```

Conditions by trial.
```{r plot trials}
ms <- d %>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test") %>%
  group_by(change, trial, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = trial, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

Conditions by agents.
```{r trials per condition and agent}
d %>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

```{r plot agents}
ms <- d %>%
  filter(!id %in% x$id) %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(change, choiceAgent, id) %>%
  summarise(correct = mean(correct)) %>%
  multi_boot_standard(col = "correct")

ggplot(ms, 
       aes(x = choiceAgent, y = mean, col = change)) +
  geom_line(aes(group= change)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_hline(yintercept = 0.5, lty=2)+
  theme_few() + 
  scale_colour_solarized()
```

### 2018-11-28 stats/adults/mcc_pref.weak3.Rmd
add kids so and pref models

--- 2018-05-08 stats/mcc_pref.weak2.Rmd
@@
 ## importing data
-d <- read_csv(file="pref.weak.data2.csv") %>%
+d <- read_csv(file="pref.weak.data3.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
@@
   filter(correct == 0)
+
+# check if someone participated twice
+# no one
+d %>%
+  filter(trial_type == "train") %>%
+  group_by(id)%>%
+  summarise(n = length(correct)) %>%
+  filter(n > 2)
 
@@
 # maximal converging model
-lm <- glmer(correct ~ change + (change |id) + (change || choiceAgent), 
+lm <- glmer(correct ~ change + (change |id) + (change | choiceAgent), 
               data = data_cg, family = binomial, 

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
add kids so and pref models

---
title: "MCC Kids Model Predictions"
author: "Manuel Bohn"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(coda)
library(reshape2)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```
# Pretest

Loading data

```{r pretest data}

pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
  filter(age != "2",
         trial_type != "train")%>%
  mutate(age_bin = factor(age),
         experiment = "preference_pretest",
         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
         agent = ifelse( change == "false", agent, altAgent))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)

inf_data <- read_csv(file="../data/kids_inf_data.csv")%>%
  filter(subage != "2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = factor(subage),
         experiment = "informativeness_pretest",
         condition = ifelse(control == "no", "test", "control"))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)

pre_data <- bind_rows(pref_data,
                      inf_data)

```

## Pretest results

```{r pretest plot}

pre_p1 <- pre_data %>%
  group_by(experiment,condition,age_num,subid)%>%
  summarise(correct = mean(correct))

ggplot(data = pre_p1, aes(x = age_num, y = correct, col = condition)) +
  geom_smooth(method = "lm", se = F)+
  geom_jitter(alpha = .5, height = 0, width = 0)+
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~experiment)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized()

```

## RSA model

```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

var prior_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

var labels = ["dax","wug"]

var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

var lexicon2 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "circle" :
utterance.label == "wug" ? obj.shape == "triangle" : 
true
}

var lexiconObjects = {
"dax = triangle": {
triangle: "dax", circle: "wug"
},
"dax = circle": {
triangle: "wug", circle: "dax"
},
}

var lexiconObject = {
"dax = triangle": lexicon1,
"dax = circle" : lexicon2
}

var point = function(utterance, obj){
return obj.location == utterance.point
}

var utterancePrior = function(obj, lexiconName){
var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
var point = uniformDraw(locationsWithShape)
var label = lexiconObjects[lexiconName][obj.shape]
return {label: label, point: point}
}

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
'
```

```{r rsa model, include = FALSE}

rsaModel <- '

var pragmaticListener = function(utterance, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speaker = function(obj, lexiconName, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}
'
```

## Informativeness

###  Inf prior predictions 
```{r prior speaker optimality slope}
priorSoWebppl <- '

var infData = dataFromR
var priorProbs = [.5, .5, .5] 
var speakerOptimality = []

var model  = function(){

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var speakerOptimality = so_int  + so_slope * (age - row.minage)

      var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs, speakerOptimality)

      //display(JSON.stringify(row.minage))

    }, infData)

  return extend({so_int: so_int, so_slope: so_slope})
}
'
```

```{r speaker optimality prior pred}
#so_prior <- readRDS("../saves/so_prior.rds")

so_prior<- webppl(
  program_code = paste(rsaUtils, rsaModel, priorSoWebppl , sep='\n'),
  data = inf_data%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  inference_opts = list(method = "forward", samples = 1000, verbose = T)
)

saveRDS(so_prior, "../saves/so_prior.rds")

priorPred <- so_prior%>%
  spread(Parameter, value)%>%
  mutate(chain = factor(Chain))

so_prior <- so_prior%>%
  mutate(chain = factor(Chain))

mean_so_pre <-priorPred%>%
  summarise(int = mean(so_int),
            slope = mean(so_slope))

```

```{r plot prior pred}
ggplot(data = priorPred) +
  geom_abline(aes(intercept = so_int, slope = so_slope), col = "grey", alpha = 0.3)+
  geom_abline(data = mean_so_pre, aes(intercept = int, slope = slope), size = 1)+
  scale_x_continuous(limits=c(0, 2), name="age", breaks = c(0:2), labels = c(3:5)) +
  scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
  theme_few()
```

```{r}
ggplot(data = so_prior, aes(x = value, fill = chain)) +
  geom_density(alpha = .5)+
  facet_wrap(~Parameter)+
  theme_few()
```

### Inf posterior predictions

```{r posterior speaker optimality slope}
postSoWebppl <- '

var infData = dataFromR
var priorProbs = [.5, .5, .5]

var model  = function(){

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)

      var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs, speakerOptimality)

      observe(rsaPredictions, row.correct)

      //display(rsaPredictions.score( row.correct))
      //display(JSON.stringify(row.correct))
      //display(JSON.stringify(rsaPredictions))

    }, infData)

  return extend({so_int: so_int, so_slope: so_slope})
}
'
```

```{r speaker optimality posterior pred}
# so_post <- readRDS("../saves/so_post.rds")

so_post <- webppl(
  program_code = paste(rsaUtils, rsaModel, postSoWebppl , sep='\n'),
  data = inf_data%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

# saveRDS(so_post, "../saves/so_post.rds")

postPred <- so_post%>%
  spread(Parameter, value)%>%
  mutate(chain = factor(Chain))

so_post <- so_post%>%
  mutate(chain = factor(Chain))

mean_so_post <-postPred%>%
  #group_by(chain)%>%
  summarise(int = mean(so_int),
            slope = mean(so_slope))

# confidence intervals
x_plot <- seq(0, 2, by = 0.1)

ci_so_post <- sapply(1:length(postPred$so_int), function(idx) {
           postPred$so_int[idx] + postPred$so_slope[idx] * x_plot
        })

colnames(ci_so_post) <- 1:length(postPred$so_int)
ci_so_post <- as.data.frame(cbind(x_plot, ci_so_post))
ci_so_post <- melt(ci_so_post, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")

ci_so_post <- ci_so_post %>%
  group_by(x_plot)%>%
  summarise(ci_upper = hdi_upper(y_plot),
            ci_lower = hdi_lower(y_plot))

```

```{r plot posterior pred}

ggplot(data = postPred) +
  geom_abline(aes(intercept = so_int, slope = so_slope), col = "grey", alpha = 0.2)+
  geom_ribbon(data = ci_so_post, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
  geom_abline(data = mean_so_post, aes(intercept = int, slope = slope), size = 1)+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
  scale_y_continuous(limits=c(-2, 4), name="Speaker optimality")+
  #facet_wrap(~chain)+
  theme_few()

```

```{r}
ggplot(data = so_post ) +
  geom_density(aes(x = value, fill = chain), alpha = .5)+
  facet_wrap(~Parameter)+
  theme_few()
```

## Preference

### Pref prior predictions

```{r prior preference congruent}
priorPrefConWebppl <- '

var prefData = dataFromR
var priorProbs = []

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var model  = function(){

  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))

      var priorProbs= [1-priorReg, 1-priorReg, priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})

      // observe(priorPredictions, row.correct)

     // display(JSON.stringify(priorReg))

    }, prefData)

  return extend({pref_int: pref_int, pref_slope: pref_slope})
}
'
```

```{r prior preference slope}
priorPrefInconWebppl <- '

var prefData = dataFromR
var priorProbs = []

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var model  = function(){

  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))

      var priorProbs= [priorReg, priorReg, 1-priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})

      // observe(priorPredictions, row.correct)

     // display(JSON.stringify(priorReg))

    }, prefData)

  return extend({pref_int: pref_int, pref_slope: pref_slope})
}
'
```

```{r pref prior pred}

# congruent condition

# pref_prior_con <- readRDS("../saves/pref_prior_con.rds")

pref_prior_con<- webppl(
  program_code = paste(rsaUtils, rsaModel, priorPrefConWebppl , sep='\n'),
  data = pref_data%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  inference_opts = list(method = "forward", samples = 1000, verbose = T)
)

 # saveRDS(pref_prior_con, "../saves/pref_prior_con.rds")

# incongruent condition

#pref_prior_incon <- readRDS("../saves/pref_prior_incon.rds")

pref_prior_incon<- webppl(
  program_code = paste(rsaUtils, rsaModel, priorPrefInconWebppl , sep='\n'),
  data = pref_data%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  inference_opts = list(method = "forward", samples = 1000, verbose = T)
)

 #saveRDS(pref_prior_incon, "../saves/pref_prior_incon.rds")

```

```{r}
# congruent condition
prefPriorPredCon <- pref_prior_con%>%
  spread(Parameter, value)

pref_prior_con <- pref_prior_con%>%
  mutate(chain = factor(Chain),
         alignment = "congruent")

x_plot <- seq(0, 2, by = 0.1)

model_predictions <- sapply(1:length(prefPriorPredCon$pref_int), function(idx) {
            plogis(prefPriorPredCon$pref_int[idx] + prefPriorPredCon$pref_slope[idx] * x_plot)
        })

colnames(model_predictions) <- 1:length(prefPriorPredCon$pref_int)
plot_pref_prior_con <- as.data.frame(cbind(x_plot, model_predictions))
plot_pref_prior_con <- melt(plot_pref_prior_con, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")

plot_prior_con_mean <- plot_pref_prior_con%>%
  group_by(x_plot)%>%
  summarise(y_plot = mean(y_plot))

# incongruent condition

prefPriorPredIncon <- pref_prior_incon%>%
  spread(Parameter, value)

pref_prior_incon <- pref_prior_incon%>%
  mutate(chain = factor(Chain),
         alignment = "incongruent")

model_predictions <- sapply(1:length(prefPriorPredIncon$pref_int), function(idx) {
            plogis(prefPriorPredIncon$pref_int[idx] + prefPriorPredIncon$pref_slope[idx] * x_plot)
        })

colnames(model_predictions) <- 1:length(prefPriorPredIncon$pref_int)
plot_pref_prior_incon <- as.data.frame(cbind(x_plot, model_predictions))
plot_pref_prior_incon <- melt(plot_pref_prior_incon, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")

# joining datasets

plot_pref_prior <- bind_rows(
  plot_pref_prior_con %>% mutate(alignment = "congruent"),
  plot_pref_prior_incon %>% mutate(alignment = "incongruent")
)

plot_prior_mean <- plot_pref_prior%>%
  group_by(alignment,x_plot)%>%
  summarise(mean = mean(y_plot),
            ci_upper = hdi_upper(y_plot),
            ci_lower = hdi_lower(y_plot))

pref_prior <- bind_rows(
  pref_prior_con,
  pref_prior_incon
)

```

```{r plot prior pred}

ggplot(plot_pref_prior) + 
  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey",alpha = 0.2) +
  #geom_ribbon(data = plot_prior_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "red", alpha = 0.5) +
  geom_line(data = plot_prior_mean, aes(x_plot, mean), col = "black", size =1) +
  xlab("age") + ylab("p(y | x)") +
  facet_wrap(~alignment)+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
  theme_few()

```

```{r}
ggplot(data = pref_prior, aes(x = value, fill = chain)) +
  geom_density(alpha = 0.3)+
  facet_grid(Parameter~ alignment)+
  theme_few()
```

### Pref posterior predictions

```{r posterior preference congruent}
postPrefConWebppl <- '

var prefData = dataFromR
var priorProbs = []

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var model  = function(){

  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))

      var priorProbs= [1-priorReg, priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})

      observe(priorPredictions, row.correct)

     // display(JSON.stringify(priorReg))

    }, prefData)

  return extend({pref_int: pref_int, pref_slope: pref_slope})
}
'
```

```{r}
postPrefInconWebppl <- '

var prefData = dataFromR
var priorProbs = []

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var model  = function(){

  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})

    map(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))

      var priorProbs= [priorReg, priorReg, 1-priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})

      observe(priorPredictions, row.correct)

     // display(JSON.stringify(priorReg))

    }, prefData)

  return extend({pref_int: pref_int, pref_slope: pref_slope})
}
'
```

```{r pref post pred}

# Same Speaker
# congruent
#pref_post_con_same <- readRDS("../saves/pref_post_con_same.rds")

pref_post_con_same<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

saveRDS(pref_post_con_same, "../saves/pref_post_con_same.rds")

# Same Speaker
# incongruent
#pref_post_incon_same <- readRDS("../saves/pref_post_incon_same.rds")

pref_post_incon_same<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefInconWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

saveRDS(pref_post_incon_same, "../saves/pref_post_incon_same.rds")

# Different Speaker
# congruent
#pref_post_con_diff <- readRDS("../saves/pref_post_con_diff.rds")

pref_post_con_diff<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "different_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

 saveRDS(pref_post_con_diff, "../saves/pref_post_con_diff.rds")

# Different Speaker
# incongruent
#pref_post_incon_diff <- readRDS("../saves/pref_post_incon_diff.rds")

pref_post_incon_diff<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefInconWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "different_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

saveRDS(pref_post_incon_diff, "../saves/pref_post_incon_diff.rds")

```

```{r}
# Same Speaker
# congruent

prefPostPredConSame <- pref_post_con_same%>%
  spread(Parameter, value)

pref_post_con_same <- pref_post_con_same%>%
  mutate(chain = factor(Chain))%>%
  mutate(alignment = "congruent",
         condition = "same speaker")

x_plot <- seq(0, 2, by = 0.1)

post_predictions_con_same <- sapply(1:length(prefPostPredConSame$pref_int), function(idx) {
            plogis(prefPostPredConSame$pref_int[idx] + prefPostPredConSame$pref_slope[idx] * x_plot)
        })

colnames(post_predictions_con_same) <- 1:length(prefPostPredConSame$pref_int)
plot_post_data_con_same <- as.data.frame(cbind(x_plot, post_predictions_con_same))
plot_post_data_con_same <- melt(plot_post_data_con_same, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")%>%
  mutate(alignment = "congruent",
         condition = "same speaker")

# Same Speaker
# incongruent

prefPostPredInconSame <- pref_post_incon_same%>%
  spread(Parameter, value)

pref_post_incon_same <- pref_post_incon_same%>%
  mutate(chain = factor(Chain))%>%
  mutate(alignment = "incongruent",
         condition = "same speaker")

post_predictions_incon_same <- sapply(1:length(prefPostPredInconSame$pref_int), function(idx) {
            plogis(prefPostPredInconSame$pref_int[idx] + prefPostPredInconSame$pref_slope[idx] * x_plot)
        })

colnames(post_predictions_incon_same) <- 1:length(prefPostPredInconSame$pref_int)
plot_post_data_incon_same <- as.data.frame(cbind(x_plot, post_predictions_incon_same))
plot_post_data_incon_same <- melt(plot_post_data_incon_same, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")%>%
  mutate(alignment = "incongruent",
         condition = "same speaker")

# Different speaker
# congruent
prefPostPredConDiff <- pref_post_con_diff%>%
  spread(Parameter, value)

pref_post_con_diff <- pref_post_con_diff%>%
  mutate(chain = factor(Chain))%>%
  mutate(alignment = "congruent",
         condition = "different speaker")

post_predictions_con_diff <- sapply(1:length(prefPostPredConDiff$pref_int), function(idx) {
            plogis(prefPostPredConDiff$pref_int[idx] + prefPostPredConDiff$pref_slope[idx] * x_plot)
        })

colnames(post_predictions_con_diff) <- 1:length(prefPostPredConDiff$pref_int)
plot_post_data_con_diff <- as.data.frame(cbind(x_plot, post_predictions_con_diff))
plot_post_data_con_diff <- melt(plot_post_data_con_diff, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")%>%
  mutate(alignment = "congruent",
         condition = "different speaker")

# Different speaker
# incongruent
prefPostPredInconDiff <- pref_post_incon_diff%>%
  spread(Parameter, value)

pref_post_incon_diff <- pref_post_incon_diff%>%
  mutate(chain = factor(Chain))%>%
  mutate(alignment = "incongruent",
         condition = "different speaker")

post_predictions_incon_diff <- sapply(1:length(prefPostPredInconDiff$pref_int), function(idx) {
            plogis(prefPostPredInconDiff$pref_int[idx] + prefPostPredInconDiff$pref_slope[idx] * x_plot)
        })

colnames(post_predictions_incon_diff) <- 1:length(prefPostPredInconDiff$pref_int)
plot_post_data_incon_diff <- as.data.frame(cbind(x_plot, post_predictions_incon_diff))
plot_post_data_incon_diff <- melt(plot_post_data_incon_diff, id.vars = "x_plot", variable.name = "iteration", 
        value.name = "y_plot")%>%
  mutate(alignment = "incongruent",
         condition = "different speaker")

# combining datasets

pref_post <- bind_rows(
  pref_post_con_diff,
  pref_post_incon_diff,
  pref_post_con_same,
  pref_post_incon_same
)

plot_post_data <- bind_rows(
  plot_post_data_incon_same,
  plot_post_data_con_same,
  plot_post_data_incon_diff,
  plot_post_data_con_diff
)

plot_post_data_mean <- plot_post_data%>%
  group_by(alignment,condition,x_plot)%>%
  summarise(mean = mean(y_plot),
            ci_upper = hdi_upper(y_plot),
            ci_lower = hdi_lower(y_plot))
```

```{r}

ggplot(plot_post_data) + 
  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey", alpha = 0.2) + 
  geom_ribbon(data = plot_post_data_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
  geom_line(data = plot_post_data_mean, aes(x_plot, mean), col = "black") + 
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
  facet_grid(alignment~condition)+
  theme_few()

```

```{r}
ggplot(data = pref_post, aes(x = value, fill = chain)) +
  geom_density(alpha = 0.3)+
  facet_grid(Parameter ~ alignment*condition)+
  theme_few()
```

# Model Predictions

```{r}

pref_post_same<- webppl(
  program_code = paste(rsaUtils, rsaModel, postPrefWebppl , sep='\n'),
  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

```

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
sketch out full bda model

@@
 ```
+
+## MH sketching
+
+```{r}
+postPrefConWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = filter(dataFromR, {experiment: "preference"})
+var infData = filter(dataFromR, {experiment: "informativeness"})
+
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.1)
+
+var all_conditions = levels(prefData, "condition")
+
+var priorProbs = []
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  map(function(row){
+
+    var age = row.age_num
+
+    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+    var inf_priorProbs = [.5, .5, .5]
+
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+    inf_priorProbs, speakerOptimality)
+
+    observe(rsaPredictions, row.correct)
+
+    //display(rsaPredictions.score( row.correct))
+    //display(JSON.stringify(row.correct))
+    //display(JSON.stringify(rsaPredictions))
+
+  }, infData)
+
+  var pref_params = map(function(cndtn){
+    var conditionData = filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    map(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+     // display(JSON.stringify(priorReg))
+
+    }, conditionData)
+
+    return {pref_int, pref_slope, condition: cndtn}
+
+  }, all_conditions)
+
+  var diff_speaker_params = filter(pref_params, 
+        {condition: "different_speaker"})[0]
+
+  var same_speaker_params = filter(pref_params, 
+        {condition: "same_speaker"})[0]
+
+  var predictions_by_age = map(function(age_bin){
+
+    var speakerOptimality = so_int  + so_slope * age_bin
+
+    var diff_priorReg = logistic(diff_speaker_params.pref_int +
+            diff_speaker_params.pref_slope * age_bin)
+
+    var diff_priorProbs_congruent = [1-priorReg, 1-priorReg, priorReg]
+    var diff_priorProbs_incongruent = [priorReg, priorReg, 1-priorReg]
+
+  var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent, speakerOptimality))
+
+      ...
+
+    var same_priorReg = logistic(same_speaker_params.pref_int +
+            same_speaker_params.pref_slope * age_bin)
+
+    ...
+
+    return extend(diff_speaker_params, same_speaker_params, {
+      diff_priorReg,
+      same_priorReg,
+      speakerOptimality,
+      rsaPredictions_diff_cong,
+      rsaPredictions_diff_incong,
+      rsaPredictions_same_cong,
+      rsaPredictions_same_incong,
+      age_bin,
+      so_slope,
+      so_int
+    })
+
+  }, binned_age_range)
+
+  return predictions_by_age
+}
+'
+```
+
+```{r}
+postSoWebppl <- '
+
+var infData = dataFromR
+var priorProbs = [.5, .5, .5]
+
+var model  = function(){
+
+  return extend({so_int: so_int, so_slope: so_slope})
+}
+'
+```

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
move files

--- 2018-11-28 stats/kids/kids_model_predictions.Rmd
@@
 
-      var priorProbs= [1-priorReg, priorReg]
+      var priorProbs= [1-priorReg,1-priorReg, priorReg]
 
       var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
       return obj.shape == "circle" ? 1 : 0
@@
 
-pref_post_con_same<- webppl(
+pref_post_con_same2<- webppl(
   program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
@@
 
+# 2 vs object world
+
+```{r posterior preference congruent}
+postPrefConWebppl2 <- '
+
+var prefData = dataFromR
+var priorProbs = []
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+
+  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    map(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+     // display(JSON.stringify(priorReg))
+
+    }, prefData)
+
+  return extend({pref_int: pref_int, pref_slope: pref_slope})
+}
+'
+```
+
+```{r}
+
+# Same Speaker
+# congruent
+#pref_post_con_same <- readRDS("../saves/pref_post_con_same.rds")
+
+pref_post_con_same2<- webppl(
+  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl2 , sep='\n'),
+  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 3,
+  cores = 3,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+)
+
+prefPostPredConSame2 <- pref_post_con_same2%>%
+  spread(Parameter, value)
+
+pref_post_con_same2 <- pref_post_con_same2%>%
+  mutate(chain = factor(Chain))%>%
+  mutate(alignment = "congruent",
+         condition = "same speaker")
+
+x_plot <- seq(0, 2, by = 0.1)
+
+post_predictions_con_same2 <- sapply(1:length(prefPostPredConSame2$pref_int), function(idx) {
+            plogis(prefPostPredConSame2$pref_int[idx] + prefPostPredConSame2$pref_slope[idx] * x_plot)
+        })
+
+colnames(post_predictions_con_same2) <- 1:length(prefPostPredConSame2$pref_int)
+plot_post_data_con_same2 <- as.data.frame(cbind(x_plot, post_predictions_con_same2))
+plot_post_data_con_same2 <- melt(plot_post_data_con_same2, id.vars = "x_plot", variable.name = "iteration", 
+        value.name = "y_plot")%>%
+  mutate(alignment = "congruent",
+         condition = "same speaker",
+         world = "2 objects")
+
+x <- bind_rows(
+  plot_post_data_con_same2,
+  plot_post_data_con_same
+)
+
+x_mean <- x%>%
+  group_by(world,x_plot)%>%
+  summarise(mean = mean(y_plot),
+            ci_upper = hdi_upper(y_plot),
+            ci_lower = hdi_lower(y_plot))
+
+a <- prefPostPredConSame2%>%
+  summarise(mean_int = mean(pref_int),
+            mean_slope = mean(pref_slope))%>%
+  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
+  mutate(x = x_plot,
+         world = "2 objects")
+
+b <- prefPostPredConSame%>%
+  summarise(mean_int = mean(pref_int),
+            mean_slope = mean(pref_slope))%>%
+  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
+  mutate(x = x_plot,
+         world = "3 objects")
+
+c <- bind_rows(a,b)
+
+```
+
+```{r}
+
+ggplot(x) + 
+  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey", alpha = 0.2) + 
+  geom_ribbon(data = x_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
+  geom_line(data = x_mean, aes(x_plot, mean), col = "black") + 
+  geom_line(data = c, aes(x, y), col = "red") + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
+  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
+  facet_grid(~world)+
+  theme_few()
+
+```
+
 # Model Predictions

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
kids model predictions update

@@
 ```{r}
-
-pref_post_same<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefWebppl , sep='\n'),
-  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-```
-
-## MH sketching
-
-```{r}
-postPrefConWebppl <- '
+modelPredWebppl <- '
 
@@
 
-var priorProbs = []
+//var priorProbs = []
 
@@
     var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+
 var inf_priorProbs = [.5, .5, .5]
@@
 
-    //display(rsaPredictions.score( row.correct))
-    //display(JSON.stringify(row.correct))
-    //display(JSON.stringify(rsaPredictions))
-
   }, infData)
@@
   var pref_params = map(function(cndtn){
+
     var conditionData = filter(prefData, {condition: cndtn})
@@
 
-    var diff_priorProbs_congruent = [1-priorReg, 1-priorReg, priorReg]
-    var diff_priorProbs_incongruent = [priorReg, priorReg, 1-priorReg]
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
 
@@
 
-      ...
+  var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
 
@@
 
-    ...
-
-    return extend(diff_speaker_params, same_speaker_params, {
-      diff_priorReg,
-      same_priorReg,
-      speakerOptimality,
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+  var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+
+  var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
+
+    return extend(
+    //diff_speaker_params, same_speaker_params, 
+{
+     // diff_priorReg,
+    //  same_priorReg,
+    //  speakerOptimality,
       rsaPredictions_diff_cong,
@@
       age_bin,
-      so_slope,
-      so_int
+    //  so_slope,
+    //  so_int
     })
@@
 
-```{r}
-postSoWebppl <- '
-
-var infData = dataFromR
-var priorProbs = [.5, .5, .5]
-
-var model  = function(){
-
-  return extend({so_int: so_int, so_slope: so_slope})
-}
-'
-```
+```{r combined model predictions}
+model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+  data = pre_data, 
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 20, burn = 1, verbose = T)
+)
+
+```

### 2018-11-28 stats/kids/kids_model_predictions.Rmd
cache rsa and replace maps with foreach

@@
 
-var pragmaticListener = function(utterance, priorProbs, speakerOptimality){
+var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
 Infer({method: "enumerate", model: function(){
@@
 }})
-}
-
-var speaker = function(obj, lexiconName, priorProbs, speakerOptimality){
+})
+
+var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
 Infer({method: "enumerate", model: function(){
@@
 }})
-}
-
-var literalListener = function(utterance, priorProbs){
+})
+
+var literalListener = cache(function(utterance, priorProbs){
 Infer({method: "enumerate", model: function(){
@@
 }})
-}
+})
 
@@
 
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
 //var priorProbs = []
@@
 
-  map(function(row){
+  foreach(function(row){
 
@@
 
-    map(function(row){
+    foreach(function(row){
 

### 2019-01-09 papers/cogsci2019/cogsci2019.Rmd
first draft CogSci paper

---
title: "Integrating Common Ground and Informativeness in Pragmatic Word Learning"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
   \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
    \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "Pragmatic inferences are an integral part of language comprehension and learning. To recover the intended meaning of an utterance, listeners need to balance and integrate different sources in information. In a series of experiments, we studied how listeners integrate general expectations about speakers with expectations that are specific to the interactional history with  a particular speaker. We used a Bayesian cognitive model to formalize the integration process. In Experiment 1 and 2 we replicated findings showing that listeners make inferences based on general and speaker specific expectations. Using the empirical measurements from these experiments, we generated model predictions about how they should be integrated. We tested these predictions in Experiment 3, which combined both expectations in a single design. Experiment 4 replicated and extended Experiment 3 to a broader set of conditions. Across both experiments, listeners based their inferences on both types of expectations. Overall, model predictions and data were highly correlated. Predictions from the model incorporating both types of information described listeners’ behavior better compared to alternative models based on only one type of information. This research shows that listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian cognitive models. Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension."

keywords:
    "Pragmatics; Word learning; Common ground; Bayesian models"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
library(ggpubr)
library(lme4)
library(broom)
library(exactRankTests)
```

```{r}
# data ex 1 and ex 2
d1 <- bind_rows(read_csv(file="../../stats/data/novel.data.csv"),
               read_csv(file="../../stats/data/pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         control = ifelse(change == "true", "true" , "false"))

d2 <- read_csv(file="../../stats/data/inf.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

dex12 <- bind_rows(d1,d2) %>%
  filter(trial_type == "test")%>%
  mutate(control= relevel(factor(control), ref = "true"),
         choiceAgent = ifelse( control == "false", agent, altAgent)) # re-code agent for preference and novelty

# data ex 3
d3 <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
               read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

# check if someone did both experiments
# yes, two people
x <- d3 %>%
  filter(trial_type == "train")%>%
  group_by(id)%>%
  summarise(n = length(correct_inf)) %>%
  filter(n > 2)

# exclude those who did both experiments
dex3 <- d3 %>%
  filter(!id %in% x$id) %>%
  mutate(Speaker = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Prior = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
         choiceAgent = ifelse (change == "same", agent, altAgent))%>%
  filter(trial_type == "test")

d4 <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
               read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
               read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
               read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
               read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
               ) %>%
  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))

x <- d4 %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(correct_inf = mean(correct_inf)) %>%
  filter(correct_inf == 0)

dex4 <- d4 %>%
  filter(!id %in% x$id)%>% 
  distinct(id, alltrial, .keep_all = TRUE) %>%
  filter(trial_type != "train") %>%
  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
         Experiment = ifelse(grepl("pref",experiment), "Preference", "Novelty"),
         Prior = ifelse(prior == "weak", "Weak", ifelse(prior == "medium", "Medium", "Strong"))
         )

# loading model comparisons and predictions

pred_ex3 <- readRDS(file = "../../stats/saves/model_predictions_ex3_1.rds")

pred_ex4 <- readRDS(file = "../../stats/saves/model_predictions_ex3_variable_priors.rds")

bf_ex3 <- readRDS(file = "../../stats/saves/ex3_bf.rds")

bf_ex4 <- readRDS(file = "../../stats/saves/ex4_bf.rds")

```

# Introduction

One of the most astonishing features of natural language is that it allows us to communicate precise meanings despite the fact that each utterance is inherently ambiguous. The conventional couplings between sounds (words) and objects constrain what a speaker may mean by an utterance. However, the intended meaning of the utterance is not reducible to the words that are contained in it. For example, the same utterance (“Look, there it is!”) could be intended to refer to very different things depending on whether someone is searching for their wallet or looking for the bus stop. It takes additional pragmatic inferences to recover the intended meaning [@levinson2000presumptive].

Pragmatic inferences rest on a set of expectations that interlocutors bring to the table when entering a communicative interaction. On the one hand, speakers and listeners have the general expectation that their partner communicates in an informative and relevant way [@sperber2001relevance]. Grice [-@grice1991studies] summarised this expectation via the cooperative principle: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the principle highlights a second type of expectation: interlocutors expect each other to produce and interpret utterances in light of the shared common ground between them [@clark1996using]. Common ground refers to bits of information that are assumed to be shared, either because they result from joint experience or were otherwise grounded [@bohn2018common]. The nature of the corresponding expectations vary with the individuals involved.

Both general and common ground expectations can support children’s word learning [@clark2009first; @tomasello2009constructing]. On the one hand, children have been found to learn novel words by assuming that the speaker is informative [@frank2014inferring]. That is, in the absence of any prior interaction with the speaker, children interpreted a novel word as referring to the most informative referent. On the other hand, children learn novel words by relying on common ground expectations [@akhtar1996role; @bohn2018common]. For example, when a speaker expressed preference for a particular object, children expect a novel word from the same speaker to refer to the previously preferred object [@saylor2009preschoolers].

But how are general and common ground expectations integrated with one another? Are pragmatic inferences strengthened additively when both support a particular interpretation? How are they weighed when they are in conflict? The rational speech act (RSA) framework [@frank2012predicting] offers a formal framework for this information integration problem. RSA models are characterized by their recursive structure in which speakers and listeners reason about each other’s interpretation of utterances in context. RSA models have been found to make accurate quantitative predictions about various forms of pragmatic language use and word learning [@goodman2016pragmatic]. However, a comprehensive treatment of how general and common ground expectations are integrated, is still missing.

Within RSA models, each agent in this recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference. A natural locus within these models for information integration is the tradeoff between the prior probability of a particular referent (the degree to which it is in common ground) and the likelihood of that referent given the current utterance (general pragmatic interpretation).

Here we investigate information integration in pragmatic reasoning by experimentally manipulating speaker specific and common ground information and testing how adult listeners integrate them in a word learning scenario. In Experiment 1 and 2, we replicate earlier findings with adults and children showing that listeners expect speakers to a) produce informative utterances (Experiment 1) and b) communicate about things that are relevant to common ground (Experiment 2). Based on these results, we derive model predictions about how these two components should be integrated. In Experiment 3, we test how listeners integrate expectations and compare model predictions to empirical data. Experiment 4 replicates and extends Experiment 3 by gradually varying the strength of common ground assumptions.

# Method

## General Design

Each experiment was implemented on a website (using JavaScript and HTML) to which participants were directed. Figure \ref{fig:design} provides a schematic overview of the setup and experimental procedures. The instructions informed participants that they will see a number of animal characters asking for novel toys. Participants’ task was to identify the toy a given animal is requesting. The basic layout involved two tables with toys on them, located left and right of a little hill, on which the animal was standing. For each animal, we recorded a set of utterances (one speaker per animal) that were used throughout the experiments to provide information and make requests. At test, toys were requested using the following utterance: “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”. Participants responded by clicking on one of the toys. Each experiment started with two training trials in which animals requested familiar objects (car and ball).

For all experiments, we pre-registered the sample size, experimental design and the statistical analysis. For Experiment 3 and 4, we also registered the model structure and predictions (see [https://osf.io/u7kxe](https://osf.io/u7kxe))

```{r design, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Schematic experimental procedure. In all conditions, at test (bottom), the speaker ambiguously requested an object using a non-word (e.g. “dax”). Participants clicked on the object they thought the speaker referred to. Informativeness (Experiment 1, left) translated to making one object less frequent in context. Common ground (Experiment 2, middle) was manipulated by making one object prefered by, or new to the speaker. Experiment 3 (right) combined manipulations. When expressing e.g. preference for an object on a table with two objects (panel 3 from top), the respective object was temporally enlarged. Condition shown here: preference - same speaker - incongruent."}
img <- png::readPNG("figs/method_figure.png")
grid::grid.raster(img)
```

# Experiment 1

## Participants, Design and Procedure

All participants were recruited from Amazon Mechanical Turk and had US IP addresses. We planned the sample size in each experiment to be 120 data points per cell. Experiment 1 had 40 participants.Informativeness was manipulated by making one object less frequent in context. In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Figure 1 in red). On each trial, the animal introduced themselves, turned towards the table with the two objects and made a request. If listeners expect speakers to produce informative utterances, they should select object B. This choice follows from the counterfactual inference that if the (informative) speaker would have wanted to request A, they would have turned to the table that only contained A. On the other hand, since B is only located on the table together with A, there was no alternative way to request B in a less ambiguous way. In the control condition, both tables contained two objects, one of which was randomly determined as the correct one. No inference was therefore licenced based on the animals turning. Each participant received three trials in each condition.

## Results and Discussion

```{r ex1-results}
ex1t <- dex12 %>%
  filter(condition == "informativeness")%>%
  group_by(control, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(control) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(control,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model
lm_ex1 <- glmer(correct ~ control +
              (control |id) + (control |agent), 
              data = dex12%>%filter(condition == "informativeness"), 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

Participants selected the less frequent object above chance in the test condition (t = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to the control condition (genreralized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker (animal).}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p*  `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`). This result replicates earlier work [@frank2014inferring].

```{r plotexp12, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3.4, fig.height=2, fig.cap = "Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig. 1). Transparent dots show data from individual particpants, solid dots represent condition means, error bars are 95 \\% CIs. Dashed line indicates performance expected by chance."}

p1 <- dex12 %>%
  filter(trial_type == "test") %>%
  mutate(control = ifelse(control == "true", "Control", "Test"),
         condition = factor(condition), 
         experiment = ifelse(condition == "informativeness", "1","2"))%>%
  group_by(experiment,condition ,control, id) %>%
  summarise(correct = mean(correct))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

 ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = .7)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Expected Choice")+
  facet_wrap( ~ condition, labeller = as_labeller(c(`preference`="Exp. 2 - Pref.", `novelty`="Exp. 2 - Nov.", `informativeness`="Exp. 1 - Inf.")))+
  theme_few(base_size = 10) + 
  ylim(-0.05,1.05)+
  guides(alpha = F,size =F, col = F)+
  scale_color_manual(name = "Condition",
                     breaks=c("Test","Control"),
                     values= c("#839496","black"))

```

# Experiment 2

We manipulated common ground expectations based on two ways which have succesfully been used in developmental studies [e.g. @akhtar1996role; @saylor2009preschoolers]. Speakers either expressed preference for one object or one object was new to the speaker.

## Participants, Design and Procedure

There were 80 participants, 40 per manipulation. In the preference manipulation, each table had a different object. In the beginning, the animal appeared on the hill and introduced themselves. Next, they turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude. Then, the animal disappeared. After a short period of time, either the same or a different animal appeared and requested an object while facing straight (see Figure 1 in blue). If participants took into account the information they gained about the speaker, they should select the previously preferred object if the returning animal was the same. If a different animal returned, they should choose randomly between objects.

In the novelty manipulation, one table was initially empty while there was an object on the other one (see Figure \ref{fig:design}). The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”). Next, the animal quickly disappeared. The same animal re-appeared and the sequence above was repeated. When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away. Like in preference, we now manipulated if the same animal or a different one would return. In case of the same animal returning, listeners could infer the referent of the subsequent request by considering that one object was new to the speaker and therefore more likely to be of interest to them. No such inference was licensed when a different animal returned because both objects were equally new to them.

## Results and Discussion

```{r ex2-results-pref}
ex2tpref <- dex12 %>%
  filter(condition == "preference")%>%
  group_by(control, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(control) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(control,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model (maximally converging)
lm_ex2pref <- glmer(correct ~ control +
              (1|id) + (control |choiceAgent), 
              data = dex12%>%filter(condition == "preference"), 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

```{r ex2-results-nov}
ex2tnov <- dex12 %>%
  filter(condition == "novelty")%>%
  group_by(control, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(control) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(control,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model
lm_ex2nov <- glmer(correct ~ control +
              (1|id) + (control |choiceAgent), 
              data = dex12%>%filter(condition == "novelty"), 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

Participants selected the preferred object above chance when the same animal returned (t = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`). Thus, listeners inferred the referent of the utterance by considering previous interactions with the speaker. Interestingly, participants to some extend transferred preference from one animal to the other and also selected the preferred object above chance when a different animal returned (t = `r ex2tpref%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "true")%>%pull(p_value)`). In sum, this study shows that adults make comparable infernces to children [@saylor2009preschoolers].

The novel object was selected above chance when the same animal returned (t = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}). Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(p.value)`). Thus, like children [@akhtar1996role], participants used their prior information about the speaker to resolve ambiguity in their utterance.

# Experiment 3

```{r plotexp3, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Results from Experiment 3. Dashed line indicates performance expected by chance. Plotting conventions are the same as in Figure 2. All conditions in which CIs do not overlap with chance line are also statistically different from chance based on two-tailed Wilcoxon tests."}

p3 <- dex3 %>%
  group_by(Prior,Speaker ,Alignment, id) %>%
  summarise(correct = mean(correct_inf))

p4 <- p3 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  #geom_rect(data = p4, aes(fill = NA), color = "#859900", size = 2.5, alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
  geom_jitter(data = p3, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
  geom_pointrange(data = p4, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .7)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( ~ Prior + Speaker) +
  theme_few(base_size = 10) + 
  ylim(-0.05,1.05)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_fill_manual(name="Condition",
                     breaks=c("1","2","3"),
                     values= c("#859900","#859900","#859900"))

```

Experiment 1 and 2 separately measured two types of pragmatic inferences. The first was based on the expectation that speakers produce informative utterances. The second was based on the expectations that speakers produce their utterances in light of the ongoing social interaction (common ground). In Experiment 3, we combined both types of expectations to study how listeners integrate them.

## Participants, Design and Procedure

A total of 121 individuals participated in the experiment. The test situation was the same as in the test condition in Experiment 1: One table with object of type A and the other with an object of type A and B. Again, the animal always turned to the table with two objects and ambiguously requested an object. In Experiment 1, the listener had no prior information about each object. In Experiment 3, however, we manipulated common ground expectations in the same way as in Experiment 2. For example, the animal would turn to the table with one object and express their dis-liking of object A, then they would turn to the other table and express their liking of object B (not using labels). Next, after quickly disappearing, the animal would reappear, turn to the table with two objects and make a request.

For each version of Experiment 2, there were 4 conditions in Experiment 3. If the preferred/novel object was the less frequent one (object B), the two expectations were congruent. If the preferred/novel object was the more frequent one (object A), expectations were incongruent. For each type of expectation alignment, we varied if the same or a different animal returned. Participants either completed the preference or novelty version and received two test trials in each of the four conditions. Before discussing the empirical results, we briefly discuss the cognitive model we used to predict expectation integration.

## Model Predictions

To derive predictions, we used a probabilistic RSA model that simulates a pragmatic listener reasoning about a cooperative speaker who is trying to refer to an object [@frank2012predicting]. The speaker chooses how to refer to the object by reasoning about a naive listener who does not know the labels for the object [@frank2014inferring]. Mathematically, the probability that the listener chooses a referent given an utterance is defined as follows:  
$$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$
Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance to refer to a specific referent. It is defined as the surprisal of an utterance given the referent for a naive listener, who interprets utterances in a literal way:

$$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$

The numerical strength of the expression above depends on $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances.

The term $P_S(r_s)$ denotes the prior probability that a speaker will refer to a given referent. This probability represents the listeners expectations about the speaker depending on the manipulation (preference or novelty) and the identity of the speaker (same or different speaker).

In our model, we used the results from Experiment 1 and 2 to specify $\alpha$ as well as $P_S(r_s)$. The former was set to yield the proportion measured in Experiment 1 in a model with uniform priors. The prior probability for each object was the proportion with which this object was chosen in Experiment 2\footnote{Proportions were measured when participants chose between two objects. However, in Experiment 3, three objects were involved. For each object we used the proportion measured in Experiment 2 as the prior probability.This approached spread out the absolute probability mass for each object but conserved the relative relation between objects.}. Based on these parameter settings, we predicted the proportion with which listeners will choose the less frequent object in each unique combination of alignment and speaker identity separately for each prior manipulation (eight conditions total, see Figure \ref{fig:plotexp3}). We compared the fit of this pragmatic model to two alternative models using Bayes Factors (BF). The first alternative model ignored the speaker specific expectations (flat prior model) while the second ignored the informativeness inference (prior only model). To capture the idea that behavioral data is to some degree noisy, all models included a noise parameter, which reflects that, with a certain probability, participants respond randomly instead of in line with the intended manipulation on a given trial. Noise parameters are estimated based on the data.

## Results and Discussion

```{r plotmodelcomp, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4. (C) Data for strong prior manipualtion in Experiment 3 and 4. Error bars = 95 \\%  HDIs."}

pc1 <- pred_ex3%>%
  filter(Model == "Noisy RSA Model")%>%
  mutate(Prior = "Strong")

c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 10) + 
  guides(col = F)+
  scale_colour_viridis_d()

pc2 <- pred_ex4%>%
  filter(Model == "Noisy RSA Model")

c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 10) + 
  scale_colour_manual(values = rev(viridis::viridis(3)))

pc3 <- data.frame(
    ex3 = pc1%>%pull(Data),
    ex3_ci_l = pc1%>%pull(Data_ci_low),
    ex3_ci_u = pc1%>%pull(Data_ci_up),
    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
    Prior = "Strong")

c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Data Experiment 3")+
  ylab("Data Experiment 4")+
  theme_few(base_size = 10)+ 
  scale_color_viridis_d()

ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T , labels = c("A","B","C"), vjust = 1)

```

```{r ex3_tab, results="asis"}
#comaprison to chance
ex3_tab <- dex3 %>%  
  filter(trial_type == "test") %>%
  group_by(Speaker ,Prior,Alignment, id) %>%
  summarise(correct_inf = mean(correct_inf)) %>%
  summarize(correct_inf = list(correct_inf)) %>%
  group_by(Speaker ,Prior,Alignment) %>%
  mutate(M = mean(unlist(correct_inf)),
         W = wilcox.exact(unlist(correct_inf), mu = 0.5)$statistic,
         p = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
  select(Prior,Alignment, Speaker, M , W,p)%>%
  mutate(M = round(M,2),
         p = ifelse(p<.001,"< .001",as.character(substr(round(p,3),2,5),sep=" ")))

#tab1 <- xtable::xtable(ex3_tab, caption = "Proportion of choice of less frequent object for each unique condition in Experiment 3.", label = "bubub")

#print(tab1, type="latex", comment = F, table.placement = "H")

```

```{r ex3_results, cache=T}
# model 
lm_ex3 <- glmer(correct_inf ~ Prior*Speaker*Alignment + (Speaker+Alignment|id) + (Speaker+Alignment|choiceAgent), 
              data = dex3, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex3)

lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

```{r model_comp}

model_comp <- cor.test(
  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(mean),
  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(Data)
  )

model_comp_r <- tidy(model_comp) %>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         estimate = round(estimate,2))

```

Results are discussed in the form of the proportion with which listeners chose the less frequent object. For a comparison to chance within each unique condition see Figure \ref{fig:plotexp3}. Both alignment and speaker identity influenced participants’ responses  (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`). Figure \ref{fig:plotmodelcomp} shows the mean response in each unique condition compared to the model. Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`). Model fit was better in the model taking into account both types of expectations compared to the flat prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs. No prior") %>%pull(BayesFactor),digits = 2)`) or prior only model (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs. Prior only") %>%pull(BayesFactor), digits = 2)`).

Interestingly, like in Experiment 2, there was a transfer of preference in case of a speaker change. Participants were at chance in the preference - different speaker - incongruent condition (see Figure \ref{fig:plotexp3}). If preference would have been specific to a particular individual, participants should have selected the less frequent object above chance (as they did in the corresponding condition with the novelty manipulation).

# Experiment 4

In Experiment 4, we replicated and extended Experiment 3 by manipulating the strength of the common ground expectations. Our main goal was to investigate the scope of our cognitive model and we therefore limit the description of the methods and the discussion of the results to the aspects relevant to the comparison between model predictions and data.

## Participants, Design and Procedure

This experiment had 453 participants. The structure of the experiment was the same as in Experiment 3. For each common ground expectation (preference and novelty), we intended to have a strong, a medium and a weak manipulation. The strength of each manipulation was determined by the proportion with which participants chose the preferred / novel object given the manipulation. We succeeded in this for novelty. For preference we did not find a manipulation that yielded only a weak preference.

The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication. For novelty, in the medium manipulation, the animal turned to each table only once before the test. In the weak manipulation, the animal only turned to the table with an object before the test. In the medium manipulation for preference, the animal only expressed liking and did so in a more subtle way (saying only: “Oh, wow”). Participants were assigned to one level of common ground expectation and completed two test trials in each of the four conditions.

Model predictions were obtained in the same way as in Experiment 3. The likelihood term of the model was identical. For the each level of common ground expectation, we measured the proportion with which participants chose the preferred / novel object in a separate experiment. Due to space limitations, we do not discuss them in any more detail here. Like in Experiment 3, the results of these experiments were used to specify the prior distribution in the model.

## Results and Discussion

```{r ex4_results}
repl <- cor.test(
  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(Data),
  pred_ex4%>%filter(Model == "Noisy RSA Model", Prior == "Strong")%>%pull(Data)
  )

repl_r <- tidy(repl) %>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         estimate = round(estimate,2))

ex4_comp <- cor.test(
  pred_ex4%>%filter(Model == "Noisy RSA Model")%>%pull(mean),
  pred_ex4%>%filter(Model == "Noisy RSA Model")%>%pull(Data)
  )

ex4_comp_r <- tidy(ex4_comp) %>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         estimate = round(estimate,2))

```

As noted above, the strong prior manipulation was a direct replication of Experiment 3. Results from the two rounds of data collection were highly correlated (r = `r repl_r$estimate`, *p* `r repl_r$p.value`, see Figure \ref{fig:plotmodelcomp}C). Across levels of prior manipulation, the data from Experiment 4 were highly correlated to the corresponding model predictions (r = `r ex4_comp_r$estimate`, *p* `r ex4_comp_r$p.value`, see Figure \ref{fig:plotmodelcomp}B). Again, the pragmatic model provided a better fit compared to the flat prior (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs. No prior") %>%pull(BayesFactor),digits = 2)` ) or prior only model (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs. Prior only") %>%pull(BayesFactor), digits = 2)`).

# Discussion

Language use and learning requires balancing different types of expectations about one’s interlocutor. Here we used a Bayesian cognitive model to predict this integration process. Experiment 1 and 2 replicated earlier studies showing that adult listeners expect speakers to produce utterances in an informative way as well as in light of common ground. Next, we combined the procedures from the first two experiments to study how listeners would integrate them. We used the results from Experiment 1 and 2 to specify the model parameters that represented the two types of expectations and make parameter-free predictions about new behavior. Experiments 3 and 4 showed that both types of expectations influenced listeners inferences. In general, listener behavior accurately described by our model, suggesting that – at least in population aggregate – listeners trade off flexibly between speaker specific and general pragmatic expectations.

Notably, Experiment 3 also included situations in which the two expectations were in conflict. For example, in some trials the animal expressed preference for object A, which was also the more frequent object. In these situations, participants chose the preferred object as the referent  (see also Figure \ref{fig:plotexp3}). A simple explanation for this pattern might be that common ground manipulations were simply “stronger” in that they produced higher rates of expected choice when presented on their own (see Figure \ref{fig:plotexp12}). However, in Experiment 4 we observed the same pattern in the medium manipulation for novelty (results not discussed above, see online repository for details) even though the manipulation alone yielded numerically weaker results compared to the general expectation in Experiment 1. In each case, the pattern in the data was  predicted by the model This illustrates the conditional nature of pragmatic inference: The informativeness of an utterance critically depends on the context, including common ground. If prior interactions already single out one object as the more likely referent, subsequent considerations of informativeness take place in light of this prior information and not independent of it.

In our model, we treated common ground expectations as equivalent to more basic manipulations of contextual salience [e.g. in @frank2012predicting] and did not explicitly model the social-cognitive processes that give rise to these expectations. The interaction around the object prior to the test event simply increased the probability that this particular speaker will refer to the object subsequently. The same change could be brought about if one of the objects would be made perceptually more salient, for example by making it flash. In future work, it would be interesting to explore ways to model common ground expectations explicitly as well as to contrast perceptual and interactional salience.

A logical next step will be to extend the work presented here to children. As outlined above, pragmatic reasoning is though to play an important role in how children learn new words. An ontogenetic study would also show to what extent the modelling approach taken here is suitable to address questions about development. Another fruitful future direction would be to experimentally manipulate expectations about speaker informativeness. For example, if a speaker repeatedly behaves in an irrational way (e.g. labels dogs as cats), listeners might be less inclined to assume that utterances containing novel words are produced in an informative way.

This work integrates different perspectives on the study of pragmatic inference. Previous work focused either on general or speaker specific expectations. The methodological approach taken here illustrates how computational and experimental approaches can be used in conjunction to explicate theories of language use and learning.

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em}

# Acknowledgements

MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.

# References

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2019-01-09 papers/cogsci2019/cogsci2019.tex
first draft CogSci paper

--- 2019-01-09 papers/cogsci2019/cogsci2019.Rmd
@@
----
-title: "Integrating Common Ground and Informativeness in Pragmatic Word Learning"
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+% Template for Cogsci submission with R Markdown
 
-author-information: > 
+% Stuff changed from original Markdown PLOS Template
+\documentclass[10pt, letterpaper]{article}
+
+\usepackage{cogsci}
+\usepackage{pslatex}
+\usepackage{float}
+\usepackage{caption}
+
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% hyperref package, useful for hyperlinks
+\usepackage{hyperref}
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
+
+% Sweave(-like)
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
+\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
+\newenvironment{Schunk}{}{}
+\DefineVerbatimEnvironment{Code}{Verbatim}{}
+\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
+\newenvironment{CodeChunk}{}{}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+\usepackage{color}
+
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% % Text layout
+% \topmargin 0.0cm
+% \oddsidemargin 0.5cm
+% \evensidemargin 0.5cm
+% \textwidth 16cm
+% \textheight 21cm
+
+\title{Integrating Common Ground and Informativeness in Pragmatic Word Learning}
+
 \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
@@
 
-abstract: 
-    "Pragmatic inferences are an integral part of language comprehension and learning.
-To recover the intended meaning of an utterance, listeners need to balance and integrate different sources in information.
-In a series of experiments, we studied how listeners integrate general expectations about speakers with expectations that are specific to the interactional history with  a particular speaker.
-We used a Bayesian cognitive model to formalize the integration process.
-In Experiment 1 and 2 we replicated findings showing that listeners make inferences based on general and speaker specific expectations.
-Using the empirical measurements from these experiments, we generated model predictions about how they should be integrated.
-We tested these predictions in Experiment 3, which combined both expectations in a single design.
-Experiment 4 replicated and extended Experiment 3 to a broader set of conditions.
-Across both experiments, listeners based their inferences on both types of expectations.
-Overall, model predictions and data were highly correlated.
-Predictions from the model incorporating both types of information described listeners’ behavior better compared to alternative models based on only one type of information.
-This research shows that listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian cognitive models.
-Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension."
+\begin{document}
 
-keywords:
-    "Pragmatics; Word learning; Common ground; Bayesian models"
+\maketitle
 
-output: cogsci2016::cogsci_paper
----
+\begin{abstract}
+Pragmatic inferences are an integral part of language comprehension and
+learning. To recover the intended meaning of an utterance, listeners
+need to balance and integrate different sources in information. In a
+series of experiments, we studied how listeners integrate general
+expectations about speakers with expectations that are specific to the
+interactional history with a particular speaker. We used a Bayesian
+cognitive model to formalize the integration process. In Experiment 1
+and 2 we replicated findings showing that listeners make inferences
+based on general and speaker specific expectations. Using the empirical
+measurements from these experiments, we generated model predictions
+about how they should be integrated. We tested these predictions in
+Experiment 3, which combined both expectations in a single design.
+Experiment 4 replicated and extended Experiment 3 to a broader set of
+conditions. Across both experiments, listeners based their inferences on
+both types of expectations. Overall, model predictions and data were
+highly correlated. Predictions from the model incorporating both types
+of information described listeners' behavior better compared to
+alternative models based on only one type of information. This research
+shows that listeners flexibly integrate different forms of social
+expectations across a range of contexts, a process which can be
+described using Bayesian cognitive models. Our approach highlights how
+experiments and computational models can be used in conjunction to
+inform theories about language use and comprehension.
 
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
-```
+\textbf{Keywords:}
+Pragmatics; Word learning; Common ground; Bayesian models
+\end{abstract}
 
-```{r, libraries}
-library(png)
-library(grid)
-library(ggplot2)
-library(xtable)
-library(tidyverse)
-library(knitr)
-library(ggthemes)
-library(langcog)
-library(rwebppl)
-library(matrixStats)
-library(coda)
-library(ggpubr)
-library(lme4)
-library(broom)
-library(exactRankTests)
-```
+\section{Introduction}\label{introduction}
 
-```{r}
-# data ex 1 and ex 2
-d1 <- bind_rows(read_csv(file="../../stats/data/novel.data.csv"),
-               read_csv(file="../../stats/data/pref.data.csv")) %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         control = ifelse(change == "true", "true" , "false"))
+One of the most astonishing features of natural language is that it
+allows us to communicate precise meanings despite the fact that each
+utterance is inherently ambiguous. The conventional couplings between
+sounds (words) and objects constrain what a speaker may mean by an
+utterance. However, the intended meaning of the utterance is not
+reducible to the words that are contained in it. For example, the same
+utterance (``Look, there it is!'') could be intended to refer to very
+different things depending on whether someone is searching for their
+wallet or looking for the bus stop. It takes additional pragmatic
+inferences to recover the intended meaning (Levinson, 2000).
 
-d2 <- read_csv(file="../../stats/data/inf.data.csv") %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+Pragmatic inferences rest on a set of expectations that interlocutors
+bring to the table when entering a communicative interaction. On the one
+hand, speakers and listeners have the general expectation that their
+partner communicates in an informative and relevant way (Sperber \&
+Wilson, 2001). Grice (1991) summarised this expectation via the
+cooperative principle: ``Make your contribution such as is required, at
+the stage at which it occurs, by the accepted purpose or direction of
+the talk exchange in which you are engaged.'' Importantly, the second
+half of the principle highlights a second type of expectation:
+interlocutors expect each other to produce and interpret utterances in
+light of the shared common ground between them (H. H. Clark, 1996).
+Common ground refers to bits of information that are assumed to be
+shared, either because they result from joint experience or were
+otherwise grounded (Bohn \& Koymen, 2018). The nature of the
+corresponding expectations vary with the individuals involved.
 
-dex12 <- bind_rows(d1,d2) %>%
-  filter(trial_type == "test")%>%
-  mutate(control= relevel(factor(control), ref = "true"),
-         choiceAgent = ifelse( control == "false", agent, altAgent)) # re-code agent for preference and novelty
+Both general and common ground expectations can support children's word
+learning (E. V. Clark, 2009; Tomasello, 2009). On the one hand, children
+have been found to learn novel words by assuming that the speaker is
+informative (Frank \& Goodman, 2014). That is, in the absence of any
+prior interaction with the speaker, children interpreted a novel word as
+referring to the most informative referent. On the other hand, children
+learn novel words by relying on common ground expectations (Akhtar,
+Carpenter, \& Tomasello, 1996; Bohn \& Koymen, 2018). For example, when
+a speaker expressed preference for a particular object, children expect
+a novel word from the same speaker to refer to the previously preferred
+object (Saylor, Sabbagh, Fortuna, \& Troseth, 2009).
 
-# data ex 3
-d3 <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
-               read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+But how are general and common ground expectations integrated with one
+another? Are pragmatic inferences strengthened additively when both
+support a particular interpretation? How are they weighed when they are
+in conflict? The rational speech act (RSA) framework (Frank \& Goodman,
+2012) offers a formal framework for this information integration
+problem. RSA models are characterized by their recursive structure in
+which speakers and listeners reason about each other's interpretation of
+utterances in context. RSA models have been found to make accurate
+quantitative predictions about various forms of pragmatic language use
+and word learning (Goodman \& Frank, 2016). However, a comprehensive
+treatment of how general and common ground expectations are integrated,
+is still missing.
 
-# check if someone did both experiments
-# yes, two people
-x <- d3 %>%
-  filter(trial_type == "train")%>%
-  group_by(id)%>%
-  summarise(n = length(correct_inf)) %>%
-  filter(n > 2)
+Within RSA models, each agent in this recursion is modeled as a Bayesian
+reasoner; thus, information integration is treated as a process of
+probabilistic inference. A natural locus within these models for
+information integration is the tradeoff between the prior probability of
+a particular referent (the degree to which it is in common ground) and
+the likelihood of that referent given the current utterance (general
+pragmatic interpretation).
 
-# exclude those who did both experiments
-dex3 <- d3 %>%
-  filter(!id %in% x$id) %>%
-  mutate(Speaker = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Prior = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
-         choiceAgent = ifelse (change == "same", agent, altAgent))%>%
-  filter(trial_type == "test")
+Here we investigate information integration in pragmatic reasoning by
+experimentally manipulating speaker specific and common ground
+information and testing how adult listeners integrate them in a word
+learning scenario. In Experiment 1 and 2, we replicate earlier findings
+with adults and children showing that listeners expect speakers to a)
+produce informative utterances (Experiment 1) and b) communicate about
+things that are relevant to common ground (Experiment 2). Based on these
+results, we derive model predictions about how these two components
+should be integrated. In Experiment 3, we test how listeners integrate
+expectations and compare model predictions to empirical data. Experiment
+4 replicates and extends Experiment 3 by gradually varying the strength
+of common ground assumptions.
 
-d4 <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
-               ) %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+\section{Method}\label{method}
 
-x <- d4 %>%
-  filter(trial_type == "train") %>%
-  group_by(id)%>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  filter(correct_inf == 0)
+\subsection{General Design}\label{general-design}
 
-dex4 <- d4 %>%
-  filter(!id %in% x$id)%>% 
-  distinct(id, alltrial, .keep_all = TRUE) %>%
-  filter(trial_type != "train") %>%
-  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Experiment = ifelse(grepl("pref",experiment), "Preference", "Novelty"),
-         Prior = ifelse(prior == "weak", "Weak", ifelse(prior == "medium", "Medium", "Strong"))
-         )
+Each experiment was implemented on a website (using JavaScript and HTML)
+to which participants were directed. Figure \ref{fig:design} provides a
+schematic overview of the setup and experimental procedures. The
+instructions informed participants that they will see a number of animal
+characters asking for novel toys. Participants' task was to identify the
+toy a given animal is requesting. The basic layout involved two tables
+with toys on them, located left and right of a little hill, on which the
+animal was standing. For each animal, we recorded a set of utterances
+(one speaker per animal) that were used throughout the experiments to
+provide information and make requests. At test, toys were requested
+using the following utterance: ``Oh cool, there is a {[}non-word{]} on
+the table, how neat, can you give me the {[}non-word{]}?''. Participants
+responded by clicking on one of the toys. Each experiment started with
+two training trials in which animals requested familiar objects (car and
+ball).
 
-# loading model comparisons and predictions
+For all experiments, we pre-registered the sample size, experimental
+design and the statistical analysis. For Experiment 3 and 4, we also
+registered the model structure and predictions (see
+\url{https://osf.io/u7kxe})
 
-pred_ex3 <- readRDS(file = "../../stats/saves/model_predictions_ex3_1.rds")
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-pred_ex4 <- readRDS(file = "../../stats/saves/model_predictions_ex3_variable_priors.rds")
+{\centering \includegraphics{figs/design-1}
 
-bf_ex3 <- readRDS(file = "../../stats/saves/ex3_bf.rds")
+}
 
-bf_ex4 <- readRDS(file = "../../stats/saves/ex4_bf.rds")
-
-```
-
-# Introduction
-
-One of the most astonishing features of natural language is that it allows us to communicate precise meanings despite the fact that each utterance is inherently ambiguous.
-The conventional couplings between sounds (words) and objects constrain what a speaker may mean by an utterance.
-However, the intended meaning of the utterance is not reducible to the words that are contained in it.
-For example, the same utterance (“Look, there it is!”) could be intended to refer to very different things depending on whether someone is searching for their wallet or looking for the bus stop.
-It takes additional pragmatic inferences to recover the intended meaning [@levinson2000presumptive].
-
-Pragmatic inferences rest on a set of expectations that interlocutors bring to the table when entering a communicative interaction.
-On the one hand, speakers and listeners have the general expectation that their partner communicates in an informative and relevant way [@sperber2001relevance].
-Grice [-@grice1991studies] summarised this expectation via the cooperative principle: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the principle highlights a second type of expectation: interlocutors expect each other to produce and interpret utterances in light of the shared common ground between them [@clark1996using].
-Common ground refers to bits of information that are assumed to be shared, either because they result from joint experience or were otherwise grounded [@bohn2018common].
-The nature of the corresponding expectations vary with the individuals involved.
-
-Both general and common ground expectations can support children’s word learning [@clark2009first; @tomasello2009constructing].
-On the one hand, children have been found to learn novel words by assuming that the speaker is informative [@frank2014inferring].
-That is, in the absence of any prior interaction with the speaker, children interpreted a novel word as referring to the most informative referent.
-On the other hand, children learn novel words by relying on common ground expectations [@akhtar1996role; @bohn2018common].
-For example, when a speaker expressed preference for a particular object, children expect a novel word from the same speaker to refer to the previously preferred object [@saylor2009preschoolers].
-
-But how are general and common ground expectations integrated with one another?
-Are pragmatic inferences strengthened additively when both support a particular interpretation?
-How are they weighed when they are in conflict?
-The rational speech act (RSA) framework [@frank2012predicting] offers a formal framework for this information integration problem.
-RSA models are characterized by their recursive structure in which speakers and listeners reason about each other’s interpretation of utterances in context.
-RSA models have been found to make accurate quantitative predictions about various forms of pragmatic language use and word learning [@goodman2016pragmatic].
-However, a comprehensive treatment of how general and common ground expectations are integrated, is still missing.
-
-Within RSA models, each agent in this recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
-A natural locus within these models for information integration is the tradeoff between the prior probability of a particular referent (the degree to which it is in common ground) and the likelihood of that referent given the current utterance (general pragmatic interpretation).
-
-Here we investigate information integration in pragmatic reasoning by experimentally manipulating speaker specific and common ground information and testing how adult listeners integrate them in a word learning scenario.
-In Experiment 1 and 2, we replicate earlier findings with adults and children showing that listeners expect speakers to a) produce informative utterances (Experiment 1) and b) communicate about things that are relevant to common ground (Experiment 2).
-Based on these results, we derive model predictions about how these two components should be integrated.
-In Experiment 3, we test how listeners integrate expectations and compare model predictions to empirical data.
-Experiment 4 replicates and extends Experiment 3 by gradually varying the strength of common ground assumptions.
-
-# Method
-
-## General Design
-
-Each experiment was implemented on a website (using JavaScript and HTML) to which participants were directed.
-Figure \ref{fig:design} provides a schematic overview of the setup and experimental procedures.
-The instructions informed participants that they will see a number of animal characters asking for novel toys.
-Participants’ task was to identify the toy a given animal is requesting.
-The basic layout involved two tables with toys on them, located left and right of a little hill, on which the animal was standing.
-For each animal, we recorded a set of utterances (one speaker per animal) that were used throughout the experiments to provide information and make requests.
-At test, toys were requested using the following utterance: “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”.
-Participants responded by clicking on one of the toys.
-Each experiment started with two training trials in which animals requested familiar objects (car and ball).
-
-For all experiments, we pre-registered the sample size, experimental design and the statistical analysis.
-For Experiment 3 and 4, we also registered the model structure and predictions (see [https://osf.io/u7kxe](https://osf.io/u7kxe))
-
-```{r design, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Schematic experimental procedure.
+\caption[Schematic experimental procedure]{Schematic experimental procedure.
 In all conditions, at test (bottom), the speaker ambiguously requested an object using a non-word (e.g.
@@
 preference for an object on a table with two objects (panel 3 from top), the respective object was temporally enlarged.
-Condition shown here: preference - same speaker - incongruent."}
-img <- png::readPNG("figs/method_figure.png")
-grid::grid.raster(img)
-```
+Condition shown here: preference - same speaker - incongruent.}\label{fig:design}
+\end{figure*}
+\end{CodeChunk}
 
-# Experiment 1
+\section{Experiment 1}\label{experiment-1}
 
-## Participants, Design and Procedure
+\subsection{Participants, Design and
+Procedure}\label{participants-design-and-procedure}
 
-All participants were recruited from Amazon Mechanical Turk and had US IP addresses.
-We planned the sample size in each experiment to be 120 data points per cell.
-Experiment 1 had 40 participants.Informativeness was manipulated by making one object less frequent in context.
-In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Figure 1 in red).
-On each trial, the animal introduced themselves, turned towards the table with the two objects and made a request.
-If listeners expect speakers to produce informative utterances, they should select object B.
-This choice follows from the counterfactual inference that if the (informative) speaker would have wanted to request A, they would have turned to the table that only contained A.
-On the other hand, since B is only located on the table together with A, there was no alternative way to request B in a less ambiguous way.
-In the control condition, both tables contained two objects, one of which was randomly determined as the correct one.
-No inference was therefore licenced based on the animals turning.
-Each participant received three trials in each condition.
+All participants were recruited from Amazon Mechanical Turk and had US
+IP addresses. We planned the sample size in each experiment to be 120
+data points per cell. Experiment 1 had 40 participants.Informativeness
+was manipulated by making one object less frequent in context. In the
+test condition, one table contained one object of type A and the other
+table contained one object of type A and one of type B (see Figure 1 in
+red). On each trial, the animal introduced themselves, turned towards
+the table with the two objects and made a request. If listeners expect
+speakers to produce informative utterances, they should select object B.
+This choice follows from the counterfactual inference that if the
+(informative) speaker would have wanted to request A, they would have
+turned to the table that only contained A. On the other hand, since B is
+only located on the table together with A, there was no alternative way
+to request B in a less ambiguous way. In the control condition, both
+tables contained two objects, one of which was randomly determined as
+the correct one. No inference was therefore licenced based on the
+animals turning. Each participant received three trials in each
+condition.
 
-## Results and Discussion
+\subsection{Results and Discussion}\label{results-and-discussion}
 
-```{r ex1-results}
-ex1t <- dex12 %>%
-  filter(condition == "informativeness")%>%
-  group_by(control, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(control) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(control,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
+Participants selected the less frequent object above chance in the test
+condition (t = 5.51, \emph{p} \textless{} .001, see Figure
+\ref{fig:plotexp12}) and did so more often compared to the control
+condition (genreralized linear mixed model
+(GLMM\footnote{All models included random effects for subject and speaker (animal).}):\emph{\(\beta\)}
+= 1.49, se = 0.5 \emph{p} = .003). This result replicates earlier work
+(Frank \& Goodman, 2014).
 
-# model
-lm_ex1 <- glmer(correct ~ control +
-              (control |id) + (control |agent), 
-              data = dex12%>%filter(condition == "informativeness"), 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+\begin{CodeChunk}
+\begin{figure}[H]
 
-ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
+{\centering \includegraphics{figs/plotexp12-1}
 
-Participants selected the less frequent object above chance in the test condition (t = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to the control condition (genreralized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker (animal).}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p*  `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
-This result replicates earlier work [@frank2014inferring].
+}
 
-```{r plotexp12, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3.4, fig.height=2, fig.cap = "Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig.
+\caption[Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig]{Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig.
 1).
-Transparent dots show data from individual particpants, solid dots represent condition means, error bars are 95 \\% CIs.
-Dashed line indicates performance expected by chance."}
+Transparent dots show data from individual particpants, solid dots represent condition means, error bars are 95 \% CIs.
+Dashed line indicates performance expected by chance.}\label{fig:plotexp12}
+\end{figure}
+\end{CodeChunk}
 
-p1 <- dex12 %>%
-  filter(trial_type == "test") %>%
-  mutate(control = ifelse(control == "true", "Control", "Test"),
-         condition = factor(condition), 
-         experiment = ifelse(condition == "informativeness", "1","2"))%>%
-  group_by(experiment,condition ,control, id) %>%
-  summarise(correct = mean(correct))
+\section{Experiment 2}\label{experiment-2}
 
-p2 <- p1 %>%
-  multi_boot_standard(col = "correct")
+We manipulated common ground expectations based on two ways which have
+succesfully been used in developmental studies (e.g. Akhtar et al.,
+1996; Saylor et al., 2009). Speakers either expressed preference for one
+object or one object was new to the speaker.
 
- ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = .7)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Expected Choice")+
-  facet_wrap( ~ condition, labeller = as_labeller(c(`preference`="Exp. 2 - Pref.", `novelty`="Exp. 2 - Nov.", `informativeness`="Exp. 1 - Inf.")))+
-  theme_few(base_size = 10) + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F,size =F, col = F)+
-  scale_color_manual(name = "Condition",
-                     breaks=c("Test","Control"),
-                     values= c("#839496","black"))
+\subsection{Participants, Design and
+Procedure}\label{participants-design-and-procedure-1}
 
-```
+There were 80 participants, 40 per manipulation. In the preference
+manipulation, each table had a different object. In the beginning, the
+animal appeared on the hill and introduced themselves. Next, they turned
+to one of the tables and expressed either that they liked (``Oh wow, I
+really like that one'') or disliked (``Oh bleh, I really don't like that
+one'') the object before turning to the other side and expressing the
+respective other attitude. Then, the animal disappeared. After a short
+period of time, either the same or a different animal appeared and
+requested an object while facing straight (see Figure 1 in blue). If
+participants took into account the information they gained about the
+speaker, they should select the previously preferred object if the
+returning animal was the same. If a different animal returned, they
+should choose randomly between objects.
 
-# Experiment 2
+In the novelty manipulation, one table was initially empty while there
+was an object on the other one (see Figure \ref{fig:design}). The animal
+turned to one of the sides and commented either on the presence (``Aha,
+look at that'') or the absence of an object (``Hm, nothing there'').
+Next, the animal quickly disappeared. The same animal re-appeared and
+the sequence above was repeated. When the animal disappeared for the
+second time, a second object appeared on the empty table while the
+animal was away. Like in preference, we now manipulated if the same
+animal or a different one would return. In case of the same animal
+returning, listeners could infer the referent of the subsequent request
+by considering that one object was new to the speaker and therefore more
+likely to be of interest to them. No such inference was licensed when a
+different animal returned because both objects were equally new to them.
 
-We manipulated common ground expectations based on two ways which have succesfully been used in developmental studies [e.g.
-@akhtar1996role; @saylor2009preschoolers].
-Speakers either expressed preference for one object or one object was new to the speaker.
+\subsection{Results and Discussion}\label{results-and-discussion-1}
 
-## Participants, Design and Procedure
+Participants selected the preferred object above chance when the same
+animal returned (t = 29.14, \emph{p} \textless{} .001, see Figure
+\ref{fig:plotexp12}) and did so more often compared to trials in which a
+different animal returned (GLMM: \(\beta\) = 2.97, se = 0.7, \emph{p}
+\textless{} .001). Thus, listeners inferred the referent of the
+utterance by considering previous interactions with the speaker.
+Interestingly, participants to some extend transferred preference from
+one animal to the other and also selected the preferred object above
+chance when a different animal returned (t = 2.7, \emph{p} = .01). In
+sum, this study shows that adults make comparable infernces to children
+(Saylor et al., 2009).
 
-There were 80 participants, 40 per manipulation.
-In the preference manipulation, each table had a different object.
-In the beginning, the animal appeared on the hill and introduced themselves.
-Next, they turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
-Then, the animal disappeared.
-After a short period of time, either the same or a different animal appeared and requested an object while facing straight (see Figure 1 in blue).
-If participants took into account the information they gained about the speaker, they should select the previously preferred object if the returning animal was the same.
-If a different animal returned, they should choose randomly between objects.
+The novel object was selected above chance when the same animal returned
+(t = 6.77, \emph{p} \textless{} .001) but not when a different one
+appeared (t = 1.49, \emph{p} = .144, see Figure \ref{fig:plotexp12}).
+Furthermore, the two conditions differed in the expected direction
+(\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{} .001). Thus, like
+children (Akhtar et al., 1996), participants used their prior
+information about the speaker to resolve ambiguity in their utterance.
 
-In the novelty manipulation, one table was initially empty while there was an object on the other one (see Figure \ref{fig:design}).
-The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
-Next, the animal quickly disappeared.
-The same animal re-appeared and the sequence above was repeated.
-When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
-Like in preference, we now manipulated if the same animal or a different one would return.
-In case of the same animal returning, listeners could infer the referent of the subsequent request by considering that one object was new to the speaker and therefore more likely to be of interest to them.
-No such inference was licensed when a different animal returned because both objects were equally new to them.
+\section{Experiment 3}\label{experiment-3}
 
-## Results and Discussion
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-```{r ex2-results-pref}
-ex2tpref <- dex12 %>%
-  filter(condition == "preference")%>%
-  group_by(control, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(control) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(control,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
+{\centering \includegraphics{figs/plotexp3-1}
 
-# model (maximally converging)
-lm_ex2pref <- glmer(correct ~ control +
-              (1|id) + (control |choiceAgent), 
-              data = dex12%>%filter(condition == "preference"), 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+}
 
-ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
-
-```{r ex2-results-nov}
-ex2tnov <- dex12 %>%
-  filter(condition == "novelty")%>%
-  group_by(control, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(control) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(control,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
-# model
-lm_ex2nov <- glmer(correct ~ control +
-              (1|id) + (control |choiceAgent), 
-              data = dex12%>%filter(condition == "novelty"), 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
-
-Participants selected the preferred object above chance when the same animal returned (t = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
-Thus, listeners inferred the referent of the utterance by considering previous interactions with the speaker.
-Interestingly, participants to some extend transferred preference from one animal to the other and also selected the preferred object above chance when a different animal returned (t = `r ex2tpref%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "true")%>%pull(p_value)`).
-In sum, this study shows that adults make comparable infernces to children [@saylor2009preschoolers].
-
-The novel object was selected above chance when the same animal returned (t = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}).
-Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
-Thus, like children [@akhtar1996role], participants used their prior information about the speaker to resolve ambiguity in their utterance.
-
-# Experiment 3
-
-```{r plotexp3, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2.5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Results from Experiment 3.
+\caption[Results from Experiment 3]{Results from Experiment 3.
 Dashed line indicates performance expected by chance.
 Plotting conventions are the same as in Figure 2.
-All conditions in which CIs do not overlap with chance line are also statistically different from chance based on two-tailed Wilcoxon tests."}
+All conditions in which CIs do not overlap with chance line are also statistically different from chance based on two-tailed Wilcoxon tests.}\label{fig:plotexp3}
+\end{figure*}
+\end{CodeChunk}
 
-p3 <- dex3 %>%
-  group_by(Prior,Speaker ,Alignment, id) %>%
-  summarise(correct = mean(correct_inf))
+Experiment 1 and 2 separately measured two types of pragmatic
+inferences. The first was based on the expectation that speakers produce
+informative utterances. The second was based on the expectations that
+speakers produce their utterances in light of the ongoing social
+interaction (common ground). In Experiment 3, we combined both types of
+expectations to study how listeners integrate them.
 
-p4 <- p3 %>%
-  multi_boot_standard(col = "correct")
+\subsection{Participants, Design and
+Procedure}\label{participants-design-and-procedure-2}
 
-ggplot() +
-  #geom_rect(data = p4, aes(fill = NA), color = "#859900", size = 2.5, alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
-  geom_jitter(data = p3, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .7)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
-  facet_grid ( ~ Prior + Speaker) +
-  theme_few(base_size = 10) + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F, fill = F, col = F)+ 
-  scale_fill_manual(name="Condition",
-                     breaks=c("1","2","3"),
-                     values= c("#859900","#859900","#859900"))
+A total of 121 individuals participated in the experiment. The test
+situation was the same as in the test condition in Experiment 1: One
+table with object of type A and the other with an object of type A and
+B. Again, the animal always turned to the table with two objects and
+ambiguously requested an object. In Experiment 1, the listener had no
+prior information about each object. In Experiment 3, however, we
+manipulated common ground expectations in the same way as in Experiment
+2. For example, the animal would turn to the table with one object and
+express their dis-liking of object A, then they would turn to the other
+table and express their liking of object B (not using labels). Next,
+after quickly disappearing, the animal would reappear, turn to the table
+with two objects and make a request.
 
-```
+For each version of Experiment 2, there were 4 conditions in Experiment
+3. If the preferred/novel object was the less frequent one (object B),
+the two expectations were congruent. If the preferred/novel object was
+the more frequent one (object A), expectations were incongruent. For
+each type of expectation alignment, we varied if the same or a different
+animal returned. Participants either completed the preference or novelty
+version and received two test trials in each of the four conditions.
+Before discussing the empirical results, we briefly discuss the
+cognitive model we used to predict expectation integration.
 
-Experiment 1 and 2 separately measured two types of pragmatic inferences.
-The first was based on the expectation that speakers produce informative utterances.
-The second was based on the expectations that speakers produce their utterances in light of the ongoing social interaction (common ground).
-In Experiment 3, we combined both types of expectations to study how listeners integrate them.
+\subsection{Model Predictions}\label{model-predictions}
 
-## Participants, Design and Procedure
+To derive predictions, we used a probabilistic RSA model that simulates
+a pragmatic listener reasoning about a cooperative speaker who is trying
+to refer to an object (Frank \& Goodman, 2012). The speaker chooses how
+to refer to the object by reasoning about a naive listener who does not
+know the labels for the object (Frank \& Goodman, 2014). Mathematically,
+the probability that the listener chooses a referent given an utterance
+is defined as follows:\\
+\[P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)\] Here, \(P_S(u|r_s)\) is the
+likelihood that the speaker will use an utterance to refer to a specific
+referent. It is defined as the surprisal of an utterance given the
+referent for a naive listener, who interprets utterances in a literal
+way:
 
-A total of 121 individuals participated in the experiment.
-The test situation was the same as in the test condition in Experiment 1: One table with object of type A and the other with an object of type A and B.
-Again, the animal always turned to the table with two objects and ambiguously requested an object.
-In Experiment 1, the listener had no prior information about each object.
-In Experiment 3, however, we manipulated common ground expectations in the same way as in Experiment 2.
-For example, the animal would turn to the table with one object and express their dis-liking of object A, then they would turn to the other table and express their liking of object B (not using labels).
-Next, after quickly disappearing, the animal would reappear, turn to the table with two objects and make a request.
+\[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\]
 
-For each version of Experiment 2, there were 4 conditions in Experiment 3.
-If the preferred/novel object was the less frequent one (object B), the two expectations were congruent.
-If the preferred/novel object was the more frequent one (object A), expectations were incongruent.
-For each type of expectation alignment, we varied if the same or a different animal returned.
-Participants either completed the preference or novelty version and received two test trials in each of the four conditions.
-Before discussing the empirical results, we briefly discuss the cognitive model we used to predict expectation integration.
+The numerical strength of the expression above depends on \(\alpha\),
+which can be interpreted as an indicator of how rational the speaker is
+in choosing utterances.
 
-## Model Predictions
+The term \(P_S(r_s)\) denotes the prior probability that a speaker will
+refer to a given referent. This probability represents the listeners
+expectations about the speaker depending on the manipulation (preference
+or novelty) and the identity of the speaker (same or different speaker).
 
-To derive predictions, we used a probabilistic RSA model that simulates a pragmatic listener reasoning about a cooperative speaker who is trying to refer to an object [@frank2012predicting].
-The speaker chooses how to refer to the object by reasoning about a naive listener who does not know the labels for the object [@frank2014inferring].
-Mathematically, the probability that the listener chooses a referent given an utterance is defined as follows:
-$$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$
-Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance to refer to a specific referent.
-It is defined as the surprisal of an utterance given the referent for a naive listener, who interprets utterances in a literal way:
-
-$$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$
-
-The numerical strength of the expression above depends on $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances.
-
-The term $P_S(r_s)$ denotes the prior probability that a speaker will refer to a given referent.
-This probability represents the listeners expectations about the speaker depending on the manipulation (preference or novelty) and the identity of the speaker (same or different speaker).
-
-In our model, we used the results from Experiment 1 and 2 to specify $\alpha$ as well as $P_S(r_s)$.
-The former was set to yield the proportion measured in Experiment 1 in a model with uniform priors.
-The prior probability for each object was the proportion with which this object was chosen in Experiment 2\footnote{Proportions were measured when participants chose between two objects.
+In our model, we used the results from Experiment 1 and 2 to specify
+\(\alpha\) as well as \(P_S(r_s)\). The former was set to yield the
+proportion measured in Experiment 1 in a model with uniform priors. The
+prior probability for each object was the proportion with which this
+object was chosen in Experiment
+2\footnote{Proportions were measured when participants chose between two objects.
 However, in Experiment 3, three objects were involved.
 For each object we used the proportion measured in Experiment 2 as the prior probability.This approached spread out the absolute probability mass for each object but conserved the relative relation between objects.}.
-Based on these parameter settings, we predicted the proportion with which listeners will choose the less frequent object in each unique combination of alignment and speaker identity separately for each prior manipulation (eight conditions total, see Figure \ref{fig:plotexp3}).
-We compared the fit of this pragmatic model to two alternative models using Bayes Factors (BF).
-The first alternative model ignored the speaker specific expectations (flat prior model) while the second ignored the informativeness inference (prior only model).
-To capture the idea that behavioral data is to some degree noisy, all models included a noise parameter, which reflects that, with a certain probability, participants respond randomly instead of in line with the intended manipulation on a given trial.
-Noise parameters are estimated based on the data.
+Based on these parameter settings, we predicted the proportion with
+which listeners will choose the less frequent object in each unique
+combination of alignment and speaker identity separately for each prior
+manipulation (eight conditions total, see Figure \ref{fig:plotexp3}). We
+compared the fit of this pragmatic model to two alternative models using
+Bayes Factors (BF). The first alternative model ignored the speaker
+specific expectations (flat prior model) while the second ignored the
+informativeness inference (prior only model). To capture the idea that
+behavioral data is to some degree noisy, all models included a ``noise
+parameter'', which reflects that, with a certain probability,
+participants respond randomly instead of in line with the intended
+manipulation on a given trial. Noise parameters are estimated based on
+the data.
 
-## Results and Discussion
+\subsection{Results and Discussion}\label{results-and-discussion-2}
 
-```{r plotmodelcomp, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4.
+\begin{CodeChunk}
+\begin{figure*}[h]
+
+{\centering \includegraphics{figs/plotmodelcomp-1}
+
+}
+
+\caption[(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4]{(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4.
 (C) Data for strong prior manipualtion in Experiment 3 and 4.
-Error bars = 95 \\%  HDIs."}
+Error bars = 95 \%  HDIs.}\label{fig:plotmodelcomp}
+\end{figure*}
+\end{CodeChunk}
 
-pc1 <- pred_ex3%>%
-  filter(Model == "Noisy RSA Model")%>%
-  mutate(Prior = "Strong")
+Results are discussed in the form of the proportion with which listeners
+chose the less frequent object. For a comparison to chance within each
+unique condition see Figure \ref{fig:plotexp3}. Both alignment and
+speaker identity influenced participants' responses (GLMM model term:
+\texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57, \emph{p}
+\textless{} .001). Figure \ref{fig:plotmodelcomp} shows the mean
+response in each unique condition compared to the model. Model
+predictions and data were highly correlated (r = 0.96, \emph{p}
+\textless{} .001). Model fit was better in the model taking into account
+both types of expectations compared to the flat prior (BF = 2e+79) or
+prior only model (BF = 1.8e+34).
 
-c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  theme_few(base_size = 10) + 
-  guides(col = F)+
-  scale_colour_viridis_d()
+Interestingly, like in Experiment 2, there was a transfer of preference
+in case of a speaker change. Participants were at chance in the
+preference - different speaker - incongruent condition (see Figure
+\ref{fig:plotexp3}). If preference would have been specific to a
+particular individual, participants should have selected the less
+frequent object above chance (as they did in the corresponding condition
+with the novelty manipulation).
 
-pc2 <- pred_ex4%>%
-  filter(Model == "Noisy RSA Model")
+\section{Experiment 4}\label{experiment-4}
 
-c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  theme_few(base_size = 10) + 
-  scale_colour_manual(values = rev(viridis::viridis(3)))
+In Experiment 4, we replicated and extended Experiment 3 by manipulating
+the strength of the common ground expectations. Our main goal was to
+investigate the scope of our cognitive model and we therefore limit the
+description of the methods and the discussion of the results to the
+aspects relevant to the comparison between model predictions and data.
 
-pc3 <- data.frame(
-    ex3 = pc1%>%pull(Data),
-    ex3_ci_l = pc1%>%pull(Data_ci_low),
-    ex3_ci_u = pc1%>%pull(Data_ci_up),
-    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
-    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
-    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
-    Prior = "Strong")
+\subsection{Participants, Design and
+Procedure}\label{participants-design-and-procedure-3}
 
-c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
-  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Data Experiment 3")+
-  ylab("Data Experiment 4")+
-  theme_few(base_size = 10)+ 
-  scale_color_viridis_d()
+This experiment had 453 participants. The structure of the experiment
+was the same as in Experiment 3. For each common ground expectation
+(preference and novelty), we intended to have a strong, a medium and a
+weak manipulation. The strength of each manipulation was determined by
+the proportion with which participants chose the preferred / novel
+object given the manipulation. We succeeded in this for novelty. For
+preference we did not find a manipulation that yielded only a weak
+preference.
 
-ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T , labels = c("A","B","C"), vjust = 1)
+The strong manipulations were identical to Experiment 3 and the results
+are therefore a direct replication. For novelty, in the medium
+manipulation, the animal turned to each table only once before the test.
+In the weak manipulation, the animal only turned to the table with an
+object before the test. In the medium manipulation for preference, the
+animal only expressed liking and did so in a more subtle way (saying
+only: ``Oh, wow''). Participants were assigned to one level of common
+ground expectation and completed two test trials in each of the four
+conditions.
 
-```
+Model predictions were obtained in the same way as in Experiment 3. The
+likelihood term of the model was identical. For the each level of common
+ground expectation, we measured the proportion with which participants
+chose the preferred / novel object in a separate experiment. Due to
+space limitations, we do not discuss them in any more detail here. Like
+in Experiment 3, the results of these experiments were used to specify
+the prior distribution in the model.
 
-```{r ex3_tab, results="asis"}
-#comaprison to chance
-ex3_tab <- dex3 %>%  
-  filter(trial_type == "test") %>%
-  group_by(Speaker ,Prior,Alignment, id) %>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  summarize(correct_inf = list(correct_inf)) %>%
-  group_by(Speaker ,Prior,Alignment) %>%
-  mutate(M = mean(unlist(correct_inf)),
-         W = wilcox.exact(unlist(correct_inf), mu = 0.5)$statistic,
-         p = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
-  select(Prior,Alignment, Speaker, M , W,p)%>%
-  mutate(M = round(M,2),
-         p = ifelse(p<.001,"< .001",as.character(substr(round(p,3),2,5),sep=" ")))
+\subsection{Results and Discussion}\label{results-and-discussion-3}
 
-#tab1 <- xtable::xtable(ex3_tab, caption = "Proportion of choice of less frequent object for each unique condition in Experiment 3.", label = "bubub")
+As noted above, the strong prior manipulation was a direct replication
+of Experiment 3. Results from the two rounds of data collection were
+highly correlated (r = 0.97, \emph{p} \textless{} .001, see Figure
+\ref{fig:plotmodelcomp}C). Across levels of prior manipulation, the data
+from Experiment 4 were highly correlated to the corresponding model
+predictions (r = 0.91, \emph{p} \textless{} .001, see Figure
+\ref{fig:plotmodelcomp}B). Again, the pragmatic model provided a better
+fit compared to the flat prior (BF = 4.4e+74 ) or prior only model (BF =
+1.8e+84).
 
-#print(tab1, type="latex", comment = F, table.placement = "H")
+\section{Discussion}\label{discussion}
 
-```
+Language use and learning requires balancing different types of
+expectations about one's interlocutor. Here we used a Bayesian cognitive
+model to predict this integration process. Experiment 1 and 2 replicated
+earlier studies showing that adult listeners expect speakers to produce
+utterances in an informative way as well as in light of common ground.
+Next, we combined the procedures from the first two experiments to study
+how listeners would integrate them. We used the results from Experiment
+1 and 2 to specify the model parameters that represented the two types
+of expectations and make parameter-free predictions about new behavior.
+Experiments 3 and 4 showed that both types of expectations influenced
+listeners inferences. In general, listener behavior accurately described
+by our model, suggesting that -- at least in population aggregate --
+listeners trade off flexibly between speaker specific and general
+pragmatic expectations.
 
-```{r ex3_results, cache=T}
-# model 
-lm_ex3 <- glmer(correct_inf ~ Prior*Speaker*Alignment + (Speaker+Alignment|id) + (Speaker+Alignment|choiceAgent), 
-              data = dex3, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+Notably, Experiment 3 also included situations in which the two
+expectations were in conflict. For example, in some trials the animal
+expressed preference for object A, which was also the more frequent
+object. In these situations, participants chose the preferred object as
+the referent (see also Figure \ref{fig:plotexp3}). A simple explanation
+for this pattern might be that common ground manipulations were simply
+``stronger'' in that they produced higher rates of expected choice when
+presented on their own (see Figure \ref{fig:plotexp12}). However, in
+Experiment 4 we observed the same pattern in the medium manipulation for
+novelty (results not discussed above, see online repository for details)
+even though the manipulation alone yielded numerically weaker results
+compared to the general expectation in Experiment 1. In each case, the
+pattern in the data was predicted by the model This illustrates the
+conditional nature of pragmatic inference: The informativeness of an
+utterance critically depends on the context, including common ground. If
+prior interactions already single out one object as the more likely
+referent, subsequent considerations of informativeness take place in
+light of this prior information and not independent of it.
 
-#summary(lm_ex3)
+In our model, we treated common ground expectations as equivalent to
+more basic manipulations of contextual salience (e.g.~in Frank \&
+Goodman, 2012) and did not explicitly model the social-cognitive
+processes that give rise to these expectations. The interaction around
+the object prior to the test event simply increased the probability that
+this particular speaker will refer to the object subsequently. The same
+change could be brought about if one of the objects would be made
+perceptually more salient, for example by making it flash. In future
+work, it would be interesting to explore ways to model common ground
+expectations explicitly as well as to contrast perceptual and
+interactional salience.
 
-lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
+A logical next step will be to extend the work presented here to
+children. As outlined above, pragmatic reasoning is though to play an
+important role in how children learn new words. An ontogenetic study
+would also show to what extent the modelling approach taken here is
+suitable to address questions about development. Another fruitful future
+direction would be to experimentally manipulate expectations about
+speaker informativeness. For example, if a speaker repeatedly behaves in
+an irrational way (e.g.~labels dogs as cats), listeners might be less
+inclined to assume that utterances containing novel words are produced
+in an informative way.
 
-```
+This work integrates different perspectives on the study of pragmatic
+inference. Previous work focused either on general or speaker specific
+expectations. The methodological approach taken here illustrates how
+computational and experimental approaches can be used in conjunction to
+explicate theories of language use and learning.
 
-```{r model_comp}
+\vspace{1em}
+\fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}}
+\vspace{1em}
 
-model_comp <- cor.test(
-  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(mean),
-  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(Data)
-  )
+\section{Acknowledgements}\label{acknowledgements}
 
-model_comp_r <- tidy(model_comp) %>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         estimate = round(estimate,2))
+MB received funding from the European Union's Horizon 2020 research and
+innovation programme under the Marie Sklodowska-Curie grant agreement No
+749229.
 
-```
+\section{References}\label{references}
 
-Results are discussed in the form of the proportion with which listeners chose the less frequent object.
-For a comparison to chance within each unique condition see Figure \ref{fig:plotexp3}.
-Both alignment and speaker identity influenced participants’ responses  (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
-Figure \ref{fig:plotmodelcomp} shows the mean response in each unique condition compared to the model.
-Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).
-Model fit was better in the model taking into account both types of expectations compared to the flat prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
-No prior") %>%pull(BayesFactor),digits = 2)`) or prior only model (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
-Prior only") %>%pull(BayesFactor), digits = 2)`).
+\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
 
-Interestingly, like in Experiment 2, there was a transfer of preference in case of a speaker change.
-Participants were at chance in the preference - different speaker - incongruent condition (see Figure \ref{fig:plotexp3}).
-If preference would have been specific to a particular individual, participants should have selected the less frequent object above chance (as they did in the corresponding condition with the novelty manipulation).
+\hypertarget{refs}{}
+\hypertarget{ref-akhtar1996role}{}
+Akhtar, N., Carpenter, M., \& Tomasello, M. (1996). The role of
+discourse novelty in early word learning. \emph{Child Development},
+\emph{67}(2), 635--645.
 
-# Experiment 4
+\hypertarget{ref-bohn2018common}{}
+Bohn, M., \& Koymen, B. (2018). Common ground and development.
+\emph{Child Development Perspectives}, \emph{12}(2), 104--108.
 
-In Experiment 4, we replicated and extended Experiment 3 by manipulating the strength of the common ground expectations.
-Our main goal was to investigate the scope of our cognitive model and we therefore limit the description of the methods and the discussion of the results to the aspects relevant to the comparison between model predictions and data.
+\hypertarget{ref-clark2009first}{}
+Clark, E. V. (2009). \emph{First language acquisition}. Cambridge
+University Press.
 
-## Participants, Design and Procedure
+\hypertarget{ref-clark1996using}{}
+Clark, H. H. (1996). \emph{Using language}. Cambridge University Press.
 
-This experiment had 453 participants.
-The structure of the experiment was the same as in Experiment 3.
-For each common ground expectation (preference and novelty), we intended to have a strong, a medium and a weak manipulation.
-The strength of each manipulation was determined by the proportion with which participants chose the preferred / novel object given the manipulation.
-We succeeded in this for novelty.
-For preference we did not find a manipulation that yielded only a weak preference.
+\hypertarget{ref-frank2012predicting}{}
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
+in language games. \emph{Science}, \emph{336}(6084), 998--998.
 
-The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication.
-For novelty, in the medium manipulation, the animal turned to each table only once before the test.
-In the weak manipulation, the animal only turned to the table with an object before the test.
-In the medium manipulation for preference, the animal only expressed liking and did so in a more subtle way (saying only: “Oh, wow”).
-Participants were assigned to one level of common ground expectation and completed two test trials in each of the four conditions.
+\hypertarget{ref-frank2014inferring}{}
+Frank, M. C., \& Goodman, N. D. (2014). Inferring word meanings by
+assuming that speakers are informative. \emph{Cognitive Psychology},
+\emph{75}, 80--96.
 
-Model predictions were obtained in the same way as in Experiment 3.
-The likelihood term of the model was identical.
-For the each level of common ground expectation, we measured the proportion with which participants chose the preferred / novel object in a separate experiment.
-Due to space limitations, we do not discuss them in any more detail here.
-Like in Experiment 3, the results of these experiments were used to specify the prior distribution in the model.
+\hypertarget{ref-goodman2016pragmatic}{}
+Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language
+interpretation as probabilistic inference. \emph{Trends in Cognitive
+Sciences}, \emph{20}(11), 818--829.
 
-## Results and Discussion
+\hypertarget{ref-grice1991studies}{}
+Grice, H. P. (1991). \emph{Studies in the way of words}. Harvard
+University Press.
 
-```{r ex4_results}
-repl <- cor.test(
-  pred_ex3%>%filter(Model == "Noisy RSA Model")%>%pull(Data),
-  pred_ex4%>%filter(Model == "Noisy RSA Model", Prior == "Strong")%>%pull(Data)
-  )
+\hypertarget{ref-levinson2000presumptive}{}
+Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of
+generalized conversational implicature}. MIT press.
 
-repl_r <- tidy(repl) %>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         estimate = round(estimate,2))
+\hypertarget{ref-saylor2009preschoolers}{}
+Saylor, M. M., Sabbagh, M. A., Fortuna, A., \& Troseth, G. (2009).
+Preschoolers use speakers' preferences to learn words. \emph{Cognitive
+Development}, \emph{24}(2), 125--132.
 
-ex4_comp <- cor.test(
-  pred_ex4%>%filter(Model == "Noisy RSA Model")%>%pull(mean),
-  pred_ex4%>%filter(Model == "Noisy RSA Model")%>%pull(Data)
-  )
+\hypertarget{ref-sperber2001relevance}{}
+Sperber, D., \& Wilson, D. (2001). \emph{Relevance: Communication and
+cognition} (2nd ed.). Oxford; Cambridge, MA: Blackwell Publishers.
 
-ex4_comp_r <- tidy(ex4_comp) %>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         estimate = round(estimate,2))
+\hypertarget{ref-tomasello2009constructing}{}
+Tomasello, M. (2009). \emph{Constructing a language}. Harvard university
+press.
 
-```
-
-As noted above, the strong prior manipulation was a direct replication of Experiment 3.
-Results from the two rounds of data collection were highly correlated (r = `r repl_r$estimate`, *p* `r repl_r$p.value`, see Figure \ref{fig:plotmodelcomp}C).
-Across levels of prior manipulation, the data from Experiment 4 were highly correlated to the corresponding model predictions (r = `r ex4_comp_r$estimate`, *p* `r ex4_comp_r$p.value`, see Figure \ref{fig:plotmodelcomp}B).
-Again, the pragmatic model provided a better fit compared to the flat prior (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
-No prior") %>%pull(BayesFactor),digits = 2)` ) or prior only model (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
-Prior only") %>%pull(BayesFactor), digits = 2)`).
-
-# Discussion
-
-Language use and learning requires balancing different types of expectations about one’s interlocutor.
-Here we used a Bayesian cognitive model to predict this integration process.
-Experiment 1 and 2 replicated earlier studies showing that adult listeners expect speakers to produce utterances in an informative way as well as in light of common ground.
-Next, we combined the procedures from the first two experiments to study how listeners would integrate them.
-We used the results from Experiment 1 and 2 to specify the model parameters that represented the two types of expectations and make parameter-free predictions about new behavior.
-Experiments 3 and 4 showed that both types of expectations influenced listeners inferences.
-In general, listener behavior accurately described by our model, suggesting that – at least in population aggregate – listeners trade off flexibly between speaker specific and general pragmatic expectations.
-
-Notably, Experiment 3 also included situations in which the two expectations were in conflict.
-For example, in some trials the animal expressed preference for object A, which was also the more frequent object.
-In these situations, participants chose the preferred object as the referent  (see also Figure \ref{fig:plotexp3}).
-A simple explanation for this pattern might be that common ground manipulations were simply “stronger” in that they produced higher rates of expected choice when presented on their own (see Figure \ref{fig:plotexp12}).
-However, in Experiment 4 we observed the same pattern in the medium manipulation for novelty (results not discussed above, see online repository for details) even though the manipulation alone yielded numerically weaker results compared to the general expectation in Experiment 1.
-In each case, the pattern in the data was  predicted by the model This illustrates the conditional nature of pragmatic inference: The informativeness of an utterance critically depends on the context, including common ground.
-If prior interactions already single out one object as the more likely referent, subsequent considerations of informativeness take place in light of this prior information and not independent of it.
-
-In our model, we treated common ground expectations as equivalent to more basic manipulations of contextual salience [e.g.
-in @frank2012predicting] and did not explicitly model the social-cognitive processes that give rise to these expectations.
-The interaction around the object prior to the test event simply increased the probability that this particular speaker will refer to the object subsequently.
-The same change could be brought about if one of the objects would be made perceptually more salient, for example by making it flash.
-In future work, it would be interesting to explore ways to model common ground expectations explicitly as well as to contrast perceptual and interactional salience.
-
-A logical next step will be to extend the work presented here to children.
-As outlined above, pragmatic reasoning is though to play an important role in how children learn new words.
-An ontogenetic study would also show to what extent the modelling approach taken here is suitable to address questions about development.
-Another fruitful future direction would be to experimentally manipulate expectations about speaker informativeness.
-For example, if a speaker repeatedly behaves in an irrational way (e.g.
-labels dogs as cats), listeners might be less inclined to assume that utterances containing novel words are produced in an informative way.
-
-This work integrates different perspectives on the study of pragmatic inference.
-Previous work focused either on general or speaker specific expectations.
-The methodological approach taken here illustrates how computational and experimental approaches can be used in conjunction to explicate theories of language use and learning.
-
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em}
-
-# Acknowledgements
-
-MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.
-
-# References
-
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\end{document}

### 2019-01-09 stats/adults/ex3_comparisons.Rmd
first draft CogSci paper

@@
 
-load("mcc_model_comparison.RData")
+load("../saves/mcc_model_comparison.RData")
 
@@
 ```{r model no prior noise loglikelihood}
+no.prior.loglikelihood <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.allPriorProbs
+
+var model = function(){
+  var noise = uniformDrift({a: 0, b:1, width: 0.1})
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+  var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+var loglike = Binomial({
+        p: Math.exp(modelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+}, allConditions)
+
+ return sum(conditionOutput)
+}
+'
+```
+
+```{r model no prior noise loglikelihood}
 no.prior.noise.loglikelihood <-'
@@
 ```{r model loglikelihoods}
+
 ###################
 # RSA Models
+###################
+
+llh.rsa <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA")
+
+llh.rsa.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy")
+
+llh.rsa.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Regularized")
+
+llh.rsa.noise.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "RSA Noisy Regularized")
+
+###################
+# Prior only models
+###################
+
+llh.prior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "Prior only")
+
+llh.prior.noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "Prior only Noisy")
+
+llh.prior.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+)%>%
+  mutate(Model = "Prior only Regularized")
+
+llh.prior.noise.regPrior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
+  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
+  data_var = "dataFromR",
+  model_var = "model",
+  inference_opts = list(method = "forward", samples = 10000),
+  chains = 3, cores = 3
+) %>%
+  mutate(Model = "Prior only Noisy Regularized")
+
+###################
+# no Prior Models
 ###################
@@
 
-llh.rsa <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
+llh.no.prior <- webppl(
+  program_code = paste(rsaUtils, rsaModel2, no.prior.loglikelihood, sep='\n'),
   data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
@@
 )%>%
-  mutate(Model = "RSA")
-
-llh.rsa.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "RSA Noisy")
-
-llh.rsa.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "RSA Regularized")
-
-llh.rsa.noise.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "RSA Noisy Regularized")
-
-###################
-# Prior only models
-###################
-
-llh.prior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "Prior only")
-
-llh.prior.noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "Prior only Noisy")
-
-llh.prior.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-)%>%
-  mutate(Model = "Prior only Regularized")
-
-llh.prior.noise.regPrior <- webppl(
-  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
-  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
-  data_var = "dataFromR",
-  model_var = "model",
-  inference_opts = list(method = "forward", samples = 10000),
-  chains = 3, cores = 3
-) %>%
-  mutate(Model = "Prior only Noisy Regularized")
+  mutate(Model = "No Prior")
 
@@
 
+```
+
+```{r bayes factors, echo = FALSE}
+
+bf <- data.frame(
+  Comparison = c("Pragmatic vs. Prior only","Pragmatic vs. No prior", "No Prior vs. Prior only"),
+  BayesFactor = c(
+    exp(llh.plot$logP[llh.plot$Model== "Pragmatic"] - llh.plot$logP[llh.plot$Model== "Prior only"]),
+    exp(llh.plot$logP[llh.plot$Model== "Pragmatic"] - llh.plot$logP[llh.plot$Model== "No Prior"]),
+    exp(llh.plot$logP[llh.plot$Model== "Prior only"] - llh.plot$logP[llh.plot$Model== "No Prior"]))
+)
+
+bf%>%
+  kable(digits = 2)
 ```
@@
 ```
+
+```{r}
+save.image("../saves/mcc_model_comparison.RData")
+
+saveRDS(bf, "../saves/ex3_bf.rds")
+
+saveRDS(vp.bf, "../saves/ex4_bf.rds")
+
+```
+
+# old code .. ignore
 
@@
 ```
-
-```{r}
-save.image("mcc_model_comparison.RData")
-```

### 2019-01-09 stats/adults/mcc_priors_overview.Rmd
first draft CogSci paper

--- 2018-05-10 stats/mcc_priors_overview.Rmd
@@
 
-```{r data}
-d3 <- read_csv(file="novel.weak.data2.csv") %>%
+```{r data, include = F}
+d3 <- read_csv(file="../data/novel.weak.data2.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d4 <- read_csv(file="novel.weak.data.csv") %>%
+d4 <- read_csv(file="../data/novel.weak.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d1 <- read_csv(file="novel.data.csv") %>%
+d1 <- read_csv(file="../data/novel.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d2 <-read_csv(file="pref.data.csv") %>%
+d2 <-read_csv(file="../data/pref.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d5 <-read_csv(file="pref.weak.data.csv") %>%
+d5 <-read_csv(file="../data/pref.weak.data.csv") %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
@@
 
-d6 <-read_csv(file="pref.weak.data3.csv") %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         strength = "1_weak")
+#d6 <-read_csv(file="pref.weak.data3.csv") %>%
+#  mutate(trial_type = ifelse(trial == "train", "train", "test"),
+#         strength = "1_weak")
 
-d <- bind_rows(d1,d2,d3,d4,d5,d6)
+d <- bind_rows(d1,d2,d3,d4,d5)
 
@@
   distinct(id, alltrial, .keep_all = TRUE)
+
+length(unique(d$id))
 ```
 
-```{r plot data}
+```{r plot data, echo = F}
 

### 2019-01-09 stats/adults/visualizations.Rmd
first draft CogSci paper

--- 2018-10-29 stats/visualizations.Rmd
@@
 ```{r setup, include=FALSE}
-load("mcc_model_comparison.RData")
+load("../saves/mcc_model_comparison.RData")
 
@@
   filter(trial_type == "test") %>%
-  mutate(control = ifelse(control == "true", "Control", "Test")) %>%
-  group_by(condition ,control, id) %>%
+  mutate(control = ifelse(control == "true", "Control", "Test"),
+         condition = factor(condition), 
+         experiment = ifelse(condition == "1", "1","2"))%>%
+  group_by(experiment,condition ,control, id) %>%
   summarise(correct = mean(correct))
@@
 p2 <- p1 %>%
-  multi_boot_standard(col = "correct") %>%
-  ungroup()%>%
-  mutate(condition = as.character(condition))
+  multi_boot_standard(col = "correct")
 
@@
 
-exp12 <- ggplot() +
-  geom_rect(data = p2, aes(fill = NA), alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
+ ggplot() +
+  geom_rect(data = p2, aes(colour = experiment, size = 4), fill = NA, alpha = 1 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf, show.legend=FALSE)+
   geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
@@
   labs(x="",y="Expected Choice")+
-  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness"))) +
-  theme_few(base_size = 20) + 
+  facet_wrap( ~ condition, labeller = as_labeller(c(`2`="Exp. 2 - Preference", `3`="Exp. 2 - Novelty", `1`="Exp. 1 - Informativeness")))+
+  theme_few() + 
   ylim(-0.05,1.05)+
-  guides(alpha = F, fill = F)+ 
-  scale_color_manual(name="Condition",
-                     breaks=c("Control","Test"),
-                     values= c("#657b83","black"))+
-  scale_fill_manual(name="Condition",
-                     breaks=c("1","2","3"),
-                     values= c("#dc322f","#268bd2","#268bd2"))+
+  guides(alpha = F,size =F)+
+  scale_color_manual(name = "Condition",
+                     breaks=c("Test","Control"),
+                     values= c("#dc322f","#268bd2","#839496","black"))+
   theme(axis.text.x=element_blank(),axis.ticks.x=element_blank(),
-        panel.border = element_rect(color = "#268bd2", fill = NA, size = 6))
+        panel.border = element_blank()
+        )
 
+```
+
+```{r}
+ggarrange(exp1,exp2,exp3, ncol = 3, nrow = 1, legend = "right", common.legend = T)
 ```
@@
 ```
+
+# kids
+
+```{r pretest data, include=FALSE}
+pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
+  filter(age != "2",
+         trial_type != "train")%>%
+  mutate(age_bin = factor(age),
+         experiment = "preference_pretest",
+         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
+         agent = ifelse( change == "false", agent, altAgent),
+         minage = min(age_num))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)
+
+inf_data <- read_csv(file="../data/kids_inf_data.csv")%>%
+  filter(subage != "2",
+         trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = factor(subage),
+         experiment = "informativeness_pretest",
+         condition = ifelse(control == "no", "test", "control"),
+        minage = min(age_num))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)
+
+pre_data <- bind_rows(pref_data,
+                      inf_data)
+```
+
+```{r pretest plot so, echo = F}
+
+pre_so <- pre_data %>%
+  filter(experiment == "informativeness_pretest")%>%
+  group_by(age_num,subid)%>%
+  summarise(correct = mean(correct))
+
+ggplot(data = pre_so, aes(x = age_num, y = correct)) +
+  geom_jitter(alpha = 1, height = 0.1, width = 0.1, col = "grey")+
+  geom_smooth(method = "lm", se = T, col = "black",fill = "darkgreen", alpha = .4, size = 1)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  #ggtitle("Informativeness data")+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)+
+  theme(panel.border = element_rect(color = "#dc322f", fill = NA, size = 6))
+```
+
+```{r}
+ggsave("../graphs/kids_inf2.png", width = 3, height = 3, scale = 1.5)
+```
+
+```{r pretest plot prior, echo = F}
+
+pre_prior <- pre_data %>%
+  filter(experiment == "preference_pretest")%>%
+  group_by(condition,age_num,subid)%>%
+  summarise(correct = mean(correct))
+
+ggplot(data = pre_prior, aes(x = age_num, y = correct, col = condition)) +
+  geom_jitter(alpha = 0.5, height = 0.1, width = 0.1)+
+  geom_smooth(aes(fill = condition),method = "lm", se = T, col = "black",  alpha = .5, size = 1)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  #ggtitle("Preference data")+
+  ylim(0,1)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()+
+  theme(panel.border = element_rect(color = "#268bd2", fill = NA, size = 6),legend.position="bottom")
+
+```
+
+```{r}
+ggsave("../graphs/kids_pref.png", width = 5, height = 4, scale = 1.5)
+```
+
+```{r pretest plot prior, echo = F}
+
+kids_novel_data <- read_csv(file="../data/kids_novel.data.round1.csv")%>%
+  filter(age != 2)%>%
+  mutate(condition = ifelse(change == "false", "same_speaker", "different_speaker"))
+
+p_kids_novel <- kids_novel_data %>%
+  group_by(condition,age_num,subid)%>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p_kids_novel, aes(x = age_num, y = correct, col = condition)) +
+  geom_jitter(alpha = 0.5, height = 0.1, width = 0.1)+
+  geom_smooth(aes(fill = condition),method = "lm", se = T, col = "black",  alpha = .5, size = 1)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  #ggtitle("Preference data")+
+  ylim(0,1)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()+
+  theme(panel.border = element_rect(color = "#268bd2", fill = NA, size = 6),legend.position="bottom")
+
+```
+
+```{r}
+ggsave("../graphs/kids_novel.png", width = 5, height = 4, scale = 1.5)
+```
+
+### Model based speaker optimality by age
+
+```{r plot so model pred, echo = F}
+
+plot_model_pred_so <- kids_model_pred_so%>%
+  group_by(age_bin)%>%
+  summarise(mean = mean(speakerOptimality),
+            lci = hdi_lower(speakerOptimality),
+            uci = hdi_upper(speakerOptimality))
+
+ggplot(data = plot_model_pred_so) +
+  geom_line(data = kids_model_pred_so,aes(age_bin, speakerOptimality, group = iteration), col = "grey", alpha = 0.3) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci), fill = "green", alpha = .2) +
+  geom_line(aes(age_bin, mean), col = "black", size = 1, alpha = 1) + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
+  geom_hline(yintercept = 0, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  #ggtitle("Informativeness data")+
+  ylim(-4,4)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 1/4)+
+  theme(panel.border = element_rect(color = "#dc322f", fill = NA, size = 6))
+
+```
+
+```{r}
+ggsave("../graphs/kids_so_model.png", width = 3, height = 3, scale = 1.5)
+```
+
+```{r plot prior model pred, echo = F}
+plot_model_pred_prior <- kids_model_pred_prior%>%
+  group_by(age_bin,condition)%>%
+  summarise(mean = mean(prop_preferred),
+            lci = hdi_lower(prop_preferred),
+            uci = hdi_upper(prop_preferred))
+
+ggplot(data = p_kids_novel, aes(x = age_num, y = correct, col = condition)) +
+  geom_jitter(alpha = 0.5, height = 0.1, width = 0.1)+
+  geom_smooth(aes(fill = condition),method = "lm", se = T, col = "black",  alpha = .5, size = 1)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  #ggtitle("Preference data")+
+  ylim(0,1)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()+
+  theme(panel.border = element_rect(color = "#268bd2", fill = NA, size = 6),legend.position="bottom")
+
+ggplot(data = plot_model_pred_prior) +
+  geom_line(data = kids_model_pred_prior,aes(age_bin, prop_preferred, group = paste(iteration,condition, sep= ""), col = condition), alpha = 0.05) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = condition), alpha = .5) +
+  geom_line(aes(age_bin, mean, group = condition), col = "black", size = 1, alpha = 1) + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  scale_y_continuous(limits=c(-0.05,1.05), name="Proportion Expected Choice")+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few(base_size = 20) +
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()+
+  theme(panel.border = element_rect(color = "#268bd2", fill = NA, size = 6),legend.position="bottom")
+
+```
+
+```{r}
+ggsave("../graphs/kids_prior_model.png", width = 5, height = 4, scale = 1.5)
+```
+
+```{r}
+model_comp_mean_ci <- bind_rows(
+#plot_model_pred%>%ungroup()%>%mutate(model = "RSA"), 
+plot_prior_only_pred%>%ungroup()%>%mutate(model = "Prior Only"),
+no_prior_plot%>%ungroup()%>%mutate(model = "No Prior")
+)
+
+model_comp <- bind_rows(
+#kids_model_pred %>%mutate(model = "RSA"),
+prior_only_model%>%mutate(model = "Prior Only"),
+no_prior_pred%>%select(-so_slope,-so_int,-speakerOptimality)%>%mutate(model = "No Prior")
+  )
+
+```
+
+```{r, include = F}
+ggplot(model_comp_mean_ci)+
+  geom_line(data = model_comp,aes(age_bin, prop_informative, group = paste(iteration,Speaker,model, sep= ""), col = model),  alpha = 0.01) + 
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few(base_size = 20)+
+  scale_color_manual( values = c("#dc322f","#268bd2"))+
+  scale_fill_manual(values = c("#dc322f","#268bd2"))
+```
+
+```{r, include = F}
+ggsave("../graphs/kids_no_prior_prior_only_model_predictions.pdf", width = 9, height = 7, scale = 1.2)
+```

### 2019-01-09 stats/kids/kids_Ex3_pref.Rmd
first draft CogSci paper

---
title: "MCC Ex3 Preference Kids"
author: "Manuel Bohn"
output: html_document
---

```{r import data, include = F}
###
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

## importing data
files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,42,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

raw_data <- raw_data %>%
  mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
         subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
         subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))

raw_data%>%
  #group_by(paste(subid,test_date))%>%
  group_by(subid)%>%
  summarise(n= n())

unique(raw_data$subid)

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "ex3p")%>%
  select(subid,experimenter,keep_drop,sex,dob)

#unique(log$subid)
sum(log$keep_drop == "drop")

d <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

unique(d$check_age)

```

# Sample size per age bin

```{r kids per age group,echo = F }

d %>%
  group_by(subage,subid)%>%
  summarise(n_trials = n())%>%
  mutate(full_data = ifelse(n_trials == 10,"yes","no"))%>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)),
            n_full_data = sum(full_data == "yes"))%>%
  knitr::kable(digits = 2)

```

# Datapoints per cell

```{r kids per age group,echo = F }

d %>%
  filter(trial != "filler1",trial != "filler2")%>%
  group_by(subage,speaker,alignment)%>%
  summarise(datapoints = n())%>%
  knitr::kable(digits = 2)

```

# Plot filler by age

```{r plot by age, echo= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_inf))

pf2 <- pf1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pf1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = pf2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

# Plot by age group

```{r plot by age, echo= FALSE}

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(speaker, alignment ,subage, subid) %>%
  summarise(correct = mean(correct_inf))

p2 <- p1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p1, aes(x = alignment, y = correct, col = alignment, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = alignment, y = mean, col = alignment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(speaker~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot by age continous

```{r plot by age, echo= FALSE}

p3 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(speaker, alignment ,age_num, subid) %>%
  summarise(correct = mean(correct_inf))

ggplot(data = p3, aes(x = age_num, y = correct_inf)) +
  geom_jitter(width = .025,height = .025, alpha = .2)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(speaker~alignment)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  coord_fixed(ratio = 2)

```

```{r model}

library(lme4)

dm <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(age_num = scale(age_num, center = T, scale = T))

mex3 <- glmer(correct_inf ~ age_num*speaker*alignment 
      + (speaker*alignment | subid) 
      + (age_num*speaker*alignment | agent), 
      family = "binomial",
      data = dm,
      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(mex3)
```

```{r chance_comp}
mod <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(subage,speaker,alignment) %>%
  do(models = glmer(correct_inf ~ 1+ (1|subid),data=., family=binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))

library(broom)

tidy(mod, models) %>%
  filter(term =="(Intercept)")
```

### 2019-01-09 stats/kids/kids_model_predictions.Rmd
first draft CogSci paper

@@
 author: "Manuel Bohn"
-output: html_document
+output: 
+  html_document:
+      code_folding: hide
 ---
 
-```{r}
-knitr::opts_chunk$set(echo = TRUE)
+```{r, include = F}
+knitr::opts_chunk$set(echo = TRUE, warning = F)
 ```
@@
 library(ggthemes)
+library(ggpubr)
 library(langcog)
@@
 ```
+
 # Pretest
 
-Loading data
-
-```{r pretest data}
-
+```{r pretest data, include=FALSE}
 pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
@@
          condition = ifelse(change == "false", "same_speaker", "different_speaker"),
-         agent = ifelse( change == "false", agent, altAgent))%>%
-  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)
+         agent = ifelse( change == "false", agent, altAgent),
+         minage = min(age_num))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)
 
@@
          experiment = "informativeness_pretest",
-         condition = ifelse(control == "no", "test", "control"))%>%
-  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)
+         condition = ifelse(control == "no", "test", "control"),
+        minage = min(age_num))%>%
+  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct,minage)
 
@@
                       inf_data)
-
 ```
@@
 
-```{r pretest plot}
-
-pre_p1 <- pre_data %>%
-  group_by(experiment,condition,age_num,subid)%>%
+This is the data we use to estimate the speaker optimality nad the age specific prior.
+
+```{r pretest plot so, echo = F}
+
+pre_so <- pre_data %>%
+  filter(experiment == "informativeness_pretest")%>%
+  group_by(age_num,subid)%>%
   summarise(correct = mean(correct))
 
-ggplot(data = pre_p1, aes(x = age_num, y = correct, col = condition)) +
-  geom_smooth(method = "lm", se = F)+
-  geom_jitter(alpha = .5, height = 0, width = 0)+
+plot_inf <- ggplot(data = pre_so, aes(x = age_num, y = correct)) +
+  geom_jitter(alpha = 1, height = 0.1, width = 0.1, col = "grey")+
+  geom_smooth(method = "lm", se = T, col = "black",fill = "darkgreen", alpha = .4, size = .4)+
   geom_hline(yintercept = 0.5, lty=2)+
-  facet_wrap(~experiment)+
+  labs(x="age",y="Proportion Expected Choice")+
+  theme_few() +
+  ggtitle("Informativeness data")+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  coord_fixed(ratio = 2)
+```
+
+```{r pretest plot prior, echo = F}
+
+pre_prior <- pre_data %>%
+  filter(experiment == "preference_pretest")%>%
+  group_by(condition,age_num,subid)%>%
+  summarise(correct = mean(correct))
+
+plot_pref <- ggplot(data = pre_prior, aes(x = age_num, y = correct, col = condition)) +
+  geom_jitter(alpha = 0.5, height = 0.1, width = 0.1)+
+  geom_smooth(aes(fill = condition),method = "lm", se = T, col = "black",  alpha = .5, size = .4)+
+  geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Proportion Expected Choice")+
   theme_few() +
+  ggtitle("Preference data")+
   ylim(-0.05,1.05)+
   guides(alpha = F)+ 
-  scale_colour_solarized()
-
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
+```{r, echo = F, fig.width= 8}
+ggarrange(plot_inf, plot_pref, widths = c(1.29,2))
 ```
@@
 
-```{r rsaUtils, include = FALSE}
+### Model utensils.
+
+There are two types of objects, one used in the 3-object world of the RSA model (`all_objects`) and one used in the 2-object world of the prior (`prior_objects`).
+
+```{r rsaUtils}
 rsaUtils <- '
@@
 
-```{r rsa model, include = FALSE}
+### RSA model code
+
+```{r rsa model}
 
 rsaModel <- '
+var literalListener = cache(function(utterance, priorProbs){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior); 
+var lexicon = lexiconObject[lexiconName];
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+if ("label" in utterance) {
+ var truthValue = lexicon(utterance, obj);
+ condition(truthValue)
+}
+if (utterance.point) {
+ var truthValuePoint = point(utterance, obj);
+ condition(truthValuePoint)
+}
+return obj.shape 
+}})
+})
+
+var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance, priorProbs);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+})
 
@@
 
-var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
-Infer({method: "enumerate", model: function(){
-var utterance = utterancePrior(obj, lexiconName);
-var L0 = literalListener(utterance, priorProbs);
- factor(speakerOptimality * L0.score(obj.shape))
-return utterance
-}})
-})
-
-var literalListener = cache(function(utterance, priorProbs){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior); 
-var lexicon = lexiconObject[lexiconName];
-var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-if ("label" in utterance) {
- var truthValue = lexicon(utterance, obj);
- condition(truthValue)
-}
-if (utterance.point) {
- var truthValuePoint = point(utterance, obj);
- condition(truthValuePoint)
-}
-return obj.shape 
-}})
-})
-
 var addNoise = function(dist, noiseParam){
@@
 
-## Informativeness
-
-###  Inf prior predictions 
+### Priors for intercept and slope for speaker optimality and preference
+
+Sanity check for the priors on slope and intercept.
+
+#### Speaker optimality
+
 ```{r prior speaker optimality slope}
 priorSoWebppl <- '
-
 var infData = dataFromR
@@
 var speakerOptimality = []
-
 var model  = function(){
-
   var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
   var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
     map(function(row){
-
       var age = row.age_num
-
       var speakerOptimality = so_int  + so_slope * (age - row.minage)
-
       var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs, speakerOptimality)
@@
       //display(JSON.stringify(row.minage))
-
     }, infData)
-
   return extend({so_int: so_int, so_slope: so_slope})
@@
 ```{r speaker optimality prior pred}
-#so_prior <- readRDS("../saves/so_prior.rds")
-
-so_prior<- webppl(
-  program_code = paste(rsaUtils, rsaModel, priorSoWebppl , sep='\n'),
-  data = inf_data%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  inference_opts = list(method = "forward", samples = 1000, verbose = T)
-)
-
-saveRDS(so_prior, "../saves/so_prior.rds")
+so_prior <- readRDS("../saves/so_prior.rds")
+# so_prior<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, priorSoWebppl , sep='\n'),
+#   data = inf_data%>%mutate(minage = min(age_num)), 
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 1,
+#   inference_opts = list(method = "forward", samples = 1000, verbose = T)
+# )
+#saveRDS(so_prior, "../saves/so_prior.rds")
 
@@
 
-```
-
-```{r plot prior pred}
-ggplot(data = priorPred) +
+so_prior_plot <- ggplot(data = priorPred) +
   geom_abline(aes(intercept = so_int, slope = so_slope), col = "grey", alpha = 0.3)+
-  geom_abline(data = mean_so_pre, aes(intercept = int, slope = slope), size = 1)+
+  geom_abline(data = mean_so_pre, aes(intercept = int, slope = slope), size = 0.4)+
   scale_x_continuous(limits=c(0, 2), name="age", breaks = c(0:2), labels = c(3:5)) +
   scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
+  ggtitle("Model speaker optimality prior")+
+  coord_fixed(ratio=1/4)+
   theme_few()
@@
 
-```{r}
-ggplot(data = so_prior, aes(x = value, fill = chain)) +
-  geom_density(alpha = .5)+
-  facet_wrap(~Parameter)+
-  theme_few()
-```
-
-### Inf posterior predictions
-
-```{r posterior speaker optimality slope}
-postSoWebppl <- '
-
-var infData = dataFromR
-var priorProbs = [.5, .5, .5]
-
-var model  = function(){
-
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    map(function(row){
-
-      var age = row.age_num
-
-      var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
-
-      var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs, speakerOptimality)
-
-      observe(rsaPredictions, row.correct)
-
-      //display(rsaPredictions.score( row.correct))
-      //display(JSON.stringify(row.correct))
-      //display(JSON.stringify(rsaPredictions))
-
-    }, infData)
-
-  return extend({so_int: so_int, so_slope: so_slope})
-}
-'
-```
-
-```{r speaker optimality posterior pred}
-# so_post <- readRDS("../saves/so_post.rds")
-
-so_post <- webppl(
-  program_code = paste(rsaUtils, rsaModel, postSoWebppl , sep='\n'),
-  data = inf_data%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-# saveRDS(so_post, "../saves/so_post.rds")
-
-postPred <- so_post%>%
-  spread(Parameter, value)%>%
-  mutate(chain = factor(Chain))
-
-so_post <- so_post%>%
-  mutate(chain = factor(Chain))
-
-mean_so_post <-postPred%>%
-  #group_by(chain)%>%
-  summarise(int = mean(so_int),
-            slope = mean(so_slope))
-
-# confidence intervals
-x_plot <- seq(0, 2, by = 0.1)
-
-ci_so_post <- sapply(1:length(postPred$so_int), function(idx) {
-           postPred$so_int[idx] + postPred$so_slope[idx] * x_plot
-        })
-
-colnames(ci_so_post) <- 1:length(postPred$so_int)
-ci_so_post <- as.data.frame(cbind(x_plot, ci_so_post))
-ci_so_post <- melt(ci_so_post, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")
-
-ci_so_post <- ci_so_post %>%
-  group_by(x_plot)%>%
-  summarise(ci_upper = hdi_upper(y_plot),
-            ci_lower = hdi_lower(y_plot))
-
-```
-
-```{r plot posterior pred}
-
-ggplot(data = postPred) +
-  geom_abline(aes(intercept = so_int, slope = so_slope), col = "grey", alpha = 0.2)+
-  geom_ribbon(data = ci_so_post, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
-  geom_abline(data = mean_so_post, aes(intercept = int, slope = slope), size = 1)+
-  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
-  scale_y_continuous(limits=c(-2, 4), name="Speaker optimality")+
-  #facet_wrap(~chain)+
-  theme_few()
-
-```
-
-```{r}
-ggplot(data = so_post ) +
-  geom_density(aes(x = value, fill = chain), alpha = .5)+
-  facet_wrap(~Parameter)+
-  theme_few()
-```
-
-## Preference
-
-### Pref prior predictions
+#### Preference
 
 ```{r prior preference congruent}
-priorPrefConWebppl <- '
-
+priorPreWebppl <- '
 var prefData = dataFromR
 var priorProbs = [] 
-
 var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
 var model  = function(){
-
   var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
   var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
     map(function(row){
-
       var age = row.age_num
-
       var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [1-priorReg, 1-priorReg, priorReg]
-
+      var priorProbs= [1-priorReg, priorReg]
       var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
       return obj.shape == "circle" ? 1 : 0
@@
       // observe(priorPredictions, row.correct)
-
      // display(JSON.stringify(priorReg))
-
     }, prefData)
-
   return extend({pref_int: pref_int, pref_slope: pref_slope})
@@
 
-```{r prior preference slope}
-priorPrefInconWebppl <- '
-
-var prefData = dataFromR
-var priorProbs = []
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    map(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [priorReg, priorReg, 1-priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      // observe(priorPredictions, row.correct)
-
-     // display(JSON.stringify(priorReg))
-
-    }, prefData)
-
-  return extend({pref_int: pref_int, pref_slope: pref_slope})
-}
-'
-```
-
-```{r pref prior pred}
-
-# congruent condition
-
-# pref_prior_con <- readRDS("../saves/pref_prior_con.rds")
-
-pref_prior_con<- webppl(
-  program_code = paste(rsaUtils, rsaModel, priorPrefConWebppl , sep='\n'),
-  data = pref_data%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  inference_opts = list(method = "forward", samples = 1000, verbose = T)
-)
-
+```{r}
+pref_prior_con <- readRDS("../saves/pref_prior_con.rds")
+
+# pref_prior_con<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, priorPrefConWebppl , sep='\n'),
+#   data = pref_data%>%mutate(minage = min(age_num)), 
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 1,
+#   inference_opts = list(method = "forward", samples = 1000, verbose = T)
+# )
  # saveRDS(pref_prior_con, "../saves/pref_prior_con.rds")
 
-# incongruent condition
-
-#pref_prior_incon <- readRDS("../saves/pref_prior_incon.rds")
-
-pref_prior_incon<- webppl(
-  program_code = paste(rsaUtils, rsaModel, priorPrefInconWebppl , sep='\n'),
-  data = pref_data%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  inference_opts = list(method = "forward", samples = 1000, verbose = T)
-)
-
- #saveRDS(pref_prior_incon, "../saves/pref_prior_incon.rds")
-
-```
-
-```{r}
-# congruent condition
 prefPriorPredCon <- pref_prior_con%>%
@@
 x_plot <- seq(0, 2, by = 0.1)
-
 model_predictions <- sapply(1:length(prefPriorPredCon$pref_int), function(idx) {
@@
         })
-
 colnames(model_predictions) <- 1:length(prefPriorPredCon$pref_int)
@@
 
-# incongruent condition
-
-prefPriorPredIncon <- pref_prior_incon%>%
-  spread(Parameter, value)
-
-pref_prior_incon <- pref_prior_incon%>%
-  mutate(chain = factor(Chain),
-         alignment = "incongruent")
-
-model_predictions <- sapply(1:length(prefPriorPredIncon$pref_int), function(idx) {
-            plogis(prefPriorPredIncon$pref_int[idx] + prefPriorPredIncon$pref_slope[idx] * x_plot)
-        })
-
-colnames(model_predictions) <- 1:length(prefPriorPredIncon$pref_int)
-plot_pref_prior_incon <- as.data.frame(cbind(x_plot, model_predictions))
-plot_pref_prior_incon <- melt(plot_pref_prior_incon, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")
-
-# joining datasets
-
-plot_pref_prior <- bind_rows(
-  plot_pref_prior_con %>% mutate(alignment = "congruent"),
-  plot_pref_prior_incon %>% mutate(alignment = "incongruent")
-)
-
-plot_prior_mean <- plot_pref_prior%>%
-  group_by(alignment,x_plot)%>%
-  summarise(mean = mean(y_plot),
-            ci_upper = hdi_upper(y_plot),
-            ci_lower = hdi_lower(y_plot))
-
-pref_prior <- bind_rows(
-  pref_prior_con,
-  pref_prior_incon
-)
-
-```
-
-```{r plot prior pred}
-
-ggplot(plot_pref_prior) + 
+pref_prior_plot <- ggplot(plot_pref_prior_con) + 
   geom_line(aes(x_plot, y_plot, group = iteration), col = "grey",alpha = 0.2) +
   #geom_ribbon(data = plot_prior_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "red", alpha = 0.5) +
-  geom_line(data = plot_prior_mean, aes(x_plot, mean), col = "black", size =1) +
-  xlab("age") + ylab("p(y | x)") +
-  facet_wrap(~alignment)+
+  geom_line(data = plot_prior_con_mean, aes(x_plot, y_plot), col = "black", size = 0.4) +
+  xlab("age") + ylab("Proportion Expected Choice") +
   scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
   scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
+  ggtitle("Model preference prior")+
+  coord_fixed(ratio=2)+
   theme_few()
-
-```
-
-```{r}
-ggplot(data = pref_prior, aes(x = value, fill = chain)) +
-  geom_density(alpha = 0.3)+
-  facet_grid(Parameter~ alignment)+
-  theme_few()
-```
-
-### Pref posterior predictions
-
-```{r posterior preference congruent}
-postPrefConWebppl <- '
-
-var prefData = dataFromR
-var priorProbs = []
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    map(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [1-priorReg,1-priorReg, priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-     // display(JSON.stringify(priorReg))
-
-    }, prefData)
-
-  return extend({pref_int: pref_int, pref_slope: pref_slope})
-}
-'
-```
-
-```{r}
-postPrefInconWebppl <- '
-
-var prefData = dataFromR
-var priorProbs = []
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    map(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [priorReg, priorReg, 1-priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-     // display(JSON.stringify(priorReg))
-
-    }, prefData)
-
-  return extend({pref_int: pref_int, pref_slope: pref_slope})
-}
-'
-```
-
-```{r pref post pred}
-
-# Same Speaker
-# congruent
-#pref_post_con_same <- readRDS("../saves/pref_post_con_same.rds")
-
-pref_post_con_same2<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
-  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-saveRDS(pref_post_con_same, "../saves/pref_post_con_same.rds")
-
-# Same Speaker
-# incongruent
-#pref_post_incon_same <- readRDS("../saves/pref_post_incon_same.rds")
-
-pref_post_incon_same<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefInconWebppl , sep='\n'),
-  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-saveRDS(pref_post_incon_same, "../saves/pref_post_incon_same.rds")
-
-# Different Speaker
-# congruent
-#pref_post_con_diff <- readRDS("../saves/pref_post_con_diff.rds")
-
-pref_post_con_diff<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl , sep='\n'),
-  data = pref_data%>%filter(condition == "different_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
- saveRDS(pref_post_con_diff, "../saves/pref_post_con_diff.rds")
-
-# Different Speaker
-# incongruent
-#pref_post_incon_diff <- readRDS("../saves/pref_post_incon_diff.rds")
-
-pref_post_incon_diff<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefInconWebppl , sep='\n'),
-  data = pref_data%>%filter(condition == "different_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-saveRDS(pref_post_incon_diff, "../saves/pref_post_incon_diff.rds")
-
-```
-
-```{r}
-# Same Speaker
-# congruent
-
-prefPostPredConSame <- pref_post_con_same%>%
-  spread(Parameter, value)
-
-pref_post_con_same <- pref_post_con_same%>%
-  mutate(chain = factor(Chain))%>%
-  mutate(alignment = "congruent",
-         condition = "same speaker")
-
-x_plot <- seq(0, 2, by = 0.1)
-
-post_predictions_con_same <- sapply(1:length(prefPostPredConSame$pref_int), function(idx) {
-            plogis(prefPostPredConSame$pref_int[idx] + prefPostPredConSame$pref_slope[idx] * x_plot)
-        })
-
-colnames(post_predictions_con_same) <- 1:length(prefPostPredConSame$pref_int)
-plot_post_data_con_same <- as.data.frame(cbind(x_plot, post_predictions_con_same))
-plot_post_data_con_same <- melt(plot_post_data_con_same, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")%>%
-  mutate(alignment = "congruent",
-         condition = "same speaker")
-
-# Same Speaker
-# incongruent
-
-prefPostPredInconSame <- pref_post_incon_same%>%
-  spread(Parameter, value)
-
-pref_post_incon_same <- pref_post_incon_same%>%
-  mutate(chain = factor(Chain))%>%
-  mutate(alignment = "incongruent",
-         condition = "same speaker")
-
-post_predictions_incon_same <- sapply(1:length(prefPostPredInconSame$pref_int), function(idx) {
-            plogis(prefPostPredInconSame$pref_int[idx] + prefPostPredInconSame$pref_slope[idx] * x_plot)
-        })
-
-colnames(post_predictions_incon_same) <- 1:length(prefPostPredInconSame$pref_int)
-plot_post_data_incon_same <- as.data.frame(cbind(x_plot, post_predictions_incon_same))
-plot_post_data_incon_same <- melt(plot_post_data_incon_same, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")%>%
-  mutate(alignment = "incongruent",
-         condition = "same speaker")
-
-# Different speaker
-# congruent
-prefPostPredConDiff <- pref_post_con_diff%>%
-  spread(Parameter, value)
-
-pref_post_con_diff <- pref_post_con_diff%>%
-  mutate(chain = factor(Chain))%>%
-  mutate(alignment = "congruent",
-         condition = "different speaker")
-
-post_predictions_con_diff <- sapply(1:length(prefPostPredConDiff$pref_int), function(idx) {
-            plogis(prefPostPredConDiff$pref_int[idx] + prefPostPredConDiff$pref_slope[idx] * x_plot)
-        })
-
-colnames(post_predictions_con_diff) <- 1:length(prefPostPredConDiff$pref_int)
-plot_post_data_con_diff <- as.data.frame(cbind(x_plot, post_predictions_con_diff))
-plot_post_data_con_diff <- melt(plot_post_data_con_diff, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")%>%
-  mutate(alignment = "congruent",
-         condition = "different speaker")
-
-# Different speaker
-# incongruent
-prefPostPredInconDiff <- pref_post_incon_diff%>%
-  spread(Parameter, value)
-
-pref_post_incon_diff <- pref_post_incon_diff%>%
-  mutate(chain = factor(Chain))%>%
-  mutate(alignment = "incongruent",
-         condition = "different speaker")
-
-post_predictions_incon_diff <- sapply(1:length(prefPostPredInconDiff$pref_int), function(idx) {
-            plogis(prefPostPredInconDiff$pref_int[idx] + prefPostPredInconDiff$pref_slope[idx] * x_plot)
-        })
-
-colnames(post_predictions_incon_diff) <- 1:length(prefPostPredInconDiff$pref_int)
-plot_post_data_incon_diff <- as.data.frame(cbind(x_plot, post_predictions_incon_diff))
-plot_post_data_incon_diff <- melt(plot_post_data_incon_diff, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")%>%
-  mutate(alignment = "incongruent",
-         condition = "different speaker")
-
-# combining datasets
-
-pref_post <- bind_rows(
-  pref_post_con_diff,
-  pref_post_incon_diff,
-  pref_post_con_same,
-  pref_post_incon_same
-)
-
-plot_post_data <- bind_rows(
-  plot_post_data_incon_same,
-  plot_post_data_con_same,
-  plot_post_data_incon_diff,
-  plot_post_data_con_diff
-)
-
-plot_post_data_mean <- plot_post_data%>%
-  group_by(alignment,condition,x_plot)%>%
-  summarise(mean = mean(y_plot),
-            ci_upper = hdi_upper(y_plot),
-            ci_lower = hdi_lower(y_plot))
-```
-
-```{r}
-
-ggplot(plot_post_data) + 
-  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey", alpha = 0.2) + 
-  geom_ribbon(data = plot_post_data_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
-  geom_line(data = plot_post_data_mean, aes(x_plot, mean), col = "black") + 
-  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
-  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
-  facet_grid(alignment~condition)+
-  theme_few()
-
-```
-
-```{r}
-ggplot(data = pref_post, aes(x = value, fill = chain)) +
-  geom_density(alpha = 0.3)+
-  facet_grid(Parameter ~ alignment*condition)+
-  theme_few()
-```
-
-# 2 vs object world
-
-```{r posterior preference congruent}
-postPrefConWebppl2 <- '
-
-var prefData = dataFromR
-var priorProbs = []
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    map(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [1-priorReg, priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-     // display(JSON.stringify(priorReg))
-
-    }, prefData)
-
-  return extend({pref_int: pref_int, pref_slope: pref_slope})
-}
-'
-```
-
-```{r}
-
-# Same Speaker
-# congruent
-#pref_post_con_same <- readRDS("../saves/pref_post_con_same.rds")
-
-pref_post_con_same2<- webppl(
-  program_code = paste(rsaUtils, rsaModel, postPrefConWebppl2 , sep='\n'),
-  data = pref_data%>%filter(condition == "same_speaker")%>%mutate(minage = min(age_num)), 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 3,
-  cores = 3,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-prefPostPredConSame2 <- pref_post_con_same2%>%
-  spread(Parameter, value)
-
-pref_post_con_same2 <- pref_post_con_same2%>%
-  mutate(chain = factor(Chain))%>%
-  mutate(alignment = "congruent",
-         condition = "same speaker")
-
-x_plot <- seq(0, 2, by = 0.1)
-
-post_predictions_con_same2 <- sapply(1:length(prefPostPredConSame2$pref_int), function(idx) {
-            plogis(prefPostPredConSame2$pref_int[idx] + prefPostPredConSame2$pref_slope[idx] * x_plot)
-        })
-
-colnames(post_predictions_con_same2) <- 1:length(prefPostPredConSame2$pref_int)
-plot_post_data_con_same2 <- as.data.frame(cbind(x_plot, post_predictions_con_same2))
-plot_post_data_con_same2 <- melt(plot_post_data_con_same2, id.vars = "x_plot", variable.name = "iteration", 
-        value.name = "y_plot")%>%
-  mutate(alignment = "congruent",
-         condition = "same speaker",
-         world = "2 objects")
-
-x <- bind_rows(
-  plot_post_data_con_same2,
-  plot_post_data_con_same
-)
-
-x_mean <- x%>%
-  group_by(world,x_plot)%>%
-  summarise(mean = mean(y_plot),
-            ci_upper = hdi_upper(y_plot),
-            ci_lower = hdi_lower(y_plot))
-
-a <- prefPostPredConSame2%>%
-  summarise(mean_int = mean(pref_int),
-            mean_slope = mean(pref_slope))%>%
-  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
-  mutate(x = x_plot,
-         world = "2 objects")
-
-b <- prefPostPredConSame%>%
-  summarise(mean_int = mean(pref_int),
-            mean_slope = mean(pref_slope))%>%
-  expand(y = plogis(mean_int + mean_slope * x_plot))%>%
-  mutate(x = x_plot,
-         world = "3 objects")
-
-c <- bind_rows(a,b)
-
-```
-
-```{r}
-
-ggplot(x) + 
-  geom_line(aes(x_plot, y_plot, group = iteration), col = "grey", alpha = 0.2) + 
-  geom_ribbon(data = x_mean, aes(x =x_plot, ymin = ci_lower, ymax = ci_upper), fill = "darkgreen", alpha = 0.3) +
-  geom_line(data = x_mean, aes(x_plot, mean), col = "black") + 
-  geom_line(data = c, aes(x, y), col = "red") + 
-  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0:2), labels = c(3:5)) +
-  scale_y_continuous(limits = c(0, 1), name="P in favor of preferred object")+
-  facet_grid(~world)+
-  theme_few()
-
-```
+```
+
+```{r, echo = F, fig.width= 8}
+ggarrange(so_prior_plot, pref_prior_plot)
+```
+
+There is no information in the priors. All structure in the models further down comes from the data
 
 # Model Predictions
+
+## Model code for predictions
 
@@
 }
-var prefData = filter(dataFromR, {experiment: "preference"})
-var infData = filter(dataFromR, {experiment: "informativeness"})
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
 
 // make finer grained as needed
-var binned_age_range = _.range(0, 2, 0.1)
+var binned_age_range = _.range(0, 2, 0.05)
 
@@
 
-//var priorProbs = []
-
 var logistic = function(x) {1 / (1 + Math.exp(-x))}
@@
 
-    var conditionData = filter(prefData, {condition: cndtn})
+    var conditionData = _.filter(prefData, {condition: cndtn})
 
@@
 
-     // display(JSON.stringify(priorReg))
-
     }, conditionData)
@@
 
-  var diff_speaker_params = filter(pref_params, 
+  var diff_speaker_params = _.filter(pref_params, 
         {condition: "different_speaker"})[0]
 
-  var same_speaker_params = filter(pref_params, 
+  var same_speaker_params = _.filter(pref_params, 
         {condition: "same_speaker"})[0]
@@
     return extend(
-    //diff_speaker_params, same_speaker_params, 
+    // diff_speaker_params, same_speaker_params, 
       {
-     // diff_priorReg,
-    //  same_priorReg,
-    //  speakerOptimality,
+      diff_priorReg,
+      same_priorReg,
+      speakerOptimality,
       rsaPredictions_diff_cong,
@@
       age_bin,
-    //  so_slope,
-    //  so_int
+      so_slope,
+      so_int,
+
     })
@@
 
+## Sampling predictions
+
+Taking samples and munging the data.
+
 ```{r combined model predictions}
-model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
-  data = pre_data, 
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  cores = 1,
-  inference_opts = list(method = "MCMC", samples = 20, burn = 1, verbose = T)
+
+model_pred <- readRDS("../saves/kids_model_predictions.rds")
+
+# model_pred<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+#   data = pre_data,
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
+# )
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+kids_model_pred <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
+kids_model_pred_so <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
+
+kids_model_pred_prior <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
+  gather(condition, prop_preferred, -iteration,-age_bin)%>%
+  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
+
+```
+## Sanity checks
+
+### Model based speaker optimality by age
+
+```{r plot so model pred, echo = F}
+
+plot_model_pred_so <- kids_model_pred_so%>%
+  group_by(age_bin)%>%
+  summarise(mean = mean(speakerOptimality),
+            lci = hdi_lower(speakerOptimality),
+            uci = hdi_upper(speakerOptimality))
+
+pred_so_plot <- ggplot(data = plot_model_pred_so) +
+  geom_line(data = kids_model_pred_so,aes(age_bin, speakerOptimality, group = iteration), col = "grey", alpha = 0.3) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci), fill = "green", alpha = .2) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
+  ggtitle("Speaker optimality model")+
+  #facet_wrap(~chain)+
+  theme_few()+
+  coord_fixed(ratio=1/4)
+
+```
+
+```{r, echo = F, fig.width= 8}
+ggarrange(pred_so_plot, plot_inf)
+```
+
+Here we estimate the speaker optimality parameter that best captures the data for the different ages. The model based estimate nicely captures the developmental trend.
+
+```{r plot prior model pred, echo = F}
+plot_model_pred_prior <- kids_model_pred_prior%>%
+  group_by(age_bin,condition)%>%
+  summarise(mean = mean(prop_preferred),
+            lci = hdi_lower(prop_preferred),
+            uci = hdi_upper(prop_preferred))
+
+pred_prior_plot <- ggplot(data = plot_model_pred_prior) +
+  geom_line(data = kids_model_pred_prior,aes(age_bin, prop_preferred, group = paste(iteration,condition, sep= ""), col = condition), alpha = 0.05) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = condition), alpha = .5) +
+  geom_line(aes(age_bin, mean, group = condition), col = "black", size = 0.4, alpha = 1) + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  scale_y_continuous(limits=c(-0.05,1.05), name="Proportion Expected Choice")+
+  geom_hline(yintercept = 0.5, lty=2)+
+  theme_few()+
+  ggtitle("Preference model")+
+  coord_fixed(ratio = 2)+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
+### Model based priors by age
+
+```{r, echo= F, fig.width= 10}
+ggarrange(pred_prior_plot, plot_pref, common.legend = T, legend = "right")
+```
+
+The model accurately captures the the difference between conditions as well as the developmental trend we see in the data.
+
+## RSA Model Predictions
+
+These are the predictions from the RSA model which takes in the age specific speaker optimality parameter and the age specific priors.
+The priors are converted from 2-object world into 3-object world before going into the model.
+This corresponds to the way we handled the priors for adults.
+
+```{r plot RSA model predictions, echo = F, fig.width= 10}
+
+  plot_model_pred <- kids_model_pred %>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
+
+pred_plot <- ggplot(plot_model_pred)+
+  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
+  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion Expected Choice")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  guides(col = F)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+```
+
+```{r, echo= F, fig.width= 10, fig.height = 8}
+pred_plot
+```
+
+## No Prior Model Predictions
+
+```{r, include = F}
+
+no_prior_pred <- bind_rows(
+  kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "same_speaker",
+                              Alignment = "congruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "different_speaker",
+                              Alignment = "congruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "same_speaker",
+                              Alignment = "incongruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "different_speaker",
+                              Alignment = "incongruent")
+  ) %>%
+  mutate(prop_informative = plogis(so_int+so_slope*age_bin))
+
+no_prior_plot <- no_prior_pred %>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
+
+plot_no_prior <- ggplot(no_prior_plot)+
+  geom_line(data = no_prior_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
+  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion Expected Choice")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  guides(col = F)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+```
+
+```{r, echo = F, fig.width= 10, fig.height = 8}
+plot_no_prior
+```
+
+## Prior Only Model
+
+```{r prior only model}
+priorOnlyWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.05)
+
+var all_conditions = levels(prefData, "condition")
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+
+  var pref_params = map(function(cndtn){
+
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+    }, conditionData)
+
+    return {pref_int, pref_slope, condition: cndtn}
+
+  }, all_conditions)
+
+  var diff_speaker_params = _.filter(pref_params, 
+        {condition: "different_speaker"})[0]
+
+  var same_speaker_params = _.filter(pref_params, 
+        {condition: "same_speaker"})[0]
+
+  var predictions_by_age = map(function(age_bin){
+
+    var diff_priorReg = logistic(diff_speaker_params.pref_int +
+            diff_speaker_params.pref_slope * age_bin)
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var same_priorReg = logistic(same_speaker_params.pref_int +
+            same_speaker_params.pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+ var priorPredictions_diff_con = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_congruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+  var priorPredictions_diff_incon = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+ var priorPredictions_same_con = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_congruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+  var priorPredictions_same_incon = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+     var prior_diff_con = Math.exp(priorPredictions_diff_con.score(1))
+var prior_diff_incon = Math.exp(priorPredictions_diff_incon.score(1))
+     var prior_same_con = Math.exp(priorPredictions_same_con.score(1))
+var prior_same_incon = Math.exp(priorPredictions_same_incon.score(1))
+
+    return extend(
+      {prior_diff_con,
+prior_diff_incon,
+prior_same_con,
+prior_same_incon,
+    age_bin})
+
+  }, binned_age_range)
+
+  return predictions_by_age 
+}
+'
+```
+
+```{r}
+
+prior_only_predictions <- readRDS("../saves/prior_only_predictions.rds")
+
+# prior_only_predictions<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, priorOnlyWebppl , sep='\n'),
+#   data = pre_data,
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 3,
+#   cores = 3,
+#   inference_opts = list(method = "MCMC", samples = 1000, burn = 200, verbose = T)
+# )
+
+#saveRDS(prior_only_predictions, "../saves/prior_only_predictions.rds")
+
+prior_only_model <- prior_only_predictions %>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3000,each = 40))%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "con", "congruent","incongruent"))
+
+```
+
+```{r plot prior only model predictions, include= F}
+
+plot_prior_only_pred <- prior_only_model %>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
+
+prior_only_plot <- ggplot(plot_prior_only_pred)+
+  geom_line(data = prior_only_model,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
+  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion Expected Choice")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
+```{r, echo = F, fig.width= 10, fig.height = 8}
+prior_only_plot
+```
+
+## Comparing model predictions
+
+```{r}
+model_comp_mean_ci <- bind_rows(
+plot_model_pred%>%ungroup()%>%mutate(model = "RSA"), 
+plot_prior_only_pred%>%ungroup()%>%mutate(model = "Prior Only"),
+no_prior_plot%>%ungroup()%>%mutate(model = "No Prior")
 )
 
-```
+model_comp <- bind_rows(
+kids_model_pred %>%mutate(model = "RSA"),
+prior_only_model%>%mutate(model = "Prior Only"),
+no_prior_pred%>%select(-so_slope,-so_int,-speakerOptimality)%>%mutate(model = "No Prior")
+  )
+
+```
+
+```{r, include = F}
+pred_plot <- ggplot(model_comp_mean_ci)+
+  geom_line(data = model_comp,aes(age_bin, prop_informative, group = paste(iteration,Speaker,model, sep= ""), col = model),  alpha = 0.01) + 
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_viridis_d()+
+  scale_fill_viridis_d()
+```
+
+```{r, echo = F, fig.width= 10, fig.height = 8}
+pred_plot
+```
+
+```{r, include = F}
+#ggsave("../graphs/no_prior_prior_only_model_predictions.pdf", width = 10, height = 8, scale = 1)
+```
+
+# Model vs data
+
+```{r import data, include = F}
+###
+library(tidyverse)
+library(knitr)
+library(langcog)
+library(ggthemes)
+library(jsonlite)
+library(readxl)
+
+## importing data
+files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,42,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+raw_data <- raw_data %>%
+  mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
+         subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
+         subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
+
+raw_data%>%
+  #group_by(paste(subid,test_date))%>%
+  group_by(subid)%>%
+  summarise(n= n())
+
+unique(raw_data$subid)
+
+log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "ex3p")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+#unique(log$subid)
+sum(log$keep_drop == "drop")
+
+d <- left_join(raw_data,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
+         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+
+```
+
+## Plot comparing model and data by continous age
+```{r comparison plot by age, echo= FALSE}
+
+p_data <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3,
+         Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
+         Alignment = alignment)%>%
+  group_by(Speaker, alignment ,age_bin, subid)
+
+ggplot(model_comp_mean_ci)+
+  geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1, linetype = 2) + 
+  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
+## Correlation plot
+```{r}
+
+data <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
+         Alignment = alignment)%>%
+  group_by(Speaker, Alignment ,subage) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         Data_ci_lower  = qbeta(.025, a, b),
+         Data_ci_upper = qbeta(.975, a, b),
+         Data = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+model <- model_comp %>%
+  mutate(subage = ifelse(age_bin<1,"3","4"))%>%
+  group_by(model,Speaker,Alignment,subage)%>%
+  summarise(Model = mean(prop_informative),
+            Model_ci_lower = hdi_lower(prop_informative),
+            Model_ci_upper = hdi_upper(prop_informative))
+
+cor_plot <- model %>%
+  ungroup()%>%
+  mutate(Data = rep(data$Data,3),
+         Data_ci_lower = rep(data$Data_ci_lower,3),
+         Data_ci_upper  =rep(data$Data_ci_upper,3))
+
+ggplot(data = cor_plot,aes(x = Model, y = Data, col = subage)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  coord_fixed()+
+  stat_cor(method = "pearson", label.x = 0.1, label.y = 0.9, aes(x = Model, y = Data), inherit.aes = F)+
+  facet_grid(~model)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 10) + 
+  scale_colour_solarized()
+
+cor.test(cor_plot$Model,cor_plot$Data)
+```

### 2019-01-09 stats/kids/kids_summary_inf_pilot.Rmd
first draft CogSci paper

--- 2018-10-29 stats/mcc_summary_inf_pilot_kids.Rmd
@@
 ## round 1 adult design
-d_round_1 <- read_csv(file="kids_inf.data.csv")%>%
+d_round_1 <- read_csv(file="../data/kids_inf.data.csv")%>%
   filter(trial != "train", control == "false")%>%
@@
 
-```{r plot, echo = FALSE, warning = FALSE, fig.width=12}
+```{r plot, echo = FALSE, warning = FALSE, fig.width=12, fig.height=3}
 
@@
 ggplot() +
-  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2), position = position_jitterdodge(jitter.width = 0.05, jitter.height = 0.05, dodge.width = 0.5))+
+  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = 0.5))+
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_grid(subage~experiment)+
+  theme_few(base_size = 20) +
+  facet_grid(~experiment)+
   ylim(-0.05,1.05)+
@@
   theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
+```
+
+```{r}
+ggsave("../graphs/kids_inf_pilot.png", width = 12, height = 3, scale = 1.5)
 ```

### 2019-01-22 papers/cogsci2019/CogSCi2019_new.Rmd
CogSci paper new template

--- 2019-01-09 papers/cogsci2019/cogsci2019.Rmd
@@
 
-abstract: 
-    "Pragmatic inferences are an integral part of language comprehension and learning.
+abstract: >
+    Pragmatic inferences are an integral part of language comprehension and learning.
 To recover the intended meaning of an utterance, listeners need to balance and integrate different sources in information.
@@
 This research shows that listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian cognitive models.
-Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension."
+Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension.
 
-keywords:
-    "Pragmatics; Word learning; Common ground; Bayesian models"
+keywords: >
+    Pragmatics; Word learning; Common ground; Bayesian models
 
 output: cogsci2016::cogsci_paper
+#final-submission: \cogscifinalcopy
 ---

### 2019-01-22 papers/cogsci2019/CogSCi2019_new.tex
CogSci paper new template

--- 2019-01-09 papers/cogsci2019/cogsci2019.tex
@@
 % cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
+\usepackage{apacite}
+
+% KM added 1/4/18 to allow control of blind submission
 
@@
 
-\title{Integrating Common Ground and Informativeness in Pragmatic Word Learning}
+\title{How to Make a Proceedings Paper Submission}
 
@@
 informativeness inference (prior only model). To capture the idea that
-behavioral data is to some degree noisy, all models included a ``noise
-parameter'', which reflects that, with a certain probability,
-participants respond randomly instead of in line with the intended
-manipulation on a given trial. Noise parameters are estimated based on
-the data.
+behavioral data is to some degree noisy, all models included a noise
+parameter, which reflects that, with a certain probability, participants
+respond randomly instead of in line with the intended manipulation on a
+given trial. Noise parameters are estimated based on the data.
 
@@
 
+\bibliographystyle{apacite}
+
 \end{document}

### 2019-01-22 stats/kids/kids_Ex3_pref.Rmd
CogSci paper new template

@@
 author: "Manuel Bohn"
-output: html_document
+output:
+  html_document:
+    code_folding: hide
 ---
@@
 library(readxl)
+library(coda)
+
+estimate_mode <- function(s) {
+  d <- density(s)
+  return(d$x[which.max(d$y)])
+}
+
+hdi_upper<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","upper"])
+}
+
+hdi_lower<- function(s){
+  m <- HPDinterval(mcmc(s))
+  return(m["var1","lower"])
+}
 
@@
          subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
-
-raw_data%>%
-  #group_by(paste(subid,test_date))%>%
-  group_by(subid)%>%
-  summarise(n= n())
-
-unique(raw_data$subid)
+#unique(raw_data$subid)
 
@@
 
-unique(d$check_age)
+```
+
+## Overview
+
+This is what the study looked like.
+The animal first commented on an object on one side, then on an object on the other side (preference manipulation) and then disappeared.
+Then either the same or a different animal returned (speaker change manipulation), turned to the tree with the two objects and said it had a e.g.
+"dax".
+Then, two new trees appeared, each with one type of object and children were asked to pick the tree with the "dax".
+
+```{r setup, echo = F, fig.cap="Screenshot from the experiment", fig.align = "center"}
+
+knitr::include_graphics("../../papers/figures/kids_ex3_setup.png")
 
@@
 
-# Sample size per age bin
+Manipulations:
 
-```{r kids per age group,echo = F }
+* Age: Measured continuous 
+* Speaker: same or different
+* Alignment: congruent(preferred object = less frequent) or in-congruent (preferred = more frequent)
 
-d %>%
-  group_by(subage,subid)%>%
-  summarise(n_trials = n())%>%
-  mutate(full_data = ifelse(n_trials == 10,"yes","no"))%>%
-  group_by(subage)%>%
-  summarise(n = length(unique(subid)),
-            n_full_data = sum(full_data == "yes"))%>%
-  knitr::kable(digits = 2)
+Crossing this results in four conditions (cells) per age group.
+Data was collected within subjects, with two (one if they decided to opt out earlier) trials per cell (combination of alignment and speaker).
 
-```
+Total N = `r length(unique(d$subid))`. We amended the preregistration saying that we want 80 data points per cell. The table below shows that we got this.
 
-# Datapoints per cell
-
-```{r kids per age group,echo = F }
-
+```{r kids per age group, echo = F }
 d %>%
@@
   group_by(subage,speaker,alignment)%>%
-  summarise(datapoints = n())%>%
+  summarise(n = length(unique(subid)),
+            datapoints = n())%>%
   knitr::kable(digits = 2)
-
 ```
 
-# Plot filler by age
+### Filler trials
 
-```{r plot by age, echo= FALSE}
+Filler trials by age.
+Each child started with two filler trials.
+In these trials, each tree only had one feature.
+Children had no problem learning words in unambiguous cases, showing they get the basic procedure.
+
+```{r filler by age, echo= FALSE, fig.height=3,fig.width=3}
 pf1 <- d %>%
@@
 ggplot() +
-  geom_jitter(data = pf1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
-  geom_pointrange(data = pf2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = pf1, aes(x = subage, y = correct,  alpha = .2),width = .1,height = .025)+
+  geom_pointrange(data = pf2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
+  guides(alpha = F)
 ```
 
-# Plot by age group
+## Comparison to chance by age bin
 
-```{r plot by age, echo= FALSE}
+### Plot
+
+For the plot, data is aggregated within individual and age bin.
+Looking at the data this way, it looks like 3-year-olds do not care about speaker and alignment but have a slight overall tendency to pick the more informative object.
+4-year-olds, on the other hand, seem to behave quite differently in the different cells.
+```{r plot by age binned}
 
@@
   guides(alpha = F)+ 
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  scale_colour_solarized(name="Alignment")
 ```
 
-# Plot by age continous
+### Model within each cell
 
-```{r plot by age, echo= FALSE}
+Given the unequal number of trials per subject, we pre-registered models for the comparison to chance within each cell, testing the intercept against 0.
+Model structure was: `correct_inf ~ 1 + (1|subid) + (1|agent)`.
+Results are in line with what you see in the plot above.
+
+```{r chance_comp, warning=F, message=F}
+library(lme4)
+
+mod <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(subage,speaker,alignment) %>%
+  do(models = glmer(correct_inf ~ 1+ (1|subid) + (1|agent),data=., family=binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
+
+library(broom)
+
+tidy(mod, models) %>%
+  filter(term =="(Intercept)") %>%
+  select(-term, -group)%>%
+  kable(digits = 2)
+```
+
+## Plot by age continous
+
+Here is the data plotted with age continuous. Regression lines and CIs are based on loess fits.
+
+```{r plot by age}
 
@@
          trial != "filler2")%>%
-  group_by(speaker, alignment ,age_num, subid) %>%
-  summarise(correct = mean(correct_inf))
+  group_by(speaker, alignment ,age_num, subid)
 
@@
   geom_jitter(width = .025,height = .025, alpha = .2)+
-  geom_smooth(method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  geom_smooth(method = "loess",  se = T,  alpha = .5, size = .4, span = 2)+
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="Age",y="Proportion Expected Choice")+
+  labs(x="Age",y="Proportion more informative")+
   theme_few() +
@@
   ylim(-0.05,1.05)+
-  guides(alpha = F)+
-  coord_fixed(ratio = 2)
+  guides(alpha = F)
 
@@
 
-```{r model}
+## GLMM
+
+The goal of the frequentest model was to see if the three manipulations (age, speaker and alignment have an effect).
+The model converges as pre-registered: `correct_inf ~ age_num*speaker*alignment + (speaker*alignment | subid) + (age_num*speaker*alignment | agent)`.
+
+The significant 3-way interaction shows that all three components matter. This is good news, showing that all of the things we hypothesized to be important actually affected children's behavior.
+
+```{r model, cache = T, warning=F, message=F}
 
@@
 
-summary(mex3)
+tidy(mex3) %>%
+  filter(group =="fixed") %>%
+  select(-group)%>%
+  kable(digits = 2)
+
 ```
 
-```{r chance_comp}
-mod <- d %>%
+## Comparing data to model
+
+### Models vs data by age contious
+
+The black line is the loess fit based on the data (same as above).
+Models are shown in different colors.
+It looks like the RSA model is making the best predictions (relative to the others).
+The fit is far from perfect, but I guess that was expected.
+We will eventually compare models using Bayes Factors.
+
+```{r comparison plot by age,warning=F, message=F, fig.height= 6, fig.width=10}
+
+p_data <- d %>%
   filter(trial != "filler1",
          trial != "filler2")%>%
-  group_by(subage,speaker,alignment) %>%
-  do(models = glmer(correct_inf ~ 1+ (1|subid),data=., family=binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
+  mutate(age_bin = age_num - 3,
+         Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
+         Alignment = alignment)%>%
+  group_by(Speaker, alignment ,age_bin, subid)
 
-library(broom)
+kids_model_comp_mean_ci <- readRDS("../saves/kids_model_comp_mean_ci.rds")
 
-tidy(mod, models) %>%
-  filter(term =="(Intercept)")
+ggplot(kids_model_comp_mean_ci)+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = .5, linetype = 2) + 
+  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.8, method = "glm", method.args = list(family = "binomial"), se = T,  alpha = .7)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few(base_size = 20)+
+  scale_color_viridis_d(direction = -1)+
+  scale_fill_viridis_d(direction = -1)
 ```
+
+```{r, include = F}
+ggsave("../graphs/kids_all_model.pdf", width = 11.1, height = 8, scale = 1)
+```
+
+### Correlation plot by age bin
+
+Not sure if this makes much sense: I binned and averaged the model predictions and the data by age to get correlation plots.
+Even though the correlation is higher for the prior only model, the predictions are systematically off.
+```{r, cache = T, warning=F, message=F}
+
+data <- d %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
+         Alignment = alignment)%>%
+  group_by(Speaker, Alignment ,subage) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         Data_ci_lower  = qbeta(.025, a, b),
+         Data_ci_upper = qbeta(.975, a, b),
+         Data = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+kids_model_comp <- readRDS("../saves/kids_model_comp.rds")
+
+model <- kids_model_comp %>%
+  mutate(subage = ifelse(age_bin<1,"3","4"))%>%
+  group_by(model,Speaker,Alignment,subage)%>%
+  summarise(Model = mean(prop_informative),
+            Model_ci_lower = hdi_lower(prop_informative),
+            Model_ci_upper = hdi_upper(prop_informative))
+
+cor_plot <- model %>%
+  ungroup()%>%
+  mutate(Data = rep(data$Data,3),
+         Data_ci_lower = rep(data$Data_ci_lower,3),
+         Data_ci_upper  =rep(data$Data_ci_upper,3))
+
+library(ggpubr)
+
+ggplot(data = cor_plot,aes(x = Model, y = Data, col = subage)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  coord_fixed()+
+  stat_cor(method = "pearson", label.x = 0.1, label.y = 0.9, aes(x = Model, y = Data), inherit.aes = F)+
+  facet_grid(~model)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 10) + 
+  scale_colour_solarized()
+```

### 2019-01-22 stats/kids/kids_inf_2.Rmd
CogSci paper new template

--- 2018-11-08 stats/mcc_inf.kids.Rmd
@@
 ---
-title: "MCC Informativeness Kids 2"
+title: "MCC Informativeness Kids - Additional data"
 author: "Manuel Bohn"
@@
 ## importing data
-files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
+files <- dir("~/Work/MCC/git-mcc/kids_info_data_2/")
 
@@
 for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_data_2/",f,sep="")
   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,45,str_length(jf)-11)
+  date <- str_sub(jf,47,str_length(jf)-11)
   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
@@
 
+length(unique(raw_data$subid))
+
 d_raw <-raw_data %>%
-  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
-         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
-         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
-         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
-         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
-         experiment = "mcc_kids_inf_2")
+  mutate(test_date = as.Date(test_date),
+         experiment = "mcc_kids_inf_2_2")
 
-log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "inf")%>%
+log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "inf2")%>%
   select(subid,experimenter,keep_drop,sex,dob)
@@
 
-pf1 %>%
-  filter(correct == 0)
+length(unique(d$subid))
+
+write_csv(d, "data/kids_inf_2_data.csv")
 

### 2019-01-28 papers/cogsci2019/cogsci2019.Rmd
cogsci draft

@@
 
-abstract: 
-    "Pragmatic inferences are an integral part of language comprehension and learning.
-To recover the intended meaning of an utterance, listeners need to balance and integrate different sources in information.
-In a series of experiments, we studied how listeners integrate general expectations about speakers with expectations that are specific to the interactional history with  a particular speaker.
-We used a Bayesian cognitive model to formalize the integration process.
-In Experiment 1 and 2 we replicated findings showing that listeners make inferences based on general and speaker specific expectations.
-Using the empirical measurements from these experiments, we generated model predictions about how they should be integrated.
-We tested these predictions in Experiment 3, which combined both expectations in a single design.
+abstract: >
+    Pragmatic inferences are an integral part of language learning and comprehension.
+To recover the intended meaning of an utterance, listeners need to balance and integrate different sources of contextual information.
+In a series of experiments, we studied how listeners integrate general expectations about speakers with expectations specific to their interactional history with a particular speaker.
+We used a Bayesian pragmatics model to formalize the integration process.
+In Experiments 1 and 2, we replicated previous findings showing that listeners make inferences based on speaker-general and speaker-specific expectations.
+We then used the empirical measurements from these experiments to generate model predictions about how the two kinds of expectations should be integrated, which we tested in Experiment 3.
 Experiment 4 replicated and extended Experiment 3 to a broader set of conditions.
-Across both experiments, listeners based their inferences on both types of expectations.
-Overall, model predictions and data were highly correlated.
-Predictions from the model incorporating both types of information described listeners’ behavior better compared to alternative models based on only one type of information.
-This research shows that listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian cognitive models.
-Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension."
+In both experiments, listeners based their inferences on both types of expectations.
+We found that model performance was also consistent with this finding; with better fit for a model which incorporated both general- and specific-information compared to baselines incorporating only one type.
+Listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian models of pragmatic reasoning.
+Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension.
 
-keywords:
-    "Pragmatics; Word learning; Common ground; Bayesian models"
+keywords: >
+    Pragmatics; Word learning; Common ground; Bayesian models
 
 output: cogsci2016::cogsci_paper
+#final-submission: \cogscifinalcopy
 ---
@@
 
-One of the most astonishing features of natural language is that it allows us to communicate precise meanings despite the fact that each utterance is inherently ambiguous.
-The conventional couplings between sounds (words) and objects constrain what a speaker may mean by an utterance.
-However, the intended meaning of the utterance is not reducible to the words that are contained in it.
-For example, the same utterance (“Look, there it is!”) could be intended to refer to very different things depending on whether someone is searching for their wallet or looking for the bus stop.
-It takes additional pragmatic inferences to recover the intended meaning [@levinson2000presumptive].
+One of the most astonishing features of natural language is that it allows us to communicate precise meanings despite the fact that most utterances are inherently ambiguous.
+While the conventional mapping between sounds (words) and objects constrain what a speaker may mean by an utterance, the intended meaning of the utterance is not reducible to the words that are contained in it.
+It takes additional pragmatic inference to recover the intended meaning [@levinson2000presumptive].
 
@@
 On the one hand, speakers and listeners have the general expectation that their partner communicates in an informative and relevant way [@sperber2001relevance].
-Grice [-@grice1991studies] summarised this expectation via the cooperative principle: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the principle highlights a second type of expectation: interlocutors expect each other to produce and interpret utterances in light of the shared common ground between them [@clark1996using].
-Common ground refers to bits of information that are assumed to be shared, either because they result from joint experience or were otherwise grounded [@bohn2018common].
-The nature of the corresponding expectations vary with the individuals involved.
+Grice [-@grice1991studies] summarised this expectation via the “Cooperative Principle”: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the Cooperative Principle describes a second type of expectation: interlocutors expect each other to produce and interpret utterances *in light of the shared common ground between them* [@clark1996using].
+Common ground refers to bits of information that are assumed to be shared, either because they were mentioned over the course of the conversation or grounded through some form of joint experience [@bohn2018common].
+Note that by its very nature, common ground may vary with the individuals involved in a particular conversation.
 
-Both general and common ground expectations can support children’s word learning [@clark2009first; @tomasello2009constructing].
-On the one hand, children have been found to learn novel words by assuming that the speaker is informative [@frank2014inferring].
+These same general and specific expectations can support children’s word learning [@clark2009first; @tomasello2009constructing].
+On the one hand, children have been found to learn novel words by assuming speakers are generally informative [@frank2014inferring].
 That is, in the absence of any prior interaction with the speaker, children interpreted a novel word as referring to the most informative referent.
-On the other hand, children learn novel words by relying on common ground expectations [@akhtar1996role; @bohn2018common].
+On the other hand, children use conversation-specific common ground expectations to decide which object a specific speaker is referring to when they use a novel word [@akhtar1996role].
 For example, when a speaker expressed preference for a particular object, children expect a novel word from the same speaker to refer to the previously preferred object [@saylor2009preschoolers].
 
-But how are general and common ground expectations integrated with one another?
+But how do listeners integrate general and common ground-related expectations during word learning?
 Are pragmatic inferences strengthened additively when both support a particular interpretation?
 How are they weighed when they are in conflict?
-The rational speech act (RSA) framework [@frank2012predicting] offers a formal framework for this information integration problem.
-RSA models are characterized by their recursive structure in which speakers and listeners reason about each other’s interpretation of utterances in context.
-RSA models have been found to make accurate quantitative predictions about various forms of pragmatic language use and word learning [@goodman2016pragmatic].
-However, a comprehensive treatment of how general and common ground expectations are integrated, is still missing.
+The Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic] offers a formal framework for addressing this information integration problem.
+RSA models are characterized by a recursive structure in which a pragmatic listener tries to uncover a speaker’s intended meaning by assuming the speaker chose their utterance in order to get a naive listener to recover their intended meaning.
+RSA models have made accurate quantitative predictions about various forms of pragmatic language use and word learning [@goodman2016pragmatic].
+However, a comprehensive treatment of how general and common ground expectations are integrated is still missing.
 
 Within RSA models, each agent in this recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
-A natural locus within these models for information integration is the tradeoff between the prior probability of a particular referent (the degree to which it is in common ground) and the likelihood of that referent given the current utterance (general pragmatic interpretation).
+The speaker-general informativeness expectation is already encoded in the structure of the model: Speakers produce utterances to aid the listener in disambiguating referents.
+We operationalize speaker-specific, common ground information as the shared prior probability of referents in the context of the utterance.
+Thus, a natural locus for information integration within these models is the tradeoff between the prior probability of a particular referent and the likelihood of that referent given the current utterance.
 
-Here we investigate information integration in pragmatic reasoning by experimentally manipulating speaker specific and common ground information and testing how adult listeners integrate them in a word learning scenario.
-In Experiment 1 and 2, we replicate earlier findings with adults and children showing that listeners expect speakers to a) produce informative utterances (Experiment 1) and b) communicate about things that are relevant to common ground (Experiment 2).
-Based on these results, we derive model predictions about how these two components should be integrated.
-In Experiment 3, we test how listeners integrate expectations and compare model predictions to empirical data.
-Experiment 4 replicates and extends Experiment 3 by gradually varying the strength of common ground assumptions.
+Here we evaluate this rational, pragmatic account of information integration.
+We isolate speaker-specific and common-ground information experimentally, then test how adult listeners combine them in a word learning setting.
+In Experiments 1 and 2, we replicate findings showing that listeners expect speakers to a) produce informative utterances (Experiment 1) and b) communicate about things that are relevant to common ground (Experiment 2).
+Based on these results, we generate model predictions using the RSA framework about how these two components should be integrated.
+In Experiment 3, we test how listeners integrate their expectations and compare model predictions to empirical data.
+Experiment 4 replicates and extends Experiment 3 by varying the strength of common ground assumptions.
 
@@
 
-Each experiment was implemented on a website (using JavaScript and HTML) to which participants were directed.
+Experiments were conducted online using Amazon’s Mechanical Turk.
 Figure \ref{fig:design} provides a schematic overview of the setup and experimental procedures.
-The instructions informed participants that they will see a number of animal characters asking for novel toys.
-Participants’ task was to identify the toy a given animal is requesting.
+The instructions informed participants that they would see a number of animal characters asking for novel toys.
+Participants were asked to identify the toy being requested by a particular animal.
 The basic layout involved two tables with toys on them, located left and right of a little hill, on which the animal was standing.
@@
 For all experiments, we pre-registered the sample size, experimental design and the statistical analysis.
-For Experiment 3 and 4, we also registered the model structure and predictions (see [https://osf.io/u7kxe](https://osf.io/u7kxe))
+For Experiment 3 and 4, we also registered the model structure and predictions (see [masked for peer review])
 
@@
 Informativeness (Experiment 1, left) translated to making one object less frequent in context.
-Common ground (Experiment 2, middle) was manipulated by making one object prefered by, or new to the speaker.
+Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
 Experiment 3 (right) combined manipulations.
 When expressing e.g.
-preference for an object on a table with two objects (panel 3 from top), the respective object was temporally enlarged.
-Condition shown here: preference - same speaker - incongruent."}
+preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
+Condition shown here: preference - same speaker - incongruent.
+Green plus signs represent an expression of preference and red minus of dispreference (see main text for details)."}
 img <- png::readPNG("figs/method_figure.png")
@@
 All participants were recruited from Amazon Mechanical Turk and had US IP addresses.
-We planned the sample size in each experiment to be 120 data points per cell.
-Experiment 1 had 40 participants.Informativeness was manipulated by making one object less frequent in context.
-In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Figure 1 in red).
-On each trial, the animal introduced themselves, turned towards the table with the two objects and made a request.
+Sample size in each experiment was planned to be 120 data points per cell.
+Experiment 1 had 40 participants.
+In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Figure \ref{fig:design}, left).
+On each trial, the animal introduced themselves (e.g.
+“Hi, I’m Dog”), turned towards the table with the two objects and made a request.
 If listeners expect speakers to produce informative utterances, they should select object B.
@@
 In the control condition, both tables contained two objects, one of which was randomly determined as the correct one.
-No inference was therefore licenced based on the animals turning.
-Each participant received three trials in each condition.
+No inference was therefore licenced.
+Each participant received three trials in each condition for a total of six trials, presented in a randomized order.
 
@@
 
-Participants selected the less frequent object above chance in the test condition (t = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to the control condition (genreralized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker (animal).}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p*  `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
-This result replicates earlier work [@frank2014inferring].
+Participants selected the less frequent object above chance in the test condition (t(`r ex1t%>%filter(control == "false")%>%pull(df)`) = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to the control condition (genreralized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker (animal).}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p*  `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+This result replicates earlier work [@frank2014inferring] and is consistent with the hypothesis that listeners expect speakers to communicate in an informative way.
 
-```{r plotexp12, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3.4, fig.height=2, fig.cap = "Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig.
+```{r plotexp12, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3.4, fig.height=2, fig.cap = "Results from Experiment 1 and 2.
+For preference and novelty, control refers to a different speaker (see Fig.
 1).
-Transparent dots show data from individual particpants, solid dots represent condition means, error bars are 95 \\% CIs.
+Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95 \\% CIs.
 Dashed line indicates performance expected by chance."}
@@
 
-We manipulated common ground expectations based on two ways which have succesfully been used in developmental studies [e.g.
+We manipulated common ground expectations based on procedures that have successfully been used in developmental studies [e.g.
 @akhtar1996role; @saylor2009preschoolers].
@@
 
-There were 80 participants, 40 per manipulation.
-In the preference manipulation, each table had a different object.
+We collected data from 80 participants, with 40 in each condition.
+In the preference condition, each table had a different object.
 In the beginning, the animal appeared on the hill and introduced themselves.
@@
 Then, the animal disappeared.
-After a short period of time, either the same or a different animal appeared and requested an object while facing straight (see Figure 1 in blue).
+After a short period of time, either the same or a different animal appeared and requested an object while facing straight ahead (see Figure \ref{fig:design}, middle).
 If participants took into account the information they gained about the speaker, they should select the previously preferred object if the returning animal was the same.
@@
 
-In the novelty manipulation, one table was initially empty while there was an object on the other one (see Figure \ref{fig:design}).
+In the novelty condition, one table was initially empty while there was an object on the other table (see Figure \ref{fig:design}).
 The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
-Next, the animal quickly disappeared.
+Next, the animal disappeared.
 The same animal re-appeared and the sequence above was repeated.
 When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
-Like in preference, we now manipulated if the same animal or a different one would return.
+Like in the preference condition, we now manipulated if the same animal or a different one returned.
 In case of the same animal returning, listeners could infer the referent of the subsequent request by considering that one object was new to the speaker and therefore more likely to be of interest to them.
-No such inference was licensed when a different animal returned because both objects were equally new to them.
+However, no such inference was licensed when a different animal returned because both objects were novel.
 
@@
 
-Participants selected the preferred object above chance when the same animal returned (t = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Participants selected the preferred object above chance when the same animal returned (t(`r ex2tpref%>%filter(control == "false")%>%pull(df)`) = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
 Thus, listeners inferred the referent of the utterance by considering previous interactions with the speaker.
-Interestingly, participants to some extend transferred preference from one animal to the other and also selected the preferred object above chance when a different animal returned (t = `r ex2tpref%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "true")%>%pull(p_value)`).
-In sum, this study shows that adults make comparable infernces to children [@saylor2009preschoolers].
+Interestingly, participants transferred preference to some extent from one animal to the other and selected the preferred object above chance when a different animal returned (t(`r ex2tpref%>%filter(control == "true")%>%pull(df)`) = `r ex2tpref%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "true")%>%pull(p_value)`).
+In sum, this study shows that adults make comparable inferences to children [@saylor2009preschoolers].
 
-The novel object was selected above chance when the same animal returned (t = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}).
+The novel object was selected above chance when the same animal returned (t(`r ex2tnov%>%filter(control == "false")%>%pull(df)`) = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t(`r ex2tnov%>%filter(control == "true")%>%pull(df)`) = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}).
 Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
-Thus, like children [@akhtar1996role], participants used their prior information about the speaker to resolve ambiguity in their utterance.
+Thus, like children [@akhtar1996role], adults used their prior information about the speaker to resolve ambiguity in the utterance.
 
@@
 
-Experiment 1 and 2 separately measured two types of pragmatic inferences.
-The first was based on the expectation that speakers produce informative utterances.
-The second was based on the expectations that speakers produce their utterances in light of the ongoing social interaction (common ground).
-In Experiment 3, we combined both types of expectations to study how listeners integrate them.
+In Experiment 3, we combined the expectations studied in Experiment 1 and 2 to study how listeners integrate them.
 
@@
 In Experiment 3, however, we manipulated common ground expectations in the same way as in Experiment 2.
-For example, the animal would turn to the table with one object and express their dis-liking of object A, then they would turn to the other table and express their liking of object B (not using labels).
-Next, after quickly disappearing, the animal would reappear, turn to the table with two objects and make a request.
+For example, the animal would turn to the table with one object and express that they don’t like object A, then they would turn to the other table and express that they like object B.
+Next, after quickly disappearing, the animal would reappear, turn to the table with two objects and make a request (see Figure \ref{fig:design}, right).
 
-For each version of Experiment 2, there were 4 conditions in Experiment 3.
+For each common ground condition, there were 4 conditions in Experiment 3 resulting from the cross of congruent/incongruent informativeness with same/different speaker.
 If the preferred/novel object was the less frequent one (object B), the two expectations were congruent.
@@
 For each type of expectation alignment, we varied if the same or a different animal returned.
-Participants either completed the preference or novelty version and received two test trials in each of the four conditions.
+Participants either completed the preference or novelty version with two test trials in each of the four conditions.
 Before discussing the empirical results, we briefly discuss the cognitive model we used to predict expectation integration.
@@
 The speaker chooses how to refer to the object by reasoning about a naive listener who does not know the labels for the object [@frank2014inferring].
-Mathematically, the probability that the listener chooses a referent given an utterance is defined as follows:
+The conditional probability that the listener chooses a referent given an utterance is defined as follows:
 $$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$
-Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance to refer to a specific referent.
-It is defined as the surprisal of an utterance given the referent for a naive listener, who interprets utterances in a literal way:
-
+Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance u to refer to a specific referent r.
+It is defined in terms of a utility function $U_S(u;s)$ consisting of the surprisal of $u$ for a naive listener $L_0$, who interprets $u$ according its literal semantics:
 $$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$
-
-The numerical strength of the expression above depends on $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances.
+The numerical strength of the expression above depends on $\alpha$ scalar value, α, which can be interpreted as an indicator of how rational the speaker is in choosing utterances (i.e.
+as alpha increases, the speaker is more likely to choose the most informative utterance).
 
@@
 
-In our model, we used the results from Experiment 1 and 2 to specify $\alpha$ as well as $P_S(r_s)$.
-The former was set to yield the proportion measured in Experiment 1 in a model with uniform priors.
-The prior probability for each object was the proportion with which this object was chosen in Experiment 2\footnote{Proportions were measured when participants chose between two objects.
+We used the results from Experiment 1 and 2 to specify $\alpha$ as well as $P_S(r_s)$ in our model.
+We set $\alpha$ so that a model with uniform priors would predict the average proportion measured in Experiment 1.
+The prior probability for each object was set to be the proportion with which this object was chosen in Experiment 2\footnote{Proportions were measured when participants chose between two objects.
 However, in Experiment 3, three objects were involved.
 For each object we used the proportion measured in Experiment 2 as the prior probability.This approached spread out the absolute probability mass for each object but conserved the relative relation between objects.}.
-Based on these parameter settings, we predicted the proportion with which listeners will choose the less frequent object in each unique combination of alignment and speaker identity separately for each prior manipulation (eight conditions total, see Figure \ref{fig:plotexp3}).
+Based on these parameter settings, we predicted the proportion with which listeners will choose the more informative object in each of eight unique conditions mentioned above (see also Figure \ref{fig:plotexp3}).
 We compared the fit of this pragmatic model to two alternative models using Bayes Factors (BF).
-The first alternative model ignored the speaker specific expectations (flat prior model) while the second ignored the informativeness inference (prior only model).
-To capture the idea that behavioral data is to some degree noisy, all models included a noise parameter, which reflects that, with a certain probability, participants respond randomly instead of in line with the intended manipulation on a given trial.
-Noise parameters are estimated based on the data.
+The first alternative model ignored the speaker specific expectations (uniform prior model) while the second ignored the informativeness inference (prior only model).
+
+<!-- All models included a “noise parameter”, reflecting that participants may respond randomly instead of in line with the intended manipulation on a given trial.
+Noise parameters were estimated based on the data.
+-->
 
 ## Results and Discussion
-
-```{r plotmodelcomp, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4.
-(C) Data for strong prior manipualtion in Experiment 3 and 4.
-Error bars = 95 \\%  HDIs."}
-
-pc1 <- pred_ex3%>%
-  filter(Model == "Noisy RSA Model")%>%
-  mutate(Prior = "Strong")
-
-c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  theme_few(base_size = 10) + 
-  guides(col = F)+
-  scale_colour_viridis_d()
-
-pc2 <- pred_ex4%>%
-  filter(Model == "Noisy RSA Model")
-
-c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  theme_few(base_size = 10) + 
-  scale_colour_manual(values = rev(viridis::viridis(3)))
-
-pc3 <- data.frame(
-    ex3 = pc1%>%pull(Data),
-    ex3_ci_l = pc1%>%pull(Data_ci_low),
-    ex3_ci_u = pc1%>%pull(Data_ci_up),
-    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
-    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
-    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
-    Prior = "Strong")
-
-c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
-  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Data Experiment 3")+
-  ylab("Data Experiment 4")+
-  theme_few(base_size = 10)+ 
-  scale_color_viridis_d()
-
-ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T , labels = c("A","B","C"), vjust = 1)
-
-```
 
@@
 
-Results are discussed in the form of the proportion with which listeners chose the less frequent object.
-For a comparison to chance within each unique condition see Figure \ref{fig:plotexp3}.
-Both alignment and speaker identity influenced participants’ responses  (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
-Figure \ref{fig:plotmodelcomp} shows the mean response in each unique condition compared to the model.
-Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).
-Model fit was better in the model taking into account both types of expectations compared to the flat prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
+Results are discussed in the form of the proportion with which listeners chose the more informative object (i.e., the object that would be the more informative referent when only considering speaker general information).
+For a comparison to chance within each unique condition see \ref{fig:plotexp3}.
+Combinations of alignment and speaker identity differed in how they influenced participants’ responses (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
+Figure \ref{fig:plotmodelcomp}A and B shows the mean response in each unique condition compared to the pragmatics model.
+Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).Model fit was much better in the model taking into account both types of expectations compared to the uniform prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
 No prior") %>%pull(BayesFactor),digits = 2)`) or prior only model (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
@@
 
-Interestingly, like in Experiment 2, there was a transfer of preference in case of a speaker change.
+Interestingly, as in Experiment 2, there was a transfer of preference in the case of speaker change.
 Participants were at chance in the preference - different speaker - incongruent condition (see Figure \ref{fig:plotexp3}).
 If preference would have been specific to a particular individual, participants should have selected the less frequent object above chance (as they did in the corresponding condition with the novelty manipulation).
+Because it takes into account the measurement from the earlier experiment, our model predicts these results; future work might explicitly model generalization across speakers.
 
@@
 In Experiment 4, we replicated and extended Experiment 3 by manipulating the strength of the common ground expectations.
-Our main goal was to investigate the scope of our cognitive model and we therefore limit the description of the methods and the discussion of the results to the aspects relevant to the comparison between model predictions and data.
+Our main goal was to investigate the quantitative accuracy of our cognitive model and we therefore limit the description of the methods and the discussion of the results to the aspects relevant to the comparison between model predictions and data.
 
@@
 The structure of the experiment was the same as in Experiment 3.
-For each common ground expectation (preference and novelty), we intended to have a strong, a medium and a weak manipulation.
-The strength of each manipulation was determined by the proportion with which participants chose the preferred / novel object given the manipulation.
-We succeeded in this for novelty.
-For preference we did not find a manipulation that yielded only a weak preference.
+For each common ground expectation (preference and novelty), we intended to have a strong, a medium and a weak condition.
+The strength of each condition was determined by the proportion with which participants chose the preferred/novel object given the manipulation.
+We succeeded in generating quantitative variability for novelty.
+For preference we piloted a number of additional manipulations but did no find one that yielded a weaker preference compared to a medium condition.
 
-The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication.
-For novelty, in the medium manipulation, the animal turned to each table only once before the test.
-In the weak manipulation, the animal only turned to the table with an object before the test.
-In the medium manipulation for preference, the animal only expressed liking and did so in a more subtle way (saying only: “Oh, wow”).
-Participants were assigned to one level of common ground expectation and completed two test trials in each of the four conditions.
+The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication (see Figure \ref{fig:plotmodelcomp}C).
+For novelty, in the medium condition, the animal turned to each table only once before the test.
+In the weak condition, the animal only turned to the table with an object before the test (instead of turning to and commenting on both).
+In the medium condition for preference, the animal only expressed liking and did so in a more subtle way (saying only: “Oh, wow” while pointing to the object).
+Participants were assigned to one level of common ground expectation and completed two test trials in each of the four conditions (alignment x speaker change).
 
-Model predictions were obtained in the same way as in Experiment 3.
-The likelihood term of the model was identical.
-For the each level of common ground expectation, we measured the proportion with which participants chose the preferred / novel object in a separate experiment.
-Due to space limitations, we do not discuss them in any more detail here.
-Like in Experiment 3, the results of these experiments were used to specify the prior distribution in the model.
+Model predictions were obtained in the same way as in Experiment 3; with $\alpha$ inferred from the data and $P_S(r_s)$ measured empirically (in a set of corresponding experiments parallel to Experiment 2).
 
 ## Results and Discussion
+
+```{r plotmodelcomp, fig.env="figure*", fig.pos = "h", fig.width=7, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4.
+(C) Data for strong prior manipulation in Experiment 3 and 4, providing a noise ceiling for the reliability of measurements.
+Error bars = 95 \\%  HDIs."}
+
+pc1 <- pred_ex3%>%
+  filter(Model == "Noisy RSA Model")%>%
+  mutate(Prior = "Strong")
+
+c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 10) + 
+  guides(col = F)+
+  scale_colour_viridis_d()
+
+pc2 <- pred_ex4%>%
+  filter(Model == "Noisy RSA Model")
+
+c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 10) + 
+  scale_colour_manual(values = rev(viridis::viridis(3)))
+
+pc3 <- data.frame(
+    ex3 = pc1%>%pull(Data),
+    ex3_ci_l = pc1%>%pull(Data_ci_low),
+    ex3_ci_u = pc1%>%pull(Data_ci_up),
+    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
+    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
+    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
+    Prior = "Strong")
+
+c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
+  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = ex3, y = ex4), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Data Experiment 3")+
+  ylab("Data Experiment 4")+
+  theme_few(base_size = 10)+ 
+  scale_color_viridis_d()
+
+ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T , labels = c("A","B","C"), vjust = 1)
+
+```
 
@@
 
-As noted above, the strong prior manipulation was a direct replication of Experiment 3.
+As noted above, the strong prior condition was a direct replication of Experiment 3.
 Results from the two rounds of data collection were highly correlated (r = `r repl_r$estimate`, *p* `r repl_r$p.value`, see Figure \ref{fig:plotmodelcomp}C).
 Across levels of prior manipulation, the data from Experiment 4 were highly correlated to the corresponding model predictions (r = `r ex4_comp_r$estimate`, *p* `r ex4_comp_r$p.value`, see Figure \ref{fig:plotmodelcomp}B).
-Again, the pragmatic model provided a better fit compared to the flat prior (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
+Again, the pragmatics model provided a much better fit compared to the flat prior (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
 No prior") %>%pull(BayesFactor),digits = 2)` ) or prior only model (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
@@
 
-Language use and learning requires balancing different types of expectations about one’s interlocutor.
-Here we used a Bayesian cognitive model to predict this integration process.
-Experiment 1 and 2 replicated earlier studies showing that adult listeners expect speakers to produce utterances in an informative way as well as in light of common ground.
-Next, we combined the procedures from the first two experiments to study how listeners would integrate them.
-We used the results from Experiment 1 and 2 to specify the model parameters that represented the two types of expectations and make parameter-free predictions about new behavior.
+Language use and learning requires balancing different types of expectations about one’s interlocutor - both expectations about how speakers behave in general and specific expectations about how a particular speaker might behave in a particular context.
+Here we used a computational pragmatics model to predict this integration process.
+Experiment 1 and 2 replicated previous studies showing that adult listeners expect speakers to produce utterances informatively and also with respect to common ground.
+We then combined the procedures from the first two experiments to study how listeners would integrate these two types of information.
+We used the results from Experiment 1 and 2 to specify model parameters that represented the two types of expectations, generating predictions about new behavior.
 Experiments 3 and 4 showed that both types of expectations influenced listeners inferences.
-In general, listener behavior accurately described by our model, suggesting that – at least in population aggregate – listeners trade off flexibly between speaker specific and general pragmatic expectations.
+In general, listener behavior was accurately described by our model, suggesting that listeners trade-off flexibly between speaker specific and general pragmatic expectations.
 
 Notably, Experiment 3 also included situations in which the two expectations were in conflict.
-For example, in some trials the animal expressed preference for object A, which was also the more frequent object.
-In these situations, participants chose the preferred object as the referent  (see also Figure \ref{fig:plotexp3}).
-A simple explanation for this pattern might be that common ground manipulations were simply “stronger” in that they produced higher rates of expected choice when presented on their own (see Figure \ref{fig:plotexp12}).
-However, in Experiment 4 we observed the same pattern in the medium manipulation for novelty (results not discussed above, see online repository for details) even though the manipulation alone yielded numerically weaker results compared to the general expectation in Experiment 1.
-In each case, the pattern in the data was  predicted by the model This illustrates the conditional nature of pragmatic inference: The informativeness of an utterance critically depends on the context, including common ground.
-If prior interactions already single out one object as the more likely referent, subsequent considerations of informativeness take place in light of this prior information and not independent of it.
+For example, in some trials the speaker expressed preference for object A, which was also the more frequent (less informative) object.
+In these situations, a majority of participants chose the preferred object as the referent (see also Figure \ref{fig:plotexp3} preference--same speaker--incongruent).
+A simple explanation for this pattern might be that common ground manipulations were simply “stronger”, corroborated by the fact they produced higher rates of expected choice than the informativeness expectation when the two were presented in isolation (see Figure \ref{fig:plotexp12}).
+In Experiment 4, however, the medium manipulation for novelty yielded numerically weaker results compared to the informativeness expectation in Experiment 1, and yet participants still selected the novel object above chance when the expectations were in conflict.
+Why is this?
+
+Because common ground is represented in our model as the listener’s prior distribution, speakers can reason about it in choosing their utterance.That is, in the mind of the listener, the speaker computes the effect of each utterance on a naive listener with shared common ground.
+Therefore, when prior interactions implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of prior information.
+
+<!-- In some cases, this constraining effect of prior knowledge can lead to counterintuitive predictions from RSA models [see @degen2015wonky for discussion and model extension].  -->
 
@@
 
-A logical next step will be to extend the work presented here to children.
-As outlined above, pragmatic reasoning is though to play an important role in how children learn new words.
-An ontogenetic study would also show to what extent the modelling approach taken here is suitable to address questions about development.
-Another fruitful future direction would be to experimentally manipulate expectations about speaker informativeness.
-For example, if a speaker repeatedly behaves in an irrational way (e.g.
-labels dogs as cats), listeners might be less inclined to assume that utterances containing novel words are produced in an informative way.
+<!-- Pragmatic reasoning is thought to play an important role in how children learn new words.
+Thus, a logical next step will be to extend the work presented here to children.
+An ontogenetic study would also show to what extent the modelling approach taken here is suitable to address questions about developmental change.
+-->
 
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em}
+<!-- \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at [masked for peer review]}} \vspace{1em} -->
+
+<!-- \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->
 
@@
 
-MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.
+Masked for peer review.
+
+<!-- MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229. -->
 

### 2019-01-28 papers/cogsci2019/cogsci2019.tex
cogsci draft

@@
 \begin{abstract}
-Pragmatic inferences are an integral part of language comprehension and
-learning. To recover the intended meaning of an utterance, listeners
-need to balance and integrate different sources in information. In a
-series of experiments, we studied how listeners integrate general
-expectations about speakers with expectations that are specific to the
-interactional history with a particular speaker. We used a Bayesian
-cognitive model to formalize the integration process. In Experiment 1
-and 2 we replicated findings showing that listeners make inferences
-based on general and speaker specific expectations. Using the empirical
-measurements from these experiments, we generated model predictions
-about how they should be integrated. We tested these predictions in
-Experiment 3, which combined both expectations in a single design.
+Pragmatic inferences are an integral part of language learning and
+comprehension. To recover the intended meaning of an utterance,
+listeners need to balance and integrate different sources of contextual
+information. In a series of experiments, we studied how listeners
+integrate general expectations about speakers with expectations specific
+to their interactional history with a particular speaker. We used a
+Bayesian pragmatics model to formalize the integration process. In
+Experiments 1 and 2, we replicated previous findings showing that
+listeners make inferences based on speaker-general and speaker-specific
+expectations. We then used the empirical measurements from these
+experiments to generate model predictions about how the two kinds of
+expectations should be integrated, which we tested in Experiment 3.
 Experiment 4 replicated and extended Experiment 3 to a broader set of
-conditions. Across both experiments, listeners based their inferences on
-both types of expectations. Overall, model predictions and data were
-highly correlated. Predictions from the model incorporating both types
-of information described listeners' behavior better compared to
-alternative models based on only one type of information. This research
-shows that listeners flexibly integrate different forms of social
-expectations across a range of contexts, a process which can be
-described using Bayesian cognitive models. Our approach highlights how
-experiments and computational models can be used in conjunction to
-inform theories about language use and comprehension.
+conditions. In both experiments, listeners based their inferences on
+both types of expectations. We found that model performance was also
+consistent with this finding; with better fit for a model which
+incorporated both general- and specific-information compared to
+baselines incorporating only one type. Listeners flexibly integrate
+different forms of social expectations across a range of contexts, a
+process which can be described using Bayesian models of pragmatic
+reasoning. Our approach highlights how experiments and computational
+models can be used in conjunction to inform theories about language use
+and comprehension.
 
@@
 One of the most astonishing features of natural language is that it
-allows us to communicate precise meanings despite the fact that each
-utterance is inherently ambiguous. The conventional couplings between
-sounds (words) and objects constrain what a speaker may mean by an
-utterance. However, the intended meaning of the utterance is not
-reducible to the words that are contained in it. For example, the same
-utterance (``Look, there it is!'') could be intended to refer to very
-different things depending on whether someone is searching for their
-wallet or looking for the bus stop. It takes additional pragmatic
-inferences to recover the intended meaning (Levinson, 2000).
+allows us to communicate precise meanings despite the fact that most
+utterances are inherently ambiguous. While the conventional mapping
+between sounds (words) and objects constrain what a speaker may mean by
+an utterance, the intended meaning of the utterance is not reducible to
+the words that are contained in it. It takes additional pragmatic
+inference to recover the intended meaning (Levinson, 2000).
 
@@
 Wilson, 2001). Grice (1991) summarised this expectation via the
-cooperative principle: ``Make your contribution such as is required, at
-the stage at which it occurs, by the accepted purpose or direction of
+``Cooperative Principle'': ``Make your contribution such as is required,
+at the stage at which it occurs, by the accepted purpose or direction of
 the talk exchange in which you are engaged.'' Importantly, the second
-half of the principle highlights a second type of expectation:
-interlocutors expect each other to produce and interpret utterances in
-light of the shared common ground between them (H. H. Clark, 1996).
-Common ground refers to bits of information that are assumed to be
-shared, either because they result from joint experience or were
-otherwise grounded (Bohn \& Koymen, 2018). The nature of the
-corresponding expectations vary with the individuals involved.
+half of the Cooperative Principle describes a second type of
+expectation: interlocutors expect each other to produce and interpret
+utterances \emph{in light of the shared common ground between them} (H.
+H. Clark, 1996). Common ground refers to bits of information that are
+assumed to be shared, either because they were mentioned over the course
+of the conversation or grounded through some form of joint experience
+(Bohn \& Koymen, 2018). Note that by its very nature, common ground may
+vary with the individuals involved in a particular conversation.
 
-Both general and common ground expectations can support children's word
+These same general and specific expectations can support children's word
 learning (E. V. Clark, 2009; Tomasello, 2009). On the one hand, children
-have been found to learn novel words by assuming that the speaker is
+have been found to learn novel words by assuming speakers are generally
 informative (Frank \& Goodman, 2014). That is, in the absence of any
@@
 referring to the most informative referent. On the other hand, children
-learn novel words by relying on common ground expectations (Akhtar,
-Carpenter, \& Tomasello, 1996; Bohn \& Koymen, 2018). For example, when
-a speaker expressed preference for a particular object, children expect
-a novel word from the same speaker to refer to the previously preferred
-object (Saylor, Sabbagh, Fortuna, \& Troseth, 2009).
+use conversation-specific common ground expectations to decide which
+object a specific speaker is referring to when they use a novel word
+(Akhtar, Carpenter, \& Tomasello, 1996). For example, when a speaker
+expressed preference for a particular object, children expect a novel
+word from the same speaker to refer to the previously preferred object
+(Saylor, Sabbagh, Fortuna, \& Troseth, 2009).
 
-But how are general and common ground expectations integrated with one
-another? Are pragmatic inferences strengthened additively when both
-support a particular interpretation? How are they weighed when they are
-in conflict? The rational speech act (RSA) framework (Frank \& Goodman,
-2012) offers a formal framework for this information integration
-problem. RSA models are characterized by their recursive structure in
-which speakers and listeners reason about each other's interpretation of
-utterances in context. RSA models have been found to make accurate
-quantitative predictions about various forms of pragmatic language use
-and word learning (Goodman \& Frank, 2016). However, a comprehensive
-treatment of how general and common ground expectations are integrated,
-is still missing.
+But how do listeners integrate general and common ground-related
+expectations during word learning? Are pragmatic inferences strengthened
+additively when both support a particular interpretation? How are they
+weighed when they are in conflict? The Rational Speech Act (RSA)
+framework (Frank \& Goodman, 2012; Goodman \& Frank, 2016) offers a
+formal framework for addressing this information integration problem.
+RSA models are characterized by a recursive structure in which a
+pragmatic listener tries to uncover a speaker's intended meaning by
+assuming the speaker chose their utterance in order to get a naive
+listener to recover their intended meaning. RSA models have made
+accurate quantitative predictions about various forms of pragmatic
+language use and word learning (Goodman \& Frank, 2016). However, a
+comprehensive treatment of how general and common ground expectations
+are integrated is still missing.
 
@@
 reasoner; thus, information integration is treated as a process of
-probabilistic inference. A natural locus within these models for
-information integration is the tradeoff between the prior probability of
-a particular referent (the degree to which it is in common ground) and
-the likelihood of that referent given the current utterance (general
-pragmatic interpretation).
+probabilistic inference. The speaker-general informativeness expectation
+is already encoded in the structure of the model: Speakers produce
+utterances to aid the listener in disambiguating referents. We
+operationalize speaker-specific, common ground information as the shared
+prior probability of referents in the context of the utterance. Thus, a
+natural locus for information integration within these models is the
+tradeoff between the prior probability of a particular referent and the
+likelihood of that referent given the current utterance.
 
-Here we investigate information integration in pragmatic reasoning by
-experimentally manipulating speaker specific and common ground
-information and testing how adult listeners integrate them in a word
-learning scenario. In Experiment 1 and 2, we replicate earlier findings
-with adults and children showing that listeners expect speakers to a)
-produce informative utterances (Experiment 1) and b) communicate about
-things that are relevant to common ground (Experiment 2). Based on these
-results, we derive model predictions about how these two components
+Here we evaluate this rational, pragmatic account of information
+integration. We isolate speaker-specific and common-ground information
+experimentally, then test how adult listeners combine them in a word
+learning setting. In Experiments 1 and 2, we replicate findings showing
+that listeners expect speakers to a) produce informative utterances
+(Experiment 1) and b) communicate about things that are relevant to
+common ground (Experiment 2). Based on these results, we generate model
+predictions using the RSA framework about how these two components
 should be integrated. In Experiment 3, we test how listeners integrate
-expectations and compare model predictions to empirical data. Experiment
-4 replicates and extends Experiment 3 by gradually varying the strength
+their expectations and compare model predictions to empirical data.
+Experiment 4 replicates and extends Experiment 3 by varying the strength
 of common ground assumptions.
@@
 
-Each experiment was implemented on a website (using JavaScript and HTML)
-to which participants were directed. Figure \ref{fig:design} provides a
-schematic overview of the setup and experimental procedures. The
-instructions informed participants that they will see a number of animal
-characters asking for novel toys. Participants' task was to identify the
-toy a given animal is requesting. The basic layout involved two tables
-with toys on them, located left and right of a little hill, on which the
-animal was standing. For each animal, we recorded a set of utterances
-(one speaker per animal) that were used throughout the experiments to
-provide information and make requests. At test, toys were requested
-using the following utterance: ``Oh cool, there is a {[}non-word{]} on
-the table, how neat, can you give me the {[}non-word{]}?''. Participants
-responded by clicking on one of the toys. Each experiment started with
-two training trials in which animals requested familiar objects (car and
+Experiments were conducted online using Amazon's Mechanical Turk. Figure
+\ref{fig:design} provides a schematic overview of the setup and
+experimental procedures. The instructions informed participants that
+they would see a number of animal characters asking for novel toys.
+Participants were asked to identify the toy being requested by a
+particular animal. The basic layout involved two tables with toys on
+them, located left and right of a little hill, on which the animal was
+standing. For each animal, we recorded a set of utterances (one speaker
+per animal) that were used throughout the experiments to provide
+information and make requests. At test, toys were requested using the
+following utterance: ``Oh cool, there is a {[}non-word{]} on the table,
+how neat, can you give me the {[}non-word{]}?''. Participants responded
+by clicking on one of the toys. Each experiment started with two
+training trials in which animals requested familiar objects (car and
 ball).
@@
 design and the statistical analysis. For Experiment 3 and 4, we also
-registered the model structure and predictions (see
-\url{https://osf.io/u7kxe})
+registered the model structure and predictions (see {[}masked for peer
+review{]})
 
@@
 Informativeness (Experiment 1, left) translated to making one object less frequent in context.
-Common ground (Experiment 2, middle) was manipulated by making one object prefered by, or new to the speaker.
+Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
 Experiment 3 (right) combined manipulations.
 When expressing e.g.
-preference for an object on a table with two objects (panel 3 from top), the respective object was temporally enlarged.
-Condition shown here: preference - same speaker - incongruent.}\label{fig:design}
+preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
+Condition shown here: preference - same speaker - incongruent.
+Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).}\label{fig:design}
 \end{figure*}
@@
 All participants were recruited from Amazon Mechanical Turk and had US
-IP addresses. We planned the sample size in each experiment to be 120
-data points per cell. Experiment 1 had 40 participants.Informativeness
-was manipulated by making one object less frequent in context. In the
-test condition, one table contained one object of type A and the other
-table contained one object of type A and one of type B (see Figure 1 in
-red). On each trial, the animal introduced themselves, turned towards
-the table with the two objects and made a request. If listeners expect
-speakers to produce informative utterances, they should select object B.
-This choice follows from the counterfactual inference that if the
-(informative) speaker would have wanted to request A, they would have
-turned to the table that only contained A. On the other hand, since B is
-only located on the table together with A, there was no alternative way
-to request B in a less ambiguous way. In the control condition, both
-tables contained two objects, one of which was randomly determined as
-the correct one. No inference was therefore licenced based on the
-animals turning. Each participant received three trials in each
-condition.
+IP addresses. Sample size in each experiment was planned to be 120 data
+points per cell. Experiment 1 had 40 participants. In the test
+condition, one table contained one object of type A and the other table
+contained one object of type A and one of type B (see Figure
+\ref{fig:design}, left). On each trial, the animal introduced themselves
+(e.g. ``Hi, I'm Dog''), turned towards the table with the two objects
+and made a request. If listeners expect speakers to produce informative
+utterances, they should select object B. This choice follows from the
+counterfactual inference that if the (informative) speaker would have
+wanted to request A, they would have turned to the table that only
+contained A. On the other hand, since B is only located on the table
+together with A, there was no alternative way to request B in a less
+ambiguous way. In the control condition, both tables contained two
+objects, one of which was randomly determined as the correct one. No
+inference was therefore licenced. Each participant received three trials
+in each condition for a total of six trials, presented in a randomized
+order.
 
@@
 Participants selected the less frequent object above chance in the test
-condition (t = 5.51, \emph{p} \textless{} .001, see Figure
+condition (t(39) = 5.51, \emph{p} \textless{} .001, see Figure
 \ref{fig:plotexp12}) and did so more often compared to the control
@@
 = 1.49, se = 0.5 \emph{p} = .003). This result replicates earlier work
-(Frank \& Goodman, 2014).
+(Frank \& Goodman, 2014) and is consistent with the hypothesis that
+listeners expect speakers to communicate in an informative way.
 
@@
 
-\caption[Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig]{Results from Experiment 1 and 2.For preference and novelty, control refers to a different speaker (see Fig.
+\caption[Results from Experiment 1 and 2]{Results from Experiment 1 and 2.
+For preference and novelty, control refers to a different speaker (see Fig.
 1).
-Transparent dots show data from individual particpants, solid dots represent condition means, error bars are 95 \% CIs.
+Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95 \% CIs.
 Dashed line indicates performance expected by chance.}\label{fig:plotexp12}
@@
 
-We manipulated common ground expectations based on two ways which have
-succesfully been used in developmental studies (e.g. Akhtar et al.,
+We manipulated common ground expectations based on procedures that have
+successfully been used in developmental studies (e.g. Akhtar et al.,
 1996; Saylor et al., 2009). Speakers either expressed preference for one
@@
 
-There were 80 participants, 40 per manipulation. In the preference
-manipulation, each table had a different object. In the beginning, the
-animal appeared on the hill and introduced themselves. Next, they turned
-to one of the tables and expressed either that they liked (``Oh wow, I
-really like that one'') or disliked (``Oh bleh, I really don't like that
-one'') the object before turning to the other side and expressing the
-respective other attitude. Then, the animal disappeared. After a short
-period of time, either the same or a different animal appeared and
-requested an object while facing straight (see Figure 1 in blue). If
-participants took into account the information they gained about the
-speaker, they should select the previously preferred object if the
-returning animal was the same. If a different animal returned, they
-should choose randomly between objects.
+We collected data from 80 participants, with 40 in each condition. In
+the preference condition, each table had a different object. In the
+beginning, the animal appeared on the hill and introduced themselves.
+Next, they turned to one of the tables and expressed either that they
+liked (``Oh wow, I really like that one'') or disliked (``Oh bleh, I
+really don't like that one'') the object before turning to the other
+side and expressing the respective other attitude. Then, the animal
+disappeared. After a short period of time, either the same or a
+different animal appeared and requested an object while facing straight
+ahead (see Figure \ref{fig:design}, middle). If participants took into
+account the information they gained about the speaker, they should
+select the previously preferred object if the returning animal was the
+same. If a different animal returned, they should choose randomly
+between objects.
 
-In the novelty manipulation, one table was initially empty while there
-was an object on the other one (see Figure \ref{fig:design}). The animal
+In the novelty condition, one table was initially empty while there was
+an object on the other table (see Figure \ref{fig:design}). The animal
 turned to one of the sides and commented either on the presence (``Aha,
 look at that'') or the absence of an object (``Hm, nothing there'').
-Next, the animal quickly disappeared. The same animal re-appeared and
-the sequence above was repeated. When the animal disappeared for the
-second time, a second object appeared on the empty table while the
-animal was away. Like in preference, we now manipulated if the same
-animal or a different one would return. In case of the same animal
+Next, the animal disappeared. The same animal re-appeared and the
+sequence above was repeated. When the animal disappeared for the second
+time, a second object appeared on the empty table while the animal was
+away. Like in the preference condition, we now manipulated if the same
+animal or a different one returned. In case of the same animal
 returning, listeners could infer the referent of the subsequent request
 by considering that one object was new to the speaker and therefore more
-likely to be of interest to them. No such inference was licensed when a
-different animal returned because both objects were equally new to them.
+likely to be of interest to them. However, no such inference was
+licensed when a different animal returned because both objects were
+novel.
 
@@
 Participants selected the preferred object above chance when the same
-animal returned (t = 29.14, \emph{p} \textless{} .001, see Figure
+animal returned (t(39) = 29.14, \emph{p} \textless{} .001, see Figure
 \ref{fig:plotexp12}) and did so more often compared to trials in which a
@@
 utterance by considering previous interactions with the speaker.
-Interestingly, participants to some extend transferred preference from
-one animal to the other and also selected the preferred object above
-chance when a different animal returned (t = 2.7, \emph{p} = .01). In
-sum, this study shows that adults make comparable infernces to children
+Interestingly, participants transferred preference to some extent from
+one animal to the other and selected the preferred object above chance
+when a different animal returned (t(39) = 2.7, \emph{p} = .01). In sum,
+this study shows that adults make comparable inferences to children
 (Saylor et al., 2009).
@@
 The novel object was selected above chance when the same animal returned
-(t = 6.77, \emph{p} \textless{} .001) but not when a different one
-appeared (t = 1.49, \emph{p} = .144, see Figure \ref{fig:plotexp12}).
-Furthermore, the two conditions differed in the expected direction
-(\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{} .001). Thus, like
-children (Akhtar et al., 1996), participants used their prior
-information about the speaker to resolve ambiguity in their utterance.
+(t(39) = 6.77, \emph{p} \textless{} .001) but not when a different one
+appeared (t(39) = 1.49, \emph{p} = .144, see Figure
+\ref{fig:plotexp12}). Furthermore, the two conditions differed in the
+expected direction (\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{}
+.001). Thus, like children (Akhtar et al., 1996), adults used their
+prior information about the speaker to resolve ambiguity in the
+utterance.
 
@@
 
-Experiment 1 and 2 separately measured two types of pragmatic
-inferences. The first was based on the expectation that speakers produce
-informative utterances. The second was based on the expectations that
-speakers produce their utterances in light of the ongoing social
-interaction (common ground). In Experiment 3, we combined both types of
-expectations to study how listeners integrate them.
+In Experiment 3, we combined the expectations studied in Experiment 1
+and 2 to study how listeners integrate them.
 
@@
 2. For example, the animal would turn to the table with one object and
-express their dis-liking of object A, then they would turn to the other
-table and express their liking of object B (not using labels). Next,
-after quickly disappearing, the animal would reappear, turn to the table
-with two objects and make a request.
+express that they don't like object A, then they would turn to the other
+table and express that they like object B. Next, after quickly
+disappearing, the animal would reappear, turn to the table with two
+objects and make a request (see Figure \ref{fig:design}, right).
 
-For each version of Experiment 2, there were 4 conditions in Experiment
-3. If the preferred/novel object was the less frequent one (object B),
-the two expectations were congruent. If the preferred/novel object was
-the more frequent one (object A), expectations were incongruent. For
-each type of expectation alignment, we varied if the same or a different
-animal returned. Participants either completed the preference or novelty
-version and received two test trials in each of the four conditions.
-Before discussing the empirical results, we briefly discuss the
-cognitive model we used to predict expectation integration.
+For each common ground condition, there were 4 conditions in Experiment
+3 resulting from the cross of congruent/incongruent informativeness with
+same/different speaker. If the preferred/novel object was the less
+frequent one (object B), the two expectations were congruent. If the
+preferred/novel object was the more frequent one (object A),
+expectations were incongruent. For each type of expectation alignment,
+we varied if the same or a different animal returned. Participants
+either completed the preference or novelty version with two test trials
+in each of the four conditions. Before discussing the empirical results,
+we briefly discuss the cognitive model we used to predict expectation
+integration.
 
@@
 to refer to the object by reasoning about a naive listener who does not
-know the labels for the object (Frank \& Goodman, 2014). Mathematically,
-the probability that the listener chooses a referent given an utterance
-is defined as follows:\\
-\[P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)\] Here, \(P_S(u|r_s)\) is the
-likelihood that the speaker will use an utterance to refer to a specific
-referent. It is defined as the surprisal of an utterance given the
-referent for a naive listener, who interprets utterances in a literal
-way:
-
-\[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\]
-
-The numerical strength of the expression above depends on \(\alpha\),
-which can be interpreted as an indicator of how rational the speaker is
-in choosing utterances.
+know the labels for the object (Frank \& Goodman, 2014). The conditional
+probability that the listener chooses a referent given an utterance is
+defined as follows: \[P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)\] Here,
+\(P_S(u|r_s)\) is the likelihood that the speaker will use an utterance
+u to refer to a specific referent r. It is defined in terms of a utility
+function \(U_S(u;s)\) consisting of the surprisal of \(u\) for a naive
+listener \(L_0\), who interprets \(u\) according its literal semantics:
+\[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\] The numerical strength of the
+expression above depends on \(\alpha\) scalar value, α, which can be
+interpreted as an indicator of how rational the speaker is in choosing
+utterances (i.e.~as alpha increases, the speaker is more likely to
+choose the most informative utterance).
 
@@
 
-In our model, we used the results from Experiment 1 and 2 to specify
-\(\alpha\) as well as \(P_S(r_s)\). The former was set to yield the
-proportion measured in Experiment 1 in a model with uniform priors. The
-prior probability for each object was the proportion with which this
-object was chosen in Experiment
+We used the results from Experiment 1 and 2 to specify \(\alpha\) as
+well as \(P_S(r_s)\) in our model. We set \(\alpha\) so that a model
+with uniform priors would predict the average proportion measured in
+Experiment 1. The prior probability for each object was set to be the
+proportion with which this object was chosen in Experiment
 2\footnote{Proportions were measured when participants chose between two objects.
@@
 Based on these parameter settings, we predicted the proportion with
-which listeners will choose the less frequent object in each unique
-combination of alignment and speaker identity separately for each prior
-manipulation (eight conditions total, see Figure \ref{fig:plotexp3}). We
-compared the fit of this pragmatic model to two alternative models using
-Bayes Factors (BF). The first alternative model ignored the speaker
-specific expectations (flat prior model) while the second ignored the
-informativeness inference (prior only model). To capture the idea that
-behavioral data is to some degree noisy, all models included a ``noise
-parameter'', which reflects that, with a certain probability,
-participants respond randomly instead of in line with the intended
-manipulation on a given trial. Noise parameters are estimated based on
-the data.
+which listeners will choose the more informative object in each of eight
+unique conditions mentioned above (see also Figure \ref{fig:plotexp3}).
+We compared the fit of this pragmatic model to two alternative models
+using Bayes Factors (BF). The first alternative model ignored the
+speaker specific expectations (uniform prior model) while the second
+ignored the informativeness inference (prior only model).
 
 \subsection{Results and Discussion}\label{results-and-discussion-2}
+
+Results are discussed in the form of the proportion with which listeners
+chose the more informative object (i.e., the object that would be the
+more informative referent when only considering speaker general
+information). For a comparison to chance within each unique condition
+see \ref{fig:plotexp3}. Combinations of alignment and speaker identity
+differed in how they influenced participants' responses (GLMM model
+term: \texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57, \emph{p}
+\textless{} .001). Figure \ref{fig:plotmodelcomp}A and B shows the mean
+response in each unique condition compared to the pragmatics model.
+Model predictions and data were highly correlated (r = 0.96, \emph{p}
+\textless{} .001).Model fit was much better in the model taking into
+account both types of expectations compared to the uniform prior (BF =
+2e+79) or prior only model (BF = 1.8e+34).
+
+Interestingly, as in Experiment 2, there was a transfer of preference in
+the case of speaker change. Participants were at chance in the
+preference - different speaker - incongruent condition (see Figure
+\ref{fig:plotexp3}). If preference would have been specific to a
+particular individual, participants should have selected the less
+frequent object above chance (as they did in the corresponding condition
+with the novelty manipulation). Because it takes into account the
+measurement from the earlier experiment, our model predicts these
+results; future work might explicitly model generalization across
+speakers.
+
+\section{Experiment 4}\label{experiment-4}
+
+In Experiment 4, we replicated and extended Experiment 3 by manipulating
+the strength of the common ground expectations. Our main goal was to
+investigate the quantitative accuracy of our cognitive model and we
+therefore limit the description of the methods and the discussion of the
+results to the aspects relevant to the comparison between model
+predictions and data.
+
+\subsection{Participants, Design and
+Procedure}\label{participants-design-and-procedure-3}
+
+This experiment had 453 participants. The structure of the experiment
+was the same as in Experiment 3. For each common ground expectation
+(preference and novelty), we intended to have a strong, a medium and a
+weak condition. The strength of each condition was determined by the
+proportion with which participants chose the preferred/novel object
+given the manipulation. We succeeded in generating quantitative
+variability for novelty. For preference we piloted a number of
+additional manipulations but did no find one that yielded a weaker
+preference compared to a medium condition.
+
+The strong manipulations were identical to Experiment 3 and the results
+are therefore a direct replication (see Figure
+\ref{fig:plotmodelcomp}C). For novelty, in the medium condition, the
+animal turned to each table only once before the test. In the weak
+condition, the animal only turned to the table with an object before the
+test (instead of turning to and commenting on both). In the medium
+condition for preference, the animal only expressed liking and did so in
+a more subtle way (saying only: ``Oh, wow'' while pointing to the
+object). Participants were assigned to one level of common ground
+expectation and completed two test trials in each of the four conditions
+(alignment x speaker change).
+
+Model predictions were obtained in the same way as in Experiment 3; with
+\(\alpha\) inferred from the data and \(P_S(r_s)\) measured empirically
+(in a set of corresponding experiments parallel to Experiment 2).
+
+\subsection{Results and Discussion}\label{results-and-discussion-3}
 
@@
 \caption[(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4]{(A) Model predictions compared to data for Experiment 3 and (B) Experiment 4.
-(C) Data for strong prior manipualtion in Experiment 3 and 4.
+(C) Data for strong prior manipulation in Experiment 3 and 4, providing a noise ceiling for the reliability of measurements.
 Error bars = 95 \%  HDIs.}\label{fig:plotmodelcomp}
@@
 
-Results are discussed in the form of the proportion with which listeners
-chose the less frequent object. For a comparison to chance within each
-unique condition see Figure \ref{fig:plotexp3}. Both alignment and
-speaker identity influenced participants' responses (GLMM model term:
-\texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57, \emph{p}
-\textless{} .001). Figure \ref{fig:plotmodelcomp} shows the mean
-response in each unique condition compared to the model. Model
-predictions and data were highly correlated (r = 0.96, \emph{p}
-\textless{} .001). Model fit was better in the model taking into account
-both types of expectations compared to the flat prior (BF = 2e+79) or
-prior only model (BF = 1.8e+34).
-
-Interestingly, like in Experiment 2, there was a transfer of preference
-in case of a speaker change. Participants were at chance in the
-preference - different speaker - incongruent condition (see Figure
-\ref{fig:plotexp3}). If preference would have been specific to a
-particular individual, participants should have selected the less
-frequent object above chance (as they did in the corresponding condition
-with the novelty manipulation).
-
-\section{Experiment 4}\label{experiment-4}
-
-In Experiment 4, we replicated and extended Experiment 3 by manipulating
-the strength of the common ground expectations. Our main goal was to
-investigate the scope of our cognitive model and we therefore limit the
-description of the methods and the discussion of the results to the
-aspects relevant to the comparison between model predictions and data.
-
-\subsection{Participants, Design and
-Procedure}\label{participants-design-and-procedure-3}
-
-This experiment had 453 participants. The structure of the experiment
-was the same as in Experiment 3. For each common ground expectation
-(preference and novelty), we intended to have a strong, a medium and a
-weak manipulation. The strength of each manipulation was determined by
-the proportion with which participants chose the preferred / novel
-object given the manipulation. We succeeded in this for novelty. For
-preference we did not find a manipulation that yielded only a weak
-preference.
-
-The strong manipulations were identical to Experiment 3 and the results
-are therefore a direct replication. For novelty, in the medium
-manipulation, the animal turned to each table only once before the test.
-In the weak manipulation, the animal only turned to the table with an
-object before the test. In the medium manipulation for preference, the
-animal only expressed liking and did so in a more subtle way (saying
-only: ``Oh, wow''). Participants were assigned to one level of common
-ground expectation and completed two test trials in each of the four
-conditions.
-
-Model predictions were obtained in the same way as in Experiment 3. The
-likelihood term of the model was identical. For the each level of common
-ground expectation, we measured the proportion with which participants
-chose the preferred / novel object in a separate experiment. Due to
-space limitations, we do not discuss them in any more detail here. Like
-in Experiment 3, the results of these experiments were used to specify
-the prior distribution in the model.
-
-\subsection{Results and Discussion}\label{results-and-discussion-3}
-
-As noted above, the strong prior manipulation was a direct replication
-of Experiment 3. Results from the two rounds of data collection were
-highly correlated (r = 0.97, \emph{p} \textless{} .001, see Figure
+As noted above, the strong prior condition was a direct replication of
+Experiment 3. Results from the two rounds of data collection were highly
+correlated (r = 0.97, \emph{p} \textless{} .001, see Figure
 \ref{fig:plotmodelcomp}C). Across levels of prior manipulation, the data
@@
 predictions (r = 0.91, \emph{p} \textless{} .001, see Figure
-\ref{fig:plotmodelcomp}B). Again, the pragmatic model provided a better
-fit compared to the flat prior (BF = 4.4e+74 ) or prior only model (BF =
-1.8e+84).
+\ref{fig:plotmodelcomp}B). Again, the pragmatics model provided a much
+better fit compared to the flat prior (BF = 4.4e+74 ) or prior only
+model (BF = 1.8e+84).
 
@@
 Language use and learning requires balancing different types of
-expectations about one's interlocutor. Here we used a Bayesian cognitive
-model to predict this integration process. Experiment 1 and 2 replicated
-earlier studies showing that adult listeners expect speakers to produce
-utterances in an informative way as well as in light of common ground.
-Next, we combined the procedures from the first two experiments to study
-how listeners would integrate them. We used the results from Experiment
-1 and 2 to specify the model parameters that represented the two types
-of expectations and make parameter-free predictions about new behavior.
-Experiments 3 and 4 showed that both types of expectations influenced
-listeners inferences. In general, listener behavior accurately described
-by our model, suggesting that -- at least in population aggregate --
-listeners trade off flexibly between speaker specific and general
-pragmatic expectations.
+expectations about one's interlocutor - both expectations about how
+speakers behave in general and specific expectations about how a
+particular speaker might behave in a particular context. Here we used a
+computational pragmatics model to predict this integration process.
+Experiment 1 and 2 replicated previous studies showing that adult
+listeners expect speakers to produce utterances informatively and also
+with respect to common ground. We then combined the procedures from the
+first two experiments to study how listeners would integrate these two
+types of information. We used the results from Experiment 1 and 2 to
+specify model parameters that represented the two types of expectations,
+generating predictions about new behavior. Experiments 3 and 4 showed
+that both types of expectations influenced listeners inferences. In
+general, listener behavior was accurately described by our model,
+suggesting that listeners trade-off flexibly between speaker specific
+and general pragmatic expectations.
 
 Notably, Experiment 3 also included situations in which the two
-expectations were in conflict. For example, in some trials the animal
+expectations were in conflict. For example, in some trials the speaker
 expressed preference for object A, which was also the more frequent
-object. In these situations, participants chose the preferred object as
-the referent (see also Figure \ref{fig:plotexp3}). A simple explanation
-for this pattern might be that common ground manipulations were simply
-``stronger'' in that they produced higher rates of expected choice when
-presented on their own (see Figure \ref{fig:plotexp12}). However, in
-Experiment 4 we observed the same pattern in the medium manipulation for
-novelty (results not discussed above, see online repository for details)
-even though the manipulation alone yielded numerically weaker results
-compared to the general expectation in Experiment 1. In each case, the
-pattern in the data was predicted by the model This illustrates the
-conditional nature of pragmatic inference: The informativeness of an
-utterance critically depends on the context, including common ground. If
-prior interactions already single out one object as the more likely
-referent, subsequent considerations of informativeness take place in
-light of this prior information and not independent of it.
+(less informative) object. In these situations, a majority of
+participants chose the preferred object as the referent (see also Figure
+\ref{fig:plotexp3} preference--same speaker--incongruent). A simple
+explanation for this pattern might be that common ground manipulations
+were simply ``stronger'', corroborated by the fact they produced higher
+rates of expected choice than the informativeness expectation when the
+two were presented in isolation (see Figure \ref{fig:plotexp12}). In
+Experiment 4, however, the medium manipulation for novelty yielded
+numerically weaker results compared to the informativeness expectation
+in Experiment 1, and yet participants still selected the novel object
+above chance when the expectations were in conflict. Why is this?
+
+Because common ground is represented in our model as the listener's
+prior distribution, speakers can reason about it in choosing their
+utterance.That is, in the mind of the listener, the speaker computes the
+effect of each utterance on a naive listener with shared common ground.
+Therefore, when prior interactions implicate one object as the more
+likely referent, the speaker reasons that this object will be the
+inferred referent of any semantically plausible utterance, even when the
+same utterance would point to a different object in the absence of prior
+information.
 
@@
 
-A logical next step will be to extend the work presented here to
-children. As outlined above, pragmatic reasoning is though to play an
-important role in how children learn new words. An ontogenetic study
-would also show to what extent the modelling approach taken here is
-suitable to address questions about development. Another fruitful future
-direction would be to experimentally manipulate expectations about
-speaker informativeness. For example, if a speaker repeatedly behaves in
-an irrational way (e.g.~labels dogs as cats), listeners might be less
-inclined to assume that utterances containing novel words are produced
-in an informative way.
-
 This work integrates different perspectives on the study of pragmatic
@@
 
-\vspace{1em}
-\fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}}
-\vspace{1em}
-
 \section{Acknowledgements}\label{acknowledgements}
 
-MB received funding from the European Union's Horizon 2020 research and
-innovation programme under the Marie Sklodowska-Curie grant agreement No
-749229.
+Masked for peer review.
 

### 2019-01-29 papers/cogsci2019/cogsci2019.Rmd
add saves to cogsci folder

@@
 In both experiments, listeners based their inferences on both types of expectations.
-We found that model performance was also consistent with this finding; with better fit for a model which incorporated both general- and specific-information compared to baselines incorporating only one type.
+We found that model performance was also consistent with this finding; with better fit for a model which incorporated both general and specific information compared to baselines incorporating only one type.
 Listeners flexibly integrate different forms of social expectations across a range of contexts, a process which can be described using Bayesian models of pragmatic reasoning.
-Our approach highlights how experiments and computational models can be used in conjunction to inform theories about language use and comprehension.
 
@@
 On the one hand, speakers and listeners have the general expectation that their partner communicates in an informative and relevant way [@sperber2001relevance].
-Grice [-@grice1991studies] summarised this expectation via the “Cooperative Principle”: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the Cooperative Principle describes a second type of expectation: interlocutors expect each other to produce and interpret utterances *in light of the shared common ground between them* [@clark1996using].
+Grice [-@grice1991studies] summarised this expectation via the *Cooperative Principle*: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Importantly, the second half of the Cooperative Principle describes a second type of expectation: interlocutors expect each other to produce and interpret utterances *in light of the shared common ground between them* [@clark1996using].
 Common ground refers to bits of information that are assumed to be shared, either because they were mentioned over the course of the conversation or grounded through some form of joint experience [@bohn2018common].
@@
 We operationalize speaker-specific, common ground information as the shared prior probability of referents in the context of the utterance.
-Thus, a natural locus for information integration within these models is the tradeoff between the prior probability of a particular referent and the likelihood of that referent given the current utterance.
+Thus, a natural locus for information integration within these models is the trade off between the prior probability of a particular referent and the likelihood of that referent given the current utterance.
 
@@
 Experiments were conducted online using Amazon’s Mechanical Turk.
-Figure \ref{fig:design} provides a schematic overview of the setup and experimental procedures.
+Fig.
+\ref{fig:design} provides a schematic overview of the setup and experimental procedures.
 The instructions informed participants that they would see a number of animal characters asking for novel toys.
@@
 Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
-Experiment 3 (right) combined manipulations.
+Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).
 When expressing e.g.
 preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
-Condition shown here: preference - same speaker - incongruent.
-Green plus signs represent an expression of preference and red minus of dispreference (see main text for details)."}
+Experiment 3 (right) combined manipulations.
+Condition shown here: preference - same speaker - incongruent."}
 img <- png::readPNG("figs/method_figure.png")
@@
 Experiment 1 had 40 participants.
-In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Figure \ref{fig:design}, left).
+In the test condition, one table contained one object of type A and the other table contained one object of type A and one of type B (see Fig.
+\ref{fig:design}, left).
 On each trial, the animal introduced themselves (e.g.
@@
 In the control condition, both tables contained two objects, one of which was randomly determined as the correct one.
-No inference was therefore licenced.
+No inference was therefore licensed.
 Each participant received three trials in each condition for a total of six trials, presented in a randomized order.
@@
 
-Participants selected the less frequent object above chance in the test condition (t(`r ex1t%>%filter(control == "false")%>%pull(df)`) = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to the control condition (genreralized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker (animal).}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p*  `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Participants selected the less frequent object above chance in the test condition (t(`r ex1t%>%filter(control == "false")%>%pull(df)`) = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Fig.
+\ref{fig:plotexp12}) and did so more often compared to the control condition (generalized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker.}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p* `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
 This result replicates earlier work [@frank2014inferring] and is consistent with the hypothesis that listeners expect speakers to communicate in an informative way.
@@
 1).
-Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95 \\% CIs.
+Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95\\% CIs.
 Dashed line indicates performance expected by chance."}
@@
   geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = .7)+
+  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = .5)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 Then, the animal disappeared.
-After a short period of time, either the same or a different animal appeared and requested an object while facing straight ahead (see Figure \ref{fig:design}, middle).
+After a short period of time, either the same or a different animal appeared and requested an object while facing straight ahead (see Fig.
+\ref{fig:design}, middle).
 If participants took into account the information they gained about the speaker, they should select the previously preferred object if the returning animal was the same.
@@
 
-In the novelty condition, one table was initially empty while there was an object on the other table (see Figure \ref{fig:design}).
+In the novelty condition, one table was initially empty while there was an object on the other table (see Fig.
+\ref{fig:design}).
 The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
@@
 
-Participants selected the preferred object above chance when the same animal returned (t(`r ex2tpref%>%filter(control == "false")%>%pull(df)`) = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Participants selected the preferred object above chance when the same animal returned (t(`r ex2tpref%>%filter(control == "false")%>%pull(df)`) = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Fig.
+\ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
 Thus, listeners inferred the referent of the utterance by considering previous interactions with the speaker.
@@
 
-The novel object was selected above chance when the same animal returned (t(`r ex2tnov%>%filter(control == "false")%>%pull(df)`) = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t(`r ex2tnov%>%filter(control == "true")%>%pull(df)`) = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Figure \ref{fig:plotexp12}).
+The novel object was selected above chance when the same animal returned (t(`r ex2tnov%>%filter(control == "false")%>%pull(df)`) = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t(`r ex2tnov%>%filter(control == "true")%>%pull(df)`) = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Fig.
+\ref{fig:plotexp12}).
 Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
@@
 Dashed line indicates performance expected by chance.
-Plotting conventions are the same as in Figure 2.
+Plotting conventions are the same as in Fig.
+2.
 All conditions in which CIs do not overlap with chance line are also statistically different from chance based on two-tailed Wilcoxon tests."}
@@
   geom_jitter(data = p3, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .7)+
+  geom_pointrange(data = p4, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .5)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
-In Experiment 3, we combined the expectations studied in Experiment 1 and 2 to study how listeners integrate them.
+In Experiment 3, we combined the expectations studied in Experiment 1 and 2 to see how listeners integrate them.
 
@@
 In Experiment 3, however, we manipulated common ground expectations in the same way as in Experiment 2.
-For example, the animal would turn to the table with one object and express that they don’t like object A, then they would turn to the other table and express that they like object B.
-Next, after quickly disappearing, the animal would reappear, turn to the table with two objects and make a request (see Figure \ref{fig:design}, right).
+For example, the animal would turn to the table with one object and express that they don’t like object A, then turn to the other table and express that they like object B.
+Next, after quickly disappearing, they would reappear, turn to the table with two objects and make a request (see Fig.
+\ref{fig:design}, right).
 
@@
 $$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$
-The numerical strength of the expression above depends on $\alpha$ scalar value, α, which can be interpreted as an indicator of how rational the speaker is in choosing utterances (i.e.
-as alpha increases, the speaker is more likely to choose the most informative utterance).
+The numerical strength of the expression above depends on a scalar value, $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances (i.e.
+as $\alpha$ increases, the speaker is more likely to choose the most informative utterance).
 
@@
 For each object we used the proportion measured in Experiment 2 as the prior probability.This approached spread out the absolute probability mass for each object but conserved the relative relation between objects.}.
-Based on these parameter settings, we predicted the proportion with which listeners will choose the more informative object in each of eight unique conditions mentioned above (see also Figure \ref{fig:plotexp3}).
+Based on these parameter settings, we predicted the proportion with which listeners will choose the more informative object in each of eight unique conditions mentioned above (see also Fig.
+\ref{fig:plotexp3}).
 We compared the fit of this pragmatic model to two alternative models using Bayes Factors (BF).
 The first alternative model ignored the speaker specific expectations (uniform prior model) while the second ignored the informativeness inference (prior only model).
+All models included a noise parameter, reflecting that participants may respond randomly instead of in line with the intended manipulation on a given trial.
+Noise parameters were estimated based on the data.
+They range between 0 and 1 and reflect the proportion of responses that are estimated to be random instead of following the pattern predicted by the model.
 
@@
 Combinations of alignment and speaker identity differed in how they influenced participants’ responses (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
-Figure \ref{fig:plotmodelcomp}A and B shows the mean response in each unique condition compared to the pragmatics model.
+Fig.
+\ref{fig:plotmodelcomp}A and B shows the mean response in each unique condition compared to the pragmatics model.
 Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).Model fit was much better in the model taking into account both types of expectations compared to the uniform prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
@@
 Prior only") %>%pull(BayesFactor), digits = 2)`).
+The inferred noise level in the pragmatics model was 0.27 (95% HDI: 0.21 - 0.34].
 
 Interestingly, as in Experiment 2, there was a transfer of preference in the case of speaker change.
-Participants were at chance in the preference - different speaker - incongruent condition (see Figure \ref{fig:plotexp3}).
+Participants were at chance in the preference - different speaker - incongruent condition (see Fig.
+\ref{fig:plotexp3}).
 If preference would have been specific to a particular individual, participants should have selected the less frequent object above chance (as they did in the corresponding condition with the novelty manipulation).
@@
 
-In Experiment 4, we replicated and extended Experiment 3 by manipulating the strength of the common ground expectations.
-Our main goal was to investigate the quantitative accuracy of our cognitive model and we therefore limit the description of the methods and the discussion of the results to the aspects relevant to the comparison between model predictions and data.
+Here we replicated and extended Experiment 3 by manipulating the strength of the common ground expectations.
 
@@
 
-The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication (see Figure \ref{fig:plotmodelcomp}C).
+The strong manipulations were identical to Experiment 3 and the results are therefore a direct replication (see Fig.
+\ref{fig:plotmodelcomp}C).
 For novelty, in the medium condition, the animal turned to each table only once before the test.
@@
 (C) Data for strong prior manipulation in Experiment 3 and 4, providing a noise ceiling for the reliability of measurements.
-Error bars = 95 \\%  HDIs."}
+Error bars = 95\\% HDIs."}
 
@@
 As noted above, the strong prior condition was a direct replication of Experiment 3.
-Results from the two rounds of data collection were highly correlated (r = `r repl_r$estimate`, *p* `r repl_r$p.value`, see Figure \ref{fig:plotmodelcomp}C).
-Across levels of prior manipulation, the data from Experiment 4 were highly correlated to the corresponding model predictions (r = `r ex4_comp_r$estimate`, *p* `r ex4_comp_r$p.value`, see Figure \ref{fig:plotmodelcomp}B).
+Results from the two rounds of data collection were highly correlated (r = `r repl_r$estimate`, *p* `r repl_r$p.value`, see Fig.
+\ref{fig:plotmodelcomp}C).
+Across levels of prior manipulation, the data from Experiment 4 were highly correlated to the corresponding model predictions (r = `r ex4_comp_r$estimate`, *p* `r ex4_comp_r$p.value`, see Fig.
+\ref{fig:plotmodelcomp}B).
 Again, the pragmatics model provided a much better fit compared to the flat prior (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
-No prior") %>%pull(BayesFactor),digits = 2)` ) or prior only model (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
+No prior") %>%pull(BayesFactor),digits = 2)`) or prior only model (BF = `r format(bf_ex4%>%filter(Comparison == "Pragmatic vs.
 Prior only") %>%pull(BayesFactor), digits = 2)`).
+The inferred noise level in the pragmatics model was 0.28 (95% HDI: 0.24 - 0.32].
 
@@
 Language use and learning requires balancing different types of expectations about one’s interlocutor - both expectations about how speakers behave in general and specific expectations about how a particular speaker might behave in a particular context.
-Here we used a computational pragmatics model to predict this integration process.
+Here we used a Bayesian pragmatics model to predict this integration process.
 Experiment 1 and 2 replicated previous studies showing that adult listeners expect speakers to produce utterances informatively and also with respect to common ground.
-We then combined the procedures from the first two experiments to study how listeners would integrate these two types of information.
+We then combined the procedures from the first two experiments to study how listeners would integrate expectations.
 We used the results from Experiment 1 and 2 to specify model parameters that represented the two types of expectations, generating predictions about new behavior.
 Experiments 3 and 4 showed that both types of expectations influenced listeners inferences.
-In general, listener behavior was accurately described by our model, suggesting that listeners trade-off flexibly between speaker specific and general pragmatic expectations.
+Overall, listener behavior was accurately described by our model, suggesting that listeners trade-off flexibly between speaker specific and general pragmatic expectations.
 
@@
 For example, in some trials the speaker expressed preference for object A, which was also the more frequent (less informative) object.
-In these situations, a majority of participants chose the preferred object as the referent (see also Figure \ref{fig:plotexp3} preference--same speaker--incongruent).
-A simple explanation for this pattern might be that common ground manipulations were simply “stronger”, corroborated by the fact they produced higher rates of expected choice than the informativeness expectation when the two were presented in isolation (see Figure \ref{fig:plotexp12}).
+In these situations, a majority of participants chose the preferred object as the referent (see also Fig.
+\ref{fig:plotexp3} preference--same speaker--incongruent).
+A simple explanation for this pattern might be that common ground manipulations were simply “stronger”, corroborated by the fact they produced higher rates of expected choice than the informativeness expectation when the two were presented in isolation (see Fig.
+\ref{fig:plotexp12}).
 In Experiment 4, however, the medium manipulation for novelty yielded numerically weaker results compared to the informativeness expectation in Experiment 1, and yet participants still selected the novel object above chance when the expectations were in conflict.
 Why is this?
-
-Because common ground is represented in our model as the listener’s prior distribution, speakers can reason about it in choosing their utterance.That is, in the mind of the listener, the speaker computes the effect of each utterance on a naive listener with shared common ground.
+Because common ground is represented in our model as the listener’s prior distribution, speakers can reason about it in choosing their utterance.
+That is, in the mind of the listener, the speaker computes the effect of each utterance on a naive listener with shared common ground.
 Therefore, when prior interactions implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of prior information.

### 2019-01-29 papers/cogsci2019/cogsci2019.tex
add saves to cogsci folder

@@
 consistent with this finding; with better fit for a model which
-incorporated both general- and specific-information compared to
-baselines incorporating only one type. Listeners flexibly integrate
-different forms of social expectations across a range of contexts, a
-process which can be described using Bayesian models of pragmatic
-reasoning. Our approach highlights how experiments and computational
-models can be used in conjunction to inform theories about language use
-and comprehension.
+incorporated both general and specific information compared to baselines
+incorporating only one type. Listeners flexibly integrate different
+forms of social expectations across a range of contexts, a process which
+can be described using Bayesian models of pragmatic reasoning.
 
@@
 Wilson, 2001). Grice (1991) summarised this expectation via the
-``Cooperative Principle'': ``Make your contribution such as is required,
-at the stage at which it occurs, by the accepted purpose or direction of
-the talk exchange in which you are engaged.'' Importantly, the second
-half of the Cooperative Principle describes a second type of
+\emph{Cooperative Principle}: ``Make your contribution such as is
+required, at the stage at which it occurs, by the accepted purpose or
+direction of the talk exchange in which you are engaged.'' Importantly,
+the second half of the Cooperative Principle describes a second type of
 expectation: interlocutors expect each other to produce and interpret
@@
 natural locus for information integration within these models is the
-tradeoff between the prior probability of a particular referent and the
+trade off between the prior probability of a particular referent and the
 likelihood of that referent given the current utterance.
@@
 
-Experiments were conducted online using Amazon's Mechanical Turk. Figure
+Experiments were conducted online using Amazon's Mechanical Turk. Fig.
 \ref{fig:design} provides a schematic overview of the setup and
@@
 Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
-Experiment 3 (right) combined manipulations.
+Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).
 When expressing e.g.
 preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
-Condition shown here: preference - same speaker - incongruent.
-Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).}\label{fig:design}
+Experiment 3 (right) combined manipulations.
+Condition shown here: preference - same speaker - incongruent.}\label{fig:design}
 \end{figure*}
@@
 condition, one table contained one object of type A and the other table
-contained one object of type A and one of type B (see Figure
+contained one object of type A and one of type B (see Fig.
 \ref{fig:design}, left). On each trial, the animal introduced themselves
@@
 objects, one of which was randomly determined as the correct one. No
-inference was therefore licenced. Each participant received three trials
+inference was therefore licensed. Each participant received three trials
 in each condition for a total of six trials, presented in a randomized
@@
 Participants selected the less frequent object above chance in the test
-condition (t(39) = 5.51, \emph{p} \textless{} .001, see Figure
+condition (t(39) = 5.51, \emph{p} \textless{} .001, see Fig.
 \ref{fig:plotexp12}) and did so more often compared to the control
-condition (genreralized linear mixed model
-(GLMM\footnote{All models included random effects for subject and speaker (animal).}):\emph{\(\beta\)}
+condition (generalized linear mixed model
+(GLMM\footnote{All models included random effects for subject and speaker.}):\emph{\(\beta\)}
 = 1.49, se = 0.5 \emph{p} = .003). This result replicates earlier work
@@
 1).
-Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95 \% CIs.
+Transparent dots show data from individual participants, solid dots represent condition means, error bars are 95\% CIs.
 Dashed line indicates performance expected by chance.}\label{fig:plotexp12}
@@
 different animal appeared and requested an object while facing straight
-ahead (see Figure \ref{fig:design}, middle). If participants took into
+ahead (see Fig. \ref{fig:design}, middle). If participants took into
 account the information they gained about the speaker, they should
@@
 In the novelty condition, one table was initially empty while there was
-an object on the other table (see Figure \ref{fig:design}). The animal
+an object on the other table (see Fig. \ref{fig:design}). The animal
 turned to one of the sides and commented either on the presence (``Aha,
@@
 Participants selected the preferred object above chance when the same
-animal returned (t(39) = 29.14, \emph{p} \textless{} .001, see Figure
+animal returned (t(39) = 29.14, \emph{p} \textless{} .001, see Fig.
 \ref{fig:plotexp12}) and did so more often compared to trials in which a
@@
 (t(39) = 6.77, \emph{p} \textless{} .001) but not when a different one
-appeared (t(39) = 1.49, \emph{p} = .144, see Figure
-\ref{fig:plotexp12}). Furthermore, the two conditions differed in the
-expected direction (\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{}
-.001). Thus, like children (Akhtar et al., 1996), adults used their
-prior information about the speaker to resolve ambiguity in the
-utterance.
+appeared (t(39) = 1.49, \emph{p} = .144, see Fig. \ref{fig:plotexp12}).
+Furthermore, the two conditions differed in the expected direction
+(\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{} .001). Thus, like
+children (Akhtar et al., 1996), adults used their prior information
+about the speaker to resolve ambiguity in the utterance.
 
@@
 Dashed line indicates performance expected by chance.
-Plotting conventions are the same as in Figure 2.
+Plotting conventions are the same as in Fig.
+2.
 All conditions in which CIs do not overlap with chance line are also statistically different from chance based on two-tailed Wilcoxon tests.}\label{fig:plotexp3}
@@
 In Experiment 3, we combined the expectations studied in Experiment 1
-and 2 to study how listeners integrate them.
+and 2 to see how listeners integrate them.
 
@@
 2. For example, the animal would turn to the table with one object and
-express that they don't like object A, then they would turn to the other
-table and express that they like object B. Next, after quickly
-disappearing, the animal would reappear, turn to the table with two
-objects and make a request (see Figure \ref{fig:design}, right).
+express that they don't like object A, then turn to the other table and
+express that they like object B. Next, after quickly disappearing, they
+would reappear, turn to the table with two objects and make a request
+(see Fig. \ref{fig:design}, right).
 
@@
 \[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\] The numerical strength of the
-expression above depends on \(\alpha\) scalar value, α, which can be
+expression above depends on a scalar value, \(\alpha\), which can be
 interpreted as an indicator of how rational the speaker is in choosing
-utterances (i.e.~as alpha increases, the speaker is more likely to
+utterances (i.e.~as \(\alpha\) increases, the speaker is more likely to
 choose the most informative utterance).
@@
 which listeners will choose the more informative object in each of eight
-unique conditions mentioned above (see also Figure \ref{fig:plotexp3}).
-We compared the fit of this pragmatic model to two alternative models
-using Bayes Factors (BF). The first alternative model ignored the
-speaker specific expectations (uniform prior model) while the second
-ignored the informativeness inference (prior only model).
+unique conditions mentioned above (see also Fig. \ref{fig:plotexp3}). We
+compared the fit of this pragmatic model to two alternative models using
+Bayes Factors (BF). The first alternative model ignored the speaker
+specific expectations (uniform prior model) while the second ignored the
+informativeness inference (prior only model). All models included a
+noise parameter, reflecting that participants may respond randomly
+instead of in line with the intended manipulation on a given trial.
+Noise parameters were estimated based on the data. They range between 0
+and 1 and reflect the proportion of responses that are estimated to be
+random instead of following the pattern predicted by the model.
 
@@
 term: \texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57, \emph{p}
-\textless{} .001). Figure \ref{fig:plotmodelcomp}A and B shows the mean
+\textless{} .001). Fig. \ref{fig:plotmodelcomp}A and B shows the mean
 response in each unique condition compared to the pragmatics model.
@@
 account both types of expectations compared to the uniform prior (BF =
-2e+79) or prior only model (BF = 1.8e+34).
+2e+79) or prior only model (BF = 1.8e+34). The inferred noise level in
+the pragmatics model was 0.27 (95\% HDI: 0.21 - 0.34{]}.
 
@@
 the case of speaker change. Participants were at chance in the
-preference - different speaker - incongruent condition (see Figure
+preference - different speaker - incongruent condition (see Fig.
 \ref{fig:plotexp3}). If preference would have been specific to a
@@
 
-In Experiment 4, we replicated and extended Experiment 3 by manipulating
-the strength of the common ground expectations. Our main goal was to
-investigate the quantitative accuracy of our cognitive model and we
-therefore limit the description of the methods and the discussion of the
-results to the aspects relevant to the comparison between model
-predictions and data.
+Here we replicated and extended Experiment 3 by manipulating the
+strength of the common ground expectations.
 
@@
 The strong manipulations were identical to Experiment 3 and the results
-are therefore a direct replication (see Figure
-\ref{fig:plotmodelcomp}C). For novelty, in the medium condition, the
-animal turned to each table only once before the test. In the weak
-condition, the animal only turned to the table with an object before the
-test (instead of turning to and commenting on both). In the medium
-condition for preference, the animal only expressed liking and did so in
-a more subtle way (saying only: ``Oh, wow'' while pointing to the
-object). Participants were assigned to one level of common ground
-expectation and completed two test trials in each of the four conditions
-(alignment x speaker change).
+are therefore a direct replication (see Fig. \ref{fig:plotmodelcomp}C).
+For novelty, in the medium condition, the animal turned to each table
+only once before the test. In the weak condition, the animal only turned
+to the table with an object before the test (instead of turning to and
+commenting on both). In the medium condition for preference, the animal
+only expressed liking and did so in a more subtle way (saying only:
+``Oh, wow'' while pointing to the object). Participants were assigned to
+one level of common ground expectation and completed two test trials in
+each of the four conditions (alignment x speaker change).
 
@@
 (C) Data for strong prior manipulation in Experiment 3 and 4, providing a noise ceiling for the reliability of measurements.
-Error bars = 95 \%  HDIs.}\label{fig:plotmodelcomp}
+Error bars = 95\% HDIs.}\label{fig:plotmodelcomp}
 \end{figure*}
@@
 Experiment 3. Results from the two rounds of data collection were highly
-correlated (r = 0.97, \emph{p} \textless{} .001, see Figure
+correlated (r = 0.97, \emph{p} \textless{} .001, see Fig.
 \ref{fig:plotmodelcomp}C). Across levels of prior manipulation, the data
 from Experiment 4 were highly correlated to the corresponding model
-predictions (r = 0.91, \emph{p} \textless{} .001, see Figure
+predictions (r = 0.91, \emph{p} \textless{} .001, see Fig.
 \ref{fig:plotmodelcomp}B). Again, the pragmatics model provided a much
-better fit compared to the flat prior (BF = 4.4e+74 ) or prior only
-model (BF = 1.8e+84).
+better fit compared to the flat prior (BF = 4.4e+74) or prior only model
+(BF = 1.8e+84). The inferred noise level in the pragmatics model was
+0.28 (95\% HDI: 0.24 - 0.32{]}.
 
@@
 particular speaker might behave in a particular context. Here we used a
-computational pragmatics model to predict this integration process.
+Bayesian pragmatics model to predict this integration process.
 Experiment 1 and 2 replicated previous studies showing that adult
@@
 with respect to common ground. We then combined the procedures from the
-first two experiments to study how listeners would integrate these two
-types of information. We used the results from Experiment 1 and 2 to
-specify model parameters that represented the two types of expectations,
+first two experiments to study how listeners would integrate
+expectations. We used the results from Experiment 1 and 2 to specify
+model parameters that represented the two types of expectations,
 generating predictions about new behavior. Experiments 3 and 4 showed
-that both types of expectations influenced listeners inferences. In
-general, listener behavior was accurately described by our model,
+that both types of expectations influenced listeners inferences.
+Overall, listener behavior was accurately described by our model,
 suggesting that listeners trade-off flexibly between speaker specific
@@
 (less informative) object. In these situations, a majority of
-participants chose the preferred object as the referent (see also Figure
+participants chose the preferred object as the referent (see also Fig.
 \ref{fig:plotexp3} preference--same speaker--incongruent). A simple
@@
 rates of expected choice than the informativeness expectation when the
-two were presented in isolation (see Figure \ref{fig:plotexp12}). In
+two were presented in isolation (see Fig. \ref{fig:plotexp12}). In
 Experiment 4, however, the medium manipulation for novelty yielded
@@
 above chance when the expectations were in conflict. Why is this?
-
 Because common ground is represented in our model as the listener's
 prior distribution, speakers can reason about it in choosing their
-utterance.That is, in the mind of the listener, the speaker computes the
-effect of each utterance on a naive listener with shared common ground.
-Therefore, when prior interactions implicate one object as the more
-likely referent, the speaker reasons that this object will be the
+utterance. That is, in the mind of the listener, the speaker computes
+the effect of each utterance on a naive listener with shared common
+ground. Therefore, when prior interactions implicate one object as the
+more likely referent, the speaker reasons that this object will be the
 inferred referent of any semantically plausible utterance, even when the

### 2019-01-29 stats/adults/ex3_2_variable_priors_comparison.Rmd
add kids so and pref models
first draft CogSci paper
add saves to cogsci folder

--- 2018-07-26 stats/ex3_2_variable_priors_comparison.Rmd
@@
 ```{r setup, include=FALSE}
+load("../saves/mcc_model_comparison.RData")
+
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-bf <- data.frame(
+vp.bf <- data.frame(
   Comparison = c("Pragmatic vs. Prior only","Pragmatic vs. No prior", "No Prior vs. Prior only"),
@@
 
-bf%>%
+vp.bf%>%
   kable(digits = 2)
@@
 
+x <- p.llh.plot.variable %>%
+  group_by(Model)%>%
+  summarize(mean = mean(logP))
+
 ```
@@
 
-save.image("mcc_model_comparison.RData")
+save.image("../saves/mcc_model_comparison.RData")
 ```

### 2019-01-29 stats/kids/kids_novel.Rmd
add saves to cogsci folder

--- 2018-10-29 stats/mcc_novel.kids.Rmd
@@
 
-d_new <- read_csv(file="kids_novel.data.csv")%>%
+d_new <- read_csv(file="../data/kids_novel.data.csv")%>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))
 
-d_old <- read_csv(file="kids_novel.data.round1.csv")%>%
+d_old <- read_csv(file="../data/kids_novel.data.round1.csv")%>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"))

### 2019-01-29 papers/cogsci2019/cogsci2019.Rmd
add saves to cogsci folder

@@
 
-pred_ex3 <- readRDS(file = "../../stats/saves/model_predictions_ex3_1.rds")
+pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")
 
-pred_ex4 <- readRDS(file = "../../stats/saves/model_predictions_ex3_variable_priors.rds")
+pred_ex4 <- readRDS(file = "stats/saves/model_predictions_ex3_variable_priors.rds")
 
-bf_ex3 <- readRDS(file = "../../stats/saves/ex3_bf.rds")
+bf_ex3 <- readRDS(file = "stats/saves/ex3_bf.rds")
 
-bf_ex4 <- readRDS(file = "../../stats/saves/ex4_bf.rds")
+bf_ex4 <- readRDS(file = "stats/saves/ex4_bf.rds")
 

### 2019-02-05 papers/cogsci2019/cogsci2019.Rmd
update cogsci submission

@@
 library(langcog)
-library(rwebppl)
 library(matrixStats)
@@
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         control = ifelse(change == "true", "true" , "false"))
+         control = ifelse(change == TRUE, "true" , "false"))
 
 d2 <- read_csv(file="../../stats/data/inf.data.csv") %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))
+  mutate(trial_type = ifelse(trial == "train", "train", "test"),
+         control = ifelse(control == TRUE, "true", "false"))
 
@@
 
-pred_ex4 <- readRDS(file = "stats/saves/model_predictions_ex3_variable_priors.rds")
+pred_ex4 <- readRDS(file = "saves/model_predictions_ex3_variable_priors.rds")
 
-bf_ex3 <- readRDS(file = "stats/saves/ex3_bf.rds")
+bf_ex3 <- readRDS(file = "saves/ex3_bf.rds")
 
-bf_ex4 <- readRDS(file = "stats/saves/ex4_bf.rds")
+bf_ex4 <- readRDS(file = "saves/ex4_bf.rds")
 
@@
 
-Within RSA models, each agent in this recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
+Within RSA models, each agent in the recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
 The speaker-general informativeness expectation is already encoded in the structure of the model: Speakers produce utterances to aid the listener in disambiguating referents.
@@
 Experiment 4 replicates and extends Experiment 3 by varying the strength of common ground assumptions.
+For all experiments, we pre-registered the sample size, experimental design and the statistical analysis.
+For Experiment 3 and 4, we also registered the model structure and predictions (see [masked for peer review])
 
@@
 
-For all experiments, we pre-registered the sample size, experimental design and the statistical analysis.
-For Experiment 3 and 4, we also registered the model structure and predictions (see [masked for peer review])
-
 ```{r design, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=5, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Schematic experimental procedure.
@@
 Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
-Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).
+Green plus signs represent utterances that expressed preference and red minus of dispreference (see main text for details).
+Experiment 3 (right) combined manipulations.
 When expressing e.g.
 preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
-Experiment 3 (right) combined manipulations.
-Condition shown here: preference - same speaker - incongruent."}
+Condition for Experiment 3 shown here: preference - same speaker - incongruent."}
 img <- png::readPNG("figs/method_figure.png")
@@
 A total of 121 individuals participated in the experiment.
-The test situation was the same as in the test condition in Experiment 1: One table with object of type A and the other with an object of type A and B.
+The test situation was the same as in the test condition in Experiment 1 (see Fig.
+\ref{fig:design}, right): One table with object of type A and the other with an object of type A and B.
 Again, the animal always turned to the table with two objects and ambiguously requested an object.
@@
 For example, the animal would turn to the table with one object and express that they don’t like object A, then turn to the other table and express that they like object B.
-Next, after quickly disappearing, they would reappear, turn to the table with two objects and make a request (see Fig.
-\ref{fig:design}, right).
+Next, after quickly disappearing, they would reappear, turn to the table with two objects and make a request.
 
@@
 Participants either completed the preference or novelty version with two test trials in each of the four conditions.
-Before discussing the empirical results, we briefly discuss the cognitive model we used to predict expectation integration.
+Before discussing the empirical results, we briefly discuss the model we used to predict expectation integration.
 
@@
 $$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$
-Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance u to refer to a specific referent r.
+Here, $P_S(u|r_s)$ is the likelihood that the speaker will use an utterance $u$ to refer to a specific referent r.
 It is defined in terms of a utility function $U_S(u;s)$ consisting of the surprisal of $u$ for a naive listener $L_0$, who interprets $u$ according its literal semantics:
@@
 
-Results are discussed in the form of the proportion with which listeners chose the more informative object (i.e., the object that would be the more informative referent when only considering speaker general information).
-For a comparison to chance within each unique condition see \ref{fig:plotexp3}.
+Results are discussed in the form of the proportion with which listeners chose the more informative object (i.e., the object that would be the more informative referent when only considering speaker general expectations).
+For a comparison to chance within each unique condition see Fig.
+\ref{fig:plotexp3}.
 Combinations of alignment and speaker identity differed in how they influenced participants’ responses (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
 Fig.
-\ref{fig:plotmodelcomp}A and B shows the mean response in each unique condition compared to the pragmatics model.
-Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).Model fit was much better in the model taking into account both types of expectations compared to the uniform prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
+\ref{fig:plotmodelcomp}A shows the mean response in each unique condition compared to the pragmatics model.
+Model predictions and data were highly correlated (r = `r model_comp_r$estimate`, *p* `r model_comp_r$p.value`).
+Model fit was much better in the model taking into account both types of expectations compared to the uniform prior (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
 No prior") %>%pull(BayesFactor),digits = 2)`) or prior only model (BF = `r format(bf_ex3%>%filter(Comparison == "Pragmatic vs.
 Prior only") %>%pull(BayesFactor), digits = 2)`).
-The inferred noise level in the pragmatics model was 0.27 (95% HDI: 0.21 - 0.34].
+The inferred noise level in the pragmatics model was 0.27 (95% HDI: 0.21 - 0.34).
 
@@
 Prior only") %>%pull(BayesFactor), digits = 2)`).
-The inferred noise level in the pragmatics model was 0.28 (95% HDI: 0.24 - 0.32].
+The inferred noise level in the pragmatics model was 0.28 (95% HDI: 0.24 - 0.32).
 
@@
 
-Language use and learning requires balancing different types of expectations about one’s interlocutor - both expectations about how speakers behave in general and specific expectations about how a particular speaker might behave in a particular context.
+Language use and learning requires balancing different types of expectations about one’s interlocutor - expectations about how speakers behave in general and expectations about how a particular speaker might behave in a particular context.
 Here we used a Bayesian pragmatics model to predict this integration process.

### 2019-02-05 papers/cogsci2019/cogsci2019.tex
update cogsci submission

@@
 
-Within RSA models, each agent in this recursion is modeled as a Bayesian
+Within RSA models, each agent in the recursion is modeled as a Bayesian
 reasoner; thus, information integration is treated as a process of
@@
 Experiment 4 replicates and extends Experiment 3 by varying the strength
-of common ground assumptions.
+of common ground assumptions. For all experiments, we pre-registered the
+sample size, experimental design and the statistical analysis. For
+Experiment 3 and 4, we also registered the model structure and
+predictions (see {[}masked for peer review{]})
 
@@
 
-For all experiments, we pre-registered the sample size, experimental
-design and the statistical analysis. For Experiment 3 and 4, we also
-registered the model structure and predictions (see {[}masked for peer
-review{]})
-
 \begin{CodeChunk}
@@
 Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
-Green plus signs represent an expression of preference and red minus of dispreference (see main text for details).
+Green plus signs represent utterances that expressed preference and red minus of dispreference (see main text for details).
+Experiment 3 (right) combined manipulations.
 When expressing e.g.
 preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
-Experiment 3 (right) combined manipulations.
-Condition shown here: preference - same speaker - incongruent.}\label{fig:design}
+Condition for Experiment 3 shown here: preference - same speaker - incongruent.}\label{fig:design}
 \end{figure*}
@@
 A total of 121 individuals participated in the experiment. The test
-situation was the same as in the test condition in Experiment 1: One
-table with object of type A and the other with an object of type A and
-B. Again, the animal always turned to the table with two objects and
-ambiguously requested an object. In Experiment 1, the listener had no
-prior information about each object. In Experiment 3, however, we
-manipulated common ground expectations in the same way as in Experiment
-2. For example, the animal would turn to the table with one object and
-express that they don't like object A, then turn to the other table and
-express that they like object B. Next, after quickly disappearing, they
-would reappear, turn to the table with two objects and make a request
-(see Fig. \ref{fig:design}, right).
+situation was the same as in the test condition in Experiment 1 (see
+Fig. \ref{fig:design}, right): One table with object of type A and the
+other with an object of type A and B. Again, the animal always turned to
+the table with two objects and ambiguously requested an object. In
+Experiment 1, the listener had no prior information about each object.
+In Experiment 3, however, we manipulated common ground expectations in
+the same way as in Experiment 2. For example, the animal would turn to
+the table with one object and express that they don't like object A,
+then turn to the other table and express that they like object B. Next,
+after quickly disappearing, they would reappear, turn to the table with
+two objects and make a request.
 
@@
 in each of the four conditions. Before discussing the empirical results,
-we briefly discuss the cognitive model we used to predict expectation
-integration.
+we briefly discuss the model we used to predict expectation integration.
 
@@
 \(P_S(u|r_s)\) is the likelihood that the speaker will use an utterance
-u to refer to a specific referent r. It is defined in terms of a utility
-function \(U_S(u;s)\) consisting of the surprisal of \(u\) for a naive
-listener \(L_0\), who interprets \(u\) according its literal semantics:
-\[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\] The numerical strength of the
-expression above depends on a scalar value, \(\alpha\), which can be
-interpreted as an indicator of how rational the speaker is in choosing
-utterances (i.e.~as \(\alpha\) increases, the speaker is more likely to
-choose the most informative utterance).
+\(u\) to refer to a specific referent r. It is defined in terms of a
+utility function \(U_S(u;s)\) consisting of the surprisal of \(u\) for a
+naive listener \(L_0\), who interprets \(u\) according its literal
+semantics: \[P_S(u|r_s)\propto exp(\alpha U_S(u;s))\] The numerical
+strength of the expression above depends on a scalar value, \(\alpha\),
+which can be interpreted as an indicator of how rational the speaker is
+in choosing utterances (i.e.~as \(\alpha\) increases, the speaker is
+more likely to choose the most informative utterance).
 
@@
 more informative referent when only considering speaker general
-information). For a comparison to chance within each unique condition
-see \ref{fig:plotexp3}. Combinations of alignment and speaker identity
-differed in how they influenced participants' responses (GLMM model
-term: \texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57, \emph{p}
-\textless{} .001). Fig. \ref{fig:plotmodelcomp}A and B shows the mean
+expectations). For a comparison to chance within each unique condition
+see Fig. \ref{fig:plotexp3}. Combinations of alignment and speaker
+identity differed in how they influenced participants' responses (GLMM
+model term: \texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57,
+\emph{p} \textless{} .001). Fig. \ref{fig:plotmodelcomp}A shows the mean
 response in each unique condition compared to the pragmatics model.
 Model predictions and data were highly correlated (r = 0.96, \emph{p}
-\textless{} .001).Model fit was much better in the model taking into
+\textless{} .001). Model fit was much better in the model taking into
 account both types of expectations compared to the uniform prior (BF =
 2e+79) or prior only model (BF = 1.8e+34). The inferred noise level in
-the pragmatics model was 0.27 (95\% HDI: 0.21 - 0.34{]}.
+the pragmatics model was 0.27 (95\% HDI: 0.21 - 0.34).
 
@@
 (BF = 1.8e+84). The inferred noise level in the pragmatics model was
-0.28 (95\% HDI: 0.24 - 0.32{]}.
+0.28 (95\% HDI: 0.24 - 0.32).
 
@@
 Language use and learning requires balancing different types of
-expectations about one's interlocutor - both expectations about how
-speakers behave in general and specific expectations about how a
-particular speaker might behave in a particular context. Here we used a
-Bayesian pragmatics model to predict this integration process.
-Experiment 1 and 2 replicated previous studies showing that adult
-listeners expect speakers to produce utterances informatively and also
-with respect to common ground. We then combined the procedures from the
-first two experiments to study how listeners would integrate
-expectations. We used the results from Experiment 1 and 2 to specify
-model parameters that represented the two types of expectations,
-generating predictions about new behavior. Experiments 3 and 4 showed
-that both types of expectations influenced listeners inferences.
-Overall, listener behavior was accurately described by our model,
-suggesting that listeners trade-off flexibly between speaker specific
-and general pragmatic expectations.
+expectations about one's interlocutor - expectations about how speakers
+behave in general and expectations about how a particular speaker might
+behave in a particular context. Here we used a Bayesian pragmatics model
+to predict this integration process. Experiment 1 and 2 replicated
+previous studies showing that adult listeners expect speakers to produce
+utterances informatively and also with respect to common ground. We then
+combined the procedures from the first two experiments to study how
+listeners would integrate expectations. We used the results from
+Experiment 1 and 2 to specify model parameters that represented the two
+types of expectations, generating predictions about new behavior.
+Experiments 3 and 4 showed that both types of expectations influenced
+listeners inferences. Overall, listener behavior was accurately
+described by our model, suggesting that listeners trade-off flexibly
+between speaker specific and general pragmatic expectations.
 
@@
 \hypertarget{ref-clark2009first}{}
-Clark, E. V. (2009). \emph{First language acquisition}. Cambridge
-University Press.
+Clark, E. V. (2009). \emph{First language acquisition}. Cambridge:
+Cambridge University Press.
 
 \hypertarget{ref-clark1996using}{}
-Clark, H. H. (1996). \emph{Using language}. Cambridge University Press.
+Clark, H. H. (1996). \emph{Using language}. Cambridge: Cambridge
+University Press.
 
@@
 \hypertarget{ref-grice1991studies}{}
-Grice, H. P. (1991). \emph{Studies in the way of words}. Harvard
-University Press.
+Grice, H. P. (1991). \emph{Studies in the way of words}. Cambridge, MA:
+Harvard University Press.
 
@@
 Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of
-generalized conversational implicature}. MIT press.
+generalized conversational implicature}. Cambridge, MA: MIT press.
 
@@
 Sperber, D., \& Wilson, D. (2001). \emph{Relevance: Communication and
-cognition} (2nd ed.). Oxford; Cambridge, MA: Blackwell Publishers.
+cognition} (2nd ed.). Cambridge, MA: Blackwell Publishers.
 
 \hypertarget{ref-tomasello2009constructing}{}
-Tomasello, M. (2009). \emph{Constructing a language}. Harvard university
-press.
+Tomasello, M. (2009). \emph{Constructing a language}. Cambridge, MA:
+Harvard University Press.
 

### 2019-02-05 stats/adults/visualizations.Rmd
update cogsci submission

@@
 
-d1 <- bind_rows(read_csv(file="novel.data.csv"),
-               read_csv(file="pref.data.csv")) %>%
+d1 <- bind_rows(read_csv(file="../data/novel.data.csv"),
+               read_csv(file="../data/pref.data.csv")) %>%
   mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         control = ifelse(change == "true", "true" , "false"))
+         control = ifelse(change == TRUE, "true" , "false"))
 
-d2 <- read_csv(file="inf.data.csv") %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+d2 <- read_csv(file="../data/inf.data.csv") %>%
+  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"),
+         control = ifelse(control == TRUE, "true" , "false"))
 
@@
 
-dat <- bind_rows(read_csv(file="ex3.novel.data.csv"),
-               read_csv(file="ex3.pref.data.csv")) %>%
+dat <- bind_rows(read_csv(file="../data/ex3.novel.data.csv"),
+               read_csv(file="../data/ex3.pref.data.csv")) %>%
   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
-
-dat %>%
-  filter(alignment == "incongruent") %>%
-  filter(correct_inf == correct_prior)
 
@@
                      breaks=c("1","2","3"),
-                     values= c("#859900","#859900","#859900"))+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
-        panel.border = element_rect(color = "#859900", fill = NA, size = 6))
+                     values= c("#859900","#859900","#859900"))
+
+pdata <- p1 %>%
+  multi_boot_standard(col = "correct")%>%
+  mutate(Model = "Data")
+
+pmd <- bind_rows(pdata, plot.model%>%
+                   filter(Model == "Noisy RSA Model")%>%
+                   ungroup()%>%
+                   mutate(Prior = "Strong",
+                          Model = "RSA Model"))
+
+ggplot() +
+  geom_jitter(data = p1, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
+  geom_pointrange(data = pmd, aes(x = Alignment, y = mean,col = Model, ymin = ci_lower, ymax = ci_upper),size = 1,  position = position_dodge(width = .5))+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Choosing More Informative")+
+  facet_grid ( ~ Experiment + Change) +
+  theme_few(base_size = 14) + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_manual(name="Condition",
+                     breaks=c("Data","RSA Model"),
+                     values= c("black","#859900"))+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
 
@@
 ```{r}
-ggsave("graphs/data_ex3_round1.pdf", width = 6.5, height = 3, scale = 1.8)
+ ggsave("../graphs/Ex3_1_data_model_pred.pdf", width = 6.5, height = 3, scale = 1.3)
 ```
@@
   xlab("Model")+
-  ggtitle("Experiment 3")+
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.9, aes(x = mean, y = Data), inherit.aes = F, size = 6)+
+  #ggtitle("Experiment 3")+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 4)+
   #geom_smooth(method = "lm", se = F, col = "black", size =1)+
-  theme_few(base_size = 20) + 
+  theme_few(base_size = ) + 
   guides(col = F)+
@@
 ```{r}
-ggsave("graphs/model_critique_ex3_round1.png", width = 4, height = 4, scale = 1)
+ggsave("../graphs/model_critique_ex3_round1.png", width = 3, height = 3, scale = 1)
 ```
@@
 
+```{r plotmodelcomp}
+
+pc1 <- plot.model%>%
+  filter(Model == "Noisy RSA Model")%>%
+  mutate(Prior = "Strong")
+
+c1 <-ggplot(data = pc1,aes(x = mean, y = Data, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 12) + 
+  guides(col = F)+
+  scale_colour_viridis_d()
+
+pc2 <- pred.ex3%>%
+  filter(Model == "Noisy RSA Model")
+
+c2 <- ggplot(data = pc2,aes(x = mean, y = Data, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = Data_ci_low, ymax = Data_ci_up),width = 0,size = .5 )+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = Data), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few(base_size = 12) + 
+  scale_colour_manual(values = rev(viridis::viridis(3)))
+
+pc3 <- data.frame(
+    ex3 = pc1%>%pull(Data),
+    ex3_ci_l = pc1%>%pull(Data_ci_low),
+    ex3_ci_u = pc1%>%pull(Data_ci_up),
+    ex4 = pc2%>%filter(Prior == "Strong")%>%pull(Data),
+    ex4_ci_l = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_low),
+    ex4_ci_u = pc2%>%filter(Prior == "Strong")%>%pull(Data_ci_up),
+    Prior = "Strong")
+
+c3 <- ggplot(data = pc3,aes(x = ex3, y = ex4, col = Prior)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = ex4_ci_l, ymax = ex4_ci_u),width = 0,size = .5 )+
+  geom_errorbarh(aes(xmin = ex3_ci_l, xmax = ex3_ci_u), height = 0,size = .5)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = ex3, y = ex4), inherit.aes = F, size = 3)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Data Experiment 3")+
+  ylab("Data Experiment 4")+
+  theme_few(base_size = 12)+ 
+  scale_color_viridis_d()
+
+ggarrange(c1, c2, c3, ncol = 3, nrow = 1, legend = "right", common.legend = T)
+
+```
+
 ```{r}
-ggsave("graphs/model_critique_ex3_round1_2.pdf", width = 10, height = 4, scale = 1.2)
+ggsave("../graphs/overview_ex3_4.pdf", width = 10, height = 3, scale = 1)
 ```

### 2019-02-05 stats/kids/kids_inf_2.Rmd
add saves to cogsci folder
update cogsci submission

@@
   mutate(test_date = as.Date(test_date),
-         experiment = "mcc_kids_inf_2_2")
+         experiment = "mcc_kids_inf_2_2",
+         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))
 
@@
   select(subid,experimenter,keep_drop,sex,dob)
+
+length(unique(log$subid))
+
+sum(log$keep_drop=="drop")
 
@@
 
-write_csv(d, "data/kids_inf_2_data.csv")
+#write_csv(d, "data/kids_inf_2_data.csv")
 

### 2019-02-05 stats/kids/kids_model_predictions.Rmd
CogSci paper new template
update cogsci submission

@@
          experiment = "preference_pretest",
-         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
-         agent = ifelse( change == "false", agent, altAgent),
+         condition = ifelse(change == F, "same_speaker", "different_speaker"),
+         agent = ifelse( change == F, agent, altAgent),
          minage = min(age_num))%>%
@@
 
+## Noisy model predictions
+
+```{r}
+noisyModelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
+
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.05)
+
+var all_conditions = levels(prefData, "condition")
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  foreach(function(row){
+
+    var age = row.age_num
+
+    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+
+    var inf_priorProbs = [.5, .5, .5]
+
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+    inf_priorProbs, speakerOptimality)
+
+    observe(rsaPredictions, row.correct)
+
+  }, infData)
+
+  var pref_params = map(function(cndtn){
+
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+    }, conditionData)
+
+    return {pref_int, pref_slope, condition: cndtn}
+
+  }, all_conditions)
+
+  var diff_speaker_params = _.filter(pref_params, 
+        {condition: "different_speaker"})[0]
+
+  var same_speaker_params = _.filter(pref_params, 
+        {condition: "same_speaker"})[0]
+
+  var predictions_by_age = map(function(age_bin){
+
+    var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+    var speakerOptimality = so_int  + so_slope * age_bin
+
+    var diff_priorReg = logistic(diff_speaker_params.pref_int +
+            diff_speaker_params.pref_slope * age_bin)
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
+
+    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
+
+    var rsaPredictions_diff_incong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality)
+
+ var noisyRsaPredictions_diff_incong = expectation(addNoise(rsaPredictions_diff_incong, noise))
+
+    var same_priorReg = logistic(same_speaker_params.pref_int +
+            same_speaker_params.pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+  var rsaPredictions_same_cong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality)
+
+ var noisyRsaPredictions_same_cong = expectation(addNoise(rsaPredictions_same_cong, noise))
+
+   var rsaPredictions_same_incong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality)
+
+ var noisyRsaPredictions_same_incong = expectation(addNoise(rsaPredictions_same_incong, noise))
+
+    return extend(
+    // diff_speaker_params, same_speaker_params, 
+      {
+      diff_priorReg,
+      same_priorReg,
+      speakerOptimality,
+      noisyRsaPredictions_diff_cong,
+      noisyRsaPredictions_diff_incong,
+      noisyRsaPredictions_same_cong,
+      noisyRsaPredictions_same_incong,
+      age_bin,
+      so_slope,
+      so_int,
+      noise
+    })
+
+  }, binned_age_range)
+
+  return predictions_by_age
+}
+'
+```
+
 ## Sampling predictions
@@
 
-# model_pred<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
-#   data = pre_data,
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
-# )
+model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+)
 
@@
   mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
+
+```
+
+```{r noisy combined model predictions}
+
+noisy_model_pred <- readRDS("../saves/kids_noisy_model_predictions.rds")
+
+noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+)
+
+#saveRDS(noisy_model_pred, file = "../saves/kids_noisy_model_predictions.rds")
+
+kids_noisy_model_pred <- noisy_model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:8000,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin,-noise)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
 
@@
 pred_plot
+```
+
+## Noisy RSA Model Predictions
+
+```{r plot RSA model predictions, echo = F, fig.width= 10}
+
+  plot_noisy_model_pred <- kids_noisy_model_pred %>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
+
+pred_noisy_plot <- ggplot(plot_noisy_model_pred)+
+  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
+  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion Expected Choice")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  guides(col = F)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+```
+
+```{r, echo= F, fig.width= 10, fig.height = 8}
+pred_noisy_plot
 ```
@@
 
+#saveRDS(model_comp_mean_ci, "../saves/kids_model_comp_mean_ci.rds")
+
 model_comp <- bind_rows(
@@
   )
+
+# saveRDS(model_comp, "../saves/kids_model_comp.rds")
 

### 2019-02-05 stats/kids/kids_novel.Rmd
update cogsci submission

@@
   scale_colour_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
+                     breaks=c(F, T),
                      labels=c("No", "Yes"))
@@
 ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
-  geom_smooth(method = "loess", se = T)+
+  geom_smooth(method = "lm", se = T)+
   geom_jitter( alpha = .5, height = 0.04)+

### 2019-02-05 stats/kids/kids_model_predictions.Rmd
update repo for MH

@@
   mutate(chain = factor(Chain),
-         alignment = "congruent")
+         Alignment = "congruent")
 
@@
 
-## Model code for predictions
+## Basic RSA model predictions
 
@@
 '
+```
+
+```{r combined model predictions}
+
+model_pred <- readRDS("../saves/kids_model_predictions.rds")
+
+# model_pred<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+#   data = pre_data,
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
+# )
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+kids_model_pred <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
+kids_model_pred_so <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
+
+kids_model_pred_prior <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
+  gather(condition, prop_preferred, -iteration,-age_bin)%>%
+  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
+
 ```
@@
 
-## Sampling predictions
-
-Taking samples and munging the data.
-
-```{r combined model predictions}
-
-model_pred <- readRDS("../saves/kids_model_predictions.rds")
-
-model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
-  data = pre_data,
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 4,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
-
-kids_model_pred <- model_pred%>%
+## Prior only model
+
+```{r prior only model}
+priorOnlyWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.05)
+
+var all_conditions = levels(prefData, "condition")
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+
+  var pref_params = map(function(cndtn){
+
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+    }, conditionData)
+
+    return {pref_int, pref_slope, condition: cndtn}
+
+  }, all_conditions)
+
+  var diff_speaker_params = _.filter(pref_params, 
+        {condition: "different_speaker"})[0]
+
+  var same_speaker_params = _.filter(pref_params, 
+        {condition: "same_speaker"})[0]
+
+  var predictions_by_age = map(function(age_bin){
+
+    var diff_priorReg = logistic(diff_speaker_params.pref_int +
+            diff_speaker_params.pref_slope * age_bin)
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var same_priorReg = logistic(same_speaker_params.pref_int +
+            same_speaker_params.pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+ var priorPredictions_diff_con = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_congruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+  var priorPredictions_diff_incon = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+ var priorPredictions_same_con = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_congruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+  var priorPredictions_same_incon = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+     var prior_diff_con = Math.exp(priorPredictions_diff_con.score(1))
+var prior_diff_incon = Math.exp(priorPredictions_diff_incon.score(1))
+     var prior_same_con = Math.exp(priorPredictions_same_con.score(1))
+var prior_same_incon = Math.exp(priorPredictions_same_incon.score(1))
+
+    return extend(
+      {prior_diff_con,
+prior_diff_incon,
+prior_same_con,
+prior_same_incon,
+    age_bin})
+
+  }, binned_age_range)
+
+  return predictions_by_age 
+}
+'
+```
+
+```{r}
+
+prior_only_predictions <- readRDS("../saves/prior_only_predictions.rds")
+
+# prior_only_predictions<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, priorOnlyWebppl , sep='\n'),
+#   data = pre_data,
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 3,
+#   cores = 3,
+#   inference_opts = list(method = "MCMC", samples = 1000, burn = 200, verbose = T)
+# )
+
+#saveRDS(prior_only_predictions, "../saves/prior_only_predictions.rds")
+
+prior_only_model <- prior_only_predictions %>%
   select(value) %>%
   map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  mutate(iteration = rep(1:3000,each = 40))%>%
   gather(condition, prop_informative, -iteration,-age_bin)%>%
@@
   mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
-         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
-
-kids_model_pred_so <- model_pred%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
-
-kids_model_pred_prior <- model_pred%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
-  gather(condition, prop_preferred, -iteration,-age_bin)%>%
-  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
+         Alignment = ifelse(Alignment == "con", "congruent","incongruent"))
 
@@
 ```
-## Sanity checks
+# Sanity checks
 
@@
 The model accurately captures the the difference between conditions as well as the developmental trend we see in the data.
+
+# Visualizing model predictions
 
@@
 
-```{r prior only model}
-priorOnlyWebppl <- '
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
-
-// make finer grained as needed
-var binned_age_range = _.range(0, 2, 0.05)
-
-var all_conditions = levels(prefData, "condition")
-
-var foreach = function(fn, lst) {
-    var foreach_ = function(i) {
-        if (i < lst.length) {
-            fn(lst[i]);
-            foreach_(i + 1);
-        }
-    };
-    foreach_(0);
-};
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  var pref_params = map(function(cndtn){
-
-    var conditionData = _.filter(prefData, {condition: cndtn})
-
-    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    foreach(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [1-priorReg, priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-    }, conditionData)
-
-    return {pref_int, pref_slope, condition: cndtn}
-
-  }, all_conditions)
-
-  var diff_speaker_params = _.filter(pref_params, 
-        {condition: "different_speaker"})[0]
-
-  var same_speaker_params = _.filter(pref_params, 
-        {condition: "same_speaker"})[0]
-
-  var predictions_by_age = map(function(age_bin){
-
-    var diff_priorReg = logistic(diff_speaker_params.pref_int +
-            diff_speaker_params.pref_slope * age_bin)
-
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var same_priorReg = logistic(same_speaker_params.pref_int +
-            same_speaker_params.pref_slope * age_bin)
-
-    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
-
-    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
-
- var priorPredictions_diff_con = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_congruent}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-  var priorPredictions_diff_incon = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
- var priorPredictions_same_con = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_congruent}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-  var priorPredictions_same_incon = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_incongruent}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-     var prior_diff_con = Math.exp(priorPredictions_diff_con.score(1))
-var prior_diff_incon = Math.exp(priorPredictions_diff_incon.score(1))
-     var prior_same_con = Math.exp(priorPredictions_same_con.score(1))
-var prior_same_incon = Math.exp(priorPredictions_same_incon.score(1))
-
-    return extend(
-      {prior_diff_con,
-prior_diff_incon,
-prior_same_con,
-prior_same_incon,
-    age_bin})
-
-  }, binned_age_range)
-
-  return predictions_by_age 
-}
-'
-```
-
-```{r}
-
-prior_only_predictions <- readRDS("../saves/prior_only_predictions.rds")
-
-# prior_only_predictions<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, priorOnlyWebppl , sep='\n'),
-#   data = pre_data,
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 3,
-#   cores = 3,
-#   inference_opts = list(method = "MCMC", samples = 1000, burn = 200, verbose = T)
-# )
-
-#saveRDS(prior_only_predictions, "../saves/prior_only_predictions.rds")
-
-prior_only_model <- prior_only_predictions %>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3000,each = 40))%>%
-  gather(condition, prop_informative, -iteration,-age_bin)%>%
-  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
-  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
-         Alignment = ifelse(Alignment == "con", "congruent","incongruent"))
-
-```
-
 ```{r plot prior only model predictions, include= F}
@@
 ## importing data
-files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
-
-raw_data <- data_frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
-  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-  date <- str_sub(jf,42,str_length(jf)-11)
-  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-  raw_data <- bind_rows(raw_data, id)
-}
-
-raw_data <- raw_data %>%
-  mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
-         subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
-         subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
-
-raw_data%>%
-  #group_by(paste(subid,test_date))%>%
-  group_by(subid)%>%
-  summarise(n= n())
-
-unique(raw_data$subid)
-
-log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "ex3p")%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-#unique(log$subid)
-sum(log$keep_drop == "drop")
-
-d <- left_join(raw_data,log, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
-  mutate(dob = as.numeric(dob),
-         dob = as.Date(dob,origin = "1899-12-30"),
-         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+d <- read_csv(file="../data/kids_ex3_data.csv")
+
+# files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
+# 
+# raw_data <- data_frame()
+# for (f in files) {
+#   jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
+#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+#   date <- str_sub(jf,42,str_length(jf)-11)
+#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+#   raw_data <- bind_rows(raw_data, id)
+# }
+# 
+# raw_data <- raw_data %>%
+#   mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
+#          subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
+#          subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
+# 
+# raw_data%>%
+#   #group_by(paste(subid,test_date))%>%
+#   group_by(subid)%>%
+#   summarise(n= n())
+#   
+# unique(raw_data$subid)
+# 
+# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
+#   filter(Condition == "ex3p")%>%
+#   select(subid,experimenter,keep_drop,sex,dob)
+# 
+# #unique(log$subid)
+# sum(log$keep_drop == "drop")
+# 
+# d <- left_join(raw_data,log, by = "subid")%>%
+#   filter(keep_drop == "keep")%>%
+#   mutate(dob = as.numeric(dob),
+#          dob = as.Date(dob,origin = "1899-12-30"),
+#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
+#          Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
+#          Alignment = alignment)%>%
+#   select(-speaker,-alignment)
+# 
+# 
+# #write_csv(d, "../data/kids_ex3_data.csv")
 
@@
          trial != "filler2")%>%
-  mutate(age_bin = age_num - 3,
-         Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
-         Alignment = alignment)%>%
-  group_by(Speaker, alignment ,age_bin, subid)
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)
 
@@
          trial != "filler2")%>%
-  mutate(Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
-         Alignment = alignment)%>%
   group_by(Speaker, Alignment ,subage) %>%

### 2019-02-08 stats/kids/kids_Ex3_pref.Rmd
update kids model preictions

@@
   geom_jitter(width = .025,height = .025, alpha = .2)+
-  geom_smooth(method = "loess",  se = T,  alpha = .5, size = .4, span = 2)+
+    geom_smooth(col = "black", size = 0.8, method = "glm", method.args = list(family = "binomial"), se = T,  alpha = .7)+
   geom_hline(yintercept = 0.5, lty=2)+

### 2019-02-08 stats/kids/kids_model_predictions.Rmd
update kids model preictions

@@
 ```{r pretest data, include=FALSE}
+
 pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
@@
          experiment = "preference_pretest",
-         condition = ifelse(change == F, "same_speaker", "different_speaker"),
-         agent = ifelse( change == F, agent, altAgent),
+         condition = ifelse(change == F | change == "false", "same_speaker", "different_speaker"),
+         agent = ifelse( change == F | change == "false", agent, altAgent),
          minage = min(age_num))%>%
@@
                       inf_data)
+
+ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
+  filter(trial != "filler1",trial != "filler2")
+
 ```
@@
 
-## Basic RSA model predictions
+## Model parameters by age bin
 
 ```{r}
-modelPredWebppl <- '
+paramModelWebppl <- '
 
@@
 var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
-
 // make finer grained as needed
 var binned_age_range = _.range(0, 2, 0.05)
-
 var all_conditions = levels(prefData, "condition")
-
 var foreach = function(fn, lst) {
@@
 };
-
 var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
 var model  = function(){
-
   var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
   var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
   foreach(function(row){
-
     var age = row.age_num
-
     var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
@@
     var inf_priorProbs = [.5, .5, .5] 
-
     var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
@@
     observe(rsaPredictions, row.correct)
-
   }, infData)
-
   var pref_params = map(function(cndtn){
-
     var conditionData = _.filter(prefData, {condition: cndtn})
@@
     foreach(function(row){
-
       var age = row.age_num
-
       var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
       var priorProbs= [1-priorReg, priorReg]
-
       var priorPredictions = Infer({method: "enumerate", model: function(){
@@
       observe(priorPredictions, row.correct)
-
     }, conditionData)
@@
         {condition: "different_speaker"})[0]
-
   var same_speaker_params = _.filter(pref_params, 
@@
 
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
-
-    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
-
     var same_priorReg = logistic(same_speaker_params.pref_int +
@@
 
-    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
-
-    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
-
-    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
-
-    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
-
     return extend(
-    // diff_speaker_params, same_speaker_params, 
       {
@@
       speakerOptimality,
-      rsaPredictions_diff_cong,
-      rsaPredictions_diff_incong,
-      rsaPredictions_same_cong,
-      rsaPredictions_same_incong,
       age_bin,
-      so_slope,
-      so_int,
 
@@
 
-```{r combined model predictions}
-
-model_pred <- readRDS("../saves/kids_model_predictions.rds")
-
-# model_pred<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+```{r}
+params_by_age<- readRDS("../saves/params_by_age.rds")
+
+# params_by_age<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, paramModelWebppl , sep='\n'),
 #   data = pre_data,
@@
 #   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
 # )
-
-#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
-
-kids_model_pred <- model_pred%>%
+# 
+# saveRDS(params_by_age, file = "../saves/params_by_age.rds")
+
+model_params_by_age <- params_by_age%>%
   select(value) %>%
   map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
-  gather(condition, prop_informative, -iteration,-age_bin)%>%
-  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
-  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
-         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
-
-kids_model_pred_so <- model_pred%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
-
-kids_model_pred_prior <- model_pred%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3600,each = 40))%>%
-  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
-  gather(condition, prop_preferred, -iteration,-age_bin)%>%
-  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
-
-```
-
-## Noisy model predictions
+  group_by(age_bin)%>%
+  summarise(so_map = estimate_mode(speakerOptimality),
+            diff_priorReg_map = estimate_mode(diff_priorReg),
+            same_priorReg_map = estimate_mode(same_priorReg))
+
+```
+
+## Basic RSA model predictions
 
 ```{r}
-noisyModelPredWebppl <- '
+modelPredWebppl <- '
 
@@
 }
-var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
-var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
-
-// make finer grained as needed
-var binned_age_range = _.range(0, 2, 0.05)
-
-var all_conditions = levels(prefData, "condition")
+
+var ex3Data = dataFromR.ex3data
+var modelParams = dataFromR.modelParams
+
+    display(JSON.stringify(ex3Data))
 
@@
 
+var predict_by_age = function(age_bin){
+
+    //display(JSON.stringify(age_bin))
+
+    var speakerOptimality = age_bin.so_map
+
+    var diff_priorReg = age_bin.diff_priorReg_map
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
+
+    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
+
+    var same_priorReg =age_bin.same_priorReg_map
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+
+    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
+
+  return extend(
+      {rsaPredictions_diff_cong,
+      rsaPredictions_diff_incong,
+      rsaPredictions_same_cong,
+      rsaPredictions_same_incong,
+      age_bin
+    })
+
+ }
+
+var predictions_by_age = map(predict_by_age, modelParams)
+
+predictions_by_age
+
+'
+```
+
+```{r combined model predictions}
+
+#model_pred <- readRDS("../saves/kids_model_predictions.rds")
+
+model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+  data = list(ex3data = ex3_data, modelParams = model_params_by_age),
+  data_var = "dataFromR",
+  model_var = "predict_by_age",
+  chains = 1,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 10, burn = 1, verbose = T)
+)
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+```
+
+## Noisy model predictions
+
+```{r}
+noisyModelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
+
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.05)
+
+var all_conditions = levels(prefData, "condition")
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
 var model  = function(){
+
+  // global parameters
+
+  var noise = uniformDrift({a: 0, b:1, width: 0.1})
 
@@
 
-    var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
     var speakerOptimality = so_int  + so_slope * age_bin
@@
 
-    return extend(
-    // diff_speaker_params, same_speaker_params, 
-      {
-      diff_priorReg,
-      same_priorReg,
-      speakerOptimality,
-      noisyRsaPredictions_diff_cong,
-      noisyRsaPredictions_diff_incong,
-      noisyRsaPredictions_same_cong,
-      noisyRsaPredictions_same_incong,
-      age_bin,
-      so_slope,
-      so_int,
-      noise
-    })
+    return [ 
+    [ age_bin + "_diff_cong",  noisyRsaPredictions_diff_cong],
+    [ age_bin + "_diff_incong",  noisyRsaPredictions_diff_incong],
+    [ age_bin + "_same_cong",  noisyRsaPredictions_same_cong],
+    [ age_bin + "_same_incong",  noisyRsaPredictions_same_incong],
+]
 
@@
 
-  return predictions_by_age
+return _.fromPairs(predictions_by_age.concat([
+["so_slope", so_slope],
+["so_int", so_int],
+["noise", noise]
+]))
+
 }
 '
+```
+```{r noisy combined model predictions}
+
+noisy_model_pred <- readRDS("../saves/kids_noisy_model_predictions.rds")
+
+noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+)
+
+#saveRDS(noisy_model_pred, file = "../saves/kids_noisy_model_predictions.rds")
+
+kids_noisy_model_pred <- noisy_model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:8000,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin,-noise)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
 ```
@@
 
-```{r noisy combined model predictions}
-
-noisy_model_pred <- readRDS("../saves/kids_noisy_model_predictions.rds")
-
-noisy_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
-  data = pre_data,
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 4,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-)
-
-#saveRDS(noisy_model_pred, file = "../saves/kids_noisy_model_predictions.rds")
-
-kids_noisy_model_pred <- noisy_model_pred%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  mutate(iteration = rep(1:8000,each = 40))%>%
-  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
-  gather(condition, prop_informative, -iteration,-age_bin,-noise)%>%
-  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
-  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
-         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
-
-```
 # Sanity checks
@@
 ## importing data
-d <- read_csv(file="../data/kids_ex3_data.csv")
+ex3_data <- read_csv(file="../data/kids_ex3_data.csv")
 

### 2019-02-08 stats/kids/kids_pref_2.Rmd
update kids model preictions

--- 2018-07-26 stats/mcc_pref.kids.Rmd
@@
 library(ggthemes)
+library(jsonlite)
+library(readxl)
 
 ## importing data
+files <- dir("~/Work/MCC/git-mcc/kids_pref_data_2/")
 
-d_ipad <- read_csv(file="kids_pref.data.csv")
+ raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_pref_data_2/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,45,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
 
-d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
-  mutate(age_num = as.numeric(as.character(age_num)))
+length(unique(raw_data$subid))
 
-d <- bind_rows(d_ipad,d_hand_code)%>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
-  filter(subid != "200718_8_pref")
+d_raw <-raw_data %>%
+  mutate(test_date = as.Date(test_date),
+         experiment = "mcc_kids_pref_2")
 
-# check if someone needs to be excluded because wrong in training
-# no one
-d %>%
-  filter(trial_type == "train") %>%
-  group_by(subid)%>%
-  summarise(correct = mean(correct)) %>%
-  filter(correct == 0)
+log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "pref2")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+length(unique(log$subid))
+
+sum(log$keep_drop=="drop")
+
+d <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
+         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+
+length(unique(d$subid))
 
@@
 
-# Subjects
+# Sample size per age bin
 
-There was one additional 4yo in the data set, whom I excluded to get the pre-registered sample size of 45 total.
-For the modeling we might want to include her as that gives us a tiny bit more precision.
+```{r kids per age group,echo = F }
 
-## Overall
-
-All training trials were answered correctly, suggesting that children generally understood the procedure.
-Sex is not included in the data set but the sex ration is fairly balances across age bins (47 to 60% girls).
-
-```{r sanity checks, echo = FALSE,warning = FALSE, message = FALSE}
-
-## sanity checks
 d %>%
-  group_by(trial_type) %>%
-  summarise(n = length(unique(subid)), 
-            correct = mean(correct)) %>%
+  group_by(subage)%>%
+  summarise(n = length(unique(subid)))%>%
   knitr::kable(digits = 2)
@@
 
-## By age bin
-
-Just to check if we got the planned sample size of 15 per bin.
-
-```{r kids per age group,echo = FALSE}
-
-d %>%
-  group_by(age)%>%
-  summarise(n = length(unique(subid)),
-            age_num = mean(age_num))%>%
-  knitr::kable(digits = 2)
-```
-
 # Plots
-
-## Plot across age bins
-
-Medium overall effect of speaker change.
-
-```{r plot across age}
-p3 <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(change, subid) %>%
-  summarise(correct = mean(correct))
-
-p4 <- p3 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p3, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
-```
 
@@
 p1 <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(change,age, subid) %>%
+  filter(trial != "train") %>%
+  group_by(speakerChange,subage, subid) %>%
   summarise(correct = mean(correct))
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = change, y = correct, col = change, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = change, y = mean, col = change, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p1, aes(x = speakerChange, y = correct, col = speakerChange, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   theme_few() +
-  facet_wrap(~age)+
+  facet_wrap(~subage)+
   ylim(-0.05,1.05)+

### 2019-02-11 stats/kids/kids_inf.Rmd
add kids so and pref models
update cogsci submission
add data from kids ex1 inf replication

--- 2018-11-08 stats/mcc_inf.kids.Rmd
@@
 
-log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
+log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
   filter(Condition == "inf")%>%
@@
 
-pf1 %>%
-  filter(correct == 0)
+#write_csv(d, "data/kids_inf_data.csv")
 
@@
   filter(trial != "filler1",
-         trial != "filler2") %>%
+         trial != "filler2", 
+         subage != "2") %>%
   group_by(age_num, subid) %>%

### 2019-02-11 stats/kids/kids_inf_2.Rmd
add data from kids ex1 inf replication

@@
 
-#write_csv(d, "data/kids_inf_2_data.csv")
+#write_csv(d, "../data/kids_inf_2_data.csv")
 
@@
 ```
+
+# Joining round 1 and round 2
+
+```{r}
+files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,45,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_raw <-raw_data %>%
+  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
+         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
+         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
+         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
+         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
+         experiment = "mcc_kids_inf_2")
+
+log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
+  filter(Condition == "inf")%>%
+  select(subid,experimenter,keep_drop,sex,dob)
+
+d2 <- left_join(d_raw,log, by = "subid")%>%
+  filter(keep_drop == "keep")%>%
+  mutate(dob = as.numeric(dob),
+         dob = as.Date(dob,origin = "1899-12-30"),
+         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+
+d_sum <- bind_rows(d%>%select(-test_date),d2%>%select(-test_date)%>%filter(subage!="2"))%>%
+    filter(trial != "filler1",
+         trial != "filler2")
+
+```
+
+```{r}
+d_sum %>%
+  group_by(subage)%>%
+  summarise(n = length(unique(subid)))%>%
+  knitr::kable(digits = 2)
+```
+
+```{r plot by age, echo= FALSE}
+
+p_sum1 <- d_sum %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(control,subage, subid) %>%
+  summarise(correct = mean(correct))
+
+p_sum2 <- p_sum1 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p_sum1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p_sum2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Control",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+# Plot with age as continuous variable
+
+```{r plot by numerical age, echo = F}
+p_sum3 <- d_sum %>%
+  filter(trial != "filler1",
+         trial != "filler2") %>%
+  group_by(age_num, subid) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p_sum3, aes(x = age_num, y = correct)) +
+  geom_smooth(method = "lm", se = T)+
+  geom_point( alpha = .5, width = 0.02)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("No", "Yes"))
+```
+
+```{r, include=F}
+## model
+library(lme4)
+
+lm_data_sum <- d_sum%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# maximal converging model
+lm_sum <- glmer(correct ~ age_num + (1 | subid), 
+              data = lm_data_sum, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+```
+
+```{r, echo = F}
+summary(lm_sum)
+```

### 2019-02-11 stats/kids/kids_pref_2.Rmd
add data from kids ex1 inf replication

@@
 knitr::opts_chunk$set(echo = FALSE)
+
 ###
@@
 p5 <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(change,age_num, subid) %>%
+  filter(trial != "train") %>%
+  group_by(speakerChange,age_num, subid) %>%
   summarise(correct = mean(correct))
 
-ggplot(data = p5, aes(x = age_num, y = correct, col = change)) +
-  geom_smooth(method = "loess", se = T)+
+ggplot(data = p5, aes(x = age_num, y = correct, col = speakerChange)) +
+  geom_smooth(method = "lm", se = T)+
   geom_jitter( alpha = .5, height = 0.04)+

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
add data from kids ex1 inf replication

@@
 
-inf_data <- read_csv(file="../data/kids_inf_data.csv")%>%
+inf_data <- bind_rows(
+  read_csv(file="../data/kids_inf_data.csv"),
+  read_csv(file="../data/kids_inf_2_data.csv"))%>%
   filter(subage != "2",

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
kids noisy model predcitions

@@
 ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
-  filter(trial != "filler1",trial != "filler2")
+  filter(trial != "filler1",trial != "filler2")%>%
+  mutate(binned_age=cut(age_num, breaks=seq.int(3, 5, 0.05), labels=seq.int(0, 1.95, 0.05)))
 
@@
 var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
 '
@@
 
-    display(JSON.stringify(ex3Data))
-
-var foreach = function(fn, lst) {
-    var foreach_ = function(i) {
-        if (i < lst.length) {
-            fn(lst[i]);
-            foreach_(i + 1);
-        }
-    };
-    foreach_(0);
-};
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
+    //display(JSON.stringify(ex3Data))
 
@@
   data = list(ex3data = ex3_data, modelParams = model_params_by_age),
+  data_var = "dataFromR"
+)
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+```
+
+## Noisy model predictions
+
+```{r}
+ageConditions <- data.frame(
+  age_bin = rep(seq.int(0, 1.95, 0.05),4),
+  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
+  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))
+```
+
+```{r}
+noisyModelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+var ex3Data = dataFromR.ex3data
+var modelParams = dataFromR.modelParams
+var ageConditions = dataFromR.ageConditions
+
+var predict_by_age = function(age_bin){
+
+  var model = function(){
+    var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+    var conditionOutput = map(function(conditionInfo){
+
+   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
+
+    var speakerOptimality = age_bin.so_map
+
+    var diff_priorReg = age_bin.diff_priorReg_map
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
+
+    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
+
+    map(function(d){ 
+      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
+    }, ageConditionSpecificData)
+
+  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
+
+}, ageConditions)
+
+}
+
+var predictions_by_age = map(predict_by_age, modelParams)
+
+predictions_by_age
+
+'
+```
+
+```{r}
+noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
+  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
   data_var = "dataFromR",
-  model_var = "predict_by_age",
+  model_var = "model",
   chains = 1,
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 10, burn = 1, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
 )
 
-#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
-
-```
-
-## Noisy model predictions
+```
 

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
partially repair noise induced rsa bda model

@@
 
-var predict_by_age = function(age_bin){
-
 var model = function(){
@@
 
+  var predict_by_age = function(age_bin){
+
     var conditionOutput = map(function(conditionInfo){
 
-   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
-
+   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
     var speakerOptimality = age_bin.so_map
@@
 
-    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
+    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)
 
@@
     }, ageConditionSpecificData)
+  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
+  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))
 
@@
   }
-
   var predictions_by_age = map(predict_by_age, modelParams)
-
-predictions_by_age
+  display(JSON.stringify(predictions_by_age))
+  return predictions_by_age
+}
 
@@
   program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
-  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
+  data =list(ex3data = ex3_data %>% mutate(binned_age = as.numeric(as.character(binned_age))), 
+             modelParams = model_params_by_age, 
+             ageConditions = ageConditions),
   data_var = "dataFromR",
@@
   chains = 1,
-  cores = 4,
+  cores = 1,
   inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)

### 2019-02-11 stats/kids/kids_model_predictions.Rmd
update kids model pred plot

--- 2019-02-11 stats/kids/kids_model_predictions.Rmd
@@
 
+kids_model_pred <- model_pred %>%
+  mutate(age_bin = age_bin.age_bin)%>%
+  select(rsaPredictions_diff_cong,rsaPredictions_diff_incong,rsaPredictions_same_cong,rsaPredictions_same_incong,age_bin)%>%
+  gather(condition, prop_informative, -age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
 ```
@@
 var ex3Data = dataFromR.ex3data
-var modelParams = dataFromR.modelParams
+var modelParams = dataFromR.modelParams[0]
 var ageConditions = dataFromR.ageConditions
-
-var predict_by_age = function(age_bin){
 
@@
 
-   var ageConditionSpecificData =  _.filter(ex3Data, {age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
-
-    var speakerOptimality = age_bin.so_map
-
-    var diff_priorReg = age_bin.diff_priorReg_map
+   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
+
+   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})
+
+    display(JSON.stringify(ageSpecificParams))
+
+    var speakerOptimality = ageSpecificParams.so_map
+
+    var diff_priorReg = ageSpecificParams.diff_priorReg_map
 
@@
 }
-
-var predictions_by_age = map(predict_by_age, modelParams)
-
-predictions_by_age
-
 '
@@
 ```
+
 ```{r noisy combined model predictions}
@@
 
-pred_plot <- ggplot(plot_model_pred)+
+ggplot(kids_model_pred)+
   #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
   #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
-  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
-  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_line(aes(age_bin, prop_informative), col = "black", size = 0.4, alpha = 1) + 
   geom_hline(yintercept = 0.5, lty=2)+
@@
 
-```{r import data, include = F}
-###
-library(tidyverse)
-library(knitr)
-library(langcog)
-library(ggthemes)
-library(jsonlite)
-library(readxl)
-
-## importing data
-ex3_data <- read_csv(file="../data/kids_ex3_data.csv")
-
-# files <- dir("~/Work/MCC/git-mcc/kids_EX3/pref/")
-# 
-# raw_data <- data_frame()
-# for (f in files) {
-#   jf <- paste("~/Work/MCC/git-mcc/kids_EX3/pref/",f,sep="")
-#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
-#   date <- str_sub(jf,42,str_length(jf)-11)
-#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
-#   raw_data <- bind_rows(raw_data, id)
-# }
-# 
-# raw_data <- raw_data %>%
-#   mutate(subid = ifelse(subid == "181128_3_ex3p....","181128_3_ex3p" , subid),
-#          subid = ifelse(subid == "181128_1_ex3p.","181128_1_ex3p" , subid),
-#          subid = ifelse(subid == " 181218_10_ex3p","181218_10_ex3p" , subid))
-# 
-# raw_data%>%
-#   #group_by(paste(subid,test_date))%>%
-#   group_by(subid)%>%
-#   summarise(n= n())
-#   
-# unique(raw_data$subid)
-# 
-# log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
-#   filter(Condition == "ex3p")%>%
-#   select(subid,experimenter,keep_drop,sex,dob)
-# 
-# #unique(log$subid)
-# sum(log$keep_drop == "drop")
-# 
-# d <- left_join(raw_data,log, by = "subid")%>%
-#   filter(keep_drop == "keep")%>%
-#   mutate(dob = as.numeric(dob),
-#          dob = as.Date(dob,origin = "1899-12-30"),
-#          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
-#          Speaker = ifelse(speaker == "same", "same_speaker", "different_speaker"),
-#          Alignment = alignment)%>%
-#   select(-speaker,-alignment)
-# 
-# 
-# #write_csv(d, "../data/kids_ex3_data.csv")
-
-```
-
 ## Plot comparing model and data by continous age
@@
 
-p_data <- d %>%
+p_data <- ex3_data %>%
   filter(trial != "filler1",
@@
 
-ggplot(model_comp_mean_ci)+
-  geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
-  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
-  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1, linetype = 2) + 
+ggplot(kids_model_pred)+
+  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
+  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, prop_informative, col = model), size = 1, alpha = 1, linetype = 1) + 
   geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+

### 2019-02-12 stats/kids/kids_model_predictions.Rmd

@@
 noisyModelPredWebppl <- '
-
 var levels = function(df, label){
@@
 }
-
 var ex3Data = dataFromR.ex3data
-var modelParams = dataFromR.modelParams[0]
+var modelParams = dataFromR.modelParams
 var ageConditions = dataFromR.ageConditions
-
 var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
+  var predict_by_age = function(age_bin){
     var conditionOutput = map(function(conditionInfo){
-
    var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
-
-   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})
-
-    display(JSON.stringify(ageSpecificParams))
-
-    var speakerOptimality = ageSpecificParams.so_map
-
-    var diff_priorReg = ageSpecificParams.diff_priorReg_map
-
+    var speakerOptimality = age_bin.so_map
+
+    var diff_priorReg = age_bin.diff_priorReg_map
     var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
     var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
@@
     var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
-
-    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
-
+    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)
     map(function(d){ 
@@
     }, ageConditionSpecificData)
+  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
+  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))
 
   return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
-
   }, ageConditions)
-
+  }
+  var predictions_by_age = map(predict_by_age, modelParams)
+  display(JSON.stringify(predictions_by_age))
+  return predictions_by_age
 }

### 2019-02-24 papers/cogsci2019/cogsci2019.Rmd
kids model prediction with replication data

@@
 output: cogsci2016::cogsci_paper
-#final-submission: \cogscifinalcopy
+final-submission: \cogscifinalcopy
 ---
@@
 
-<!-- \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->
 
@@
 
-<!-- MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229. -->
+MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.
 

### 2019-02-24 stats/kids/kids_inf_biling.Rmd
kids model prediction with replication data

--- 2019-02-11 stats/kids/kids_inf_2.Rmd
@@
 
-raw_data <- data_frame()
+raw_data_2 <- data_frame()
 for (f in files) {
@@
   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
+  raw_data_2 <- bind_rows(raw_data_2, id)
+}
+
+d_raw_2 <-raw_data_2 %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(test_date = as.Date(test_date),
+         experiment = "mcc_kids_inf_2_2",
+         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))%>%
+  select(subid,subage,trial,correct,test_date)
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_data/")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_data/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,45,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
   raw_data <- bind_rows(raw_data, id)
@@
 
-length(unique(raw_data$subid))
+d_raw <-raw_data %>%
+    filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
+         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
+         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
+         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
+         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
+         experiment = "mcc_kids_inf_2")%>%
+  select(subid,subage,trial,correct,test_date)%>%
+  mutate(test_date = as.Date(test_date))
 
-d_raw <-raw_data %>%
-  mutate(test_date = as.Date(test_date),
-         experiment = "mcc_kids_inf_2_2",
-         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees")
+
+raw_data_trees <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,50,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
+  raw_data_trees <- bind_rows(raw_data_trees, id)
+}
+
+d_trees <- raw_data_trees %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")%>%
+  mutate(test_date = as.Date(test_date))%>%
+  select(subid,subage,trial,correct,test_date)
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,63,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_robots <- raw_data %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")%>%
+  mutate(test_date = as.Date(test_date))%>%
+  select(subid,subage,trial,correct,test_date)
+
+files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right")
+
+raw_data <- data_frame()
+for (f in files) {
+  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right/",f,sep="")
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
+  date <- str_sub(jf,61,str_length(jf)-11)
+  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
+  raw_data <- bind_rows(raw_data, id)
+}
+
+d_trees_left_right <- raw_data %>%
+  filter(trial != "train1",
+         trial != "train2",
+         trial != "filler1",
+         trial != "filler2",
+         subage != "Test")%>%
+  mutate(test_date = as.Date(test_date))%>%
+  select(subid,subage,trial,correct,test_date)
+
+d_sum <- bind_rows(
+  d_raw_2,
+  d_raw,
+  d_trees,
+  d_robots,
+  d_trees_left_right)
 
 log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "inf2")%>%
-  select(subid,experimenter,keep_drop,sex,dob)
+  filter(Condition == "inf" | Condition == "inf2")%>%
+  select(subid,experimenter,keep_drop,sex,dob, English, parent1_ed,parent2_ed)%>%
+  mutate(language_status = ifelse(English == "100" | English == "90-95", "mono_ling", "bi_ling"))
 
-length(unique(log$subid))
-
-sum(log$keep_drop=="drop")
-
-d <- left_join(d_raw,log, by = "subid")%>%
-  filter(keep_drop == "keep")%>%
+d <- left_join(d_sum,log, by = "subid")%>%
   mutate(dob = as.numeric(dob),
@@
          age_num = lubridate::time_length(difftime(test_date,dob), "years"),
-         check_age = ifelse(substr(age_num,1,1) == subage, T, F))
+         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
+  filter(language_status != "NA", 
+         English != "NA")
 
-length(unique(d$subid))
-
-#write_csv(d, "../data/kids_inf_2_data.csv")
+write_csv(d, "../data/kids_inf_data_megan.csv")
 
@@
 d %>%
-  group_by(subage)%>%
-  summarise(n = length(unique(subid)))%>%
-  knitr::kable(digits = 2)
+  group_by(subage, sex)%>%
+  summarise(n = length(unique(subid)))
 
-```
-
-# Plot filler by age
-
-```{r filler by age, echo= FALSE, warning= FALSE}
-pf1 <- d %>%
-      filter(trial == "filler1" | trial == "filler2")%>%
-  group_by(control,subage, subid) %>%
-  summarise(correct = mean(correct))
-
-pf2 <- pf1 %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
-  theme_few() +
-  facet_wrap(~subage)+
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
 ```
@@
 p1 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(control,subage, subid) %>%
+  group_by(sex,subage, subid) %>%
   summarise(correct = mean(correct))
@@
 ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_jitter(data = p1, aes(x = sex, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = sex, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
   guides(alpha = F)+ 
-  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Control",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  scale_colour_solarized()
 ```
@@
 p5 <- d %>%
-  filter(trial != "filler1",
-         trial != "filler2") %>%
-  group_by(age_num, subid) %>%
+  group_by(language_status,age_num, subid) %>%
   summarise(correct = mean(correct))
 
-ggplot(data = p5, aes(x = age_num, y = correct)) +
+ggplot(data = p5, aes(x = age_num, y = correct,col = language_status)) +
   geom_smooth(method = "lm", se = T)+
@@
   #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
-  scale_colour_solarized(name="Speaker Change",
-                     breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+  scale_colour_solarized()
 ```

### 2019-02-24 stats/kids/kids_model_predictions.Rmd
kids model prediction with replication data

--- 2019-02-11 stats/kids/kids_model_predictions.Rmd
@@
 
-## Model parameters by age bin
+## Across age bins
+
+### RSA model predictions across age bins
+
+```{r}
+modelPredAcrossWebppl <- '
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
+// make finer grained as needed
+var binned_age_range = _.range(0, 2, 0.05)
+var all_conditions = levels(prefData, "condition")
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+var model  = function(){
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+  foreach(function(row){
+    var age = row.age_num
+    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+
+    var inf_priorProbs = [.5, .5, .5] 
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+    inf_priorProbs, speakerOptimality)
+
+    observe(rsaPredictions, row.correct)
+  }, infData)
+  var pref_params = map(function(cndtn){
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+      var age = row.age_num
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+      var priorProbs= [1-priorReg, priorReg]
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+    }, conditionData)
+
+    return {pref_int, pref_slope, condition: cndtn}
+
+  }, all_conditions)
+
+  var diff_speaker_params = _.filter(pref_params, 
+        {condition: "different_speaker"})[0]
+  var same_speaker_params = _.filter(pref_params, 
+        {condition: "same_speaker"})[0]
+
+  var predictions_by_age = map(function(age_bin){
+
+    var speakerOptimality = so_int  + so_slope * age_bin
+
+    var diff_priorReg = logistic(diff_speaker_params.pref_int +
+            diff_speaker_params.pref_slope * age_bin)
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
+    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
+
+    var same_priorReg = logistic(same_speaker_params.pref_int +
+            same_speaker_params.pref_slope * age_bin)
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
+    return extend(
+    // diff_speaker_params, same_speaker_params, 
+      {
+     diff_priorReg,
+     same_priorReg,
+     speakerOptimality,
+    rsaPredictions_diff_cong,
+    rsaPredictions_diff_incong,
+    rsaPredictions_same_cong,
+      rsaPredictions_same_incong,
+      age_bin,
+    //  so_slope,
+    //  so_int,
+    })
+
+  }, binned_age_range)
+
+  return predictions_by_age
+}
+'
+```
+
+Taking samples and munging the data.
+
+```{r combined model predictions}
+model_pred_across <- readRDS("../saves/kids_model_predictions.rds")
+
+model_pred_across<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredAcrossWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
+)
+
+saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+kids_model_pred_across <- model_pred_across%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
+kids_model_pred_so <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
+
+kids_model_pred_prior <- model_pred%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3600,each = 40))%>%
+  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
+  gather(condition, prop_preferred, -iteration,-age_bin)%>%
+  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
+
+```
+
+## By age bin with noise
+
+### Model parameters by age bin
 
@@
 
-## Basic RSA model predictions
+### RSA model predictions by age bin
 
@@
 
-## Noisy model predictions
+### Noisy RSA predictions by age bin
 
@@
   Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))
+
+ageParams <- data.frame(
+  age_bin = rep(seq.int(0, 1.95, 0.05),4),
+  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
+  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)),
+  SpeakOpt = rep(model_params_by_age$so_map,4))
+
+listPrior <- data.frame(
+  a = 1:length(ageParams$age_bin),
+  ob1 = c(1- model_params_by_age$same_priorReg_map,
+          model_params_by_age$same_priorReg_map,
+          1- model_params_by_age$diff_priorReg_map,
+          model_params_by_age$diff_priorReg_map),
+  ob2 = c(1- model_params_by_age$same_priorReg_map,
+          model_params_by_age$same_priorReg_map,
+          1- model_params_by_age$diff_priorReg_map,
+          model_params_by_age$diff_priorReg_map),
+  ob3 = c(model_params_by_age$same_priorReg_map,
+          1- model_params_by_age$same_priorReg_map,
+          model_params_by_age$diff_priorReg_map,
+          1- model_params_by_age$diff_priorReg_map))%>%
+  group_by(a)%>%
+  mutate(list = list(c(ob1,ob2,ob3)))%>%
+  pull(list)
+
+ageParams$priorP <- listPrior
+
+```
+
+```{r}
+noisyModelPredWebppl <-'
+var allConditions = dataFromR.ageConditions
+var allData = dataFromR.ex3data
+var allParams = dataFromR.ageParams
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
+
+      var ageConditionSpecificParams =  _.filter(allParams, {age_bin: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
+
+    //display(JSON.stringify(ageConditionSpecificParams[0].priorProbs))
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, ageConditionSpecificParams[0].priorProbs,   ageConditionSpecificParams[0].SpeakOpt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.age_bin + "-" + conditionInfo.Speaker + "-" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+ return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
 ```
@@
 var ex3Data = dataFromR.ex3data
-var modelParams = dataFromR.modelParams[0]
 var ageConditions = dataFromR.ageConditions
+var ageParams = dataFromR.ageParams
+
+display(JSON.stringify(ageParams))
 
@@
   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+ // var predict_by_age = function(age_bin){
 
@@
 
-   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})
-
-    display(JSON.stringify(ageSpecificParams))
-
-    var speakerOptimality = ageSpecificParams.so_map
-
-    var diff_priorReg = ageSpecificParams.diff_priorReg_map
-
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
-
-    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
-
+   var ageConditionSpecificParams =  _.filter(ageParams, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
+
+ display(JSON.stringify(ageConditionSpecificParams))
+
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, ageConditionSpecificParams[0].Prior,   ageConditionSpecificParams[0].SpeakOpt)
+
+    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)
     map(function(d){ 
@@
     }, ageConditionSpecificData)
+  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
+  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))
 
   return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
-
   }, ageConditions)
-
+//  }
+//  var predictions_by_age = map(predict_by_age, modelParams)
+  //display(JSON.stringify(predictions_by_age))
+//  return predictions_by_age
 }
@@
   program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
-  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
+  data =list(ex3data = ex3_data %>% mutate(binned_age = as.numeric(as.character(binned_age))), 
+             ageConditions = ageConditions,
+             ageParams = ageParams),
   data_var = "dataFromR",
   model_var = "model",
-  chains = 1,
+  chains = 4,
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 1000, burn = 200, verbose = T)
 )
+
+posterior.noise <- noisy_model_pred %>%
+  filter(Parameter %in% c("noise", "priorExponent"))
+
+ggplot(posterior.noise, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+posterior.predictive <- noisy_model_pred %>%
+  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
+  separate(Parameter, into = c("age_bin", "Speaker", "Alignment"), sep="-")%>%
+  group_by(age_bin,Alignment,Speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age_bin = as.numeric(age_bin))
 
@@
 
-## Prior only model
+### Prior only model
 
@@
 
-## Plot comparing model and data by continous age
-```{r comparison plot by age, echo= FALSE}
+## Predictions across age bins
+
+```{r comparison plot, echo= FALSE}
 
@@
 
-ggplot(kids_model_pred)+
+ggplot(posterior.predictive)+
   #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
-  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
-  geom_line(aes(age_bin, prop_informative, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_ribbon(aes(x =age_bin, ymin = ci_lower, ymax = ci_upper), alpha = .4) +
+  geom_line(aes(age_bin, mean), size = 1, alpha = 1, linetype = 1) + 
   geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
-  #geom_hline(yintercept = 0.5, lty=2)+
+  geom_hline(yintercept = 0.5, lty=2)+
   labs(y="proportion more informative")+
@@
 
+## Predictions by age bin
+
+### Plot comparing noisy model and data by continous age
+```{r comparison plot by age, echo= FALSE}
+
+p_data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)
+
+ggplot(posterior.predictive)+
+  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x =age_bin, ymin = ci_lower, ymax = ci_upper), alpha = .4) +
+  geom_line(aes(age_bin, mean), size = 1, alpha = 1, linetype = 1) + 
+  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
 ## Correlation plot
@@
 
-data <- d %>%
+data <- ex3_data %>%
   filter(trial != "filler1",
@@
 
-model <- model_comp %>%
+model <- kids_model_pred %>%
   mutate(subage = ifelse(age_bin<1,"3","4"))%>%
   group_by(model,Speaker,Alignment,subage)%>%
-  summarise(Model = mean(prop_informative),
-            Model_ci_lower = hdi_lower(prop_informative),
-            Model_ci_upper = hdi_upper(prop_informative))
+  summarise(Model = mean(prop_informative))
 
@@
   ungroup()%>%
-  mutate(Data = rep(data$Data,3),
-         Data_ci_lower = rep(data$Data_ci_lower,3),
-         Data_ci_upper  =rep(data$Data_ci_upper,3))
+  mutate(Data = data$Data,
+         Data_ci_lower = data$Data_ci_lower,
+         Data_ci_upper  =data$Data_ci_upper,3)
 
@@
   geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
-  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  #geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
   coord_fixed()+

### 2019-02-24 stats/kids/kids_pref.Rmd
kids model prediction with replication data

--- 2018-11-23 stats/kids_pref.Rmd
@@
 
-d <- read_csv(file="data/kids_pref_data.csv")
+d <- read_csv(file="../data/kids_pref_data.csv")
 
@@
   filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
+  mutate(choiceAgent = ifelse( change == F, agent, altAgent),
          age_num = scale(age_num, center = TRUE, scale = TRUE))

### 2019-02-24 stats/kids/kids_pref_2.Rmd
kids model prediction with replication data

@@
 ---
-title: "MCC Preference Kids"
+title: "MCC Preference Kids - Replication"
 author: "Manuel Bohn"
-date: "23 7 2018"
 output: html_document
@@
 
+#write_csv(d, "../data/kids_pref_2_data.csv")
+
 ```
@@
   knitr::kable(digits = 2)
-
 ```
@@
 
+## Plot across age bins
+
+```{r plot across age,echo = F}
+p3 <- d %>%
+  filter(trial != "train") %>%
+  group_by(speakerChange,subid) %>%
+  summarise(correct = mean(correct))
+
+p4 <- p3 %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p3, aes(x = speakerChange, y = correct, col = speakerChange, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p4, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("Same Speaker", "Different Speaker"))
+```
+
 ## Plot by age bin
 
-```{r plot by age}
+```{r plot by age,echo = F}
 p1 <- d %>%
@@
                      breaks=c("false", "true"),
-                     labels=c("No", "Yes"))
+                     labels=c("Same Speaker", "Different Speaker"))
 ```
@@
 
-```{r plot by numerical age}
+```{r plot by numerical age,echo = F}
 p5 <- d %>%
@@
 
-## T-tests against chance across age bins
-```{r}
+## T-tests against chance per age bin
+```{r,echo = F}
 ## t tests against chance
 d %>%
-  filter(trial_type == "test") %>%
-  group_by(change, subid) %>%
+  filter(trial != "train") %>%
+  group_by(subage,speakerChange, subid) %>%
   summarise(correct = mean(correct)) %>%
   summarise(correct = list(correct)) %>%
-  group_by(change) %>%
+  group_by(subage,speakerChange) %>%
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
@@
          p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(change,df,t_value,p_value) %>%
-  knitr::kable(digits = 3)
-
-```
-
-## T-tests against chance per age bin
-```{r}
-## t tests against chance
-d %>%
-  filter(trial_type == "test") %>%
-  group_by(age,change, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(age,change) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(age,change,df,t_value,p_value) %>%
+  select(subage,speakerChange,df,t_value,p_value) %>%
   knitr::kable(digits = 3)
@@
 
-With age as continuous variable.
-We pre-registered the model with an interaction between age and change as a random slope for subject: `(change * age| subid)`.
-However, including age here seems unnecessary since each subject has only one age.
-I therefore took the interaction out in the model below.
-
-Results mirror what we see in the plots above: increasing effect of speaker change across development.
-
-```{r}
+```{r, warning= F, message=F, }
 ## model
@@
 lm_data <- d%>%
-  filter(trial_type == "test")%>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
+  filter(trial != "train")%>%
+  mutate(choiceAgent = ifelse( speakerChange == "false", agent, altAgent),
          age_num = scale(age_num, center = TRUE, scale = TRUE))
@@
 # maximal converging model
-lm <- glmer(correct ~ age_num * change + (change | subid) + (age_num * change | choiceAgent), 
+lm <- glmer(correct ~ age_num * speakerChange + (speakerChange | subid) + (age_num * speakerChange | choiceAgent), 
               data = lm_data, family = binomial, 
@@
 
-# Additional plots
+# Joining round 1 and round 2
 
-To check for trial and item effects.
+```{r,include= F}
 
-## Conditions by trial
-```{r plot trials}
-ms <- d %>%
-  filter(trial_type == "test") %>%
-  group_by(change, trial, subid) %>%
-  summarise(correct = mean(correct)) %>%
+d1 <- read_csv(file="../data/kids_pref_data.csv")%>%
+  filter(age != "2")%>%
+  mutate(speakerChange = ifelse(change == F, "false", "true"),
+         subage = as.character(age))
+
+d_sum <- bind_rows(d,d1)%>%
+    filter(trial != "train")
+
+```
+## sample size
+```{r,echo = F}
+d_sum %>%
+  group_by(subage)%>%
+  summarise(n = length(unique(subid)))%>%
+  knitr::kable(digits = 2)
+```
+
+## Plot by age bin
+
+```{r plot by age sum ,echo = F}
+p_sum1 <- d_sum %>%
+  filter(trial != "train") %>%
+  group_by(speakerChange,subage, subid) %>%
+  summarise(correct = mean(correct))
+
+p_sum2 <- p_sum1 %>%
   multi_boot_standard(col = "correct")
 
-ggplot(ms, 
-       aes(x = trial, y = mean, col = change)) +
-  geom_line(aes(group= change)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
+ggplot() +
+  geom_jitter(data = p_sum1, aes(x = speakerChange, y = correct, col = speakerChange, alpha = .2),width = .3,height = .025)+
+  geom_pointrange(data = p_sum2, aes(x = speakerChange, y = mean, col = speakerChange, ymin = ci_lower, ymax = ci_upper),size = .8)+
   geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
   theme_few() +
-  scale_colour_solarized()
+  facet_wrap(~subage)+
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("Same Speaker", "Different Speaker"))
 ```
 
-## By agent
-```{r plot agents}
-ms <- d %>%
-  filter(trial_type == "test") %>%
-  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
-  group_by(change, choiceAgent, subid) %>%
-  summarise(correct = mean(correct)) %>%
-  multi_boot_standard(col = "correct")
+## Plot with age as continuous variable
 
-ggplot(ms, 
-       aes(x = choiceAgent, y = mean, col = change)) +
-  geom_line(aes(group= change)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
+```{r plot by numerical age sum ,echo = F}
+p_sum3 <- d_sum %>%
+  filter(trial != "train") %>%
+  group_by(speakerChange,age_num, subid) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p_sum3, aes(x = age_num, y = correct, col = speakerChange)) +
+  geom_smooth(method = "lm", se = T)+
+  geom_jitter( alpha = .5, height = 0.04)+
   geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion Expected Choice")+
   theme_few() +
-  scale_colour_solarized()
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
+  scale_colour_solarized(name="Speaker Change",
+                     breaks=c("false", "true"),
+                     labels=c("Same Speaker", "Different Speaker"))
 ```
+## GLMM
+
+```{r, warning=F,message=F}
+## model
+library(lme4)
+
+lm_sum_data <- d_sum%>%
+  filter(trial != "train")%>%
+  mutate(choiceAgent = ifelse( speakerChange == "false", agent, altAgent),
+         age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# maximal converging model
+lm_sum <- glmer(correct ~ age_num * speakerChange + (speakerChange | subid) + (age_num * speakerChange | choiceAgent), 
+              data = lm_sum_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+summary(lm_sum)
+
+```

### 2019-03-06 papers/full_paper/methods.Rmd
update kids model predictions

---
title: "MCC Paper MEthods"
author: "Manuel Bohn"
output: 
  html_document:
  toc: true
  toc_float: true

---

```{r setup, include=FALSE}

# load packages and functions
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
library(ggpubr)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

```{r}
# preparing datafiles (delete eventually)

# d <- read_csv(file="../../stats/data/inf.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          trial = alltrial -2,
#          experiment = "adult_ex1",
#          condition = ifelse(control == TRUE, "control", "test") )%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,  trial,condition, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex1.csv")
# 
# d <- read_csv(file="../../stats/data/novel.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_novelty",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_novelty.csv")
# 
# d <- read_csv(file="../../stats/data/pref.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_preference",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_preference.csv")
# 
# d <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
#                read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"),
#          agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(experiment == "novel_inf","novelty", "preference"),
#          experiment = "adult_ex3",
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"))%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, speaker ,alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex3.csv")
# 
# 
# d <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
#                ) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"),
#          agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(grepl("novel",experiment),"novelty", "preference"),
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"),
#          prior_manipulation = prior,
#          experiment = "adult_ex4")%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, prior_manipulation, speaker, alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex4.csv")
#
# 
# d <- bind_rows(read_csv(file="../../stats/data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
#                        read_csv(file="../../stats/data/kids_pref_2_data.csv"))%>%
#   filter(trial != "train")%>%
#   mutate(age_bin = factor(age),
#          experiment = "child_ex2",
#          condition = ifelse(speakerChange == F, "same_speaker", "different_speaker"),
#          agent = ifelse( speakerChange == F, agent, altAgent),
#          id = subid)%>%
#   filter(trial != "train")%>%
#   select(experiment,id,age_bin,age_num,trial,condition,agent,correct)
# 
# write_csv(d , path="../../stats/data/child_ex2.csv")
#
# d <- bind_rows(
#   read_csv(file="../../stats/data/kids_inf_data.csv"),
#   read_csv(file="../../stats/data/kids_inf_2_data.csv"))%>%
#   filter(subage != "2",
#          trial != "filler1",
#          trial != "filler2")%>%
#   mutate(age_bin = factor(subage),
#          experiment = "child_ex1",
#          id =subid)%>%
#   select(experiment,id,age_bin,age_num,trial,correct)
# 
# write_csv(d , path="../../stats/data/child_ex1.csv") 
# 
# 
# d <- read_csv(file="../../stats/data/kids_ex3_data.csv")%>%
#   mutate(experiment = "child_ex3",
#          id = subid, 
#          age_bin = subage,
#          speaker = Speaker,
#          alignment = Alignment)%>%
#   filter(trial != "filler1",trial != "filler2")%>%
#   select(experiment, id,age_bin,age_num,trial, speaker, alignment, agent, correct_inf)
#  
# write_csv(d , path="../../stats/data/child_ex3.csv")

```

```{r data, include= FALSE}
# load data files

# adults exp 1 
adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
# adults exp 2 novelty
adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
# adults exp 2 preference
adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
# adults ex3
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
# adults ex4
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv")

# children ex1
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# children ex2 preference
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
# children ex3
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

# Adults 
## Experiment 1

```{r, figure 1}

p_fig1 <- bind_rows(adult_ex1_data,
                    adult_ex2_novelty_data %>%
                      mutate(condition = ifelse(condition == "same_speaker","test", "control")),
                    adult_ex2_preference_data%>% 
                      mutate(condition = ifelse(condition == "same_speaker","test", "control"))) %>%
  mutate(experiment = factor(experiment),
         condition = factor(condition, levels = c("test","control")))%>%
  group_by(experiment,condition , id) %>%
  summarise(correct = mean(correct))

p_fig1x <- p_fig1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p_fig1, aes(x = condition, y = correct, col = condition), alpha = 0.3, width = .3,height = .02)+
  geom_pointrange(data = p_fig1x, aes(x = condition, y = mean, col = condition,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Correct")+
  facet_wrap( ~ experiment, labeller = as_labeller(c(`adult_ex2_preference`="Exp. 2 - Pref.", `adult_ex2_novelty`="Exp. 2 - Nov.", `adult_ex1`="Exp. 1")))+
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F,size =F)+
  scale_color_solarized(name = "Condition",
                     breaks=c("test","control"))+
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

```

```{r, figure x}

p_figx <- bind_rows(child_ex1_data%>%
                      mutate(condition = "test"),
                    child_ex2_data %>%
                      mutate(condition = ifelse(condition == "same_speaker","test", "control"))) %>%
  mutate(experiment = factor(experiment),
         condition = factor(condition, levels = c("test","control")))%>%
  group_by(experiment,condition,age_num, id) %>%
  summarise(correct = mean(correct))

ggplot(data = p_figx, aes(x = age_num, y = correct, col = condition)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  facet_wrap( ~ experiment, labeller = as_labeller(c(`child_ex2`="Exp. 2", `child_ex1`="Exp. 1")))+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_solarized(name = "Condition")+
  scale_fill_solarized(name = "Condition")

```
```{r, fig.height=3, fig.width=8}
#ggarrange(fig1_a, fig1_c, ncol = 2, nrow = 1, common.legend = F, legend = "bottom", widths = c(1,1.2))
```

### 2019-03-06 papers/full_paper/models.Rmd
update kids model predictions

---
title: "MCC Model Predictions"
author: "Manuel Bohn"
date: "15 6 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(coda)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

# Adults

## Model utensils code

```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

var labels = ["dax","wug"]

var lexicon1 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "triangle" :
utterance.label == "wug" ? obj.shape == "circle" : 
true
}

var lexicon2 = function(utterance, obj){
utterance.label == "dax" ? obj.shape == "circle" :
utterance.label == "wug" ? obj.shape == "triangle" : 
true
}

var lexiconObjects = {
"dax = triangle": {
triangle: "dax", circle: "wug"
},
"dax = circle": {
triangle: "wug", circle: "dax"
},
}

var lexiconObject = {
"dax = triangle": lexicon1,
"dax = circle" : lexicon2
}

var point = function(utterance, obj){
return obj.location == utterance.point
}

var utterancePrior = function(obj, lexiconName){
var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
var point = uniformDraw(locationsWithShape)
var label = lexiconObjects[lexiconName][obj.shape]
return {label: label, point: point}
}

var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})

var speakerOptimality = 2.25;

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}
'
```

## Pragmatic RSA model code

```{r rsaModel}
rsaModel <- '
var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speaker = function(obj, lexiconName, priorProbs){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}
'
```

## Adult model predictions

### Experiment 4

#### Model parameters and data
```{r ex4 data}
# load data  from experiment 4 to infer noise parameter
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
```

```{r}
# load data from prior strength manipulation experiments to set priors

adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
```

```{r model setup, include = FALSE}

# create datafiles with model parameters

strongPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("strong",8))

strong_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

strong_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "strong",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

strongPrior$prior = list(
    c(1-strong_prior_pref_same$prior,1-strong_prior_pref_same$prior,strong_prior_pref_same$prior), 
    c(strong_prior_pref_same$prior,strong_prior_pref_same$prior,1-strong_prior_pref_same$prior), 
    c(1-strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior,strong_prior_pref_diff$prior), 
    c(strong_prior_pref_diff$prior,strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior),
    c(1-strong_prior_novel_same$prior,1-strong_prior_novel_same$prior,strong_prior_novel_same$prior), 
    c(strong_prior_novel_same$prior,strong_prior_novel_same$prior,1-strong_prior_novel_same$prior), 
    c(1-strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior,strong_prior_novel_diff$prior), 
    c(strong_prior_novel_diff$prior,strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior))

mediumPrior <- data.frame(
  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("medium",8))

medium_prior_pref_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_pref_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "preference",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

medium_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "medium",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

mediumPrior$prior = list(
    c(1-medium_prior_pref_same$prior,1-medium_prior_pref_same$prior,medium_prior_pref_same$prior), 
    c(medium_prior_pref_same$prior,medium_prior_pref_same$prior,1-medium_prior_pref_same$prior), 
    c(1-medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior,medium_prior_pref_diff$prior), 
    c(medium_prior_pref_diff$prior,medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior),
    c(1-medium_prior_novel_same$prior,1-medium_prior_novel_same$prior,medium_prior_novel_same$prior), 
    c(medium_prior_novel_same$prior,medium_prior_novel_same$prior,1-medium_prior_novel_same$prior), 
    c(1-medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior,medium_prior_novel_diff$prior), 
    c(medium_prior_novel_diff$prior,medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior))

weakPrior <- data.frame(
  common_ground_manipulation = c("novelty","novelty","novelty","novelty"),
  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker"),
  alignment = c("congruent","incongruent","congruent","incongruent"),
  prior_manipulation = rep("weak",4))

weak_prior_novel_same <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "same_speaker")%>%
  summarise(prior = mean(correct))

weak_prior_novel_diff <- adult_ex4_prior_data %>%
  filter(common_ground_manipulation == "novelty",
         prior_manipulation == "weak",
         speaker == "different_speaker")%>%
  summarise(prior = mean(correct))

weakPrior$prior = list(
    c(1-weak_prior_novel_same$prior,1-weak_prior_novel_same$prior,weak_prior_novel_same$prior), 
    c(weak_prior_novel_same$prior,weak_prior_novel_same$prior,1-weak_prior_novel_same$prior), 
    c(1-weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior,weak_prior_novel_diff$prior), 
    c(weak_prior_novel_diff$prior,weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior))

# combining all priors into one data frame
predPrior = rbind(strongPrior,mediumPrior,weakPrior)

# data frame to keep track of unique conditions
allConditions <- predPrior %>%
  select(-prior)

```

#### Pragmatic model predictions

```{r model rsa noise, include = FALSE}
predictions.rsa <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions pragmatic model, include = FALSE}

# ex4_pragm_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.rsa, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior), 
#   data_var = "dataFromR",
#   model_var = "model",
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_pragm_model.rds")

ex4_pragm_model <- readRDS("../../stats/saves/ex4_pragm_model.rds")

# model predictions
ex4_pragm_model_pred <- ex4_pragm_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="pragmatic",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))

## noise parameter
ex4_pragm_model_noise <- ex4_pragm_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

#### Prior only model predictions

```{r model prior only , include = FALSE}
predictions.prior.only <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions prior only model, include = FALSE}

# ex4_prior_only_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
#   data_var = "dataFromR",
#   model_var = "model",
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_prior_only_model.rds")

ex4_prior_only_model <- readRDS("../../stats/saves/ex4_prior_only_model.rds")

# model predictions
ex4_prior_only_model_pred <- ex4_prior_only_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="prior_only",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))

## noise parameter
ex4_prior_only_model_noise <- ex4_prior_only_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

```{r model flat prior, include = FALSE}
predictions.flat.prior <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.predPrior

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})

   var conditionSpecificPriors = [.5, .5, .5]

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

  return extend(_.fromPairs(conditionOutput), {noise: noise})

}
'
```

```{r predictions prior only model, include = FALSE}

# ex4_flat_prior_model <- webppl(
#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior, sep='\n'),
#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
#   data_var = "dataFromR",
#   model_var = "model",
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# ) %>%
#   saveRDS("../../stats/saves/ex4_flat_prior_model.rds")

ex4_flat_prior_model <- readRDS("../../stats/saves/ex4_flat_prior_model.rds")

# model predictions
ex4_flat_prior_model_pred <- ex4_flat_prior_model %>%
  filter(!(Parameter %in% c("noise")))  %>%
  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
  mutate(model="flat_prior",
         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))

## noise parameter
ex4_flat_prior_model_noise <- ex4_flat_prior_model %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

```{r}
# combine model predictions with data

# summarize data 
adult_ex4_data_summary <- adult_ex4_data %>%
  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
  mutate(model = "data") %>%
  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         ci_lower  = qbeta(.025, a, b),
         ci_upper = qbeta(.975, a, b),
         mean = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

# summarize model predictions
ex_4_model_pred <- bind_rows(
  ex4_pragm_model_pred,
  ex4_prior_only_model_pred,
  ex4_flat_prior_model_pred
)%>%
  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper = hdi_upper(value))

# combine model predictions and data

ex_4_pred <- bind_rows(
  ex_4_model_pred,
  adult_ex4_data_summary
)

```

#### Plot model predictions and data

```{r plot ex4 model predictions and data}
ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Choosing More Informative")+
  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic","flat_prior","prior_only"),
                     values= c("black","#859900","#6c71c4","#b58900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

#### Correlation plot model predictions and data

```{r plot }
## correlation round 1

ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))

ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few(base_size = ) + 
  scale_colour_ptol()
```

### 2019-03-06 stats/adults/visualizations.Rmd
update kids model predictions

@@
 ```{r pretest data, include=FALSE}
-pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
-  filter(age != "2",
-         trial_type != "train")%>%
+pref_data <- bind_rows(read_csv(file="../data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
+                       read_csv(file="../data/kids_pref_2_data.csv"))%>%
+  filter(trial != "train")%>%
   mutate(age_bin = factor(age),
          experiment = "preference_pretest",
-         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
-         agent = ifelse( change == "false", agent, altAgent),
+         condition = ifelse(speakerChange == F | speakerChange == "false", "same_speaker", "different_speaker"),
+         agent = ifelse( speakerChange == F | speakerChange == "false", agent, altAgent),
          minage = min(age_num))%>%
@@
                       inf_data)
+
+ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
+  filter(trial != "filler1",trial != "filler2")%>%
+  mutate(binned_age=cut(age_num, breaks=seq.int(3, 5, 0.05), labels=seq.int(0, 1.95, 0.05)))
 ```
@@
   labs(x="age",y="Proportion Expected Choice")+
-  theme_few(base_size = 20) +
+  theme_few() +
   #ggtitle("Preference data")+
@@
 ```{r}
-ggsave("../graphs/kids_pref.png", width = 5, height = 4, scale = 1.5)
+ggsave("../graphs/kids_pref.png", width = 3.5, height = 3.5, scale = 1.2)
 ```
@@
   filter(age != 2)%>%
-  mutate(condition = ifelse(change == "false", "same_speaker", "different_speaker"))
+  mutate(condition = ifelse(change == F, "same_speaker", "different_speaker"))
 
@@
 ```{r}
-ggsave("../graphs/kids_novel.png", width = 5, height = 4, scale = 1.5)
+ggsave("../graphs/kids_novel.png", width = 3.5, height = 3.5, scale = 1.2)
 ```
@@
 ```{r}
+
+prior_only_predictions_across <- readRDS("../saves/prior_only_predictions_across.rds")
+
+prior_only_model_across <- prior_only_predictions_across %>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:4000,each = 40))%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "con", "congruent","incongruent"))
+
+model_pred_across <- readRDS("../saves/kids_model_predictions_across.rds")
+
+kids_model_pred_across <- model_pred_across%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3400,each = 40))%>%
+  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
+kids_model_pred_so <- model_pred_across%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3400,each = 40))%>%
+  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
+
+no_prior_pred_across <- bind_rows(
+  kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "same_speaker",
+                              Alignment = "congruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "different_speaker",
+                              Alignment = "congruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "same_speaker",
+                              Alignment = "incongruent"),
+    kids_model_pred_so%>%mutate(model = "no prior",
+                              Speaker = "different_speaker",
+                              Alignment = "incongruent")
+  ) %>%
+  mutate(prop_informative = plogis(so_int+so_slope*age_bin))
+
 model_comp_mean_ci <- bind_rows(
-#plot_model_pred%>%ungroup()%>%mutate(model = "RSA"), 
-plot_prior_only_pred%>%ungroup()%>%mutate(model = "Prior Only"),
-no_prior_plot%>%ungroup()%>%mutate(model = "No Prior")
-)
+kids_model_pred_across%>%mutate(model = "Pragmatic"), 
+prior_only_model_across%>%mutate(model = "Prior Only"),
+no_prior_pred_across%>%mutate(model = "No Prior")
+)%>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
 
-model_comp <- bind_rows(
-#kids_model_pred %>%mutate(model = "RSA"),
-prior_only_model%>%mutate(model = "Prior Only"),
-no_prior_pred%>%select(-so_slope,-so_int,-speakerOptimality)%>%mutate(model = "No Prior")
-  )
+```
+### All models predictions
 
+```{r, include = F}
+p_data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)
+
+ggplot(model_comp_mean_ci)+
+  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = .5, alpha = 1, linetype = 2) + 
+  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion More Informative")+
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  ylim(-0.05,1.05)+
+  facet_grid(~Speaker+Alignment)+
+  theme_few()+
+  coord_fixed(ratio = 2)+
+  scale_colour_brewer(palette = "Dark2")+
+  scale_fill_brewer(palette = "Dark2")
 ```
@@
 ```{r, include = F}
-ggplot(model_comp_mean_ci)+
-  geom_line(data = model_comp,aes(age_bin, prop_informative, group = paste(iteration,Speaker,model, sep= ""), col = model),  alpha = 0.01) + 
+ggsave("../graphs/kids_model_predictions.png", width = 10, height = 3, scale = 1)
+```
+
+### RSA model predictions
+
+```{r, include = F}
+
+model_comp_mean_ci_rsa <- bind_rows(
+kids_model_pred_across%>%mutate(model = "Pragmatic"), 
+prior_only_model_across%>%mutate(model = "Prior Only")%>%mutate(prop_informative = 5),
+no_prior_pred_across%>%mutate(model = "No Prior")%>%mutate(prop_informative = 5)
+)%>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
+
+p_data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)
+
+p_data_2 <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)%>%
+  summarise(correct_inf = mean(correct_inf))
+
+ggplot(model_comp_mean_ci_rsa)+
+  geom_jitter(data = p_data_2, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
   geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
-  geom_line(aes(age_bin, mean, col = model), size = 1, alpha = 1) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(y="proportion more informative")+
+  geom_line(aes(age_bin, mean, col = model), size = .5, alpha = 1, linetype = 2) + 
+  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion More Informative")+
   scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
   ylim(-0.05,1.05)+
-  facet_grid(Speaker~Alignment)+
-  theme_few(base_size = 20)+
-  scale_color_manual( values = c("#dc322f","#268bd2"))+
-  scale_fill_manual(values = c("#dc322f","#268bd2"))
+  facet_grid(~Speaker+Alignment)+
+  theme_few()+
+  coord_fixed(ratio = 2)+
+  scale_colour_brewer(palette = "Dark2")+
+  scale_fill_brewer(palette = "Dark2")
 ```
@@
 ```{r, include = F}
-ggsave("../graphs/kids_no_prior_prior_only_model_predictions.pdf", width = 9, height = 7, scale = 1.2)
+ggsave("../graphs/kids_data.png", width = 10, height = 3, scale = 1)
 ```
+
+```{r}
+
+data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(Speaker, Alignment ,subage) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         Data_ci_lower  = qbeta(.025, a, b),
+         Data_ci_upper = qbeta(.975, a, b),
+         Data = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+model <- kids_model_pred_across %>%
+  mutate(subage = ifelse(age_bin<1,"3","4"))%>%
+  group_by(model,Speaker,Alignment,subage)%>%
+  summarise(Model = mean(prop_informative),
+            Model_ci_lower =hdi_lower(prop_informative) ,
+            Model_ci_upper = hdi_upper(prop_informative))
+
+cor_plot <- model %>%
+  ungroup()%>%
+  mutate(Data = data$Data,
+         Data_ci_lower = data$Data_ci_lower,
+         Data_ci_upper  =data$Data_ci_upper,3)
+
+ggplot(data = cor_plot,aes(x = Model, y = Data, col = subage)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  coord_fixed()+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few() + 
+  scale_colour_solarized()
+
+cor.test(cor_plot$Model,cor_plot$Data)
+```
+
+```{r}
+ggsave("../graphs/model_critique_kids.png", width = 3, height = 2.5, scale = 1.3)
+```

### 2019-03-06 stats/kids/kids_model_predictions.Rmd
update kids model predictions

--- 2019-02-11 stats/kids/kids_model_predictions.Rmd
@@
 
-pref_data <- read_csv(file="../data/kids_pref_data.csv")%>%
-  filter(age != "2",
-         trial_type != "train")%>%
+pref_data <- bind_rows(read_csv(file="../data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
+                       read_csv(file="../data/kids_pref_2_data.csv"))%>%
+  filter(trial != "train")%>%
   mutate(age_bin = factor(age),
          experiment = "preference_pretest",
-         condition = ifelse(change == F | change == "false", "same_speaker", "different_speaker"),
-         agent = ifelse( change == F | change == "false", agent, altAgent),
+         condition = ifelse(speakerChange == F | speakerChange == "false", "same_speaker", "different_speaker"),
+         agent = ifelse( speakerChange == F | speakerChange == "false", agent, altAgent),
          minage = min(age_num))%>%
@@
 ex3_data <- read_csv(file="../data/kids_ex3_data.csv")%>%
-  filter(trial != "filler1",trial != "filler2")%>%
-  mutate(binned_age=cut(age_num, breaks=seq.int(3, 5, 0.05), labels=seq.int(0, 1.95, 0.05)))
+  filter(trial != "filler1",trial != "filler2")
 
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Proportion Expected Choice")+
+  labs(x="",y="Proportion Preferred Choice")+
   theme_few() +
-  ggtitle("Preference data")+
+  #ggtitle("Preference data")+
   ylim(-0.05,1.05)+
@@
   scale_fill_solarized()
+
+```
+
+```{r}
+
+ggsave("../graphs/ex_2_kids_pref.png", width = 2, height = 2, scale = 2)
 
@@
 
-# Model Predictions
-
-## Model parameters by age bin
-
-```{r}
-paramModelWebppl <- '
-
+# Model Predictions Across age bins
+
+## RSA model predictions across age bins
+
+```{r}
+modelPredAcrossWebppl <- '
 var levels = function(df, label){
@@
             diff_speaker_params.pref_slope * age_bin)
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
+    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
 
@@
             same_speaker_params.pref_slope * age_bin)
-
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
     return extend(
+    // diff_speaker_params, same_speaker_params, 
       {
@@
      speakerOptimality,
-      age_bin,
-
-    })
-
-  }, binned_age_range)
-
-  return predictions_by_age
-}
-'
-```
-
-```{r}
-params_by_age<- readRDS("../saves/params_by_age.rds")
-
-# params_by_age<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, paramModelWebppl , sep='\n'),
-#   data = pre_data,
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
-# )
-# 
-# saveRDS(params_by_age, file = "../saves/params_by_age.rds")
-
-model_params_by_age <- params_by_age%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  group_by(age_bin)%>%
-  summarise(so_map = estimate_mode(speakerOptimality),
-            diff_priorReg_map = estimate_mode(diff_priorReg),
-            same_priorReg_map = estimate_mode(same_priorReg))
-
-```
-
-## Basic RSA model predictions
-
-```{r}
-modelPredWebppl <- '
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-
-var ex3Data = dataFromR.ex3data
-var modelParams = dataFromR.modelParams
-
-    //display(JSON.stringify(ex3Data))
-
-var predict_by_age = function(age_bin){
-
-    //display(JSON.stringify(age_bin))
-
-    var speakerOptimality = age_bin.so_map
-
-    var diff_priorReg = age_bin.diff_priorReg_map
-
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
-
-    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
-
-    var same_priorReg =age_bin.same_priorReg_map
-
-    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
-
-    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
-
-    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
-
-    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
-
-  return extend(
-      {rsaPredictions_diff_cong,
+    rsaPredictions_diff_cong,
     rsaPredictions_diff_incong,
@@
       rsaPredictions_same_incong,
-      age_bin
+      age_bin,
+    //  so_slope,
+    //  so_int,
     })
 
- }
-
-var predictions_by_age = map(predict_by_age, modelParams)
-
-predictions_by_age
-
+  }, binned_age_range)
+
+  return predictions_by_age
+}
 '
@@
 
+Taking samples and munging the data.
+
 ```{r combined model predictions}
-
-#model_pred <- readRDS("../saves/kids_model_predictions.rds")
-
-model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
-  data = list(ex3data = ex3_data, modelParams = model_params_by_age),
-  data_var = "dataFromR"
-)
-
-#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
-
-kids_model_pred <- model_pred %>%
-  mutate(age_bin = age_bin.age_bin)%>%
-  select(rsaPredictions_diff_cong,rsaPredictions_diff_incong,rsaPredictions_same_cong,rsaPredictions_same_incong,age_bin)%>%
-  gather(condition, prop_informative, -age_bin)%>%
-  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
-  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
-         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
-```
-
-## Noisy model predictions
-
-```{r}
-ageConditions <- data.frame(
-  age_bin = rep(seq.int(0, 1.95, 0.05),4),
-  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
-  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))
-```
-
-```{r}
-noisyModelPredWebppl <- '
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-
-var ex3Data = dataFromR.ex3data
-var modelParams = dataFromR.modelParams[0]
-var ageConditions = dataFromR.ageConditions
-
-var model = function(){
-    var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-    var conditionOutput = map(function(conditionInfo){
-
-   var ageConditionSpecificData =  _.filter(ex3Data, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})
-
-   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})
-
-    display(JSON.stringify(ageSpecificParams))
-
-    var speakerOptimality = ageSpecificParams.so_map
-
-    var diff_priorReg = ageSpecificParams.diff_priorReg_map
-
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
-
-    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
-
-    map(function(d){ 
-      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
-    }, ageConditionSpecificData)
-
-  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
-
-}, ageConditions)
-
-}
-'
-```
-
-```{r}
-noisy_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
-  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 1,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
-)
-
-```
-
-```{r}
-noisyModelPredWebppl <- '
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
-var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
-
-// make finer grained as needed
-var binned_age_range = _.range(0, 2, 0.05)
-
-var all_conditions = levels(prefData, "condition")
-
-var foreach = function(fn, lst) {
-    var foreach_ = function(i) {
-        if (i < lst.length) {
-            fn(lst[i]);
-            foreach_(i + 1);
-        }
-    };
-    foreach_(0);
-};
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var model  = function(){
-
-  // global parameters
-
-  var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-  foreach(function(row){
-
-    var age = row.age_num
-
-    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
-
-    var inf_priorProbs = [.5, .5, .5]
-
-    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
-    inf_priorProbs, speakerOptimality)
-
-    observe(rsaPredictions, row.correct)
-
-  }, infData)
-
-  var pref_params = map(function(cndtn){
-
-    var conditionData = _.filter(prefData, {condition: cndtn})
-
-    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    foreach(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-
-      var priorProbs= [1-priorReg, priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-    }, conditionData)
-
-    return {pref_int, pref_slope, condition: cndtn}
-
-  }, all_conditions)
-
-  var diff_speaker_params = _.filter(pref_params, 
-        {condition: "different_speaker"})[0]
-
-  var same_speaker_params = _.filter(pref_params, 
-        {condition: "same_speaker"})[0]
-
-  var predictions_by_age = map(function(age_bin){
-
-    var speakerOptimality = so_int  + so_slope * age_bin
-
-    var diff_priorReg = logistic(diff_speaker_params.pref_int +
-            diff_speaker_params.pref_slope * age_bin)
-
-    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
-
-    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
-
-    var rsaPredictions_diff_cong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality)
-
-    var noisyRsaPredictions_diff_cong = expectation(addNoise(rsaPredictions_diff_cong, noise))
-
-    var rsaPredictions_diff_incong = pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality)
-
- var noisyRsaPredictions_diff_incong = expectation(addNoise(rsaPredictions_diff_incong, noise))
-
-    var same_priorReg = logistic(same_speaker_params.pref_int +
-            same_speaker_params.pref_slope * age_bin)
-
-    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
-
-    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
-
-  var rsaPredictions_same_cong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality)
-
- var noisyRsaPredictions_same_cong = expectation(addNoise(rsaPredictions_same_cong, noise))
-
-   var rsaPredictions_same_incong = pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality)
-
- var noisyRsaPredictions_same_incong = expectation(addNoise(rsaPredictions_same_incong, noise))
-
-    return [ 
-    [ age_bin + "_diff_cong",  noisyRsaPredictions_diff_cong],
-    [ age_bin + "_diff_incong",  noisyRsaPredictions_diff_incong],
-    [ age_bin + "_same_cong",  noisyRsaPredictions_same_cong],
-    [ age_bin + "_same_incong",  noisyRsaPredictions_same_incong],
-]
-
-  }, binned_age_range)
-
-return _.fromPairs(predictions_by_age.concat([
-["so_slope", so_slope],
-["so_int", so_int],
-["noise", noise]
-]))
-
-}
-'
-```
-
-```{r noisy combined model predictions}
-
-noisy_model_pred <- readRDS("../saves/kids_noisy_model_predictions.rds")
-
-noisy_model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
+model_pred_across <- readRDS("../saves/kids_model_predictions_across.rds")
+
+model_pred_across<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredAcrossWebppl , sep='\n'),
   data = pre_data,
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
 )
 
-#saveRDS(noisy_model_pred, file = "../saves/kids_noisy_model_predictions.rds")
-
-kids_noisy_model_pred <- noisy_model_pred%>%
+saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+kids_model_pred_across <- model_pred_across%>%
   select(value) %>%
   map_df(bind_rows)%>%
-  mutate(iteration = rep(1:8000,each = 40))%>%
+  mutate(iteration = rep(1:3400,each = 40))%>%
   select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
-  gather(condition, prop_informative, -iteration,-age_bin,-noise)%>%
+  gather(condition, prop_informative, -iteration,-age_bin)%>%
   separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
@@
          Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))
+
+kids_model_pred_so <- model_pred_across%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3400,each = 40))%>%
+  select(so_slope,so_int,age_bin,iteration,speakerOptimality)
+
+kids_model_pred_prior <- model_pred_across%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  mutate(iteration = rep(1:3400,each = 40))%>%
+  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
+  gather(condition, prop_preferred, -iteration,-age_bin)%>%
+  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))
 
@@
 
-prior_only_predictions <- readRDS("../saves/prior_only_predictions.rds")
+prior_only_predictions_across <- readRDS("../saves/prior_only_predictions_across.rds")
 
@@
 
-prior_only_model <- prior_only_predictions %>%
+prior_only_model_across <- prior_only_predictions_across %>%
   select(value) %>%
   map_df(bind_rows)%>%
-  mutate(iteration = rep(1:3000,each = 40))%>%
+  mutate(iteration = rep(1:4000,each = 40))%>%
   gather(condition, prop_informative, -iteration,-age_bin)%>%
@@
 
-# Sanity checks
+## Sanity checks
 
@@
 
-# Visualizing model predictions
-
-## RSA Model Predictions
+## Visualizing model predictions
+
+### RSA Model Predictions
 
@@
 
-```{r plot RSA model predictions, echo = F, fig.width= 10}
-
-  plot_model_pred <- kids_model_pred %>%
+```{r plot RSA model predictions, echo = F}
+
+  model_pred_across <- kids_model_pred_across %>%
   group_by(model,age_bin,Speaker,Alignment)%>%
@@
 
-ggplot(kids_model_pred)+
-  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
+ggplot(model_pred_across)+
   #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
-  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
-  geom_line(aes(age_bin, prop_informative), col = "black", size = 0.4, alpha = 1) + 
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(y="Proportion Expected Choice")+
-  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
-  ylim(-0.05,1.05)+
-  guides(col = F)+
-  facet_grid(Speaker~Alignment)+
-  theme_few()+
-  scale_color_solarized()+
-  scale_fill_solarized()
-```
-
-```{r, echo= F, fig.width= 10, fig.height = 8}
-pred_plot
-```
-
-## Noisy RSA Model Predictions
-
-```{r plot RSA model predictions, echo = F, fig.width= 10}
-
-  plot_noisy_model_pred <- kids_noisy_model_pred %>%
-  group_by(model,age_bin,Speaker,Alignment)%>%
-  summarise(mean = mean(prop_informative),
-            lci = hdi_lower(prop_informative),
-            uci = hdi_upper(prop_informative))
-
-pred_noisy_plot <- ggplot(plot_noisy_model_pred)+
-  #geom_line(data = kids_model_pred,aes(age_bin, prop_informative, group = paste(iteration,Speaker, sep= ""), col = Speaker),  alpha = 0.05) + 
-  #geom_pointrange(aes(y = mean, ymin = lci, ymax = uci))+
-  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = Speaker), alpha = .4) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci), alpha = .4) +
   geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
@@
 
-```{r, echo= F, fig.width= 10, fig.height = 8}
-pred_noisy_plot
-```
-
-## No Prior Model Predictions
+## No Prior Model Predictions Across
 
@@
 
-no_prior_pred <- bind_rows(
+no_prior_pred_across <- bind_rows(
   kids_model_pred_so%>%mutate(model = "no prior",
@@
 model_comp_mean_ci <- bind_rows(
-plot_model_pred%>%ungroup()%>%mutate(model = "RSA"), 
-plot_prior_only_pred%>%ungroup()%>%mutate(model = "Prior Only"),
-no_prior_plot%>%ungroup()%>%mutate(model = "No Prior")
-)
+kids_model_pred_across%>%mutate(model = "RSA"), 
+prior_only_model_across%>%mutate(model = "Prior Only"),
+no_prior_pred_across%>%mutate(model = "No Prior")
+)%>%
+  group_by(model,age_bin,Speaker,Alignment)%>%
+  summarise(mean = mean(prop_informative),
+            lci = hdi_lower(prop_informative),
+            uci = hdi_upper(prop_informative))
 
 #saveRDS(model_comp_mean_ci, "../saves/kids_model_comp_mean_ci.rds")
-
-model_comp <- bind_rows(
-kids_model_pred %>%mutate(model = "RSA"),
-prior_only_model%>%mutate(model = "Prior Only"),
-no_prior_pred%>%select(-so_slope,-so_int,-speakerOptimality)%>%mutate(model = "No Prior")
-  )
-
-# saveRDS(model_comp, "../saves/kids_model_comp.rds")
 
@@
 
-# Model vs data
-
-## Plot comparing model and data by continous age
-```{r comparison plot by age, echo= FALSE}
-
+## Model vs data
+
+### Predictions across age bins
+
+```{r comparison plot, echo= FALSE}
 p_data <- ex3_data %>%
@@
 
-ggplot(kids_model_pred)+
+ggplot(model_comp_mean_ci)+
   #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
-  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
-  geom_line(aes(age_bin, prop_informative, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
+  geom_line(aes(age_bin, mean, col = model), size = .7, alpha = 1, linetype = 1) + 
   geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
-  #geom_hline(yintercept = 0.5, lty=2)+
+  geom_hline(yintercept = 0.5, lty=2)+
   labs(y="proportion more informative")+
@@
 
-## Correlation plot
-```{r}
-
-data <- d %>%
+### Correlation plot
+```{r}
+
+data <- ex3_data %>%
   filter(trial != "filler1",
@@
 
-model <- model_comp %>%
+model <- kids_model_pred_across %>%
   mutate(subage = ifelse(age_bin<1,"3","4"))%>%
@@
   summarise(Model = mean(prop_informative),
-            Model_ci_lower = hdi_lower(prop_informative),
+            Model_ci_lower =hdi_lower(prop_informative) ,
             Model_ci_upper = hdi_upper(prop_informative))
@@
 ```
+
+# Model predictions by age bin
+
+## Model parameters by age bin
+
+```{r}
+paramModelWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
+
+// make finer grained as needed
+
+var binned_age_range = _.range(0, 2, 0.05)
+var all_conditions = levels(prefData, "condition")
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+  foreach(function(row){
+    var age = row.age_num
+    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+
+    var inf_priorProbs = [.5, .5, .5] 
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+    inf_priorProbs, speakerOptimality)
+
+    observe(rsaPredictions, row.correct)
+  }, infData)
+
+  var pref_params = map(function(cndtn){
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+      var age = row.age_num
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+    }, conditionData)
+
+    return [
+      {condition: cndtn, param: "pref_int", val: pref_int}, 
+      {condition: cndtn, param: "pref_slope", val: pref_slope}
+    ]
+
+  }, all_conditions)
+
+  return _.flatten(pref_params).concat(
+    [
+      {condition: "NA", param: "so_slope", val: so_slope},
+      {condition: "NA", param: "so_int", val: so_int}
+    ]
+  )
+}
+'
+```
+
+```{r}
+params_by_age<- readRDS("../saves/params_by_age.rds")
+
+params_by_age<- webppl(
+  program_code = paste(rsaUtils, rsaModel, paramModelWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+)
+
+#saveRDS(params_by_age, file = "../saves/params_by_age.rds")
+
+model_params <- params_by_age%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  group_by(condition,param)%>%
+  summarise(param_map = estimate_mode(val))%>%
+  mutate(cond = paste(condition, param, sep = "_"))%>%
+  ungroup()%>%
+  select(cond,param_map)%>%
+  spread(cond,param_map)
+
+```
+
+## RSA model predictions by age bin
+
+```{r}
+modelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+var age_bins = _.range(0, 2, 0.05)
+var ex3Data = dataFromR.ex3data
+var modelParams = dataFromR.modelParams[0]
+
+   //display(JSON.stringify(modelParams))
+
+var predict_by_age = function(age_bin){
+
+    //display(JSON.stringify(age_bin))
+
+    var speakerOptimality = modelParams.NA_so_int + modelParams.NA_so_slope * age_bin
+
+    var diff_priorReg = logistic(modelParams.different_speaker_pref_int + modelParams.different_speaker_pref_slope * age_bin)
+
+    //display(JSON.stringify(modelParams))
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
+
+    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
+
+    var same_priorReg = logistic(modelParams.same_speaker_pref_int + modelParams.same_speaker_pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+
+    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
+
+  return extend(
+      {rsaPredictions_diff_cong,
+      rsaPredictions_diff_incong,
+      rsaPredictions_same_cong,
+      rsaPredictions_same_incong,
+      age_bin
+    })
+
+ }
+
+var predictions_by_age = map(predict_by_age, age_bins)
+
+predictions_by_age
+
+'
+```
+
+```{r combined model predictions}
+
+model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
+  data = list(ex3data = ex3_data_param, modelParams = model_params),
+  data_var = "dataFromR"
+)
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+pred <- model_pred %>%
+  gather(condition, mean, -age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
+         model = "parameter free", 
+         age = age_bin+3)%>%
+  select(-age_bin)
+```
+
+## Noisy RSA model Predictions
+
+```{r}
+
+ex3_data_param <- ex3_data%>%
+  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
+         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
+         so_int = model_params$NA_so_int,
+         so_slope = model_params$NA_so_slope,
+         same_speaker_pref_int = model_params$same_speaker_pref_int,
+         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
+         so = plogis(so_int+so_slope*(age_num-min(age_num))),
+         diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
+         same_prior = plogis(same_speaker_pref_int+same_speaker_pref_slope*(age_num-min(age_num))))%>%
+  group_by(subid,trial)%>%
+        mutate(priorProbs = ifelse(Speaker == "same_speaker" & Alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
+                                   ifelse(Speaker == "different_speaker" & Alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
+                                          ifelse(Speaker == "same_speaker" & Alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
+                                                 list(c(diff_prior,diff_prior,1-diff_prior))
+
+                                   ))))%>%
+  select(Speaker,age_num,Alignment,so,priorProbs,correct_inf)
+
+```
+
+### Noise parameter across age
+
+```{r}
+noisyModelPredWebppl <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r}
+noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
+  data =list(ex3data = ex3_data_param),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+)
+
+posterior.noise <- noisy_model_pred %>%
+  filter(Parameter %in% c("noise"))
+
+ggplot(posterior.noise, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+noisy_pred <- noisy_model_pred %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("age", "Speaker", "Alignment"), sep="/")%>%
+  mutate( model = "noise parameter across age")%>%
+  group_by(model, age,Alignment,Speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+```
+
+### Developmental noise parameter
+
+```{r}
+developmentalNoisyModelPred <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.2})
+  var noise_int = uniformDrift({a: -2, b: 2, width: 0.2})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num))
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+dev_noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, developmentalNoisyModelPred , sep='\n'),
+  data =list(ex3data = ex3_data_param),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+)
+
+posterior.noise <- dev_noisy_model_pred %>%
+  filter(Parameter %in% c("noise_int", "noise_slope"))
+
+ggplot(posterior.noise, aes(x = value))+
+  geom_histogram()+
+  facet_wrap(~Parameter, scales = 'free')
+
+dev_noisy_pred <- dev_noisy_model_pred %>%
+  filter(!(Parameter %in% c("noise_int", "noise_slope"))) %>%
+  separate(Parameter, into = c("age", "Speaker", "Alignment"), sep="/")%>%
+  mutate( model = "developmental noise parameter")%>%
+  group_by(model, age,Alignment,Speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+```
+
+## Plot comparing noisy model and data by continous age
+```{r comparison plot by age, echo= FALSE}
+
+models <- bind_rows(
+  pred,
+  noisy_pred,
+  dev_noisy_pred
+)
+
+p_data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  mutate(age_bin = age_num - 3)%>%
+  group_by(Speaker, Alignment ,age_bin, subid)
+
+ggplot(models)+
+  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  ylim(-0.05,1.05)+
+  facet_grid(Speaker~Alignment)+
+  theme_few()+
+  scale_color_solarized()+
+  scale_fill_solarized()
+
+```
+
+```{r}
+data <- ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(Speaker, Alignment ,subage) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         Data_ci_lower  = qbeta(.025, a, b),
+         Data_ci_upper = qbeta(.975, a, b),
+         Data = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+model <- models %>%
+  mutate(age = ifelse(age<4,"3","4"))%>%
+  group_by(model,Speaker,Alignment,age)%>%
+  summarise(Model = mean(mean),
+            Model_ci_lower =hdi_lower(mean) ,
+            Model_ci_upper = hdi_upper(mean))
+
+cor_plot <- model %>%
+  ungroup()%>%
+  mutate(Data = rep(data$Data,3),
+         Data_ci_lower = rep(data$Data_ci_lower,3),
+         Data_ci_upper  =rep( data$Data_ci_upper,3))
+
+ggplot(data = cor_plot,aes(x = Model, y = Data, col = age)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  coord_fixed()+
+  facet_grid(~model)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few() + 
+  scale_colour_solarized()
+```

### 2019-03-06 papers/full_paper/models.Rmd
adult models for paper first pass

@@
 ---
-title: "MCC Model Predictions"
+title: "MCC Models"
 author: "Manuel Bohn"
-date: "15 6 2018"
 output: html_document
@@
 
-## Adult model predictions
+## Adult models
+
+### Experiment 3
+#### Model parameters and data
+
+```{r ex3 data}
+# load data  from experiment 4 to infer noise parameter
+adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
+```
+
+```{r}
+# load data from prior manipulation experiments to set priors
+adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
+adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
+```
+
+```{r model setup ex 4, include = FALSE}
+
+# create datafiles with model parameters
+predPriorEx3 <- data.frame(
+  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
+  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
+  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"))
+
+prior_pref_same <- adult_ex2_preference_data %>%
+  filter(condition == "same_speaker")%>%
+  summarise(prior = mean(correct))
+
+prior_pref_diff <- adult_ex2_preference_data %>%
+  filter(condition == "different_speaker")%>%
+  summarise(prior = mean(correct))
+
+prior_novel_same <- adult_ex2_novelty_data %>%
+  filter(condition == "same_speaker")%>%
+  summarise(prior = mean(correct))
+
+prior_novel_diff <- adult_ex2_novelty_data %>%
+  filter(condition == "different_speaker")%>%
+  summarise(prior = mean(correct))
+
+predPriorEx3$prior = list(
+    c(1-prior_pref_same$prior,1-prior_pref_same$prior,prior_pref_same$prior), 
+    c(prior_pref_same$prior,prior_pref_same$prior,1-prior_pref_same$prior), 
+    c(1-prior_pref_diff$prior,1-prior_pref_diff$prior,prior_pref_diff$prior), 
+    c(prior_pref_diff$prior,prior_pref_diff$prior,1-prior_pref_diff$prior),
+    c(1-prior_novel_same$prior,1-prior_novel_same$prior,prior_novel_same$prior), 
+    c(prior_novel_same$prior,prior_novel_same$prior,1-prior_novel_same$prior), 
+    c(1-prior_novel_diff$prior,1-prior_novel_diff$prior,prior_novel_diff$prior), 
+    c(prior_novel_diff$prior,prior_novel_diff$prior,1-prior_novel_diff$prior))
+
+# data frame to keep track of unique conditions
+allConditionsEx3 <- predPriorEx3 %>%
+  select(-prior)
+
+```
+
+#### Model predictions
+
+##### Pragmatic model
+
+```{r model rsa noise ex3, include = FALSE}
+predictions.rsa.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+
+}
+'
+```
+
+```{r predictions pragmatic model ex 3, include = FALSE}
+
+# ex3_pragm_model <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_pragm_model.rds")
+
+ex3_pragm_model <- readRDS("../../stats/saves/ex3_pragm_model.rds")
+
+# model predictions
+ex3_pragm_model_pred <- ex3_pragm_model %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic")
+
+## noise parameter
+ex3_pragm_model_noise <- ex3_pragm_model %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+##### Prior only model
+
+```{r model prior only ex3 , include = FALSE}
+predictions.prior.only.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+return extend(_.fromPairs(conditionOutput), {noise: noise})
+
+}
+'
+```
+
+```{r predictions prior only model ex3, include = FALSE}
+
+# ex3_prior_only_model <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_prior_only_model.rds")
+
+ex3_prior_only_model <- readRDS("../../stats/saves/ex3_prior_only_model.rds")
+
+# model predictions
+ex3_prior_only_model_pred <- ex3_prior_only_model %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only")
+
+## noise parameter
+ex3_prior_only_model_noise <- ex3_prior_only_model %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+##### Flat prior model
+
+```{r model flat prior ex3, include = FALSE}
+predictions.flat.prior.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+   map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allConditions)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+
+}
+'
+```
+
+```{r predictions prior only model ex3, include = FALSE}
+
+# ex3_flat_prior_model <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_flat_prior_model.rds")
+
+ex3_flat_prior_model <- readRDS("../../stats/saves/ex3_flat_prior_model.rds")
+
+# model predictions
+ex3_flat_prior_model_pred <- ex3_flat_prior_model %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior")
+
+## noise parameter
+ex3_flat_prior_model_noise <- ex3_flat_prior_model %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+```{r}
+# combine model predictions with data
+
+# summarize data 
+adult_ex3_data_summary <- adult_ex3_data %>%
+  mutate(model = "data") %>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+# summarize model predictions
+ex_3_model_pred <- bind_rows(
+  ex3_pragm_model_pred,
+  ex3_prior_only_model_pred,
+  ex3_flat_prior_model_pred
+)%>%
+  group_by(model,common_ground_manipulation,speaker,alignment) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper = hdi_upper(value))
+
+# combine model predictions and data
+
+ex_3_pred <- bind_rows(
+  ex_3_model_pred,
+  adult_ex3_data_summary
+)
+
+```
+
+##### Plot model predictions and data
+
+```{r plot ex3 model predictions and data}
+ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Choosing More Informative")+
+  facet_grid (~ common_ground_manipulation + speaker) +
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_manual(name="Model",
+                     breaks=c("data","pragmatic","flat_prior","prior_only"),
+                     values= c("black","#859900","#6c71c4","#b58900"))+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+```
+
+##### Correlation plot model predictions and data
+
+```{r plot }
+
+ex_3_cor_plot <- ex_3_pred %>%
+  ungroup()%>%
+  filter(model != "data") %>%
+  mutate(data_mean = rep(ex_3_pred%>%filter(model == "data")%>%pull(mean),3),
+         data_ci_lower = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_lower),3),
+         data_ci_upper = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_upper),3))
+
+ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "#BB5566")) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  guides(col = F)+
+  facet_grid ( ~ model) +
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
+  theme_few()
+
+```
+
+#### Model comparison
+
+```{r model likelihood rsa ex3, include = FALSE}
+loglike.rsa.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+}, allConditions)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r model likelihood prior only ex3 , include = FALSE}
+loglike.prior.only.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+}, allConditions)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r model likelihood flat prior ex3, include = FALSE}
+loglike.flat.prior.ex3 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+
+var model = function(){
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+}, allConditions)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r ex3 model comparison}
+# ex3_pragm_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+
+ex3_pragm_model_loglike <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")%>%
+  mutate(model = "pragmatic")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+# ex3_prior_only_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# )%>%
+#   saveRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")
+
+ex3_prior_only_model_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")%>%
+  mutate(model = "prior_only")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+# ex3_flat_prior_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex3, sep='\n'),
+#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# )%>%
+#   saveRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")
+
+ex3_flat_prior_model_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")%>%
+  mutate(model = "flat_prior")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_model_comparison <- bind_rows(
+  ex3_pragm_model_loglike,
+  ex3_prior_only_model_loglike,
+  ex3_flat_prior_model_loglike
+)%>%
+  mutate(model = reorder(model,logP))
+```
+##### Plot for likelihoods
+
+```{r}
+ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
+  geom_point(size = 7)+
+  theme_few()+ 
+  xlab("Model")+
+  ylab("Log-likelihood")+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(col = F)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#859900","#b58900","#6c71c4"))
+```
+
+##### Bayes factors
+
+```{r}
+ex3_bf <- data.frame(
+  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
+  bayes_factor = c(
+    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"]),
+    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]),
+    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]))
+)
+
+ex3_bf%>%
+  kable(digits = 2)
+```
 
@@
 
-```{r model setup, include = FALSE}
+```{r model setup ex 4, include = FALSE}
 
@@
 # combining all priors into one data frame
-predPrior = rbind(strongPrior,mediumPrior,weakPrior)
+predPriorEx4 = rbind(strongPrior,mediumPrior,weakPrior)
 
 # data frame to keep track of unique conditions
-allConditions <- predPrior %>%
+allConditionsEx4 <- predPriorEx4 %>%
   select(-prior)
@@
 
-#### Pragmatic model predictions
+#### Model predictions
 
-```{r model rsa noise, include = FALSE}
-predictions.rsa <-'
+##### Pragmatic model
+
+```{r model rsa noise ex4, include = FALSE}
+predictions.rsa.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var conditionOutput = map(function(conditionInfo){
+
+    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
+
+  }, allConditions)
+
+   conditionOutput
+
+'
+```
+
+```{r predictions pragmatic model, include = FALSE}
+
+ex4_pragm_model <- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
+  data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+  data_var = "dataFromR"
+)
+
+# model predictions
+ex4_pragm_model_pred <- ex4_pragm_model %>%
+  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+  mutate(value = `1`,
+         model="pragmatic",
+         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  select(-`1`)
+
+```
+
+##### Prior only model
+
+```{r model prior only ex4 , include = FALSE}
+predictions.prior.only.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var conditionOutput = map(function(conditionInfo){
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
+
+}, allConditions)
+
+conditionOutput
+
+'
+```
+
+```{r predictions prior only model ex 4, include = FALSE}
+
+ex4_prior_only_model <- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
+  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_prior_only_model_noise$mean),
+  data_var = "dataFromR"
+)
+
+# model predictions
+ex4_prior_only_model_pred <- ex4_prior_only_model %>%
+  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+  mutate(value = `1`,
+         model="prior_only",
+         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  select(-`1`)
+
+```
+
+##### Flat prior model
+
+```{r model flat prior ex4, include = FALSE}
+predictions.flat.prior.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var conditionOutput = map(function(conditionInfo){
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
+
+}, allConditions)
+
+conditionOutput
+
+'
+```
+
+```{r predictions flat prior model ex 4, include = FALSE}
+
+ex4_flat_prior_model <- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
+  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_flat_prior_model_noise$mean),
+  data_var = "dataFromR"
+)
+
+# model predictions
+ex4_flat_prior_model_pred <- ex4_flat_prior_model %>%
+separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+  mutate(value = `1`,
+         model="flat_prior",
+         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  select(-`1`)
+```
+
+```{r}
+# combine model predictions with data
+
+# summarize data 
+adult_ex4_data_summary <- adult_ex4_data %>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  mutate(model = "data") %>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+# summarize model predictions
+ex_4_model_pred <- bind_rows(
+  ex4_pragm_model_pred,
+  ex4_prior_only_model_pred,
+  ex4_flat_prior_model_pred
+) %>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  rename(mean = value)%>%
+  summarise(mean = mean,
+            ci_lower = mean,
+            ci_upper= mean)
+
+# combine model predictions and data
+
+ex_4_pred <- bind_rows(
+  ex_4_model_pred,
+  adult_ex4_data_summary
+)
+
+```
+
+##### Plot model predictions and data
+
+```{r plot ex4 model predictions and data}
+ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Choosing More Informative")+
+  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_manual(name="Model",
+                     breaks=c("data","pragmatic","flat_prior","prior_only"),
+                     values= c("black","#859900","#6c71c4","#b58900"))+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+```
+
+##### Correlation plot model predictions and data
+
+```{r plot }
+## correlation round 1
+
+ex_4_cor_plot <- ex_4_pred %>%
+  ungroup()%>%
+  filter(model != "data") %>%
+  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
+         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
+         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))
+
+ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid ( ~ model) +
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
+  theme_few(base_size = ) + 
+  scale_colour_ptol()
+```
+
+#### Model comparison
+
+```{r model likelihood rsa ex4, include = FALSE}
+loglike.rsa.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var model = function(){
+
+var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+  }, allConditions)
+
+  return sum(conditionOutput)
+
+}
+'
+```
+
+```{r model likelihood prior only ex4 , include = FALSE}
+loglike.prior.only.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var model = function(){
+
+var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+  }, allConditions)
+
+  return sum(conditionOutput)
+}
+'
+```
+
+```{r model likelihood flat prior ex4, include = FALSE}
+loglike.flat.prior.ex4 <-'
+var allConditions = dataFromR.allConditions
+var allData = dataFromR.allData
+var allPriorProbs = dataFromR.predPrior
+var noise = dataFromR.noise[0]
+
+var model = function(){
+
+var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+
+  return  loglike
+
+  }, allConditions)
+
+  return sum(conditionOutput)
+}
+'
+```
+
+```{r ex 4 model comparison}
+# ex4_pragm_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4, sep='\n'),
+#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_pragm_model_loglike.rds")
+
+ex4_pragm_model_loglike <- readRDS("../../stats/saves/ex4_pragm_model_loglike.rds")%>%
+  mutate(model = "pragmatic")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+# ex4_prior_only_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex4, sep='\n'),
+#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")
+
+ex4_prior_only_model_loglike <- readRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")%>%
+  mutate(model = "prior_only")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+# ex4_flat_prior_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex4, sep='\n'),
+#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")
+
+ex4_flat_prior_model_loglike <- readRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")%>%
+  mutate(model = "flat_prior")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex4_model_comparison <- bind_rows(
+  ex4_pragm_model_loglike,
+  ex4_prior_only_model_loglike,
+  ex4_flat_prior_model_loglike
+)%>%
+  mutate(model = reorder(model,logP))
+```
+
+##### Plot for likelihoods
+
+```{r}
+ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
+  geom_point(size = 7)+
+  theme_few()+ 
+  xlab("Model")+
+  ylab("Log-likelihood")+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(col = F)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#859900","#6c71c4"))
+```
+
+##### Bayes factors
+
+```{r}
+ex4_bf <- data.frame(
+  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
+  bayes_factor = c(
+    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]),
+    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"]),
+    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]))
+)
+
+ex4_bf%>%
+  kable(digits = 2)
+```
+#### Appendix: Model predictions with inferred noise
+
+```{r model rsa noise ex4, include = FALSE}
+predictions.rsa.ex4 <-'
 var allConditions = dataFromR.allConditions
@@
 
-```{r predictions pragmatic model, include = FALSE}
+```{r predictions pragmatic model ex 4 inf noise, include = FALSE}
 
-# ex4_pragm_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.rsa, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior), 
+# ex4_pragm_model_inf_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
+#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4),
 #   data_var = "dataFromR",
 #   model_var = "model",
+#   chains = 4,
+#   cores = 4,
 #   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
 # ) %>%
-#   saveRDS("../../stats/saves/ex4_pragm_model.rds")
+#   saveRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")
 
-ex4_pragm_model <- readRDS("../../stats/saves/ex4_pragm_model.rds")
+ex4_pragm_model_inf_noise <- readRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")
 
 # model predictions
-ex4_pragm_model_pred <- ex4_pragm_model %>%
+ex4_pragm_model_pred_inf_noise <- ex4_pragm_model_inf_noise %>%
   filter(!(Parameter %in% c("noise")))  %>%
@@
 ## noise parameter
-ex4_pragm_model_noise <- ex4_pragm_model %>%
+ex4_pragm_model_noise_inf_noise <- ex4_pragm_model_inf_noise %>%
   filter(Parameter %in% c("noise"))  %>%
@@
 
-#### Prior only model predictions
-
-```{r model prior only , include = FALSE}
-predictions.prior.only <-'
+```{r model prior only ex4 , include = FALSE}
+predictions.prior.only.ex4 <-'
 var allConditions = dataFromR.allConditions
@@
 
-```{r predictions prior only model, include = FALSE}
+```{r predictions prior only model ex 4 inf noise, include = FALSE}
 
-# ex4_prior_only_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only, sep='\n'),
+# ex4_prior_only_model_inf_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
 #   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
@@
 # ) %>%
-#   saveRDS("../../stats/saves/ex4_prior_only_model.rds")
+#   saveRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")
 
-ex4_prior_only_model <- readRDS("../../stats/saves/ex4_prior_only_model.rds")
+ex4_prior_only_model_inf_noise <- readRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")
 
 # model predictions
-ex4_prior_only_model_pred <- ex4_prior_only_model %>%
+ex4_prior_only_model_pred_inf_noise <- ex4_prior_only_model_inf_noise %>%
   filter(!(Parameter %in% c("noise")))  %>%
@@
 ## noise parameter
-ex4_prior_only_model_noise <- ex4_prior_only_model %>%
+ex4_prior_only_model_noise_inf_noise <- ex4_prior_only_model_inf_noise %>%
   filter(Parameter %in% c("noise"))  %>%
@@
 
-```{r model flat prior, include = FALSE}
-predictions.flat.prior <-'
+```{r model flat prior ex4, include = FALSE}
+predictions.flat.prior.ex4 <-'
 var allConditions = dataFromR.allConditions
@@
 
-```{r predictions prior only model, include = FALSE}
+```{r predictions flat prior model ex 4 inf noise, include = FALSE}
 
-# ex4_flat_prior_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior, sep='\n'),
+# ex4_flat_prior_model_inf_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
 #   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
@@
 # ) %>%
-#   saveRDS("../../stats/saves/ex4_flat_prior_model.rds")
+#   saveRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")
 
-ex4_flat_prior_model <- readRDS("../../stats/saves/ex4_flat_prior_model.rds")
+ex4_flat_prior_model_inf_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")
 
 # model predictions
-ex4_flat_prior_model_pred <- ex4_flat_prior_model %>%
+ex4_flat_prior_model_pred_inf_noise <- ex4_flat_prior_model_inf_noise %>%
   filter(!(Parameter %in% c("noise")))  %>%
@@
 ## noise parameter
-ex4_flat_prior_model_noise <- ex4_flat_prior_model %>%
+ex4_flat_prior_model_noise_inf_noise <- ex4_flat_prior_model_inf_noise %>%
   filter(Parameter %in% c("noise"))  %>%
@@
 
-```{r}
-# combine model predictions with data
-
-# summarize data 
-adult_ex4_data_summary <- adult_ex4_data %>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
-  mutate(model = "data") %>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  summarize(k = sum(correct_inf), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         ci_lower  = qbeta(.025, a, b),
-         ci_upper = qbeta(.975, a, b),
-         mean = (a-1)/(a+b-2))%>%
-  select(-a,-b,-n,-k)
-
-# summarize model predictions
-ex_4_model_pred <- bind_rows(
-  ex4_pragm_model_pred,
-  ex4_prior_only_model_pred,
-  ex4_flat_prior_model_pred
-)%>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper = hdi_upper(value))
-
-# combine model predictions and data
-
-ex_4_pred <- bind_rows(
-  ex_4_model_pred,
-  adult_ex4_data_summary
-)
-
-```
-
-#### Plot model predictions and data
-
-```{r plot ex4 model predictions and data}
-ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
-  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
-  theme_few() + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_color_manual(name="Model",
-                     breaks=c("data","pragmatic","flat_prior","prior_only"),
-                     values= c("black","#859900","#6c71c4","#b58900"))+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
-```
-
-#### Correlation plot model predictions and data
-
-```{r plot }
-## correlation round 1
-
-ex_4_cor_plot <- ex_4_pred %>%
-  ungroup()%>%
-  filter(model != "data") %>%
-  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
-         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
-         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))
-
-ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = 1)+
-  geom_point(size = 3)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  facet_grid ( ~ model) +
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
-  theme_few(base_size = ) + 
-  scale_colour_ptol()
-```
+# Children

### 2019-03-06 stats/kids/kids_model_predictions.Rmd
adult models for paper first pass

@@
                                    ))))%>%
-  select(Speaker,age_num,Alignment,so,priorProbs,correct_inf)
+  ungroup()%>%
+  mutate(min_age = min(age_num))%>%
+  select(Speaker,age_num,min_age,Alignment,so,priorProbs,correct_inf)
 
@@
 
-  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.2})
-  var noise_int = uniformDrift({a: -2, b: 2, width: 0.2})
+  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var noise_int = uniformDrift({a: -2, b: 2, width: 0.4})
 
@@
 
-    var noise = logistic(noise_int + noise_slope * (row.age_num))
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.min_age))
+
+    //display(JSON.stringify(noise))
 
@@
   mutate(age = as.numeric(age))
+```
+
+```{r}
+
+x <- data_frame(
+  age = rep(seq(0,2, by = 0.05),8),
+  param = c(rep("-2/-2",41),rep("-2/-1",41),rep("-1/-1",41),rep("-1/0",41),rep("0/-1",41),rep("1/1",41),rep("2/1",41),rep("2/2",41)),
+  int = c(rep(-2,41),rep(-2,41),rep(-1,41),rep(-1,41),rep(0,41),rep(1,41),rep(2,41),rep(2,41)),
+  slope = c(rep(-2,41),rep(-1,41),rep(-1,41),rep(0,41),rep(-1,41),rep(1,41),rep(1,41),rep(2,41))
+) %>%
+  mutate(y = plogis(int + slope *age))
+
+ggplot(x, aes(x = age, y= y,col = param))+
+  geom_line()+
+  ylim(0,1)
 

### 2019-03-08 papers/full_paper/methods.Rmd
advance model description for paper

@@
 #          agent = ifelse( speakerChange == F, agent, altAgent),
-#          id = subid)%>%
+#          id = subid,
+#          minage = min(age_num))%>%
 #   filter(trial != "train")%>%
-#   select(experiment,id,age_bin,age_num,trial,condition,agent,correct)
+#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)
 # 
@@
 #          experiment = "child_ex1",
-#          id =subid)%>%
-#   select(experiment,id,age_bin,age_num,trial,correct)
+#          id =subid,
+#          minage = min(age_num))%>%
+#   select(experiment,id,age_bin,age_num,minage,trial,correct)
 # 
@@
 #          speaker = Speaker,
-#          alignment = Alignment)%>%
+#          alignment = Alignment,
+#          minage = min(age_num))%>%
 #   filter(trial != "filler1",trial != "filler2")%>%
-#   select(experiment, id,age_bin,age_num,trial, speaker, alignment, agent, correct_inf)
+#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)
 # 
@@
 child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv")
+
+# model predictions adults ex3
+ex3_model_predictions <- readRDS("../../stats/saves/ex3_model_predictions.rds")
+# model comparison adults ex3
+ex3_model_comparison <- readRDS("../../stats/saves/ex3_model_comparison.rds")
+# model predictions adults ex4
+ex4_model_predictions <- readRDS("../../stats/saves/ex4_model_predictions.rds")
+# model comparison adults ex4
+ex4_model_comparison <- readRDS("../../stats/saves/ex4_model_comparison.rds")
 ```

### 2019-03-08 papers/full_paper/models.Rmd
advance model description for paper

@@
 
-# Adults
-
-## Model utensils code
+# Model code
+
+## Model utensils
 
@@
 
+var prior_objects = [
+{ shape: "triangle", id:1, location: 1},  
+{ shape: "circle", id:1, location: 2}
+]
+
 var labels = ["dax","wug"]
@@
 }
-'
-```
-
-## Pragmatic RSA model code
+
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+'
+```
+
+# Adults
+
+## RSA model code
 
@@
 
-## Adult models
-
-### Experiment 3
-#### Model parameters and data
+## Experiment 3
+
+### Model parameters and data
 
 ```{r ex3 data}
-# load data  from experiment 4 to infer noise parameter
+# load data from experiment 3
 adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
@@
 
-#### Model predictions
+### Model predictions
 
@@
 )
+
+#saveRDS(ex_3_pred, "../../stats/saves/ex3_model_predictions.rds")
 
@@
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_point(size = 3)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
   coord_fixed()+
@@
 
-#### Model comparison
+### Model comparison
 
@@
   mutate(model = reorder(model,logP))
+
+#saveRDS(ex3_model_comparison, "../../stats/saves/ex3_model_comparison.rds")
+
 ```
@@
 
-### Experiment 4
-
-#### Model parameters and data
+## Experiment 4
+
+### Model parameters and data
 ```{r ex4 data}
-# load data  from experiment 4 to infer noise parameter
+# load data  from experiment 4 
 adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
@@
 # load data from prior strength manipulation experiments to set priors
-
 adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
@@
 
+#saveRDS(ex_4_pred, "../../stats/saves/ex4_model_predictions.rds")
+
 ```
@@
   mutate(model = reorder(model,logP))
+
+#saveRDS(ex4_model_comparison, "../../stats/saves/ex4_model_comparison.rds")
 ```
@@
 # Children
+
+## RSA model code
+```{r rsa model}
+
+childRsaModel <- '
+var literalListener = cache(function(utterance, priorProbs){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior); 
+var lexicon = lexiconObject[lexiconName];
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+if ("label" in utterance) {
+ var truthValue = lexicon(utterance, obj);
+ condition(truthValue)
+}
+if (utterance.point) {
+ var truthValuePoint = point(utterance, obj);
+ condition(truthValuePoint)
+}
+return obj.shape 
+}})
+})
+
+var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance, priorProbs);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+})
+
+var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior);
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
+observe(S1, utterance)
+return obj.shape == "circle" ? 1 : 0
+}})
+})
+
+var addNoise = function(dist, noiseParam){
+   Infer({model: function(){ 
+      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
+    }
+   })
+}
+'
+```
+
+## Model parameters and data
+
+```{r ex3 data}
+# children ex3 data
+child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
+```
+
+```{r}
+# load data from ex1 manipulation experiments to set speaker optimality parameter
+child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
+# load data from ex2 experiment to set priors
+child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
+```
+
+```{r}
+childModelParam <- '
+var prefData = dataFromR.prefData
+var infData = dataFromR.infData
+
+var all_conditions = levels(prefData, "condition")
+
+var model  = function(){
+
+  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+  foreach(function(row){
+
+  var age = row.age_num
+  var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
+
+    var inf_priorProbs = [.5, .5, .5]
+
+  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+   inf_priorProbs, speakerOptimality) 
+   observe(rsaPredictions, row.correct)
+
+  }, infData)
+
+  var pref_params = map(function(cndtn){
+
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+
+      var age = row.age_num
+
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+
+    }, conditionData)
+
+    return [
+      {param: "pref_int", val: pref_int, condition: cndtn}, 
+      {param: "pref_slope", val: pref_slope, condition: cndtn}
+    ]
+
+  }, all_conditions)
+
+  return _.flatten(pref_params).concat(
+    [
+      { param: "so_slope", val: so_slope},
+      { param: "so_int", val: so_int}
+    ]
+  )
+}
+'
+```
+
+```{r}
+# child_model_param<- webppl(
+#   program_code = paste(rsaUtils, childRsaModel, childModelParam , sep='\n'),
+#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+# )%>%
+#   saveRDS("../../stats/saves/child_model_param.rds")
+
+child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  group_by(param,condition)%>%
+  summarise(param_map = estimate_mode(val))%>%
+  mutate(cond = paste(param,condition, sep = "_"))%>%
+  ungroup()%>%
+  select(cond,param_map)%>%
+  spread(cond,param_map)%>%
+  rename(so_int = so_int_NA,
+         so_slope = so_slope_NA)
+
+```
+
+```{r}
+# visualize model priors in comparison to data 
+child_prior_plot <- child_ex2_data %>%
+  group_by(id,age_num,minage,condition)%>%
+  summarise(correct = mean(correct))%>%
+  mutate(model = ifelse(condition == "different_speaker",
+                        plogis(child_model_param$pref_int_different_speaker + child_model_param$pref_slope_different_speaker * (age_num-minage)),
+                        plogis(child_model_param$pref_int_same_speaker + child_model_param$pref_slope_same_speaker * (age_num-minage)
+                        )))
+
+ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
+  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
+  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
+  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="Age",y="Proportion Correct")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_solarized(name = "Condition")+
+  scale_fill_solarized(name = "Condition")
+```
+
+```{r}
+# visualize speaker optimality in comparison to data 
+child_so_plot <- child_ex1_data %>%
+  group_by(id,age_num,minage)%>%
+  summarise(correct = mean(correct))%>%
+  mutate(model = child_model_param$so_int + child_model_param$so_slope * (age_num - minage))
+
+ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
+  geom_line(alpha = .5, size = .7)+
+  labs(x="Age",y="Speaker optimality parameter")+
+  theme_few() +
+  geom_hline(yintercept = 0, lty=2)+
+  ylim(-3,3)+
+  guides(alpha = F)
+```
+
+```{r}
+ex3_model_data <- child_ex3_data%>%
+  mutate(so_int = child_model_param$so_int,
+         so_slope = child_model_param$so_slope,
+         pref_int_different_speaker = child_model_param$pref_int_different_speaker,
+         pref_slope_different_speaker = child_model_param$pref_slope_different_speaker,
+         pref_int_same_speaker = child_model_param$pref_int_same_speaker,
+         pref_slope_same_speaker = child_model_param$pref_slope_same_speaker,
+         so = so_int+so_slope*(age_num-min(age_num)),
+         diff_prior = plogis(pref_int_different_speaker+pref_slope_different_speaker*(age_num-min(age_num))),
+         same_prior = plogis(pref_int_same_speaker+pref_slope_same_speaker*(age_num-min(age_num))))%>%
+  group_by(id,trial)%>%
+        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
+                                   ifelse(speaker == "different_speaker" & alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
+                                          ifelse(speaker == "same_speaker" & alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
+                                                 list(c(diff_prior,diff_prior,1-diff_prior))
+
+                                   ))))%>%
+  ungroup()%>%
+  select(speaker,age_num,minage,alignment,so,priorProbs,correct_inf)
+
+```
+## Model predictions
+
+### Pragmatic model
+
+```{r}
+child.ex3.rsa.predictions <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_pragm_model<- webppl(
+#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
+#   data =list(ex3data = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model.rds")
+
+child_ex3_pragm_model <- readRDS("../../stats/saves/child_ex3_pragm_model.rds")
+
+child_ex3_pragm_model_predictions <- child_ex3_pragm_model%>%
+  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
+  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic")%>%
+  group_by(model,age,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+child_ex3_pragm_model_noise <- child_ex3_pragm_model %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+### Prior only model
+
+```{r}
+child.ex3.prior.only.predictions <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_prior_only_model<- webppl(
+#   program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
+#   data =list(ex3data = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model.rds")
+
+child_ex3_prior_only_model <- readRDS("../../stats/saves/child_ex3_prior_only_model.rds")
+
+child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model%>%
+  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
+  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only")%>%
+  group_by(model,age,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+child_ex3_prior_only_model_noise <- child_ex3_prior_only_model %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+### Flat prior model
+
+```{r}
+child.ex3.flat.prior.predictions <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
+
+    var prior = [.5, .5, .5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_flat_prior_model<- webppl(
+#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
+#   data =list(ex3data = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model.rds")
+
+child_ex3_flat_prior_model <- readRDS("../../stats/saves/child_ex3_flat_prior_model.rds")
+
+child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model%>%
+  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
+  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior")%>%
+  group_by(model,age,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+child_ex3_flat_prior_model_noise <- child_ex3_flat_prior_model %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+### Plot for noise parameter
+
+```{r visualizing noise parameters}
+plot_noise_param <- data_frame(
+  age = rep(seq(0,2, by = 0.05),3),
+  model = c(
+    rep("pragmatic",41),
+    rep("prior_only",41),
+    rep("flat_prior",41)),
+  int = c(
+    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
+    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
+    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41)
+    ),
+  slope = c(
+    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
+    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
+    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41)
+    )
+) %>%
+  mutate(y = plogis(int + slope *age))
+
+plot_child_noise_param_dev <- ggplot(plot_noise_param, aes(x = age, y= y, col = model))+
+  geom_line(size = 2)+
+  ylim(0,1)+
+  theme_few()+
+  ylab("Noise parameter")+
+  scale_color_manual(name="Model",
+                     breaks=c("pragmatic","flat_prior","prior_only"),
+                     values= c("#859900","#6c71c4","#b58900"))
+
+child_noise_param_by_model <- bind_rows(
+  child_ex3_pragm_model%>%mutate(model="pragmatic"),
+  child_ex3_prior_only_model%>%mutate(model="prior_only"),
+  child_ex3_flat_prior_model%>%mutate(model="flat_prior")
+) %>%
+  filter(Parameter %in% c("noise_int", "noise_slope"))
+
+plot_child_noise_param_by_model <- ggplot(child_noise_param_by_model, aes(x = value, col = model))+
+  geom_density()+
+  facet_grid(model~Parameter, scales = 'free')+
+  theme_few()+
+  scale_color_manual(name="Model",
+                     breaks=c("pragmatic","flat_prior","prior_only"),
+                     values= c("#859900","#6c71c4","#b58900"))
+
+ggarrange(plot_child_noise_param_by_model, plot_child_noise_param_dev, common.legend = T)
+```
+
+### Plot model predictions and data
+
+```{r}
+child_model_predictions <- bind_rows(
+  child_ex3_pragm_model_predictions,
+  child_ex3_flat_prior_model_predictions,
+  child_ex3_prior_only_model_predictions
+  )
+
+plot_child_ex3_data <- child_ex3_data%>%
+  group_by(age_num,speaker,alignment)%>%
+  summarise(mean = mean(correct_inf))
+
+ggplot(child_model_predictions)+
+  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="proportion more informative")+
+  ylim(-0.05,1.05)+
+  facet_grid(speaker~alignment)+
+  theme_few()+
+  scale_color_manual(name="Model",
+                     breaks=c("pragmatic","flat_prior","prior_only"),
+                     values= c("#859900","#6c71c4","#b58900"))+
+  scale_fill_manual(name="Model",
+                     breaks=c("pragmatic","flat_prior","prior_only"),
+                     values= c("#859900","#6c71c4","#b58900"))
+
+```
+
+### Correlation plot model predictions and data
+
+```{r}
+child_cor_data <- child_ex3_data %>%
+  filter(trial != "filler1",
+         trial != "filler2")%>%
+  group_by(speaker, alignment, age_bin) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         Data_ci_lower  = qbeta(.025, a, b),
+         Data_ci_upper = qbeta(.975, a, b),
+         Data = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+child_cor_model <- child_model_predictions %>%
+  mutate(age = ifelse(age<4,"3","4"))%>%
+  group_by(model,speaker,alignment, age)%>%
+  summarise(Model = mean(mean),
+            Model_ci_lower =hdi_lower(mean) ,
+            Model_ci_upper = hdi_upper(mean))
+
+child_cor_plot <- child_cor_model %>%
+  ungroup()%>%
+  mutate(Data = rep(child_cor_data$Data,3),
+         Data_ci_lower = rep(child_cor_data$Data_ci_lower,3),
+         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,3))
+
+ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
+  coord_fixed()+
+  facet_grid(~model)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few() + 
+  scale_colour_ptol()
+```

### 2019-03-08 stats/kids/kids_model_predictions.Rmd
advance model description for paper

@@
 ```{r}
-params_by_age<- readRDS("../saves/params_by_age.rds")
+params_by_age<- readRDS("../saves/child_model_param.rds")
 
@@
          same_speaker_pref_slope = model_params$same_speaker_pref_slope,
-         so = plogis(so_int+so_slope*(age_num-min(age_num))),
+         so = so_int+so_slope*(age_num-min(age_num)),
          diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
@@
 
-  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var noise_int = uniformDrift({a: -2, b: 2, width: 0.4})
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
 
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 8000, burn = 2000, verbose = T)
 )
@@
 
+plot.posterior.noise <- posterior.noise%>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value))%>%
+  spread(Parameter,mean)
+
+x <- data_frame(
+  age = rep(seq(0,2, by = 0.05),1),
+  `int/slope` = c(rep(paste(round(plot.posterior.noise$noise_int,2),round(plot.posterior.noise$noise_slope,2), sep = "/"),41)),
+  int = c(rep(plot.posterior.noise$noise_int,41)),
+  slope = c(rep(plot.posterior.noise$noise_slope,41))
+) %>%
+  mutate(y = plogis(int + slope *age))
+
+ggplot(x, aes(x = age, y= y,col = `int/slope`))+
+  geom_line()+
+  ylim(0,1)
+
 ```
@@
   geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
+  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 1, se = T,  alpha = .5, size = .4)+
   #geom_hline(yintercept = 0.5, lty=2)+

### 2019-03-09 papers/full_paper/models.Rmd
clean version models with non parametric model predictions for kids

@@
 
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
 var output = map(function(row){
 
-    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
-
     var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
 
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
 
@@
 
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_pragm_model<- webppl(
-#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
-#   data =list(ex3data = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model.rds")
-
-child_ex3_pragm_model <- readRDS("../../stats/saves/child_ex3_pragm_model.rds")
-
-child_ex3_pragm_model_predictions <- child_ex3_pragm_model%>%
-  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
-  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic")%>%
-  group_by(model,age,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-child_ex3_pragm_model_noise <- child_ex3_pragm_model %>%
-  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
-  group_by(Parameter)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
+output
+
+'
+```
+
+```{r}
+child_ex3_pragm_model<- webppl(
+  program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
+  data =list(ex3data = ex3_model_data),
+  data_var = "dataFromR"
+)
+
+# model predictions
+child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
+  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="pragmatic",
+         age = as.numeric(age))%>%
+  select(-`1`)
 ```
@@
 
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
   var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
 
@@
 
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
 
@@
 
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_prior_only_model<- webppl(
-#   program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
-#   data =list(ex3data = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model.rds")
-
-child_ex3_prior_only_model <- readRDS("../../stats/saves/child_ex3_prior_only_model.rds")
-
-child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model%>%
-  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
-  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only")%>%
-  group_by(model,age,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-child_ex3_prior_only_model_noise <- child_ex3_prior_only_model %>%
-  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
-  group_by(Parameter)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
+ output
+
+'
+```
+
+```{r}
+child_ex3_prior_only_model<- webppl(
+  program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
+  data =list(ex3data = ex3_model_data),
+  data_var = "dataFromR"
+)
+
+# model predictions
+child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
+  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="prior_only",
+         age = as.numeric(age))%>%
+  select(-`1`)
 
@@
 
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
   var output = map(function(row){
 
-    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))
-
     var prior = [.5, .5, .5]
@@
 
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model<- webppl(
-#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
-#   data =list(ex3data = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model.rds")
-
-child_ex3_flat_prior_model <- readRDS("../../stats/saves/child_ex3_flat_prior_model.rds")
-
-child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model%>%
-  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
-  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior")%>%
-  group_by(model,age,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-child_ex3_flat_prior_model_noise <- child_ex3_flat_prior_model %>%
-  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
-  group_by(Parameter)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-### Plot for noise parameter
-
-```{r visualizing noise parameters}
-plot_noise_param <- data_frame(
-  age = rep(seq(0,2, by = 0.05),3),
-  model = c(
-    rep("pragmatic",41),
-    rep("prior_only",41),
-    rep("flat_prior",41)),
-  int = c(
-    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
-    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
-    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41)
-    ),
-  slope = c(
-    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
-    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
-    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41)
-    )
-) %>%
-  mutate(y = plogis(int + slope *age))
-
-plot_child_noise_param_dev <- ggplot(plot_noise_param, aes(x = age, y= y, col = model))+
-  geom_line(size = 2)+
-  ylim(0,1)+
-  theme_few()+
-  ylab("Noise parameter")+
-  scale_color_manual(name="Model",
-                     breaks=c("pragmatic","flat_prior","prior_only"),
-                     values= c("#859900","#6c71c4","#b58900"))
-
-child_noise_param_by_model <- bind_rows(
-  child_ex3_pragm_model%>%mutate(model="pragmatic"),
-  child_ex3_prior_only_model%>%mutate(model="prior_only"),
-  child_ex3_flat_prior_model%>%mutate(model="flat_prior")
-) %>%
-  filter(Parameter %in% c("noise_int", "noise_slope"))
-
-plot_child_noise_param_by_model <- ggplot(child_noise_param_by_model, aes(x = value, col = model))+
-  geom_density()+
-  facet_grid(model~Parameter, scales = 'free')+
-  theme_few()+
-  scale_color_manual(name="Model",
-                     breaks=c("pragmatic","flat_prior","prior_only"),
-                     values= c("#859900","#6c71c4","#b58900"))
-
-ggarrange(plot_child_noise_param_by_model, plot_child_noise_param_dev, common.legend = T)
+output
+
+'
+```
+
+```{r}
+child_ex3_flat_prior_model<- webppl(
+  program_code = paste(rsaUtils, childRsaModel, child.ex3.flat.prior.predictions , sep='\n'),
+  data =list(ex3data = ex3_model_data),
+  data_var = "dataFromR")
+
+# model predictions
+child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
+  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="flat_prior",
+         age = as.numeric(age))%>%
+  select(-`1`)
+
 ```
@@
   #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
-  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
-  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
   geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
@@
   group_by(model,speaker,alignment, age)%>%
-  summarise(Model = mean(mean),
-            Model_ci_lower =hdi_lower(mean) ,
-            Model_ci_upper = hdi_upper(mean))
+  summarise(Model = mean(value))
 
@@
   geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
-  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
   coord_fixed()+

### 2019-03-09 stats/kids/kids_model_predictions.Rmd
clean version models with non parametric model predictions for kids

@@
   geom_jitter(alpha = 1, height = 0.1, width = 0.1, col = "grey")+
-  geom_smooth(method = "lm", se = T, col = "black",fill = "darkgreen", alpha = .4, size = .4)+
+  geom_smooth(method = "lm", formula = y ~ x + I(x^2), se = T, col = "black",fill = "darkgreen", alpha = .4, size = .4)+
   geom_hline(yintercept = 0.5, lty=2)+
@@
 var model  = function(){
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_slope = uniformDrift({a: -3, b: 3, width: 0.4})
+  var so_slope_quad = uniformDrift({a: -3, b: 3, width: 0.4})
+  var so_int = uniformDrift({a: -3, b: 3, width: 0.4})
+
+  foreach(function(row){
+    var age = row.age_num
+    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage) + so_slope_quad * Math.pow((age - infData[0].minage),2)
+
+    var inf_priorProbs = [.5, .5, .5] 
+    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+    inf_priorProbs, speakerOptimality)
+
+    observe(rsaPredictions, row.correct)
+  }, infData)
+
+  var pref_params = map(function(cndtn){
+    var conditionData = _.filter(prefData, {condition: cndtn})
+
+    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
+    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
+
+    foreach(function(row){
+      var age = row.age_num
+      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
+      var priorProbs= [1-priorReg, priorReg]
+
+      var priorPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+      }})
+
+      observe(priorPredictions, row.correct)
+    }, conditionData)
+
+    return [
+      {condition: cndtn, param: "pref_int", val: pref_int}, 
+      {condition: cndtn, param: "pref_slope", val: pref_slope}
+    ]
+
+  }, all_conditions)
+
+  return _.flatten(pref_params).concat(
+    [
+      {condition: "NA", param: "so_slope", val: so_slope},
+      {condition: "NA", param: "so_slope_quad", val: so_slope_quad},
+      {condition: "NA", param: "so_int", val: so_int}
+    ]
+  )
+}
+'
+```
+
+```{r}
+linParamModelWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
+var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
+
+// make finer grained as needed
+
+var binned_age_range = _.range(0, 2, 0.05)
+var all_conditions = levels(prefData, "condition")
+var foreach = function(fn, lst) {
+    var foreach_ = function(i) {
+        if (i < lst.length) {
+            fn(lst[i]);
+            foreach_(i + 1);
+        }
+    };
+    foreach_(0);
+};
+
+var logistic = function(x) {1 / (1 + Math.exp(-x))}
+
+var model  = function(){
+  var so_slope = uniformDrift({a: -3, b: 3, width: 0.4})
+  var so_slope_quad = uniformDrift({a: -3, b: 3, width: 0.4})
+  var so_int = uniformDrift({a: -3, b: 3, width: 0.4})
+
   foreach(function(row){
@@
 ```{r}
-params_by_age<- readRDS("../saves/child_model_param.rds")
-
 params_by_age<- webppl(
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
+  inference_opts = list(method = "MCMC", samples =2000, burn = 1000, verbose = T)
 )
@@
 
+so_plot <- child_ex1_data %>%
+  group_by(id,age_num,minage)%>%
+  summarise(correct = mean(correct))%>%
+  mutate(model = model_params$NA_so_int + model_params$NA_so_slope * (age_num - minage) + model_params$NA_so_slope_quad * (age_num - minage)^2)
+
+ggplot(data = so_plot, aes(x = age_num, y = model)) +
+  geom_line(alpha = .5, size = .7)+
+  labs(x="Age",y="Speaker optimality parameter")+
+  theme_few() +
+  geom_hline(yintercept = 0, lty=2)+
+  ylim(-3,3)+
+  guides(alpha = F)
+
+# linear parameters
+
+lin_params_by_age<- webppl(
+  program_code = paste(rsaUtils, rsaModel, linParamModelWebppl , sep='\n'),
+  data = pre_data,
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples =2000, burn = 1000, verbose = T)
+)
+
+lin_model_params <- lin_params_by_age%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  group_by(condition,param)%>%
+  summarise(param_map = estimate_mode(val))%>%
+  mutate(cond = paste(condition, param, sep = "_"))%>%
+  ungroup()%>%
+  select(cond,param_map)%>%
+  spread(cond,param_map)
+
+lin_so_plot <- child_ex1_data %>%
+  group_by(id,age_num,minage)%>%
+  summarise(correct = mean(correct))%>%
+  mutate(model = lin_model_params$NA_so_int + lin_model_params$NA_so_slope * (age_num - minage))
+
+ggplot(data = lin_so_plot, aes(x = age_num, y = model)) +
+  geom_line(alpha = .5, size = .7)+
+  labs(x="Age",y="Speaker optimality parameter")+
+  theme_few() +
+  geom_hline(yintercept = 0, lty=2)+
+  ylim(-3,3)+
+  guides(alpha = F)
+
+```
+
+```{r}
+plot_model_pred_so <- kids_model_pred_so%>%
+  group_by(age_bin)%>%
+  summarise(mean = mean(speakerOptimality),
+            lci = hdi_lower(speakerOptimality),
+            uci = hdi_upper(speakerOptimality))
+
+pred_so_plot <- ggplot(data = plot_model_pred_so) +
+  geom_line(data = kids_model_pred_so,aes(age_bin, speakerOptimality, group = iteration), col = "grey", alpha = 0.3) +
+  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci), fill = "green", alpha = .2) +
+  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
+  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
+  scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
+  ggtitle("Speaker optimality model")+
+  #facet_wrap(~chain)+
+  theme_few()+
+  coord_fixed(ratio=1/4)
 ```
@@
 ```{r}
-modelPredWebppl <- '
+linModelPredWebppl <- '
 
@@
 
-model_pred<- webppl(
-  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
-  data = list(ex3data = ex3_data_param, modelParams = model_params),
+lin_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, linModelPredWebppl , sep='\n'),
+  data = list(ex3data = ex3_data_param, modelParams = lin_model_params),
   data_var = "dataFromR"
@@
 
-pred <- model_pred %>%
+lin_pred <- lin_model_pred %>%
   gather(condition, mean, -age_bin)%>%
@@
          Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
-         model = "parameter free", 
+         model = "pragmatic_linear", 
          age = age_bin+3)%>%
   select(-age_bin)
+```
+
+```{r}
+linFlatModelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+var age_bins = _.range(0, 2, 0.05)
+var ex3Data = dataFromR.ex3data
+var modelParams = dataFromR.modelParams[0]
+
+   //display(JSON.stringify(modelParams))
+
+var predict_by_age = function(age_bin){
+
+    //display(JSON.stringify(age_bin))
+
+    var speakerOptimality = modelParams.NA_so_int + modelParams.NA_so_slope * age_bin
+
+    var diff_priorReg = logistic(modelParams.different_speaker_pref_int + modelParams.different_speaker_pref_slope * age_bin)
+
+    //display(JSON.stringify(modelParams))
+
+    var diff_priorProbs_congruent = [0.5, 0.5, 0.5]
+
+    var diff_priorProbs_incongruent = [0.5, 0.5, 0.5]
+
+    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
+
+    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))
+
+    var same_priorReg = logistic(modelParams.same_speaker_pref_int + modelParams.same_speaker_pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [0.5, 0.5, 0.5]
+
+    var same_priorProbs_incongruent = [0.5, 0.5, 0.5]
+
+    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
+
+    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
+
+  return extend(
+      {rsaPredictions_diff_cong,
+      rsaPredictions_diff_incong,
+      rsaPredictions_same_cong,
+      rsaPredictions_same_incong,
+      age_bin
+    })
+
+ }
+
+var predictions_by_age = map(predict_by_age, age_bins)
+
+predictions_by_age
+
+'
+```
+
+```{r combined model predictions}
+
+model_pred_flat_lin <- webppl(
+  program_code = paste(rsaUtils, rsaModel, linFlatModelPredWebppl , sep='\n'),
+  data = list(ex3data = ex3_data_param, modelParams = model_params),
+  data_var = "dataFromR"
+)
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+lin_flat_pred <- model_pred_flat %>%
+  gather(condition, mean, -age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
+         model = "flat_prior", 
+         age = age_bin+3)%>%
+  select(-age_bin)
+```
+
+```{r}
+linPriorModelPredWebppl <- '
+
+var levels = function(df, label){
+  return _.uniq(_.map(df, label));
+}
+
+var age_bins = _.range(0, 2, 0.05)
+var ex3Data = dataFromR.ex3data
+var modelParams = dataFromR.modelParams[0]
+
+   //display(JSON.stringify(modelParams))
+
+var predict_by_age = function(age_bin){
+
+    //display(JSON.stringify(age_bin))
+
+    var speakerOptimality = modelParams.NA_so_int + modelParams.NA_so_slope * age_bin
+
+    var diff_priorReg = logistic(modelParams.different_speaker_pref_int + modelParams.different_speaker_pref_slope * age_bin)
+
+    //display(JSON.stringify(modelParams))
+
+    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
+
+    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]
+
+    var rsaPredictions_diff_cong =  Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_congruent}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var rsaPredictions_diff_incong =Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var same_priorReg = logistic(modelParams.same_speaker_pref_int + modelParams.same_speaker_pref_slope * age_bin)
+
+    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
+
+    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
+
+    var rsaPredictions_same_cong = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var rsaPredictions_same_incong = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_incongruent}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+   var predictions_diff_cong  =   Math.exp(rsaPredictions_diff_cong.score(1))
+   var predictions_diff_incong  =   Math.exp(rsaPredictions_diff_incong.score(1))
+   var predictions_same_cong  =   Math.exp(rsaPredictions_same_cong.score(1))
+   var predictions_same_incong  =   Math.exp(rsaPredictions_same_incong.score(1))
+
+  return extend(
+      {predictions_diff_cong,
+      predictions_diff_incong,
+      predictions_same_cong,
+      predictions_same_incong,
+      age_bin
+    })
+
+ }
+
+var predictions_by_age = map(predict_by_age, age_bins)
+
+predictions_by_age
+
+'
+```
+
+```{r combined model predictions}
+
+lin_model_pred_prior<- webppl(
+  program_code = paste(rsaUtils, rsaModel, linPriorModelPredWebppl , sep='\n'),
+  data = list(ex3data = ex3_data_param, modelParams = lin_model_params),
+  data_var = "dataFromR"
+)
+
+#saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")
+
+lin_pred_prior <- lin_model_pred_prior %>%
+  gather(condition, mean, -age_bin)%>%
+  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
+  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
+         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
+         model = "prior_only", 
+         age = age_bin+3)%>%
+  select(-age_bin)
+
 ```
@@
          so_slope = model_params$NA_so_slope,
+         so_slope_quad = model_params$NA_so_slope_quad,
          same_speaker_pref_int = model_params$same_speaker_pref_int,
          same_speaker_pref_slope = model_params$same_speaker_pref_slope,
-         so = so_int+so_slope*(age_num-min(age_num)),
+         so = so_int+so_slope*(age_num-min(age_num))+so_slope_quad*(age_num-min(age_num))^2,
          diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
@@
 models <- bind_rows(
-  pred,
-  noisy_pred,
-  dev_noisy_pred
+  quad_pred,
+  lin_pred,
+  lin_flat_pred,
+  lin_pred_prior
 )
@@
   #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
-  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  #geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
   geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 1, se = T,  alpha = .5, size = .4)+
+  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 2, se = T,  alpha = .5, size = .4)+
   #geom_hline(yintercept = 0.5, lty=2)+
@@
   ungroup()%>%
-  mutate(Data = rep(data$Data,3),
-         Data_ci_lower = rep(data$Data_ci_lower,3),
-         Data_ci_upper  =rep( data$Data_ci_upper,3))
+  mutate(Data = rep(data$Data,4),
+         Data_ci_lower = rep(data$Data_ci_lower,4),
+         Data_ci_upper  =rep( data$Data_ci_upper,4))
 

### 2019-03-10 papers/full_paper/models.Rmd
parameter free model predictions

@@
 
-```{r rsaUtils, include = FALSE}
+```{r rsaUtils}
 rsaUtils <- '
@@
 ## RSA model code
-
-```{r rsaModel}
+```{r rsa model}
 rsaModel <- '
-var pragmaticListener = function(utterance, priorProbs){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior);
-var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-var S1 = speaker(obj, lexiconName, priorProbs);
-observe(S1, utterance)
-return obj.shape == "circle" ? 1 : 0
-}})
-}
-
-var speaker = function(obj, lexiconName, priorProbs){
-Infer({method: "enumerate", model: function(){
-var utterance = utterancePrior(obj, lexiconName);
-var L0 = literalListener(utterance, priorProbs);
- factor(speakerOptimality * L0.score(obj.shape))
-return utterance
-}})
-}
-
-var literalListener = function(utterance, priorProbs){
+var literalListener = cache(function(utterance, priorProbs){
 Infer({method: "enumerate", model: function(){
@@
 }})
+})
+
+var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
+Infer({method: "enumerate", model: function(){
+var utterance = utterancePrior(obj, lexiconName);
+var L0 = literalListener(utterance, priorProbs);
+ factor(speakerOptimality * L0.score(obj.shape))
+return utterance
+}})
+})
+
+var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
+Infer({method: "enumerate", model: function(){
+var lexiconName = sample(LexiconPrior);
+var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
+var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
+observe(S1, utterance)
+return obj.shape == "circle" ? 1 : 0
+}})
+})
+
+var addNoise = function(dist, noiseParam){
+   Infer({model: function(){ 
+      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
+    }
+   })
 }
@@
 
-```{r ex3 data}
+```{r ex3 data adults}
 # load data from experiment 3
@@
 
-```{r}
+```{r ex 1 and 2 data adults}
+# adults exp 1 
+adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
 # load data from prior manipulation experiments to set priors
@@
 
-```{r model setup ex 4, include = FALSE}
-
+#### Inferring speaker optimality parameter and setting priors
+
+```{r model parameter adults}
+speakOptParam <- '
+var data = dataFromR.data
+
+var model  = function(){
+
+  var speakerOptimality = uniformDrift({a: -3, b: 7, width: 0.2})
+
+  foreach(function(row){
+
+  var priorProbs = [.5, .5, .5]
+
+  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
+   priorProbs, speakerOptimality) 
+   observe(rsaPredictions, row.correct)
+
+  }, data)
+
+  return speakerOptimality
+
+  }
+'
+```
+
+```{r inferring speaker optimality parameter adults}
+# adult_model_param<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, speakOptParam , sep='\n'),
+#   data = list(data = adult_ex1_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#   saveRDS("../../stats/saves/adult_model_param.rds")
+
+adult_model_param <- readRDS("../../stats/saves/adult_model_param.rds")%>%
+  select(value) %>%
+  summarise(so_map = estimate_mode(value),
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+```{r visualize speaker optimality parameter adults}
+# visualize speaker optimality parameter
+plot_adult_model_speak_opt <- readRDS("../../stats/saves/adult_model_param.rds")%>%
+  select(value)
+
+ggplot(plot_adult_model_speak_opt, aes(value))+
+  geom_density()+
+  xlab("Speaker optimality")+
+  theme_few()
+```
+
+```{r model setup ex 3 adults, include = FALSE}
 # create datafiles with model parameters
-predPriorEx3 <- data.frame(
+model_params_ex3 <- data.frame(
   common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
   speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
-  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"))
+  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
+  speak_opt = adult_model_param$so_map)
 
@@
 
-predPriorEx3$prior = list(
+model_params_ex3$prior = list(
     c(1-prior_pref_same$prior,1-prior_pref_same$prior,prior_pref_same$prior), 
@@
 
-# data frame to keep track of unique conditions
-allConditionsEx3 <- predPriorEx3 %>%
-  select(-prior)
-
 ```
@@
 
-```{r model rsa noise ex3, include = FALSE}
+```{r model rsa noise ex3 adults, include = FALSE}
 predictions.rsa.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
+
+var allData = dataFromR.data
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.prior,row.speak_opt)
+
+    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
 '
@@
 
-```{r predictions pragmatic model ex 3, include = FALSE}
-
-# ex3_pragm_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_pragm_model.rds")
-
-ex3_pragm_model <- readRDS("../../stats/saves/ex3_pragm_model.rds")
+```{r predictions pragmatic model ex 3 adults, include = FALSE}
+ex3_pragm_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3 , sep='\n'),
+  data =list(data = model_params_ex3),
+  data_var = "dataFromR"
+)
 
 # model predictions
-ex3_pragm_model_pred <- ex3_pragm_model %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic")
-
-## noise parameter
-ex3_pragm_model_noise <- ex3_pragm_model %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
+ex3_pragm_model_predictions <- ex3_pragm_model %>%
+  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="pragmatic")%>%
+  select(-`1`)
 
@@
 
-```{r model prior only ex3 , include = FALSE}
+```{r model prior only ex3 adults, include = FALSE}
 predictions.prior.only.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+var allData = dataFromR.data
+
+var output = map(function(row){
 
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      var obj = sample( Categorical({vs: all_objects, ps: row.prior}));
       return obj.shape == "circle" ? 1 : 0
@@
 
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
+    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
+
 '
@@
 
-```{r predictions prior only model ex3, include = FALSE}
-
-# ex3_prior_only_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_prior_only_model.rds")
-
-ex3_prior_only_model <- readRDS("../../stats/saves/ex3_prior_only_model.rds")
+```{r predictions prior only model ex3 adults, include = FALSE}
+ex3_prior_only_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3 , sep='\n'),
+  data =list(data = model_params_ex3),
+  data_var = "dataFromR"
+)
 
 # model predictions
-ex3_prior_only_model_pred <- ex3_prior_only_model %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only")
-
-## noise parameter
-ex3_prior_only_model_noise <- ex3_prior_only_model %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
+ex3_prior_only_model_predictions <- ex3_prior_only_model %>%
+  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="prior_only")%>%
+  select(-`1`)
 ```
@@
 
-```{r model flat prior ex3, include = FALSE}
+```{r model flat prior ex3 adults, include = FALSE}
 predictions.flat.prior.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
+var allData = dataFromR.data
+
+var prior = [.5, .5, .5]
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.speak_opt)
+
+    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
 '
@@
 
-```{r predictions prior only model ex3, include = FALSE}
-
-# ex3_flat_prior_model <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_flat_prior_model.rds")
-
-ex3_flat_prior_model <- readRDS("../../stats/saves/ex3_flat_prior_model.rds")
+```{r predictions prior only model ex3 adults, include = FALSE}
+ex3_flat_prior_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3 , sep='\n'),
+  data =list(data = model_params_ex3),
+  data_var = "dataFromR"
+)
 
 # model predictions
-ex3_flat_prior_model_pred <- ex3_flat_prior_model %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior")
-
-## noise parameter
-ex3_flat_prior_model_noise <- ex3_flat_prior_model %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
+ex3_flat_prior_model_predictions <- ex3_flat_prior_model %>%
+  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
+  mutate(value = `1`,
+         model="flat_prior")%>%
+  select(-`1`)
 
@@
 ex_3_model_pred <- bind_rows(
-  ex3_pragm_model_pred,
-  ex3_prior_only_model_pred,
-  ex3_flat_prior_model_pred
+  ex3_pragm_model_predictions,
+  ex3_prior_only_model_predictions,
+  ex3_flat_prior_model_predictions
 )%>%
-  group_by(model,common_ground_manipulation,speaker,alignment) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper = hdi_upper(value))
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = mean(value))%>%
+  mutate(ci_lower = mean,
+         ci_upper = mean)
 
@@
 
-```{r plot ex3 model predictions and data}
+```{r plot ex3 model predictions and data adults}
 ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
@@
 
-```{r plot }
+```{r correlation plot ex3 adults}
 
@@
 
-### Model comparison
-
-```{r model likelihood rsa ex3, include = FALSE}
-loglike.rsa.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-}, allConditions)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r model likelihood prior only ex3 , include = FALSE}
-loglike.prior.only.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-}, allConditions)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r model likelihood flat prior ex3, include = FALSE}
-loglike.flat.prior.ex3 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-}, allConditions)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r ex3 model comparison}
-# ex3_pragm_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
-
-ex3_pragm_model_loglike <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")%>%
-  mutate(model = "pragmatic")%>%
+## Model comparison
+
+```{r log likes ex3 adults}
+# calculating model log-likelihoods
+log_like_pragmatic_ex3 <- adult_ex3_data %>%
+  left_join(ex3_pragm_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-# ex3_prior_only_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# )%>%
-#   saveRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")
-
-ex3_prior_only_model_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_loglike.rds")%>%
-  mutate(model = "prior_only")%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_flat_prior_ex3 <- adult_ex3_data %>%
+  left_join(ex3_flat_prior_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-# ex3_flat_prior_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex3, sep='\n'),
-#   data = list(allData = adult_ex3_data, allConditions = allConditionsEx3, predPrior = predPriorEx3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# )%>%
-#   saveRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")
-
-ex3_flat_prior_model_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_loglike.rds")%>%
-  mutate(model = "flat_prior")%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_prior_only_ex3 <- adult_ex3_data %>%
+  left_join(ex3_prior_only_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
+  summarise(model_log_like = sum(log_like))
 
 ex3_model_comparison <- bind_rows(
-  ex3_pragm_model_loglike,
-  ex3_prior_only_model_loglike,
-  ex3_flat_prior_model_loglike
+  log_like_pragmatic_ex3,
+  log_like_flat_prior_ex3,
+  log_like_prior_only_ex3
 )%>%
-  mutate(model = reorder(model,logP))
-
-#saveRDS(ex3_model_comparison, "../../stats/saves/ex3_model_comparison.rds")
-
-```
-##### Plot for likelihoods
-
-```{r}
-ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
+  mutate(model = reorder(model,model_log_like))
+```
+
+### Plot for likelihoods
+
+```{r likelihood plot adults}
+ggplot(ex3_model_comparison, aes(x = model, y = model_log_like, col = model))+
+  geom_segment( aes(x=model, xend=model, y=-600, yend=model_log_like), col = "black", size = 1)+
   geom_point(size = 7)+
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))
-```
-
-##### Bayes factors
-
-```{r}
+                    values= c("#b58900","#859900","#6c71c4"))
+```
+
+### Bayes factors
+
+```{r bayes factors ex3 adults}
 ex3_bf <- data.frame(
-  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
-  bayes_factor = c(
-    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"]),
-    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "pragmatic"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]),
-    exp(ex3_model_comparison$logP[ex3_model_comparison$model== "prior_only"] - ex3_model_comparison$logP[ex3_model_comparison$model== "flat_prior"]))
+  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
+  log_bayes_factor = c(
+    log_like_pragmatic_ex3$model_log_like - log_like_flat_prior_ex3$model_log_like,
+    log_like_pragmatic_ex3$model_log_like- log_like_prior_only_ex3$model_log_like,
+    log_like_flat_prior_ex3$model_log_like - log_like_prior_only_ex3$model_log_like)
 )
@@
 ### Model parameters and data
-```{r ex4 data}
+```{r ex4 data adults}
 # load data  from experiment 4 
@@
 
-```{r}
+```{r prior pre-tests data adults}
 # load data from prior strength manipulation experiments to set priors
@@
 # combining all priors into one data frame
-predPriorEx4 = rbind(strongPrior,mediumPrior,weakPrior)
-
-# data frame to keep track of unique conditions
-allConditionsEx4 <- predPriorEx4 %>%
-  select(-prior)
+model_params_ex4 = rbind(strongPrior,mediumPrior,weakPrior)%>%
+  mutate(speak_opt = adult_model_param$so_map)
 
@@
 
-```{r model rsa noise ex4, include = FALSE}
+```{r model rsa noise ex4 adults, include = FALSE}
 predictions.rsa.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var conditionOutput = map(function(conditionInfo){
-
-    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
-
-  }, allConditions)
-
-   conditionOutput
+
+var allData = dataFromR.data
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.prior,row.speak_opt)
+
+    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
 
@@
 
-```{r predictions pragmatic model, include = FALSE}
-
-ex4_pragm_model <- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
-  data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+```{r predictions pragmatic model ex 4 adults, include = FALSE}
+ex4_pragm_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4 , sep='\n'),
+  data =list(data = model_params_ex4),
   data_var = "dataFromR"
@@
 # model predictions
-ex4_pragm_model_pred <- ex4_pragm_model %>%
-  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+ex4_pragm_model_predictions <- ex4_pragm_model %>%
+  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
   mutate(value = `1`,
-         model="pragmatic",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+         model="pragmatic")%>%
   select(-`1`)
@@
 
-```{r model prior only ex4 , include = FALSE}
+```{r model prior only ex4 adults, include = FALSE}
 predictions.prior.only.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var conditionOutput = map(function(conditionInfo){
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
+
+var allData = dataFromR.data
+
+var output = map(function(row){
 
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
+      var obj = sample( Categorical({vs: all_objects, ps: row.prior}));
       return obj.shape == "circle" ? 1 : 0
@@
 
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
-
-}, allConditions)
-
-conditionOutput
+    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
 
@@
 
-```{r predictions prior only model ex 4, include = FALSE}
-
-ex4_prior_only_model <- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
-  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_prior_only_model_noise$mean),
+```{r predictions prior only model ex4 adults, include = FALSE}
+ex4_prior_only_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4 , sep='\n'),
+  data =list(data = model_params_ex4),
   data_var = "dataFromR"
@@
 # model predictions
-ex4_prior_only_model_pred <- ex4_prior_only_model %>%
-  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+ex4_prior_only_model_predictions <- ex4_prior_only_model %>%
+  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
   mutate(value = `1`,
-         model="prior_only",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+         model="prior_only")%>%
   select(-`1`)
-
 ```
@@
 
-```{r model flat prior ex4, include = FALSE}
+```{r model flat prior ex4 adults, include = FALSE}
 predictions.flat.prior.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var conditionOutput = map(function(conditionInfo){
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-  return  extend([conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))])
-
-}, allConditions)
-
-conditionOutput
-
+var allData = dataFromR.data
+
+var prior = [.5, .5, .5]
+
+var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.speak_opt)
+
+    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+
+}, allData)
+
+output
 '
@@
 
-```{r predictions flat prior model ex 4, include = FALSE}
-
-ex4_flat_prior_model <- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
-  data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior, noise = ex3_flat_prior_model_noise$mean),
+```{r predictions prior only model ex4 adults, include = FALSE}
+ex4_flat_prior_model<- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4 , sep='\n'),
+  data =list(data = model_params_ex4),
   data_var = "dataFromR"
@@
 # model predictions
-ex4_flat_prior_model_pred <- ex4_flat_prior_model %>%
-separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
+ex4_flat_prior_model_predictions <- ex4_flat_prior_model %>%
+  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
   mutate(value = `1`,
-         model="flat_prior",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+         model="flat_prior")%>%
   select(-`1`)
-```
-
-```{r}
+
+```
+
+```{r join model predictions and data ex4 adults}
 # combine model predictions with data
@@
 ex_4_model_pred <- bind_rows(
-  ex4_pragm_model_pred,
-  ex4_prior_only_model_pred,
-  ex4_flat_prior_model_pred
-) %>%
+  ex4_pragm_model_predictions,
+  ex4_prior_only_model_predictions,
+  ex4_flat_prior_model_predictions
+)%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
   group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  rename(mean = value)%>%
-  summarise(mean = mean,
-            ci_lower = mean,
-            ci_upper= mean)
+  summarise(mean = mean(value))%>%
+  mutate(ci_lower = mean,
+         ci_upper = mean)
 
@@
 
-```{r plot ex4 model predictions and data}
+```{r plot ex4 model predictions and data adults}
 ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
@@
 
-```{r plot }
-## correlation round 1
+```{r correlation plot ex4 adults}
 
@@
 
-### Model comparison
-
-```{r model likelihood rsa ex4, include = FALSE}
-loglike.rsa.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var model = function(){
-
-var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-    var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-  }, allConditions)
-
-  return sum(conditionOutput)
-
-}
-'
-```
-
-```{r model likelihood prior only ex4 , include = FALSE}
-loglike.prior.only.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var model = function(){
-
-var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-  }, allConditions)
-
-  return sum(conditionOutput)
-}
-'
-```
-
-```{r model likelihood flat prior ex4, include = FALSE}
-loglike.flat.prior.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-var noise = dataFromR.noise[0]
-
-var model = function(){
-
-var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-
-  return  loglike
-
-  }, allConditions)
-
-  return sum(conditionOutput)
-}
-'
-```
-
-```{r ex 4 model comparison}
-# ex4_pragm_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_pragm_model_loglike.rds")
-
-ex4_pragm_model_loglike <- readRDS("../../stats/saves/ex4_pragm_model_loglike.rds")%>%
-  mutate(model = "pragmatic")%>%
+## Model comparison
+
+```{r loglikes ex4 adults}
+# calculating model log-likelihoods
+log_like_pragmatic_ex4 <- adult_ex4_data %>%
+  left_join(ex4_pragm_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-# ex4_prior_only_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")
-
-ex4_prior_only_model_loglike <- readRDS("../../stats/saves/ex4_prior_only_model_loglike.rds")%>%
-  mutate(model = "prior_only")%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_flat_prior_ex4 <- adult_ex4_data %>%
+  left_join(ex4_flat_prior_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-# ex4_flat_prior_model_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4, 
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")
-
-ex4_flat_prior_model_loglike <- readRDS("../../stats/saves/ex4_flat_prior_model_loglike.rds")%>%
-  mutate(model = "flat_prior")%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_prior_only_ex4 <- adult_ex4_data %>%
+  left_join(ex4_prior_only_model_predictions)%>%
+  mutate(like = ifelse(correct_inf == "1",value,1-value),
+         log_like = log(like))%>%
   group_by(model)%>%
-  summarize(logP = logSumExp(value))
+  summarise(model_log_like = sum(log_like))
 
 ex4_model_comparison <- bind_rows(
-  ex4_pragm_model_loglike,
-  ex4_prior_only_model_loglike,
-  ex4_flat_prior_model_loglike
+  log_like_pragmatic_ex4,
+  log_like_flat_prior_ex4,
+  log_like_prior_only_ex4
 )%>%
-  mutate(model = reorder(model,logP))
-
-#saveRDS(ex4_model_comparison, "../../stats/saves/ex4_model_comparison.rds")
-```
-
-##### Plot for likelihoods
-
-```{r}
-ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=0, yend=logP), col = "black", size = 1)+
+  mutate(model = reorder(model,model_log_like))
+```
+
+### Plot for likelihoods
+
+```{r plot for loglikelihood ex4 adults}
+ggplot(ex4_model_comparison, aes(x = model, y = model_log_like, col = model))+
+  geom_segment( aes(x=model, xend=model, y=-1500, yend=model_log_like), col = "black", size = 1)+
   geom_point(size = 7)+
@@
 
-##### Bayes factors
-
-```{r}
+### Bayes factors
+
+```{r bayes factors ex4 adults}
 ex4_bf <- data.frame(
-  comparison = c("pragmatic vs. prior_only","pragmatic vs. flat_prior", "flat_rior vs. prior_only"),
-  bayes_factor = c(
-    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]),
-    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "pragmatic"] - ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"]),
-    exp(ex4_model_comparison$logP[ex4_model_comparison$model== "flat_prior"] - ex4_model_comparison$logP[ex4_model_comparison$model== "prior_only"]))
+  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
+  log_bayes_factor = c(
+    log_like_pragmatic_ex4$model_log_like - log_like_flat_prior_ex4$model_log_like,
+    log_like_pragmatic_ex4$model_log_like- log_like_prior_only_ex4$model_log_like,
+    log_like_flat_prior_ex4$model_log_like - log_like_prior_only_ex4$model_log_like)
 )
@@
 ```
-#### Appendix: Model predictions with inferred noise
-
-```{r model rsa noise ex4, include = FALSE}
-predictions.rsa.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].prior)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
-'
-```
-
-```{r predictions pragmatic model ex 4 inf noise, include = FALSE}
-
-# ex4_pragm_model_inf_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")
-
-ex4_pragm_model_inf_noise <- readRDS("../../stats/saves/ex4_pragm_model_inf_noise.rds")
-
-# model predictions
-ex4_pragm_model_pred_inf_noise <- ex4_pragm_model_inf_noise %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
-  mutate(model="pragmatic",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))
-
-## noise parameter
-ex4_pragm_model_noise_inf_noise <- ex4_pragm_model_inf_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-```{r model prior only ex4 , include = FALSE}
-predictions.prior.only.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var conditionSpecificPriors =  _.filter(allPriorProbs, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].prior}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
-'
-```
-
-```{r predictions prior only model ex 4 inf noise, include = FALSE}
-
-# ex4_prior_only_model_inf_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")
-
-ex4_prior_only_model_inf_noise <- readRDS("../../stats/saves/ex4_prior_only_model_inf_noise.rds")
-
-# model predictions
-ex4_prior_only_model_pred_inf_noise <- ex4_prior_only_model_inf_noise %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
-  mutate(model="prior_only",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))
-
-## noise parameter
-ex4_prior_only_model_noise_inf_noise <- ex4_prior_only_model_inf_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-```{r model flat prior ex4, include = FALSE}
-predictions.flat.prior.ex4 <-'
-var allConditions = dataFromR.allConditions
-var allData = dataFromR.allData
-var allPriorProbs = dataFromR.predPrior
-
-var model = function(){
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment, prior_manipulation : conditionInfo.prior_manipulation})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors)
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-   map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment+ "/" + conditionInfo.prior_manipulation, Math.exp(noisyModelPredictions.score(1))]
-
-}, allConditions)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-
-}
-'
-```
-
-```{r predictions flat prior model ex 4 inf noise, include = FALSE}
-
-# ex4_flat_prior_model_inf_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4, sep='\n'),
-#   data = list(allData = adult_ex4_data, allConditions = allConditions, predPrior = predPrior),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")
-
-ex4_flat_prior_model_inf_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_inf_noise.rds")
-
-# model predictions
-ex4_flat_prior_model_pred_inf_noise <- ex4_flat_prior_model_inf_noise %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation", "speaker", "alignment", "prior_manipulation"), sep="/")%>%
-  mutate(model="flat_prior",
-         prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))
-
-## noise parameter
-ex4_flat_prior_model_noise_inf_noise <- ex4_flat_prior_model_inf_noise %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
 # Children
 
-## RSA model code
-```{r rsa model}
-
-childRsaModel <- '
-var literalListener = cache(function(utterance, priorProbs){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior); 
-var lexicon = lexiconObject[lexiconName];
-var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-if ("label" in utterance) {
- var truthValue = lexicon(utterance, obj);
- condition(truthValue)
-}
-if (utterance.point) {
- var truthValuePoint = point(utterance, obj);
- condition(truthValuePoint)
-}
-return obj.shape 
-}})
-})
-
-var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
-Infer({method: "enumerate", model: function(){
-var utterance = utterancePrior(obj, lexiconName);
-var L0 = literalListener(utterance, priorProbs);
- factor(speakerOptimality * L0.score(obj.shape))
-return utterance
-}})
-})
-
-var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
-Infer({method: "enumerate", model: function(){
-var lexiconName = sample(LexiconPrior);
-var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
-observe(S1, utterance)
-return obj.shape == "circle" ? 1 : 0
-}})
-})
-
-var addNoise = function(dist, noiseParam){
-   Infer({model: function(){ 
-      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
-    }
-   })
-}
-'
-```
-
 ## Model parameters and data
 
-```{r ex3 data}
+```{r ex3 data children}
 # children ex3 data
@@
 
-```{r}
+```{r ex1 and ex2 data children}
 # load data from ex1 manipulation experiments to set speaker optimality parameter
@@
 
-```{r}
+#### Inferring speaker optimality parameter and priors
+
+```{r model parameters children}
 childModelParam <- '
@@
 
-  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
+  var so_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var so_int = uniformDrift({a: -3, b: 7, width: 0.2})
 
@@
 
-```{r}
+```{r inferring model parameters children}
 # child_model_param<- webppl(
-#   program_code = paste(rsaUtils, childRsaModel, childModelParam , sep='\n'),
+#   program_code = paste(rsaUtils, rsaModel, childModelParam , sep='\n'),
 #   data = list(prefData = child_ex2_data, infData = child_ex1_data),
@@
 #   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
+#   inference_opts = list(method = "MCMC", samples = 7000, burn = 1000, verbose = T)
 # )%>%
@@
 
-```{r}
+```{r visualize model parameters children}
+# visualize inferred parameter
+plot_child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
+  select(value)%>%
+  map_df(bind_rows)%>%
+  mutate(type = ifelse(grepl("pref",param),"prior", "speaker optimality"))
+
+ggplot(plot_child_model_param, aes(val))+
+  geom_density()+
+  xlab("Parameter")+
+  facet_grid(type~param+condition)+
+  theme_few()
+```
+
+```{r visualize prior children}
 # visualize model priors in comparison to data 
@@
 
-```{r}
+```{r visualize speaker optimality children}
 # visualize speaker optimality in comparison to data 
@@
 
-```{r}
+```{r model setup ex3 children}
 ex3_model_data <- child_ex3_data%>%
@@
 
-```{r}
+```{r pragmatic model ex3 children}
 child.ex3.rsa.predictions <-'
@@
 
-    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
+    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
 
@@
 
-```{r}
+```{r predictions pragmatic model ex3 children}
 child_ex3_pragm_model<- webppl(
-  program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
   data =list(ex3data = ex3_model_data),
@@
 child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
   mutate(value = `1`,
@@
 
-```{r}
+```{r prior only model ex3 children}
 child.ex3.prior.only.predictions <-'
@@
 
-    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
+    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment+ "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
 
@@
 
-```{r}
+```{r predictions prior only model ex3 children}
 child_ex3_prior_only_model<- webppl(
-  program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions , sep='\n'),
   data =list(ex3data = ex3_model_data),
@@
 child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
   mutate(value = `1`,
@@
 
-```{r}
+```{r flat prior model ex3 children}
 child.ex3.flat.prior.predictions <-'
@@
 
-    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
+    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
 
@@
 
-```{r}
+```{r predictions flat prior model ex3 children}
 child_ex3_flat_prior_model<- webppl(
-  program_code = paste(rsaUtils, childRsaModel, child.ex3.flat.prior.predictions , sep='\n'),
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions , sep='\n'),
   data =list(ex3data = ex3_model_data),
@@
 child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
+  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
   mutate(value = `1`,
@@
 
-```{r}
+```{r plot model predictions ex3 children}
 child_model_predictions <- bind_rows(
@@
   geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
+  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .5)+
   #geom_hline(yintercept = 0.5, lty=2)+
@@
 
-```{r}
+```{r correlation plot ex3 children}
 child_cor_data <- child_ex3_data %>%
@@
 ```
+
+## Model comparison
+
+```{r model loglike ex3 children}
+# calculating model log-likelihoods
+
+log_like_pragmatic <- child_ex3_pragm_model_predictions %>%
+  mutate(like = ifelse(correct == "1",value,1-value),
+         log_like = log(like))%>%
+  group_by(model)%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_flat_prior <- child_ex3_flat_prior_model_predictions %>%
+  mutate(like = ifelse(correct == "1",value,1-value),
+         log_like = log(like))%>%
+  group_by(model)%>%
+  summarise(model_log_like = sum(log_like))
+
+log_like_prior_only <- child_ex3_prior_only_model_predictions %>%
+  mutate(like = ifelse(correct == "1",value,1-value),
+         log_like = log(like))%>%
+  group_by(model)%>%
+  summarise(model_log_like = sum(log_like))
+
+child_ex3_model_comparison <- bind_rows(
+  log_like_pragmatic,
+  log_like_flat_prior,
+  log_like_prior_only
+)%>%
+  mutate(model = reorder(model,model_log_like))
+```
+
+### Plot for likelihoods
+
+```{r plot model loglikes ex3 children}
+ggplot(child_ex3_model_comparison, aes(x = model, y = model_log_like, col = model))+
+  geom_segment( aes(x=model, xend=model, y=-425, yend=model_log_like), col = "black", size = 1)+
+  geom_point(size = 7)+
+  theme_few()+ 
+  xlab("Model")+
+  ylab("Log-likelihood")+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
+  guides(col = F)+
+  ylim(-550,-425)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#859900","#6c71c4"))
+```
+
+### Bayes factors
+
+```{r bayes factors ex3 children}
+child_ex3_bf <- data.frame(
+  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
+  log_bayes_factor = c(
+    log_like_pragmatic$model_log_like - log_like_flat_prior$model_log_like,
+    log_like_pragmatic$model_log_like- log_like_prior_only$model_log_like,
+    log_like_flat_prior$model_log_like - log_like_prior_only$model_log_like)
+)
+
+child_ex3_bf%>%
+  kable(digits = 2)
+```
+
+# Appendix 1: Fully Bayesian analysis

### 2019-03-11 papers/full_paper/models.Rmd
update model description

@@
 ```{r model parameter adults}
+
+# The prior on the speaker optimality parameter is largely positive but also contains negative values so that it could, in theory, result in a parameter that leads to model predictions below chance.
+The same prior is used for the intercept on children's parameters, where performance was below chance.
 speakOptParam <- '
@@
 ```{r model parameters children}
+# In theory, we would expect the speaker optimality parameter to always be positive.
+The prior for the intercept should therefore not include neagtive values.
+However, in the context of our study, the youngest children performed below chance and increased with age.
+This pattern can only be captured by the model if we allow the intercept to take negative values.
+To combine these considerations, the prior for the intercept is skewed towards being positive, but also includes negative values.
+The prior on the slope is agnostic about the shape of the developmental trajectory.
 childModelParam <- '
@@
   scale_fill_solarized(name = "Condition")
+
+# dashed line represents the developmental trajectories based on the estimated parameters 
 ```
@@
 
-ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
-  geom_line(alpha = .5, size = .7)+
+plot_child_so <- ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
+  geom_hline(yintercept = 0, lty=2)+
+  geom_line( size = 2)+
   labs(x="Age",y="Speaker optimality parameter")+
   theme_few() +
-  geom_hline(yintercept = 0, lty=2)+
+  ggtitle("Speaker optimality parameter")+
   ylim(-3,3)+
   guides(alpha = F)
+
+plot_ex1_child <-child_ex1_data %>%
+  group_by(age_num, id) %>%
+  summarise(correct = mean(correct))%>%
+  ggplot(data = ., aes(x = age_num, y = correct)) +
+  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
+  geom_smooth(method = "lm", se = T, alpha = .5, size = .7)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="Age",y="Proportion Correct")+
+  ggtitle("Data ex1 children")+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)
+
+ggarrange(plot_child_so,plot_ex1_child)
 ```

### 2019-03-11 papers/full_paper/models.Rmd
update model param priors

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
 
@@
 ```{r model parameter adults}
-
-# The prior on the speaker optimality parameter is largely positive but also contains negative values so that it could, in theory, result in a parameter that leads to model predictions below chance.
-The same prior is used for the intercept on children's parameters, where performance was below chance.
+# Cauchy prior on the speaker optimality parameter around 1, based on previous work (e.g. Frank & Goodman, 2014) 
 speakOptParam <- '
@@
 
-  var speakerOptimality = uniformDrift({a: -3, b: 7, width: 0.2})
+  var speakerOptimality = sample(Cauchy({location: 1, scale: 2}))
 
@@
 
-```{r model setup ex 3 adults, include = FALSE}
+```{r model setup ex 3 adults}
 # create datafiles with model parameters
@@
 
-```{r model rsa noise ex3 adults, include = FALSE}
+```{r model rsa noise ex3 adults}
 predictions.rsa.ex3 <-'
@@
 
-```{r predictions pragmatic model ex 3 adults, include = FALSE}
+```{r predictions pragmatic model ex 3 adults}
 ex3_pragm_model<- webppl(
@@
 
-```{r model prior only ex3 adults, include = FALSE}
+```{r model prior only ex3 adults}
 predictions.prior.only.ex3 <-'
@@
 
-```{r predictions prior only model ex3 adults, include = FALSE}
+```{r predictions prior only model ex3 adults}
 ex3_prior_only_model<- webppl(
@@
 
-```{r model flat prior ex3 adults, include = FALSE}
+```{r model flat prior ex3 adults}
 predictions.flat.prior.ex3 <-'
@@
 
-```{r predictions prior only model ex3 adults, include = FALSE}
+```{r predictions flat prior model ex3 adults}
 ex3_flat_prior_model<- webppl(
@@
 
-```{r model setup ex 4, include = FALSE}
+```{r model setup ex 4}
 
@@
 
-```{r model rsa noise ex4 adults, include = FALSE}
+```{r model rsa noise ex4 adults}
 predictions.rsa.ex4 <-'
@@
 
-```{r predictions pragmatic model ex 4 adults, include = FALSE}
+```{r predictions pragmatic model ex 4 adults}
 ex4_pragm_model<- webppl(
@@
 
-```{r model prior only ex4 adults, include = FALSE}
+```{r model prior only ex4 adults}
 predictions.prior.only.ex4 <-'
@@
 
-```{r predictions prior only model ex4 adults, include = FALSE}
+```{r predictions prior only model ex4 adults}
 ex4_prior_only_model<- webppl(
@@
 
-```{r model flat prior ex4 adults, include = FALSE}
+```{r model flat prior ex4 adults}
 predictions.flat.prior.ex4 <-'
@@
 
-```{r predictions prior only model ex4 adults, include = FALSE}
+```{r predictions flat prior model ex4 adults}
 ex4_flat_prior_model<- webppl(
@@
 ```{r model parameters children}
-# In theory, we would expect the speaker optimality parameter to always be positive.
-The prior for the intercept should therefore not include neagtive values.
-However, in the context of our study, the youngest children performed below chance and increased with age.
-This pattern can only be captured by the model if we allow the intercept to take negative values.
-To combine these considerations, the prior for the intercept is skewed towards being positive, but also includes negative values.
-The prior on the slope is agnostic about the shape of the developmental trajectory.
+# The prior on the speaker optimality intercept is the same as for the adult speaker optimality parameter.
+
 childModelParam <- '
@@
 
-  var so_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var so_int = uniformDrift({a: -3, b: 7, width: 0.2})
+  var so_slope = sample(Cauchy({location: 0, scale: 2}))
+  var so_int = sample(Cauchy({location: 1, scale: 2}))
 
@@
 #   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 7000, burn = 1000, verbose = T)
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
 # )%>%

### 2019-03-11 papers/full_paper/methods.Rmd
clean up saves

@@
 
-# model predictions adults ex3
-ex3_model_predictions <- readRDS("../../stats/saves/ex3_model_predictions.rds")
-# model comparison adults ex3
-ex3_model_comparison <- readRDS("../../stats/saves/ex3_model_comparison.rds")
-# model predictions adults ex4
-ex4_model_predictions <- readRDS("../../stats/saves/ex4_model_predictions.rds")
-# model comparison adults ex4
-ex4_model_comparison <- readRDS("../../stats/saves/ex4_model_comparison.rds")
 ```
@@
 # Adults
-## Experiment 1
+
+## Seperate assessment of general and speaker specific expectations (Exp. 1 and 2).
 
 ```{r, figure 1}
-
 p_fig1 <- bind_rows(adult_ex1_data,
@@
   labs(x="",y="Proportion Correct")+
-  facet_wrap( ~ experiment, labeller = as_labeller(c(`adult_ex2_preference`="Exp. 2 - Pref.", `adult_ex2_novelty`="Exp. 2 - Nov.", `adult_ex1`="Exp. 1")))+
+  facet_wrap( ~ experiment, labeller = as_labeller(c(`adult_ex2_preference`="Exp. 2 - Pref.", `adult_ex2_novelty`="Exp. 2 - Nov.", `adult_ex1`="Exp. 1 - Info.")))+
   theme_few() + 
@@
 
+## Model predictions for information integration evaluated against new data (Exp 3).
+
+```{r figure adults}
+
+adult_ex3_plot_data <- adult_ex3_data%>%
+  group_by(common_ground_manipulation,speaker,alignment,id)%>%
+  summarise(mean = mean(correct_inf))%>%
+  mutate(model = "data")
+
+adult_ex3_pred <- readRDS( "../../stats/saves/adult_ex3_model_predictions_data.rds")%>%
+  filter(model != "flat_prior",
+         model != "prior_only")%>%
+  mutate(prior_manipulation = "strong",
+        experiment = "experiment 3")
+
+adult_ex4_pred <- readRDS( "../../stats/saves/adult_ex4_model_predictions_data.rds")%>%
+  filter(model != "flat_prior",
+         model != "prior_only")%>%
+  mutate(experiment = "experiment 4")
+
+ggplot(data = adult_ex3_pred, aes(x = alignment, y = mean, col = model)) +
+  geom_jitter(data = adult_ex3_plot_data, alpha = .1, height = 0.02)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .6,  position = position_dodge(width = .5), pch = 5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Choosing more informative")+
+  facet_grid (~ common_ground_manipulation + speaker) +
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_manual(name="Model",
+                     breaks=c("data","pragmatic","flat_prior","prior_only"),
+                     values= c("black","#859900","#6c71c4","#b58900"))+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+
+```
+
+## Replication and extension to varying levels of prior manipulation (Exp 4).
+
+```{r}
+
+adult_ex3_cor_plot <- adult_ex3_pred %>%
+  ungroup()%>%
+  filter(model != "data") %>%
+  mutate(data_mean = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(mean),1),
+         data_ci_lower = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(ci_lower),1),
+         data_ci_upper = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(ci_upper),1))
+
+adult_ex4_cor_plot <- adult_ex4_pred %>%
+  ungroup()%>%
+  filter(model != "data") %>%
+  mutate(data_mean = rep(adult_ex4_pred%>%filter(model == "data")%>%pull(mean),1),
+         data_ci_lower = rep(adult_ex4_pred%>%filter(model == "data")%>%pull(ci_lower),1),
+         data_ci_upper = rep(adult_ex4_pred%>%filter(model == "data")%>%pull(ci_upper),1))
+
+adult_rep_cor_plot <- adult_ex4_pred %>%
+  ungroup()%>%
+  filter(model == "data",
+         prior_manipulation == "strong") %>%
+  mutate(data_mean = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(mean),1),
+         data_ci_lower = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(ci_lower),1),
+         data_ci_upper = rep(adult_ex3_pred%>%filter(model == "data")%>%pull(ci_upper),1),
+         experiment = "replication")
+
+adult_pred <- bind_rows(adult_ex3_cor_plot,
+                        adult_ex4_cor_plot,
+                        adult_rep_cor_plot)%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"),
+         experiment = factor(experiment,levels = c("experiment 3", "replication", "experiment 4")))
+
+ggplot(data = adult_pred,aes(x = mean, y = data_mean, col = prior_manipulation)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("")+
+  ylab("")+
+  facet_grid ( ~ experiment) +
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
+  theme_few() + 
+  scale_colour_ptol(name = "Prior manipulation")
+
+```
+
+# Children
+
+## Seperate assessment of general and speaker specific expectations.
+
+## Model predictions for information integration evaluated against new data.
+
 ```{r, figure x}
 
-p_figx <- bind_rows(child_ex1_data%>%
+plot_child_ex12 <- bind_rows(child_ex1_data%>%
                       mutate(condition = "test"),
@@
 
-ggplot(data = p_figx, aes(x = age_num, y = correct, col = condition)) +
-  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
+ggplot(data = plot_child_ex12, aes(x = age_num, y = correct, col = condition)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(alpha = 0.2, height = 0.02, width = 0)+
   geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
-  geom_hline(yintercept = 0.5, lty=2)+
   labs(x="Age",y="Proportion Correct")+
-  facet_wrap( ~ experiment, labeller = as_labeller(c(`child_ex2`="Exp. 2", `child_ex1`="Exp. 1")))+
+  facet_wrap( ~ experiment, labeller = as_labeller(c(`child_ex2`="Exp. 2 - Pref.", `child_ex1`="Exp. 1 - Info.")))+
   theme_few() +
@@
 ```
-```{r, fig.height=3, fig.width=8}
-#ggarrange(fig1_a, fig1_c, ncol = 2, nrow = 1, common.legend = F, legend = "bottom", widths = c(1,1.2))
+
+```{r}
+child_model_predictions <- readRDS(  "../../stats/saves/child_ex3_model_predictions.rds")%>%
+  filter(model != "flat_prior",
+         model != "prior_only")
+
+plot_child_ex3_data <- child_ex3_data%>%
+  group_by(age_num,speaker,alignment)%>%
+  summarise(mean = mean(correct_inf))
+
+ggplot(child_model_predictions)+
+  geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .01,height = .01, alpha = .2)+
+  geom_line(aes(x = age, y = value, col = model), size = 1.2, alpha = 1, linetype = 1) + 
+  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .4)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="Age",y="Proportion more informative")+
+  ylim(-0.05,1.05)+
+  facet_grid(~speaker+ alignment)+
+  coord_fixed(ratio = 1.5)+
+  theme_few()+
+  scale_color_manual(name=NULL,
+                     breaks=c("pragmatic"),
+                     labels = c("Model predictions"),
+                     values= c("#859900"))
+  # + theme(
+  #   legend.position = c(.23, .45),
+  #   legend.justification = c("right", "top"),
+  #   legend.background = element_blank()
+  #   )
+
 ```
+
+```{r}
+child_cor_model <- child_model_predictions %>%
+  mutate(age = ifelse(age<4,"3","4"))%>%
+  group_by(model,speaker,alignment, age)%>%
+  summarise(Model = mean(value))
+
+child_cor_plot <- child_cor_model %>%
+  ungroup()%>%
+  mutate(Data = rep(child_cor_data$Data,1),
+         Data_ci_lower = rep(child_cor_data$Data_ci_lower,1),
+         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,1))
+
+ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  coord_fixed()+
+  #facet_grid(~model)+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  theme_few() + 
+  scale_colour_ptol()
+
+```

### 2019-03-11 papers/full_paper/models.Rmd
clean up saves

@@
 
-#saveRDS(ex_3_pred, "../../stats/saves/ex3_model_predictions.rds")
+#saveRDS(ex_3_pred, "../../stats/saves/adult_ex3_model_predictions_data.rds")
 
@@
 adult_ex4_data_summary <- adult_ex4_data %>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
   mutate(model = "data") %>%
@@
 )%>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "weak"))%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
   group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
@@
 
-#saveRDS(ex_4_pred, "../../stats/saves/ex4_model_predictions.rds")
+#saveRDS(ex_4_pred, "../../stats/saves/adult_ex4_model_predictions_data.rds")
 
@@
 
+#saveRDS(child_model_predictions, "../../stats/saves/child_ex3_model_predictions.rds")
+
 plot_child_ex3_data <- child_ex3_data%>%

### 2019-03-12 papers/full_paper/models.Rmd
comments and edits up to model comparison

@@
 
-## Model utensils
+## Model utilities
 
@@
 rsaUtils <- '
+// three objects: triangle_1 on table 1, triangle_2 and circle_1 on table 2
 var all_objects = [
@@
 
+// listener prior is over types, not tokens (we use uniformDraw on prior_objects)
 var prior_objects = [
@@
 
+// two possible lexica, corresponding to meaning of words "dax" and "wug"
 var lexicon1 = function(utterance, obj){
@@
       priorProbs, speakerOptimality)
+
     observe(rsaPredictions, row.correct)
-
   }, data)
@@
 ```
+
+**issue: here we are passing `adult_ex1_data` when we want `adult_ex1_data %>% filter(condition == "test")`**
 
@@
 
+makePriorList = function(p){
+  c(1 - p, 1 - p, p)
+}
+
+makeInversePriorList = function(p){
+  c(p, p, 1 - p)
+}
+
 model_params_ex3$prior = list(
-    c(1-prior_pref_same$prior,1-prior_pref_same$prior,prior_pref_same$prior), 
-    c(prior_pref_same$prior,prior_pref_same$prior,1-prior_pref_same$prior), 
-    c(1-prior_pref_diff$prior,1-prior_pref_diff$prior,prior_pref_diff$prior), 
-    c(prior_pref_diff$prior,prior_pref_diff$prior,1-prior_pref_diff$prior),
-    c(1-prior_novel_same$prior,1-prior_novel_same$prior,prior_novel_same$prior), 
-    c(prior_novel_same$prior,prior_novel_same$prior,1-prior_novel_same$prior), 
-    c(1-prior_novel_diff$prior,1-prior_novel_diff$prior,prior_novel_diff$prior), 
-    c(prior_novel_diff$prior,prior_novel_diff$prior,1-prior_novel_diff$prior))
-
+  makePriorList(prior_pref_same$prior), 
+  makeInversePriorList(prior_pref_same$prior), 
+  makePriorList(prior_pref_diff$prior), 
+  makeInversePriorList(prior_pref_diff$prior), 
+  makePriorList(prior_novel_same$prior), 
+  makeInversePriorList(prior_novel_same$prior), 
+  makePriorList(prior_novel_diff$prior), 
+  makeInversePriorList(prior_novel_diff$prior)
+)
 ```
@@
 
-    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
+    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
 
@@
   filter(model != "data") %>%
-  mutate(data_mean = rep(ex_3_pred%>%filter(model == "data")%>%pull(mean),3),
-         data_ci_lower = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_lower),3),
-         data_ci_upper = rep(ex_3_pred%>%filter(model == "data")%>%pull(ci_upper),3))
+  left_join(., ex_3_pred %>%
+    ungroup()%>%
+    filter(model == "data") %>%
+    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
+    select(-model)
+  )
 

### 2019-03-12 papers/full_paper/models.Rmd
refactor parameter passing for adult ex4 to reduce chance of copy errors

@@
   speak_opt = adult_model_param$so_map)
-
+prior_pref_summary <- adult_ex2_preference_data %>%
+  group_by(condition)
 prior_pref_same <- adult_ex2_preference_data %>%
@@
   left_join(ex3_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
          log_like = log(like))%>%
@@
   left_join(ex3_flat_prior_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
          log_like = log(like))%>%
@@
   left_join(ex3_prior_only_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
          log_like = log(like))%>%
@@
 ```{r bayes factors ex3 adults}
-ex3_bf <- data.frame(
-  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
-  log_bayes_factor = c(
-    log_like_pragmatic_ex3$model_log_like - log_like_flat_prior_ex3$model_log_like,
-    log_like_pragmatic_ex3$model_log_like- log_like_prior_only_ex3$model_log_like,
-    log_like_flat_prior_ex3$model_log_like - log_like_prior_only_ex3$model_log_like)
-)
-
-ex3_bf%>%
+
+ex3_bf <- bind_rows(
+  log_like_pragmatic_ex3,
+  log_like_flat_prior_ex3,
+  log_like_prior_only_ex3
+) %>% spread(model, model_log_like) %>%
+  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
+         "pragmatic > prior_only" = pragmatic - prior_only,
+         "flat_prior > prior_only" = flat_prior - prior_only) %>%
+  select(-pragmatic,  -flat_prior, -prior_only)
+
+ex3_bf %>%
   kable(digits = 2)
@@
 
-strongPrior <- data.frame(
-  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
-  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
-  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
-  prior_manipulation = rep("strong",8))
-
-strong_prior_pref_same <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "preference",
-         prior_manipulation == "strong",
-         speaker == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-strong_prior_pref_diff <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "preference",
-         prior_manipulation == "strong",
-         speaker == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-strong_prior_novel_same <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "strong",
-         speaker == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-strong_prior_novel_diff <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "strong",
-         speaker == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-strongPrior$prior = list(
-    c(1-strong_prior_pref_same$prior,1-strong_prior_pref_same$prior,strong_prior_pref_same$prior), 
-    c(strong_prior_pref_same$prior,strong_prior_pref_same$prior,1-strong_prior_pref_same$prior), 
-    c(1-strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior,strong_prior_pref_diff$prior), 
-    c(strong_prior_pref_diff$prior,strong_prior_pref_diff$prior,1-strong_prior_pref_diff$prior),
-    c(1-strong_prior_novel_same$prior,1-strong_prior_novel_same$prior,strong_prior_novel_same$prior), 
-    c(strong_prior_novel_same$prior,strong_prior_novel_same$prior,1-strong_prior_novel_same$prior), 
-    c(1-strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior,strong_prior_novel_diff$prior), 
-    c(strong_prior_novel_diff$prior,strong_prior_novel_diff$prior,1-strong_prior_novel_diff$prior))
-
-mediumPrior <- data.frame(
-  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
-  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
-  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
-  prior_manipulation = rep("medium",8))
-
-medium_prior_pref_same <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "preference",
-         prior_manipulation == "medium",
-         speaker == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-medium_prior_pref_diff <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "preference",
-         prior_manipulation == "medium",
-         speaker == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-medium_prior_novel_same <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "medium",
-         speaker == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-medium_prior_novel_diff <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "medium",
-         speaker == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-mediumPrior$prior = list(
-    c(1-medium_prior_pref_same$prior,1-medium_prior_pref_same$prior,medium_prior_pref_same$prior), 
-    c(medium_prior_pref_same$prior,medium_prior_pref_same$prior,1-medium_prior_pref_same$prior), 
-    c(1-medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior,medium_prior_pref_diff$prior), 
-    c(medium_prior_pref_diff$prior,medium_prior_pref_diff$prior,1-medium_prior_pref_diff$prior),
-    c(1-medium_prior_novel_same$prior,1-medium_prior_novel_same$prior,medium_prior_novel_same$prior), 
-    c(medium_prior_novel_same$prior,medium_prior_novel_same$prior,1-medium_prior_novel_same$prior), 
-    c(1-medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior,medium_prior_novel_diff$prior), 
-    c(medium_prior_novel_diff$prior,medium_prior_novel_diff$prior,1-medium_prior_novel_diff$prior))
-
-weakPrior <- data.frame(
-  common_ground_manipulation = c("novelty","novelty","novelty","novelty"),
-  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker"),
-  alignment = c("congruent","incongruent","congruent","incongruent"),
-  prior_manipulation = rep("weak",4))
-
-weak_prior_novel_same <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "weak",
-         speaker == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-weak_prior_novel_diff <- adult_ex4_prior_data %>%
-  filter(common_ground_manipulation == "novelty",
-         prior_manipulation == "weak",
-         speaker == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-weakPrior$prior = list(
-    c(1-weak_prior_novel_same$prior,1-weak_prior_novel_same$prior,weak_prior_novel_same$prior), 
-    c(weak_prior_novel_same$prior,weak_prior_novel_same$prior,1-weak_prior_novel_same$prior), 
-    c(1-weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior,weak_prior_novel_diff$prior), 
-    c(weak_prior_novel_diff$prior,weak_prior_novel_diff$prior,1-weak_prior_novel_diff$prior))
-
-# combining all priors into one data frame
-model_params_ex4 = rbind(strongPrior,mediumPrior,weakPrior)%>%
+strongPrior <- expand.grid(
+  common_ground_manipulation = c("preference","novelty"),
+  speaker = c("same_speaker","different_speaker"),
+  prior_manipulation = c("strong", "medium", "weak")
+)
+
+strong_prior_summary <- adult_ex4_prior_data %>%
+  group_by(common_ground_manipulation, prior_manipulation, speaker) %>%
+  summarize(prior = mean(correct))
+
+model_params_ex4 <- left_join( 
+  strongPrior, 
+  strong_prior_summary# %>% filter(prior_manipulation == "strong")
+) %>%
+  rename(congruent = prior) %>%
+  mutate(incongruent = 1 - congruent) %>%
+  gather(alignment, prior, congruent, incongruent) %>%
+  drop_na() %>%
   mutate(speak_opt = adult_model_param$so_map)
-
 ```
@@
 var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.prior,row.speak_opt)
+    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
 
@@
 
+    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
+
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.prior}));
+      var obj = sample( Categorical({vs: all_objects, ps: priorProbLst}));
       return obj.shape == "circle" ? 1 : 0
@@
 ```{r correlation plot ex4 adults}
-
 ex_4_cor_plot <- ex_4_pred %>%
@@
   filter(model != "data") %>%
-  mutate(data_mean = rep(ex_4_pred%>%filter(model == "data")%>%pull(mean),3),
-         data_ci_lower = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_lower),3),
-         data_ci_upper = rep(ex_4_pred%>%filter(model == "data")%>%pull(ci_upper),3))
+  left_join(., ex_4_pred %>%
+    ungroup()%>%
+    filter(model == "data") %>%
+    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
+    select(-model)
+  )
 
@@
   left_join(ex4_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  mutate(like = ifelse(correct_inf == 1 , value, 1 - value),
          log_like = log(like))%>%
@@
   left_join(ex4_flat_prior_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  mutate(like = ifelse(correct_inf ==  1, value , 1 - value),
          log_like = log(like))%>%
@@
 log_like_prior_only_ex4 <- adult_ex4_data %>%
-  left_join(ex4_prior_only_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == "1",value,1-value),
+  left_join(ex4_prior_only_model_predictions) %>%
+  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
          log_like = log(like))%>%
@@
 ```{r bayes factors ex4 adults}
-ex4_bf <- data.frame(
-  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
-  log_bayes_factor = c(
-    log_like_pragmatic_ex4$model_log_like - log_like_flat_prior_ex4$model_log_like,
-    log_like_pragmatic_ex4$model_log_like- log_like_prior_only_ex4$model_log_like,
-    log_like_flat_prior_ex4$model_log_like - log_like_prior_only_ex4$model_log_like)
-)
-
-ex4_bf%>%
+ex4_bf <- bind_rows(
+  log_like_pragmatic_ex4,
+  log_like_flat_prior_ex4,
+  log_like_prior_only_ex4
+) %>% spread(model, model_log_like) %>%
+  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
+         "pragmatic > prior_only" = pragmatic - prior_only,
+         "flat_prior > prior_only" = flat_prior - prior_only) %>%
+  select(-pragmatic,  -flat_prior, -prior_only)
+
+ex4_bf %>%
   kable(digits = 2)
 ```
+
 # Children

### 2019-03-12 papers/full_paper/models.Rmd
refactor param passing for ex3

@@
 # create datafiles with model parameters
-model_params_ex3 <- data.frame(
-  common_ground_manipulation = c("preference","preference","preference","preference","novelty","novelty","novelty","novelty"),
-  speaker = c("same_speaker","same_speaker","different_speaker","different_speaker","same_speaker","same_speaker","different_speaker","different_speaker"),
-  alignment = c("congruent","incongruent","congruent","incongruent","congruent","incongruent","congruent","incongruent"),
-  speak_opt = adult_model_param$so_map)
-prior_pref_summary <- adult_ex2_preference_data %>%
-  group_by(condition)
-prior_pref_same <- adult_ex2_preference_data %>%
-  filter(condition == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-prior_pref_diff <- adult_ex2_preference_data %>%
-  filter(condition == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-prior_novel_same <- adult_ex2_novelty_data %>%
-  filter(condition == "same_speaker")%>%
-  summarise(prior = mean(correct))
-
-prior_novel_diff <- adult_ex2_novelty_data %>%
-  filter(condition == "different_speaker")%>%
-  summarise(prior = mean(correct))
-
-makePriorList = function(p){
-  c(1 - p, 1 - p, p)
-}
-
-makeInversePriorList = function(p){
-  c(p, p, 1 - p)
-}
-
-model_params_ex3$prior = list(
-  makePriorList(prior_pref_same$prior), 
-  makeInversePriorList(prior_pref_same$prior), 
-  makePriorList(prior_pref_diff$prior), 
-  makeInversePriorList(prior_pref_diff$prior), 
-  makePriorList(prior_novel_same$prior), 
-  makeInversePriorList(prior_novel_same$prior), 
-  makePriorList(prior_novel_diff$prior), 
-  makeInversePriorList(prior_novel_diff$prior)
-)
+model_params_ex3 <- expand.grid(
+  common_ground_manipulation = c("preference", "novelty"),
+  speaker = c("same_speaker", "different_speaker"),
+  speak_opt = adult_model_param$so_map
+  )
+
+prior_pref_summary <- bind_rows(
+  adult_ex2_preference_data,
+  adult_ex2_novelty_data) %>%
+  group_by(condition, experiment) %>%
+  summarise(prior = mean(correct)) %>%
+  mutate(experiment = gsub("adult_ex2_", "", experiment)) %>%
+  rename(common_ground_manipulation = experiment,
+         speaker = condition)
+
+model_params_ex3 <- left_join( 
+  model_params_ex3, 
+  prior_pref_summary, by = c("common_ground_manipulation", "speaker")
+) %>%
+  rename(congruent = prior) %>%
+  mutate(incongruent = 1 - congruent) %>%
+  gather(alignment, prior, congruent, incongruent)
+
 ```
@@
 var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.prior,row.speak_opt)
+    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
 
@@
 var output = map(function(row){
+  var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
 
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.prior}));
+      var obj = sample( Categorical({vs: all_objects, ps: priorProbLst}));
       return obj.shape == "circle" ? 1 : 0
@@
 
-var prior = [.5, .5, .5]
+var priorProbLst = [.5, .5, .5]
 
@@
 
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.speak_opt)
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
 

### 2019-03-13 papers/full_paper/models.Rmd
update adult so params

@@
 
-**issue: here we are passing `adult_ex1_data` when we want `adult_ex1_data %>% filter(condition == "test")`**
-
 ```{r inferring speaker optimality parameter adults}
@@
 #   program_code = paste(rsaUtils, rsaModel, speakOptParam , sep='\n'),
-#   data = list(data = adult_ex1_data),
+#   data = list(data = adult_ex1_data %>% filter(condition == "test")),
 #   data_var = "dataFromR",

### 2019-03-18 papers/full_paper/models.Rmd
update noisy models

@@
 library(coda)
+library(matrixStats)
 library(ggpubr)
@@
 
-##### Pragmatic model
-
-```{r model rsa noise ex3 adults}
+#### Pragmatic model
+
+##### Parameter free
+
+```{r model rsa ex3 adults}
 predictions.rsa.ex3 <-'
@@
 
-##### Prior only model
+##### Noise parameter
+
+```{r model rsa noise ex3, include = FALSE}
+predictions.rsa.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions pragmatic model ex 3, include = FALSE}
+ex3_pragm_model_noise <- webppl(
+  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3.noise, sep='\n'),
+  data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+) %>%
+  saveRDS("../../stats/saves/ex3_pragm_model_noise.rds")
+
+# model predictions
+ex3_pragm_model_pred_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex3_pragm_model_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+```
+#### Prior only model
 
@@
 
-##### Flat prior model
+#### Flat prior model
 
@@
   ex_3_model_pred,
+  ex3_pragm_model_pred_noise,
   adult_ex3_data_summary
@@
 
+### Loglike Parameter free model
 ```{r log likes ex3 adults}
@@
   mutate(model = reorder(model,model_log_like))
+```
+
+### Loglike models with noise
+
+```{r model rsa noise ex3, include = FALSE}
+loglike.rsa.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex3_pragm_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 2)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")
+
+ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
+  mutate(model = "pragmatic")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
 ```

### 2019-03-18 stats/kids/kids_model_predictions.Rmd
update noisy models

@@
 
+model_params <- readRDS("../../stats/saves/child_model_param.rds")%>%
+  select(value) %>%
+  map_df(bind_rows)%>%
+  group_by(param,condition)%>%
+  summarise(param_map = estimate_mode(val))%>%
+  mutate(cond = paste(param,condition, sep = "_"))%>%
+  ungroup()%>%
+  select(cond,param_map)%>%
+  spread(cond,param_map)%>%
+  rename(so_int = so_int_NA,
+         so_slope = so_slope_NA)
+
 ex3_data_param <- ex3_data%>%
-  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
-         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
-         so_int = model_params$NA_so_int,
-         so_slope = model_params$NA_so_slope,
-         so_slope_quad = model_params$NA_so_slope_quad,
-         same_speaker_pref_int = model_params$same_speaker_pref_int,
-         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
-         so = so_int+so_slope*(age_num-min(age_num))+so_slope_quad*(age_num-min(age_num))^2,
+  mutate(different_speaker_pref_int = model_params$pref_int_different_speaker,
+         different_speaker_pref_slope = model_params$pref_slope_different_speaker,
+         so_int = model_params$so_int,
+         so_slope = model_params$so_slope,
+         same_speaker_pref_int = model_params$pref_int_same_speaker,
+         same_speaker_pref_slope = model_params$pref_slope_same_speaker,
+         so = so_int+so_slope*(age_num-min(age_num)),
          diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
@@
 
-    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment, Math.exp(noisyModelPredictions.score(1))]
+    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment + "/" + row.correct_inf, Math.exp(noisyModelPredictions.score(1))]
 
@@
   filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "Speaker", "Alignment"), sep="/")%>%
+  separate(Parameter, into = c("age", "speaker", "alignment", "correct"), sep="/")%>%
   mutate( model = "noise parameter across age")%>%
-  group_by(model, age,Alignment,Speaker) %>%
+  group_by(model, age,alignment,speaker, correct) %>%
   summarise(mean = estimate_mode(value), 
@@
 
+log_like_noisy_model <- noisy_pred %>%
+  mutate(like = ifelse(correct == "1",mean,1-mean),
+         log_like = log(like))%>%
+  group_by(model)%>%
+  summarise(model_log_like = sum(log_like))
+
 ```
@@
 
-    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment, Math.exp(noisyModelPredictions.score(1))]
+    return  [row.age_num + "/" + row.Speaker + "/" + row.Alignment , Math.exp(noisyModelPredictions.score(1))]
 
@@
   cores = 4,
-  inference_opts = list(method = "MCMC", samples = 8000, burn = 2000, verbose = T)
+  inference_opts = list(method = "MCMC", samples = 2000, burn = 2000, verbose = T)
 )
@@
 
+child_ex3_pragm_model_predictions<- child_ex3_pragm_model_predictions%>%
+  mutate(mean = value,
+         ci_lower = value,
+         ci_upper = value)
+
 models <- bind_rows(
-  quad_pred,
-  lin_pred,
-  lin_flat_pred,
-  lin_pred_prior
+  noisy_pred,
+child_ex3_pragm_model_predictions
 )
 
-p_data <- ex3_data %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
+p_data <- child_ex3_data %>%
   mutate(age_bin = age_num - 3)%>%
-  group_by(Speaker, Alignment ,age_bin, subid)
+  group_by(speaker, alignment ,age_bin, id)
 
@@
   ylim(-0.05,1.05)+
-  facet_grid(Speaker~Alignment)+
+  facet_grid(speaker~alignment)+
   theme_few()+
@@
 ```
+
+# model comparison
+
+```{r}
+noisyModelPredWebpplLoglike <-'
+
+var allData = dataFromR.ex3data
+
+var model = function(){
+
+  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    display(JSON.stringify(row.correct_inf))
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n:row.correct_inf})
+
+  return  loglike
+
+}, allData)
+
+  return sum(output)
+
+}
+'
+```
+
+```{r}
+
+noisy_model_pred<- webppl(
+  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebpplLoglike , sep='\n'),
+  data =list(ex3data = ex3_data_param),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 4,
+  cores = 4,
+  inference_opts = list(method = "forward", samples = 2)
+)
+
+# ex4_pragm_model_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4, sep='\n'),
+#   data = list(Data = adult_ex4_data, allConditions = allConditionsEx4, predPrior = predPriorEx4, noise = ex3_pragm_model_noise$mean),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4, 
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_pragm_model_loglike.rds")
+
+ex4_pragm_model_loglike <- readRDS("../../stats/saves/ex4_pragm_model_loglike.rds")%>%
+  mutate(model = "pragmatic")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+```

### 2019-03-20 papers/full_paper/models.Rmd
add noisy model predictions adults ex 3

@@
 var output = map(function(row){
+
     var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
@@
 
-```{r predictions pragmatic model ex 3, include = FALSE}
-ex3_pragm_model_noise <- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3.noise, sep='\n'),
-  data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-  data_var = "dataFromR",
-  model_var = "model",
-  chains = 4,
-  cores = 4,
-  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-) %>%
-  saveRDS("../../stats/saves/ex3_pragm_model_noise.rds")
+```{r predictions pragmatic model ex 3 noise, include = FALSE}
+# ex3_pragm_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_pragm_model_noise.rds")
 
@@
 ## noise parameter
-ex3_pragm_model_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+ex3_pragm_model_noise_param <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
@@
 ```
+
 #### Prior only model
 
+##### Parameter free
 ```{r model prior only ex3 adults}
@@
 
+##### Noise parameter
+
+```{r model prior only noise ex3, include = FALSE}
+predictions.prior.only.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions prior only model ex 3 noise, include = FALSE}
+# ex3_prior_only_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_prior_only_model_noise.rds")
+
+# model predictions
+ex3_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+```
+
 #### Flat prior model
 
+##### Parameter free
 ```{r model flat prior ex3 adults}
@@
 ```
+
+##### Noise parameter
+
+```{r model flat prior noise ex3, include = FALSE}
+predictions.flat.prior.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions flat prior model ex 3 noise, include = FALSE}
+# ex3_flat_prior_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_flat_prior_model_noise.rds")
+
+# model predictions
+ex3_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+```
+
+#### Compare model predictions to data
 
@@
 # summarize model predictions
-ex_3_model_pred <- bind_rows(
-  ex3_pragm_model_predictions,
-  ex3_prior_only_model_predictions,
-  ex3_flat_prior_model_predictions
+ex_3_model_pred_param_free <- bind_rows(
+  ex3_pragm_model_predictions
+  #ex3_prior_only_model_predictions,
+  #ex3_flat_prior_model_predictions
 )%>%
@@
          ci_upper = mean)
+
+ex_3_model_pred <- 
+  bind_rows(
+    ex_3_model_pred_param_free,
+    ex3_pragm_model_pred_noise,
+            ex3_prior_only_model_pred_noise,
+            ex3_flat_prior_model_pred_noise)
 
@@
   scale_color_manual(name="Model",
-                     breaks=c("data","pragmatic","flat_prior","prior_only"),
-                     values= c("black","#859900","#6c71c4","#b58900"))+
+                     breaks=c("data","pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
+                     values= c("black","#859900","#00afaf","#6c71c4","#b58900"))+
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
@@
   group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
+  summarise(logP = sum(log_like))
 
@@
   group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
-ex3_model_comparison <- bind_rows(
-  log_like_pragmatic_ex3,
-  log_like_flat_prior_ex3,
-  log_like_prior_only_ex3
-)%>%
-  mutate(model = reorder(model,model_log_like))
+  summarise(logP = sum(log_like))
 ```
@@
 
+#### Pragmatic model 
 ```{r model rsa noise ex3, include = FALSE}
@@
 #   cores = 4,
-#   inference_opts = list(method = "forward", samples = 2)
+#   inference_opts = list(method = "forward", samples = 5000)
 # ) %>%
@@
 ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
-  mutate(model = "pragmatic")%>%
+  mutate(model = "pragmatic_noise")%>%
   group_by(model)%>%
@@
 ```
+#### Prior only model
+
+```{r model prior only noise ex3, include = FALSE}
+loglike.prior.only.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex3_prior_only_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")
+
+ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+```
+
+#### Flat prior model
+
+```{r model flat prior noise ex3, include = FALSE}
+loglike.flat.prior.ex3.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5,.5]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex3_flat_prior_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex3.noise, sep='\n'),
+#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")
+
+ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+```
+
+```{r}
+ex3_model_comparison <- bind_rows(
+  log_like_pragmatic_ex3,
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+)%>%
+  mutate(model = reorder(model,logP))
+```
 
@@
 ```{r likelihood plot adults}
-ggplot(ex3_model_comparison, aes(x = model, y = model_log_like, col = model))+
-  geom_segment( aes(x=model, xend=model, y=-600, yend=model_log_like), col = "black", size = 1)+
+ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
   geom_point(size = 7)+
@@
   guides(col = F)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#859900","#6c71c4"))
+  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
+                    values= c("#00afaf","#b58900","#859900","#6c71c4"))
 ```
@@
   log_like_pragmatic_ex3,
-  log_like_flat_prior_ex3,
-  log_like_prior_only_ex3
-) %>% spread(model, model_log_like) %>%
-  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
-         "pragmatic > prior_only" = pragmatic - prior_only,
-         "flat_prior > prior_only" = flat_prior - prior_only) %>%
-  select(-pragmatic,  -flat_prior, -prior_only)
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+) %>% spread(model, logP) %>%
+  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
+         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
+         "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
+         "prior_only_noise > flat_prior_noise" = prior_only_noise - flat_prior_noise) %>%
+  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)
 

### 2019-03-20 papers/full_paper/models.Rmd
update ex4 adults model predictions and comparison with noise

@@
 
-##### Parameter free
-```{r model prior only ex3 adults}
-predictions.prior.only.ex3 <-'
-
-var allData = dataFromR.data
-
-var output = map(function(row){
-  var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbLst}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions prior only model ex3 adults}
-ex3_prior_only_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3 , sep='\n'),
-  data =list(data = model_params_ex3),
-  data_var = "dataFromR"
-)
-
-# model predictions
-ex3_prior_only_model_predictions <- ex3_prior_only_model %>%
-  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="prior_only")%>%
-  select(-`1`)
-```
-
 ##### Noise parameter
@@
 #### Flat prior model
-
-##### Parameter free
-```{r model flat prior ex3 adults}
-predictions.flat.prior.ex3 <-'
-var allData = dataFromR.data
-
-var priorProbLst = [.5, .5, .5]
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
-
-    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-'
-```
-
-```{r predictions flat prior model ex3 adults}
-ex3_flat_prior_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3 , sep='\n'),
-  data =list(data = model_params_ex3),
-  data_var = "dataFromR"
-)
-
-# model predictions
-ex3_flat_prior_model_predictions <- ex3_flat_prior_model %>%
-  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="flat_prior")%>%
-  select(-`1`)
-
-```
 
@@
   ex3_pragm_model_predictions
-  #ex3_prior_only_model_predictions,
-  #ex3_flat_prior_model_predictions
 )%>%
@@
 
-## Model comparison
-
-### Loglike Parameter free model
+### Model comparison
+
+#### Loglike Parameter free model
 ```{r log likes ex3 adults}
@@
   summarise(logP = sum(log_like))
-
-log_like_flat_prior_ex3 <- adult_ex3_data %>%
-  left_join(ex3_flat_prior_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(logP = sum(log_like))
-
-log_like_prior_only_ex3 <- adult_ex3_data %>%
-  left_join(ex3_prior_only_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(logP = sum(log_like))
-```
-
-### Loglike models with noise
-
-#### Pragmatic model 
+```
+
+#### Loglike models with noise
+
+##### Pragmatic model 
 ```{r model rsa noise ex3, include = FALSE}
@@
 ```
-#### Prior only model
+##### Prior only model
 
@@
 
-#### Flat prior model
+##### Flat prior model
 
@@
 
-### Plot for likelihoods
+#### Plot for likelihoods
 
@@
 
-### Bayes factors
+#### Bayes factors
 
@@
 
-### Model predictions
-
-##### Pragmatic model
-
-```{r model rsa noise ex4 adults}
-predictions.rsa.ex4 <-'
-
-var allData = dataFromR.data
-
-var output = map(function(row){
-    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
-
-    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 4 adults}
-ex4_pragm_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4 , sep='\n'),
-  data =list(data = model_params_ex4),
-  data_var = "dataFromR"
-)
+### Model predictions (including noise parameter)
+
+#### Pragmatic model
+
+```{r model rsa noise ex4, include = FALSE}
+predictions.rsa.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions pragmatic model ex 4 noise, include = FALSE}
+# ex4_pragm_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_pragm_model_noise.rds")
 
 # model predictions
-ex4_pragm_model_predictions <- ex4_pragm_model %>%
-  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="pragmatic")%>%
-  select(-`1`)
-
-```
-
-##### Prior only model
-
-```{r model prior only ex4 adults}
-predictions.prior.only.ex4 <-'
-
-var allData = dataFromR.data
-
-var output = map(function(row){
-
-    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
+ex4_pragm_model_pred_noise <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+```
+
+#### Prior only model
+
+```{r model prior only noise ex4, include = FALSE}
+predictions.prior.only.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
 
   var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: priorProbLst}));
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
       return obj.shape == "circle" ? 1 : 0
@@
 
-    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions prior only model ex4 adults}
-ex4_prior_only_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4 , sep='\n'),
-  data =list(data = model_params_ex4),
-  data_var = "dataFromR"
-)
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions prior only model ex 4 noise, include = FALSE}
+# ex4_prior_only_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_prior_only_model_noise.rds")
 
 # model predictions
-ex4_prior_only_model_predictions <- ex4_prior_only_model %>%
-  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="prior_only")%>%
-  select(-`1`)
-```
-
-##### Flat prior model
-
-```{r model flat prior ex4 adults}
-predictions.flat.prior.ex4 <-'
-var allData = dataFromR.data
-
-var prior = [.5, .5, .5]
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.speak_opt)
-
-    return extend([row.common_ground_manipulation + "/" + row.prior_manipulation + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-'
-```
-
-```{r predictions flat prior model ex4 adults}
-ex4_flat_prior_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4 , sep='\n'),
-  data =list(data = model_params_ex4),
-  data_var = "dataFromR"
-)
+ex4_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex4_prior_only_model_noise_param <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+```
+
+#### Flat prior model
+
+```{r model flat prior noise ex4, include = FALSE}
+predictions.flat.prior.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5, .5]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+ map(function(d){ 
+      observe(noisyModelPredictions, d.correct_inf)
+    }, conditionSpecificData)
+
+  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allParams)
+
+  return extend(_.fromPairs(conditionOutput), {noise: noise})
+}
+'
+```
+
+```{r predictions flat prior model ex 4 noise, include = FALSE}
+# ex4_flat_prior_model_noise <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_flat_prior_model_noise.rds")
 
 # model predictions
-ex4_flat_prior_model_predictions <- ex4_flat_prior_model %>%
-  separate(`0`, into = c("common_ground_manipulation","prior_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="flat_prior")%>%
-  select(-`1`)
-
+ex4_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+## noise parameter
+ex4_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
 ```
@@
 ex_4_model_pred <- bind_rows(
-  ex4_pragm_model_predictions,
-  ex4_prior_only_model_predictions,
-  ex4_flat_prior_model_predictions
+  ex4_pragm_model_pred_noise,
+  ex4_prior_only_model_pred_noise,
+  ex4_flat_prior_model_pred_noise
 )%>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  summarise(mean = mean(value))%>%
-  mutate(ci_lower = mean,
-         ci_upper = mean)
+  ungroup()%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))
 
@@
 
-##### Plot model predictions and data
+### Compare model predictions to data
+
+#### Plot model predictions and data
 
@@
   scale_color_manual(name="Model",
-                     breaks=c("data","pragmatic","flat_prior","prior_only"),
+                     breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                      values= c("black","#859900","#6c71c4","#b58900"))+
@@
 
-##### Correlation plot model predictions and data
+#### Correlation plot model predictions and data
 
@@
 
-## Model comparison
-
-```{r loglikes ex4 adults}
-# calculating model log-likelihoods
-log_like_pragmatic_ex4 <- adult_ex4_data %>%
-  left_join(ex4_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1 , value, 1 - value),
-         log_like = log(like))%>%
+### Model comparison
+
+#### Loglike models with noise
+
+##### Pragmatic model 
+```{r model rsa noise ex4, include = FALSE}
+loglike.rsa.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+ var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex4_pragm_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds")
+
+ex4_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds")%>%
+  mutate(model = "pragmatic_noise")%>%
   group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
-log_like_flat_prior_ex4 <- adult_ex4_data %>%
-  left_join(ex4_flat_prior_model_predictions)%>%
-  mutate(like = ifelse(correct_inf ==  1, value , 1 - value),
-         log_like = log(like))%>%
+  summarize(logP = logSumExp(value))
+```
+
+##### Prior only model
+
+```{r model prior only noise ex4, include = FALSE}
+loglike.prior.only.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+ var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
+
+  var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
+      return obj.shape == "circle" ? 1 : 0
+  }})
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex4_prior_only_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds")
+
+ex4_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds")%>%
+  mutate(model = "prior_only_noise")%>%
   group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
-log_like_prior_only_ex4 <- adult_ex4_data %>%
-  left_join(ex4_prior_only_model_predictions) %>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
+  summarize(logP = logSumExp(value))
+```
+
+##### Flat prior model
+
+```{r model flat prior noise ex4, include = FALSE}
+loglike.flat.prior.ex4.noise <-'
+var allParams = dataFromR.allParams
+var allData = dataFromR.allData
+
+var model = function(){
+
+   var noise = uniformDrift({a: 0, b:1, width: 0.1})
+
+  var conditionOutput = map(function(conditionInfo){
+
+ var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
+
+   var conditionSpecificPriors = [.5, .5,.5]
+
+      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
+
+   var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    var loglike = Binomial({
+        p: Math.exp(noisyModelPredictions.score(1)), 
+        n: conditionSpecificData.length}).score(
+      sum(_.map(conditionSpecificData, "correct_inf"))
+    )
+  return  loglike
+
+}, allParams)
+
+ return sum(conditionOutput)
+
+}
+'
+```
+
+```{r}
+# ex4_flat_prior_model_noise_loglike <- webppl(
+#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex4.noise, sep='\n'),
+#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "forward", samples = 5000)
+# ) %>%
+#   saveRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds")
+
+ex4_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds")%>%
+  mutate(model = "flat_prior_noise")%>%
   group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
+  summarize(logP = logSumExp(value))
+```
+
+```{r}
 ex4_model_comparison <- bind_rows(
-  log_like_pragmatic_ex4,
-  log_like_flat_prior_ex4,
-  log_like_prior_only_ex4
+  ex4_pragm_model_noise_loglike,
+  ex4_flat_prior_model_noise_loglike,
+  ex4_prior_only_model_noise_loglike
 )%>%
-  mutate(model = reorder(model,model_log_like))
-```
-
-### Plot for likelihoods
+  mutate(model = reorder(model,logP))
+```
+
+#### Plot for likelihoods
 
 ```{r plot for loglikelihood ex4 adults}
-ggplot(ex4_model_comparison, aes(x = model, y = model_log_like, col = model))+
-  geom_segment( aes(x=model, xend=model, y=-1500, yend=model_log_like), col = "black", size = 1)+
+ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
   geom_point(size = 7)+
@@
 ex4_bf <- bind_rows(
-  log_like_pragmatic_ex4,
-  log_like_flat_prior_ex4,
-  log_like_prior_only_ex4
-) %>% spread(model, model_log_like) %>%
-  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
-         "pragmatic > prior_only" = pragmatic - prior_only,
-         "flat_prior > prior_only" = flat_prior - prior_only) %>%
-  select(-pragmatic,  -flat_prior, -prior_only)
+  ex4_pragm_model_noise_loglike,
+  ex4_flat_prior_model_noise_loglike,
+  ex4_prior_only_model_noise_loglike
+) %>% spread(model, logP) %>%
+  mutate("pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
+         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
+         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
+  select(-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)
 

### 2019-03-20 papers/full_paper/models.Rmd
child noisy model predictions

@@
 
+#### Parameter free
+
 ```{r pragmatic model ex3 children}
@@
 
-var allData = dataFromR.ex3data
+var allData = dataFromR.allData
 
@@
   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
-  data =list(ex3data = ex3_model_data),
+  data =list(allData = ex3_model_data),
   data_var = "dataFromR"
@@
   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(value = `1`,
+  mutate(mean = `1`,
+         ci_lower = mean,
+         ci_upper = mean,
          model="pragmatic",
@@
 
+#### Noise parameter
+
+```{r}
+child.ex3.rsa.predictions.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r}
+# child_ex3_pragm_model_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")
+
+# model predictions
+child_ex3_pragm_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "pragmatic_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_pragm_model_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
 ### Prior only model
@@
   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions , sep='\n'),
-  data =list(ex3data = ex3_model_data),
+  data =list(allData = ex3_model_data),
   data_var = "dataFromR"
@@
   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(value = `1`,
+  mutate(mean = `1`,
          model="prior_only",
@@
   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions , sep='\n'),
-  data =list(ex3data = ex3_model_data),
+  data =list(allData = ex3_model_data),
   data_var = "dataFromR")
@@
   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(value = `1`,
+  mutate(mean = `1`,
          model="flat_prior",
@@
 child_model_predictions <- bind_rows(
+  child_ex3_pragm_model_predictions_noise,
   child_ex3_pragm_model_predictions,
@@
   #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
-  geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
   geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .5)+
@@
   scale_color_manual(name="Model",
-                     breaks=c("pragmatic","flat_prior","prior_only"),
-                     values= c("#859900","#6c71c4","#b58900"))+
+                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
+                     values= c("#859900","#00afaf","#6c71c4","#b58900"))+
   scale_fill_manual(name="Model",
-                     breaks=c("pragmatic","flat_prior","prior_only"),
-                     values= c("#859900","#6c71c4","#b58900"))
+                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
+                     values= c("#859900","#00afaf","#6c71c4","#b58900"))
 
@@
   group_by(model,speaker,alignment, age)%>%
-  summarise(Model = mean(value))
+  summarise(Model = mean(mean))
 
@@
   ungroup()%>%
-  mutate(Data = rep(child_cor_data$Data,3),
-         Data_ci_lower = rep(child_cor_data$Data_ci_lower,3),
-         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,3))
+  mutate(Data = rep(child_cor_data$Data,4),
+         Data_ci_lower = rep(child_cor_data$Data_ci_lower,4),
+         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,4))
 

### 2019-03-23 papers/full_paper/models.Rmd
ais version of model for likelihoods

@@
 ```{r}
-# child_ex3_pragm_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")
+child_ex3_pragm_model_noise<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  model_var = "model",
+  chains = 1,
+  cores = 1,
+  inference_opts = list(method = "MCMC", samples = 100, burn = 5, verbose = T)
+)
+
+%>%
+   saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")
 
@@
 
+```{r}
+child.ex3.rsa.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 100
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+child_ex3_pragm_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)
+```
+
 ```{r model loglike ex3 children}

### 2019-03-24 papers/full_paper/models.Rmd
kids model comparison first pass

--- 2019-03-20 papers/full_paper/models.Rmd
@@
 
-#### Loglike models with noise
+#### Marginal likelihoods
 
@@
 
+#### Developmental noise parameter
+
+```{r}
+child.ex3.rsa.predictions.developmental.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_pragm_model_developmental_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.developmental.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds")
+
+# model predictions
+child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "pragmatic_developmental_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_pragm_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+```{r}
+developmental_noise_parameter <- data_frame(
+  age = rep(seq(0,2, by = 0.05),1),
+  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
+                filter(Parameter == "noise_int")%>%
+                pull(mean),41)),
+  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
+                filter(Parameter == "noise_slope")%>%
+                pull(mean),41))
+) %>%
+  mutate(y = plogis(int + slope *age))
+
+ggplot(developmental_noise_parameter, aes(x = age, y= y))+
+  geom_line(size = 2)+
+  ylab("Noise Parameter")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()
+```
+
 ### Prior only model
@@
 
+## Compare model predictions to data
+
 ### Plot model predictions and data
@@
   child_ex3_pragm_model_predictions_noise,
-  child_ex3_pragm_model_predictions,
-  child_ex3_flat_prior_model_predictions,
-  child_ex3_prior_only_model_predictions
+  child_ex3_pragm_model_predictions_developmental_noise,
+  child_ex3_pragm_model_predictions
+  #child_ex3_flat_prior_model_predictions,
+  #child_ex3_prior_only_model_predictions
   )
@@
   geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1,  se = T,  alpha = .5)+
+  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
   #geom_hline(yintercept = 0.5, lty=2)+
@@
 
+### Marginal likelihoods
+
+#### Pragmatic model
+
+##### Parameter free
+
+```{r pragmatic model ex3 children}
+child.ex3.rsa.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    observe(modelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+
+'
+```
+
+```{r}
+# child_ex3_pragm_model_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
+
+child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "pragmatic")%>%
+  group_by(model)%>%
+  summarise(logP = mean(V1))
+
+```
+
+##### Noise parameter
+
+```{r}
+child.ex3.rsa.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+# child_ex3_pragm_model_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+
+child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "pragmatic_noise")%>%
+  group_by(model)%>%
+  summarise(logP = mean(V1))
+
+```
+
+##### Developmental noise parameter
+
+```{r}
+child.ex3.rsa.developmental.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+
+child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "pragmatic_developmental_noise")%>%
+  group_by(model)%>%
+  summarise(logP = mean(V1))
+
+```
+
+#### Flat prior model
+
+```{r}
+child.ex3.flat.prior.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [.5,.5,.5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+# child_ex3_flat_prior_model_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+
+child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model)%>%
+  summarise(logP = mean(V1))
+```
+
+#### Prior only model
+
+```{r}
+child.ex3.prior.only.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+# child_ex3_prior_only_model_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+
+child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model)%>%
+  summarise(logP = mean(V1))
+```
+
 ```{r model loglike ex3 children}
@@
 
-log_like_pragmatic <- child_ex3_pragm_model_predictions %>%
-  mutate(like = ifelse(correct == "1",value,1-value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
-log_like_flat_prior <- child_ex3_flat_prior_model_predictions %>%
-  mutate(like = ifelse(correct == "1",value,1-value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
-log_like_prior_only <- child_ex3_prior_only_model_predictions %>%
-  mutate(like = ifelse(correct == "1",value,1-value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(model_log_like = sum(log_like))
-
 child_ex3_model_comparison <- bind_rows(
-  log_like_pragmatic,
-  log_like_flat_prior,
-  log_like_prior_only
+  child_ex3_pragm_model_likelihood,
+ child_ex3_pragm_model_noise_likelihood,
+child_ex3_flat_prior_model_noise_likelihood,
+  child_ex3_prior_only_model_noise_likelihood
 )%>%
-  mutate(model = reorder(model,model_log_like))
+  mutate(model = reorder(model,logP))
 ```
@@
 ```{r plot model loglikes ex3 children}
-ggplot(child_ex3_model_comparison, aes(x = model, y = model_log_like, col = model))+
-  geom_segment( aes(x=model, xend=model, y=-425, yend=model_log_like), col = "black", size = 1)+
+ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
+  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
   geom_point(size = 7)+
@@
   guides(col = F)+
-  ylim(-550,-425)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#859900","#6c71c4"))
+  ylim(-475,-400)+
+  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
+                    values= c("#859900","#00afaf","#b58900","#6c71c4"))
+
 ```
@@
 ```{r bayes factors ex3 children}
-child_ex3_bf <- data.frame(
-  comparison = c("pragmatic vs. flat_prior","pragmatic vs. prior_only", "flat_rior vs. prior_only"),
-  log_bayes_factor = c(
-    log_like_pragmatic$model_log_like - log_like_flat_prior$model_log_like,
-    log_like_pragmatic$model_log_like- log_like_prior_only$model_log_like,
-    log_like_flat_prior$model_log_like - log_like_prior_only$model_log_like)
-)
+child_ex3_bf <- child_ex3_model_comparison%>%
+  spread(model, logP) %>%
+  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
+          "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
+         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
+         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
+  select(-pragmatic,-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)
 

### 2019-03-24 papers/full_paper/models.Rmd
kids model predictions and comaprison complete first pass

@@
 #### Compare model predictions to data
+
+##### Noise parameters
+
+```{r}
+ex3_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "pragmatic"),
+  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "prior_only"),
+  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "flat_prior")
+  )
+
+ggplot(ex3_noise_parameters, aes(x = value, col = model, fill = model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
 
@@
 ### Compare model predictions to data
+
+##### Noise parameters
+
+```{r}
+ex4_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "pragmatic"),
+  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "prior_only"),
+  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "flat_prior")
+  )
+
+ggplot(ex4_noise_parameters, aes(x = value, col = model, fill = model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
 
@@
 # model predictions
-child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
   filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
@@
 
-```{r}
-developmental_noise_parameter <- data_frame(
-  age = rep(seq(0,2, by = 0.05),1),
-  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
-                filter(Parameter == "noise_int")%>%
-                pull(mean),41)),
-  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
-                filter(Parameter == "noise_slope")%>%
-                pull(mean),41))
-) %>%
-  mutate(y = plogis(int + slope *age))
-
-ggplot(developmental_noise_parameter, aes(x = age, y= y))+
-  geom_line(size = 2)+
-  ylab("Noise Parameter")+
-  xlab("Age")+
-  ylim(0,1)+
-  theme_few()
-```
-
 ### Prior only model
+
+#### Parameter free
 
@@
 
+#### Noise parameter
+
+```{r}
+child.ex3.prior.only.predictions.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
+
+  var output = map(function(row){
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+```{r}
+# child_ex3_prior_only_model_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds")
+
+# model predictions
+child_ex3_prior_only_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+#### Developmental noise parameter
+
+```{r}
+child.ex3.prior.only.predictions.developmental.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+      var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_prior_only_model_developmental_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.developmental.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds")
+
+# model predictions
+child_ex3_prior_only_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
+  filter(!(Parameter %in% c("noise_int","noise_slope"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "prior_only_developmental_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
 ### Flat prior model
+
+#### Parameter free
 
@@
 
+#### Noise parameter
+
+```{r}
+child.ex3.flat.prior.predictions.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
+
+  var output = map(function(row){
+
+    var prior = [.5,.5,.5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise: noise})
+
+}
+'
+```
+
+#### Developmental noise parameter
+
+```{r}
+child.ex3.flat.prior.predictions.developmental.noise <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+    var prior = [.5,.5,.5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
+
+}, allData)
+
+ return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
+
+}
+'
+```
+
+```{r}
+# child_ex3_flat_prior_model_developmental_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.developmental.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds")
+
+# model predictions
+child_ex3_flat_prior_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
+  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "flat_prior_developmental_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
+  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
+  group_by(Parameter)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
+```{r}
+# child_ex3_flat_prior_model_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")
+
+# model predictions
+child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
 ## Compare model predictions to data
+
+### Noise parameters
+
+```{r}
+child_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "pragmatic"),
+  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "prior_only"),
+  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(model = "flat_prior")
+  )
+
+ggplot(child_noise_parameters, aes(x = value, col = model, fill = model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
+
+### Developmental noise parameters
+```{r}
+developmental_noise_parameter <- data_frame(
+  age = rep(seq(0,2, by = 0.05),3),
+  model = c(rep("pragmatic",41),
+            rep("flat_prior",41),
+            rep("prior_only",41)),
+  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
+                filter(Parameter == "noise_int")%>%
+                pull(mean),41),
+          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
+                filter(Parameter == "noise_int")%>%
+                pull(mean),41),
+          rep(child_ex3_prior_only_model_developmental_noise_param%>%
+                filter(Parameter == "noise_int")%>%
+                pull(mean),41)
+          ),
+  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
+                filter(Parameter == "noise_slope")%>%
+                pull(mean),41),
+          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
+                filter(Parameter == "noise_slope")%>%
+                pull(mean),41),
+          rep(child_ex3_prior_only_model_developmental_noise_param%>%
+                filter(Parameter == "noise_slope")%>%
+                pull(mean),41))
+) %>%
+  mutate(y = plogis(int + slope *age))
+
+ggplot(developmental_noise_parameter, aes(x = age, y= y, col = model))+
+  geom_line(size = 1)+
+  ylab("Noise parameter")+
+  xlab("Age")+
+  ylim(0,1)+
+  theme_few()+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
 
@@
   child_ex3_pragm_model_predictions_noise,
-  child_ex3_pragm_model_predictions_developmental_noise,
-  child_ex3_pragm_model_predictions
+  #child_ex3_pragm_model_predictions_developmental_noise,
+  child_ex3_pragm_model_predictions,
+  child_ex3_prior_only_model_predictions_noise,
+  child_ex3_flat_prior_model_predictions_noise
   #child_ex3_flat_prior_model_predictions,
@@
   scale_color_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
-                     values= c("#859900","#00afaf","#6c71c4","#b58900"))+
+                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
+                     values= c("#b58900","#00afaf","#6c71c4","#859900"))+
   scale_fill_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
-                     values= c("#859900","#00afaf","#6c71c4","#b58900"))
+                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
+                     values= c("#b58900","#00afaf","#6c71c4","#859900"))
 
@@
   as.tibble()%>%
-  mutate(model = "pragmatic")%>%
-  group_by(model)%>%
+  mutate(model = "pragmatic",
+         parameter = "parameter free")%>%
+  group_by(model,parameter)%>%
   summarise(logP = mean(V1))
@@
   as.tibble()%>%
-  mutate(model = "pragmatic_noise")%>%
-  group_by(model)%>%
+  mutate(model = "pragmatic",
+         parameter = "noise")%>%
+  group_by(model,parameter)%>%
   summarise(logP = mean(V1))
@@
 ```{r}
-child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  chains = 3,
-  cores = 3
-)%>%
-  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
 
@@
   as.tibble()%>%
-  mutate(model = "pragmatic_developmental_noise")%>%
-  group_by(model)%>%
+  mutate(model = "pragmatic",
+         parameter = "developmental noise")%>%
+  group_by(model,parameter)%>%
   summarise(logP = mean(V1))
@@
 
-```{r}
-child.ex3.flat.prior.noise.marginal.likelihood <-'
+##### Parameter free
+
+```{r}
+child.ex3.flat.prior.marginal.likelihood <-'
 
@@
 
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
+    observe(modelPredictions, row.correct_inf)
 
@@
 ```{r}
+# child_ex3_flat_prior_model_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+
+child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "flat_prior",
+         parameter = "parameter free")%>%
+  group_by(model,parameter)%>%
+  summarise(logP = mean(V1))
+```
+
+##### Noise parameter
+
+```{r}
+child.ex3.flat.prior.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var prior = [.5,.5,.5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
 # child_ex3_flat_prior_model_noise_likelihood<- webppl(
@@
   as.tibble()%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model)%>%
+  mutate(model = "flat_prior",
+         parameter = "noise")%>%
+  group_by(model,parameter)%>%
   summarise(logP = mean(V1))
@@
 
+##### Developmental noise parameter
+
+```{r}
+child.ex3.flat.prior.developmental.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+    var prior = [.5,.5,.5]
+
+    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+
+child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "flat_prior",
+         parameter = "developmental noise")%>%
+  group_by(model,parameter)%>%
+  summarise(logP = mean(V1))
+
+```
+
 #### Prior only model
 
-```{r}
-child.ex3.prior.only.noise.marginal.likelihood <-'
+##### Parameter free
+
+```{r}
+child.ex3.prior.only.marginal.likelihood <-'
 
@@
 ```{r}
+# child_ex3_prior_only_model_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+
+child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "prior_only",
+         parameter = "parameter free")%>%
+  group_by(model,parameter)%>%
+  summarise(logP = mean(V1))
+```
+
+##### Noise parameter
+
+```{r}
+child.ex3.prior.only.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise = uniform({a: 0, b: 1})
+
+  var output = map(function(row){
+
+    var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
 # child_ex3_prior_only_model_noise_likelihood<- webppl(
@@
   as.tibble()%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model)%>%
+  mutate(model = "prior_only",
+         parameter = "noise")%>%
+  group_by(model,parameter)%>%
+  summarise(logP = mean(V1))
+```
+
+##### Developmental noise parameter
+
+```{r}
+child.ex3.prior.only.developmental.noise.marginal.likelihood <-'
+
+var allData = dataFromR.allData
+
+var model = function(){
+
+  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
+  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
+
+  var output = map(function(row){
+
+    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
+
+    var modelPredictions = Infer({method: "enumerate", model: function(){
+      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
+      return obj.shape == "circle" ? 1 : 0
+       }})
+
+    var noisyModelPredictions = addNoise(modelPredictions, noise)
+
+    observe(noisyModelPredictions, row.correct_inf)
+
+}, allData)
+
+}
+
+var steps = 5000
+var samples = 1
+var mll = AIS(model, {steps:steps, samples: samples})
+mll
+'
+```
+
+```{r}
+# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   chains = 3,
+#   cores = 3
+# )%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+
+child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")%>%
+  as.tibble()%>%
+  mutate(model = "prior_only",
+         parameter = "developmental noise")%>%
+  group_by(model,parameter)%>%
   summarise(logP = mean(V1))
@@
   child_ex3_pragm_model_noise_likelihood,
+  child_ex3_pragm_model_developmental_noise_likelihood,
   child_ex3_flat_prior_model_noise_likelihood,
-  child_ex3_prior_only_model_noise_likelihood
+  child_ex3_flat_prior_model_likelihood,
+  child_ex3_flat_prior_model_developmental_noise_likelihood,
+  child_ex3_prior_only_model_noise_likelihood,
+  child_ex3_prior_only_model_likelihood,
+  child_ex3_prior_only_model_developmental_noise_likelihood
 )%>%
+  ungroup()%>%
   mutate(model = reorder(model,logP))
@@
   guides(col = F)+
+  facet_grid(~parameter)+
   ylim(-475,-400)+
-  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
-                    values= c("#859900","#00afaf","#b58900","#6c71c4"))
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#859900","#b58900","#6c71c4"))
 
@@
 child_ex3_bf <- child_ex3_model_comparison%>%
+  group_by(parameter)%>%
   spread(model, logP) %>%
-  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
-          "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
-         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
-         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
-  select(-pragmatic,-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)
+  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
+         "pragmatic > prior_only" = pragmatic - prior_only,
+         "flat_prior > prior_only" = flat_prior - prior_only) %>%
+  select(-pragmatic,-flat_prior, -prior_only)
 

### 2019-03-29 papers/full_paper/SI_appendix.Rmd
first draft results and methods

--- 2019-03-24 papers/full_paper/models.Rmd
@@
 ##### Noise parameter
+
+We noted that the model predictions were relatively
 
@@
   ex_3_model_pred,
-  ex3_pragm_model_pred_noise,
   adult_ex3_data_summary
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
+  labs(x="",y="Proportion more informative")+
   facet_grid (~ common_ground_manipulation + speaker) +
@@
 
-#### Loglike Parameter free model
+#### Marginal likelihoods
+
+##### Pragmatic model
+
+###### Parameter free
+
 ```{r log likes ex3 adults}
 # calculating model log-likelihoods
-log_like_pragmatic_ex3 <- adult_ex3_data %>%
-  left_join(ex3_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(logP = sum(log_like))
-```
-
-#### Loglike models with noise
-
-##### Pragmatic model 
+# log_like_pragmatic_ex3 <- adult_ex3_data %>%
+#   left_join(ex3_pragm_model_predictions)%>%
+#   mutate(like = ifelse(correct_inf == 1, value, 1 - value),
+#          log_like = log(like))%>%
+#   group_by(model)%>%
+#   summarise(logP = sum(log_like))%>%
+#   saveRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+
+log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+```
+
+###### Noise parameter
+
 ```{r model rsa noise ex3, include = FALSE}
@@
 
+###### Noise parameter
+
 ```{r model prior only noise ex3, include = FALSE}
@@
 ##### Flat prior model
+
+###### Noise parameter
 
@@
 
-#### Bayes factors
+#### Log Bayes factors
 
@@
 
+### Prior manipulation experiments
+
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+```
+
+```{r ex4 prior pre-test plots}
+p_adult_ex4_priors <- adult_ex4_prior_data%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
+  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
+  summarise(correct = mean(correct))
+
+p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
+  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="")+
+  facet_grid(common_ground_manipulation ~ prior_manipulation)+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F,size =F)+
+  scale_color_solarized()+
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
+```
+
 ### Model parameters and data
@@
 
-```{r prior pre-tests data adults}
-# load data from prior strength manipulation experiments to set priors
-adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
-```
-
 ```{r model setup ex 4}
@@
 
-strongPrior <- expand.grid(
+ex4Prior <- expand.grid(
   common_ground_manipulation = c("preference","novelty"),
@@
 
-strong_prior_summary <- adult_ex4_prior_data %>%
+ex4_prior_summary <- adult_ex4_prior_data %>%
   group_by(common_ground_manipulation, prior_manipulation, speaker) %>%
@@
 model_params_ex4 <- left_join( 
-  strongPrior, 
-  strong_prior_summary# %>% filter(prior_manipulation == "strong")
+  ex4Prior, 
+  ex4_prior_summary
 ) %>%
@@
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
+  labs(x="",y="Proportion more informative")+
   facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
@@
                      breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("black","#859900","#6c71c4","#b58900"))+
+                     values= c("black","#b58900","#6c71c4","#859900"))+
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
+
 ```
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#859900","#6c71c4"))
-```
-
-#### Bayes factors
+                    values= c("#859900","#b58900","#6c71c4"))
+```
+
+#### Log Bayes factors
 
@@
   group_by(id,trial)%>%
-        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
-                                   ifelse(speaker == "different_speaker" & alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
-                                          ifelse(speaker == "same_speaker" & alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
+        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", 
+                                   list(c(1-same_prior,1-same_prior,same_prior)),
+                                   ifelse(speaker == "different_speaker" & alignment == "congruent",
+                                          list(c(1-diff_prior,1-diff_prior,diff_prior)),
+                                          ifelse(speaker == "same_speaker" & alignment == "incongruent",
+                                                 list(c(same_prior,same_prior,1-same_prior)),
                                                  list(c(diff_prior,diff_prior,1-diff_prior))
-
                                    ))))%>%
@@
 
+```{r}
+# child_ex3_flat_prior_model_noise<- webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   model_var = "model",
+#   chains = 4,
+#   cores = 4,
+#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
+# )%>%
+#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")
+
+# model predictions
+child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise"))) %>%
+  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model, age,alignment,speaker) %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value), 
+            ci_upper =hdi_upper(value))%>%
+  ungroup()%>%
+  mutate(age = as.numeric(age))
+
+## noise parameter
+child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+```
+
 #### Developmental noise parameter
@@
   group_by(Parameter)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-```{r}
-# child_ex3_flat_prior_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")
-
-# model predictions
-child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
-child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
   summarise(mean = estimate_mode(value), 
@@
   child_ex3_pragm_model_predictions_noise,
-  #child_ex3_pragm_model_predictions_developmental_noise,
-  child_ex3_pragm_model_predictions,
-  child_ex3_prior_only_model_predictions_noise,
-  child_ex3_flat_prior_model_predictions_noise
+  child_ex3_pragm_model_predictions_developmental_noise, 
+  child_ex3_pragm_model_predictions
+  #child_ex3_prior_only_model_predictions_noise,
+  #child_ex3_flat_prior_model_predictions_noise
   #child_ex3_flat_prior_model_predictions,
@@
 ggplot(child_model_predictions)+
-  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
+  geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
   geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
   geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
+  #geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
   #geom_hline(yintercept = 0.5, lty=2)+
-  labs(y="proportion more informative")+
+  labs(y="Proportion more informative")+
   ylim(-0.05,1.05)+
-  facet_grid(speaker~alignment)+
+  facet_grid(~speaker+alignment)+
   theme_few()+
+  theme(legend.position="bottom")+
   scale_color_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("#b58900","#00afaf","#6c71c4","#859900"))+
+                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     values= c("#00afaf","#af6300","#6c71c4"))+
   scale_fill_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("#b58900","#00afaf","#6c71c4","#859900"))
+                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     values= c("#00afaf","#af6300","#6c71c4"))
 
@@
 child_cor_data <- child_ex3_data %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(speaker, alignment, age_bin) %>%
+  group_by(age_bin,speaker, alignment) %>%
   summarize(k = sum(correct_inf), n = n())%>%
@@
          b = 1 + n - k,
-         Data_ci_lower  = qbeta(.025, a, b),
-         Data_ci_upper = qbeta(.975, a, b),
-         Data = (a-1)/(a+b-2))%>%
+         data_ci_lower  = qbeta(.025, a, b),
+         data_ci_upper = qbeta(.975, a, b),
+         data_mode = (a-1)/(a+b-2))%>%
   select(-a,-b,-n,-k)
 
-child_cor_model <- child_model_predictions %>%
-  mutate(age = ifelse(age<4,"3","4"))%>%
-  group_by(model,speaker,alignment, age)%>%
-  summarise(Model = mean(mean))
+child_cor_model <- bind_rows(
+  child_ex3_pragm_model %>%
+  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
+  mutate(value = `1`,
+         model = "pragmatic_parameter_free",
+         age = ifelse(age<4,"3","4"))%>%
+    group_by(age,model,speaker,alignment)%>%
+    summarise(model_mode = estimate_mode(value),
+              model_ci_lower = hdi_lower(value), 
+              model_ci_upper =hdi_upper(value)),
+  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+    filter(!(Parameter %in% c("noise"))) %>%
+    separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+    mutate(model = "pragmatic_noise",
+           age = ifelse(age<4,"3","4"))%>%
+    group_by(age,model,speaker,alignment) %>%
+    summarise(model_mode = estimate_mode(value), 
+              model_ci_lower = hdi_lower(value), 
+              model_ci_upper =hdi_upper(value)),
+  readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
+    filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
+    separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+    mutate(model = "pragmatic_developmental_noise",
+           age = ifelse(age<4,"3","4"))%>%
+    group_by(age,model,speaker,alignment) %>%
+    summarise(model_mode = estimate_mode(value), 
+              model_ci_lower = hdi_lower(value), 
+              model_ci_upper =hdi_upper(value))
+)
 
@@
   ungroup()%>%
-  mutate(Data = rep(child_cor_data$Data,4),
-         Data_ci_lower = rep(child_cor_data$Data_ci_lower,4),
-         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,4))
-
-ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
+  mutate(data_mode = rep(child_cor_data$data_mode,3),
+         data_ci_lower = rep(child_cor_data$data_ci_lower,3),
+         data_ci_upper  =rep( child_cor_data$data_ci_upper,3))
+
+ggplot(data = child_cor_plot,aes(x = model_mode, y = data_mode, col = age)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
   geom_point(size = 3)+
-  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
   coord_fixed()+
   facet_grid(~model)+
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mode, y = data_mode), inherit.aes = F)+
   xlim(0,1)+ylim(0,1)+
@@
 
-child_ex3_model_comparison <- bind_rows(
-  child_ex3_pragm_model_likelihood,
-  child_ex3_pragm_model_noise_likelihood,
-  child_ex3_pragm_model_developmental_noise_likelihood,
-  child_ex3_flat_prior_model_noise_likelihood,
-  child_ex3_flat_prior_model_likelihood,
-  child_ex3_flat_prior_model_developmental_noise_likelihood,
-  child_ex3_prior_only_model_noise_likelihood,
-  child_ex3_prior_only_model_likelihood,
-  child_ex3_prior_only_model_developmental_noise_likelihood
-)%>%
-  ungroup()%>%
-  mutate(model = reorder(model,logP))
+# child_ex3_model_comparison <- bind_rows(
+#   child_ex3_pragm_model_likelihood,
+#   child_ex3_pragm_model_noise_likelihood,
+#   child_ex3_pragm_model_developmental_noise_likelihood,
+#   child_ex3_flat_prior_model_noise_likelihood,
+#   child_ex3_flat_prior_model_likelihood,
+#   child_ex3_flat_prior_model_developmental_noise_likelihood,
+#   child_ex3_prior_only_model_noise_likelihood,
+#   child_ex3_prior_only_model_likelihood,
+#   child_ex3_prior_only_model_developmental_noise_likelihood
+# )%>%
+#   ungroup()%>%
+#   mutate(model = reorder(model,logP))%>%
+#   saveRDS("../../stats/saves/child_ex3_model_comparison.rds")
+
+child_ex3_model_comparison <- readRDS("../../stats/saves/child_ex3_model_comparison.rds")
+
 ```
@@
 
-### Bayes factors
+### Log Bayes factors
+
+```{r}
+child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
+  filter(model == "pragmatic")%>%
+  spread(parameter, logP) %>%
+  mutate("dev. noise > noise" = `developmental noise` - noise,
+         "noise > parameter free" = noise - `parameter free`,
+         "dev. noise > parameter free" = `developmental noise` - `parameter free`) %>%
+  select(-`parameter free`,-`developmental noise`, -noise)
+
+child_ex3_pragmatic_models_bf%>%
+  kable(digits = 2)
+```
 

### 2019-03-29 papers/full_paper/manuscript.Rmd
first draft results and methods

---
title             : "Predicting the integration of social information in pragmatic word learning across development"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
    email         : "bohn@stanford.edu"
  - name          : "Michael Henry Tessler"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
  - id            : "3"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"

author_note: |
  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling"
wordcount         : "X"

bibliography      : ["library.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
# load packages and functions

knitr::opts_chunk$set(echo = F, include = F, out.width = "\\textwidth", fig.pos = "!h")

library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
#library(ggpubr)
library(lme4)
library(broom)
library(readxl)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

```{r}
# preparing datafiles (delete eventually)

# d <- read_csv(file="../../stats/data/inf.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          trial = alltrial -2,
#          experiment = "adult_ex1",
#          condition = ifelse(control == TRUE, "control", "test") )%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,  trial,condition, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex1.csv")
# 
# d <- read_csv(file="../../stats/data/novel.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_novelty",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_novelty.csv")
# 
# d <- read_csv(file="../../stats/data/pref.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_preference",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_preference.csv")
# 
# d <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
#                read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
#   distinct(id, alltrial, .keep_all = TRUE) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
# 
# exclude <- d %>%
#   filter(trial_type == "train") %>%
#   group_by(id)%>%
#   summarise(correct_inf = mean(correct_inf)) %>%
#   filter(correct_inf == 0)
# 
# d <- d%>%
#   filter(!id %in% exclude$id)%>%
#   mutate(agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(experiment == "novel_inf","novelty", "preference"),
#          experiment = "adult_ex3",
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"))%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, speaker ,alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex3.csv")
# 
# 
#
# d <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
#                ) %>%
#   distinct(id, alltrial, .keep_all = TRUE) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
#          
# exclude <- d %>%
#   filter(trial_type == "train") %>%
#   group_by(id)%>%
#   summarise(correct_inf = mean(correct_inf)) %>%
#   filter(correct_inf == 0)
# 
# d <- d%>%
#   filter(!id %in% exclude$id)%>%
#   mutate(agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(grepl("novel",experiment),"novelty", "preference"),
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"),
#          prior_manipulation = prior,
#          experiment = "adult_ex4")%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, prior_manipulation, speaker, alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex4.csv")
#
# 
# d <- bind_rows(read_csv(file="../../stats/data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
#                        read_csv(file="../../stats/data/kids_pref_2_data.csv")%>% mutate(age = subage))%>%
#   filter(trial != "train")%>%
#   mutate(age_bin = factor(age),
#          experiment = "child_ex2",
#          condition = ifelse(speakerChange == F, "same_speaker", "different_speaker"),
#          agent = ifelse( speakerChange == F, agent, altAgent),
#          id = subid,
#          minage = min(age_num))%>%
#   filter(trial != "train")%>%
#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)
# 
# write_csv(d , path="../../stats/data/child_ex2.csv")
# 
# d <- bind_rows(
#   read_csv(file="../../stats/data/kids_inf_data.csv"),
#   read_csv(file="../../stats/data/kids_inf_2_data.csv"))%>%
#   filter(subage != "2",
#          trial != "filler1",
#          trial != "filler2")%>%
#   mutate(age_bin = factor(subage),
#          experiment = "child_ex1",
#          id =subid,
#          minage = min(age_num))%>%
#   select(experiment,id,age_bin,age_num,sex,minage,trial,correct)
# 
# write_csv(d , path="../../stats/data/child_ex1.csv")
#
# d <- read_csv(file="../../stats/data/kids_ex3_data.csv")%>%
#   mutate(experiment = "child_ex3",
#          id = subid,
#          age_bin = subage,
#          speaker = Speaker,
#          alignment = Alignment,
#          minage = min(age_num))%>%
#   filter(trial != "filler1",trial != "filler2")%>%
#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)
# 
#  write_csv(d , path="../../stats/data/child_ex3.csv")

```

```{r data}
# load data files

# adults exp 1 
adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
# adults exp 2 novelty
adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
# adults exp 2 preference
adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
# adults ex3
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv")
# prior strength manipulation experiments in experiment 4
adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
# adults ex4
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv")

# children ex1
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# children ex2 preference
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
# children ex3
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

# Introduction

Language use as and learning  integration of different sources of information. Next to conventional syntax and semantics, expectations about communicative interactions play a decisive role. These expectations can be considered on two levels. on the one hand, general expectations that apply to any interlocutor. On top of this there is information that is particular to a specific speaker which is included in the common ground between interlocutors. This generates specific expectations .

Knowledge of communicative conventions such as words in a language could also be considered as (cultural) common ground information, generating certain expectations about communicative behavior

In practice, communication requires balancing and integrating these different sources of information. RSA bla bla

From a developmental perspective

took a truyl developmental perspective in a

```{r fig1, include = T, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the adult experiments. In all conditions, at test (bottom), the speaker ambiguously requested an object using a non-word (e.g. “dax”). Participants clicked on the object they thought the speaker referred to. Informativeness (Experiment 1, left) translated to making one object less frequent in context. Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker. Green plus signs represent utterances that expressed preference and red minus of dispreference (see main text for details). Experiment 3 (right) combined manipulations. When expressing e.g. preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged. Condition for Experiment 3 shown here: preference - same speaker - incongruent.", out.width="450px"}
knitr::include_graphics("./figures/fig1.png")
```

# Adults

## Assessment of general and speaker specific expectations (Experiment 1 and 2)

As a first step, we assessed whether adults make general and common ground inferences when tested separately. In experiment 1, participants could infer which object a novel word referred to by assuming that the speaker communicated in an informative way. The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig. 1A). When the speaker turned to the table with the two objects (A and B) and used an novel word to request one of them, participants could infer that the word referred to object B. This follows from the counter-factual inferences that, if the (informative) speaker would have wanted to refer to object A, they would have turned to the table with the single object, because this would have been the least ambiguous way to refer to this object. As a consequence, turning to the table with two objects most likely reflects an intention to refer to object B. In the control condition, both tables contained both objects and no inference could be made based on the speaker's behavior.

```{r fig2, include = T, fig.align = "center", fig.cap = "Results from experiment 1 and 2 for adults. For preference and novelty, control refers to a different speaker (see Fig. 1B). Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs. Dashed line indicates performance expected by chance.", out.width="250px"}
knitr::include_graphics("./figures/fig2.png")
```

```{r ex1 results}
ex1t <- adult_ex1_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(condition,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model
lm_ex1 <- glmer(correct ~ condition +
              (condition |id) + (condition |agent), 
              data = adult_ex1_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

Participants made the inference consistent with the assumption that the speaker communicated informatively: They selected object B above chance (0.5) in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, see Fig. 2) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).

```{r ex2-results}
ex2tpref <- adult_ex2_preference_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(condition,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model (maximally converging)
lm_ex2pref <- glmer(correct ~ condition +
              (1|id) + (condition |agent), 
              data = adult_ex2_preference_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

ex2tnov <- adult_ex2_novelty_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(condition,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# model
lm_ex2nov <- glmer(correct ~ condition +
              (1|id) + (condition |agent), 
              data = adult_ex2_novelty_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

In experiment 2, we tested if participants use common ground information that is specific to a speaker to infer the referent of a novel word. In the preference manipulation (Fig. 1B . left), the speaker expressed preference for one of two objects. When the speaker later used a novel word to requested an object, participants could infer the referent by assuming that the speaker was talking about the object they liked. In a control condition, a different speaker, whose preferences were unknown, made the request. Adults selected the preferred object above chance when the same speaker made the request (t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig. 2) and more so compared to when a different speaker asked for an object ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).

In the novelty manipulation (Fig 1B - right), the speaker encountered one object on one of the tables. Later, a second object appeared. The second object was therefore new to the speaker. When the same speaker later used a novel word to requested an object (in a slightly excited way), participants could infer that it was the new object they are referring to. In contrast, when a different speaker, tho whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge. In line with this reasoning, participants selected the new object above chance with the same speaker (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig. 2), and more often compared to the different speaker ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`). Taken together, experiment 1 and 2 showed that adults use general and speaker specific expectations to identify the referent of a novel word. In the following, we studied how these expectations are integrated when combined experimentally.

## Model predictions for information integration evaluated against new data (Experiment 3).

We modeled the integration of general and common ground expectations as a process of probabilistic inference. We used the results of experiment 1 and 2 to inform key parameters in the model's architecture. Within the RSA framework, general expectations that speakers (or listeners) communicate in a cooperative and informative way are reflected in the model's recursive structure. When interpreting an utterance, the hypothetical listener imagines that it was generated by a pragmatic speaker whose goal is to produce the most informative utterance. The pragmatic speaker is modeled as reasoning about what the most informative utterance would be for a naive listener, who does not know the novel words. Importantly, the utterance in this case includes not just the novel word but also the turning to one of the tables. The conditional probability that the listener interprets an utterance as referring to a particular referent is defined as:

$$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$

Here, the term $P_S(u|r_s)$ denotes the likelihood that the pragmatic speaker will produce a particular utterance $u$ to refer to a referent $r$. It is defined in terms of a utility function $U_S(u;s)$ consisting of the surprisal of $u$ for a naive listener, who interprets $u$ according its literal semantics:

$$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$

This utility is maximized in order to decide which utterance to use to communicate about a particular referent, reflecting the expectation that the speaker communicates in an informative way. The absolute strength of $P_S(u|r_s)$ depends on a scalar value, $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances (i.e. as $\alpha$ increases, the speaker is more likely to choose the most informative utterance). We used the data from experiment 1 to specify how rational participants thought speakers were in the current setup. That is, we inferred which value of $\alpha$ would generate model predictions (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in experiment 1.

We treated common ground expectations as changes in the prior probability that a particular referent is being referred to ($P_S(r_s)$ in the first equation). For example, if the speaker expresses preference for object A, and the same speaker later requests an object, then A has a higher probability of being the referent of a subsequent utterance, regardless of any additional pragmatic considerations. We used the proportions measured in experiment 2 to specify the probability distribution across referents for the different common ground manipulations (novelty or preference, same or different speaker).

With $\alpha$ and $P_S(r_s)$ fixed based on experiment 1 and 2, we generated model predictions for situations in which general and common ground expectations had to be integrated (Fig. 1C). Expectations could either be congruent or incongruent. If, for example, object A was the more informative object (unique to that table) and also the one the speaker expressed preference for, expectations were congruent. Next, the speaker who made the request could either be the same as the one in the previous interaction or a different one. Finally, common ground information could be manipulated in the form of preference or novelty. This resulted in a total of 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions for which we generated model predictions. In order to capture that behavioral data is to some extend noisy, all models included a noise parameter. Noise parameters ranged between 0 and 1 and reflect the proportion of responses that are estimated (based on the data) to be random instead of in line with model predictions. Including the noise parameter greatly improved the model fit to the data (see SI Appendix for details). We did not preregister the inclusion of a noise parameter for experiment 3 but did so for all subsequent experiments.

```{r ex3 GLMM, cache=T}
# model 
lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex3_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex3)

lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

In experiment 3, we collected new behavioral data for each of the eight conditions. Experimentally, we combined the procedures of experiment 1 and 2. The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig. 1C). We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only general expectations are considered). Before comparing responses to model predictions we fit a generalized linear mixed model (GLMM) to the data to test if participant's responses varied across conditions. Participants distinguished between congruent and incongruent trials when the speaker remained the same (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).

```{r fig3, include = T, fig.align = "center", fig.cap = "Results from experiment 3 and 4 for adults. Data and model predictions by condition for experiment 3 (A). Transparent dots show data from individual participants, diamonds represent condition means. Corrrelation between model predictions and data in experiment 3 (B), between data in experiment 3 and data for the strong prior manipulation in experiment 4 (direct replication - C) and between model predictions and data in experiment 4 (D). Coefficients and p-values are based on Pearson correlation statistics. Error bars represent 95\\% HDIs.", out.width="450px"}
knitr::include_graphics("./figures/fig3.png")
```

```{r model comparison ex3}
ex3_bf <- bind_rows(
  readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds") %>% mutate(model = "prior_only_noise"),
  readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds") %>% mutate(model = "pragmatic_noise"),
  readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds") %>% mutate(model = "flat_prior_noise")
)%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))%>%
  bind_rows(readRDS("../../stats/saves/ex3_pragm_model_loglike.rds") %>% mutate(model = "pragmatic_parameter_free"))%>%
  spread(model, logP) %>%
  mutate("pragmatic_noise_pragmatic_parameter_free" = exp(pragmatic_noise - pragmatic_parameter_free),
         "pragmatic_noise_prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
         "pragmatic_noise_flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
         "prior_only_noise_flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
  select(-pragmatic_parameter_free,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)

ex3_pragm_model_noise_param <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)
```

Model predictions were highly correlated with the average response in each condition (Fig. 3A and B). We compared the fit of the pragmatics model described above to two alternative models: the *flat prior* model ignored the speaker specific expectation and the *prior only* model ignored the informativeness inference. This analysis tests whether the trade-off between expectations in the pragmatics model captured the structure in the data better compared to models that assume that participants only consider one type of expectation at a time. Model fit was much better for the pragmatic compared to the flat prior (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both types of expectations. The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)` ). This value was considerably lower for the pragmatics model, compared to the alternative models (see SI Appendix), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.

## Replication and extension to different levels of speaker specific expectation (Experiment 4).

The goal of experiment 4 was twofold: First, to replicate the results of experiment 3 and second, to test the generalizability of the pragmatics model to a larger range of conditions. Compared to experiment 3, we manipulated the strength of the common ground expectations. For both, preference and novelty, we planned to have a strong, a medium and a weak manipulation. Expectation strength was manipulated by changing the way the speaker interacted with the objects prior to the request and measured as the proportion with which participants chose the preferred/novel object in the same speaker condition (see SI Appendix for results). For novelty, we succeeded in finding three qualitatively different manipulations. For preference, we piloted a number of manipulations but did not find a way to indicate only weak preference. Experiment 4 therefore included strong and medium manipulations for novelty and preference and a weak manipulation for novelty. The general expectation was the same as in experiment 3. For each level we crossed general and common ground expectations in the same way as in experiment 3, resulting in a total of 8 (strong) + 8 (medium) + 4 (weak) = 20 conditions. The strong manipulation was a direct replication of experiment 3. Model predictions were generated in the same way as in experiment 3.

```{r ex4 GLMMs, cache=T}
# strong

lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex4_strong)

lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex4_medium)

lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex4_weak)

lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

Again, before evaluating model predictions, we fit GLMMs to the data for each level of common ground manipulation. Participants distinguished between congruent and incongruent trials when the speaker remained the same for the strong ($\beta$ = `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`)\footnote{Here, this effect differed between novelty and preference: model term manipulation x alignment x speaker; $\beta$ = `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, p `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`} and medium ($\beta$ = `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`), but not the weak manipulation ($\beta$ = `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`, model term: `alignment x speaker` in all cases). This pattern validates our manipulations. If the speaker specific manipulation is weak, changing the speaker has no differential impact on the informativeness inference. Results from the strong manipulation in experiment 4 further replicated findings from experiment 3 (Fig. 3C).

```{r model comparison ex4}
ex4_bf <- bind_rows(
  readRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds") %>% mutate(model = "prior_only_noise"),
  readRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds") %>% mutate(model = "pragmatic_noise"),
  readRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds") %>% mutate(model = "flat_prior_noise")
)%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))%>%
  spread(model, logP) %>%
  mutate("pragmatic_noise_prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
         "pragmatic_noise_flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
         "prior_only_noise_flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
  select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)

ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)
```

Model predictions from the pragmatics model were again highly correlated with the average response in each condition (Fig. 3D). We evaluated model fit for the same models as in experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`). The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was again lower compared to the alternative models (see SI Appendix).

Summarizing experiment 3 and 4, we saw that adults flexibly integrated different expectations about a speaker in a word learning scenario. This process was best described by a model that treated information integration as a form of probabilistic inference. Next, we took a developmental perspective and studied if the same model could be used to describe children's word learning.

# Children

## Assessment of general and speaker specific expectations (Experiment 1 and 2)

We approached children's word learning in the same way as adults'. First, we measured the strength of general (informativeness) and common ground (preference) expectations and used these measurements to set model parameters. Then we generated model predictions for how expectations should be integrated. Finally, we compared model predictions to new behavioral data. In this, we took a truly developmental perspective. We sampled children continuously across the entire age range and generated model predictions for the average developmental trajectory in each condition. In all the following experiments, we tested children between 3.0 and 4.9 years of age. For experiment 1 and 2, we also tested two-year-olds but did not find sufficient evidence that they make general and/or common ground inferences in the tasks we used.

```{r child ex1 and 2 results}
#experiment 1
child_ex1t <- child_ex1_data %>%
  group_by(age_bin, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age_bin) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(age_bin,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

child_ex1_lm_data <- child_ex1_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# GLMM
child_ex1_lm <- glmer(correct ~ age_num + (1 | id), 
              data = child_ex1_lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(child_ex1_lm)

child_lm_ex1_r <- tidy(child_ex1_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

# experiment 2
child_ex2t <- child_ex2_data %>%
  group_by(condition,age_bin, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition,age_bin) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
  select(age_bin,df,t_value,p_value)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2))

# GLMM

child_ex2_lm_data <- child_ex2_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (condition*age_num | agent), 
              data = child_ex2_lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(child_ex2_lm)

child_lm_ex2_r <- tidy(child_ex2_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

Children were only tested in the test condition in experiment 1. To compare children's performance to chance level, we binned age by year. Four-year-olds selected the more informative object (i.e. the object that was unique to the location the speaker turned to) above chance (t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`). Three-year-olds, on the other hand, did not (t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`). Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig. 4). Thus, children's expectation that speakers communicate in an informative way increased with age.

In experiment 2, we assessed whether children use common ground information to identify the referent of a novel word. We tested children with the novelty as well as the preference manipulation but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty. We therefore dropped this manipulation and focused on preference for the remainder of the study.

```{r fig4, include = T, fig.align = "center", fig.cap = "Results from experiment 1 and 2 for children For preference, control refers to to the different speaker condition (see Fig. 1B). Transparent dots show data from individual participants, regression lines show fitted linear models with 95\\% CIs. Dashed line indicates performance expected by chance.", out.width="250px"}
knitr::include_graphics("./figures/fig4.png")
```

For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`), whereas three-year-olds did not (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`). However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, Fig. 4). Thus, children across the age range used common ground information to infer the referent of a novel word.

## Model predictions for information integration evaluated against new data (Experiment 3)

We used the measurements from experiment 1 and 2 to specify $\alpha$ and $P_S(r_s)$ in the pragmatics model. However, instead of setting these parameters to a single value, we used the data to infer the intercept and slope that best described the developmental trajectory for each parameter. For $P_S(r_s)$, this was done separately for the same speaker and the different speaker condition (see SI Appendix for details). These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions. As for adults, all models included a noise parameter, which was estimated based on the data.

```{r child ex3 GLMM, cache = T}
child_ex3_lm_data <- child_ex3_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
      + (speaker*alignment | id) 
      + (age_num*speaker*alignment | agent), 
      family = "binomial",
      data = child_ex3_lm_data,
      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(child_ex3_lm)

child_lm_ex3_r <- tidy(child_ex3_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

In experiment 3, we combined the procedures of experiment 1 and 2 and collected new data from children between 3.0 and 4.9 years of age in each of the four conditions (Fig. 1C). Before comparing the data to model predictions, we fit a GLMM to the data to test if children distinguished between conditions. Children's propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).

```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 3 for children. Purple lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants (A). Correlation between model predictions and condition means binned by year (B). Coefficent and p-value are based on Pearson correlation statistic. Error bars represent 95\\% HDIs.", out.width="450px"}
knitr::include_graphics("./figures/fig5.png")
```

```{r child model comparison}

child_ex3_bf <- readRDS("../../stats/saves/child_ex3_model_comparison.rds") %>%
  group_by(parameter)%>%
  spread(model, logP) %>%
  mutate("pragmatic_flat_prior" = exp(pragmatic - flat_prior),
         "pragmatic_prior_only" = exp(pragmatic - prior_only),
         "flat_prior_prior_only" = exp(flat_prior - prior_only)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

child_ex3_pragm_model_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
```

Next, we evaluated the model predictions (Fig 5A). For the correlational analysis, we binned model predictions and data by year. There was a substantial correlation between the predicted and measured average response in each age bin (Fig. 5B). For the model comparison, we treated age continuously. As for adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`). The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (see SI Appendix). The high level of inferred noise moved the model predictions in all conditions close to chance level (Fig. 5A). We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more. This analysis was not preregistered. Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age. In each case, the pragmatics model provided a better fit compared to the alternative models (flat prior: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; prior only: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`). Taken together, these results suggest that children's word learning is best described as a flexible integration of general and common ground expectations.

# Discussion

prior as change in salience

Development is reflected as change in each expectation, the process of integration is assumed to be the same. this could be changed in the future

bring down noise level for 3yo when testing between subjects?

# Methods

All experimental procedures, sample sizes and statistical analysis were pre-registered (https://osf.io/u7kxe/). Experimental stimuli, data files and analysis scripts are freely available in an online repository (https://github.com/manuelbohn/mcc).

## Participants

Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9. Experiment 1 and each manipulation of experiment 2 had *N* = 40 participants. Sample size in experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`. *N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations. Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.

Children were recruited from the floor of the Children's Discovery Museum in San Jose, California, USA. Parents gave informed consent and provided demographic information. We collected data from a total of 243 children between 3.0 and 4.9 years of age. We excluded 15 due to less than 75% of reported exposure to English, five because they responded incorrect on 2/2 training trials, three because of equipment malfunction and two because they quit before half of the test trials were completed. The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in experiment 1, *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in experiment 2 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in experiment 3.

## Experimental procedures

All experiments were framed as games in which participants would learn words from animals. They were implemented in HTML/JavaScript as a website. Adults were directed to the website via MTurk and responded by clicking objects. Children were guided through the game by an experimenter and responded by touching objects on the screen. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests. All studies started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball). Subsequent test trials in each condition were presented in a random order.

The setup of experiment 1 for adults is shown in Fig. 1A. In the beginning of each trial, the animal introduced themselves (e.g. “Hi, I’m Dog”) and then turned towards the table with the two objects. The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”). In the test condition, there was one object on the other table whereas in the control condition there were two. Participants received six trials, three per condition.

The setup for experiment 2 is shown in Fig. 1B. In the preference manipulation, the animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude. Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead. This procedure was the strong preference manipulation. In the medium version, the animal only expressed preference and did so in a more subtle way (simply saying: "Oh, wow").

In the novelty manipulation one of the tables was initially empty. The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm..., nothing there”) of an object before turning to the other side and commenting in a complementary way. After shortly disappearing, the same animal repeated the sequence above. When the animal left a second time, a new object appeared on the empty table. Next, either the same or a different animal returned and requested an object. This corresponded to the strong manipulation. For the medium manipulation, the animal turned to each table only once before the new object appeared. In the weak manipulation, the animal only commented on the present object once and never turned to the empty table. Participants always received six trials, three with the same and three with the different speaker.

For experiment 3 and 4 we inserted the common ground manipulation before the request in the setup of experiment 1 (Fig. 1C). For example, the animal turned to the table with one object and express that they liked object A, then turned to the other table and express that they did not like object B. Next, after quickly disappearing, the animal reappeared, turned to the table with two objects and make a request. To make it clear, which of the objects the speaker commented on while being turned to the table with the two objects during the common ground manipulation, the object was temporarily enlarged. Participants completed eight trials for one of the common ground manipulations with two  trials per condition (same/different speaker x congruent/incongruent).

Experiment 1 for children was modeled after @frank2014inferring. Instead of on tables, objects were presented as hanging in trees. After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”). Next, the trees and the objects in them disappeared and new trees replaced them. The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced). While facing straight, the animal first said "Here are some more trees" and then asked the child to pick the tree with the object that corresponded to the novel word ("Which of these trees has a [non-word]"). Children received six trials in a single test condition.

Experiment 2 for children was identical to the strong preference manipulation for adults. Children received eight trials, four with the same and four with a different animal returning.

In experiment 3 for children, we again inserted the preference manipulation into the setup of experiment 1. After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking. Then the animal turned to the other tree and expressed the other attitude for the other kind of object. Next, the animal disappeared and either the same or a different animal returned. The rest of the trial was identical to the label and request phase of experiment 1. Children received eight trials, two per condition (same/different speaker x congruent/incongruent).

## Analysis

All analysis were run in R [@R-base]. GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4]. Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl]. The flat prior model had the same structure as the pragmatics model but used a uniform prior over objects. The prior only model predicted choice based on the prior probability for each object alone. Note that the proportions that informed the prior distribution in the pragmatics and prior only model were measured when participants chose between two objects in experiment 2. In experiment 3, however, three objects were involved. For each object we used the proportion measured in experiment 2 as the prior probability. This approach spread out the absolute probability mass but conserved the relative relation between objects. Bayes Factors for model comparisons are based on marginal likelihoods of each model given the data. The corresponding model code can be found in the associated online repository.

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-03-29 stats/adults/ex3_2_variable_priors_comparison.Rmd
first draft results and methods

@@
 
-dat <- bind_rows(read_csv(file="ex3.2.novel.strong.data.csv"),
-               read_csv(file="ex3.2.novel.medium.data.csv"),
-               read_csv(file="ex3.2.novel.weak.data.csv"),
-               read_csv(file="ex3.2.pref.strong.data.csv"),
-               read_csv(file="ex3.2.pref.medium.data.csv")
+dat <- bind_rows(read_csv(file="../data/ex3.2.novel.strong.data.csv"),
+               read_csv(file="../data/ex3.2.novel.medium.data.csv"),
+               read_csv(file="../data/ex3.2.novel.weak.data.csv"),
+               read_csv(file="../data/ex3.2.pref.strong.data.csv"),
+               read_csv(file="../data/ex3.2.pref.medium.data.csv")
                ) %>%
@@
   filter(Prior == "Strong") %>%
-  mutate(item = ifelse( change == "false", agent, altAgent))
+  mutate(item = ifelse( change == "same", agent, altAgent))
 
@@
   filter(Prior == "Medium") %>%
-  mutate(item = ifelse( change == "false", agent, altAgent))
+  mutate(item = ifelse( change == "same", agent, altAgent))
 
@@
   filter(Prior == "Weak") %>%
-  mutate(item = ifelse( change == "false", agent, altAgent))
+  mutate(item = ifelse( change == "same", agent, altAgent))
 

### 2019-03-29 papers/full_paper/manuscript.Rmd
first draft results and methods

@@
 
-Participants made the inference consistent with the assumption that the speaker communicated informatively: They selected object B above chance (0.5) in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, see Fig.
+Participants made the inference consistent with the assumption that the speaker communicated informatively: They selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, see Fig.
 2) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).

### 2019-04-03 papers/full_paper/SI_appendix.Rmd
first draft full paper

@@
   xlab("Model")+
+  ylab("Data")+
   theme_few() + 

### 2019-04-03 papers/full_paper/manuscript.Rmd
first draft full paper

@@
 ---
-title             : "Predicting the integration of social information in pragmatic word learning across development"
+title             : "Predicting information integration in pragmatic word learning across development"
 
@@
 author_note: |
-  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229.
+  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+We thank Jacqueline Quirke, Sabina Zacco and especially Megan Merrick for help with the data collection.
 
 abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
+  Language is used and learned in complex social settings.
+To infer what a speaker means, listeners have to go beyond the literal meaning of words and rely on pragmatic inferences.
+During language acquisition, the same processes can help children to learn the meaning of novel words.
+Yet, pragmatic inferences require balancing multiple sources of social information.
+Here we study this integration process.
+We isolate two types of pragmatic inference and formalize how they should be integrated in a Bayesian pragmatics model.
+We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.
 
@@
 
-Language use as and learning  integration of different sources of information.
-Next to conventional syntax and semantics, expectations about communicative interactions play a decisive role.
-These expectations can be considered on two levels.
-on the one hand, general expectations that apply to any interlocutor.
-On top of this there is information that is particular to a specific speaker which is included in the common ground between interlocutors.
-This generates specific expectations .
+Language use and language learning require integrating and balancing different sources of information.
+And even though linguistic cues, such as conventional syntax and semantics, may provide strong evidence about the intended meaning of an utterance, additional pragmatic inferences are necessary arrive at a precise interpretation [@levinson2000presumptive; @sperber2001relevance].
+A second route to meaning is even more important in the process of language learning.
+In this case, inferences based on the social embedding of the utterance are key to understanding its meaning and learning the words contained therein [@clark2009first; @tomasello2009constructing].
+In this paper, we explore how different forms of social information are integrated during word learning across development.
+More specifically, we look at information integration as a form of probabilistic inference.
 
-Knowledge of communicative conventions such as words in a language could also be considered as (cultural) common ground information, generating certain expectations about communicative behavior
+Pragmatic inferences rest on assumptions about how communication *should* proceed.
+Interlocutors mutually expect each other to communicate in a cooperative way and this mutual expectation serves as the basis for inferences that go beyond the literal meaning of an utterance [@grice1991studies; @sperber2001relevance; @tomasello2008origins].
+Paul Grice [-@grice1991studies] famously summarized this notion in his *Cooperative Principle*, which reads: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Two sets of expectations follow from this principle.
+On the one hand, there is the general expectation that one follows the principle and communicates in a relevant and informative way.
+On the other hand, there is the expectation that communication is further specific to the communicative partner, that is, that it is adjusted to the the common ground shared between speaker and listener [@bohn2018common; @clark1996using].
 
-In practice, communication requires balancing and integrating these different sources of information. RSA bla bla
+Importantly, these expectations can also support language development [@clark2009first; @tomasello2009constructing].
+Starting in infancy, children generally expect adults' communicative acts to provide them with relevant information [e.g @behne2005one].
+And preschool children learn novel words by assuming that speakers are informative [@frank2014inferring].
+In the absence of any additional information about the potential referent objects or the speaker, children expected a novel word to be intended to refer to an object it describes in a unique way [see also @stiller2015ad].
+Person specific common ground information supports communication in infancy [e.g.
+@bohn2018social; @saylor2011s] and facilitates word learning in slightly older children.
+For example, two-year-olds keep track of which object is new to a speaker to decide which object the speaker is referring to when they use a novel word [@akhtar1996role; @diesendruck2004two].
+Furthermore, when three to five year old children learn about a speaker's preference, they later use this information to identify the meaning of an unknown word coming from the same speaker [@saylor2009preschoolers].
+These studies suggest early emerging pragmatic competences.
+Yet, communicative interactions in naturalistic contexts have multiple layers and require balancing expectations [@clark1996using].
+So how are different expectations integrated?
 
-From a developmental perspective
+The Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic] offers a formal framework for addressing this integration problem.
+RSA models are characterized by their recursive structure.
+Each agent in the recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
+The expectation that speakers communicate informatively is already encoded in the structure of the model: Speakers choose utterances that help listeners in disambiguating referents.
+Common ground information can be integrated in the model as a shared prior probability of referents in the context of the utterance.
+Thus, a natural locus for information integration within RSA models is the trade off between the prior probability of a referent and the likelihood of that referent given the current utterance.
 
-took a truyl developmental perspective in a
+Here we apply this rational, pragmatic account of communication to the study of information integration during word learning.
+We do so from a developmental perspective and include children, continuously sampled between three and five years of age, as well as adults.
+For both groups, we first test speaker-specific and common ground expectations independently.
+Based on this data, we generate model predictions about how expectations should be integrated.
+Finally, we compare these predictions to newly collected data and use model comparisons to test different hypothesis about how expectations are integrated.
 
@@
 When the same speaker later used a novel word to requested an object (in a slightly excited way), participants could infer that it was the new object they are referring to.
-In contrast, when a different speaker, tho whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge.
+In contrast, when a different speaker, to whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge.
 In line with this reasoning, participants selected the new object above chance with the same speaker (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig.
@@
 
-prior as change in salience
+Integrating different sources of information is an integral part of human communication.
+To infer the intended meaning of an utterance, listeners combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
+When learning new words, social information is especially vital.
+But how are different social expectations integrated during word learning?
+Here we explored the hypothesis that information integration is a process of probabilistic inference.
+We studied how expectations that speakers communicate in an informative way are contextualized by expectations that follow from prior interactions with the speaker.
+Across development, participants' learning was best predicted by a Bayesian pragmatics model in which expectations were flexibly traded-off between one another in a probabilistic way.
+Alternative models, which considered only one type of expectation, made worse predictions.
 
-Development is reflected as change in each expectation, the process of integration is assumed to be the same. this could be changed in the future
+The pragmatics model goes beyond simply weighing expectations by some ratio.
+It offers an explicit account about how integration may proceed: Because all objects are new and their labels unknown, the initial probability of each object depends entirely on common ground information.
+Now, the listener assumes the speaker to produce their utterance based on the expected effect that their utterance will have *in light of* this shared common ground.
+Thus, inferences are not computed separately but the result of an integrated process.
 
-bring down noise level for 3yo when testing between subjects?
+In the current model, common ground information was treated in the same way as contextual salience [see e.g.
+@frank2012predicting].
+Interacting around an object changed the probability that this object will be communicated about.
+In theory, similar changes could be brought about by increasing the object's perceptual salience.
+Future work could try to explicitly model the social-cognitive processes that gave rise to common ground expectations and contrast social and perceptual salience.
+
+We conceptualized developmental change as age related changes in the propensity to make the individual inferences.
+That is, while the degree to which listeners expect speakers to be informative or follow common ground changes with age, the process by which expectations are integrated remains the same.
+This is a very parsimonious conception of developmental change and others, in which the integration process itself changes with age, are also plausible and worth exploring.
+
+Studying how multiple types of social information are balanced contributes to a comprehensive and ecologically valid model of word learning.
+In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information.
+However, in addition to social information, children can use semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [e.g.
+@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
+The everyday learning environment is complex and combines non-linguistic, linguistic as well as pragmatic cues.
+Across development, children learn to recruit these different sources of information and integrate them.
+Our studies show how computational models of language use and comprehension can be used as powerful tools to explicate and test hypothesis about how integration proceeds.
 

### 2019-04-03 papers/full_paper/manuscript.Rmd
first draft full paper

@@
 In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information.
-However, in addition to social information, children can use semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [e.g.
-@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
-The everyday learning environment is complex and combines non-linguistic, linguistic as well as pragmatic cues.
+However, the real learning environment is much richer than the what we captured in our experimental design.
+In addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
 Across development, children learn to recruit these different sources of information and integrate them.

### 2019-04-05 papers/full_paper/manuscript.Rmd
first draft full paper
prune frequentist models to avoid singular fit

@@
 Here we study this integration process.
-We isolate two types of pragmatic inference and formalize how they should be integrated in a Bayesian pragmatics model.
+We isolate two types of pragmatic inference and formalize how they should be integrated according to a Bayesian pragmatics model.
 We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.
@@
 lm_ex1 <- glmer(correct ~ condition +
-              (condition |id) + (condition |agent), 
+              (1 |id) , 
               data = adult_ex1_data, 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex1)
 
@@
 lm_ex2pref <- glmer(correct ~ condition +
-              (1|id) + (condition |agent), 
+              (1|id), 
               data = adult_ex2_preference_data, 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2pref)
 
@@
 lm_ex2nov <- glmer(correct ~ condition +
-              (1|id) + (condition |agent), 
+              (condition|id), 
               data = adult_ex2_novelty_data, 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2nov)
 
@@
 # model 
-lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
+lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
               data = adult_ex3_data, family = binomial, 
@@
 
-lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
+lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
               data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
@@
 
-lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
+lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
               data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
@@
 
-lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id) + (speaker+alignment|agent), 
+lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
               data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
@@
 child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
-      + (speaker*alignment | id) 
-      + (age_num*speaker*alignment | agent), 
+      + (speaker+alignment | id), 
       family = "binomial",
@@
 
-#summary(child_ex3_lm)
+summary(child_ex3_lm)
 

### 2019-04-15 papers/cogsci2019/cogsci2019.Rmd
clean up repo

@@
 # data ex 1 and ex 2
-  d1 <- bind_rows(read_csv(file="../../stats/data/novel.data.csv"),
-               read_csv(file="../../stats/data/pref.data.csv")) %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         control = ifelse(change == TRUE, "true" , "false"))
 
-d2 <- read_csv(file="../../stats/data/inf.data.csv") %>%
-  mutate(trial_type = ifelse(trial == "train", "train", "test"),
-         control = ifelse(control == TRUE, "true", "false"))
+adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
+# adults exp 2 novelty
+adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
+# adults exp 2 preference
+adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
 
-dex12 <- bind_rows(d1,d2) %>%
-  filter(trial_type == "test")%>%
-  mutate(control= relevel(factor(control), ref = "true"),
-         choiceAgent = ifelse( control == "false", agent, altAgent)) # re-code agent for preference and novelty
+dex12 <- bind_rows(
+    adult_ex1_data,
+    adult_ex2_novelty_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")),
+    adult_ex2_preference_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")))
 
 # data ex 3
-d3 <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
-               read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+dex3 <- read_csv(file="../../stats/data/adult_ex3.csv")
 
-# check if someone did both experiments
-# yes, two people
-x <- d3 %>%
-  filter(trial_type == "train")%>%
-  group_by(id)%>%
-  summarise(n = length(correct_inf)) %>%
-  filter(n > 2)
+# data ex 4
 
-# exclude those who did both experiments
-dex3 <- d3 %>%
-  filter(!id %in% x$id) %>%
-  mutate(Speaker = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Prior = ifelse(experiment == "pref_inf", "Preference", "Novelty"),
-         choiceAgent = ifelse (change == "same", agent, altAgent))%>%
-  filter(trial_type == "test")
-
-d4 <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
-               read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
-               ) %>%
-  mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
-
-x <- d4 %>%
-  filter(trial_type == "train") %>%
-  group_by(id)%>%
-  summarise(correct_inf = mean(correct_inf)) %>%
-  filter(correct_inf == 0)
-
-dex4 <- d4 %>%
-  filter(!id %in% x$id)%>% 
-  distinct(id, alltrial, .keep_all = TRUE) %>%
-  filter(trial_type != "train") %>%
-  mutate(Change = ifelse(change =="same", "Same speaker", "Different speaker"),
-         Alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"),
-         Experiment = ifelse(grepl("pref",experiment), "Preference", "Novelty"),
-         Prior = ifelse(prior == "weak", "Weak", ifelse(prior == "medium", "Medium", "Strong"))
-         )
+dex4 <- read_csv(file="../../stats/data/adult_ex4.csv")
 
@@
 ex1t <- dex12 %>%
-  filter(condition == "informativeness")%>%
-  group_by(control, id) %>%
+  filter(experiment == "adult_ex1")%>%
+  group_by(condition, id) %>%
   summarise(correct = mean(correct)) %>%
   summarise(correct = list(correct)) %>%
-  group_by(control) %>%
+  group_by(condition) %>%
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
@@
          p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(control,df,t_value,p_value)%>%
+  select(condition,df,t_value,p_value)%>%
   mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
@@
 # model
-lm_ex1 <- glmer(correct ~ control +
-              (control |id) + (control |agent), 
-              data = dex12%>%filter(condition == "informativeness"), 
+lm_ex1 <- glmer(correct ~ condition +
+              (1 |id), 
+              data = dex12%>%filter(experiment == "adult_ex1"), 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
@@
 
-Participants selected the less frequent object above chance in the test condition (t(`r ex1t%>%filter(control == "false")%>%pull(df)`) = `r ex1t%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex1t%>%filter(control == "false")%>%pull(p_value)`, see Fig.
-\ref{fig:plotexp12}) and did so more often compared to the control condition (generalized linear mixed model (GLMM\footnote{All models included random effects for subject and speaker.}):*$\beta$* = `r ex1_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "controlfalse")%>%pull(std.error)` *p* `r ex1_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Participants selected the less frequent object above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, see Fig.
+\ref{fig:plotexp12}) and did so more often compared to the control condition (generalized linear mixed model (GLMM\footnote{All models had maximal random effects structure conditional on model convergence.}):*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)` *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
 This result replicates earlier work [@frank2014inferring] and is consistent with the hypothesis that listeners expect speakers to communicate in an informative way.
@@
 p1 <- dex12 %>%
-  filter(trial_type == "test") %>%
-  mutate(control = ifelse(control == "true", "Control", "Test"),
-         condition = factor(condition), 
-         experiment = ifelse(condition == "informativeness", "1","2"))%>%
-  group_by(experiment,condition ,control, id) %>%
+  mutate(condition = ifelse(condition == "control", "Control", "Test"),
+         condition = factor(condition))%>%
+  group_by(experiment,condition , id) %>%
   summarise(correct = mean(correct))
@@
  ggplot() +
-  geom_jitter(data = p1, aes(x = control, y = correct, col = control), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p2, aes(x = control, y = mean, col = control,ymin = ci_lower, ymax = ci_upper),size = .5)+
+  geom_jitter(data = p1, aes(x = condition, y = correct, col = condition), alpha = 0.2, width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = condition, y = mean, col = condition,ymin = ci_lower, ymax = ci_upper),size = .5)+
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Expected Choice")+
-  facet_wrap( ~ condition, labeller = as_labeller(c(`preference`="Exp. 2 - Pref.", `novelty`="Exp. 2 - Nov.", `informativeness`="Exp. 1 - Inf.")))+
+  facet_wrap( ~ experiment, labeller = as_labeller(c(`adult_ex2_preference`="Exp. 2 - Pref.", `adult_ex2_novelty`="Exp. 2 - Nov.", `adult_ex1`="Exp. 1 - Inf.")))+
   theme_few(base_size = 10) + 
@@
 ex2tpref <- dex12 %>%
-  filter(condition == "preference")%>%
-  group_by(control, id) %>%
+  filter(experiment == "adult_ex2_preference")%>%
+  group_by(condition, id) %>%
   summarise(correct = mean(correct)) %>%
   summarise(correct = list(correct)) %>%
-  group_by(control) %>%
+  group_by(condition) %>%
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
@@
 # model (maximally converging)
-lm_ex2pref <- glmer(correct ~ control +
-              (1|id) + (control |choiceAgent), 
-              data = dex12%>%filter(condition == "preference"), 
+lm_ex2pref <- glmer(correct ~ condition +
+              (1|id), 
+              data = dex12%>%filter(experiment == "adult_ex2_preference"), 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
@@
 ex2tnov <- dex12 %>%
-  filter(condition == "novelty")%>%
-  group_by(control, id) %>%
+  filter(experiment == "adult_ex2_novelty")%>%
+  group_by(condition, id) %>%
   summarise(correct = mean(correct)) %>%
   summarise(correct = list(correct)) %>%
-  group_by(control) %>%
+  group_by(condition) %>%
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
@@
 # model
-lm_ex2nov <- glmer(correct ~ control +
-              (1|id) + (control |choiceAgent), 
-              data = dex12%>%filter(condition == "novelty"), 
+lm_ex2nov <- glmer(correct ~ condition +
+              (condition|id), 
+              data = dex12%>%filter(experiment == "adult_ex2_novelty"), 
               family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
@@
 
-Participants selected the preferred object above chance when the same animal returned (t(`r ex2tpref%>%filter(control == "false")%>%pull(df)`) = `r ex2tpref%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "false")%>%pull(p_value)`, see Fig.
-\ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Participants selected the preferred object above chance when the same animal returned (t(`r ex2tpref%>%filter(condition == "test")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "test")%>%pull(p_value)`, see Fig.
+\ref{fig:plotexp12}) and did so more often compared to trials in which a different animal returned (GLMM: $\beta$ = `r ex2pref_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
 Thus, listeners inferred the referent of the utterance by considering previous interactions with the speaker.
-Interestingly, participants transferred preference to some extent from one animal to the other and selected the preferred object above chance when a different animal returned (t(`r ex2tpref%>%filter(control == "true")%>%pull(df)`) = `r ex2tpref%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(control == "true")%>%pull(p_value)`).
+Interestingly, participants transferred preference to some extent from one animal to the other and selected the preferred object above chance when a different animal returned (t(`r ex2tpref%>%filter(condition == "control")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "control")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "control")%>%pull(p_value)`).
 In sum, this study shows that adults make comparable inferences to children [@saylor2009preschoolers].
 
-The novel object was selected above chance when the same animal returned (t(`r ex2tnov%>%filter(control == "false")%>%pull(df)`) = `r ex2tnov%>%filter(control == "false")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "false")%>%pull(p_value)`) but not when a different one appeared (t(`r ex2tnov%>%filter(control == "true")%>%pull(df)`) = `r ex2tnov%>%filter(control == "true")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(control == "true")%>%pull(p_value)`, see Fig.
+The novel object was selected above chance when the same animal returned (t(`r ex2tnov%>%filter(condition == "test")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "test")%>%pull(p_value)`) but not when a different one appeared (t(`r ex2tnov%>%filter(condition == "control")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "control")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "control")%>%pull(p_value)`, see Fig.
 \ref{fig:plotexp12}).
-Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "controlfalse")%>%pull(p.value)`).
+Furthermore, the two conditions differed in the expected direction ($\beta$ = `r ex2nov_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
 Thus, like children [@akhtar1996role], adults used their prior information about the speaker to resolve ambiguity in the utterance.
@@
 p3 <- dex3 %>%
-  group_by(Prior,Speaker ,Alignment, id) %>%
+  mutate(common_ground_manipulation = paste0(toupper(substr(common_ground_manipulation, 1, 1)), substr(common_ground_manipulation, 2, nchar(common_ground_manipulation))),
+         speaker = paste0(toupper(substr(speaker, 1, 1)), substr(speaker, 2, nchar(speaker))),
+         speaker = str_replace(speaker, "_", " "),
+         alignment = paste0(toupper(substr(alignment, 1, 1)), substr(alignment, 2, nchar(alignment))))%>%
+  group_by(common_ground_manipulation,speaker ,alignment, id) %>%
   summarise(correct = mean(correct_inf))
@@
   #geom_rect(data = p4, aes(fill = NA), color = "#859900", size = 2.5, alpha = 0.4 ,xmin = -Inf,xmax = Inf, ymin = -Inf,ymax = Inf)+
-  geom_jitter(data = p3, aes(x = Alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
-  geom_pointrange(data = p4, aes(x = Alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .5)+
+  geom_jitter(data = p3, aes(x = alignment, y = correct), alpha = 0.2, width = .3,height = .025)+
+  geom_pointrange(data = p4, aes(x = alignment, y = mean,ymin = ci_lower, ymax = ci_upper),size = .5)+
   geom_hline(yintercept = 0.5, lty=2)+
   labs(x="",y="Choosing More Informative")+
-  facet_grid ( ~ Prior + Speaker) +
+  facet_grid ( ~ common_ground_manipulation + speaker) +
   theme_few(base_size = 10) + 
@@
 ex3_tab <- dex3 %>%  
-  filter(trial_type == "test") %>%
-  group_by(Speaker ,Prior,Alignment, id) %>%
+  group_by(speaker ,common_ground_manipulation,alignment, id) %>%
   summarise(correct_inf = mean(correct_inf)) %>%
   summarize(correct_inf = list(correct_inf)) %>%
-  group_by(Speaker ,Prior,Alignment) %>%
+  group_by(speaker ,common_ground_manipulation,alignment) %>%
   mutate(M = mean(unlist(correct_inf)),
@@
          p = wilcox.exact(unlist(correct_inf), mu = 0.5)$p.value) %>%
-  select(Prior,Alignment, Speaker, M , W,p)%>%
+  select(speaker ,common_ground_manipulation,alignment, M , W,p)%>%
   mutate(M = round(M,2),
@@
 
-```{r ex3_results, cache=T}
+```{r ex3_results, cache=F}
 # model 
-lm_ex3 <- glmer(correct_inf ~ Prior*Speaker*Alignment + (Speaker+Alignment|id) + (Speaker+Alignment|choiceAgent), 
+lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
               data = dex3, family = binomial, 
@@
 \ref{fig:plotexp3}.
-Combinations of alignment and speaker identity differed in how they influenced participants’ responses (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "SpeakerSame speaker:AlignmentIncongruent")%>%pull(p.value)`).
+Combinations of alignment and speaker identity differed in how they influenced participants’ responses (GLMM model term: `alignment*speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
 Fig.
@@
 
-In our model, we treated common ground expectations as equivalent to more basic manipulations of contextual salience [e.g.
+A range probabilistic frameworks been used to model word learning [e.g.
+@fazly2010probabilistic; @frank2009using; @xu2007word].
+RSA models differ from other approaches in that they treat word learning as the outcome of a social reasoning process.
+In contrast to models for cross-situational word learning [@fazly2010probabilistic; @frank2009using], RSA models show how learning might occur in a one shot scenario based on pragmatic reasoning alone.
+While the ad hoc informativeness inference characteristic for RSA would be predicted by the model of Xu and Tenenbaum [-@xu2007word], in their work it follows from the "size principle" of generalization [@tenenbaum2001generalization] and not from social reasoning.
+In cotrast to RSA, this approach does not offer a straightforward way to incorporate other types of social information such as expectations following from common ground.
+
+We treated common ground expectations as equivalent to more basic manipulations of contextual salience [e.g.
 in @frank2012predicting] and did not explicitly model the social-cognitive processes that give rise to these expectations.
@@
 
-This work integrates different perspectives on the study of pragmatic inference.
+Our work integrates different perspectives on the study of pragmatic inference.
 Previous work focused either on general or speaker specific expectations.
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em}
 
 # Acknowledgements
-
-Masked for peer review.
 

### 2019-04-15 papers/cogsci2019/cogsci2019.tex
kids model prediction with replication data
clean up repo

@@
 % KM added 1/4/18 to allow control of blind submission
+\cogscifinalcopy
 
@@
 condition (generalized linear mixed model
-(GLMM\footnote{All models included random effects for subject and speaker.}):\emph{\(\beta\)}
-= 1.49, se = 0.5 \emph{p} = .003). This result replicates earlier work
-(Frank \& Goodman, 2014) and is consistent with the hypothesis that
-listeners expect speakers to communicate in an informative way.
+(GLMM\footnote{All models had maximal random effects structure conditional on model convergence.}):\emph{\(\beta\)}
+= 1.28, se = 0.29 \emph{p} \textless{} .001). This result replicates
+earlier work (Frank \& Goodman, 2014) and is consistent with the
+hypothesis that listeners expect speakers to communicate in an
+informative way.
 
@@
 \ref{fig:plotexp12}) and did so more often compared to trials in which a
-different animal returned (GLMM: \(\beta\) = 2.97, se = 0.7, \emph{p}
+different animal returned (GLMM: \(\beta\) = 2.92, se = 0.56, \emph{p}
 \textless{} .001). Thus, listeners inferred the referent of the
@@
 Furthermore, the two conditions differed in the expected direction
-(\(\beta\) = 1.7, se = 0.39, \emph{p} \textless{} .001). Thus, like
-children (Akhtar et al., 1996), adults used their prior information
-about the speaker to resolve ambiguity in the utterance.
+(\(\beta\) = 6.27, se = 1.96, \emph{p} = .001). Thus, like children
+(Akhtar et al., 1996), adults used their prior information about the
+speaker to resolve ambiguity in the utterance.
 
@@
 identity differed in how they influenced participants' responses (GLMM
-model term: \texttt{alignment*speaker}; \(\beta\) = -2.92, se = 0.57,
+model term: \texttt{alignment*speaker}; \(\beta\) = -2.64, se = 0.48,
 \emph{p} \textless{} .001). Fig. \ref{fig:plotmodelcomp}A shows the mean
@@
 
-In our model, we treated common ground expectations as equivalent to
-more basic manipulations of contextual salience (e.g.~in Frank \&
-Goodman, 2012) and did not explicitly model the social-cognitive
-processes that give rise to these expectations. The interaction around
-the object prior to the test event simply increased the probability that
-this particular speaker will refer to the object subsequently. The same
-change could be brought about if one of the objects would be made
-perceptually more salient, for example by making it flash. In future
-work, it would be interesting to explore ways to model common ground
-expectations explicitly as well as to contrast perceptual and
-interactional salience.
+A range probabilistic frameworks been used to model word learning (e.g.
+Fazly, Alishahi, \& Stevenson, 2010; Frank, Goodman, \& Tenenbaum, 2009;
+Xu \& Tenenbaum, 2007). RSA models differ from other approaches in that
+they treat word learning as the outcome of a social reasoning process.
+In contrast to models for cross-situational word learning (Fazly et al.,
+2010; Frank et al., 2009), RSA models show how learning might occur in a
+one shot scenario based on pragmatic reasoning alone. While the ad hoc
+informativeness inference characteristic for RSA would be predicted by
+the model of Xu and Tenenbaum (2007), in their work it follows from the
+``size principle'' of generalization (Tenenbaum \& Griffiths, 2001) and
+not from social reasoning. In cotrast to RSA, this approach does not
+offer a straightforward way to incorporate other types of social
+information such as expectations following from common ground.
 
-This work integrates different perspectives on the study of pragmatic
+We treated common ground expectations as equivalent to more basic
+manipulations of contextual salience (e.g.~in Frank \& Goodman, 2012)
+and did not explicitly model the social-cognitive processes that give
+rise to these expectations. The interaction around the object prior to
+the test event simply increased the probability that this particular
+speaker will refer to the object subsequently. The same change could be
+brought about if one of the objects would be made perceptually more
+salient, for example by making it flash. In future work, it would be
+interesting to explore ways to model common ground expectations
+explicitly as well as to contrast perceptual and interactional salience.
+
+Our work integrates different perspectives on the study of pragmatic
 inference. Previous work focused either on general or speaker specific
@@
 
+\vspace{1em}
+\fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}}
+\vspace{1em}
+
 \section{Acknowledgements}\label{acknowledgements}
 
-Masked for peer review.
+MB received funding from the European Union's Horizon 2020 research and
+innovation programme under the Marie Sklodowska-Curie grant agreement No
+749229.
 
@@
 
+\hypertarget{ref-fazly2010probabilistic}{}
+Fazly, A., Alishahi, A., \& Stevenson, S. (2010). A probabilistic
+computational model of cross-situational word learning. \emph{Cognitive
+Science}, \emph{34}(6), 1017--1063.
+
 \hypertarget{ref-frank2012predicting}{}
@@
 \emph{75}, 80--96.
+
+\hypertarget{ref-frank2009using}{}
+Frank, M. C., Goodman, N. D., \& Tenenbaum, J. B. (2009). Using
+speakers' referential intentions to model early cross-situational word
+learning. \emph{Psychological Science}, \emph{20}(5), 578--585.
 
@@
 
+\hypertarget{ref-tenenbaum2001generalization}{}
+Tenenbaum, J. B., \& Griffiths, T. L. (2001). Generalization,
+similarity, and bayesian inference. \emph{Behavioral and Brain
+Sciences}, \emph{24}(4), 629--640.
+
 \hypertarget{ref-tomasello2009constructing}{}
@@
 
+\hypertarget{ref-xu2007word}{}
+Xu, F., \& Tenenbaum, J. B. (2007). Word learning as bayesian inference.
+\emph{Psychological Review}, \emph{114}(2), 245.
+
 \bibliographystyle{apacite}

### 2019-04-15 papers/full_paper/manuscript.Rmd
clean up repo

@@
 lm_ex2pref <- glmer(correct ~ condition +
-              (1|id), 
+              (1|id) + (1|agent), 
               data = adult_ex2_preference_data, 
@@
 
-```{r ex3 GLMM, cache=T}
+```{r ex3 GLMM, cache=F}
 # model 
@@
 
-```{r ex4 GLMMs, cache=T}
+```{r ex4 GLMMs, cache=F}
 # strong
@@
 
-```{r child ex3 GLMM, cache = T}
+```{r child ex3 GLMM, cache = F}
 child_ex3_lm_data <- child_ex3_data%>%

### 2019-04-15 stats/simulations/power_analysis.r

@@ -1,197 +1,0 @@
-library(lme4)
-source("X:/Statistics/R scripts/Roger/intercept_optimization.r")
-n.children=c(12, 18, 24, 32, 40)
-subj.contrib=c(0.1, 0.2, 0.4, 0.8, 1.6)
-conds=as.factor(c("ton", "geste", "both"))
-ages=as.factor(c(18, 24))
-trial.effect=0.1
-trial.RS=0.05
-age.cond.probs=c(0.5, 0.6, 0.7, 0.6, 0.7, 0.8)
-logit.age.cond.probs=log(age.cond.probs/(1-age.cond.probs))
-
-do.all<-function(index, nc, sc){
-	keepWarnings<-function(expr){
-		localWarnings <- list()
-		value <- withCallingHandlers(expr,
-			warning = function(w) {
-				localWarnings[[length(localWarnings)+1]] <<- w
-				invokeRestart("muffleWarning")
-			}
-		)
-		list(value=value, warnings=localWarnings)
-	}
-	N=n.children[nc]*length(conds)*length(ages)
-	xdata=data.frame(expand.grid(conds, ages))
-	colnames(xdata)=c("cond", "age")
-	xdata$cond=factor(xdata$cond, levels=c("ton", "geste", "both"))
-	xdata=xdata[rep(x=1:nrow(xdata), each=n.children[nc]), ]
-	xdata$subject=as.factor(1:N)
-	n.trials=sample(1:4, N, replace=T, prob=c(0.4, 0.3, 0.2, 0.1))
-	xdata=xdata[rep(x=1:nrow(xdata), times=n.trials), ]
-	xdata$trial.nr=unlist(lapply(X=n.trials, FUN=function(input){1:input}))
-	xdata$z.trial.nr=as.vector(scale(xdata$trial.nr))
-	both.fac=as.factor(paste(xdata$age, xdata$cond, sep="_"))
-	both.fac=factor(both.fac, levels(both.fac)[c(3, 2, 1, 6, 5, 4)])
-	
-	resp=logit.age.cond.probs[as.numeric(both.fac)]+
-		xdata$z.trial.nr*(trial.effect+rnorm(n=N, mean=0, sd=trial.RS)[as.numeric(xdata$subject)])+
-		rnorm(n=N, mean=0, sd=subj.contrib[sc])[as.numeric(xdata$subject)]
-	resp=rbinom(n=nrow(xdata), size=1, prob=exp(resp)/(1+exp(resp)))
[…]

### 2019-04-26 papers/cogsci2019/cogsci2019.Rmd
first draft paper si

@@
 author-information: > 
-   \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
+   \author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Department of Psychology \\ Stanford University\\ LFE \\Leipzig University 
     \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
@@
 
-A range probabilistic frameworks been used to model word learning [e.g.
+A range of probabilistic models have been used to model word learning [e.g.
 @fazly2010probabilistic; @frank2009using; @xu2007word].
-RSA models differ from other approaches in that they treat word learning as the outcome of a social reasoning process.
+RSA models differ from these approaches in that they treat word learning as the outcome of a social reasoning process.
 In contrast to models for cross-situational word learning [@fazly2010probabilistic; @frank2009using], RSA models show how learning might occur in a one shot scenario based on pragmatic reasoning alone.
-While the ad hoc informativeness inference characteristic for RSA would be predicted by the model of Xu and Tenenbaum [-@xu2007word], in their work it follows from the "size principle" of generalization [@tenenbaum2001generalization] and not from social reasoning.
-In cotrast to RSA, this approach does not offer a straightforward way to incorporate other types of social information such as expectations following from common ground.
+While the ad-hoc informativeness inference characteristic for RSA would be predicted by the model of Xu and Tenenbaum [-@xu2007word], in their work it follows from the "size principle" of generalization [@tenenbaum2001generalization] and not from social reasoning.
+In contrast to RSA, this approach does not offer a straightforward way to incorporate other types of social information such as expectations following from common ground.
 
@@
 MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.
+MCF was supported by a Jacobs Foundation Advanced Research Fellowship and NSF #1456077.
 

### 2019-04-26 papers/cogsci2019/cogsci2019.tex
first draft paper si

@@
 
-\author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Psychology, Stanford University \\ LFE, Leipzig University 
+\author{{\large \bf Manuel Bohn} \\ \texttt{bohn@stanford.edu} \\ Department of Psychology \\ Stanford University\\ LFE \\Leipzig University 
  \And {\large \bf Michael Henry Tessler} \\ \texttt{tessler@mit.edu} \\ Department of Brain and Cognitive Sciences \\ Massachusetts Institute of Technology
@@
 
-A range probabilistic frameworks been used to model word learning (e.g.
-Fazly, Alishahi, \& Stevenson, 2010; Frank, Goodman, \& Tenenbaum, 2009;
-Xu \& Tenenbaum, 2007). RSA models differ from other approaches in that
-they treat word learning as the outcome of a social reasoning process.
-In contrast to models for cross-situational word learning (Fazly et al.,
-2010; Frank et al., 2009), RSA models show how learning might occur in a
-one shot scenario based on pragmatic reasoning alone. While the ad hoc
-informativeness inference characteristic for RSA would be predicted by
-the model of Xu and Tenenbaum (2007), in their work it follows from the
-``size principle'' of generalization (Tenenbaum \& Griffiths, 2001) and
-not from social reasoning. In cotrast to RSA, this approach does not
-offer a straightforward way to incorporate other types of social
-information such as expectations following from common ground.
+A range of probabilistic models have been used to model word learning
+(e.g. Fazly, Alishahi, \& Stevenson, 2010; Frank, Goodman, \& Tenenbaum,
+2009; Xu \& Tenenbaum, 2007). RSA models differ from these approaches in
+that they treat word learning as the outcome of a social reasoning
+process. In contrast to models for cross-situational word learning
+(Fazly et al., 2010; Frank et al., 2009), RSA models show how learning
+might occur in a one shot scenario based on pragmatic reasoning alone.
+While the ad-hoc informativeness inference characteristic for RSA would
+be predicted by the model of Xu and Tenenbaum (2007), in their work it
+follows from the ``size principle'' of generalization (Tenenbaum \&
+Griffiths, 2001) and not from social reasoning. In contrast to RSA, this
+approach does not offer a straightforward way to incorporate other types
+of social information such as expectations following from common ground.
 
@@
 innovation programme under the Marie Sklodowska-Curie grant agreement No
-749229.
+749229. MCF was supported by a Jacobs Foundation Advanced Research
+Fellowship and NSF \#1456077.
 

### 2019-04-26 papers/full_paper/SI_appendix.Rmd
clean up repo
first draft paper si

--- 2019-03-24 papers/full_paper/models.Rmd
@@
 ---
-title: "MCC Models"
-author: "Manuel Bohn"
-output:
-  html_document:
-    code_folding: hide
+title             : "Supplementary information:Predicting information integration in pragmatic word learning across development"
+shorttitle        : "Supplementary information"
+
+author: 
+  - name          : "Manuel Bohn"
+    affiliation   : "1,2"
+    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
+    email         : "bohn@stanford.edu"
+  - name          : "Michael Henry Tessler"
+    affiliation   : "3"
+  - name          : "Megan Merrick"
+    affiliation   : "1"
+  - name          : "Michael C. Frank"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "2"
+    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
+  - id            : "3"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+
+bibliography      : ["library.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : no
+mask              : no
+
+class             : "doc"
+output            : papaja::apa6_pdf
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
-
+knitr::opts_chunk$set(echo = F, warning = F, message = F, include = T)
+library(papaja)
 library(tidyverse)
@@
 library(ggpubr)
+library(lme4)
+library(broom)
 
@@
 
-# Model code
-
-## Model utilities
-
-```{r rsaUtils}
-rsaUtils <- '
-// three objects: triangle_1 on table 1, triangle_2 and circle_1 on table 2
-var all_objects = [
-{ shape: "triangle", id:1, location: 1},  
-{ shape: "triangle", id:2, location: 2},
-{ shape: "circle", id:1, location: 2}
-]
-
-// listener prior is over types, not tokens (we use uniformDraw on prior_objects)
-var prior_objects = [
-{ shape: "triangle", id:1, location: 1},  
-{ shape: "circle", id:1, location: 2}
-]
-
-var labels = ["dax","wug"]
-
-// two possible lexica, corresponding to meaning of words "dax" and "wug"
-var lexicon1 = function(utterance, obj){
-utterance.label == "dax" ? obj.shape == "triangle" :
-utterance.label == "wug" ? obj.shape == "circle" : 
-true
-}
-
-var lexicon2 = function(utterance, obj){
-utterance.label == "dax" ? obj.shape == "circle" :
-utterance.label == "wug" ? obj.shape == "triangle" : 
-true
-}
-
-var lexiconObjects = {
-"dax = triangle": {
-triangle: "dax", circle: "wug"
-},
-"dax = circle": {
-triangle: "wug", circle: "dax"
-},
-}
-
-var lexiconObject = {
-"dax = triangle": lexicon1,
-"dax = circle" : lexicon2
-}
-
-var point = function(utterance, obj){
-return obj.location == utterance.point
-}
-
-var utterancePrior = function(obj, lexiconName){
-  var locationsWithShape = _.map(_.filter(all_objects, {shape: obj.shape}), "location")
-  var point = uniformDraw(locationsWithShape)
-  var label = lexiconObjects[lexiconName][obj.shape]
-  return {label: label, point: point}
-}
-
-var LexiconPrior = Categorical({vs: ["dax = triangle","dax = circle" ], ps: [1, 1]})
-
-var speakerOptimality = 2.25;
-
-var addNoise = function(dist, noiseParam){
-   Infer({model: function(){ 
-      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
-    }
-   })
-}
-
-var foreach = function(fn, lst) {
-    var foreach_ = function(i) {
-        if (i < lst.length) {
-            fn(lst[i]);
-            foreach_(i + 1);
-        }
-    };
-    foreach_(0);
-};
-
-var logistic = function(x) {1 / (1 + Math.exp(-x))}
-
-var levels = function(df, label){
-  return _.uniq(_.map(df, label));
-}
-
-'
-```
-
-# Adults
-
-## RSA model code
-```{r rsa model}
-rsaModel <- '
-var literalListener = cache(function(utterance, priorProbs){
-  Infer({method: "enumerate", model: function(){
-    var lexiconName = sample(LexiconPrior); 
-    var lexicon = lexiconObject[lexiconName];
-    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-    if ("label" in utterance) {
-      var truthValue = lexicon(utterance, obj);
-      condition(truthValue)
-    }
-    if (utterance.point) {
-     var truthValuePoint = point(utterance, obj);
-     condition(truthValuePoint)
-    }
-    return obj.shape 
-  }})
-})
-
-var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
-  Infer({method: "enumerate", model: function(){
-    var utterance = utterancePrior(obj, lexiconName);
-    var L0 = literalListener(utterance, priorProbs);
-    factor(speakerOptimality * L0.score(obj.shape))
-    return utterance
-  }})
-})
-
-var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
-  Infer({method: "enumerate", model: function(){
-    var lexiconName = sample(LexiconPrior);
-    var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
-    var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
-    observe(S1, utterance)
-    return obj.shape == "circle" ? 1 : 0
-  }})
-})
-
-var addNoise = function(dist, noiseParam){
-   Infer({model: function(){ 
-      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
-    }
-   })
-}
-'
-```
-
-## Experiment 3
-
-### Model parameters and data
-
-```{r ex3 data adults}
-# load data from experiment 3
-adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
-```
-
-```{r ex 1 and 2 data adults}
+```{r}
+# load data files
+
 # adults exp 1 
 adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
-# load data from prior manipulation experiments to set priors
+# adults exp 2 novelty
 adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
+# adults exp 2 preference
 adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
-```
-
-#### Inferring speaker optimality parameter and setting priors
-
-```{r model parameter adults}
-# Cauchy prior on the speaker optimality parameter around 1, based on previous work (e.g. Frank & Goodman, 2014) 
-speakOptParam <- '
-var data = dataFromR.data
-
-var model  = function(){
-
-  var speakerOptimality = sample(Cauchy({location: 1, scale: 2}))
-
-  foreach(function(row){
-
-    var priorProbs = [.5, .5, .5]
-
-    var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
-      priorProbs, speakerOptimality)
-
-    observe(rsaPredictions, row.correct)
-  }, data)
-
-  return speakerOptimality
-
-}
-'
-```
-
-```{r inferring speaker optimality parameter adults}
-# adult_model_param<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, speakOptParam , sep='\n'),
-#   data = list(data = adult_ex1_data %>% filter(condition == "test")),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#   saveRDS("../../stats/saves/adult_model_param.rds")
-
-adult_model_param <- readRDS("../../stats/saves/adult_model_param.rds")%>%
-  select(value) %>%
-  summarise(so_map = estimate_mode(value),
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-```{r visualize speaker optimality parameter adults}
-# visualize speaker optimality parameter
-plot_adult_model_speak_opt <- readRDS("../../stats/saves/adult_model_param.rds")%>%
-  select(value)
-
-ggplot(plot_adult_model_speak_opt, aes(value))+
-  geom_density()+
-  xlab("Speaker optimality")+
-  theme_few()
-```
-
-```{r model setup ex 3 adults}
-# create datafiles with model parameters
-model_params_ex3 <- expand.grid(
-  common_ground_manipulation = c("preference", "novelty"),
-  speaker = c("same_speaker", "different_speaker"),
-  speak_opt = adult_model_param$so_map
-  )
-
-prior_pref_summary <- bind_rows(
-  adult_ex2_preference_data,
-  adult_ex2_novelty_data) %>%
-  group_by(condition, experiment) %>%
-  summarise(prior = mean(correct)) %>%
-  mutate(experiment = gsub("adult_ex2_", "", experiment)) %>%
-  rename(common_ground_manipulation = experiment,
-         speaker = condition)
-
-model_params_ex3 <- left_join( 
-  model_params_ex3, 
-  prior_pref_summary, by = c("common_ground_manipulation", "speaker")
-) %>%
-  rename(congruent = prior) %>%
-  mutate(incongruent = 1 - congruent) %>%
-  gather(alignment, prior, congruent, incongruent)
-
-```
-
-### Model predictions
-
-#### Pragmatic model
-
-##### Parameter free
-
-```{r model rsa ex3 adults}
-predictions.rsa.ex3 <-'
-
-var allData = dataFromR.data
-
-var output = map(function(row){
-
-    var priorProbLst = [1 - row.prior, 1 - row.prior, row.prior]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbLst, row.speak_opt)
-
-    return extend([row.common_ground_manipulation + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex 3 adults}
-ex3_pragm_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3 , sep='\n'),
-  data =list(data = model_params_ex3),
-  data_var = "dataFromR"
-)
-
-# model predictions
-ex3_pragm_model_predictions <- ex3_pragm_model %>%
-  separate(`0`, into = c("common_ground_manipulation", "speaker", "alignment"), sep="/")%>%
-  mutate(value = `1`,
-         model="pragmatic")%>%
-  select(-`1`)
-
-```
-
-##### Noise parameter
-
-```{r model rsa noise ex3, include = FALSE}
-predictions.rsa.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions pragmatic model ex 3 noise, include = FALSE}
-# ex3_pragm_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_pragm_model_noise.rds")
-
-# model predictions
-ex3_pragm_model_pred_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic_noise")%>%
-  group_by(model,common_ground_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex3_pragm_model_noise_param <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-#### Prior only model
-
-##### Noise parameter
-
-```{r model prior only noise ex3, include = FALSE}
-predictions.prior.only.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions prior only model ex 3 noise, include = FALSE}
-# ex3_prior_only_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_prior_only_model_noise.rds")
-
-# model predictions
-ex3_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only_noise")%>%
-  group_by(model,common_ground_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-#### Flat prior model
-
-##### Noise parameter
-
-```{r model flat prior noise ex3, include = FALSE}
-predictions.flat.prior.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions flat prior model ex 3 noise, include = FALSE}
-# ex3_flat_prior_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_flat_prior_model_noise.rds")
-
-# model predictions
-ex3_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior_noise")%>%
-  group_by(model,common_ground_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-#### Compare model predictions to data
-
-##### Noise parameters
-
-```{r}
-ex3_noise_parameters <- bind_rows(
-  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "pragmatic"),
-  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "prior_only"),
-  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "flat_prior")
-  )
-
-ggplot(ex3_noise_parameters, aes(x = value, col = model, fill = model))+
-  geom_density(alpha = .5)+
-  theme_few()+
-  xlim(0,1)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))+
-  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
-```
-
-```{r}
-# combine model predictions with data
-
-# summarize data 
-adult_ex3_data_summary <- adult_ex3_data %>%
-  mutate(model = "data") %>%
-  group_by(model,common_ground_manipulation,speaker,alignment)%>%
-  summarize(k = sum(correct_inf), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         ci_lower  = qbeta(.025, a, b),
-         ci_upper = qbeta(.975, a, b),
-         mean = (a-1)/(a+b-2))%>%
-  select(-a,-b,-n,-k)
-
-# summarize model predictions
-ex_3_model_pred_param_free <- bind_rows(
-  ex3_pragm_model_predictions
-)%>%
-  group_by(model,common_ground_manipulation,speaker,alignment)%>%
-  summarise(mean = mean(value))%>%
-  mutate(ci_lower = mean,
-         ci_upper = mean)
-
-ex_3_model_pred <- 
-  bind_rows(
-    ex_3_model_pred_param_free,
-    ex3_pragm_model_pred_noise,
-            ex3_prior_only_model_pred_noise,
-            ex3_flat_prior_model_pred_noise)
-
-# combine model predictions and data
-
-ex_3_pred <- bind_rows(
-  ex_3_model_pred,
-  ex3_pragm_model_pred_noise,
-  adult_ex3_data_summary
-)
-
-#saveRDS(ex_3_pred, "../../stats/saves/adult_ex3_model_predictions_data.rds")
-
-```
-
-##### Plot model predictions and data
-
-```{r plot ex3 model predictions and data adults}
-ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
+# adults ex3
+adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv")
+# prior strength manipulation experiments in experiment 4
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+# adults ex4
+adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv")
+
+# children ex1
+child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
+# children ex2 preference
+child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
+# children ex3
+child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
+```
+
+# Structure
+
+Here we present details for the cognitive models as well as supplementary analysis and results.
+Readers who are interested in the model or analysis code itself are encouraged to consult the corresponding online repository: (https://github.com/manuelbohn/mcc).
+
+# Models
+
+All models were computed in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
+
+## Pragmatics model
+
+The pragmatics model had the same basic structure as the model in Frank and Goodman [-@frank2014inferring].
+It captures the following process: A pragmatic listener ($L_1$) reasons about a pragmatic speaker ($S_1$) who is reasoning about a naive listener ($L_0$) who interprets utterances according to their literal semantics.
+The outcome is the posterior probability of a particular referent given an utterance.
+According to Bayes rule it is defined as:
+
+\begin{equation} 
+P_{L_1}(r_s|u)\propto P_{S_1}(u|r_s)P_{S_i}(r_s)
+\end{equation}
+
+The right side of this equation has two components, the likelihood $P_{S1}(u|r_s)$ and the prior $P_{S_i}(r_s)$.
+The likelihood represent the probability that a particular utterance is used to refer to the referent.
+It is defined in terms of a utility function $U_S(u;s)$:
+
+\begin{equation} 
+P_{S_1}(u|r_s)\propto exp(\alpha U_{S_1}(u;s))
+\end{equation}
+
+This utility is defined as the surprisal of $u$ for a literal listener, $L_0$:
+
+\begin{equation} 
+U_{S_1}(r_s) = logL_0(r_s|u)
+\end{equation}
+
+The literal listener computes the probability of $r_s$ according to its literal semantics.
+In our case, all objects (and their names) were new to the listener.
+That is, $L_0$ could not rely on the semantics of the utterance to discriminate between referents.
+However, the utterance also included the agents turn to one of the tables.
+The semantics of turning to one of the tables is roughly equal to using a word that could be used to describe the objects on that table.
+In addition to the utterance, $L_0$ also takes in the prior probability of the referent given the speaker.
+It is therefore defined as:
+
+\begin{equation} 
+P_{L0}(r_s|u)\propto [\![u]\!](r_s)P_{S_i}(r_s)
+\end{equation}
+
+Now, $S_1$ is assumed to choose the utterance that yields the highest utility for $L_0$. This captures the idea that speakers are trying to communicate in an informative way.
+
+As noted in the paper, the parameter $\alpha$ (speaker optimality parameter) in equation 2  determines the absolute strength of the likelihood term.
+It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
+For adults, we used the data from Experiment 1 to infer the value of $\alpha$.
+That is, we inferred which value of $\alpha$ would generate model predictions for the RSA model described above (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in Experiment 1.
+This value was then used for $\alpha$ in Experiment 3.
+
+For children, the speaker optimality parameter changed with age.
+Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept that best described the developmental trajectory in the data.
+As for adults, this was done via the RSA model with equal prior probability for each object.
+In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the overall intercept and adding the slope times the child's age (with age anchored at 0).
+
+The prior distribution over objects, $P_{S_i}(r_s)$, varied with the common ground manipulation, the identity of the speaker (indicated by subscript *i*) and the alignment of utterance and common ground information.
+Numerically, it depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children.
+
+For adults, this worked in the following way.
+For example, in Experiment 2, for the preference/same speaker condition, when the speaker indicated that they liked object A and disliked object B, the average proportion with which participants chose object A was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for object B it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
+In Experiment 3, this measurement determined the prior distribution over objects in cases whenever the the same manipulation was used (preference/same speaker).
+When utterance and common ground information were aligned (i.e.
+object A was the more informative object), the distribution of objects was (A,B,B).
+The corresponding prior distribution was therefore (`r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`).
+When information sources were dis-aligned (i.e.
+object B was the more informative one), the object distribution was (B,A,A) and the prior distribution was (`r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`).
+Note that Experiment 3 involved three objects while Experiment 2 only involved two.
+We nevertheless used the exact proportions measured in Experiment 2 for each object to inform the prior.
+This approach spread out the absolute probability mass but conserved the relative relation between objects.
+
+For children, we used the data from Experiment 6 to model the slope and intercept that best described the developmental trajectory in the data for each of the two conditions (see online repository for corresponding code).
+As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age.
+In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition (same or different speaker), adding the slope times the child's age and then using a logistic transformation to convert the outcome into proportions.
+The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
+
+## Prior only model
+
+The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused on  common ground manipulation. It is defined as:
+
+\begin{equation} 
+P_{L1}(r_s|u)\propto P_{S_i}(r_s)
+\end{equation}
+
+That is, the probability of the referent given the utterance is determined by the prior probability of the referent for a particular speaker.
+The prior distributions were set in the same way as for the pragmatics model.
+
+## Flat prior model
+
+This model was identical in structure to the pragmatics model with the exception that the prior distribution did not correspond to the measurements from Experiment 2 and did not vary with speaker identity.
+That is, regardless of common ground manipulation and speaker identity the prior distribution was always uniform (e.g.
+0.33,0.33,0.33).
+This was the case for children as well as  adults.
+The speaker optimality parameter was set in the same way as in the pragmatics model.
+
+# Experiment 4
+
+## Prior strength manipualtions
+
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+```
+
+```{r table_prior,results = "asis"}
+ex4_prior_models <- adult_ex4_prior_data %>%
+  group_by(common_ground_manipulation,prior_manipulation)%>%
+  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
+
+ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
+  filter(group == "fixed")%>%
+  select(-statistic, -group)%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2),
+         term = case_when(term == "(Intercept)" ~ "Intercept",
+                          term == "speakersame_speaker" ~ "condition (same speaker)"))%>%
+  rename(Manipulation = common_ground_manipulation,
+         Strength = prior_manipulation,
+         Term = term,
+         Estimate = estimate,
+         SE = std.error,
+         p = p.value)
+
+apa_table(
+  ex4_prior_models_table
+  , caption = "Model output for prior strength experiments "
+  , note = "Model structure in all cases: correct ~ condition + (1|id) + (1|agent)"
+  , escape = T
+)
+```
+
+Below we describe the different ways in which prior strength was manipulated.
+The corresponding experiments can be found in the online repository.
+The test event was always the same: The animal disappeared and then either the same or a different animal returned and requested an object using an unknown word.
+
+For preference, both tables initially contained an object.
+In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
+Then they turned the other side and expressed the respective other attitude.
+In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
+
+For novelty, one table was empty while there was an object on the other.
+In novelty/strong the animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
+Then the animal turned to the other side and commented in a complementary way.
+Next, the animal disappeared.
+The same animal re-appeared and the sequence above was repeated.
+When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
+In novelty/medium, the animal commented on the presence/absence of objects in the same way but did so only once.
+In novelty/weak, the animal only turned to the present object and commented on it.
+
+In all cases, the order of utterances and/or the side to which the speaker turned first were counterbalanced.
+Figure \ref{fig:priorplot} shows the results for the same speaker and different speaker conditions for each manipulation.
+
+```{r priorplot, fig.cap = "Results from prior strength manipulation Experiments.
+Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", fig.height = 3}
+
+p_adult_ex4_priors <- adult_ex4_prior_data%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
+  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
+  summarise(correct = mean(correct))
+
+p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
+  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
   geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
-  facet_grid (~ common_ground_manipulation + speaker) +
+  labs(x="",y="")+
+  facet_grid(common_ground_manipulation ~ prior_manipulation)+
   theme_few() + 
   ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_color_manual(name="Model",
-                     breaks=c("data","pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("black","#859900","#00afaf","#6c71c4","#b58900"))+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
-```
-
-##### Correlation plot model predictions and data
-
-```{r correlation plot ex3 adults}
-
-ex_3_cor_plot <- ex_3_pred %>%
-  ungroup()%>%
-  filter(model != "data") %>%
-  left_join(., ex_3_pred %>%
-    ungroup()%>%
-    filter(model == "data") %>%
-    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
-    select(-model)
-  )
-
-ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "#BB5566")) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_point(size = 2)+
-  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
-  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
-  coord_fixed()+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  ylab("Data")+
-  guides(col = F)+
-  facet_grid ( ~ model) +
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
-  theme_few()
-
-```
-
-### Model comparison
-
-#### Loglike Parameter free model
-```{r log likes ex3 adults}
-# calculating model log-likelihoods
-log_like_pragmatic_ex3 <- adult_ex3_data %>%
-  left_join(ex3_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(logP = sum(log_like))
-```
-
-#### Loglike models with noise
-
-##### Pragmatic model 
-```{r model rsa noise ex3, include = FALSE}
-loglike.rsa.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex3_pragm_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")
-
-ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
-  mutate(model = "pragmatic_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-```
-##### Prior only model
-
-```{r model prior only noise ex3, include = FALSE}
-loglike.prior.only.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex3_prior_only_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")
-
-ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-```
-
-##### Flat prior model
-
-```{r model flat prior noise ex3, include = FALSE}
-loglike.flat.prior.ex3.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5,.5]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex3_flat_prior_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex3.noise, sep='\n'),
-#   data = list(allData = adult_ex3_data, allParams = model_params_ex3),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")
-
-ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-```
-
-```{r}
-ex3_model_comparison <- bind_rows(
-  log_like_pragmatic_ex3,
-  ex3_pragm_model_noise_loglike,
-  ex3_flat_prior_model_noise_loglike,
-  ex3_prior_only_model_noise_loglike
-)%>%
-  mutate(model = reorder(model,logP))
-```
-
-#### Plot for likelihoods
-
-```{r likelihood plot adults}
-ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
-  geom_point(size = 7)+
-  theme_few()+ 
-  xlab("Model")+
-  ylab("Log-likelihood")+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  guides(col = F)+
-  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
-                    values= c("#00afaf","#b58900","#859900","#6c71c4"))
-```
-
-#### Bayes factors
-
-```{r bayes factors ex3 adults}
-
-ex3_bf <- bind_rows(
-  log_like_pragmatic_ex3,
-  ex3_pragm_model_noise_loglike,
-  ex3_flat_prior_model_noise_loglike,
-  ex3_prior_only_model_noise_loglike
-) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
-         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
-         "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
-         "prior_only_noise > flat_prior_noise" = prior_only_noise - flat_prior_noise) %>%
-  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)
-
-ex3_bf %>%
-  kable(digits = 2)
-```
-
-## Experiment 4
-
-### Model parameters and data
-```{r ex4 data adults}
-# load data  from experiment 4 
-adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
-```
-
-```{r prior pre-tests data adults}
-# load data from prior strength manipulation experiments to set priors
-adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
-```
-
-```{r model setup ex 4}
-
-# create datafiles with model parameters
-
-strongPrior <- expand.grid(
-  common_ground_manipulation = c("preference","novelty"),
-  speaker = c("same_speaker","different_speaker"),
-  prior_manipulation = c("strong", "medium", "weak")
-)
-
-strong_prior_summary <- adult_ex4_prior_data %>%
-  group_by(common_ground_manipulation, prior_manipulation, speaker) %>%
-  summarize(prior = mean(correct))
-
-model_params_ex4 <- left_join( 
-  strongPrior, 
-  strong_prior_summary# %>% filter(prior_manipulation == "strong")
-) %>%
-  rename(congruent = prior) %>%
-  mutate(incongruent = 1 - congruent) %>%
-  gather(alignment, prior, congruent, incongruent) %>%
-  drop_na() %>%
-  mutate(speak_opt = adult_model_param$so_map)
-```
-
-### Model predictions (including noise parameter)
-
-#### Pragmatic model
-
-```{r model rsa noise ex4, include = FALSE}
-predictions.rsa.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions pragmatic model ex 4 noise, include = FALSE}
-# ex4_pragm_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.rsa.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_pragm_model_noise.rds")
-
-# model predictions
-ex4_pragm_model_pred_noise <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic_noise")%>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-#### Prior only model
-
-```{r model prior only noise ex4, include = FALSE}
-predictions.prior.only.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions prior only model ex 4 noise, include = FALSE}
-# ex4_prior_only_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.prior.only.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_prior_only_model_noise.rds")
-
-# model predictions
-ex4_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only_noise")%>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex4_prior_only_model_noise_param <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-#### Flat prior model
-
-```{r model flat prior noise ex4, include = FALSE}
-predictions.flat.prior.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
-  var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5, .5]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
- map(function(d){ 
-      observe(noisyModelPredictions, d.correct_inf)
-    }, conditionSpecificData)
-
-  return  [conditionInfo.common_ground_manipulation + "/" + conditionInfo.prior_manipulation + "/" + conditionInfo.speaker + "/" +  conditionInfo.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allParams)
-
-  return extend(_.fromPairs(conditionOutput), {noise: noise})
-}
-'
-```
-
-```{r predictions flat prior model ex 4 noise, include = FALSE}
-# ex4_flat_prior_model_noise <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, predictions.flat.prior.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_flat_prior_model_noise.rds")
-
-# model predictions
-ex4_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise")))  %>%
-  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior_noise")%>%
-  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-## noise parameter
-ex4_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-```
-
-```{r join model predictions and data ex4 adults}
-# combine model predictions with data
-
-# summarize data 
+  guides(alpha = F,size =F)+
+  scale_color_solarized()+
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "right")
+```
+
+Table \ref{tab:table_prior} shows the results of a generalized linear mixed model (GLMM), fir to the data from each manipulation.
+The results show that the parameter estimates for condition (i.e.
+difference between same speaker and different speaker condition) decreases in line with the hypothesized effect of the prior manipulation.
+
+## Model predictions
+
+Figure \ref{fig:modelpredex4} compares model predictions to the data from Experiment 4.
+
+```{r modelpredex4, include = T, fig.cap = "Correlation plot for model predictions and data from Experiment 4.
+All models included a noise parameter.
+Coefficients and p-values are based on Pearson correlation statistics.
+Dots represent condition modes.
+Error bars represent 95\\% HDIs.", fig.height=2.5}
+
 adult_ex4_data_summary <- adult_ex4_data %>%
@@
 # summarize model predictions
+
+ex4_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+ex4_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+ex4_pragm_model_pred_noise <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic_noise")%>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
 ex_4_model_pred <- bind_rows(
@@
 
-#saveRDS(ex_4_pred, "../../stats/saves/adult_ex4_model_predictions_data.rds")
-
-```
-
-### Compare model predictions to data
-
-##### Noise parameters
-
-```{r}
-ex4_noise_parameters <- bind_rows(
-  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "pragmatic"),
-  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "prior_only"),
-  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "flat_prior")
-  )
-
-ggplot(ex4_noise_parameters, aes(x = value, col = model, fill = model))+
-  geom_density(alpha = .5)+
-  theme_few()+
-  xlim(0,1)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))+
-  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
-```
-
-#### Plot model predictions and data
-
-```{r plot ex4 model predictions and data adults}
-ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="Choosing More Informative")+
-  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
-  theme_few() + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_color_manual(name="Model",
-                     breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("black","#859900","#6c71c4","#b58900"))+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
-```
-
-#### Correlation plot model predictions and data
-
-```{r correlation plot ex4 adults}
 ex_4_cor_plot <- ex_4_pred %>%
@@
     select(-model)
-  )
+  )%>%
+  mutate(model =  case_when(model == "pragmatic_noise" ~ "Pragmatics",
+                            model == "prior_only_noise" ~ "Prior only",
+                            model == "flat_prior_noise" ~ "Flat prior"
+                            ))
 
@@
   theme_few(base_size = ) + 
-  scale_colour_ptol()
-```
-
-### Model comparison
-
-#### Marginal likelihoods
-
-##### Pragmatic model 
-```{r model rsa noise ex4, include = FALSE}
-loglike.rsa.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
- var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex4_pragm_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.rsa.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds")
-
+  scale_colour_ptol(name = "Prior strength")+
+  theme(legend.position = "right")
+
+```
+
+# Model comparison
+
+Analysis code for model comparison can be found in the online repository.
+
+## Experiment 3
+
+Here we report details on the model comparisons based on marginal log-likelihoods of the data for each model.
+Bayes Factors were computed by first subtracting log-likelihoods and then exponentiating the result.
+Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3.
+We did not pre-register the inclusion of the noise parameter for Experiment 4.
+The first row in Table \ref{tab:ex3_comp}
+
+```{r ex3_comp,results = "asis"}
+log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+
+ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
+  mutate(model = "pragmatic_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_model_comparison <- bind_rows(
+  log_like_pragmatic_ex3,
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+)%>%
+  mutate(model = reorder(model,logP))
+
+ex3_bf <- bind_rows(
+  log_like_pragmatic_ex3,
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+) %>% spread(model, logP) %>%
+  mutate("pragmatic_noise > pragmatic" = exp(pragmatic_noise - pragmatic),
+         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
+         "pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
+         "prior_only_noise > flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
+  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
+  gather(Comparison, BF)%>%
+  mutate(BF = formatC(BF,2))
+
+apa_table(
+  ex3_bf
+  , caption = "Bayes Factors for model comparisons in Experiment 3"
+  , escape = T
+)
+
+```
+
+Figure \ref{fig:ex3noise} shows the posterior distribution of the noise parameter for each model.
+The noise parameter was fit to the data and indicates the proportion of responses that are estimated to be due to random rather than in line with model predictions.
+That is, a model that makes predictions that are closer to the data is likely to have a lower noise parameter.
+
+```{r ex3noise, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 3", fig.height = 2}
+ex3_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Pragmatics"),
+  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Prior only"),
+  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Flat prior")
+  )
+
+ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlab("Noise parameter")+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
+
+## Experiment 4
+
+Table \ref{tab:ex4_comp} shows Bayes Factors for model comparisons in Experiment 3. As pre-registered, all models included a noise parameter.
+
+```{r ex4_comp, results="asis"}
 ex4_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds")%>%
@@
   summarize(logP = logSumExp(value))
-```
-
-##### Prior only model
-
-```{r model prior only noise ex4, include = FALSE}
-loglike.prior.only.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
- var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [1 - conditionInfo.prior, 1 - conditionInfo.prior, conditionInfo.prior]
-
-  var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors}));
-      return obj.shape == "circle" ? 1 : 0
-  }})
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex4_prior_only_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.prior.only.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds")
 
@@
   summarize(logP = logSumExp(value))
-```
-
-##### Flat prior model
-
-```{r model flat prior noise ex4, include = FALSE}
-loglike.flat.prior.ex4.noise <-'
-var allParams = dataFromR.allParams
-var allData = dataFromR.allData
-
-var model = function(){
-
-   var noise = uniformDrift({a: 0, b:1, width: 0.1})
-
-  var conditionOutput = map(function(conditionInfo){
-
- var conditionSpecificData =  _.filter(allData, {common_ground_manipulation: conditionInfo.common_ground_manipulation, prior_manipulation: conditionInfo.prior_manipulation, speaker: conditionInfo.speaker, alignment: conditionInfo.alignment})
-
-   var conditionSpecificPriors = [.5, .5,.5]
-
-      var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors, conditionInfo.speak_opt)
-
-   var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    var loglike = Binomial({
-        p: Math.exp(noisyModelPredictions.score(1)), 
-        n: conditionSpecificData.length}).score(
-      sum(_.map(conditionSpecificData, "correct_inf"))
-    )
-  return  loglike
-
-}, allParams)
-
- return sum(conditionOutput)
-
-}
-'
-```
-
-```{r}
-# ex4_flat_prior_model_noise_loglike <- webppl(
-#   program_code = paste(rsaUtils, rsaModel, loglike.flat.prior.ex4.noise, sep='\n'),
-#   data = list(allData = adult_ex4_data, allParams = model_params_ex4),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "forward", samples = 5000)
-# ) %>%
-#   saveRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds")
 
@@
   summarize(logP = logSumExp(value))
-```
-
-```{r}
-ex4_model_comparison <- bind_rows(
-  ex4_pragm_model_noise_loglike,
-  ex4_flat_prior_model_noise_loglike,
-  ex4_prior_only_model_noise_loglike
-)%>%
-  mutate(model = reorder(model,logP))
-```
-
-#### Plot for likelihoods
-
-```{r plot for loglikelihood ex4 adults}
-ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
-  geom_point(size = 7)+
-  theme_few()+ 
-  xlab("Model")+
-  ylab("Log-likelihood")+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  guides(col = F)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#859900","#6c71c4"))
-```
-
-#### Bayes factors
-
-```{r bayes factors ex4 adults}
+
 ex4_bf <- bind_rows(
@@
 ) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
-         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
-         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
-  select(-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)
-
-ex4_bf %>%
-  kable(digits = 2)
-```
-
-# Children
-
-## Model parameters and data
-
-```{r ex3 data children}
-# children ex3 data
-child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
-```
-
-```{r ex1 and ex2 data children}
-# load data from ex1 manipulation experiments to set speaker optimality parameter
-child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
-# load data from ex2 experiment to set priors
-child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
-```
-
-#### Inferring speaker optimality parameter and priors
-
-```{r model parameters children}
-# The prior on the speaker optimality intercept is the same as for the adult speaker optimality parameter.
-
-childModelParam <- '
-var prefData = dataFromR.prefData
-var infData = dataFromR.infData
-
-var all_conditions = levels(prefData, "condition")
-
-var model  = function(){
-
-  var so_slope = sample(Cauchy({location: 0, scale: 2}))
-  var so_int = sample(Cauchy({location: 1, scale: 2}))
-
-  foreach(function(row){
-
-  var age = row.age_num
-  var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)
-
-    var inf_priorProbs = [.5, .5, .5]
-
-  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
-   inf_priorProbs, speakerOptimality) 
-   observe(rsaPredictions, row.correct)
-
-  }, infData)
-
-  var pref_params = map(function(cndtn){
-
-    var conditionData = _.filter(prefData, {condition: cndtn})
-
-    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
-    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})
-
-    foreach(function(row){
-
-      var age = row.age_num
-
-      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
-      var priorProbs= [1-priorReg, priorReg]
-
-      var priorPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-      }})
-
-      observe(priorPredictions, row.correct)
-
-    }, conditionData)
-
-    return [
-      {param: "pref_int", val: pref_int, condition: cndtn}, 
-      {param: "pref_slope", val: pref_slope, condition: cndtn}
-    ]
-
-  }, all_conditions)
-
-  return _.flatten(pref_params).concat(
-    [
-      { param: "so_slope", val: so_slope},
-      { param: "so_int", val: so_int}
-    ]
-  )
-}
-'
-```
-
-```{r inferring model parameters children}
-# child_model_param<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, childModelParam , sep='\n'),
-#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#   saveRDS("../../stats/saves/child_model_param.rds")
-
-child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
-  select(value) %>%
-  map_df(bind_rows)%>%
-  group_by(param,condition)%>%
-  summarise(param_map = estimate_mode(val))%>%
-  mutate(cond = paste(param,condition, sep = "_"))%>%
-  ungroup()%>%
-  select(cond,param_map)%>%
-  spread(cond,param_map)%>%
-  rename(so_int = so_int_NA,
-         so_slope = so_slope_NA)
-
-```
-
-```{r visualize model parameters children}
-# visualize inferred parameter
-plot_child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
-  select(value)%>%
-  map_df(bind_rows)%>%
-  mutate(type = ifelse(grepl("pref",param),"prior", "speaker optimality"))
-
-ggplot(plot_child_model_param, aes(val))+
-  geom_density()+
-  xlab("Parameter")+
-  facet_grid(type~param+condition)+
-  theme_few()
-```
-
-```{r visualize prior children}
-# visualize model priors in comparison to data 
-child_prior_plot <- child_ex2_data %>%
-  group_by(id,age_num,minage,condition)%>%
-  summarise(correct = mean(correct))%>%
-  mutate(model = ifelse(condition == "different_speaker",
-                        plogis(child_model_param$pref_int_different_speaker + child_model_param$pref_slope_different_speaker * (age_num-minage)),
-                        plogis(child_model_param$pref_int_same_speaker + child_model_param$pref_slope_same_speaker * (age_num-minage)
-                        )))
-
-ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
-  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
-  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
-  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="Age",y="Proportion Correct")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)+ 
-  scale_color_solarized(name = "Condition")+
-  scale_fill_solarized(name = "Condition")
-
-# dashed line represents the developmental trajectories based on the estimated parameters 
-```
-
-```{r visualize speaker optimality children}
-# visualize speaker optimality in comparison to data 
-child_so_plot <- child_ex1_data %>%
-  group_by(id,age_num,minage)%>%
-  summarise(correct = mean(correct))%>%
-  mutate(model = child_model_param$so_int + child_model_param$so_slope * (age_num - minage))
-
-plot_child_so <- ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
-  geom_hline(yintercept = 0, lty=2)+
-  geom_line( size = 2)+
-  labs(x="Age",y="Speaker optimality parameter")+
-  theme_few() +
-  ggtitle("Speaker optimality parameter")+
-  ylim(-3,3)+
-  guides(alpha = F)
-
-plot_ex1_child <-child_ex1_data %>%
-  group_by(age_num, id) %>%
-  summarise(correct = mean(correct))%>%
-  ggplot(data = ., aes(x = age_num, y = correct)) +
-  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
-  geom_smooth(method = "lm", se = T, alpha = .5, size = .7)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="Age",y="Proportion Correct")+
-  ggtitle("Data ex1 children")+
-  theme_few() +
-  ylim(-0.05,1.05)+
-  guides(alpha = F)
-
-ggarrange(plot_child_so,plot_ex1_child)
-```
-
-```{r model setup ex3 children}
-ex3_model_data <- child_ex3_data%>%
-  mutate(so_int = child_model_param$so_int,
-         so_slope = child_model_param$so_slope,
-         pref_int_different_speaker = child_model_param$pref_int_different_speaker,
-         pref_slope_different_speaker = child_model_param$pref_slope_different_speaker,
-         pref_int_same_speaker = child_model_param$pref_int_same_speaker,
-         pref_slope_same_speaker = child_model_param$pref_slope_same_speaker,
-         so = so_int+so_slope*(age_num-min(age_num)),
-         diff_prior = plogis(pref_int_different_speaker+pref_slope_different_speaker*(age_num-min(age_num))),
-         same_prior = plogis(pref_int_same_speaker+pref_slope_same_speaker*(age_num-min(age_num))))%>%
-  group_by(id,trial)%>%
-        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
-                                   ifelse(speaker == "different_speaker" & alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
-                                          ifelse(speaker == "same_speaker" & alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
-                                                 list(c(diff_prior,diff_prior,1-diff_prior))
-
-                                   ))))%>%
-  ungroup()%>%
-  select(speaker,age_num,minage,alignment,so,priorProbs,correct_inf)
-
-```
-## Model predictions
-
-### Pragmatic model
-
-#### Parameter free
-
-```{r pragmatic model ex3 children}
-child.ex3.rsa.predictions <-'
-
-var allData = dataFromR.allData
-
-var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions pragmatic model ex3 children}
-child_ex3_pragm_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR"
-)
-
-# model predictions
-child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(mean = `1`,
-         ci_lower = mean,
-         ci_upper = mean,
-         model="pragmatic",
-         age = as.numeric(age))%>%
-  select(-`1`)
-```
-
-#### Noise parameter
+  mutate("Pragmatics > Prior only" = exp(pragmatic_noise - prior_only_noise),
+         "Pragmatics > Flat prior" = exp(pragmatic_noise - flat_prior_noise),
+         "Flat prior > Prior only" = exp(flat_prior_noise - prior_only_noise)) %>%
+  select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
+  gather(Comparison, BF)%>%
+  mutate(BF = formatC(BF,2))
+
+apa_table(
+  ex4_bf
+  , caption = "Model comparisons in Experiment 3"
+  , note = "BF = Bayes Factor; All models include a noise parameter."
+  , escape = T
+)
+
+```
+
+Figure \ref{fig:ex4noise} shows the posterior distribution of the noise parameter for each model in Experiment 4.
+
+```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 3", fig.height = 2}
+ex4_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Pragmatics"),
+  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Prior only"),
+  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Flat prior")
+  )
+
+ggplot(ex4_noise_parameters, aes(x = value, col = Model, fill = Model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlab("Noise parameter")+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
+
+## Experiment 7
+
+For children, we compared models using different types of noise parameters.
+We preregistered the model comparison for models including a single noise parameter.
+We added the additional model comparisons because the noise parameter was comparably high.
+The additional model comparisons allow us to see if the pragmatics model provides a better fit when the more emphasis is put on the model structure itself.
+The results show that this was the case.
+
+Parameter free models did not include a noise parameter.
+Noise models included a single noise parameter across age.
+Developmental noise models included a noise parameter that changed with age.
+That is, instead of a single value, we inferred an intercept and a slope for the noise parameter.
+Noise was therefore a function of the child's age.
+Table \ref{tab:child_prag_bf} shows model comparisons for the pragmatics models using different noise parameters.
+This shows that including a noise parameter improves model fit but that the type of noise parameter does not make much of a difference.
+
+```{r child_prag_bf, results = "asis"}
+child_ex3_model_comparison <- readRDS("../../stats/saves/child_ex3_model_comparison.rds")
+
+child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
+  filter(model == "pragmatic")%>%
+  spread(parameter, logP) %>%
+  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
+         "noise > parameter free" = exp(noise - `parameter free`),
+         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
+  select(-model,-`parameter free`,-`developmental noise`, -noise)%>%
+  gather(Comparison, BF)%>%
+  mutate(BF = formatC(BF,2))
+
+apa_table(
+  child_ex3_pragmatic_models_bf
+  , caption = "Model comparisons for pragmatics models in Experiment 7"
+  , note = "BF = Bayes Factor"
+  , escape = T
+)
+
+```
+
+Table \ref{tab:child_bf} shows results for model comparison for the different types of noise parameters.
+In any case, the pragmatics model provides a substantially better fit to the data compared to the alternative models
+
+```{r child_bf, results = "asis"}
+child_ex3_bf <- child_ex3_model_comparison%>%
+  rename(Parameter = parameter)%>%
+  group_by(Parameter)%>%
+  spread(model, logP) %>%
+  mutate("Pragmatics > Flat P." = formatC(exp(pragmatic - flat_prior),2),
+         "Pragmatics > P. only" = formatC(exp(pragmatic - prior_only),2),
+         "Flat P. > P. only" = formatC(exp(flat_prior - prior_only),2)) %>%
+  select(-pragmatic,-flat_prior, -prior_only)
+
+apa_table(
+  child_ex3_bf
+  , caption = "Model comparisons in Experiment 7"
+  , note = "BF = Bayes Factor"
+  , escape = T
+)
+
+```
 
 ```{r}
-child.ex3.rsa.predictions.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
-
-  var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r}
-# child_ex3_pragm_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_pragm_model_noise.rds")
-
-# model predictions
-child_ex3_pragm_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "pragmatic_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
-child_ex3_pragm_model_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-#### Developmental noise parameter
-
-```{r}
-child.ex3.rsa.predictions.developmental.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_pragm_model_developmental_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions.developmental.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds")
-
-# model predictions
-child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
-  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "pragmatic_developmental_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
+child_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Pragmatics"),
+  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Prior only"),
+  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Flat prior")
+  )
+
+child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlab("Noise parameter")+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
+
+```{r, include = T}
+
 child_ex3_pragm_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
@@
 
-```
-
-### Prior only model
-
-#### Parameter free
-
-```{r prior only model ex3 children}
-child.ex3.prior.only.predictions <-'
-
-var allData = dataFromR.allData
-
-  var output = map(function(row){
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment+ "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
- output
-
-'
-```
-
-```{r predictions prior only model ex3 children}
-child_ex3_prior_only_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR"
-)
-
-# model predictions
-child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(mean = `1`,
-         model="prior_only",
-         age = as.numeric(age))%>%
-  select(-`1`)
-
-```
-
-#### Noise parameter
-
-```{r}
-child.ex3.prior.only.predictions.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
-
-  var output = map(function(row){
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds")
-
-# model predictions
-child_ex3_prior_only_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
-child_ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-#### Developmental noise parameter
-
-```{r}
-child.ex3.prior.only.predictions.developmental.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-      var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_developmental_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.developmental.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds")
-
-# model predictions
-child_ex3_prior_only_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
-  filter(!(Parameter %in% c("noise_int","noise_slope"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "prior_only_developmental_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
 child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
@@
 
-```
-
-### Flat prior model
-
-#### Parameter free
-
-```{r flat prior model ex3 children}
-child.ex3.flat.prior.predictions <-'
-
-var allData = dataFromR.allData
-
-  var output = map(function(row){
-
-    var prior = [.5, .5, .5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    return  extend([row.age_num + "/" + row.speaker + "/" + row.alignment + "/" + row.correct_inf, Math.exp(modelPredictions.score(1))])
-
-}, allData)
-
-output
-
-'
-```
-
-```{r predictions flat prior model ex3 children}
-child_ex3_flat_prior_model<- webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR")
-
-# model predictions
-child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
-  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
-  mutate(mean = `1`,
-         model="flat_prior",
-         age = as.numeric(age))%>%
-  select(-`1`)
-
-```
-
-#### Noise parameter
-
-```{r}
-child.ex3.flat.prior.predictions.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniformDrift({a: 0, b: 1, width: 0.1})
-
-  var output = map(function(row){
-
-    var prior = [.5,.5,.5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise: noise})
-
-}
-'
-```
-
-#### Developmental noise parameter
-
-```{r}
-child.ex3.flat.prior.predictions.developmental.noise <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-    var prior = [.5,.5,.5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]
-
-}, allData)
-
- return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})
-
-}
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_developmental_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.developmental.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds")
-
-# model predictions
-child_ex3_flat_prior_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
-  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "flat_prior_developmental_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
 child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
@@
 
-```
-
-```{r}
-# child_ex3_flat_prior_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")
-
-# model predictions
-child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
-child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
-## Compare model predictions to data
-
-### Noise parameters
-
-```{r}
-child_noise_parameters <- bind_rows(
-  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "pragmatic"),
-  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "prior_only"),
-  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(model = "flat_prior")
-  )
-
-ggplot(child_noise_parameters, aes(x = value, col = model, fill = model))+
-  geom_density(alpha = .5)+
-  theme_few()+
-  xlim(0,1)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))+
-  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
-```
-
-### Developmental noise parameters
-```{r}
 developmental_noise_parameter <- data_frame(
   age = rep(seq(0,2, by = 0.05),3),
-  model = c(rep("pragmatic",41),
-            rep("flat_prior",41),
-            rep("prior_only",41)),
+  Model = c(rep("Pragmatics",41),
+            rep("Flat prior",41),
+            rep("Prior only",41)),
   int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
@@
 ) %>%
-  mutate(y = plogis(int + slope *age))
-
-ggplot(developmental_noise_parameter, aes(x = age, y= y, col = model))+
+  mutate(y = plogis(int + slope *age),
+         age = age +3)
+
+child_dev_noise_plot <- ggplot(developmental_noise_parameter, aes(x = age, y= y, col = Model))+
   geom_line(size = 1)+
@@
   theme_few()+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
                     values= c("#b58900","#6c71c4","#859900"))
@@
 
-### Plot model predictions and data
-
-```{r plot model predictions ex3 children}
-child_model_predictions <- bind_rows(
-  child_ex3_pragm_model_predictions_noise,
-  #child_ex3_pragm_model_predictions_developmental_noise,
-  child_ex3_pragm_model_predictions,
-  child_ex3_prior_only_model_predictions_noise,
-  child_ex3_flat_prior_model_predictions_noise
-  #child_ex3_flat_prior_model_predictions,
-  #child_ex3_prior_only_model_predictions
-  )
-
-#saveRDS(child_model_predictions, "../../stats/saves/child_ex3_model_predictions.rds")
-
-plot_child_ex3_data <- child_ex3_data%>%
-  group_by(age_num,speaker,alignment)%>%
-  summarise(mean = mean(correct_inf))
-
-ggplot(child_model_predictions)+
-  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
-  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
-  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
-  #geom_hline(yintercept = 0.5, lty=2)+
-  labs(y="proportion more informative")+
-  ylim(-0.05,1.05)+
-  facet_grid(speaker~alignment)+
-  theme_few()+
-  scale_color_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("#b58900","#00afaf","#6c71c4","#859900"))+
-  scale_fill_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("#b58900","#00afaf","#6c71c4","#859900"))
-
-```
-
-### Correlation plot model predictions and data
-
-```{r correlation plot ex3 children}
-child_cor_data <- child_ex3_data %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(speaker, alignment, age_bin) %>%
-  summarize(k = sum(correct_inf), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         Data_ci_lower  = qbeta(.025, a, b),
-         Data_ci_upper = qbeta(.975, a, b),
-         Data = (a-1)/(a+b-2))%>%
-  select(-a,-b,-n,-k)
-
-child_cor_model <- child_model_predictions %>%
-  mutate(age = ifelse(age<4,"3","4"))%>%
-  group_by(model,speaker,alignment, age)%>%
-  summarise(Model = mean(mean))
-
-child_cor_plot <- child_cor_model %>%
-  ungroup()%>%
-  mutate(Data = rep(child_cor_data$Data,4),
-         Data_ci_lower = rep(child_cor_data$Data_ci_lower,4),
-         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,4))
-
-ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
-  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 3)+
-  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
-  coord_fixed()+
-  facet_grid(~model)+
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
-  xlim(0,1)+ylim(0,1)+
-  xlab("Model")+
-  theme_few() + 
-  scale_colour_ptol()
-```
-
-## Model comparison
-
-### Marginal likelihoods
-
-#### Pragmatic model
-
-##### Parameter free
-
-```{r pragmatic model ex3 children}
-child.ex3.rsa.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    observe(modelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-
-'
-```
-
-```{r}
-# child_ex3_pragm_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
-
-child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "pragmatic",
-         parameter = "parameter free")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
-```
-
-##### Noise parameter
-
-```{r}
-child.ex3.rsa.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_pragm_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
-
-child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "pragmatic",
-         parameter = "noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
-```
-
-##### Developmental noise parameter
-
-```{r}
-child.ex3.rsa.developmental.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
-
-child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "pragmatic",
-         parameter = "developmental noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
-```
-
-#### Flat prior model
-
-##### Parameter free
-
-```{r}
-child.ex3.flat.prior.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [.5,.5,.5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    observe(modelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
-
-child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "flat_prior",
-         parameter = "parameter free")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-```
-
-##### Noise parameter
-
-```{r}
-child.ex3.flat.prior.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var prior = [.5,.5,.5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
-
-child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "flat_prior",
-         parameter = "noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-```
-
-##### Developmental noise parameter
-
-```{r}
-child.ex3.flat.prior.developmental.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-    var prior = [.5,.5,.5]
-
-    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
-
-child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "flat_prior",
-         parameter = "developmental noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
-```
-
-#### Prior only model
-
-##### Parameter free
-
-```{r}
-child.ex3.prior.only.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    observe(modelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
-
-child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "prior_only",
-         parameter = "parameter free")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-```
-
-##### Noise parameter
-
-```{r}
-child.ex3.prior.only.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise = uniform({a: 0, b: 1})
-
-  var output = map(function(row){
-
-    var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
-
-child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "prior_only",
-         parameter = "noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-```
-
-##### Developmental noise parameter
-
-```{r}
-child.ex3.prior.only.developmental.noise.marginal.likelihood <-'
-
-var allData = dataFromR.allData
-
-var model = function(){
-
-  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
-  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})
-
-  var output = map(function(row){
-
-    var noise = logistic(noise_int + noise_slope * (row.age_num-row.minage))
-
-    var modelPredictions = Infer({method: "enumerate", model: function(){
-      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
-      return obj.shape == "circle" ? 1 : 0
-       }})
-
-    var noisyModelPredictions = addNoise(modelPredictions, noise)
-
-    observe(noisyModelPredictions, row.correct_inf)
-
-}, allData)
-
-}
-
-var steps = 5000
-var samples = 1
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
-
-child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "prior_only",
-         parameter = "developmental noise")%>%
-  group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-```
-
-```{r model loglike ex3 children}
-# calculating model log-likelihoods
-
-child_ex3_model_comparison <- bind_rows(
-  child_ex3_pragm_model_likelihood,
-  child_ex3_pragm_model_noise_likelihood,
-  child_ex3_pragm_model_developmental_noise_likelihood,
-  child_ex3_flat_prior_model_noise_likelihood,
-  child_ex3_flat_prior_model_likelihood,
-  child_ex3_flat_prior_model_developmental_noise_likelihood,
-  child_ex3_prior_only_model_noise_likelihood,
-  child_ex3_prior_only_model_likelihood,
-  child_ex3_prior_only_model_developmental_noise_likelihood
-)%>%
-  ungroup()%>%
-  mutate(model = reorder(model,logP))
-```
-
-### Plot for likelihoods
-
-```{r plot model loglikes ex3 children}
-ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
-  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
-  geom_point(size = 7)+
-  theme_few()+ 
-  xlab("Model")+
-  ylab("Log-likelihood")+
-  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
-  guides(col = F)+
-  facet_grid(~parameter)+
-  ylim(-475,-400)+
-  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))
-
-```
-
-### Bayes factors
-
-```{r bayes factors ex3 children}
-child_ex3_bf <- child_ex3_model_comparison%>%
-  group_by(parameter)%>%
-  spread(model, logP) %>%
-  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
-         "pragmatic > prior_only" = pragmatic - prior_only,
-         "flat_prior > prior_only" = flat_prior - prior_only) %>%
-  select(-pragmatic,-flat_prior, -prior_only)
-
-child_ex3_bf%>%
-  kable(digits = 2)
-```
-
-# Appendix 1: Fully Bayesian analysis
+Figure \ref{fig:childnoise} shows the different types of noise parameters for the each model.
+Figure \ref{fig:childnoise}A shows that the pragmatics model has the lowest estimated level of noise of all the models considered.
+Figure \ref{fig:childnoise}B shows that the the pragmatics model has the lowest level of estimated noise across the entire age range.
+It also shows that noise decreases with age for the pragmatics model, suggesting that older children behaved more in line with model predictions compared to younger children.
+
+```{r childnoise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 7.
+A: single noise parameter across age, B: Developmental noise parameter.", fig.height = 2.5}
+ggarrange(child_noise_plot,child_dev_noise_plot, nrow = 1, ncol = 2, common.legend = T, legend = "right", labels = c("A","B"))
+```
+
+\newpage
+
+# References
+```{r create_r-references}
+r_refs(file = "r-references.bib")
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup

### 2019-04-26 papers/full_paper/manuscript.Rmd
first draft paper si

@@
     affiliation   : "3"
+  - name          : "Megan Merrick"
+    affiliation   : "1"
   - name          : "Michael C. Frank"
@@
 749229.
-We thank Jacqueline Quirke, Sabina Zacco and especially Megan Merrick for help with the data collection.
+MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund.
+We thank Jacqueline Quirke and Sabina Zacco for help with the data collection.
 
@@
 The prior only model predicted choice based on the prior probability for each object alone.
-Note that the proportions that informed the prior distribution in the pragmatics and prior only model were measured when participants chose between two objects in experiment 2.
-In experiment 3, however, three objects were involved.
-For each object we used the proportion measured in experiment 2 as the prior probability.
-This approach spread out the absolute probability mass but conserved the relative relation between objects.
 Bayes Factors for model comparisons are based on marginal likelihoods of each model given the data.

### 2019-04-26 papers/full_paper/models.Rmd
first draft paper si

@@
 ---
-title: "MCC Models"
-author: "Manuel Bohn"
-output:
-  html_document:
-    code_folding: hide
+title             : "Predicting information integration in pragmatic word learning across development"
+shorttitle        : "Supplementary Information"
+
+author: 
+  - name          : "Manuel Bohn"
+    affiliation   : "1,2"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
+    email         : "bohn@stanford.edu"
+  - name          : "Michael Henry Tessler"
+    affiliation   : "3"
+  - name          : "Megan Merrick"
+    affiliation   : "1"
+  - name          : "Michael C. Frank"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
+  - id            : "2"
+    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
+  - id            : "3"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+
+bibliography      : ["library.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : no
+mask              : no
+
+class             : "man"
+output            : papaja::apa6_pdf
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
+knitr::opts_chunk$set(echo = F, warning = F, message = F, include = T)
 
@@
 
-```{r rsaUtils}
+```{r rsaUtils, include = T}
 rsaUtils <- '
@@
 
-var speakerOptimality = 2.25;
-
 var addNoise = function(dist, noiseParam){
@@
 
-# Adults
-
 ## RSA model code
-```{r rsa model}
+
+```{r rsa model, include = T}
 rsaModel <- '
@@
 
+# Adults
+
 ## Experiment 3
@@
 
-```{r model parameter adults}
+```{r model parameter adults, include = T}
 # Cauchy prior on the speaker optimality parameter around 1, based on previous work (e.g. Frank & Goodman, 2014) 
@@
 
-```{r visualize speaker optimality parameter adults}
+```{r visualize speaker optimality parameter adults, echo = T}
 # visualize speaker optimality parameter
@@
 
-```{r model rsa ex3 adults}
+```{r model rsa ex3 adults, include=T}
 predictions.rsa.ex3 <-'
@@
 
-```{r model rsa noise ex3, include = FALSE}
+```{r model rsa noise ex3, include = T}
 predictions.rsa.ex3.noise <-'
@@
 
-```{r model flat prior noise ex3, include = FALSE}
+```{r model flat prior noise ex3, include = T}
 predictions.flat.prior.ex3.noise <-'
@@
 
-```{r}
+```{r, include = T}
 ex3_noise_parameters <- bind_rows(
@@
 
-```{r plot ex3 model predictions and data adults}
+```{r plot ex3 model predictions and data adults, include = T}
 ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
@@
 
-#### Loglike Parameter free model
+#### Marginal likelihoods
+
+##### Pragmatic model
+
+###### Parameter free
+
 ```{r log likes ex3 adults}
 # calculating model log-likelihoods
-log_like_pragmatic_ex3 <- adult_ex3_data %>%
-  left_join(ex3_pragm_model_predictions)%>%
-  mutate(like = ifelse(correct_inf == 1, value, 1 - value),
-         log_like = log(like))%>%
-  group_by(model)%>%
-  summarise(logP = sum(log_like))
-```
-
-#### Loglike models with noise
-
-##### Pragmatic model 
-```{r model rsa noise ex3, include = FALSE}
+# log_like_pragmatic_ex3 <- adult_ex3_data %>%
+#   left_join(ex3_pragm_model_predictions)%>%
+#   mutate(like = ifelse(correct_inf == 1, value, 1 - value),
+#          log_like = log(like))%>%
+#   group_by(model)%>%
+#   summarise(logP = sum(log_like))%>%
+#   saveRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+
+log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+```
+
+###### Noise parameter
+
+```{r loglike rsa noise ex3, include = FALSE}
 loglike.rsa.ex3.noise <-'
@@
 
-```{r model prior only noise ex3, include = FALSE}
+###### Noise parameter
+
+```{r loglike prior only noise ex3, include = FALSE}
 loglike.prior.only.ex3.noise <-'
@@
 
-```{r model flat prior noise ex3, include = FALSE}
+###### Noise parameter
+
+```{r loglike flat prior noise ex3, include = FALSE}
 loglike.flat.prior.ex3.noise <-'
@@
 
-```{r likelihood plot adults}
+```{r likelihood plot adults, include = T}
 ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
@@
 ) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
-         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
-         "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
-         "prior_only_noise > flat_prior_noise" = prior_only_noise - flat_prior_noise) %>%
+  mutate("pragmatic_noise > pragmatic" = exp(pragmatic_noise - pragmatic),
+         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
+         "pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
+         "prior_only_noise > flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
   select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)
@@
 ## Experiment 4
+
+### Prior manipulation experiments
 
@@
 
-```{r}
+```{r, include = T}
 ex4_noise_parameters <- bind_rows(
@@
 
-```{r plot ex4 model predictions and data adults}
+```{r plot ex4 model predictions and data adults, include = T}
 ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
@@
 
-```{r correlation plot ex4 adults}
+```{r correlation plot ex4 adults, include = T}
 ex_4_cor_plot <- ex_4_pred %>%
@@
 ##### Pragmatic model 
-```{r model rsa noise ex4, include = FALSE}
+```{r loglike rsa noise ex4, include = FALSE}
 loglike.rsa.ex4.noise <-'
@@
 
-```{r model prior only noise ex4, include = FALSE}
+```{r loglike prior only noise ex4, include = FALSE}
 loglike.prior.only.ex4.noise <-'
@@
 
-```{r model flat prior noise ex4, include = FALSE}
+```{r loglike flat prior noise ex4, include = FALSE}
 loglike.flat.prior.ex4.noise <-'
@@
 
-```{r plot for loglikelihood ex4 adults}
+```{r plot for loglikelihood ex4 adults, include = T}
 ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#859900","#6c71c4"))
+                    values= c("#859900","#b58900","#6c71c4"))
 ```
@@
 
-```{r bayes factors ex4 adults}
+```{r bayes factors ex4 adults, include = T}
 ex4_bf <- bind_rows(
@@
 ) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
-         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
-         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
+  mutate("pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
+         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
+         "flat_prior_noise > prior_only_noise" = exp(flat_prior_noise - prior_only_noise)) %>%
   select(-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)
@@
 
-```{r visualize model parameters children}
+```{r visualize model parameters children, include = T}
 # visualize inferred parameter
@@
 
-```{r visualize prior children}
+```{r visualize prior children, include = T}
 # visualize model priors in comparison to data 
@@
 
-```{r visualize speaker optimality children}
+```{r visualize speaker optimality children, include = T}
 # visualize speaker optimality in comparison to data 
@@
 
-```{r}
-# child_ex3_flat_prior_model_noise<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   model_var = "model",
-#   chains = 4,
-#   cores = 4,
-#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
-# )%>%
-#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")
-
-# model predictions
-child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(!(Parameter %in% c("noise"))) %>%
-  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model, age,alignment,speaker) %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value), 
-            ci_upper =hdi_upper(value))%>%
-  ungroup()%>%
-  mutate(age = as.numeric(age))
-
-## noise parameter
-child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  summarise(mean = estimate_mode(value), 
-            ci_lower = hdi_lower(value),
-            ci_upper = hdi_upper(value))
-
-```
-
 ## Compare model predictions to data
@@
 
-```{r}
+```{r, include = T}
 child_noise_parameters <- bind_rows(
@@
 ### Developmental noise parameters
-```{r}
+```{r, include = T}
 developmental_noise_parameter <- data_frame(
@@
 
-```{r plot model predictions ex3 children}
+```{r plot model predictions ex3 children, include = T}
 child_model_predictions <- bind_rows(
   child_ex3_pragm_model_predictions_noise,
-  #child_ex3_pragm_model_predictions_developmental_noise,
-  child_ex3_pragm_model_predictions,
-  child_ex3_prior_only_model_predictions_noise,
-  child_ex3_flat_prior_model_predictions_noise
+  child_ex3_pragm_model_predictions_developmental_noise, 
+  child_ex3_pragm_model_predictions
+  #child_ex3_prior_only_model_predictions_noise,
+  #child_ex3_flat_prior_model_predictions_noise
   #child_ex3_flat_prior_model_predictions,
@@
 
-```{r correlation plot ex3 children}
+```{r correlation plot ex3 children, include = T}
 child_cor_data <- child_ex3_data %>%
-  filter(trial != "filler1",
-         trial != "filler2")%>%
-  group_by(speaker, alignment, age_bin) %>%
+  group_by(age_bin,speaker, alignment) %>%
   summarize(k = sum(correct_inf), n = n())%>%
@@
   ungroup()%>%
-  mutate(Data = rep(child_cor_data$Data,4),
-         Data_ci_lower = rep(child_cor_data$Data_ci_lower,4),
-         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,4))
-
-ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
+  mutate(data_mode = rep(child_cor_data$data_mode,3),
+         data_ci_lower = rep(child_cor_data$data_ci_lower,3),
+         data_ci_upper  =rep( child_cor_data$data_ci_upper,3))
+
+ggplot(data = child_cor_plot,aes(x = model_mode, y = data_mode, col = age)) +
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
   geom_point(size = 3)+
-  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
   coord_fixed()+
   facet_grid(~model)+
-  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mode, y = data_mode), inherit.aes = F)+
   xlim(0,1)+ylim(0,1)+
   xlab("Model")+
+  ylab("Data")+
   theme_few() + 
@@
 
-```{r pragmatic model ex3 children}
+```{r loglike pragmatic model ex3 children}
 child.ex3.rsa.marginal.likelihood <-'
@@
 
-```{r}
+```{r loglike pragmatic model noise ex3 children}
 child.ex3.rsa.noise.marginal.likelihood <-'
@@
 
-```{r}
+```{r loglike pragmatic model developmental noise ex3 children}
 child.ex3.rsa.developmental.noise.marginal.likelihood <-'
@@
 
-```{r plot model loglikes ex3 children}
+```{r plot model loglikes ex3 children, include = T}
 ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
@@
 
-```{r bayes factors ex3 children}
+```{r, include = T}
+child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
+  filter(model == "pragmatic")%>%
+  spread(parameter, logP) %>%
+  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
+         "noise > parameter free" = exp(noise - `parameter free`),
+         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
+  select(-`parameter free`,-`developmental noise`, -noise)
+
+child_ex3_pragmatic_models_bf%>%
+  kable(digits = 2)
+```
+
+```{r bayes factors ex3 children, include = T}
 child_ex3_bf <- child_ex3_model_comparison%>%
@@
 ```
-
-# Appendix 1: Fully Bayesian analysis

### 2019-06-19 papers/full_paper/SI_appendix.Rmd
first draft supplementaries

@@
 Here we present details for the cognitive models as well as supplementary analysis and results.
-Readers who are interested in the model or analysis code itself are encouraged to consult the corresponding online repository: (https://github.com/manuelbohn/mcc).
+Readers who are interested in the model and/or analysis code itself are encouraged to consult the corresponding online repository: (https://github.com/manuelbohn/mcc).
 
@@
 
-All models were computed in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
+Cognitive models were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
 
@@
 
-The pragmatics model had the same basic structure as the model in Frank and Goodman [-@frank2014inferring].
-It captures the following process: A pragmatic listener ($L_1$) reasons about a pragmatic speaker ($S_1$) who is reasoning about a naive listener ($L_0$) who interprets utterances according to their literal semantics.
+The pragmatics model captures the following process: A pragmatic listener ($L_1$) reasons about a pragmatic speaker ($S_1$) who is reasoning about a literal listener ($L_0$) who interprets utterances according to their literal semantics.
 The outcome is the posterior probability of a particular referent given an utterance.
@@
 \begin{equation} 
-P_{L_1}(r_s|u)\propto P_{S_1}(u|r_s)P_{S_i}(r_s)
+P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P_(r)
 \end{equation}
 
-The right side of this equation has two components, the likelihood $P_{S1}(u|r_s)$ and the prior $P_{S_i}(r_s)$.
-The likelihood represent the probability that a particular utterance is used to refer to the referent.
-It is defined in terms of a utility function $U_S(u;s)$:
+The right side of this equation has three components, the likelihood $P_{S1}(u|r)$, the probability of the lexicon that is considered ($P(L)$) and the prior $P(r)$.
+Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon (i.e.
+word - object mapping) is more likely.
+In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexical.
+
+The likelihood represent the probability that ($S_1$) uses a particular utterance to refer to the referent. It is defined in terms of the informativity of an utterance for a referent:
 
 \begin{equation} 
-P_{S_1}(u|r_s)\propto exp(\alpha U_{S_1}(u;s))
+P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
 \end{equation}
 
-This utility is defined as the surprisal of $u$ for a literal listener, $L_0$:
+The informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance: Because the listener is assumed to not know the lexicon, the informativity of the utterance averages over the possible lexical, or words meanings, that $L_0$ considers
 
 \begin{equation} 
-U_{S_1}(r_s) = logL_0(r_s|u)
+Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
 \end{equation}
 
-The literal listener computes the probability of $r_s$ according to its literal semantics.
-In our case, all objects (and their names) were new to the listener.
-That is, $L_0$ could not rely on the semantics of the utterance to discriminate between referents.
-However, the utterance also included the agents turn to one of the tables.
+while $P(r)$ again denotes the prior probability of a referent, $L_{lit}$ encodes the literal meaning of an utterance given a particular lexicon, returning 1 if the utterance is literally true and 0 if the utterance is literally false.
+As mentioned above, because $L_1$ does not know the lexicon, the semantics of the words contained in the utterance offer no information about the referent.
+The non-linguistic aspects of the utterance, however, do.
+As described in the main text, the utterance also included the agent's turn to one of the tables.
 The semantics of turning to one of the tables is roughly equal to using a word that could be used to describe the objects on that table.
-In addition to the utterance, $L_0$ also takes in the prior probability of the referent given the speaker.
-It is therefore defined as:
+That is, $L_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
 
-\begin{equation} 
-P_{L0}(r_s|u)\propto [\![u]\!](r_s)P_{S_i}(r_s)
-\end{equation}
+### Model parameters
 
-Now, $S_1$ is assumed to choose the utterance that yields the highest utility for $L_0$. This captures the idea that speakers are trying to communicate in an informative way.
-
-As noted in the paper, the parameter $\alpha$ (speaker optimality parameter) in equation 2  determines the absolute strength of the likelihood term.
-It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
+As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term.
+It's interpretation is *how* rational $L$ thinks $S$ is in this particular context.
 For adults, we used the data from Experiment 1 to infer the value of $\alpha$.
-That is, we inferred which value of $\alpha$ would generate model predictions for the RSA model described above (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in Experiment 1.
-This value was then used for $\alpha$ in Experiment 3.
+That is, we inferred which value of $\alpha$ would generate model predictions for the RSA model (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in Experiment 1.
+This value for $\alpha$ was then used in Experiment 3 and 4.
 
 For children, the speaker optimality parameter changed with age.
-Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept that best described the developmental trajectory in the data.
+Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
 As for adults, this was done via the RSA model with equal prior probability for each object.
@@
 
-The prior distribution over objects, $P_{S_i}(r_s)$, varied with the common ground manipulation, the identity of the speaker (indicated by subscript *i*) and the alignment of utterance and common ground information.
+The prior distribution over objects, $P(r)$, varied with the common ground manipulation, the identity of the speaker and the alignment of utterance and common ground information.
 Numerically, it depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children.
 
-For adults, this worked in the following way.
-For example, in Experiment 2, for the preference/same speaker condition, when the speaker indicated that they liked object A and disliked object B, the average proportion with which participants chose object A was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for object B it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
+For adults, this worked in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker indicated that they liked object A and disliked object B, the average proportion with which participants chose object A was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for object B it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
 In Experiment 3, this measurement determined the prior distribution over objects in cases whenever the the same manipulation was used (preference/same speaker).
@@
 
-For children, we used the data from Experiment 6 to model the slope and intercept that best described the developmental trajectory in the data for each of the two conditions (see online repository for corresponding code).
+For children, we used the data from Experiment 6 to model the slope and intercept that best described the developmental trajectory in the data for each of the two conditions.
 As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age.
@@
 
-The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused on  common ground manipulation. It is defined as:
+The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused only on common ground manipulation. It is defined as:
 
 \begin{equation} 
-P_{L1}(r_s|u)\propto P_{S_i}(r_s)
+P_{L}(r|u)\propto P(r)
 \end{equation}
@@
 
-# Experiment 4
-
-## Prior strength manipualtions
+# Prior strength manipualtions Experiment 4
 
@@
 
-Below we describe the different ways in which prior strength was manipulated.
+Below we describe the different ways in which prior strength was manipulated in Experiment 4.
 The corresponding experiments can be found in the online repository.
@@
 
-Table \ref{tab:table_prior} shows the results of a generalized linear mixed model (GLMM), fir to the data from each manipulation.
+Table \ref{tab:table_prior} shows the results of a generalized linear mixed model (GLMM) fit to the data from each manipulation.
 The results show that the parameter estimates for condition (i.e.
@@
 
-## Model predictions
+# Model comparison
 
-Figure \ref{fig:modelpredex4} compares model predictions to the data from Experiment 4.
+Analysis code for model comparison can be found in the online repository.
+
+## Experiment 3
+
+Here we report details on the model comparisons.
+Model fit was assessed based on marginal log-likelihoods of the data under each model.
+Bayes Factors were computed by first subtracting log-likelihoods and then exponentiating the result.
+Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3.
+We did not pre-register the inclusion of the noise parameter for Experiment 3, but did so for all subsequent experiments for which we did model comparisons (4 and 7).
+The first row in Table \ref{tab:ex3_comp} compares the pragmatics model with noise parameter to the model without the noise parameter.
+This comparison shows that including the noise parameter greatly improves model fit.
+Figure \ref{fig:modelpredex3} compares model predictions from the models including noise parameters to the data from Experiment 3.
+
+```{r modelpredex3, include = T, fig.cap = "Correlation plot for model predictions and data from Experiment 3.
+All models depicted here included a noise parameter.
+Coefficients and p-values are based on Pearson correlation statistics.
+Dots represent condition modes.
+Error bars represent 95\\% HDIs.", fig.height=2.5}
+
+adult_ex3_data_summary <- adult_ex3_data %>%
+  mutate(model = "data") %>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+# summarize model predictions
+
+ex3_flat_prior_model_pred_noise <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="flat_prior_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+ex3_prior_only_model_pred_noise <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="prior_only_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+ex3_pragm_model_pred_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic_noise")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+ex_3_model_pred <- bind_rows(
+  ex3_flat_prior_model_pred_noise,
+  ex3_prior_only_model_pred_noise,
+  ex3_pragm_model_pred_noise
+)
+
+# combine model predictions and data
+
+ex_3_pred <- bind_rows(
+  ex_3_model_pred,
+  adult_ex3_data_summary
+)
+
+ex_3_cor_plot <- ex_3_pred %>%
+  ungroup()%>%
+  filter(model != "data") %>%
+  left_join(., ex_3_pred %>%
+    ungroup()%>%
+    filter(model == "data") %>%
+    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
+    select(-model)
+  )%>%
+  mutate(model =  case_when(model == "pragmatic_noise" ~ "Pragmatics",
+                            model == "prior_only_noise" ~ "Prior only",
+                            model == "flat_prior_noise" ~ "Flat prior"
+                            ))
+
+ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "1")) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
+  geom_point(size = 2)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
+  coord_fixed()+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid ( ~ model) +
+  guides(col = F)+
+  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
+  theme_few(base_size = )+
+  scale_color_manual(values = c("#4477AA"))+
+  theme(legend.position = "right")
+
+```
+
+```{r ex3_comp,results = "asis"}
+log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+
+ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
+  mutate(model = "pragmatic_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
+  mutate(model = "prior_only_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
+  mutate(model = "flat_prior_noise")%>%
+  group_by(model)%>%
+  summarize(logP = logSumExp(value))
+
+ex3_model_comparison <- bind_rows(
+  log_like_pragmatic_ex3,
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+)%>%
+  mutate(model = reorder(model,logP))
+
+ex3_bf <- bind_rows(
+  log_like_pragmatic_ex3,
+  ex3_pragm_model_noise_loglike,
+  ex3_flat_prior_model_noise_loglike,
+  ex3_prior_only_model_noise_loglike
+) %>% spread(model, logP) %>%
+  mutate("pragmatic_noise > pragmatic" = exp(pragmatic_noise - pragmatic),
+         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
+         "pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
+         "prior_only_noise > flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
+  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
+  gather(Comparison, BF)%>%
+  mutate(BF = formatC(BF,2))
+
+apa_table(
+  ex3_bf
+  , caption = "Bayes Factors for model comparisons in Experiment 3"
+  , escape = T
+)
+
+```
+
+```{r ex3noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.height = 2}
+ex3_noise_parameters <- bind_rows(
+  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Pragmatics"),
+  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Prior only"),
+  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  mutate(Model = "Flat prior")
+  )
+
+ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
+  geom_density(alpha = .5)+
+  theme_few()+
+  xlab("Noise parameter")+
+  xlim(0,1)+
+  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))+
+  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+                    values= c("#b58900","#6c71c4","#859900"))
+```
+
+Figure \ref{fig:ex3noise} shows the posterior distribution of the noise parameter for each model.
+The noise parameter was fit to the data and indicates the proportion of responses that are estimated to be due to random guessing rather than in line with model predictions.
+Consequently, a model that makes predictions that are closer to the data is likely to have a lower noise parameter.
+
+## Experiment 4
 
@@
 Dots represent condition modes.
-Error bars represent 95\\% HDIs.", fig.height=2.5}
+Error bars represent 95\\% HDIs.", fig.height=3}
 
@@
   scale_colour_ptol(name = "Prior strength")+
-  theme(legend.position = "right")
+  theme(legend.position = "bottom")
 
 ```
-
-# Model comparison
-
-Analysis code for model comparison can be found in the online repository.
-
-## Experiment 3
-
-Here we report details on the model comparisons based on marginal log-likelihoods of the data for each model.
-Bayes Factors were computed by first subtracting log-likelihoods and then exponentiating the result.
-Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3.
-We did not pre-register the inclusion of the noise parameter for Experiment 4.
-The first row in Table \ref{tab:ex3_comp}
-
-```{r ex3_comp,results = "asis"}
-log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
-
-ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
-  mutate(model = "pragmatic_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
-  mutate(model = "prior_only_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
-  mutate(model = "flat_prior_noise")%>%
-  group_by(model)%>%
-  summarize(logP = logSumExp(value))
-
-ex3_model_comparison <- bind_rows(
-  log_like_pragmatic_ex3,
-  ex3_pragm_model_noise_loglike,
-  ex3_flat_prior_model_noise_loglike,
-  ex3_prior_only_model_noise_loglike
-)%>%
-  mutate(model = reorder(model,logP))
-
-ex3_bf <- bind_rows(
-  log_like_pragmatic_ex3,
-  ex3_pragm_model_noise_loglike,
-  ex3_flat_prior_model_noise_loglike,
-  ex3_prior_only_model_noise_loglike
-) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > pragmatic" = exp(pragmatic_noise - pragmatic),
-         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
-         "pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
-         "prior_only_noise > flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
-  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
-  gather(Comparison, BF)%>%
-  mutate(BF = formatC(BF,2))
-
-apa_table(
-  ex3_bf
-  , caption = "Bayes Factors for model comparisons in Experiment 3"
-  , escape = T
-)
-
-```
-
-Figure \ref{fig:ex3noise} shows the posterior distribution of the noise parameter for each model.
-The noise parameter was fit to the data and indicates the proportion of responses that are estimated to be due to random rather than in line with model predictions.
-That is, a model that makes predictions that are closer to the data is likely to have a lower noise parameter.
-
-```{r ex3noise, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 3", fig.height = 2}
-ex3_noise_parameters <- bind_rows(
-  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Pragmatics"),
-  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Prior only"),
-  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
-  filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Flat prior")
-  )
-
-ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
-  geom_density(alpha = .5)+
-  theme_few()+
-  xlab("Noise parameter")+
-  xlim(0,1)+
-  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
-                    values= c("#b58900","#6c71c4","#859900"))+
-  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
-```
-
-## Experiment 4
-
-Table \ref{tab:ex4_comp} shows Bayes Factors for model comparisons in Experiment 3. As pre-registered, all models included a noise parameter.
 
@@
   ex4_bf
-  , caption = "Model comparisons in Experiment 3"
+  , caption = "Model comparisons in Experiment 4"
   , note = "BF = Bayes Factor; All models include a noise parameter."
@@
 
-Figure \ref{fig:ex4noise} shows the posterior distribution of the noise parameter for each model in Experiment 4.
-
-```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 3", fig.height = 2}
+```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.height = 2}
 ex4_noise_parameters <- bind_rows(
@@
 
+Figure \ref{fig:modelpredex4} compares model predictions to the data from Experiment 4.
+Table \ref{tab:ex4_comp} shows Bayes Factors for model comparisons in Experiment 3.
+As pre-registered, all models included a noise parameter.
+Figure \ref{fig:ex4noise} shows the posterior distribution of the noise parameter for each model in Experiment 4.
+
 ## Experiment 7
@@
 We added the additional model comparisons because the noise parameter was comparably high.
-The additional model comparisons allow us to see if the pragmatics model provides a better fit when the more emphasis is put on the model structure itself.
+The additional model comparisons allow us to see if the pragmatics model provides a better fit when more emphasis is put on the model structure itself.
 The results show that this was the case.
@@
 Table \ref{tab:child_bf} shows results for model comparison for the different types of noise parameters.
-In any case, the pragmatics model provides a substantially better fit to the data compared to the alternative models
+In all cases, the pragmatics model provides a substantially better fit to the data compared to the alternative models.
 
@@
 
+Finally, Figure \ref{fig:childcor} shows correlations between model predictions and the data, binned by year.
+Across noise parameters, model predictions and data are closest aligned (i.e.
+closest to the dotted line) for the pragmatics model, thereby corroborating the conclusions drawn based on the model comparison and the evaluation of the noise parameters.
+
+```{r childcor,  include = T, fig.cap = "Correlation plot for model predictions and data for all models considered in Experiment 7.
+Coefficients and p-values are based on Pearson correlation statistics.
+Dots represent condition modes.
+Error bars represent 95\\% HDIs.", fig.height = 7}
+
+# child_cor <- bind_rows(
+#   readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Pragmatic",
+#          noise = "Noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+# 
+#   readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Flat prior",
+#          noise = "Noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#   readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Prior only",
+#          noise = "Noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#     readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Pragmatic",
+#          noise = "Dev. noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+# 
+#   readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Flat prior",
+#          noise = "Dev. noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#   readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
+#   filter(!(Parameter %in% c("noise"))) %>%
+#   separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Prior only",
+#          noise = "Dev. noise")%>%
+#   group_by(model, noise,age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#   
+#   readRDS("../../stats/saves/child_ex3_pragm_model_param_free.rds") %>%
+#   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
+#   mutate(value = `1`,
+#          age = as.numeric(age))%>%
+#   select(-`1`)%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Pragmatic",
+#          noise = "Param. free")%>%
+#   group_by(model,noise, age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#   readRDS("../../stats/saves/child_ex3_prior_only_model_param_free.rds") %>%
+#   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
+#   mutate(value = `1`,
+#          age = as.numeric(age))%>%
+#   select(-`1`)%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Prior only",
+#          noise = "Param. free")%>%
+#   group_by(model,noise, age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value)),
+#   
+#   readRDS("../../stats/saves/child_ex3_flat_prior_model_param_free.rds") %>%
+#   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
+#   mutate(value = `1`,
+#          age = as.numeric(age))%>%
+#   select(-`1`)%>%
+#   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
+#   mutate(model = "Flat prior",
+#          noise = "Param. free")%>%
+#   group_by(model,noise, age,alignment,speaker) %>%
+#   summarise(mean = estimate_mode(value), 
+#             ci_lower = hdi_lower(value), 
+#             ci_upper =hdi_upper(value))
+# 
+# )
+
+p_child_ex3_data <- child_ex3_data %>%
+  mutate(age = as.character(age_bin), 
+         model = "Data")%>%
+  group_by(model,age, alignment, speaker) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         mean = (a-1)/(a+b-2),
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b))%>%
+  select(-a,-b,-n,-k)
+
+p_child_cor<- readRDS("../../stats/saves/child_all_models_cor.rds") %>%
+  na.omit()%>%
+  ungroup()%>%
+  mutate(data_mean = rep(p_child_ex3_data%>%pull(mean),9),
+         data_ci_upper = rep(p_child_ex3_data%>%pull(ci_upper),9),
+         data_ci_lower = rep(p_child_ex3_data%>%pull(ci_lower),9))
+
+ggplot(p_child_cor, aes(x = mean, y = data_mean, col = age)) +
+  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
+  geom_point(size = 3)+
+  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
+  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
+  coord_fixed()+
+ stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
+  xlim(0,1)+ylim(0,1)+
+  xlab("Model")+
+  ylab("Data")+
+  facet_grid(model~noise)+
+  theme_few() + 
+  scale_colour_ptol(name = "Age")+
+  theme(legend.position = "bottom")
+
+```
+
 \newpage

### 2019-06-21 papers/full_paper/SI_appendix.Rmd
add numerical example for model

@@
 \begin{equation} 
-P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P_(r)
+P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
 \end{equation}
@@
 That is, $L_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
+
+### Numerical Example
+
+Prior = 0.6416667
+SO = 2.242435
+
+\begin{equation} 
+Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
+Informativity(u; r_1) = ln(0.6416667 * 1) = -0.4436863
+Informativity(u; r_1) = ln(0.3583333 * 1) = -1.026292
+\end{equation}
+
+(For the above, I get the same results from the model if get these values from webppl)
+
+\begin{equation} 
+P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
+P_{S_1}(u|r_1) = exp(2.242435 * -0.4436863)/(exp(2.242435 * -0.4436863)+exp(2.242435 * -1.026292)) = 0.7869194
+P_{S_1}(u|r_2) = exp(2.242435 * -1.026292)/(exp(2.242435 * -0.4436863)+exp(2.242435 * -1.026292)) = 0.2130806
+\end{equation}
+
+\begin{equation} 
+P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
+P_{L_1}(r_1,L|u) = 0.7869194 * 0.6416667 /(0.7869194 * 0.6416667+0.2130806 * 0.3583333) = 0.8686484
+\end{equation}
+
+Result should be: 0.9077334746997058
 

### 2019-06-25 papers/full_paper/SI_appendix.Rmd
add numerical example for model
update numerical example

--- 2019-06-19 papers/full_paper/SI_appendix.Rmd
@@
 That is, $L_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
+
+### Numerical Example
+
+P(r_1) = 0.6416667
+P(r_2) = 0.3583333
+SO = 2.242435
+
+u_1 = point to table with 2 objects
+u_2 = point to table with 1 object
+
+\begin{equation} 
+Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
+Informativity(u_1; r_1) = log(0.6416667 * 1) = -0.4436863
+Informativity(u_2; r_1) = log(0.6416667 * 0) = -Inf
+Informativity(u_1; r_2) = log(0.3583333 * 1) = -1.026292
+Informativity(u_2; r_2) = ???? = 0
+Informativity(u_1; r_3) = log(0.3583333 * ) = -Inf
+Informativity(u_2; r_3) = ???? = 0
+
+\end{equation}
+
+\begin{equation} 
+P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
+P_{S_1}(u_1|r_1) = exp(2.242435 * -0.4436863)/(exp(2.242435 * -0.4436863)) = 1
+P_{S_1}(u_1|r_2) = exp(2.242435 * -1.026292)/(exp(2.242435 * -1.026292)+ exp(2.242435 * 0)) = 0.09100765
+P_{S_1}(u_1|r_3) = exp(2.242435 * -1.026292)/(exp(2.242435 * -1.026292)+ exp(2.242435 * 0)) = 0.09100765 <-- Why????
+\end{equation}
+
+(For the above, I get the same results from the model if get these values from webppl)
+
+\begin{equation} 
+P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
+P_{L_1}(r_1,L|u) = 1 * 0.6416667 /(1*0.6416667 + 0.09100765*0.3583333 + 0.09100765*0.3583333) = 0.9077335
+\end{equation}
 

### 2019-06-26 papers/full_paper/SI_appendix.Rmd
add prose to numerical example

--- 2019-06-19 papers/full_paper/SI_appendix.Rmd
@@
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
+
+### Numerical Example
+
+In the following, we walk through a numerical example for how model predictions were generated for the pragmatics model.
+The prediction will correspond to the parameter free model, excluding the noise parameter.
+The numbers are taken from the preference - different speaker - congruent condition.
+Fig.
+1 shows a screenshot from the adult experiment, which the model was designed to capture.
+In this context, there are three potential referents (two red-ish, one yellow-ish), of two types (red-ish and yellow-ish) on two tables.
+In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request or $u_2$, which involves turning to the left table (single object) and making a request.
+In the experiment, the speaker chose $u_1$ and we therefore model $L_1$'s interpretation of this utterance.
+
+```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot from adult experiment.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup.png")
+```
+
+From a learning perspective, we assume that the listener is learning the mappings between labels and object types instead of object tokens.
+That is, the listener either thinks the novel word refers to "red-ish objects" or "yellow-ish objects".
+
+The prior distribution over objects (left to right in Fig.1), based on Experiment 2A, for this condition was [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
+That is, the yellow object has a higher a priory probability compared to red objects.
+We start with calculating the informativity of of the utterance for each referent (red or yellow object) based on equation 3.
+
+$$
+\begin{aligned}
+&Informativity(u_1; r_1) = log(0.64 \cdot 1) = -0.44 \\
+&Informativity(u_1; r_2) = log(0.36 \cdot 1) = -1.03
+\end{aligned}
+$$
+
+with $r_1$ being the yellow object and $r_2$ being the red object.
+Next we can insert these values into equation 2 to compute the probability that the speaker chooses this utterance to refer to this type of object.
+To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
+
+$$
+\begin{aligned}
+&P_{S_1}(u_1|r_1) = \frac{exp(2.24 \cdot -0.44)}{exp(2.24 \cdot -0.44)} = 1 \\
+&P_{S_1}(u_1|r_2) = \frac{exp(2.24 \cdot -1.03)}{exp(2.24 \cdot -1.03) + exp(2.24 \cdot 0)} = 0.09
+\end{aligned}
+$$
+
+Here, the informativity for a referent is normalized across all utterances that could be used to refer to this referent.
+Finally, based on equation 1 we can use these values to compute the probability that the speaker thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
+
+$$
+\begin{aligned}
+&P_{L_1}(r_1,L|u_1) = \frac{1 * 0.64}{1\cdot0.64 + 0.09\cdot0.36 + 0.09\cdot0.36} = 0.91
+\end{aligned}
+$$
+
+Thus, we normalize across all potential states that the utterance could refer to.
 
@@
 ```{r childcor,  include = T, fig.cap = "Correlation plot for model predictions and data for all models considered in Experiment 7.
-Coefficients and p-values are based on Pearson correlation statistics.
 Dots represent condition modes.

### 2019-06-27 papers/full_paper/SI_appendix.Rmd
begin reformulating model section in terms of sets

@@
 
+## Ontology
+
+The situation we model is defined by three sets: referents $r$, utterances $u$, and lexica $L$. 
+Referents are defined two features: the type of object they are (visually discernible given their shape and color) and their location (a table).
+There are two types $t_1$, $t_2$ and two locations $l_1$ and $l_2$.
+The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (i.e., a table) and labels are novel words, which are assumed to refer to the type of the object.
+The action of the turning or pointing reduces the set of referents to those that are on the table targeted by the turn (point) and interpreting a label reduces that set further to that which is of the type referred to by that label.
+The interpretation of a label involves a lexicon $L$, which provides the label--type mappings.
+There are two lexica: one which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and one which has the inverse mapping.
+
 ## Pragmatics model
 
-The pragmatics model captures the following process: A pragmatic listener ($L_1$) reasons about a pragmatic speaker ($S_1$) who is reasoning about a literal listener ($L_0$) who interprets utterances according to their literal semantics.
-The outcome is the posterior probability of a particular referent given an utterance.
-According to Bayes rule it is defined as:
+The pragmatics model is a Rational Speech Act model that captures the following process: A pragmatic listener ($L_1$) jointly infers a referent (what object is being picked out by the utterance) and a lexicon (what does the utterance mean) by reasoning about a pragmatic speaker ($S_1$) who produces utterances to convey information to a literal listener ($L_0$), who in turn interprets utterances according to their literal meaning.
+According to Bayes rule, this inference is given by:
 
@@
 
-The right side of this equation has three components, the likelihood $P_{S1}(u|r)$, the probability of the lexicon that is considered ($P(L)$) and the prior $P(r)$.
-Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon (i.e.
-word - object mapping) is more likely.
-In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexical.
+The right side of this equation has three components: the prior distribution over referents $P(r)$, the prior distribution over lexica (word - object mappings) $P(L)$, and the likelihood that a speaker would produce the an utterance $u$ given a referent $r$ ($P_{S1}(u|r)$).
+In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we assume could be non-uniform due to our common ground manipulations (see below).
+Objects are defined a single feature: the type of object they are.
+
+The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (i.e., a table) and labels are novel words, which are assumed to refer to the type of the object.
+The action of the turning or pointing rules out the referents that are not on the table targeted by the turn (point). 
+The listener knows that the labels refer to the kind of object but does not know which kind is referred to be which label, formalized by the prior over lexica $P(L)$. 
+For example, in SI Figure 1,  two possible labels are "dax" and "wug", each of which could either mean.
+
+the listener's prior has no substantive knowledge of the meanings of the labels that a speaker could produce.
+
+In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
+
+Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon  is more likely.
+In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexica.
 
@@
 1 shows a screenshot from the adult experiment, which the model was designed to capture.
-In this context, there are three potential referents (two red-ish, one yellow-ish), of two types (red-ish and yellow-ish) on two tables.
-In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request or $u_2$, which involves turning to the left table (single object) and making a request.
+In this context, there are three potential referents (two red-ish: $r_1^r$, $r_2^r$; one yellow-ish, $r_3^y$,), of two types (red-ish and yellow-ish) on two tables.
+In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
 In the experiment, the speaker chose $u_1$ and we therefore model $L_1$'s interpretation of this utterance.
@@
 The prior distribution over objects (left to right in Fig.1), based on Experiment 2A, for this condition was [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
-That is, the yellow object has a higher a priory probability compared to red objects.
-We start with calculating the informativity of of the utterance for each referent (red or yellow object) based on equation 3.
+That is, the yellow object has a higher a priori probability compared to red objects, because the speaker previously displayed a preference for a yellow object.
+The informativity of the observed utterance for each referent (red or yellow object) can be calculated based on equation 3.
 

### 2019-06-28 papers/full_paper/SI_appendix.Rmd
refactor supplemental model and worked example

--- 2019-06-26 papers/full_paper/SI_appendix.Rmd
@@
 
+## Ontology
+
+The situation we model is defined by three sets: referents $r$, utterances $u$, and lexica $\mathcal{L}$. 
+Referents are defined by two features: the type of object they are (visually discernible given their shape and color) and their location (one of two tables).
+There are two types of objects $t_1$, $t_2$ and two locations $l_1$ and $l_2$.
+The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
+The action of turning or pointing reduces the set of referents to those that are on the table targeted by the turn (point); interpreting a label reduces that set further to those which are of the type referred to by that label.
+The interpretation of a label requires a lexicon $\mathcal{L}$, which provides the label--type mappings.
+There are two lexica: one which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and one which has the inverse mapping.
+
 ## Pragmatics model
 
-The pragmatics model captures the following process: A pragmatic listener ($L_1$) reasons about a pragmatic speaker ($S_1$) who is reasoning about a literal listener ($L_0$) who interprets utterances according to their literal semantics.
-The outcome is the posterior probability of a particular referent given an utterance.
-According to Bayes rule it is defined as:
+Our word-learning model is a model of pragmatic reasoning couched in the Rational Speech Act modeling framework.
+The model describes the following process: A pragmatic listener ($L_1$) jointly infers a referent (what object is being picked out by the utterance) and a lexicon (label--type mappings) by reasoning about a pragmatic speaker ($S_1$) who produces utterances to convey information to a literal listener ($L_0$), who in turn interprets utterances according to their literal meaning.
+According to Bayes rule, this inference is given by:
 
 \begin{equation} 
-P_{L_1}(r,L|u)\propto P_{S_1}(u|r)P(L)P(r)
+P_{L_1}(r, \mathcal{L}|u)\propto P_{S_1}(u|r)P( \mathcal{L})P(r)
 \end{equation}
 
-The right side of this equation has three components, the likelihood $P_{S1}(u|r)$, the probability of the lexicon that is considered ($P(L)$) and the prior $P(r)$.
-Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon (i.e.
-word - object mapping) is more likely.
-In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexical.
-
-The likelihood represent the probability that ($S_1$) uses a particular utterance to refer to the referent. It is defined in terms of the informativity of an utterance for a referent:
+The right-hand side of this equation has three components: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce the an utterance $u$ given a referent $r$ ($P_{S1}(u|r)$).
+In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see below for common ground manipulations).
+Because the labels produced by the speaker are all novel words, the listener has no substantive knowledge about the lexica (label--type mappings) and the prior over the two lexica (described above) is uniform.
+
+The listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent:
 
@@
 
-The informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance: Because the listener is assumed to not know the lexicon, the informativity of the utterance averages over the possible lexical, or words meanings, that $L_0$ considers
+The informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
 
 \begin{equation} 
-Informativity(u; r) = ln P(r|u) \propto ln \sum_L P(r,l|u) P(L) \propto P(r) L_{lit}
+Informativity(u; r) = \ln P_{L_0}(r|u)
 \end{equation}
 
-while $P(r)$ again denotes the prior probability of a referent, $L_{lit}$ encodes the literal meaning of an utterance given a particular lexicon, returning 1 if the utterance is literally true and 0 if the utterance is literally false.
-As mentioned above, because $L_1$ does not know the lexicon, the semantics of the words contained in the utterance offer no information about the referent.
-The non-linguistic aspects of the utterance, however, do.
-As described in the main text, the utterance also included the agent's turn to one of the tables.
-The semantics of turning to one of the tables is roughly equal to using a word that could be used to describe the objects on that table.
-That is, $L_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
+We assume that the speaker believes the literal listener to also be uncertain about the lexicon; that is, the pragmatic listener believes that the speaker (correctly) believes that the listener does not know the lexicon.
+Because the literal listener is assumed to not know the lexicon, the informativity of the utterance averages over the possible lexical, or words meanings, that $L_0$ considers:
+
+\begin{equation} 
+P_{L_0}(r|u) = \sum_L P_{L_0}(r, \mathcal{L}|u)
+\end{equation}
+
+where $P_{L_0}(r, \mathcal{L}|u)  \propto \mathcal{L}_{lit} P(r) P(\mathcal{L})$.
+$P(r)$ again denotes the prior probability of a referent, $\mathcal{L}_{lit}$ encodes the literal meaning of an utterance given a particular lexicon, returning 1 if the utterance is literally true and 0 if the utterance is literally false.
+As mentioned above, because $L_1$ does not know the lexicon, the semantics of the words contained in the utterance (i.e., the labels) offer no information about the referent.
+The non-linguistic aspect of the utterance (the turning or pointing), however, do.
+As described in above, the semantics of turning to one of the tables is roughly equivalent to saying "It's an object on that table".
+That is, $\mathcal{L}_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
+
+### Worked Example
+
+In the following, we work through a numerical example for how model predictions were generated for the pragmatics model.
+The prediction will correspond to the parameter free model described above (excluding the noise parameter).
+The values of the parameters are taken from the preference - different speaker - congruent condition.
+Fig.
+1 shows a screenshot from the adult experiment, which the model was designed to capture.
+In this context, there are three potential referents (two red-ish: $r_1^r$, $r_2^r$; one yellow-ish, $r_3^y$,), of two types (red-ish and yellow-ish) on two tables.
+In principle, the speaker, the frog in this case, can perform one of four utterances, turning either to the left or right table and producing either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
+We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax".
+
+<!-- $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
+In the experiment, the speaker chose $u_1$ and we therefore model $L_1$'s interpretation of this utterance.
+-->
+
+```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot from adult experiment.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup.png")
+```
+
+The listener is learning the mappings between labels and object types (rather than object tokens).
+That is, the listener either thinks the novel word "dax" refers to "red-ish objects" or "yellow-ish objects".
+Turning or pointing to a table always has the same meaning.
+These semantics can be described using two lexica: $\mathcal{L_1} = \{dax: \text{red-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L_2} = \{dax: \text{yellow-ish thing}, wug: \text{red-ish thing}, point: \text{location of point}\}$.
+
+MH: SHOULD MAKE THIS A DISTRIBUTION (sums to 1).
+
+The prior distribution over referents $P(r)$ (left to right in Fig.1), based on Experiment 2A, for this condition was [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
+That is, the yellow object has a higher a priori probability compared to red objects, because the speaker previously displayed a preference for a yellow object.
+
+The literal listener's posterior distribution over referents and lexica a support of size six, owing to the unique combinations of referents and lexica. 
+$$
+\begin{aligned}
+& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_1^r, u_3) P(r_1^r) P(L_1) = 0 \times 0.36 \times 0.5\\
+& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_2^r, u_3) P(r_2^r) P(L_1) = 1 \times 0.36 \times 0.5\\
+& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_3^y, u_3) P(r_3^y) P(L_1) = 0 \times 0.64 \times 0.5\\
+& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_1^r, u_3) P(r_1^r) P(L_2) = 0 \times 0.36 \times 0.5\\
+& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_2^r, u_3) P(r_2^r) P(L_2) = 0 \times 0.36 \times 0.5\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_3^y, u_3) P(r_3^y) P(L_2) = 1 \times 0.64 \times 0.5\\
+\end{aligned}
+$$
+
+because the speaker is pointing to the table with $r_2$ and $r_3$, and under $\mathcal{L_1}$, "dax" means the red object and under $\mathcal{L_2}$, "dax" means the yellow object.
+After normalization we have:
+
+$$
+\begin{aligned}
+& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3}) = 0 \\
+& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.36 \\
+& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})   = 0 \\
+& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})   = 0 \\
+& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})   = 0 \\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.64\\
+\end{aligned}
+$$
+
+then,
+
+$$
+\begin{aligned}
+&P_{L_0}(r_1|u_3) =  P_{L_0}(r_1, \mathcal{L_1}|u_3) + P_{L_0}(r_1, \mathcal{L_2}|u_3) = 0+0=0 \\
+&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L_1}|u_3) + P_{L_0}(r_2, \mathcal{L_2}|u_3) = 0.36+0=0.36 \\
+&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L_1}|u_3) + P_{L_0}(r_3, \mathcal{L_2}|u_3) = 0+64=0.64 \\
+\end{aligned}
+$$
+
+and
+
+$$
+\begin{aligned}
+&Informativity(u_3; r_1) = log(0) = -\infty \\
+&Informativity(u_3; r_2) = log(0.36) = -1.03 \\
+&Informativity(u_3; r_3) = log(0.64) = -0.44
+\end{aligned}
+$$
+
+Next we can insert these values into equation 2 to compute the probability that the speaker chooses this utterance to refer to this type of object.
+To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
+
+SEEMS LIKE WE NEED TO NORMALIZE ACROSS ALL UTTERANCES, SO WE WILL NEED TO REDO the ABOVE CALCULATIONS FOR EACH OF THE 6 UTTERANCES.
+
+$$
+\begin{aligned}
+&P_{S_1}(u_3|r_2) = \frac{exp(2.24 \cdot -1.03)}{exp(2.24 \cdot -1.03) + exp(2.24 \cdot 0)} = 0.09 \\
+&P_{S_1}(u_3|r_3) = \frac{exp(2.24 \cdot -0.44)}{exp(2.24 \cdot -0.44)} = 1 \\
+\end{aligned}
+$$
+
+Here, the informativity for a referent is normalized across all utterances that could be used to refer to this referent.
+
+Finally, based on equation 1 we can use these values to compute the probability that the speaker thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
+
+$$
+\begin{aligned}
+&P_{L_1}(r_1,L|u_1) = \frac{1 * 0.64}{1\cdot0.64 + 0.09\cdot0.36 + 0.09\cdot0.36} = 0.91
+\end{aligned}
+$$
+
+Thus, we normalize across all potential states that the utterance could refer to.
+
+<!-- The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (i.e., a table) and labels are novel words, which are assumed to refer to the type of the object.
+-->
+<!-- The action of the turning or pointing rules out the referents that are not on the table targeted by the turn (point).  -->
+<!-- The listener knows that the labels refer to the kind of object but does not know which kind is referred to be which label, formalized by the prior over lexica $P(L)$.  -->
+
+<!-- In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
+-->
+
+<!-- For example, in SI Figure 1, two possible labels are "dax" and "wug", each of which could either mean. -->
+
+<!-- Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon  is more likely.
+In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexica.
+-->
 
@@
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
-
-### Numerical Example
-
-In the following, we walk through a numerical example for how model predictions were generated for the pragmatics model.
-The prediction will correspond to the parameter free model, excluding the noise parameter.
-The numbers are taken from the preference - different speaker - congruent condition.
-Fig.
-1 shows a screenshot from the adult experiment, which the model was designed to capture.
-In this context, there are three potential referents (two red-ish, one yellow-ish), of two types (red-ish and yellow-ish) on two tables.
-In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request or $u_2$, which involves turning to the left table (single object) and making a request.
-In the experiment, the speaker chose $u_1$ and we therefore model $L_1$'s interpretation of this utterance.
-
-```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot from adult experiment.", out.width="400px"}
-knitr::include_graphics("./figures/SI_setup.png")
-```
-
-From a learning perspective, we assume that the listener is learning the mappings between labels and object types instead of object tokens.
-That is, the listener either thinks the novel word refers to "red-ish objects" or "yellow-ish objects".
-
-The prior distribution over objects (left to right in Fig.1), based on Experiment 2A, for this condition was [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
-That is, the yellow object has a higher a priory probability compared to red objects.
-We start with calculating the informativity of of the utterance for each referent (red or yellow object) based on equation 3.
-
-$$
-\begin{aligned}
-&Informativity(u_1; r_1) = log(0.64 \cdot 1) = -0.44 \\
-&Informativity(u_1; r_2) = log(0.36 \cdot 1) = -1.03
-\end{aligned}
-$$
-
-with $r_1$ being the yellow object and $r_2$ being the red object.
-Next we can insert these values into equation 2 to compute the probability that the speaker chooses this utterance to refer to this type of object.
-To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
-
-$$
-\begin{aligned}
-&P_{S_1}(u_1|r_1) = \frac{exp(2.24 \cdot -0.44)}{exp(2.24 \cdot -0.44)} = 1 \\
-&P_{S_1}(u_1|r_2) = \frac{exp(2.24 \cdot -1.03)}{exp(2.24 \cdot -1.03) + exp(2.24 \cdot 0)} = 0.09
-\end{aligned}
-$$
-
-Here, the informativity for a referent is normalized across all utterances that could be used to refer to this referent.
-Finally, based on equation 1 we can use these values to compute the probability that the speaker thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
-
-$$
-\begin{aligned}
-&P_{L_1}(r_1,L|u_1) = \frac{1 * 0.64}{1\cdot0.64 + 0.09\cdot0.36 + 0.09\cdot0.36} = 0.91
-\end{aligned}
-$$
-
-Thus, we normalize across all potential states that the utterance could refer to.
 

### 2019-07-23 papers/full_paper/SI_appendix.Rmd
continue fleshing our numerical example

@@
 There are two types of objects $t_1$, $t_2$ and two locations $l_1$ and $l_2$.
-The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
-The action of turning or pointing reduces the set of referents to those that are on the table targeted by the turn (point); interpreting a label reduces that set further to those which are of the type referred to by that label.
+The utterances available to a speaker are (action, label) pairs, where the action involves turning (pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
+The action of turning (pointing) reduces the set of referents to those that are on the table targeted by the turn (point); interpreting a label reduces that set further to those which are of the type referred to by that label.
 The interpretation of a label requires a lexicon $\mathcal{L}$, which provides the label--type mappings.
@@
 The model describes the following process: A pragmatic listener ($L_1$) jointly infers a referent (what object is being picked out by the utterance) and a lexicon (label--type mappings) by reasoning about a pragmatic speaker ($S_1$) who produces utterances to convey information to a literal listener ($L_0$), who in turn interprets utterances according to their literal meaning.
-According to Bayes rule, this inference is given by:
+According to Bayes rule, the pragmatic listener's inference is given by:
 
@@
 
-The right-hand side of this equation has three components: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce the an utterance $u$ given a referent $r$ ($P_{S1}(u|r)$).
+The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent $r$ ($P_{S1}(u|r)$).
 In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see below for common ground manipulations).
-Because the labels produced by the speaker are all novel words, the listener has no substantive knowledge about the lexica (label--type mappings) and the prior over the two lexica (described above) is uniform.
-
-The listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent:
+Because the labels produced by the speaker are all novel words, the listener has no substantive knowledge about the lexica (label--type mappings) and thus the prior over the two lexica (described above) is uniform.
+
+The pragmatic listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent:
 
@@
 
-The informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
+As spelled out in @GoodmanStuhlmuller2013, the informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
 
@@
 The non-linguistic aspect of the utterance (the turning or pointing), however, do.
-As described in above, the semantics of turning to one of the tables is roughly equivalent to saying "It's an object on that table".
+As described above, the semantics of turning to one of the tables is roughly equivalent to saying "It's an object on that table".
 That is, $\mathcal{L}_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
@@
 
-In the following, we work through a numerical example for how model predictions were generated for the pragmatics model.
+In this section, we work through a toy numerical example for how model predictions were generated for the pragmatics model.
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
-The values of the parameters are taken from the preference - different speaker - congruent condition.
+The values of the parameters are taken from the preference - different speaker - congruent condition (see below).
 Fig.
@@
 In this context, there are three potential referents (two red-ish: $r_1^r$, $r_2^r$; one yellow-ish, $r_3^y$,), of two types (red-ish and yellow-ish) on two tables.
-In principle, the speaker, the frog in this case, can perform one of four utterances, turning either to the left or right table and producing either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
-We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax".
+In principle, the speaker, the frog in this case, can produce one of four utterances, turning either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
+We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
+<-- CHECK ME.
 
@@
 
-MH: SHOULD MAKE THIS A DISTRIBUTION (sums to 1).
-
-The prior distribution over referents $P(r)$ (left to right in Fig.1), based on Experiment 2A, for this condition was [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
-That is, the yellow object has a higher a priori probability compared to red objects, because the speaker previously displayed a preference for a yellow object.
-
-The literal listener's posterior distribution over referents and lexica a support of size six, owing to the unique combinations of referents and lexica. 
+We construct the prior distribution over referents $P(r)$ based on the results of Experiment 2A, in which the speaker displayed a preference for a yellow object (see Model Parameters section below for a detailed description of how this distribution was constructed).
+The prior distribution over referents $P(r)$ (left to right in Fig.1) for this condition was [0.26, 0.26, 0.48].
+<!-- [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
+-->
+
+The literal listener's posterior distribution over referents and lexica has support of size six, owing to the unique combinations of referents and lexica.
 $$
 \begin{aligned}
-& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_1^r, u_3) P(r_1^r) P(L_1) = 0 \times 0.36 \times 0.5\\
-& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_2^r, u_3) P(r_2^r) P(L_1) = 1 \times 0.36 \times 0.5\\
-& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_3^y, u_3) P(r_3^y) P(L_1) = 0 \times 0.64 \times 0.5\\
-& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_1^r, u_3) P(r_1^r) P(L_2) = 0 \times 0.36 \times 0.5\\
-& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_2^r, u_3) P(r_2^r) P(L_2) = 0 \times 0.36 \times 0.5\\
-& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_3^y, u_3) P(r_3^y) P(L_2) = 1 \times 0.64 \times 0.5\\
+& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_1^r, u_3) P(r_1^r) P(L_1) = 0 \times 0.26 \times 0.5\\
+& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_2^r, u_3) P(r_2^r) P(L_1) = 1 \times 0.26 \times 0.5\\
+& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_3^y, u_3) P(r_3^y) P(L_1) = 0 \times 0.48 \times 0.5\\
+& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_1^r, u_3) P(r_1^r) P(L_2) = 0 \times 0.26 \times 0.5\\
+& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_2^r, u_3) P(r_2^r) P(L_2) = 0 \times 0.26 \times 0.5\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_3^y, u_3) P(r_3^y) P(L_2) = 1 \times 0.48 \times 0.5\\
 \end{aligned}
@@
 
-because the speaker is pointing to the table with $r_2$ and $r_3$, and under $\mathcal{L_1}$, "dax" means the red object and under $\mathcal{L_2}$, "dax" means the yellow object.
+because the speaker is pointing to the table with $r_2$ and $r_3$, and under $\mathcal{L}_1$, "dax" means the red object and under $\mathcal{L}_2$, "dax" means the yellow object.
 After normalization we have:
@@
 & P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3}) = 0 \\
-& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.36 \\
+& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.35 \\
 & P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})   = 0 \\
@@
 & P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.64\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.65\\
 \end{aligned}
@@
 \begin{aligned}
-&P_{L_0}(r_1|u_3) =  P_{L_0}(r_1, \mathcal{L_1}|u_3) + P_{L_0}(r_1, \mathcal{L_2}|u_3) = 0+0=0 \\
-&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L_1}|u_3) + P_{L_0}(r_2, \mathcal{L_2}|u_3) = 0.36+0=0.36 \\
-&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L_1}|u_3) + P_{L_0}(r_3, \mathcal{L_2}|u_3) = 0+64=0.64 \\
+&P_{L_0}(r_1|u_3) =  P_{L_0}(r_1, \mathcal{L}_1|u_3) + P_{L_0}(r_1, \mathcal{L}_2|u_3) = 0+0=0 \\
+&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L}_1|u_3) + P_{L_0}(r_2, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
+&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L}_1|u_3) + P_{L_0}(r_3, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
 \end{aligned}
@@
 &Informativity(u_3; r_1) = log(0) = -\infty \\
-&Informativity(u_3; r_2) = log(0.36) = -1.03 \\
-&Informativity(u_3; r_3) = log(0.64) = -0.44
+&Informativity(u_3; r_2) = log(0.35) = -1.04 \\
+&Informativity(u_3; r_3) = log(0.65) = -0.43
 \end{aligned}
@@
 
-SEEMS LIKE WE NEED TO NORMALIZE ACROSS ALL UTTERANCES, SO WE WILL NEED TO REDO the ABOVE CALCULATIONS FOR EACH OF THE 6 UTTERANCES.
+SEEMS LIKE WE NEED TO NORMALIZE ACROSS ALL UTTERANCES, SO WE WILL NEED TO REDO THE ABOVE CALCULATIONS FOR EACH OF THE 6 UTTERANCES.
 

### 2019-07-23 papers/full_paper/SI_appendix.Rmd
add note and speaker math equation

@@
 To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
+
+TO CREATE S(u | r), WE NEED TO HAVE THE INFORMATIVITY OF EACH OF THE 4 UTTERANCES.
+PASSING THE INFORMATIVITY THROUGH THE SOFT-MAX (speaker optimality) creates an "unnormalized" probability, which we then turn into a real probability by dividing by the sum of all the unnormalized probabilities of each utterance.
+
+$$
+P_{S_1}(u|r) = \frac{exp(\alpha Informativity(u;r))}{\sum_{u'} exp(\alpha Informativity(u';r))}
+$$
 

### 2019-08-01 papers/full_paper/SI_appendix.Rmd
some unsuccessful attempts to move forward the worked example

@@
 1 shows a screenshot from the adult experiment, which the model was designed to capture.
-In this context, there are three potential referents (two red-ish: $r_1^r$, $r_2^r$; one yellow-ish, $r_3^y$,), of two types (red-ish and yellow-ish) on two tables.
+In this context, there are three potential referents (two red-ish: $r_1^r$ - left tabe, $r_2^r$ - right table; one yellow-ish, $r_3^y$ - right table,), of two types (red-ish and yellow-ish) on two tables.
 In principle, the speaker, the frog in this case, can produce one of four utterances, turning either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
 We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
-<-- CHECK ME.
 
@@
 & P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3}) = 0 \\
-& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.35 \\
+& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.13 \\
 & P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})   = 0 \\
@@
 & P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.65\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.24\\
 \end{aligned}
@@
 &P_{L_0}(r_1|u_3) =  P_{L_0}(r_1, \mathcal{L}_1|u_3) + P_{L_0}(r_1, \mathcal{L}_2|u_3) = 0+0=0 \\
-&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L}_1|u_3) + P_{L_0}(r_2, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
-&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L}_1|u_3) + P_{L_0}(r_3, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
+&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L}_1|u_3) + P_{L_0}(r_2, \mathcal{L}_2|u_3) = 0.13+0=0.13 \\
+&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L}_1|u_3) + P_{L_0}(r_3, \mathcal{L}_2|u_3) = 0+0.24=0.24 \\
 \end{aligned}
@@
 &Informativity(u_3; r_1) = log(0) = -\infty \\
-&Informativity(u_3; r_2) = log(0.35) = -1.04 \\
-&Informativity(u_3; r_3) = log(0.65) = -0.43
+&Informativity(u_3; r_2) = log(0.13) = -2.04 \\
+&Informativity(u_3; r_3) = log(0.24) = -1.43
 \end{aligned}
@@
 Next we can insert these values into equation 2 to compute the probability that the speaker chooses this utterance to refer to this type of object.
-To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
+To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1 (see Model Parameters section below for how this value was estimated).
+
+$$
+P_{S_1}(u|r) = \frac{exp(\alpha Informativity(u;r))}{\sum_{u'} exp(\alpha Informativity(u';r))}
+$$
+
+Now, to compute $P_{S_1}(u_3|r_3)$, we need the informativity for $r_3$ given the other utterance with the same label. We need
+
+$$
+\begin{aligned}
+& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
+\end{aligned}
+$$
+and
+
+$$
+\begin{aligned}
+&P_{L_0}(r_3|u_1) =  P_{L_0}(r_3, \mathcal{L}_1|u_1) + P_{L_0}(r_1, \mathcal{L}_2|u_1) = 0+0=0 \\
+\end{aligned}
+$$
+as well as
+
+$$
+\begin{aligned}
+&Informativity(u_1; r_3) = log(0) = -\infty \\
+\end{aligned}
+$$
+
+to get
+
+$$
+P_{S_1}(u_3|r_3) = \frac{exp(2.24 \times -1.43)}{exp(2.24 \times -1.43)+exp(2.24 \times -\infty)}=1
+$$
+Thus, the probability that the speaker will chose $u_3$ to refer to $r_3$ is 1.
+We can now turn to equation 1 to get the probability with which the pragmatic listener ($L_1$) think that the Speaker ($S_1$) is referring to $r_3$ when producing utterance $u_3$.
+
+MANUEL: THE ABOVE HAS TO BE TRUE, AT LEAST THIS IS THE VALUE WE GET OUT OF THE WEBPPL MODEL.
+
+To get the probability with which the pragmatic listener $L_1$ think that the $S_1$ is referring to $r_3$ when producing utterance
 
@@
 PASSING THE INFORMATIVITY THROUGH THE SOFT-MAX (speaker optimality) creates an "unnormalized" probability, which we then turn into a real probability by dividing by the sum of all the unnormalized probabilities of each utterance.
-
-$$
-P_{S_1}(u|r) = \frac{exp(\alpha Informativity(u;r))}{\sum_{u'} exp(\alpha Informativity(u';r))}
-$$
 

### 2019-08-05 papers/full_paper/SI_appendix.Rmd
WIP: worked example calculation

--- 2019-07-23 papers/full_paper/SI_appendix.Rmd
@@
 
+TWO CORRECTIONS:
+- THE GENERATIVE PROCESS OF THE UTTERANCE: Speaker knows lexicon, but doesn't assume listener does, but must label (we do not model the decision as to whether or not to label).
+So the only thing informative they do is point.
+- QUD is type, not referent. Change L0 model.
+
 In this section, we work through a toy numerical example for how model predictions were generated for the pragmatics model.
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
-The values of the parameters are taken from the preference - different speaker - congruent condition (see below).
+The values of the parameters are taken from the preference - same speaker - incongruent condition (see below); that is, the pressures of informativity and preference operate in conflicting directions.
 Fig.
 1 shows a screenshot from the adult experiment, which the model was designed to capture.
-In this context, there are three potential referents (two red-ish: $r_1^r$, $r_2^r$; one yellow-ish, $r_3^y$,), of two types (red-ish and yellow-ish) on two tables.
+In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r^{table: 1}_{type:pink}$, $r^{table: 2}_{type:pink}$; one yellow-ish, $r^{table: 2}_{type:yellow}$).
+For simplicity, we refer to the referents by the shorthand: $r_{p}^1, r_{p}^2, r_y^2$.
 In principle, the speaker, the frog in this case, can produce one of four utterances, turning either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
 We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
-<-- CHECK ME.
 
@@
 The listener is learning the mappings between labels and object types (rather than object tokens).
-That is, the listener either thinks the novel word "dax" refers to "red-ish objects" or "yellow-ish objects".
+That is, the listener either believes the novel word "dax" refers to either "red-ish objects" or "yellow-ish objects".
 Turning or pointing to a table always has the same meaning.
-These semantics can be described using two lexica: $\mathcal{L_1} = \{dax: \text{red-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L_2} = \{dax: \text{yellow-ish thing}, wug: \text{red-ish thing}, point: \text{location of point}\}$.
+These semantics can be described using two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}, point: \text{location of point}\}$.
 
@@
 
+We assume that the intentional goal of the speaker is to get the listener to get an option of the correct type.
+That is, the informativity of an utterance is calculated with respect to conveying the correct object type.
+First, we calculate the literal listener's posterior distribution over referents and lexica, and marginalize (average) over objects of the same type and the different lexica. 
 The literal listener's posterior distribution over referents and lexica has support of size six, owing to the unique combinations of referents and lexica.
@@
 \begin{aligned}
-& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_1^r, u_3) P(r_1^r) P(L_1) = 0 \times 0.26 \times 0.5\\
-& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_2^r, u_3) P(r_2^r) P(L_1) = 1 \times 0.26 \times 0.5\\
-& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_3^y, u_3) P(r_3^y) P(L_1) = 0 \times 0.48 \times 0.5\\
-& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_1^r, u_3) P(r_1^r) P(L_2) = 0 \times 0.26 \times 0.5\\
-& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_2^r, u_3) P(r_2^r) P(L_2) = 0 \times 0.26 \times 0.5\\
-& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_3^y, u_3) P(r_3^y) P(L_2) = 1 \times 0.48 \times 0.5\\
+& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^1, u_3) P(r_1^r) P(L_1) = 0 \times 0.26 \times 0.5 =0\\
+& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^2, u_3) P(r_2^r) P(L_1) = 1 \times 0.26 \times 0.5 =0.13\\
+& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_y^2, u_3) P(r_3^y) P(L_1) = 0 \times 0.48 \times 0.5 =0\\
+& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^1, u_3) P(r_1^r) P(L_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^2, u_3) P(r_2^r) P(L_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_y^2, u_3) P(r_3^y) P(L_2) = 1 \times 0.48 \times 0.5=0.24\\
 \end{aligned}
@@
 
-because the speaker is pointing to the table with $r_2$ and $r_3$, and under $\mathcal{L}_1$, "dax" means the red object and under $\mathcal{L}_2$, "dax" means the yellow object.
+because the speaker is pointing to the table with $r_p^2$ and $r_y^2$, and under $\mathcal{L}_1$, "dax" means the pink object and under $\mathcal{L}_2$, "dax" means the yellow object.
 After normalization we have:
@@
 \begin{aligned}
-& P_{L_0}(r_1^r, \mathcal{L}_1 | {u_3}) = 0 \\
-& P_{L_0}(r_2^r, \mathcal{L}_1 | {u_3}) = 0.35 \\
-& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_3})   = 0 \\
-& P_{L_0}(r_1^r, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_2^r, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_3}) = 0.65\\
+& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3}) = 0 \\
+& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3}) = 0.35 \\
+& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})   = 0 \\
+& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})   = 0 \\
+& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})   = 0 \\
+& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
 \end{aligned}
 $$
+The correspondence of the token distribution (above) with the type distribution is straight-forward:
+
+$$
+\begin{aligned}
+& P_{L_0}(r_p, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  = 0+ 0.35 =0.35 \\
+& P_{L_0}(r_y, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
+& P_{L_0}(r_p, \mathcal{L}_2 | {u_3})  = P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  = 0+ 0 =0 \\
+& P_{L_0}(r_y, \mathcal{L}_2 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
+\end{aligned}
+$$
 
@@
 \begin{aligned}
-&P_{L_0}(r_1|u_3) =  P_{L_0}(r_1, \mathcal{L}_1|u_3) + P_{L_0}(r_1, \mathcal{L}_2|u_3) = 0+0=0 \\
-&P_{L_0}(r_2|u_3) =  P_{L_0}(r_2, \mathcal{L}_1|u_3) + P_{L_0}(r_2, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
-&P_{L_0}(r_3|u_3) =  P_{L_0}(r_3, \mathcal{L}_1|u_3) + P_{L_0}(r_3, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
+&P_{L_0}(r_p|u_3) =  P_{L_0}(r_p, \mathcal{L}_1|u_3) + P_{L_0}(r_p, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
+&P_{L_0}(r_y|u_3) =  P_{L_0}(r_y, \mathcal{L}_1|u_3) + P_{L_0}(r_y, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
 \end{aligned}
@@
 \begin{aligned}
-&Informativity(u_3; r_1) = log(0) = -\infty \\
-&Informativity(u_3; r_2) = log(0.35) = -1.04 \\
-&Informativity(u_3; r_3) = log(0.65) = -0.43
+&Informativity(u_3; r_p) = log(0.35) = -1.04 \\
+&Informativity(u_3; r_y) = log(0.65) = -0.43
 \end{aligned}
+$$
+
+In a similar way, we can compute the informativity of the other utterances.
+Since the words have no *a priori* meanings, $u_4$ (pointing to the right and saying "wug") will have the same informativity values as $u_3$ (pointing the right and saying "dax").
+The informativity vectors for $u_1$ and $u_2$, pointing to the left and saying either "dax" or "wug" are also identical:
+
+$$
+\begin{aligned}
+&Informativity(u_1; r_p) = log(P_{L_0}(r_p|u_1)) = log(1)  = 0\\
+&Informativity(u_1; r_y) = log(P_{L_0}(r_y|u_1)) = log(0) = -\infty
+\end{aligned}
+$$
+We assume that the speaker knows the lexicon, but doesn't believe the listener to know the lexicon.
+That is, the generative process of the utterance is tantamount to pointing to the table with the referent of the type they want and incidentally labeling it.
+The label itself carries no information.
+
+We can now compute the probability with each a speaker would produce each of the 4 utterances given the goal of conveying each of the 2 types.
+
+$$
+P_{S_1}(u|r) = \frac{\exp(\alpha \cdot Informativity(u;r))}{\sum_{u'} \exp(\alpha \cdot Informativity(u';r))}
+$$
+
+We begin with $r_p$. If the lexicon was $\mathcal{L}_1$, the speaker would say ...
+
+$$
+P_{S_1}(u|r^1_p) = \frac{\exp(\alpha \cdot Informativity(u;r_p))}{\sum_{u'} \exp(\alpha \cdot Informativity(u';r_p))}
+$$
+$$
+\exp(\alpha \cdot Informativity(u;r_p)) = \begin{cases} 
+\exp(2.24 \times 0) = 1 & \mbox{for } u_1 \\
+\exp(2.24 \times 0) = 1& \mbox{for } u_2 \\
+\exp(2.24 \times -\infty) = 0  & \mbox{for } u_3 \\
+\exp(2.24 \times -\infty) = 0& \mbox{for } u_4 \\
+\end{cases}
+$$
+
+To arrive at the speaker production probabilities, we divide by the normalizing constant (the sum of all of the unnormalized probabilties):
+
+$$
+P_{S_1}(u|r^1_p) = \begin{cases} 
+0.5  & \mbox{for } u_1 \\
+0.5 & \mbox{for } u_2 \\
+ 0  & \mbox{for } u_3 \\
+0& \mbox{for } u_4 \\
+\end{cases}
+$$
+
+For $r^2_p$, we have:
+
+$$
+\exp(\alpha \cdot Informativity(u;r^2_p)) = \begin{cases} 
+\exp(2.24 \times -\infty) = 0 & \mbox{for } u_1 \\
+\exp(2.24 \times -\infty) = 0& \mbox{for } u_2 \\
+\exp(2.24 \times -1.04) = 0.1  & \mbox{for } u_3 \\
+\exp(2.24 \times -1.04) = 0.1 & \mbox{for } u_4 \\
+\end{cases}
+$$
+
+and so:
+
+$$
+P_{S_1}(u|r^1_p) = \begin{cases} 
+0 & \mbox{for } u_1 \\
+0 & \mbox{for } u_2 \\
+0.5  & \mbox{for } u_3 \\
+0.5 & \mbox{for } u_4 \\
+\end{cases}
 $$
@@
 $$
-P_{S_1}(u|r) = \frac{exp(\alpha Informativity(u;r))}{\sum_{u'} exp(\alpha Informativity(u';r))}
+\exp(\alpha Informativity(u_3;r)) = \exp(2.24 \times)
 $$

### 2019-08-05 papers/full_paper/SI_appendix.Rmd

@@
 $$
+
+Now, to compute $P_{S_1}(u_3|r_3)$, we need the informativity for $r_3$ given the other utterance with the same label. We need
+
+$$
+\begin{aligned}
+& P_{L_0}(r_3^y, \mathcal{L}_1 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
+& P_{L_0}(r_3^y, \mathcal{L}_2 | {u_1}) = 0 \times 0.48 \times 0.5 = 0\\
+\end{aligned}
+$$
+and
+
+$$
+\begin{aligned}
+&P_{L_0}(r_3|u_1) =  P_{L_0}(r_3, \mathcal{L}_1|u_1) + P_{L_0}(r_1, \mathcal{L}_2|u_1) = 0+0=0 \\
+\end{aligned}
+$$
+as well as
+
+$$
+\begin{aligned}
+&Informativity(u_1; r_3) = log(0) = -\infty \\
+\end{aligned}
+$$
+
+to get
+
+$$
+P_{S_1}(u_3|r_3) = \frac{exp(2.24 \times -1.43)}{exp(2.24 \times -1.43)+exp(2.24 \times -\infty)}=1
+$$
+Thus, the probability that the speaker will chose $u_3$ to refer to $r_3$ is 1.
+We can now turn to equation 1 to get the probability with which the pragmatic listener ($L_1$) think that the Speaker ($S_1$) is referring to $r_3$ when producing utterance $u_3$.
+
+MANUEL: THE ABOVE HAS TO BE TRUE, AT LEAST THIS IS THE VALUE WE GET OUT OF THE WEBPPL MODEL.
+
+To get the probability with which the pragmatic listener $L_1$ think that the $S_1$ is referring to $r_3$ when producing utterance
+
+TO CREATE S(u | r), WE NEED TO HAVE THE INFORMATIVITY OF EACH OF THE 4 UTTERANCES.
+PASSING THE INFORMATIVITY THROUGH THE SOFT-MAX (speaker optimality) creates an "unnormalized" probability, which we then turn into a real probability by dividing by the sum of all the unnormalized probabilities of each utterance.
 

### 2019-08-05 papers/full_paper/SI_appendix.Rmd
finish speaker probabilities calculations

--- 2019-08-05 papers/full_paper/SI_appendix.Rmd
@@
 We assume that the intentional goal of the speaker is to get the listener to get an option of the correct type.
-That is, the informativity of an utterance is calculated with respect to conveying the correct object type.
-First, we calculate the literal listener's posterior distribution over referents and lexica, and marginalize (average) over objects of the same type and the different lexica. 
+That is, the informativity of an utterance is calculated with respect to conveying the correct object type as opposed to a particular referent (token).
+First, we calculate the literal listener's posterior distribution over referents and lexica, and marginalize (average) over objects of the same type and the different lexica to compute the informativity of an utterance for a type.
 The literal listener's posterior distribution over referents and lexica has support of size six, owing to the unique combinations of referents and lexica.
@@
 \begin{aligned}
-& P_{L_0}(r_p, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  = 0+ 0.35 =0.35 \\
-& P_{L_0}(r_y, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
-& P_{L_0}(r_p, \mathcal{L}_2 | {u_3})  = P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  = 0+ 0 =0 \\
-& P_{L_0}(r_y, \mathcal{L}_2 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
+& P_{L_0}(t_p, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  = 0+ 0.35 =0.35 \\
+& P_{L_0}(t_y, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
+& P_{L_0}(t_p, \mathcal{L}_2 | {u_3})  = P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  = 0+ 0 =0 \\
+& P_{L_0}(t_y, \mathcal{L}_2 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
 \end{aligned}
@@
 \begin{aligned}
-&P_{L_0}(r_p|u_3) =  P_{L_0}(r_p, \mathcal{L}_1|u_3) + P_{L_0}(r_p, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
-&P_{L_0}(r_y|u_3) =  P_{L_0}(r_y, \mathcal{L}_1|u_3) + P_{L_0}(r_y, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
+&P_{L_0}(t_p|u_3) =  P_{L_0}(t_p, \mathcal{L}_1|u_3) + P_{L_0}(t_p, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
+&P_{L_0}(t_y|u_3) =  P_{L_0}(t_y, \mathcal{L}_1|u_3) + P_{L_0}(t_y, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
 \end{aligned}
@@
 \begin{aligned}
-&Informativity(u_3; r_p) = log(0.35) = -1.04 \\
-&Informativity(u_3; r_y) = log(0.65) = -0.43
+&Informativity(u_3; t_p) = \log(0.35) = -1.04 \\
+&Informativity(u_3; t_y) = \log(0.65) = -0.43
 \end{aligned}
@@
 \begin{aligned}
-&Informativity(u_1; r_p) = log(P_{L_0}(r_p|u_1)) = log(1)  = 0\\
-&Informativity(u_1; r_y) = log(P_{L_0}(r_y|u_1)) = log(0) = -\infty
+&Informativity(u_1; t_p) = log(P_{L_0}(t_p|u_1)) = \log(1)  = 0\\
+&Informativity(u_1; t_y) = log(P_{L_0}(t_y|u_1)) = \log(0) = -\infty
 \end{aligned}
@@
 We assume that the speaker knows the lexicon, but doesn't believe the listener to know the lexicon.
-That is, the generative process of the utterance is tantamount to pointing to the table with the referent of the type they want and incidentally labeling it.
+That is, the generative process of the utterance is tantamount to pointing to the table with the referent of the type the speaker wants and incidentally labeling it.
 The label itself carries no information.
 
-We can now compute the probability with each a speaker would produce each of the 4 utterances given the goal of conveying each of the 2 types.
-
-$$
-P_{S_1}(u|r) = \frac{\exp(\alpha \cdot Informativity(u;r))}{\sum_{u'} \exp(\alpha \cdot Informativity(u';r))}
-$$
-
-We begin with $r_p$. If the lexicon was $\mathcal{L}_1$, the speaker would say ...
-
-$$
-P_{S_1}(u|r^1_p) = \frac{\exp(\alpha \cdot Informativity(u;r_p))}{\sum_{u'} \exp(\alpha \cdot Informativity(u';r_p))}
-$$
-$$
-\exp(\alpha \cdot Informativity(u;r_p)) = \begin{cases} 
+Recall the two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}, point: \text{location of point}\}$, and the four utterances:  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
+We begin with $t_p$. If the speaker's lexicon were $\mathcal{L}_1$:
+
+$$
+P_{S_1}(u|t_p, \mathcal{L}_1) \propto \exp(\alpha \cdot Informativity(u;t_p)) = \begin{cases} 
 \exp(2.24 \times 0) = 1 & \mbox{for } u_1 \\
-\exp(2.24 \times 0) = 1& \mbox{for } u_2 \\
-\exp(2.24 \times -\infty) = 0  & \mbox{for } u_3 \\
+\exp(2.24 \times -\infty) = 0& \mbox{for } u_2 \\
+\exp(2.24 \times -1.04) = 0.097  & \mbox{for } u_3 \\
 \exp(2.24 \times -\infty) = 0& \mbox{for } u_4 \\
@@
 $$
-
-To arrive at the speaker production probabilities, we divide by the normalizing constant (the sum of all of the unnormalized probabilties):
-
-$$
-P_{S_1}(u|r^1_p) = \begin{cases} 
-0.5  & \mbox{for } u_1 \\
-0.5 & \mbox{for } u_2 \\
- 0  & \mbox{for } u_3 \\
+To arrive at the production probabilities, you normalize:
+
+$$
+P_{S_1}(u|t_p, \mathcal{L}_1) = \begin{cases} 
+0.91  & \mbox{for } u_1 \\
+0 & \mbox{for } u_2 \\
+0.09  & \mbox{for } u_3 \\
 0& \mbox{for } u_4 \\
@@
 
-For $r^2_p$, we have:
-
-$$
-\exp(\alpha \cdot Informativity(u;r^2_p)) = \begin{cases} 
+The speaker's production probabilities are the same if the speaker's lexicon is $\mathcal{L}_2$, only the utterances use the other label:
+
+$$
+P_{S_1}(u|t_p, \mathcal{L}_2) = \begin{cases} 
+0  & \mbox{for } u_1 \\
+0.91 & \mbox{for } u_2 \\
+0  & \mbox{for } u_3 \\
+0.09& \mbox{for } u_4 \\
+\end{cases}
+$$
+That is, if the speaker is trying to convey the pinkish object type, the speaker would be 10 times more likely (under a speaker rationality parameter of 2.24) to point to the left table than to the right table.
+If instead the speaker wanted to convey the yellowish object type:
+ = -0.43
+
+$$
+P_{S_1}(u|t_y, \mathcal{L}_1) = \exp(\alpha \cdot Informativity(u;t_y)) = \begin{cases} 
 \exp(2.24 \times -\infty) = 0 & \mbox{for } u_1 \\
 \exp(2.24 \times -\infty) = 0& \mbox{for } u_2 \\
-\exp(2.24 \times -1.04) = 0.1  & \mbox{for } u_3 \\
-\exp(2.24 \times -1.04) = 0.1 & \mbox{for } u_4 \\
+\exp(2.24 \times -\infty) = 0  & \mbox{for } u_3 \\
+\exp(2.24 \times -0.43) = 0.38& \mbox{for } u_4 \\
 \end{cases}
@@
 
-and so:
-
-$$
-P_{S_1}(u|r^1_p) = \begin{cases} 
+To arrive at the production probabilities, you normalize:
+
+$$
+P_{S_1}(u|t_y, \mathcal{L}_1) = \begin{cases} 
 0  & \mbox{for } u_1 \\
 0 & \mbox{for } u_2 \\
-0.5  & \mbox{for } u_3 \\
-0.5 & \mbox{for } u_4 \\
+0  & \mbox{for } u_3 \\
+1& \mbox{for } u_4 \\
 \end{cases}
 $$
-
-Next we can insert these values into equation 2 to compute the probability that the speaker chooses this utterance to refer to this type of object.
-To do so, we need the speaker optimality parameter of $\alpha = 2.24$, which was estimated based on Experiment 1.
-
-TO CREATE S(u | r), WE NEED TO HAVE THE INFORMATIVITY OF EACH OF THE 4 UTTERANCES.
-PASSING THE INFORMATIVITY THROUGH THE SOFT-MAX (speaker optimality) creates an "unnormalized" probability, which we then turn into a real probability by dividing by the sum of all the unnormalized probabilities of each utterance.
-
-$$
-\exp(\alpha Informativity(u_3;r)) = \exp(2.24 \times)
-$$
-
-SEEMS LIKE WE NEED TO NORMALIZE ACROSS ALL UTTERANCES, SO WE WILL NEED TO REDO THE ABOVE CALCULATIONS FOR EACH OF THE 6 UTTERANCES.
+and
+
+$$
+P_{S_1}(u|t_y, \mathcal{L}_2) = \begin{cases} 
+0  & \mbox{for } u_1 \\
+0 & \mbox{for } u_2 \\
+1  & \mbox{for } u_3 \\
+0& \mbox{for } u_4 \\
+\end{cases}
+$$
+
+That is, the speaker would point to the right table and say the utterance consistent with their lexicon.
+
+Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
 
@@
 \begin{aligned}
-&P_{S_1}(u_3|r_2) = \frac{exp(2.24 \cdot -1.03)}{exp(2.24 \cdot -1.03) + exp(2.24 \cdot 0)} = 0.09 \\
-&P_{S_1}(u_3|r_3) = \frac{exp(2.24 \cdot -0.44)}{exp(2.24 \cdot -0.44)} = 1 \\
-\end{aligned}
-$$
-
-Here, the informativity for a referent is normalized across all utterances that could be used to refer to this referent.
-
-Finally, based on equation 1 we can use these values to compute the probability that the speaker thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
-
-$$
-\begin{aligned}
-&P_{L_1}(r_1,L|u_1) = \frac{1 * 0.64}{1\cdot0.64 + 0.09\cdot0.36 + 0.09\cdot0.36} = 0.91
+&P_{L_1}(t, \mathcal{L}|u ) = ...
 \end{aligned}

### 2019-08-06 papers/full_paper/SI_appendix.Rmd
finish full worked example

@@
 
-TWO CORRECTIONS:
-- THE GENERATIVE PROCESS OF THE UTTERANCE: Speaker knows lexicon, but doesn't assume listener does, but must label (we do not model the decision as to whether or not to label).
-So the only thing informative they do is point.
-- QUD is type, not referent. Change L0 model.
-
 In this section, we work through a toy numerical example for how model predictions were generated for the pragmatics model.
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
-The values of the parameters are taken from the preference - same speaker - incongruent condition (see below); that is, the pressures of informativity and preference operate in conflicting directions.
+The values of the parameters are taken from the preference - same speaker - congruent condition (see below); that is, the pressures of informativity and preference operate in the same direction.
 Fig.
@@
 \begin{aligned}
-& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^1, u_3) P(r_1^r) P(L_1) = 0 \times 0.26 \times 0.5 =0\\
-& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^2, u_3) P(r_2^r) P(L_1) = 1 \times 0.26 \times 0.5 =0.13\\
-& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_y^2, u_3) P(r_3^y) P(L_1) = 0 \times 0.48 \times 0.5 =0\\
-& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^1, u_3) P(r_1^r) P(L_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^2, u_3) P(r_2^r) P(L_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_y^2, u_3) P(r_3^y) P(L_2) = 1 \times 0.48 \times 0.5=0.24\\
+& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^1, u_3) P(r^1_r) P(\mathcal{L}_1) = 0 \times 0.26 \times 0.5 =0\\
+& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^2, u_3) P(r^2_r) P(\mathcal{L}_1) = 1 \times 0.26 \times 0.5 =0.13\\
+& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_y^2, u_3) P(r^2_y) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
+& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^1, u_3) P(r^1_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^2, u_3) P(r^2_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_y^2, u_3) P(r^2_y) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
 \end{aligned}
@@
 
-Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow object ($r_1$) when they produce $r_1$:
+Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow type ($t_y$) when they produce $u_3$ (pointing to the right table and saying "dax").
+In this case, it is the same as the probability of the yellow referent ($r^2_y$) because there is only one yellow object.
 
@@
 \begin{aligned}
-&P_{L_1}(t, \mathcal{L}|u ) = ...
+&P_{L_1}(r^2_y, \mathcal{L}|u ) = \frac{P_{S_1}(u_3 \mid t_y, \mathcal{L}) \cdot P(\mathcal{L}) \cdot P(r^2_y)}{
+\sum_{r'} P_{S_1}(u_3 \mid r', \mathcal{L}) \cdot P(\mathcal{L}) \cdot P(r')
+}
 \end{aligned}
@@
 
-Thus, we normalize across all potential states that the utterance could refer to.
+$$
+\begin{aligned}
+& P_{L_1}(r_p^1, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^1, \mathcal{L}_1) P(r^1_r) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_p^2, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^2, \mathcal{L}_1)  P(r^2_r) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_y^2, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_y^2, \mathcal{L}_1)  P(r^2_y) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
+& P_{L_1}(r_p^1, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^1, \mathcal{L}_2)  P(r^1_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_p^2, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^2, \mathcal{L}_2) P(r^2_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_y^2, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_y^2, \mathcal{L}_2) P(r^2_y) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
+\end{aligned}
+$$
+
+After normalizing, the full joint-posterior distribution over referents and lexica is:
+
+$$
+\begin{aligned}
+& P_{L_1}(r_p^1, \mathcal{L}_1 | {u_3})  = 0.045\\
+& P_{L_1}(r_p^2, \mathcal{L}_1 | {u_3})  = 0.045\\
+& P_{L_1}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
+& P_{L_1}(r_p^1, \mathcal{L}_2 | {u_3})  = 0\\
+& P_{L_1}(r_p^2, \mathcal{L}_2 | {u_3})  = 0\\
+& P_{L_1}(r_y^2, \mathcal{L}_2 | {u_3})  = 0.91\\
+\end{aligned}
+$$
+
+To arrive at the distribution on types, you simply add all of the referents of the same type and marginalize out the lexicon:
+
+$$
+\begin{aligned}
+&P_{L_1}(t_p|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r^1_p, \mathcal{L}_i|u_3) + P_{L_0}(r^2_p, \mathcal{L}_i|u_3) = 0.09 \\
+&P_{L_1}(t_y|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r^2_y, \mathcal{L}_i|u_3)  = 0.91 \\
+\end{aligned}
+$$
 

### 2019-08-07 papers/full_paper/SI_appendix.Rmd
update SI Appendix

@@
 ---
-title             : "Supplementary information:Predicting information integration in pragmatic word learning across development"
-shorttitle        : "Supplementary information"
+title             : "Supplementary information:Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+shorttitle        : " "
 
@@
 output            : papaja::apa6_pdf
+header-includes:
+  \usepackage{caption}
+  \renewcommand{\thetable}{S\arabic{table}} 
+  \renewcommand{\thefigure}{S\arabic{figure}}
 ---
@@
 
-# Structure
+# Overview
 
 Here we present details for the cognitive models as well as supplementary analysis and results.
-Readers who are interested in the model and/or analysis code itself are encouraged to consult the corresponding online repository: (https://github.com/manuelbohn/mcc).
+Readers who are interested in the model and/or analysis code itself are encouraged to consult the associated online repository: https://github.com/manuelbohn/mcc.
 
@@
 The interpretation of a label requires a lexicon $\mathcal{L}$, which provides the label--type mappings.
-There are two lexica: one which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and one which has the inverse mapping.
+There are two lexica: $\mathcal{L}_1$ which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and $\mathcal{L}_2$ which has the inverse mapping.
 
@@
 
-Our word-learning model is a model of pragmatic reasoning couched in the Rational Speech Act modeling framework.
+Our word-learning model is a model of pragmatic reasoning couched in the Rational Speech Act modeling framework [@frank2012predicting; @goodman2016pragmatic].
 The model describes the following process: A pragmatic listener ($L_1$) jointly infers a referent (what object is being picked out by the utterance) and a lexicon (label--type mappings) by reasoning about a pragmatic speaker ($S_1$) who produces utterances to convey information to a literal listener ($L_0$), who in turn interprets utterances according to their literal meaning.
@@
 
-As spelled out in @GoodmanStuhlmuller2013, the informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
+As spelled out in @goodman2013knowledge, the informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
 
@@
 
-### Worked Example
+## Worked Example
 
@@
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
-The values of the parameters are taken from the preference - same speaker - congruent condition (see below); that is, the pressures of informativity and preference operate in the same direction.
+The values of the parameters are taken from the preference--different speaker--congruent condition (see below).
 Fig.
-1 shows a screenshot from the adult experiment, which the model was designed to capture.
+\ref{fig:figS1} shows a screenshot from the adult experiment, which the model was designed to capture.
 In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r^{table: 1}_{type:pink}$, $r^{table: 2}_{type:pink}$; one yellow-ish, $r^{table: 2}_{type:yellow}$).
@@
 
-```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot from adult experiment.", out.width="400px"}
-knitr::include_graphics("./figures/SI_setup.png")
+```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 1, 3 and 4.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup_inf.png")
 ```
@@
 The listener is learning the mappings between labels and object types (rather than object tokens).
-That is, the listener either believes the novel word "dax" refers to either "red-ish objects" or "yellow-ish objects".
+That is, the listener either believes the novel word "dax" refers to either "pink-ish objects" or "yellow-ish objects".
 Turning or pointing to a table always has the same meaning.
@@
 
-We construct the prior distribution over referents $P(r)$ based on the results of Experiment 2A, in which the speaker displayed a preference for a yellow object (see Model Parameters section below for a detailed description of how this distribution was constructed).
-The prior distribution over referents $P(r)$ (left to right in Fig.1) for this condition was [0.26, 0.26, 0.48].
+We construct the prior distribution over referents $P(r)$ based on the results of Experiment 2A, in which a different speaker displayed a preference for a yellow-ish object.
+The prior distribution over referents $P(r)$ (left to right in Fig.
+\ref{fig:figS1}) for this condition was [0.26, 0.26, 0.48] (see Model Parameters section below for a detailed description of how this distribution was constructed).
 <!-- [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
@@
 
-We assume that the intentional goal of the speaker is to get the listener to get an option of the correct type.
+We assume that the intentional goal of the speaker is to get the listener to select an object of the correct type.
 That is, the informativity of an utterance is calculated with respect to conveying the correct object type as opposed to a particular referent (token).
@@
 
-because the speaker is pointing to the table with $r_p^2$ and $r_y^2$, and under $\mathcal{L}_1$, "dax" means the pink object and under $\mathcal{L}_2$, "dax" means the yellow object.
+because the speaker is pointing to the table with $r_p^2$ and $r_y^2$, and under $\mathcal{L}_1$, "dax" means the pink-ish object and under $\mathcal{L}_2$, "dax" means the yellow-ish object.
 After normalization we have:
@@
 $$
-The correspondence of the token distribution (above) with the type distribution is straight-forward:
+
+In order to get the distribution over types (instead of tokens), we simply add up the probabilities for each token from the same type. Thus, when taking
 
@@
 
-then,
+we get,
 
@@
 
-and
+and finally
 
@@
 Since the words have no *a priori* meanings, $u_4$ (pointing to the right and saying "wug") will have the same informativity values as $u_3$ (pointing the right and saying "dax").
-The informativity vectors for $u_1$ and $u_2$, pointing to the left and saying either "dax" or "wug" are also identical:
+The informativity vectors for $u_1$ and $u_2$, pointing to the left and saying either "dax" or "wug" are also identical and given by:
 
@@
 
+Based on euqation 2 we can now compute the likelihood of each utterance given an object type.
 Recall the two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}, point: \text{location of point}\}$, and the four utterances:  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
-We begin with $t_p$. If the speaker's lexicon were $\mathcal{L}_1$:
+We begin with the pink-ish type ($t_p$). If the speaker's lexicon were $\mathcal{L}_1$:
 
@@
 $$
-That is, if the speaker is trying to convey the pinkish object type, the speaker would be 10 times more likely (under a speaker rationality parameter of 2.24) to point to the left table than to the right table.
-If instead the speaker wanted to convey the yellowish object type:
- = -0.43
+That is, if the speaker is trying to convey the pink-ish object type, the speaker would be 10 times more likely (under a speaker rationality parameter of 2.24) to point to the left table than to the right table.
+This corresponds with the intuition that pointing to the left table would be a much better way to refer to a pink-ish object.
+If instead the speaker wanted to convey the yellow-ish object type ($t_y$):
 
@@
 That is, the speaker would point to the right table and say the utterance consistent with their lexicon.
+Again, intuitively this makes sense because the yellow-ish object is located only on the right table and pointing to that table presents the only way one could refer to that object type.
 
@@
 
-To arrive at the distribution on types, you simply add all of the referents of the same type and marginalize out the lexicon:
+To arrive at the distribution over types, you simply add all of the referents of the same type and marginalize out the lexicon:
 
@@
 $$
+To conclude the example, according to the parameter free pragmatics model, the proability that $L_1$ thinks that $S_1$ is reffering to a yellow-ish object when producing $u_3$ is 0.91.
+Based on this model we thus expected that, on average, participants would select the yellow-ish object in 91% of cases in the preference--different speaker--congruent condition.
 
@@
 
-### Model parameters
+## Prior only model
+
+The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused on common ground manipulation.
+The only inforamtion available to $L_1$ is the prior distribution over referents.
+It is therefore defined as:
+
+\begin{equation} 
+P_{L_1}(r|u)\propto P(r)
+\end{equation}
+
+That is, the probability of the referent given the utterance is determined by the prior probability of the referent for a particular speaker.
+The prior distributions were set in the same way as for the pragmatics model.
+
+## Flat prior model
+
+This model was identical in structure to the pragmatics model with the exception that the prior distribution did not correspond to the measurements from Experiment 2 and did not vary with speaker identity.
+That is, regardless of common ground manipulation and speaker identity the prior distribution was always uniform (i.e.
+[0.33,0.33,0.33]).
+The speaker optimality parameter $\alpha$ was set in the same way as in the pragmatics model.
+
+# Model parameters
 
 As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term.
-It's interpretation is *how* rational $L$ thinks $S$ is in this particular context.
+It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
 For adults, we used the data from Experiment 1 to infer the value of $\alpha$.
-That is, we inferred which value of $\alpha$ would generate model predictions for the RSA model (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in Experiment 1.
+That is, we inferred which value of $\alpha$ would generate model predictions for the pragmatics model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
 This value for $\alpha$ was then used in Experiment 3 and 4.
@@
 Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
-As for adults, this was done via the RSA model with equal prior probability for each object.
+As for adults, this was done via the pragmatics model with equal prior probability for each object.
 In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the overall intercept and adding the slope times the child's age (with age anchored at 0).
+The analysis code corresponding to these calculations can be found in the associated online repository.
 
@@
 Numerically, it depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children.
-
-For adults, this worked in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker indicated that they liked object A and disliked object B, the average proportion with which participants chose object A was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for object B it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
-In Experiment 3, this measurement determined the prior distribution over objects in cases whenever the the same manipulation was used (preference/same speaker).
-When utterance and common ground information were aligned (i.e.
-object A was the more informative object), the distribution of objects was (A,B,B).
-The corresponding prior distribution was therefore (`r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`).
-When information sources were dis-aligned (i.e.
-object B was the more informative one), the object distribution was (B,A,A) and the prior distribution was (`r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`, `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)`).
+Fig.
+\ref{fig:figS2} shows the test situation on Experiment 2.
+
+```{r figS2, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation in Experiment 2 for adults.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup_pref.png")
+```
+
+For adults, this worked in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker previously indicated that they liked the yellow-ish object (right table in Fig.
+\ref{fig:figS2}) and disliked the pink-ish object (left table in Fig.\ref{fig:figS2}), the average proportion with which participants chose the yellow-ish object  was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for the pink-ish object it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
+In Experiment 3 and 4, this measurement determined the prior distribution over objects in cases whenever the the same manipulation was used (preference/same speaker).
 Note that Experiment 3 involved three objects while Experiment 2 only involved two.
@@
 This approach spread out the absolute probability mass but conserved the relative relation between objects.
+Thus, when utterance and common ground information were aligned (i.e.
+the yellow-ish object was the more informative object as in Fig.
+\ref{fig:figS1}), the distribution of objects was [$r_{p}^1, r_{p}^2, r_y^2$].
+Using the raw proportions, the corresponding prior distribution was [$P(r_{p}^1) = 0.03, P(r_{p}^2) = 0.03, P(r_{y}^2) = 0.97$] and after normalizing (so that they add up to 1) it was [0.03, 0.03, 0.94].
+When information sources were dis-aligned (i.e.
+the pink-ish object was the more informative one), the object distribution was ($r_{y}^1, r_{p}^2, r_y^2$) and the prior distribution was thus [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.
 
@@
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
-
-## Prior only model
-
-The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused only on common ground manipulation. It is defined as:
-
-\begin{equation} 
-P_{L}(r|u)\propto P(r)
-\end{equation}
-
-That is, the probability of the referent given the utterance is determined by the prior probability of the referent for a particular speaker.
-The prior distributions were set in the same way as for the pragmatics model.
-
-## Flat prior model
-
-This model was identical in structure to the pragmatics model with the exception that the prior distribution did not correspond to the measurements from Experiment 2 and did not vary with speaker identity.
-That is, regardless of common ground manipulation and speaker identity the prior distribution was always uniform (e.g.
-0.33,0.33,0.33).
-This was the case for children as well as  adults.
-The speaker optimality parameter was set in the same way as in the pragmatics model.
+Model code for inferring the intercept and the slope for the child study can be found in the associated online repository.
 
@@
 
-For preference, both tables initially contained an object.
+For preference, at the beginning of the experiment both tables contained an object.
 In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
@@
 Model fit was assessed based on marginal log-likelihoods of the data under each model.
-Bayes Factors were computed by first subtracting log-likelihoods and then exponentiating the result.
+Bayes Factors were computed by first subtracting log-likelihoods for two models and then exponentiating the result.
 Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3.
@@
 This comparison shows that including the noise parameter greatly improves model fit.
-Figure \ref{fig:modelpredex3} compares model predictions from the models including noise parameters to the data from Experiment 3.
+Figure \ref{fig:modelpredex3} correlates model predictions from the models including noise parameters to the data from Experiment 3.
 
@@
 
-Figure \ref{fig:ex3noise} shows the posterior distribution of the noise parameter for each model.
+Figure \ref{fig:ex3noise} shows the posterior distribution of the noise parameter under each model.
 The noise parameter was fit to the data and indicates the proportion of responses that are estimated to be due to random guessing rather than in line with model predictions.
 Consequently, a model that makes predictions that are closer to the data is likely to have a lower noise parameter.
+The results corroborate the model comparison by showing that the pragmatics model has the lowest noise parameter.
 
@@
 
-Figure \ref{fig:modelpredex4} compares model predictions to the data from Experiment 4.
-Table \ref{tab:ex4_comp} shows Bayes Factors for model comparisons in Experiment 3.
+Figure \ref{fig:modelpredex4} correlates model predictions with the data from Experiment 4.
+Table \ref{tab:ex4_comp} shows Bayes Factors for model comparisons in Experiment 4.
 As pre-registered, all models included a noise parameter.
 Figure \ref{fig:ex4noise} shows the posterior distribution of the noise parameter for each model in Experiment 4.
+All results suggest that the pragmatics model captures the structure in the data better compared to the alternative models considered.
 
@@
 We preregistered the model comparison for models including a single noise parameter.
-We added the additional model comparisons because the noise parameter was comparably high.
+We added the additional model comparisons because the noise parameter was relatively high.
 The additional model comparisons allow us to see if the pragmatics model provides a better fit when more emphasis is put on the model structure itself.
@@
 Parameter free models did not include a noise parameter.
-Noise models included a single noise parameter across age.
+Noise models included a single noise parameter for all ages.
 Developmental noise models included a noise parameter that changed with age.
@@
 closest to the dotted line) for the pragmatics model, thereby corroborating the conclusions drawn based on the model comparison and the evaluation of the noise parameters.
+Correlations are also higher for 4yo compared to 3yo, supporting the interpretation based on the developmental noise parameter that children behaved more in line with the model predictions as they got older.
 

### 2019-08-08 papers/full_paper/SI_appendix.Rmd
rework pragmatics model section in SI

@@
 \begin{equation} 
-P_{L_1}(r, \mathcal{L}|u)\propto P_{S_1}(u|r)P( \mathcal{L})P(r)
+P_{L_1}(r, \mathcal{L}|u)\propto P_{S_1}(u|r, \mathcal{L})P( \mathcal{L})P(r)
 \end{equation}
 
-The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent $r$ ($P_{S1}(u|r)$).
+The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent $r$ and their lexicon $\mathcal{L}$: ($P_{S1}(u|r, \mathcal{L})$).
 In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see below for common ground manipulations).
@@
 
-The pragmatic listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent:
+The pragmatic listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent type ($r^t$) to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent type (r^t):
 
 \begin{equation} 
-P_{S_1}(u|r)\propto exp(\alpha Informativity(u;r))
+P_{S_1}(u^{a,l} | r^t, \mathcal{L})\propto Informativity(u^a;r^t)^\alpha \cdot P(u^l \mid \mathcal{L})
 \end{equation}
 
-As spelled out in @goodman2013knowledge, the informativity of an utterance for a referent is the (log) probability that a naive listener $L_0$ would select that referent given that utterance.
+The speaker's utterances are (action, label) pairs $(u^a, u^l)$ (i.e., we assume the speaker must turn to one of the locations and must produce a label).
+The label the speaker produces $u^l$ depends upon their lexicon $\mathcal{L}$ (i.e., they choose the label that is consistent with the object under their lexicon).
+The action (a point or a turn) the speaker produces $u^a$ is a function of that signal's informativity.
+That is, because the listener does not know the meaning of the labels, the labels carry no information to the listener.
+The informativity of the utterance (action) for a referent is the probability that a naive listener $L_0$ would select a the type of referent ($r^t$) given that utterance (action)[@goodman2013knowledge].
 
 \begin{equation} 
-Informativity(u; r) = \ln P_{L_0}(r|u)
+Informativity(u^a; r^t) = P_{L_0}(r^t|u^a)
 \end{equation}
 
-We assume that the speaker believes the literal listener to also be uncertain about the lexicon; that is, the pragmatic listener believes that the speaker (correctly) believes that the listener does not know the lexicon.
-Because the literal listener is assumed to not know the lexicon, the informativity of the utterance averages over the possible lexical, or words meanings, that $L_0$ considers:
+\noindent where the probability that the naive listener $L_0$ would select that a referent of a given type $r^t$ given the utterance $u^a$ is given by Bayes' Rule:
 
 \begin{equation} 
-P_{L_0}(r|u) = \sum_L P_{L_0}(r, \mathcal{L}|u)
+P_{L_0}(r^t|u) = \sum_{r_i \in t} P_{L_0}(r_i | u) \propto \mathcal{L}_{point} P(r^i)
 \end{equation}
 
-where $P_{L_0}(r, \mathcal{L}|u)  \propto \mathcal{L}_{lit} P(r) P(\mathcal{L})$.
-$P(r)$ again denotes the prior probability of a referent, $\mathcal{L}_{lit}$ encodes the literal meaning of an utterance given a particular lexicon, returning 1 if the utterance is literally true and 0 if the utterance is literally false.
+\noindent where \mathcal{L}_{point} encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
+We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $ \sum_{r_i \in t} P_{L_0}(r_i | u)$.
+
+$P(r)$ again denotes the prior probability of a referent, $\mathcal{L}_{point}$ encodes the literal meaning of a point, returning 1 if the object is at the location of the point and 0 if the utterance if not.
 As mentioned above, because $L_1$ does not know the lexicon, the semantics of the words contained in the utterance (i.e., the labels) offer no information about the referent.
@@
 As described above, the semantics of turning to one of the tables is roughly equivalent to saying "It's an object on that table".
-That is, $\mathcal{L}_{lit}$ returns 1 for a referent that is on the table the agent turned to and 0 for referents on the other table.
+
+The above formulation of a literal interpretation model based only on the semantics of the non-linguistic signals (points) can also be derived by positing a literal interpretation model that updates their beliefs according to the literal meanings of both labels and points, but which is uncertain about the meaning of the labels:  $P_{L_0}(r, \mathcal{L}|u)  \propto \mathcal{L}_{lit} P(r) P(\mathcal{L})$.
 

### 2019-08-08 papers/full_paper/SI_appendix.Rmd
half way through cleaning up worked example

@@
 The situation we model is defined by three sets: referents $r$, utterances $u$, and lexica $\mathcal{L}$. 
-Referents are defined by two features: the type of object they are (visually discernible given their shape and color) and their location (one of two tables).
+Referents are defined by two features $r_{t, l}$: the type of object they are $t$ (visually discernible given their shape and color) and their location $l$ (one of two tables).
 There are two types of objects $t_1$, $t_2$ and two locations $l_1$ and $l_2$.
-The utterances available to a speaker are (action, label) pairs, where the action involves turning (pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
-The action of turning (pointing) reduces the set of referents to those that are on the table targeted by the turn (point); interpreting a label reduces that set further to those which are of the type referred to by that label.
-The interpretation of a label requires a lexicon $\mathcal{L}$, which provides the label--type mappings.
-There are two lexica: $\mathcal{L}_1$ which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and $\mathcal{L}_2$ which has the inverse mapping.
+The utterances $u$ available to a speaker are (action, label) pairs $(u_a, u_w)$, where the action involves turning (pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
+There are two kinds of lexica, corresponding to the two utterance components: The lexicon of pointing $\mathcal{L}_{point}$ and the lexica of label $\mathcal{L}_1, \mathcal{L}_2$.
+The lexicon of pointing $\mathcal{L}_{point}$ encodes the meaning of a point: The action of turning (pointing) reduces the set of referents to those that are on the table targeted by the turn (point).
+The lexica of labels map labels $u_w$ onto referents: $\mathcal{L}_1$ maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and $\mathcal{L}_2$ which has the inverse mapping.
 
@@
 \begin{equation} 
-P_{L_1}(r, \mathcal{L}|u)\propto P_{S_1}(u|r, \mathcal{L})P( \mathcal{L})P(r)
+P_{L_1}(r, \mathcal{L}|u)\propto P_{S_1}(u|r_{t}, \mathcal{L})P( \mathcal{L})P(r)
 \end{equation}
 
-The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent $r$ and their lexicon $\mathcal{L}$: ($P_{S1}(u|r, \mathcal{L})$).
+The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent type $r_t$ and their lexicon $\mathcal{L}$: ($P_{S1}(u|r_t, \mathcal{L})$).
 In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see below for common ground manipulations).
@@
 
-The pragmatic listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent type ($r^t$) to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent type (r^t):
+The pragmatic listener updates their beliefs about both the referent and the lexicon by reasoning about the speaker, assumed to produce utterances to convey the referent type ($r_t$) to the listener by being a soft-max rational agent (with degree of rationality $\alpha$) with a utility function defined in terms of the informativity of an utterance for a referent type ($r_t$):
 
 \begin{equation} 
-P_{S_1}(u^{a,l} | r^t, \mathcal{L})\propto Informativity(u^a;r^t)^\alpha \cdot P(u^l \mid \mathcal{L})
+P_{S_1}(u_{a,l} | r_t, \mathcal{L})\propto Informativity(u_a;r_t)^\alpha \cdot P(u_l \mid \mathcal{L})
 \end{equation}
 
-The speaker's utterances are (action, label) pairs $(u^a, u^l)$ (i.e., we assume the speaker must turn to one of the locations and must produce a label).
-The label the speaker produces $u^l$ depends upon their lexicon $\mathcal{L}$ (i.e., they choose the label that is consistent with the object under their lexicon).
-The action (a point or a turn) the speaker produces $u^a$ is a function of that signal's informativity.
+The speaker's utterances are (action, label) pairs $(u_a, u_l)$ (i.e., we assume the speaker must turn to one of the locations and must produce a label).
+The label the speaker produces $u_l$ depends upon their lexicon $\mathcal{L}$ (i.e., they choose the label that is consistent with the object under their lexicon).
+The action (a point or a turn) the speaker produces $u_a$ is a function of that signal's informativity.
 That is, because the listener does not know the meaning of the labels, the labels carry no information to the listener.
-The informativity of the utterance (action) for a referent is the probability that a naive listener $L_0$ would select a the type of referent ($r^t$) given that utterance (action)[@goodman2013knowledge].
+The informativity of the utterance (action) for a referent is the probability that a naive listener $L_0$ would select a the type of referent ($r_t$) given that utterance (action)[@goodman2013knowledge].
 
 \begin{equation} 
-Informativity(u^a; r^t) = P_{L_0}(r^t|u^a)
+Informativity(u_a; r_t) = P_{L_0}(r_t|u_a)
 \end{equation}
 
-\noindent where the probability that the naive listener $L_0$ would select that a referent of a given type $r^t$ given the utterance $u^a$ is given by Bayes' Rule:
+\noindent where the probability that the naive listener $L_0$ would select that a referent of a given type $r_t$ given the utterance $u_a$ is given by Bayes' Rule:
 
 \begin{equation} 
-P_{L_0}(r^t|u) = \sum_{r_i \in t} P_{L_0}(r_i | u) \propto \mathcal{L}_{point} P(r^i)
+P_{L_0}(r_t|u) = \sum_{r_i \in t} P_{L_0}(r_i | u) \propto \mathcal{L}_{point} P(r_i)
 \end{equation}
 
-\noindent where \mathcal{L}_{point} encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
-We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $ \sum_{r_i \in t} P_{L_0}(r_i | u)$.
+\noindent where $\mathcal{L}_{point}$ encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
+We assume in this model that the speaker is trying to convey the type of the referent $r_t$ rather than the individual token referents $r_i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r_t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $\sum_{r_i \in t} P_{L_0}(r_i | u)$.
 
@@
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
-The values of the parameters are taken from the preference--different speaker--congruent condition (see below).
+The values of the parameters are taken from a preference  condition (see below).
 Fig.
@@
 In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r^{table: 1}_{type:pink}$, $r^{table: 2}_{type:pink}$; one yellow-ish, $r^{table: 2}_{type:yellow}$).
-For simplicity, we refer to the referents by the shorthand: $r_{p}^1, r_{p}^2, r_y^2$.
+For simplicity, we refer to the referents by the shorthand: $r_{p1}, r_{p2}, r_{y2}$.
 In principle, the speaker, the frog in this case, can produce one of four utterances, turning either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
@@
 That is, the informativity of an utterance is calculated with respect to conveying the correct object type as opposed to a particular referent (token).
-First, we calculate the literal listener's posterior distribution over referents and lexica, and marginalize (average) over objects of the same type and the different lexica to compute the informativity of an utterance for a type.
-The literal listener's posterior distribution over referents and lexica has support of size six, owing to the unique combinations of referents and lexica.
+First, we calculate the literal listener's posterior distribution over referents, and marginalize (average) over objects of the same type to compute the informativity of an utterance for a type.
+<!-- The literal listener's posterior distribution over referents and lexica has support of size six, owing to the unique combinations of referents and lexica. -->
+
 $$
 \begin{aligned}
-& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^1, u_3) P(r^1_r) P(\mathcal{L}_1) = 0 \times 0.26 \times 0.5 =0\\
-& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_p^2, u_3) P(r^2_r) P(\mathcal{L}_1) = 1 \times 0.26 \times 0.5 =0.13\\
-& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_y^2, u_3) P(r^2_y) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
-& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^1, u_3) P(r^1_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_p^2, u_3) P(r^2_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_y^2, u_3) P(r^2_y) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
+& P_{L_0}(r_{p1}| {u_3})  \propto \mathcal{L}_{point}(r_{p1}, u_3) P(r_{p1})  = 0 \times 0.26  =0\\
+& P_{L_0}(r_{p2}| {u_3})  \propto \mathcal{L}_{point}(r_{p2}, u_3) P(r_{p2})= 1 \times 0.26  =0.26\\
+& P_{L_0}(r_{y2} | {u_3})  \propto \mathcal{L}_{point}(r_{y2}, u_3) P(r_{y2})  = 1 \times 0.48  = 0.48
 \end{aligned}
@@
 
-because the speaker is pointing to the table with $r_p^2$ and $r_y^2$, and under $\mathcal{L}_1$, "dax" means the pink-ish object and under $\mathcal{L}_2$, "dax" means the yellow-ish object.
+<!-- $$ -->
+<!-- \begin{aligned} -->
+<!-- & P_{L_0}(r_{p1}, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_{p1}, u_3) P(r_{p1}) P(\mathcal{L}_1) = 0 \times 0.26 \times 0.5 =0\\ -->
+<!-- & P_{L_0}(r_{p2}, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_{p2}, u_3) P(r_{p2}) P(\mathcal{L}_1) = 1 \times 0.26 \times 0.5 =0.13\\ -->
+<!-- & P_{L_0}(r_{y2}, \mathcal{L}_1 | {u_3})  \propto \mathcal{L}_1(r_{y2}, u_3) P(r_{y2}) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\ -->
+<!-- & P_{L_0}(r_{p1}, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_{p1}, u_3) P(r_{p1}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\ -->
+<!-- & P_{L_0}(r_{p2}, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_{p2}, u_3) P(r_{p2}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\ -->
+<!-- & P_{L_0}(r_{y2}, \mathcal{L}_2 | {u_3})  \propto \mathcal{L}_2(r_{y2}, u_3) P(r_{y2}) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\ -->
+<!-- \end{aligned} -->
+<!-- $$ -->
+
+because the speaker is pointing to the table with $r_{p2}$ and $r_{y2}$.
 After normalization we have:
@@
 \begin{aligned}
-& P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3}) = 0 \\
-& P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3}) = 0.35 \\
-& P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})   = 0 \\
-& P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})   = 0 \\
-& P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
+& P_{L_0}(r_{p1}| {u_3}) = 0 \\
+& P_{L_0}(r_{p2}| {u_3}) = 0.35 \\
+& P_{L_0}(r_{y2} | {u_3}) = 0.65
 \end{aligned}
@@
 \begin{aligned}
-& P_{L_0}(t_p, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_p^1, \mathcal{L}_1 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_1 | {u_3})  = 0+ 0.35 =0.35 \\
-& P_{L_0}(t_y, \mathcal{L}_1 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
-& P_{L_0}(t_p, \mathcal{L}_2 | {u_3})  = P_{L_0}(r_p^1, \mathcal{L}_2 | {u_3})  + P_{L_0}(r_p^2, \mathcal{L}_2 | {u_3})  = 0+ 0 =0 \\
-& P_{L_0}(t_y, \mathcal{L}_2 | {u_3}) = P_{L_0}(r_y^2, \mathcal{L}_2 | {u_3}) = 0.65\\
+& P_{L_0}(r_p | {u_3}) = P_{L_0}(r_{p1}| {u_3})  + P_{L_0}(r_{p2}| {u_3})  = 0+ 0.35 =0.35 \\
+& P_{L_0}(r_y | {u_3}) = P_{L_0}(r_{y2} | {u_3}) = 0.65\\
 \end{aligned}
@@
 
-we get,
+and finally
 
@@
 \begin{aligned}
-&P_{L_0}(t_p|u_3) =  P_{L_0}(t_p, \mathcal{L}_1|u_3) + P_{L_0}(t_p, \mathcal{L}_2|u_3) = 0.35+0=0.35 \\
-&P_{L_0}(t_y|u_3) =  P_{L_0}(t_y, \mathcal{L}_1|u_3) + P_{L_0}(t_y, \mathcal{L}_2|u_3) = 0+0.65=0.65 \\
-\end{aligned}
-$$
-
-and finally
-
-$$
-\begin{aligned}
-&Informativity(u_3; t_p) = \log(0.35) = -1.04 \\
-&Informativity(u_3; t_y) = \log(0.65) = -0.43
+&Informativity(u_3; r_p) = \log(0.35) = -1.04 \\
+&Informativity(u_3; r_y) = \log(0.65) = -0.43
 \end{aligned}
@@
 \begin{aligned}
-&Informativity(u_1; t_p) = log(P_{L_0}(t_p|u_1)) = \log(1)  = 0\\
-&Informativity(u_1; t_y) = log(P_{L_0}(t_y|u_1)) = \log(0) = -\infty
+&Informativity(u_1; r_p) = log(P_{L_0}(r_p|u_1)) = \log(1)  = 0\\
+&Informativity(u_1; r_y) = log(P_{L_0}(r_y|u_1)) = \log(0) = -\infty
 \end{aligned}

### 2019-08-08 papers/full_paper/SI_appendix.Rmd
finish revising SI worked example

@@
 \begin{aligned}
-& P_{L_0}(r_p | {u_3}) = P_{L_0}(r_{p1}| {u_3})  + P_{L_0}(r_{p2}| {u_3})  = 0+ 0.35 =0.35 \\
-& P_{L_0}(r_y | {u_3}) = P_{L_0}(r_{y2} | {u_3}) = 0.65\\
-\end{aligned}
-$$
-
-and finally
-
-$$
-\begin{aligned}
-&Informativity(u_3; r_p) = \log(0.35) = -1.04 \\
-&Informativity(u_3; r_y) = \log(0.65) = -0.43
+& Informativity(u_3; r_p) = P_{L_0}(r_p | {u_3}) = P_{L_0}(r_{p1}| {u_3})  + P_{L_0}(r_{p2}| {u_3})  = 0+ 0.35 =0.35 \\
+& Informativity(u_3; r_p) = P_{L_0}(r_y | {u_3}) = P_{L_0}(r_{y2} | {u_3}) = 0.65\\
 \end{aligned}
@@
 \begin{aligned}
-&Informativity(u_1; r_p) = log(P_{L_0}(r_p|u_1)) = \log(1)  = 0\\
-&Informativity(u_1; r_y) = log(P_{L_0}(r_y|u_1)) = \log(0) = -\infty
+&Informativity(u_1; r_p) = P_{L_0}(r_p|u_1) = 1\\
+&Informativity(u_1; r_y) = P_{L_0}(r_y|u_1) = 0
 \end{aligned}
@@
 Based on euqation 2 we can now compute the likelihood of each utterance given an object type.
-Recall the two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}, point: \text{location of point}\}$, and the four utterances:  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
-We begin with the pink-ish type ($t_p$). If the speaker's lexicon were $\mathcal{L}_1$:
-
-$$
-P_{S_1}(u|t_p, \mathcal{L}_1) \propto \exp(\alpha \cdot Informativity(u;t_p)) = \begin{cases} 
-\exp(2.24 \times 0) = 1 & \mbox{for } u_1 \\
-\exp(2.24 \times -\infty) = 0& \mbox{for } u_2 \\
-\exp(2.24 \times -1.04) = 0.097  & \mbox{for } u_3 \\
-\exp(2.24 \times -\infty) = 0& \mbox{for } u_4 \\
+Recall the two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing} \}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}\}$, and the four utterances:  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
+We begin with the pink-ish type ($r_p$). If the speaker's lexicon were $\mathcal{L}_1$:
+
+$$
+P_{S_1}(u|r_p, \mathcal{L}_1) \propto   Informativity(u_a;r_p)^\alpha P(u \mid \mathcal{L}_1) = \begin{cases} 
+1^{2.24} \times 1 = 1 & \mbox{for } u_1 \\
+0^{2.24} \times 0 = 0& \mbox{for } u_2 \\
+0.35^{2.24} \times 1 = 0.095  & \mbox{for } u_3 \\
+1^{2.24} \times 0 = 0& \mbox{for } u_4 \\
 \end{cases}
 $$
-To arrive at the production probabilities, you normalize:
-
-$$
-P_{S_1}(u|t_p, \mathcal{L}_1) = \begin{cases} 
+To arrive at the production probabilities, you the values from the previous calculation so that they add to 1:
+
+$$
+P_{S_1}(u|r_p, \mathcal{L}_1) = \begin{cases} 
 0.91  & \mbox{for } u_1 \\
@@
 $$
-P_{S_1}(u|t_p, \mathcal{L}_2) = \begin{cases} 
+P_{S_1}(u|r_p, \mathcal{L}_2) = \begin{cases} 
 0  & \mbox{for } u_1 \\
@@
 This corresponds with the intuition that pointing to the left table would be a much better way to refer to a pink-ish object.
-If instead the speaker wanted to convey the yellow-ish object type ($t_y$):
-
-$$
-P_{S_1}(u|t_y, \mathcal{L}_1) = \exp(\alpha \cdot Informativity(u;t_y)) = \begin{cases} 
-\exp(2.24 \times -\infty) = 0 & \mbox{for } u_1 \\
-\exp(2.24 \times -\infty) = 0& \mbox{for } u_2 \\
-\exp(2.24 \times -\infty) = 0  & \mbox{for } u_3 \\
-\exp(2.24 \times -0.43) = 0.38& \mbox{for } u_4 \\
+If instead the speaker wanted to convey the yellow-ish object type ($r_y$):
+
+$$
+P_{S_1}(u|r_y, \mathcal{L}_1) = Informativity(u;r_y)^\alpha \cdot P(u\mid \mathcal{L}_1) = \begin{cases} 
+0^{2.24} \times 0 = 0 & \mbox{for } u_1 \\
+0^{2.24} \times 0 = 0& \mbox{for } u_2 \\
+0^{2.24} \times 0 = 0  & \mbox{for } u_3 \\
+0.65^{2.24} \times 1 = 0.38& \mbox{for } u_4 \\
 \end{cases}
@@
 $$
-P_{S_1}(u|t_y, \mathcal{L}_1) = \begin{cases} 
+P_{S_1}(u|r_y, \mathcal{L}_1) = \begin{cases} 
 0  & \mbox{for } u_1 \\
@@
 $$
-P_{S_1}(u|t_y, \mathcal{L}_2) = \begin{cases} 
+P_{S_1}(u|r_y, \mathcal{L}_2) = \begin{cases} 
 0  & \mbox{for } u_1 \\
@@
 
-Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow type ($t_y$) when they produce $u_3$ (pointing to the right table and saying "dax").
-In this case, it is the same as the probability of the yellow referent ($r^2_y$) because there is only one yellow object.
+Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow type ($r_y$) when they produce $u_3$ (pointing to the right table and saying "dax").
+In this case, it is the same as the probability of the yellow referent ($r_{y2}$) because there is only one yellow object.
 
@@
 \begin{aligned}
-&P_{L_1}(r^2_y, \mathcal{L}|u ) = \frac{P_{S_1}(u_3 \mid t_y, \mathcal{L}) \cdot P(\mathcal{L}) \cdot P(r^2_y)}{
+&P_{L_1}(r_{y2}, \mathcal{L}|u_3 ) = \frac{P_{S_1}(u_3 \mid r_y, \mathcal{L}) \cdot P(\mathcal{L}) \cdot P(r_{y2})}{
 \sum_{r'} P_{S_1}(u_3 \mid r', \mathcal{L}) \cdot P(\mathcal{L}) \cdot P(r')
@@
 \begin{aligned}
-& P_{L_1}(r_p^1, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^1, \mathcal{L}_1) P(r^1_r) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
-& P_{L_1}(r_p^2, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^2, \mathcal{L}_1)  P(r^2_r) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
-& P_{L_1}(r_y^2, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_y^2, \mathcal{L}_1)  P(r^2_y) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
-& P_{L_1}(r_p^1, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^1, \mathcal{L}_2)  P(r^1_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_1}(r_p^2, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_p^2, \mathcal{L}_2) P(r^2_r) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_1}(r_y^2, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_y^2, \mathcal{L}_2) P(r^2_y) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
+& P_{L_1}(r_{p1}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_1) P(r_{r1}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_{p2}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_1)  P(r_{r2}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_{y2}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{y2}, \mathcal{L}_1)  P(r_{y2}) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
+& P_{L_1}(r_{p1}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_2)  P(r_{r1}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_{p2}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_2) P(r_{r2}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_{y2}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{y2}, \mathcal{L}_2) P(r_{y2}) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
 \end{aligned}
@@
 \begin{aligned}
-& P_{L_1}(r_p^1, \mathcal{L}_1 | {u_3})  = 0.045\\
-& P_{L_1}(r_p^2, \mathcal{L}_1 | {u_3})  = 0.045\\
-& P_{L_1}(r_y^2, \mathcal{L}_1 | {u_3})  = 0 \\
-& P_{L_1}(r_p^1, \mathcal{L}_2 | {u_3})  = 0\\
-& P_{L_1}(r_p^2, \mathcal{L}_2 | {u_3})  = 0\\
-& P_{L_1}(r_y^2, \mathcal{L}_2 | {u_3})  = 0.91\\
+& P_{L_1}(r_{p1}, \mathcal{L}_1 | {u_3})  = 0.045\\
+& P_{L_1}(r_{p2}, \mathcal{L}_1 | {u_3})  = 0.045\\
+& P_{L_1}(r_{y2}, \mathcal{L}_1 | {u_3})  = 0 \\
+& P_{L_1}(r_{p1}, \mathcal{L}_2 | {u_3})  = 0\\
+& P_{L_1}(r_{p2}, \mathcal{L}_2 | {u_3})  = 0\\
+& P_{L_1}(r_{y2}, \mathcal{L}_2 | {u_3})  = 0.91\\
 \end{aligned}
@@
 \begin{aligned}
-&P_{L_1}(t_p|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r^1_p, \mathcal{L}_i|u_3) + P_{L_0}(r^2_p, \mathcal{L}_i|u_3) = 0.09 \\
-&P_{L_1}(t_y|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r^2_y, \mathcal{L}_i|u_3)  = 0.91 \\
+&P_{L_1}(r_p|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r_{p1}, \mathcal{L}_i|u_3) + P_{L_0}(r_{p2}, \mathcal{L}_i|u_3) = 0.09 \\
+&P_{L_1}(r_y|u_3) =  \sum_{i \in {1, 2}} P_{L_1}(r_{y2}, \mathcal{L}_i|u_3)  = 0.91 \\
 \end{aligned}

### 2019-08-08 papers/full_paper/SI_appendix.Rmd
subscripting typo
fix typos

--- 2019-08-08 papers/full_paper/SI_appendix.Rmd
@@
 
-\noindent where \mathcal{L}_{point} encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
-We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $ \sum_{r_i \in t} P_{L_0}(r_i | u)$.
+\noindent where $\mathcal{L}_{point}$ encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
+We assume in this model that the speaker is trying to convey the type of the referent $r^t$ rather than the individual token referents $r^i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r^t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $\sum_{r_i \in t} P_{L_0}(r_i | u)$.
 

### 2019-08-09 papers/full_paper/SI_appendix.Rmd
fix typos in SI appendix

--- 2019-08-08 papers/full_paper/SI_appendix.Rmd
@@
 Here we present details for the cognitive models as well as supplementary analysis and results.
-Readers who are interested in the model and/or analysis code itself are encouraged to consult the associated online repository: https://github.com/manuelbohn/mcc.
-
-# Models
+Readers who are interested in the model code and analysis code itself are encouraged to consult the associated online repository: https://github.com/manuelbohn/mcc.
+
+# Cognitive Models
 
@@
 There are two types of objects $t_1$, $t_2$ and two locations $l_1$ and $l_2$.
-The utterances $u$ available to a speaker are (action, label) pairs $(u_a, u_w)$, where the action involves turning (pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the type of the object.
-There are two kinds of lexica, corresponding to the two utterance components: The lexicon of pointing $\mathcal{L}_{point}$ and the lexica of label $\mathcal{L}_1, \mathcal{L}_2$.
-The lexicon of pointing $\mathcal{L}_{point}$ encodes the meaning of a point: The action of turning (pointing) reduces the set of referents to those that are on the table targeted by the turn (point).
-The lexica of labels map labels $u_w$ onto referents: $\mathcal{L}_1$ maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and $\mathcal{L}_2$ which has the inverse mapping.
+The utterances $u$ available to a speaker are (action, label) pairs $(u_a, u_w)$, where the action involves turning (pointing) to a particular location (a table) and labels are novel words ($w_1$, $w_2$), which are assumed to refer to the *type* of the object.
+There are two kinds of lexica, corresponding to the two utterance components: The lexicon of pointing $\mathcal{L}_{point}$ and the lexica of labels $\mathcal{L}_1, \mathcal{L}_2$.
+The lexicon of pointing $\mathcal{L}_{point}$ encodes the meaning of a point: The action of pointing reduces the set of referents to those that are on the table targeted by the point.
+The lexica of labels map labels $u_w$ onto referents: $\mathcal{L}_1$ which maps label 1 $w_1$ to type 1 $t_1$ and label 2 $w_2$ to type 2 $t_2$, and $\mathcal{L}_2$ which has the inverse mapping.
 
@@
 
-The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood that a speaker would produce an utterance $u$ given a referent type $r_t$ and their lexicon $\mathcal{L}$: ($P_{S1}(u|r_t, \mathcal{L})$).
-In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see below for common ground manipulations).
+The right-hand side of this equation has three terms: the prior distribution over referents $P(r)$, the prior distribution over lexica $P(\mathcal{L})$, and the likelihood $P_{S1}(u|r_t, \mathcal{L})$ that a speaker would produce an utterance $u$ given a referent type $r_t$ and their lexicon $\mathcal{L}$.
+
+In the situation we model, the prior on referents $P(r)$ is a categorical distribution over three objects in a scene, which we posit could be non-uniform due to what is in common ground (see main text and below for information on common ground manipulations).
 Because the labels produced by the speaker are all novel words, the listener has no substantive knowledge about the lexica (label--type mappings) and thus the prior over the two lexica (described above) is uniform.
@@
 
-The speaker's utterances are (action, label) pairs $(u_a, u_l)$ (i.e., we assume the speaker must turn to one of the locations and must produce a label).
-The label the speaker produces $u_l$ depends upon their lexicon $\mathcal{L}$ (i.e., they choose the label that is consistent with the object under their lexicon).
-The action (a point or a turn) the speaker produces $u_a$ is a function of that signal's informativity.
+The speaker's utterances are (action, label) pairs $(u_a, u_l)$ (i.e., we assume the speaker must point to one of the locations and must produce a label).
+The label the speaker produces $u_l$ depends upon their lexicon $\mathcal{L}$ (i.e., they choose the label that is consistent with the object under their lexicon).The action (point) the speaker produces $u_a$ is a function of that signal's informativity.
 That is, because the listener does not know the meaning of the labels, the labels carry no information to the listener.
+
 The informativity of the utterance (action) for a referent is the probability that a naive listener $L_0$ would select a the type of referent ($r_t$) given that utterance (action)[@goodman2013knowledge].
@@
 
-\noindent where the probability that the naive listener $L_0$ would select that a referent of a given type $r_t$ given the utterance $u_a$ is given by Bayes' Rule:
+\noindent where the probability that the naive listener $L_0$ would select a referent of a given type $r_t$ given the utterance $u_a$ is given by Bayes' Rule:
 
@@
 
-\noindent where $\mathcal{L}_{point}$ encodes the meaning of the actions (points), and is simply a truth-function stipulating the location of the referent must be at the location of the point / turn.
+\noindent where $\mathcal{L}_{point}$ encodes the meaning of the actions (points), and is simply a truth-function stipulating that the location of the referent must be at the location of the point.
+
 We assume in this model that the speaker is trying to convey the type of the referent $r_t$ rather than the individual token referents $r_i$; thus, the relevant probability for purposes of informativity is the type probability $P_{L_0}(r_t|u)$, which is simply a sum of the token probabilities for tokens that are of the same type $\sum_{r_i \in t} P_{L_0}(r_i | u)$.
@@
 As mentioned above, because $L_1$ does not know the lexicon, the semantics of the words contained in the utterance (i.e., the labels) offer no information about the referent.
-The non-linguistic aspect of the utterance (the turning or pointing), however, do.
+The non-linguistic aspect of the utterance (pointing), however, do.
 As described above, the semantics of turning to one of the tables is roughly equivalent to saying "It's an object on that table".
@@
 \ref{fig:figS1} shows a screenshot from the adult experiment, which the model was designed to capture.
-In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r^{table: 1}_{type:pink}$, $r^{table: 2}_{type:pink}$; one yellow-ish, $r^{table: 2}_{type:yellow}$).
+In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r_{type:pink, table: 1}$, $r_{type:pink,table: 2}$; one yellow-ish, $r_{type:yellow,table: 2}$).
 For simplicity, we refer to the referents by the shorthand: $r_{p1}, r_{p2}, r_{y2}$.
-In principle, the speaker, the frog in this case, can produce one of four utterances, turning either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
-We work out the example where the speaker produces utterance $u_3$, turning to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
-
-<!-- $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
-In the experiment, the speaker chose $u_1$ and we therefore model $L_1$'s interpretation of this utterance.
--->
+In principle, the speaker, the frog in this case, can produce one of four utterances, pointing either to the left or right table and saying either label ("dax" or "wug"):  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
+We work out the example where the speaker produces utterance $u_3$, pointing to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
 
@@
 
-The listener is learning the mappings between labels and object types (rather than object tokens).
-That is, the listener either believes the novel word "dax" refers to either "pink-ish objects" or "yellow-ish objects".
-Turning or pointing to a table always has the same meaning.
+As mentioned above, the listener is learning the mappings between labels and object types (rather than object tokens).
+That is, the listener either believes the novel word "dax" refers to "pink-ish objects" or "yellow-ish objects".
+Pointing to a table always has the same meaning.
 These semantics can be described using two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing}, point: \text{location of point}\}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}, point: \text{location of point}\}$.
@@
 The prior distribution over referents $P(r)$ (left to right in Fig.
-\ref{fig:figS1}) for this condition was [0.26, 0.26, 0.48] (see Model Parameters section below for a detailed description of how this distribution was constructed).
-<!-- [`r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(1-mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`; `r round(mean(adult_ex2_preference_data%>%filter(condition == "different_speaker")%>%pull(correct)),2)`].
--->
+\ref{fig:figS1}) in the example that follows was [0.26, 0.26, 0.48] (see Model Parameters section below for a detailed description of how this distribution was constructed).
 
@@
 That is, the informativity of an utterance is calculated with respect to conveying the correct object type as opposed to a particular referent (token).
+
 First, we calculate the literal listener's posterior distribution over referents, and marginalize (average) over objects of the same type to compute the informativity of an utterance for a type.
@@
 
-because the speaker is pointing to the table with $r_{p2}$ and $r_{y2}$.
+because the speaker is pointing to the right table with $r_{p2}$ and $r_{y2}$.
 After normalization we have:
@@
 
-In order to get the distribution over types (instead of tokens), we simply add up the probabilities for each token from the same type. Thus, when taking
+In order to get the distribution over types (instead of tokens), we simply add up the probabilities for each token from the same type.
 
@@
 Since the words have no *a priori* meanings, $u_4$ (pointing to the right and saying "wug") will have the same informativity values as $u_3$ (pointing the right and saying "dax").
-The informativity vectors for $u_1$ and $u_2$, pointing to the left and saying either "dax" or "wug" are also identical and given by:
+The informativity vectors for $u_1$ and $u_2$ (pointing to the left and saying either "dax" or "wug") are also identical and given by:
 
@@
 $$
-To arrive at the production probabilities, you the values from the previous calculation so that they add to 1:
+To arrive at the production probabilities, we normalize by the values from the previous calculation so that they add to 1:
 
@@
 
-To arrive at the production probabilities, you normalize:
+To arrive at the production probabilities, we normalize:
 
@@
 
-Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow type ($r_y$) when they produce $u_3$ (pointing to the right table and saying "dax").
-In this case, it is the same as the probability of the yellow referent ($r_{y2}$) because there is only one yellow object.
+Finally, based on equation 1 we can use these values to compute the probability that the listener thinks that the speaker is referring to the yellow-ish type ($r_y$) when they produce $u_3$ (pointing to the right table and saying "dax").
+In this case, it is the same as the probability of the yellow-ish referent ($r_{y2}$) because there is only one yellow object.
 
@@
 \begin{aligned}
-& P_{L_1}(r_{p1}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_1) P(r_{r1}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
-& P_{L_1}(r_{p2}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_1)  P(r_{r2}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_{p1}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_1) P(r_{p1}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
+& P_{L_1}(r_{p2}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_1)  P(r_{p2}) P(\mathcal{L}_1) = 0.09 \times 0.26 \times 0.5 =0.012\\
 & P_{L_1}(r_{y2}, \mathcal{L}_1 | {u_3})  \propto P_{S_1}(u_3 \mid r_{y2}, \mathcal{L}_1)  P(r_{y2}) P(\mathcal{L}_1) = 0 \times 0.48 \times 0.5 =0\\
-& P_{L_1}(r_{p1}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_2)  P(r_{r1}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
-& P_{L_1}(r_{p2}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_2) P(r_{r2}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_{p1}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p1}, \mathcal{L}_2)  P(r_{p1}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
+& P_{L_1}(r_{p2}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{p2}, \mathcal{L}_2) P(r_{p2}) P(\mathcal{L}_2) = 0 \times 0.26 \times 0.5=0\\
 & P_{L_1}(r_{y2}, \mathcal{L}_2 | {u_3})  \propto P_{S_1}(u_3 \mid r_{y2}, \mathcal{L}_2) P(r_{y2}) P(\mathcal{L}_2) = 1 \times 0.48 \times 0.5=0.24\\
@@
 $$
+
 To conclude the example, according to the parameter free pragmatics model, the proability that $L_1$ thinks that $S_1$ is reffering to a yellow-ish object when producing $u_3$ is 0.91.
-Based on this model we thus expected that, on average, participants would select the yellow-ish object in 91% of cases in the preference--different speaker--congruent condition.
-
-<!-- The utterances available to a speaker are (action, label) pairs, where the action involves turning (or pointing) to a particular location (i.e., a table) and labels are novel words, which are assumed to refer to the type of the object.
--->
-<!-- The action of the turning or pointing rules out the referents that are not on the table targeted by the turn (point).  -->
-<!-- The listener knows that the labels refer to the kind of object but does not know which kind is referred to be which label, formalized by the prior over lexica $P(L)$.  -->
-
-<!-- In principle, the speaker, the frog in this case, can perform one of two utterances: $u_1$, which is turning to the right table (two objects) and making a request by using a novel label or $u_2$, which involves turning to the left table (single object) and making a request by using a novel label.
--->
-
-<!-- For example, in SI Figure 1, two possible labels are "dax" and "wug", each of which could either mean. -->
-
-<!-- Because we studied word learning, we assumed that the listener ($L_1$) had no prior expectations that a particular lexicon  is more likely.
-In the model, $P(L)$ therefore took the form of a uniform distribution over potential lexica.
--->
+Based on this model we thus expected that, on average, participants would select the yellow-ish object in 91% of cases in a condition with the prior distribution specified above.
 
@@
 the yellow-ish object was the more informative object as in Fig.
-\ref{fig:figS1}), the distribution of objects was [$r_{p}^1, r_{p}^2, r_y^2$].
+\ref{fig:figS1}), the distribution of objects was [$r_{p1}, r_{p2}, r_{y2}$].
 Using the raw proportions, the corresponding prior distribution was [$P(r_{p}^1) = 0.03, P(r_{p}^2) = 0.03, P(r_{y}^2) = 0.97$] and after normalizing (so that they add up to 1) it was [0.03, 0.03, 0.94].
 When information sources were dis-aligned (i.e.
-the pink-ish object was the more informative one), the object distribution was ($r_{y}^1, r_{p}^2, r_y^2$) and the prior distribution was thus [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.
+the pink-ish object was the more informative one), the object distribution was [$r_{y1}, r_{p2}, r_{y2}$] and the prior distribution was thus [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.
 
@@
   ylab("Data")+
-  facet_grid(model~noise)+
+  facet_grid(noise~model)+
   theme_few() + 

### 2019-08-19 papers/full_paper/SI_appendix.Rmd
add analysis details to SI

@@
 title             : "Supplementary information:Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
-shorttitle        : " "
+shorttitle        : "Supplementary information"
 
@@
 library(broom)
+library(exactRankTests)
 
@@
 
-Based on euqation 2 we can now compute the likelihood of each utterance given an object type.
+Based on equation 2 we can now compute the likelihood of each utterance given an object type.
 Recall the two lexica: $\mathcal{L}_1 = \{dax: \text{pink-ish thing}, wug: \text{yellow-ish thing} \}$, $\mathcal{L}_2 = \{dax: \text{yellow-ish thing}, wug: \text{pink-ish thing}\}$, and the four utterances:  $u_1 = (\text{left}, dax)$, $u_2 = (\text{left}, wug)$, $u_3 = (\text{right}, dax)$, $u_4 = (\text{right}, wug)$.
@@
 
-To conclude the example, according to the parameter free pragmatics model, the proability that $L_1$ thinks that $S_1$ is reffering to a yellow-ish object when producing $u_3$ is 0.91.
+To conclude the example, according to the parameter free pragmatics model, the probability that $L_1$ thinks that $S_1$ is referring to a yellow-ish object when producing $u_3$ is 0.91.
 Based on this model we thus expected that, on average, participants would select the yellow-ish object in 91% of cases in a condition with the prior distribution specified above.
@@
 The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused on common ground manipulation.
-The only inforamtion available to $L_1$ is the prior distribution over referents.
+The only information available to $L_1$ is the prior distribution over referents.
 It is therefore defined as:
@@
 Model code for inferring the intercept and the slope for the child study can be found in the associated online repository.
-
-# Prior strength manipualtions Experiment 4
-
-```{r ex4 prior pre-tests data adults}
-# load data from prior strength manipulation experiments to set priors
-adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
-```
-
-```{r table_prior,results = "asis"}
-ex4_prior_models <- adult_ex4_prior_data %>%
-  group_by(common_ground_manipulation,prior_manipulation)%>%
-  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
-
-ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
-  filter(group == "fixed")%>%
-  select(-statistic, -group)%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2),
-         term = case_when(term == "(Intercept)" ~ "Intercept",
-                          term == "speakersame_speaker" ~ "condition (same speaker)"))%>%
-  rename(Manipulation = common_ground_manipulation,
-         Strength = prior_manipulation,
-         Term = term,
-         Estimate = estimate,
-         SE = std.error,
-         p = p.value)
-
-apa_table(
-  ex4_prior_models_table
-  , caption = "Model output for prior strength experiments "
-  , note = "Model structure in all cases: correct ~ condition + (1|id) + (1|agent)"
-  , escape = T
-)
-```
-
-Below we describe the different ways in which prior strength was manipulated in Experiment 4.
-The corresponding experiments can be found in the online repository.
-The test event was always the same: The animal disappeared and then either the same or a different animal returned and requested an object using an unknown word.
-
-For preference, at the beginning of the experiment both tables contained an object.
-In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
-Then they turned the other side and expressed the respective other attitude.
-In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
-
-For novelty, one table was empty while there was an object on the other.
-In novelty/strong the animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
-Then the animal turned to the other side and commented in a complementary way.
-Next, the animal disappeared.
-The same animal re-appeared and the sequence above was repeated.
-When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
-In novelty/medium, the animal commented on the presence/absence of objects in the same way but did so only once.
-In novelty/weak, the animal only turned to the present object and commented on it.
-
-In all cases, the order of utterances and/or the side to which the speaker turned first were counterbalanced.
-Figure \ref{fig:priorplot} shows the results for the same speaker and different speaker conditions for each manipulation.
-
-```{r priorplot, fig.cap = "Results from prior strength manipulation Experiments.
-Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", fig.height = 3}
-
-p_adult_ex4_priors <- adult_ex4_prior_data%>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
-  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
-  summarise(correct = mean(correct))
-
-p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
-  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="")+
-  facet_grid(common_ground_manipulation ~ prior_manipulation)+
-  theme_few() + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F,size =F)+
-  scale_color_solarized()+
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "right")
-```
-
-Table \ref{tab:table_prior} shows the results of a generalized linear mixed model (GLMM) fit to the data from each manipulation.
-The results show that the parameter estimates for condition (i.e.
-difference between same speaker and different speaker condition) decreases in line with the hypothesized effect of the prior manipulation.
 
@@
 
+# Supplemental results
+
+The following sections present details on the analyses used to evaluate whether the different experimental manipulations produced different responses.
+For all generalized linear mixed models (GLMM) we used the maximally converging random effects structure.
+
+## Experiment 1
+
+```{r table_chance_Ex_1_2,results = "asis"}
+chance_comp_ex_1_2 <- bind_rows(
+    adult_ex1_data,
+    adult_ex2_novelty_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")),
+    adult_ex2_preference_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control"))
+  )%>%
+    mutate(condition = factor(condition, levels = c("test","control")),
+           experiment = factor(experiment, levels = c("adult_ex1","adult_ex2_preference","adult_ex2_novelty")),
+           experiment = recode(experiment, 
+                               adult_ex1 = "Experiment 1",
+                               adult_ex2_preference = "Experiment 2A: Preference", 
+                               adult_ex2_novelty = "Experiment 2B: Novelty"))%>%
+  group_by(experiment,condition, id) %>%
+  summarise(correct = mean(correct))%>%
+  summarise(correct = list(correct)) %>%
+  group_by(experiment,condition) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment,condition,mean,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+apa_table(
+  chance_comp_ex_1_2
+  , caption = "Comparison to chance in each condition of Experiment 1, 2A and 2B"
+  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
+  , escape = T
+)
+
+```
+
+We used one sample t-tests to test if participants selected the more informative object (the one unique to the table the animal pointed at) above chance (50%).
+Table \ref{tab:table_chance_Ex_1_2} shows the results.
+
+```{r}
+# model
+lm_ex1 <- glmer(correct ~ condition +
+              (1 |id), 
+              data = adult_ex1_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex1)
+
+ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+To compare the two conditions, we fit the following GLMM: `correct ~ condition + (1 |id)`.
+Participants chose the more informative object more often in the test condition compared to the control condition ($\beta$ = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
+
+## Experiment 2
+
+```{r}
+# model (maximally converging)
+lm_ex2pref <- glmer(correct ~ condition +
+              (1|id) + (1|agent), 
+              data = adult_ex2_preference_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2pref)
+
+ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+
+ex2tnov <- adult_ex2_novelty_data %>%
+  group_by(condition, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(condition) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(condition,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+# model
+lm_ex2nov <- glmer(correct ~ condition +
+              (condition|id), 
+              data = adult_ex2_novelty_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2nov)
+
+ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+Table \ref{tab:table_chance_Ex_1_2} shows results for the comparison to chance in Experiment 2A and B.
+In Experiment 2A, we fit the following GLMM: `correct ~ condition + (1|id) + (1|agent)`.
+Here, `agent` refers to the animal making the request.
+Participants chose the object previously preferred by the speaker more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+For Experiment 2B, we fit the following GLMM: `correct ~ condition + (condition|id)`.
+Participants chose the novel object more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+
+## Experiment 3
+
+```{r ex3_model, results = "asis"}
+# model 
+lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
+              data = adult_ex3_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex3)
+
+lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))
+
+apa_table(
+  lm_ex3_r
+  , caption = "GLMM output for Experiment 3"
+  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+
+```
+
+To see if participants differentiated between conditions, we fit the following GLMM to the data: `correct_inf ~ common ground*speaker*alignment + (alignment|id)`.
+The dependent variable `correct_inf` captures whether participants chose the more informative object.
+Table \ref{tab:ex3_model} shows the model output.
+
+## Prior strength manipualtions Experiment 4
+
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+```
+
+```{r table_prior,results = "asis"}
+ex4_prior_models <- adult_ex4_prior_data %>%
+  group_by(common_ground_manipulation,prior_manipulation)%>%
+  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
+
+ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
+  filter(group == "fixed")%>%
+  select(-statistic, -group)%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2),
+         term = case_when(term == "(Intercept)" ~ "Intercept",
+                          term == "speakersame_speaker" ~ "condition (same speaker)"))%>%
+  rename(Manipulation = common_ground_manipulation,
+         Strength = prior_manipulation,
+         Term = term,
+         Estimate = estimate,
+         SE = std.error,
+         p = p.value)
+
+apa_table(
+  ex4_prior_models_table
+  , caption = "GLMMs output for prior strength experiments"
+  , note = "Model structure in all cases: correct ~ condition + (1|id) + (1|agent)"
+  , escape = T
+)
+```
+
+Below we describe the different ways in which prior strength was manipulated in Experiment 4.
+The corresponding experiments can be found in the online repository.
+The test event was always the same: The animal disappeared and then either the same or a different animal returned and requested an object using an unknown word.
+
+For preference, at the beginning of the experiment both tables contained an object.
+In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
+Then they turned the other side and expressed the respective other attitude.
+In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
+
+For novelty, one table was empty while there was an object on the other.
+In novelty/strong the animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
+Then the animal turned to the other side and commented in a complementary way.
+Next, the animal disappeared.
+The same animal re-appeared and the sequence above was repeated.
+When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
+In novelty/medium, the animal commented on the presence/absence of objects in the same way but did so only once.
+In novelty/weak, the animal only turned to the present object and commented on it.
+
+In all cases, the order of utterances and/or the side to which the speaker turned first were counterbalanced.
+Figure \ref{fig:priorplot} shows the results for the same speaker and different speaker conditions for each manipulation.
+
+```{r priorplot, fig.cap = "Results from prior strength manipulation Experiments.
+Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", fig.height = 3}
+
+p_adult_ex4_priors <- adult_ex4_prior_data%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
+  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
+  summarise(correct = mean(correct))
+
+p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
+  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="")+
+  facet_grid(common_ground_manipulation ~ prior_manipulation)+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F,size =F)+
+  scale_color_solarized()+
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "right")
+```
+
+Table \ref{tab:table_prior} shows the results of a GLMM fit to the data from each manipulation.
+The results show that the parameter estimates for condition (i.e.
+difference between same speaker and different speaker condition) decreases in line with the hypothesized effect of the prior manipulation.
+
+## Experiment 4
+
+```{r ex4_models, results = "asis"}
+lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_strong)
+
+lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "strong")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_medium)
+
+lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "medium")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_weak)
+
+lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "weak")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+t_ex4_r <- bind_rows(
+  lm_ex4_r_strong,
+  lm_ex4_r_medium,
+  lm_ex4_r_weak
+)
+
+apa_table(
+  t_ex4_r
+  , caption = "GLMMs output for Experiment 4"
+  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+
+```
+
+To assess how participants differentiated between combinations of manipulations, we fit a separate GLMM to the data of each level of prior strength manipulation.
+Please note that we did not find a weak manipulation for preference.
+Model outputs are shown in Table \ref{tab:ex4_models}.
+Model structure for each level of prior strength manipulation was as follows:
+
+* Strong:`correct_inf ~ common ground*speaker*alignment + (speaker+alignment|id)`
+* Medium:`correct_inf ~ common ground*speaker*alignment + (alignment|id)`
+* Weak:`correct_inf ~ correct_inf ~ speaker*alignment + (speaker+alignment|id)`
+
+## Experiment 5
+
+```{r child_chance_comp, results = "asis"}
+#experiment 1
+child_ex1t <- child_ex1_data %>%
+  mutate(condition = "test",
+         experiment = "Experiment 5")%>%
+  group_by(experiment,condition,age_bin, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(age_bin) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment,condition, mean, age_bin,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+child_ex1_lm_data <- child_ex1_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# experiment 2
+child_ex2t <- child_ex2_data %>%
+  mutate(condition = ifelse(condition == "same_speaker", "test", "control"),
+         experiment = "Experiment 6")%>%
+  group_by(experiment,condition,age_bin, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(condition,age_bin) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment, condition, mean, age_bin,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+child_chance <- 
+  bind_rows(
+    child_ex1t,
+    child_ex2t
+  )
+
+apa_table(
+  child_chance
+  , caption = "Comparison to chance in each condition of Experiment 5 and 6"
+  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
+  , escape = T
+)
+
+```
+
+Data for children was binned by year for the comparison to chance. As for adults, we used one sample t-tests for this analysis. Table \ref{tab:child_chance_comp} shows the results for Experiment 5.
+
+```{r}
+child_ex1_lm_data <- child_ex1_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# GLMM
+child_ex1_lm <- glmer(correct ~ age_num + (1 | id), 
+              data = child_ex1_lm_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex1_r <- tidy(child_ex1_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+
+```
+
+We fit a GLMM with the following structure to the trial by trial data with age as a continuous variable: `correct ~ age_num + (1|id)`.
+Results show that children became more likely to select the more informative object with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`.
+
+## Experiment 6
+
+```{r}
+child_ex2_lm_data <- child_ex2_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (1 | agent), 
+              data = child_ex2_lm_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex2_r <- tidy(child_ex2_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+Comparison to chance within each condition of Experiment 6 is given in Table \ref{tab:child_chance_comp}.
+We fit a GLMM with the following structure to the data: `correct ~ age_num*condition + (condition|id) + (1|agent)`.
+The model output shows an effect of condition (same or different speaker) ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`).
+
+## Experiment 7
+
+```{r child_models, results = "asis"}
+child_ex3_lm_data <- child_ex3_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
+      + (speaker+alignment | id), 
+      family = "binomial",
+      data = child_ex3_lm_data,
+      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex3_r <- tidy(child_ex3_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+    mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       age_num = "age",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `age_num:speakersame_speaker` = "age * speaker",
+                       `age_num:alignmentincongruent` = "age * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `age_num:speakersame_speaker:alignmentincongruent` = "age * speaker * alignment"
+         ))
+
+apa_table(
+  child_lm_ex3_r
+  , caption = "GLMM output for Experiment 7"
+  , note = "Reference level: speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+```
+
+To see if children differentiated between the different combinations of manipulations in Experiment 7, we fit the following GLMM to the data: `correct_inf ~ age_num*speaker*alignment+ (speaker+alignment|id)`.
+Model output is shown in Table \ref{tab:child_models}.
+
 \newpage

### 2019-09-03 papers/full_paper/SI_appendix.Rmd
migrate manuscript and complete SI

@@
 ---
-title             : "Supplementary information:Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
-shorttitle        : "Supplementary information"
+title             : "Supplementary information: Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+shorttitle        : "Pragmatic cue integration: Supplementary information"
 
@@
 
-Here we present details for the cognitive models as well as supplementary analysis and results.
+Here we present additional information about methods, results and cognitive models.
 Readers who are interested in the model code and analysis code itself are encouraged to consult the associated online repository: https://github.com/manuelbohn/mcc.
+
+# Supplemental methods and results
+
+The following sections present details on the analyses used to evaluate whether the different experimental manipulations produced different responses.
+For all generalized linear mixed models (GLMM) we used the maximally converging random effects structure.
+
+## Experiment 1
+
+### Procedure
+
+```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 1, 3 and 4.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup_inf.png")
+```
+
+The setup and procedure of Experiment 1 for adults are shown in Figure 1A in the main manuscript as well as Figure \ref{fig:figS1}.
+In the beginning of each trial, the animal introduced themselves (e.g.
+“Hi, I’m Dog”) and then turned towards the table with the two objects.
+The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”).
+In the test condition, there was one object on the other table (left table in Figure \ref{fig:figS1}), whereas in the control condition, there were two.
+In the control condition, no inference was possible based on the speaker’s turning and pointing.
+The “correct” object in the control condition was randomly chosen from the two objects on the table.
+Technically, this condition did not control for any alternative explanations and we therefore did not run it for children.
+Participants received six trials, three per condition.
+Conditions were presented in a random order.
+
+```{r table_chance_Ex_1_2,results = "asis"}
+chance_comp_ex_1_2 <- bind_rows(
+    adult_ex1_data,
+    adult_ex2_novelty_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")),
+    adult_ex2_preference_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control"))
+  )%>%
+    mutate(condition = factor(condition, levels = c("test","control")),
+           experiment = factor(experiment, levels = c("adult_ex1","adult_ex2_preference","adult_ex2_novelty")),
+           experiment = recode(experiment, 
+                               adult_ex1 = "Experiment 1",
+                               adult_ex2_preference = "Experiment 2A: Preference", 
+                               adult_ex2_novelty = "Experiment 2B: Novelty"))%>%
+  group_by(experiment,condition, id) %>%
+  summarise(correct = mean(correct))%>%
+  summarise(correct = list(correct)) %>%
+  group_by(experiment,condition) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment,condition,mean,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+apa_table(
+  chance_comp_ex_1_2
+  , caption = "Comparison to chance in each condition of Experiment 1, 2A and 2B"
+  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
+  , escape = T
+)
+
+```
+
+```{r plotex12, fig.cap = "Results from experiment 1 and 2 for adults.
+For preference and novelty, control refers to a different speaker (see Fig.
+1B).
+Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", fig.height = 3}
+p1 <- bind_rows(
+    adult_ex1_data,
+    adult_ex2_novelty_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")),
+    adult_ex2_preference_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control"))
+  )%>%
+    mutate(condition = factor(condition, levels = c("test","control")),
+           experiment = factor(experiment, levels = c("adult_ex1","adult_ex2_preference","adult_ex2_novelty")))%>%
+  group_by(experiment,condition, id) %>%
+  summarise(correct = mean(correct))
+
+p2 <- p1 %>%
+  multi_boot_standard(col = "correct")
+
+ ggplot() +
+  geom_jitter(data = p1, aes(x = condition, y = correct, col = condition), alpha = 0.2, width = .3,height = .025)+
+  geom_pointrange(data = p2, aes(x = condition, y = mean, col = condition,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Proportion correct")+
+  facet_wrap( ~ experiment, labeller = as_labeller(c(`adult_ex2_preference`="Exp. 2A - Preference", `adult_ex2_novelty`="Exp. 2B - Novelty", `adult_ex1`="Exp. 1 - Informativeness")))+
+  theme_few(base_size = 10) + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F,size =F)+
+  scale_color_solarized(name = "Condition",
+                     labels=c("Test","Control"))+
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = c(0.75, 0.17), 
+        legend.background = element_blank())
+```
+
+### Results
+
+We used one sample t-tests to test if participants selected the more informative object (the one unique to the table the animal pointed at) above chance (50%).
+Table \ref{tab:table_chance_Ex_1_2} and Figure \ref{fig:plotex12} show the results.
+
+```{r}
+# model
+lm_ex1 <- glmer(correct ~ condition +
+              (1 |id), 
+              data = adult_ex1_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex1)
+
+ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+To compare the two conditions, we fit the following GLMM: `correct ~ condition + (1 |id)`.
+Participants chose the more informative object more often in the test condition compared to the control condition ($\beta$ = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
+
+## Experiment 2
+
+### Procedure
+
+```{r figS2, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation in Experiment 2 for adults.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup_pref.png")
+```
+
+The setup and procedure of Experiment 2 are shown in Fig.
+1B in the main manuscript as well as Figure \ref{fig:figS2}.
+In the preference manipulation, the animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
+Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
+Here, participants could identify the referent by assuming that the speaker was talking about the object they liked, if the speaker remained the same but not when a different speaker made a request.
+This procedure corresponds to the strong preference manipulation in Experiment 4 (see below).
+
+In the novelty manipulation one of the tables was initially empty.
+The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
+After shortly disappearing, the same animal repeated the sequence above.
+When the animal left a second time, a new object appeared on the empty table.
+Next, either the same or a different animal returned and requested an object.
+In this context, participants could infer that it was the new object that the speaker was referring to, if the speaker was the same.
+In contrast, when a different speaker (to whom both objects were equally new) made a request, no inference could be made based on the speaker’s knowledge.
+This corresponded to the strong manipulation in Experiment 4 (see below).
+
+In both Experiment 2A and 2B, participants always received six trials, three with the same and three with the different speaker. Conditions were presented in a random order.
+
+### Results
+
+```{r}
+# model (maximally converging)
+lm_ex2pref <- glmer(correct ~ condition +
+              (1|id) + (1|agent), 
+              data = adult_ex2_preference_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2pref)
+
+ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+
+ex2tnov <- adult_ex2_novelty_data %>%
+  group_by(condition, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(condition) %>%
+  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(condition,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+# model
+lm_ex2nov <- glmer(correct ~ condition +
+              (condition|id), 
+              data = adult_ex2_novelty_data, 
+              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex2nov)
+
+ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+Table \ref{tab:table_chance_Ex_1_2} and Figure \ref{fig:plotex12} show results for the comparison to chance in Experiment 2A and B.
+In Experiment 2A, we fit the following GLMM: `correct ~ condition + (1|id) + (1|agent)`.
+Here, `agent` refers to the animal making the request.
+Participants chose the object previously preferred by the speaker more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+For Experiment 2B, we fit the following GLMM: `correct ~ condition + (condition|id)`.
+Participants chose the novel object more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+
+## Experiment 3
+
+### Procedure
+
+For Experiment 3 we inserted the common ground manipulation before the request in the setup of Experiment 1 (see Figure 1C in the main manuscript for one example).
+For example, the animal turned to the table with one object and expressed that they liked the object  (pink-ish object in Figure \ref{fig:figS1}), then turned to the other table and express that they did not like object B (yellow-ish object in Figure \ref{fig:figS1}).
+Next, after quickly disappearing, the animal reappeared, turned to the table with two objects and made a request.
+To make it clear, which of the objects the speaker commented on while being turned to the table with the two objects during the common ground manipulation, the object was temporarily enlarged.
+Utterances were the same as in Experiment 1 and 2A and B.
+
+Combining information sources yielded eight different conditions.
+Informativeness and common ground could either be congruent or incongruent.
+If, for example, the yellow-ish object in Figure \ref{fig:figS1} (i.e.
+the more informative object because unique to that table) was also the one the speaker expressed preference for, the two sources of information were congruent.
+Next, the speaker who made the request could either be the same as the one in the previous interaction or a different one.
+Finally, common ground information could be manipulated in the form of preference or novelty.
+This resulted in a total of 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions.
+
+Participants completed eight trials for one of the common ground manipulations with two trials per condition (same/different speaker x congruent/incongruent).
+Conditions were presented in a random order.
+
+### Results
+
+```{r ex3_model, results = "asis"}
+# model 
+lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
+              data = adult_ex3_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex3)
+
+lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))
+
+apa_table(
+  lm_ex3_r
+  , caption = "GLMM output for Experiment 3"
+  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+
+```
+
+```{r plotex3, fig.cap = "Data and model predictions by condition for Experiment 3 with adults.
+Transparent dots show data from individual participants, diamonds represent condition means.
+Empirical means are shonw in black and model predictions in pink.
+Error bars represent 95\\% HDIs.", fig.height = 4}
+adult_ex3_data_summary <- adult_ex3_data %>%
+  mutate(model = "data") %>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+adult_ex3_pragm_model_pred_noise <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
+  filter(!(Parameter %in% c("noise")))  %>%
+  separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
+  mutate(model="pragmatic")%>%
+  group_by(model,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+adult_ex3_pred <- bind_rows(
+  adult_ex3_pragm_model_pred_noise,
+  adult_ex3_data_summary
+) %>%
+  ungroup()%>%
+  mutate(common_ground_manipulation = ifelse(common_ground_manipulation == "novelty", "Novelty", "Preference"),
+         speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))
+
+adult_ex3_plot_data <- adult_ex3_data %>%
+  mutate(model = "data")%>%
+  group_by(model,id,common_ground_manipulation,speaker,alignment)%>%
+  summarise(mean = mean(correct_inf))%>%
+  ungroup()%>%
+  mutate(common_ground_manipulation = ifelse(common_ground_manipulation == "novelty", "Novelty", "Preference"),
+         speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))
+
+ggplot(data = adult_ex3_pred, aes(x = alignment, y = mean, col = model)) +
+  geom_jitter(data = adult_ex3_plot_data, alpha = .1, height = 0.02)+
+  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .6,  position = position_dodge(width = .5), pch = 5)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="Choosing more informative")+
+  facet_grid (~ common_ground_manipulation + speaker) +
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_color_manual(name= element_blank(),
+                     labels=c("Data","Model"),
+                     values= c("black","#6c71c4"))+
+  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1), legend.position = c(0.1, 0.25), 
+        legend.background = element_blank())
+```
+
+We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).
+Figure\ref{fig:plotex3} shows the result in each of the eight conditions of Experiment 3.
+Results are plotted from  The plot also shows model predictions from the pragmatics model (including the noise parameter - see below).
+
+To see if participants differentiated between conditions, we fit the following GLMM to the data: `correct_inf ~ common ground*speaker*alignment + (alignment|id)`.
+Table \ref{tab:ex3_model} shows the model output.
+Results show that participants clearly differentiated between congruent and incongruent trials when the speaker remained the same.
+
+## Experiment 4
+
+### Prior strength manipualtions
+
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+```
+
+```{r table_prior,results = "asis"}
+ex4_prior_models <- adult_ex4_prior_data %>%
+  group_by(common_ground_manipulation,prior_manipulation)%>%
+  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
+
+ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
+  filter(group == "fixed")%>%
+  select(-statistic, -group)%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2),
+         term = case_when(term == "(Intercept)" ~ "Intercept",
+                          term == "speakersame_speaker" ~ "condition (same speaker)"))%>%
+  rename(Manipulation = common_ground_manipulation,
+         Strength = prior_manipulation,
+         Term = term,
+         Estimate = estimate,
+         SE = std.error,
+         p = p.value)
+
+apa_table(
+  ex4_prior_models_table
+  , caption = "GLMMs output for prior strength experiments"
+  , note = "Model structure in all cases: correct ~ condition + (1|id) + (1|agent)"
+  , escape = T
+)
+```
+
+Below we describe the different ways in which prior strength was manipulated in Experiment 4.
+The corresponding experiments can be found in the online repository.
+The test event was always the same: The animal disappeared and then either the same or a different animal returned and requested an object using an unknown word.
+
+For preference, at the beginning of the experiment both tables contained an object.
+In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
+Then they turned the other side and expressed the respective other attitude.
+In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
+
+For novelty, one table was empty while there was an object on the other.
+In novelty/strong the animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
+Then the animal turned to the other side and commented in a complementary way.
+Next, the animal disappeared.
+The same animal re-appeared and the sequence above was repeated.
+When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
+In novelty/medium, the animal commented on the presence/absence of objects in the same way but did so only once.
+In novelty/weak, the animal only turned to the present object and commented on it.
+
+In all cases, the order of utterances and/or the side to which the speaker turned first were counterbalanced.
+Figure \ref{fig:priorplot} shows the results for the same speaker and different speaker conditions for each manipulation.
+
+```{r priorplot, fig.cap = "Results from prior strength manipulation Experiments.
+Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", fig.height = 4.5}
+
+p_adult_ex4_priors <- adult_ex4_prior_data%>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
+  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
+  summarise(correct = mean(correct))
+
+p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
+  multi_boot_standard(col = "correct")
+
+ggplot() +
+  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
+  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
+  geom_hline(yintercept = 0.5, lty=2)+
+  labs(x="",y="")+
+  facet_grid(common_ground_manipulation ~ prior_manipulation)+
+  theme_few() + 
+  ylim(-0.05,1.05)+
+  guides(alpha = F,size =F)+
+  scale_color_solarized(name = "Speaker")+
+  theme(legend.position = c(0.85, 0.1),legend.background = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
+```
+
+### Procedure
+
+The general procedure in Experiment 4 was the same as in Experiment 3.
+We ran a total of  2 (novelty or preference) x 3 (weak, medium, strong) x 2 (same or different speaker) x 2 (congruent or incongruent) - 4 (no weak manipulation for preference) = 20 conditions.
+Each participant was randomly assigned to a common ground manipulation and a level of prior strength and completed eight trials in total, two in each unique condition in that combination.
+The strong prior manipulation was a direct replication of Experiment 3.
+
+Table \ref{tab:table_prior} shows the results of a GLMM fit to the data from each manipulation.
+The results show that the parameter estimates for condition (i.e.
+difference between same speaker and different speaker condition) decreases in line with the hypothesized effect of the prior manipulation.
+
+### Results
+
+```{r}
+adult_ex4_data_summary <- adult_ex4_data %>%
+  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
+  mutate(model = "data") %>%
+  group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b),
+         mean = (a-1)/(a+b-2))%>%
+  select(-a,-b,-n,-k)
+
+cor_3_4 <- cor.test(adult_ex3_data_summary%>%pull(mean), adult_ex4_data_summary%>%filter(prior_manipulation == "strong")%>%pull(mean))
+
+```
+
+```{r ex4_models, results = "asis"}
+lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_strong)
+
+lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "strong")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_medium)
+
+lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "medium")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
+              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+#summary(lm_ex4_weak)
+
+lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+  as_tibble()%>%
+  mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       common_ground_manipulationpreference = "common ground",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
+                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
+         ))%>%
+  mutate(`prior strength` = "weak")%>%
+  select(`prior strength`, term, estimate, std.error, statistic,p.value)
+
+t_ex4_r <- bind_rows(
+  lm_ex4_r_strong,
+  lm_ex4_r_medium,
+  lm_ex4_r_weak
+)
+
+apa_table(
+  t_ex4_r
+  , caption = "GLMMs output for Experiment 4"
+  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+
+```
+
+Results from Experiment 3 and 4 (strong prior manipulation) were highly correlated (r = `r cor_3_4$estimate`, *p* > .001).
+
+To assess how participants differentiated between combinations of manipulations, we fit a separate GLMM to the data of each level of prior strength manipulation.
+Please note that we did not find a weak manipulation for preference.
+Model outputs are shown in Table \ref{tab:ex4_models}.
+Model structure for each level of prior strength manipulation was as follows:
+
+* Strong:`correct_inf ~ common ground*speaker*alignment + (speaker+alignment|id)`
+* Medium:`correct_inf ~ common ground*speaker*alignment + (alignment|id)`
+* Weak:`correct_inf ~ correct_inf ~ speaker*alignment + (speaker+alignment|id)`
+
+A general observation to make is that, with common ground information getting weaker, changing the speaker has less of an impact on the informativeness inference.
+That is, the term `alignment x speaker` is only significant for the strong and medium manipulation but not the  weak manipulation.
+
+## Experiment 5
+
+### Procedure
+
+```{r figS3, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 5 and 7.", out.width="400px"}
+knitr::include_graphics("./figures/SI_setup_inf_child.png")
+```
+
+Experiment 5 for children was modeled after [@frank2014inferring].
+Instead of on tables, objects were presented as hanging in trees in order to facilitate showing points to distinct locations (see Figure \ref{fig:figS3}).
+After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
+Next, the trees and the objects in them disappeared and new trees replaced them.
+The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced).
+While facing straight, the animal first said “Here are some more trees” and then asked the child to pick the tree with the object that corresponded to the novel word (“Which of these trees has a [non-word]?”).
+Children received six trials in a single test condition.
+
+### Results
+
+```{r child_chance_comp, results = "asis"}
+#experiment 1
+child_ex1t <- child_ex1_data %>%
+  mutate(condition = "test",
+         experiment = "Experiment 5")%>%
+  group_by(experiment,condition,age_bin, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(age_bin) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment,condition, mean, age_bin,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+child_ex1_lm_data <- child_ex1_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# experiment 2
+child_ex2t <- child_ex2_data %>%
+  mutate(condition = ifelse(condition == "same_speaker", "test", "control"),
+         experiment = "Experiment 6")%>%
+  group_by(experiment,condition,age_bin, id) %>%
+  summarise(correct = mean(correct)) %>%
+  summarise(correct = list(correct)) %>%
+  group_by(condition,age_bin) %>%
+  mutate(mean = mean(unlist(correct)),
+         df= t.test(unlist(correct), mu = 0.5)$parameter,
+         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
+  select(experiment, condition, mean, age_bin,df,t_value,p_value)%>%
+  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
+         t_value = round(t_value,2))
+
+child_chance <- 
+  bind_rows(
+    child_ex1t,
+    child_ex2t
+  )
+
+apa_table(
+  child_chance
+  , caption = "Comparison to chance in each condition of Experiment 5 and 6"
+  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
+  , escape = T
+)
+
+```
+
+```{r plotex56, fig.cap = "Results from experiment 5 and 6 for children.
+For preference, control refers to to the different speaker condition (see Fig.
+1B in main manuscript).
+Transparent dots show data from individual participants, regression lines shows smoothed conditional mean with 95\\% CI.
+Dashed line indicates performance expected by chance.", fig.height = 3.5}
+p_child_ex12 <- bind_rows(
+  child_ex1_data%>%mutate(condition = "test"),
+  child_ex2_data%>%mutate(condition = ifelse(condition == "same_speaker","test","control"))
+)%>%
+  mutate(condition = factor(condition, levels = c("control","test")))%>%
+  group_by(experiment,condition,age_num, id) %>%
+  summarise(correct = mean(correct))
+
+ggplot(data = p_child_ex12, aes(x = age_num, y = correct, col = condition)) +
+  geom_hline(yintercept = 0.5, lty=2)+
+  geom_jitter(alpha = 0.2, height = 0.02, width = 0)+
+  geom_smooth(aes(fill = condition),method = "loess", se = T, span = 2,  alpha = .5, size = .7)+
+  labs(x="Age",y="Proportion correct")+
+  facet_wrap( ~ experiment, labeller = as_labeller(c(`child_ex2`="Exp. 6 - Preference", `child_ex1`="Exp. 5 - Informativeness")))+
+  theme_few() +
+  ylim(-0.05,1.05)+
+  guides(alpha = F)+ 
+  scale_colour_solarized(name = "Condition",
+                     labels=c("Control","Test"))+
+  scale_fill_solarized(name = "Condition",
+                    labels=c("Control","Test"))+
+  theme(legend.position = c(0.1, 0.15), 
+        legend.background = element_blank())
+```
+
+Data for children was binned by year for the comparison to chance.
+As for adults, we used one sample t-tests for this analysis.
+Table \ref{tab:child_chance_comp} shows the results for Experiment 5.
+Figure \ref{fig:plotex56} (left) shows the results plotted with age as a continuous variable.
+
+```{r}
+child_ex1_lm_data <- child_ex1_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+# GLMM
+child_ex1_lm <- glmer(correct ~ age_num + (1 | id), 
+              data = child_ex1_lm_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex1_r <- tidy(child_ex1_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+
+```
+
+We fit a GLMM with the following structure to the trial by trial data with age as a continuous variable: `correct ~ age_num + (1|id)`.
+Results show that children became more likely to select the more informative object with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see also Figure \ref{fig:plotex56}).
+
+## Experiment 6
+
+```{r}
+child_ex2_lm_data <- child_ex2_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (1 | agent), 
+              data = child_ex2_lm_data, family = binomial, 
+              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex2_r <- tidy(child_ex2_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))
+```
+
+### Procedure
+
+Experiment 5 for children was identical to the strong preference manipulation for adults.
+Children received eight trials, four with the same and four with a different animal returning, presented in a random order.
+We tested children in the novelty manipulation but found that they did not reliably distinguish between the same and different speaker conditions.
+
+### Results
+
+Comparison to chance within each condition of Experiment 6 is given in Table \ref{tab:child_chance_comp}.
+We fit a GLMM with the following structure to the data: `correct ~ age_num*condition + (condition|id) + (1|agent)`.
+The model output shows an effect of condition (same or different speaker) ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see also Figure \ref{fig:plotex56}).
+
+## Experiment 7
+
+### Procedure
+
+In Experiment 7 for children, we again inserted the preference manipulation from Experiment 6 into the setup of Experiment 5.
+After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
+Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
+Next, the animal disappeared and either the same or a different animal returned.
+The rest of the trial was identical to the label and request phase of Experiment 5.
+Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
+Children had the option to opt out after half of the test trials.
+Therefore, we constraint the randomization of conditions so that children received two blocks of trials, one with a trial from each condition.
+
+### Results
+
+```{r child_models, results = "asis"}
+child_ex3_lm_data <- child_ex3_data%>%
+  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
+
+child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
+      + (speaker+alignment | id), 
+      family = "binomial",
+      data = child_ex3_lm_data,
+      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
+
+child_lm_ex3_r <- tidy(child_ex3_lm, effects = "fixed")%>%
+  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
+         std.error = round(std.error,2),
+         estimate = round(estimate,2))%>%
+    mutate(term = recode(term, 
+                       `(Intercept)` = "Intercept",
+                       age_num = "age",
+                       speakersame_speaker = "speaker",
+                       alignmentincongruent = "alignment",
+                       `age_num:speakersame_speaker` = "age * speaker",
+                       `age_num:alignmentincongruent` = "age * alignment",
+                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
+                       `age_num:speakersame_speaker:alignmentincongruent` = "age * speaker * alignment"
+         ))
+
+apa_table(
+  child_lm_ex3_r
+  , caption = "GLMM output for Experiment 7"
+  , note = "Reference level: speaker - different speaker, alignment - congruent."
+  , escape = T
+)
+```
+
+```{r plotmodelpredex7, fig.cap = "Model predictions and data for Experiment 7 with children.
+Colored lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants and the black line with grey CI shows the smoothed conditional mean of the data in each condition.", fig.height = 4}
+child_model_predictions <- readRDS("../../stats/saves/child_ex3_model_predictions.rds")%>%
+  mutate(speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))
+
+plot_child_ex3_data <- child_ex3_data%>%
+  mutate(speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))%>%
+  group_by(age_num,speaker,alignment)%>%
+  summarise(mean = mean(correct_inf))
+
+p_child_ex3_data <- child_ex3_data %>%
+  mutate(speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))
+
+ggplot(child_model_predictions)+
+  geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
+  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
+  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
+  geom_smooth(data = p_child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
+  #geom_hline(yintercept = 0.5, lty=2)+
+  labs(y="Proportion more informative", x = "Age")+
+  ylim(-0.05,1.05)+
+  facet_grid(~speaker+alignment)+
+  theme_few()+
+  theme(legend.position="bottom")+
+  scale_color_manual(name="Model",
+                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     values= c("#00afaf","#af6300","#6c71c4"))+
+  scale_fill_manual(name="Model",
+                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     values= c("#00afaf","#af6300","#6c71c4"))
+
+```
+
+Figure \ref{fig:plotmodelpredex7} shows the results for each condition plotted by age as a continuous variable.
+The same figure also shows model predictions from the pragmatics model with different noise parameters (see below).
+
+To see if children differentiated between the different combinations of manipulations in Experiment 7, we fit the following GLMM to the data: `correct_inf ~ age_num*speaker*alignment+ (speaker+alignment|id)`.
+Model output is shown in Table \ref{tab:child_models}.
 
@@
 
-## Worked Example
+### Worked Example
 
@@
 The values of the parameters are taken from a preference  condition (see below).
-Fig.
-\ref{fig:figS1} shows a screenshot from the adult experiment, which the model was designed to capture.
+Figure \ref{fig:figS1} shows a screenshot from the adult experiment, which the model was designed to capture.
 In this context, there are three potential referents of two types (pink-ish and yellow-ish; for simplicity, we refer refer the object's type by its color) on two tables: $r_{type:pink, table: 1}$, $r_{type:pink,table: 2}$; one yellow-ish, $r_{type:yellow,table: 2}$).
@@
 We work out the example where the speaker produces utterance $u_3$, pointing to the right table (two objects) and saying the label "dax" (though since the labels have no *a priori* meanings, the computation would be the same for utterance $u_4$).
-
-```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 1, 3 and 4.", out.width="400px"}
-knitr::include_graphics("./figures/SI_setup_inf.png")
-```
 
@@
 
-# Model parameters
+## Model parameters
 
@@
 \ref{fig:figS2} shows the test situation on Experiment 2.
-
-```{r figS2, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation in Experiment 2 for adults.", out.width="400px"}
-knitr::include_graphics("./figures/SI_setup_pref.png")
-```
 
@@
 We added the additional model comparisons because the noise parameter was relatively high.
-The additional model comparisons allow us to see if the pragmatics model provides a better fit when more emphasis is put on the model structure itself.
+The additional model comparisons allow us to see if the pragmatics model provides a better fit when more emphasis is put on the model structure itself (see Figure \ref{fig:plotmodelpredex7} for model predictions from the models with different noise parameters).
 The results show that this was the case.
@@
 child_ex3_model_comparison <- readRDS("../../stats/saves/child_ex3_model_comparison.rds")
-
 child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
@@
   mutate(BF = formatC(BF,2))
-
 apa_table(
@@
 )
-
 ```
@@
   select(-pragmatic,-flat_prior, -prior_only)
-
 apa_table(
@@
   )
-
 child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
@@
 ```{r, include = T}
-
 child_ex3_pragm_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
@@
             ci_upper = hdi_upper(value))
-
 child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
@@
             ci_upper = hdi_upper(value))
-
 child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
@@
             ci_upper = hdi_upper(value))
-
 developmental_noise_parameter <- data_frame(
@@
 Error bars represent 95\\% HDIs.", fig.height = 7}
-
 # child_cor <- bind_rows(
@@
          data_ci_lower = rep(p_child_ex3_data%>%pull(ci_lower),9))
-
 ggplot(p_child_cor, aes(x = mean, y = data_mean, col = age)) +
@@
   theme(legend.position = "bottom")
-
-```
-
-# Supplemental results
-
-The following sections present details on the analyses used to evaluate whether the different experimental manipulations produced different responses.
-For all generalized linear mixed models (GLMM) we used the maximally converging random effects structure.
-
-## Experiment 1
-
-```{r table_chance_Ex_1_2,results = "asis"}
-chance_comp_ex_1_2 <- bind_rows(
-    adult_ex1_data,
-    adult_ex2_novelty_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control")),
-    adult_ex2_preference_data %>% mutate(condition = ifelse(condition == "same_speaker", "test", "control"))
-  )%>%
-    mutate(condition = factor(condition, levels = c("test","control")),
-           experiment = factor(experiment, levels = c("adult_ex1","adult_ex2_preference","adult_ex2_novelty")),
-           experiment = recode(experiment, 
-                               adult_ex1 = "Experiment 1",
-                               adult_ex2_preference = "Experiment 2A: Preference", 
-                               adult_ex2_novelty = "Experiment 2B: Novelty"))%>%
-  group_by(experiment,condition, id) %>%
-  summarise(correct = mean(correct))%>%
-  summarise(correct = list(correct)) %>%
-  group_by(experiment,condition) %>%
-  mutate(mean = mean(unlist(correct)),
-         df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(experiment,condition,mean,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
-apa_table(
-  chance_comp_ex_1_2
-  , caption = "Comparison to chance in each condition of Experiment 1, 2A and 2B"
-  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
-  , escape = T
-)
-
-```
-
-We used one sample t-tests to test if participants selected the more informative object (the one unique to the table the animal pointed at) above chance (50%).
-Table \ref{tab:table_chance_Ex_1_2} shows the results.
-
-```{r}
-# model
-lm_ex1 <- glmer(correct ~ condition +
-              (1 |id), 
-              data = adult_ex1_data, 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex1)
-
-ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
-
-To compare the two conditions, we fit the following GLMM: `correct ~ condition + (1 |id)`.
-Participants chose the more informative object more often in the test condition compared to the control condition ($\beta$ = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
-
-## Experiment 2
-
-```{r}
-# model (maximally converging)
-lm_ex2pref <- glmer(correct ~ condition +
-              (1|id) + (1|agent), 
-              data = adult_ex2_preference_data, 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex2pref)
-
-ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-
-ex2tnov <- adult_ex2_novelty_data %>%
-  group_by(condition, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(condition) %>%
-  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(condition,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
-# model
-lm_ex2nov <- glmer(correct ~ condition +
-              (condition|id), 
-              data = adult_ex2_novelty_data, 
-              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex2nov)
-
-ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
-
-Table \ref{tab:table_chance_Ex_1_2} shows results for the comparison to chance in Experiment 2A and B.
-In Experiment 2A, we fit the following GLMM: `correct ~ condition + (1|id) + (1|agent)`.
-Here, `agent` refers to the animal making the request.
-Participants chose the object previously preferred by the speaker more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-For Experiment 2B, we fit the following GLMM: `correct ~ condition + (condition|id)`.
-Participants chose the novel object more often in the test (same speaker) condition compared to the control (different speaker) condition ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-
-## Experiment 3
-
-```{r ex3_model, results = "asis"}
-# model 
-lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
-              data = adult_ex3_data, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex3)
-
-lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))%>%
-  as_tibble()%>%
-  mutate(term = recode(term, 
-                       `(Intercept)` = "Intercept",
-                       common_ground_manipulationpreference = "common ground",
-                       speakersame_speaker = "speaker",
-                       alignmentincongruent = "alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
-                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
-                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
-         ))
-
-apa_table(
-  lm_ex3_r
-  , caption = "GLMM output for Experiment 3"
-  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
-  , escape = T
-)
-
-```
-
-To see if participants differentiated between conditions, we fit the following GLMM to the data: `correct_inf ~ common ground*speaker*alignment + (alignment|id)`.
-The dependent variable `correct_inf` captures whether participants chose the more informative object.
-Table \ref{tab:ex3_model} shows the model output.
-
-## Prior strength manipualtions Experiment 4
-
-```{r ex4 prior pre-tests data adults}
-# load data from prior strength manipulation experiments to set priors
-adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
-```
-
-```{r table_prior,results = "asis"}
-ex4_prior_models <- adult_ex4_prior_data %>%
-  group_by(common_ground_manipulation,prior_manipulation)%>%
-  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
-
-ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
-  filter(group == "fixed")%>%
-  select(-statistic, -group)%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2),
-         term = case_when(term == "(Intercept)" ~ "Intercept",
-                          term == "speakersame_speaker" ~ "condition (same speaker)"))%>%
-  rename(Manipulation = common_ground_manipulation,
-         Strength = prior_manipulation,
-         Term = term,
-         Estimate = estimate,
-         SE = std.error,
-         p = p.value)
-
-apa_table(
-  ex4_prior_models_table
-  , caption = "GLMMs output for prior strength experiments"
-  , note = "Model structure in all cases: correct ~ condition + (1|id) + (1|agent)"
-  , escape = T
-)
-```
-
-Below we describe the different ways in which prior strength was manipulated in Experiment 4.
-The corresponding experiments can be found in the online repository.
-The test event was always the same: The animal disappeared and then either the same or a different animal returned and requested an object using an unknown word.
-
-For preference, at the beginning of the experiment both tables contained an object.
-In preference/strong the animal turned to one side and stated that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object.
-Then they turned the other side and expressed the respective other attitude.
-In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
-
-For novelty, one table was empty while there was an object on the other.
-In novelty/strong the animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence of an object (“Hm, nothing there”).
-Then the animal turned to the other side and commented in a complementary way.
-Next, the animal disappeared.
-The same animal re-appeared and the sequence above was repeated.
-When the animal disappeared for the second time, a second object appeared on the empty table while the animal was away.
-In novelty/medium, the animal commented on the presence/absence of objects in the same way but did so only once.
-In novelty/weak, the animal only turned to the present object and commented on it.
-
-In all cases, the order of utterances and/or the side to which the speaker turned first were counterbalanced.
-Figure \ref{fig:priorplot} shows the results for the same speaker and different speaker conditions for each manipulation.
-
-```{r priorplot, fig.cap = "Results from prior strength manipulation Experiments.
-Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", fig.height = 3}
-
-p_adult_ex4_priors <- adult_ex4_prior_data%>%
-  mutate(prior_manipulation = relevel(as.factor(prior_manipulation), ref = "strong"))%>%
-  group_by(common_ground_manipulation,prior_manipulation,speaker, id) %>%
-  summarise(correct = mean(correct))
-
-p_adult_ex4_priors_ci <- p_adult_ex4_priors %>%
-  multi_boot_standard(col = "correct")
-
-ggplot() +
-  geom_jitter(data = p_adult_ex4_priors, aes(x = speaker, y = correct, col = speaker), alpha = 0.3, width = .3,height = .02)+
-  geom_pointrange(data = p_adult_ex4_priors_ci, aes(x = speaker, y = mean, col = speaker,ymin = ci_lower, ymax = ci_upper),size = .8, pch = 5, fatten = 2.5)+
-  geom_hline(yintercept = 0.5, lty=2)+
-  labs(x="",y="")+
-  facet_grid(common_ground_manipulation ~ prior_manipulation)+
-  theme_few() + 
-  ylim(-0.05,1.05)+
-  guides(alpha = F,size =F)+
-  scale_color_solarized()+
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "right")
-```
-
-Table \ref{tab:table_prior} shows the results of a GLMM fit to the data from each manipulation.
-The results show that the parameter estimates for condition (i.e.
-difference between same speaker and different speaker condition) decreases in line with the hypothesized effect of the prior manipulation.
-
-## Experiment 4
-
-```{r ex4_models, results = "asis"}
-lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_strong)
-
-lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))%>%
-  as_tibble()%>%
-  mutate(term = recode(term, 
-                       `(Intercept)` = "Intercept",
-                       common_ground_manipulationpreference = "common ground",
-                       speakersame_speaker = "speaker",
-                       alignmentincongruent = "alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
-                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
-                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
-         ))%>%
-  mutate(`prior strength` = "strong")%>%
-  select(`prior strength`, term, estimate, std.error, statistic,p.value)
-
-lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_medium)
-
-lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))%>%
-  as_tibble()%>%
-  mutate(term = recode(term, 
-                       `(Intercept)` = "Intercept",
-                       common_ground_manipulationpreference = "common ground",
-                       speakersame_speaker = "speaker",
-                       alignmentincongruent = "alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
-                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
-                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
-         ))%>%
-  mutate(`prior strength` = "medium")%>%
-  select(`prior strength`, term, estimate, std.error, statistic,p.value)
-
-lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_weak)
-
-lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))%>%
-  as_tibble()%>%
-  mutate(term = recode(term, 
-                       `(Intercept)` = "Intercept",
-                       common_ground_manipulationpreference = "common ground",
-                       speakersame_speaker = "speaker",
-                       alignmentincongruent = "alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker` = "common ground * speaker",
-                       `common_ground_manipulationpreference:alignmentincongruent` = "common ground * alignment",
-                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
-                       `common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent` = "common ground * speaker * alignment"
-         ))%>%
-  mutate(`prior strength` = "weak")%>%
-  select(`prior strength`, term, estimate, std.error, statistic,p.value)
-
-t_ex4_r <- bind_rows(
-  lm_ex4_r_strong,
-  lm_ex4_r_medium,
-  lm_ex4_r_weak
-)
-
-apa_table(
-  t_ex4_r
-  , caption = "GLMMs output for Experiment 4"
-  , note = "Reference levels: commmon ground - novelty, speaker - different speaker, alignment - congruent."
-  , escape = T
-)
-
-```
-
-To assess how participants differentiated between combinations of manipulations, we fit a separate GLMM to the data of each level of prior strength manipulation.
-Please note that we did not find a weak manipulation for preference.
-Model outputs are shown in Table \ref{tab:ex4_models}.
-Model structure for each level of prior strength manipulation was as follows:
-
-* Strong:`correct_inf ~ common ground*speaker*alignment + (speaker+alignment|id)`
-* Medium:`correct_inf ~ common ground*speaker*alignment + (alignment|id)`
-* Weak:`correct_inf ~ correct_inf ~ speaker*alignment + (speaker+alignment|id)`
-
-## Experiment 5
-
-```{r child_chance_comp, results = "asis"}
-#experiment 1
-child_ex1t <- child_ex1_data %>%
-  mutate(condition = "test",
-         experiment = "Experiment 5")%>%
-  group_by(experiment,condition,age_bin, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(age_bin) %>%
-  mutate(mean = mean(unlist(correct)),
-         df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(experiment,condition, mean, age_bin,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
-child_ex1_lm_data <- child_ex1_data%>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-# experiment 2
-child_ex2t <- child_ex2_data %>%
-  mutate(condition = ifelse(condition == "same_speaker", "test", "control"),
-         experiment = "Experiment 6")%>%
-  group_by(experiment,condition,age_bin, id) %>%
-  summarise(correct = mean(correct)) %>%
-  summarise(correct = list(correct)) %>%
-  group_by(condition,age_bin) %>%
-  mutate(mean = mean(unlist(correct)),
-         df= t.test(unlist(correct), mu = 0.5)$parameter,
-         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(experiment, condition, mean, age_bin,df,t_value,p_value)%>%
-  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
-child_chance <- 
-  bind_rows(
-    child_ex1t,
-    child_ex2t
-  )
-
-apa_table(
-  child_chance
-  , caption = "Comparison to chance in each condition of Experiment 5 and 6"
-  , note = "Proportion expected by chance = 0.5. Data aggregated within participant and conditon."
-  , escape = T
-)
-
-```
-
-Data for children was binned by year for the comparison to chance. As for adults, we used one sample t-tests for this analysis. Table \ref{tab:child_chance_comp} shows the results for Experiment 5.
-
-```{r}
-child_ex1_lm_data <- child_ex1_data%>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-# GLMM
-child_ex1_lm <- glmer(correct ~ age_num + (1 | id), 
-              data = child_ex1_lm_data, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-child_lm_ex1_r <- tidy(child_ex1_lm, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-
-```
-
-We fit a GLMM with the following structure to the trial by trial data with age as a continuous variable: `correct ~ age_num + (1|id)`.
-Results show that children became more likely to select the more informative object with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`.
-
-## Experiment 6
-
-```{r}
-child_ex2_lm_data <- child_ex2_data%>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (1 | agent), 
-              data = child_ex2_lm_data, family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-child_lm_ex2_r <- tidy(child_ex2_lm, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-```
-
-Comparison to chance within each condition of Experiment 6 is given in Table \ref{tab:child_chance_comp}.
-We fit a GLMM with the following structure to the data: `correct ~ age_num*condition + (condition|id) + (1|agent)`.
-The model output shows an effect of condition (same or different speaker) ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`).
-
-## Experiment 7
-
-```{r child_models, results = "asis"}
-child_ex3_lm_data <- child_ex3_data%>%
-  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))
-
-child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
-      + (speaker+alignment | id), 
-      family = "binomial",
-      data = child_ex3_lm_data,
-      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-child_lm_ex3_r <- tidy(child_ex3_lm, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))%>%
-    mutate(term = recode(term, 
-                       `(Intercept)` = "Intercept",
-                       age_num = "age",
-                       speakersame_speaker = "speaker",
-                       alignmentincongruent = "alignment",
-                       `age_num:speakersame_speaker` = "age * speaker",
-                       `age_num:alignmentincongruent` = "age * alignment",
-                       `speakersame_speaker:alignmentincongruent` = "speaker * alignment",
-                       `age_num:speakersame_speaker:alignmentincongruent` = "age * speaker * alignment"
-         ))
-
-apa_table(
-  child_lm_ex3_r
-  , caption = "GLMM output for Experiment 7"
-  , note = "Reference level: speaker - different speaker, alignment - congruent."
-  , escape = T
-)
-```
-
-To see if children differentiated between the different combinations of manipulations in Experiment 7, we fit the following GLMM to the data: `correct_inf ~ age_num*speaker*alignment+ (speaker+alignment|id)`.
-Model output is shown in Table \ref{tab:child_models}.
+```
+
+## Note on alternative approach
+
+In this model, we assume that the literal listener ($L_0$) is also sensitive to the prior manipulation.
+An alternative approach [used e.g.
+in @frank2012predicting] is to assume that $L_0$ has a uniform prior distribution over referents [.33, .33, .33].
+We also ran the entire analysis with this alternative approach and found no major changes in the results.
+In all cases, the pragmatics model outperformed the two alternative models, both for children as well as for adults.
+Interestingly, for adults but not for children, using a uniform prior $L_0$ yielded a lower estimate for the noise parameter in Experiment 3 and 4.
 

### 2019-09-03 papers/full_paper/manuscript.Rmd
migrate manuscript and complete SI

@@
 ---
-title             : "Predicting information integration in pragmatic word learning across development"
+title             : "Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+shorttitle        : "Pragmatic cue integration"
 
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
-    email         : "bohn@stanford.edu"
+    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
+    email         : "manuel.bohn@uni-leipzig.de"
   - name          : "Michael Henry Tessler"
@@
 
-author_note: |
-  MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
-749229.
-MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund.
-We thank Jacqueline Quirke and Sabina Zacco for help with the data collection.
-
 abstract: |
-  Language is used and learned in complex social settings.
-To infer what a speaker means, listeners have to go beyond the literal meaning of words and rely on pragmatic inferences.
-During language acquisition, the same processes can help children to learn the meaning of novel words.
-Yet, pragmatic inferences require balancing multiple sources of social information.
+  Language is learned in complex social settings where listeners must reconstruct speakers’ intentend meanings from context.
+To navigate this challenge, children can use contextual or pragmatic reasoning to learn the meaning of unfamiliar words.
+One important challenge for pragmatic reasoning is that it often requires integrating information about the current utterance with broader common ground built up over the course of an interaction.
 Here we study this integration process.
-We isolate two types of pragmatic inference and formalize how they should be integrated according to a Bayesian pragmatics model.
-We present a series of experiments with preschool children and adults that suggest that information integration is best described as a form of probabilistic inference.
+We isolate these two sources of pragmatic information and formalize both how they should be combined and how they might develop using a probabilistic model of conversational reasoning.
+We present a series of seven experiments with three- to five-year-old children and adults that suggest that these two information sources flexibly trade off with one another.
+A cue combination model accurately predicted empirical results for children and adults and provided a better fit compared with alternative models in which only one information source was considered.
+This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
 
@@
 bibliography      : ["library.bib"]
+
+csl               : pnas.csl
 
@@
 
-```{r}
-# preparing datafiles (delete eventually)
-
-# d <- read_csv(file="../../stats/data/inf.data.csv") %>%
-#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
-#          trial = alltrial -2,
-#          experiment = "adult_ex1",
-#          condition = ifelse(control == TRUE, "control", "test") )%>%
-#   filter(trial_type == "test")%>%
-#   select(experiment, id,  trial,condition, agent, correct)
-# 
-# write_csv(d , path="../../stats/data/adult_ex1.csv")
-# 
-# d <- read_csv(file="../../stats/data/novel.data.csv") %>%
-#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
-#          experiment = "adult_ex2_novelty",
-#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
-#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
-#   filter(trial != "train")%>%
-#   select(experiment, id, trial,speaker, agent, correct)
-# 
-# write_csv(d , path="../../stats/data/adult_ex2_novelty.csv")
-# 
-# d <- read_csv(file="../../stats/data/pref.data.csv") %>%
-#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
-#          experiment = "adult_ex2_preference",
-#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
-#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
-#   filter(trial != "train")%>%
-#   select(experiment, id, trial,speaker, agent, correct)
-# 
-# write_csv(d , path="../../stats/data/adult_ex2_preference.csv")
-# 
-# d <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
-#                read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
-#   distinct(id, alltrial, .keep_all = TRUE) %>%
-#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
-# 
-# exclude <- d %>%
-#   filter(trial_type == "train") %>%
-#   group_by(id)%>%
-#   summarise(correct_inf = mean(correct_inf)) %>%
-#   filter(correct_inf == 0)
-# 
-# d <- d%>%
-#   filter(!id %in% exclude$id)%>%
-#   mutate(agent = ifelse( change == "same", agent, altAgent),
-#          common_ground_manipulation = ifelse(experiment == "novel_inf","novelty", "preference"),
-#          experiment = "adult_ex3",
-#          trial = alltrial -2,
-#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"))%>%
-#   filter(trial_type == "test")%>%
-#   select(experiment, id,trial, common_ground_manipulation, speaker ,alignment, agent, correct_inf)
-# 
-# write_csv(d , path="../../stats/data/adult_ex3.csv")
-# 
-# 
-#
-# d <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
-#                read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
-#                read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
-#                read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
-#                read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
-#                ) %>%
-#   distinct(id, alltrial, .keep_all = TRUE) %>%
-#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
-#          
-# exclude <- d %>%
-#   filter(trial_type == "train") %>%
-#   group_by(id)%>%
-#   summarise(correct_inf = mean(correct_inf)) %>%
-#   filter(correct_inf == 0)
-# 
-# d <- d%>%
-#   filter(!id %in% exclude$id)%>%
-#   mutate(agent = ifelse( change == "same", agent, altAgent),
-#          common_ground_manipulation = ifelse(grepl("novel",experiment),"novelty", "preference"),
-#          trial = alltrial -2,
-#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"),
-#          prior_manipulation = prior,
-#          experiment = "adult_ex4")%>%
-#   filter(trial_type == "test")%>%
-#   select(experiment, id,trial, common_ground_manipulation, prior_manipulation, speaker, alignment, agent, correct_inf)
-# 
-# write_csv(d , path="../../stats/data/adult_ex4.csv")
-#
-# 
-# d <- bind_rows(read_csv(file="../../stats/data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
-#                        read_csv(file="../../stats/data/kids_pref_2_data.csv")%>% mutate(age = subage))%>%
-#   filter(trial != "train")%>%
-#   mutate(age_bin = factor(age),
-#          experiment = "child_ex2",
-#          condition = ifelse(speakerChange == F, "same_speaker", "different_speaker"),
-#          agent = ifelse( speakerChange == F, agent, altAgent),
-#          id = subid,
-#          minage = min(age_num))%>%
-#   filter(trial != "train")%>%
-#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)
-# 
-# write_csv(d , path="../../stats/data/child_ex2.csv")
-# 
-# d <- bind_rows(
-#   read_csv(file="../../stats/data/kids_inf_data.csv"),
-#   read_csv(file="../../stats/data/kids_inf_2_data.csv"))%>%
-#   filter(subage != "2",
-#          trial != "filler1",
-#          trial != "filler2")%>%
-#   mutate(age_bin = factor(subage),
-#          experiment = "child_ex1",
-#          id =subid,
-#          minage = min(age_num))%>%
-#   select(experiment,id,age_bin,age_num,sex,minage,trial,correct)
-# 
-# write_csv(d , path="../../stats/data/child_ex1.csv")
-#
-# d <- read_csv(file="../../stats/data/kids_ex3_data.csv")%>%
-#   mutate(experiment = "child_ex3",
-#          id = subid,
-#          age_bin = subage,
-#          speaker = Speaker,
-#          alignment = Alignment,
-#          minage = min(age_num))%>%
-#   filter(trial != "filler1",trial != "filler2")%>%
-#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)
-# 
-#  write_csv(d , path="../../stats/data/child_ex3.csv")
-
-```
-
 ```{r data}
@@
 
+# Significance statement
+
+In order to learn the meaning of a new word, children need to integrate multiple sources of information.
+Some information is provided by the utterance itself, but other contextual information accumulates over the course of a conversation and is stored in common ground.
+To understand how these sources are integrated with one another and how they might develop, we formalize this process using computational models of pragmatic reasoning.
+These models make quantitative predictions for different hypotheses about how integration proceeds.
+Across seven experiments, we find that the way in which preschoolers and adults integrate information is best described by a model that flexibly trades off between different sources of information.
+Taken together, this work presents an explicit theory of socially grounded language learning.
+
 # Introduction
 
-Language use and language learning require integrating and balancing different sources of information.
-And even though linguistic cues, such as conventional syntax and semantics, may provide strong evidence about the intended meaning of an utterance, additional pragmatic inferences are necessary arrive at a precise interpretation [@levinson2000presumptive; @sperber2001relevance].
-A second route to meaning is even more important in the process of language learning.
-In this case, inferences based on the social embedding of the utterance are key to understanding its meaning and learning the words contained therein [@clark2009first; @tomasello2009constructing].
-In this paper, we explore how different forms of social information are integrated during word learning across development.
-More specifically, we look at information integration as a form of probabilistic inference.
+What someone means by an utterance is oftentimes not reducible to the words they used.
+It takes  pragmatic inference – context-sensitive reasoning about the speaker’s intentions - to recover the intended meaning [@grice1991studies, @levinson2000presumptive, @sperber2001relevance].
+Contextual information comes in many forms.
+On the one hand, there is information provided by the utterance\footnote{We use the terms utterance, utterance-level information or utterance-level cues to capture all cues that the speaker provides for their intended meaning.
+This includes direct referential information in the form of actions such as pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.} itself.
+Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative.
+Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies, @clark1996using, @sperber2001relevance, @tomasello2008origins].
+On the other hand, there is information provided by common ground (the body of knowledge and beliefs shared between interlocutors; [@bohn2018common, @clark1996using, @clark2015common].
+Because utterances are embedded in a broader (ongoing) social interaction, common ground information serves as a background against which new utterances are interpreted, making some meanings for ambiguous terms more likely than others.
 
-Pragmatic inferences rest on assumptions about how communication *should* proceed.
-Interlocutors mutually expect each other to communicate in a cooperative way and this mutual expectation serves as the basis for inferences that go beyond the literal meaning of an utterance [@grice1991studies; @sperber2001relevance; @tomasello2008origins].
-Paul Grice [-@grice1991studies] famously summarized this notion in his *Cooperative Principle*, which reads: “Make your contribution such as is required, at the stage at which it occurs, by the accepted purpose or direction of the talk exchange in which you are engaged.” Two sets of expectations follow from this principle.
-On the one hand, there is the general expectation that one follows the principle and communicates in a relevant and informative way.
-On the other hand, there is the expectation that communication is further specific to the communicative partner, that is, that it is adjusted to the the common ground shared between speaker and listener [@bohn2018common; @clark1996using].
+Children learning their first language make inferences about intended meanings based on utterance-level and common-ground information both for language understanding and language learning [@bohn2019pervasive, @clark2009first, @tomasello2008origins].
+Starting very early, infants expect adults to produce utterances in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve].
+By age two, children are sensitive to the informativeness of communication [@o2001two].
+By age three children can use this expectation to make pragmatic inferences [@stiller2015ad, @yoon2019role] and to infer novel word meanings [@frank2014inferring].
+And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children, @horowitz2018trouble, @barner2011accessing].
+Thus, children’s ability to reason about utterance-level pragmatics is present at least by ages three to five, and possibly substantially younger.
 
-Importantly, these expectations can also support language development [@clark2009first; @tomasello2009constructing].
-Starting in infancy, children generally expect adults' communicative acts to provide them with relevant information [e.g @behne2005one].
-And preschool children learn novel words by assuming that speakers are informative [@frank2014inferring].
-In the absence of any additional information about the potential referent objects or the speaker, children expected a novel word to be intended to refer to an object it describes in a unique way [see also @stiller2015ad].
-Person specific common ground information supports communication in infancy [e.g.
-@bohn2018social; @saylor2011s] and facilitates word learning in slightly older children.
-For example, two-year-olds keep track of which object is new to a speaker to decide which object the speaker is referring to when they use a novel word [@akhtar1996role; @diesendruck2004two].
-Furthermore, when three to five year old children learn about a speaker's preference, they later use this information to identify the meaning of an unknown word coming from the same speaker [@saylor2009preschoolers].
-These studies suggest early emerging pragmatic competences.
-Yet, communicative interactions in naturalistic contexts have multiple layers and require balancing expectations [@clark1996using].
-So how are different expectations integrated?
+Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social, @saylor2011s].
+For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role, @diesendruck2004two, @saylor2009preschoolers, @sullivan2019discourse].
 
-The Rational Speech Act (RSA) framework [@frank2012predicting; @goodman2016pragmatic] offers a formal framework for addressing this integration problem.
-RSA models are characterized by their recursive structure.
-Each agent in the recursion is modeled as a Bayesian reasoner; thus, information integration is treated as a process of probabilistic inference.
-The expectation that speakers communicate informatively is already encoded in the structure of the model: Speakers choose utterances that help listeners in disambiguating referents.
-Common ground information can be integrated in the model as a shared prior probability of referents in the context of the utterance.
-Thus, a natural locus for information integration within RSA models is the trade off between the prior probability of a referent and the likelihood of that referent given the current utterance.
+All of these examples, however, highlight children’s use of a single pragmatic information source or cue.
+Harnessing multiple – potentially competing – cues poses a separate challenge.
+One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance.
+Much less is known about whether and how children – or even adults – combine these types of information.
+While many theories of pragmatic reasoning presuppose that both information sources are integrated, the nature of their relationship has typically not been specified.
+We address this challenge here.
 
-Here we apply this rational, pragmatic account of communication to the study of information integration during word learning.
-We do so from a developmental perspective and include children, continuously sampled between three and five years of age, as well as adults.
-For both groups, we first test speaker-specific and common ground expectations independently.
-Based on this data, we generate model predictions about how expectations should be integrated.
-Finally, we compare these predictions to newly collected data and use model comparisons to test different hypothesis about how expectations are integrated.
+Recent innovations in probabilistic models of pragmatic reasoning provide a quantitative method for addressing the problem of integrating multiple sources of contextual information.
+This class of computational models, which are referred to as Rational Speech Act (RSA) models [@frank2012predicting, @goodman2016pragmatic] formalize the problem of language understanding as a special case of Bayesian social reasoning.
+A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative.
+Being informative is defined as providing a message that would increase the probability of the listener recovering the speaker’s intended meaning in context.
+This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener, and provides a first approximation to what we have described above as utterance-level pragmatic information.
+
+Listeners and speakers also enter into a conversation with assumptions about what is likely to be talked about, a reflection of the common ground shared between them.
+RSA models capture common ground information as a shared prior distribution over possible intended meanings.
+Thus, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade off between the prior probability of a meaning and the informativeness of the utterance.
+This trade off between contextual factors during word learning is a unique aspect of the word learning problem that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic, @frank2009using] or describing generalizations about word meaning [@xu2007word].
+
+We make use of this framework to study pragmatic cue integration across development.
+To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans] predictions about conditions in which they either coincide or conflict.
+
+We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (Experiment 1).
+In separate experiments, we then show that adults make inferences based on common ground information (Experiment 2A and 2B).
+We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance and common ground information should be integrated.
+We consider three models that make different assumptions about the integration process: In the pragmatics model, the two information sources are integrated with one another; according to the flat prior model, participants focus only on the utterance information and in the prior only model, only common ground information is considered.
+We compare predictions from these models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).
+
+After successfully validating this approach with adults, we apply the same model-driven experimental procedure to children: We first show that they make pragmatic inferences based on utterance and common ground information separately (Experiment 5 and 6).
+Then we generate a priori model predictions and compare them to data from an experiment – parallel to Experiment 3 – in which both information sources have to be integrated (Experiment 7).
+To our knowledge, the strategy of independently estimating model parameters with separate groups and combining them via the model to make preregistered quantitative predictions about a new population has not been used before with children.
+
+Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level (Gricean) and common-ground information flexibly.
+Second, it uses Bayesian data analysis within the RSA framework to provide a model for understanding the multiple loci for developmental change in complex behaviors like contextual communication.
 
@@
 Informativeness (Experiment 1, left) translated to making one object less frequent in context.
-Common ground (Experiment 2, middle) was manipulated by making one object prefered by or new to the speaker.
-Green plus signs represent utterances that expressed preference and red minus of dispreference (see main text for details).
+Common ground (Experiment 2, middle) was manipulated by making one object preferred by or new to the speaker.
+Green plus signs represent utterances that expressed preference and red minus signs represent utterances that expressed dispreference (see main text for details).
 Experiment 3 (right) combined manipulations.
-When expressing e.g.
-preference for an object on a table with two objects (panel 3 from top), the respective object was temporarily enlarged.
-Condition for Experiment 3 shown here: preference - same speaker - incongruent.", out.width="450px"}
+One condition of Experiment 3 is shown here: preference - same speaker - incongruent.", out.width="450px"}
 knitr::include_graphics("./figures/fig1.png")
@@
 
-# Adults
+# How do adults integrate contextual sources of information?
 
-## Assessment of general and speaker specific expectations (Experiment 1 and 2)
-
-As a first step, we assessed whether adults make general and common ground inferences when tested separately.
-In experiment 1, participants could infer which object a novel word referred to by assuming that the speaker communicated in an informative way.
-The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig.
-1A).
-When the speaker turned to the table with the two objects (A and B) and used an novel word to request one of them, participants could infer that the word referred to object B.
-This follows from the counter-factual inferences that, if the (informative) speaker would have wanted to refer to object A, they would have turned to the table with the single object, because this would have been the least ambiguous way to refer to this object.
-As a consequence, turning to the table with two objects most likely reflects an intention to refer to object B.
-In the control condition, both tables contained both objects and no inference could be made based on the speaker's behavior.
-
-```{r fig2, include = T, fig.align = "center", fig.cap = "Results from experiment 1 and 2 for adults.
-For preference and novelty, control refers to a different speaker (see Fig.
-1B).
-Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="250px"}
-knitr::include_graphics("./figures/fig2.png")
-```
+## Inferences based on utterance and common ground information  (Experiments 1 and 2)
 
@@
 lm_ex1 <- glmer(correct ~ condition +
-              (1 |id) , 
+              (1 |id), 
               data = adult_ex1_data, 
@@
 
-Participants made the inference consistent with the assumption that the speaker communicated informatively: They selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, see Fig.
-2) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
-
+In Experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
+The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig.
+1A).
+When the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them, participants could infer that the word referred to object B.
+This follows from the counter-factual inferences that, if the (informative) speaker had wanted to refer to object A, they would have pointed to the table with the single object (this being the least ambiguous way to refer to that object).
+In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior.
+Participants selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
 ```{r ex2-results}
@@
 
-In experiment 2, we tested if participants use common ground information that is specific to a speaker to infer the referent of a novel word.
-In the preference manipulation (Fig.
-1B .
-left), the speaker expressed preference for one of two objects.
-When the speaker later used a novel word to requested an object, participants could infer the referent by assuming that the speaker was talking about the object they liked.
-In a control condition, a different speaker, whose preferences were unknown, made the request.
-Adults selected the preferred object above chance when the same speaker made the request (t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig.
-2) and more so compared to when a different speaker asked for an object ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-
-In the novelty manipulation (Fig 1B - right), the speaker encountered one object on one of the tables.
+In Experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role, @saylor2009preschoolers].
+In Experiment 2A, the speaker expressed a preference for one of two objects (Fig.
+1B, left).
+Later, the speaker used a novel word to request an object.
+Adults selected the preferred object above chance (t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`) and more so than in a control condition, where a different speaker, whose preferences were unknown, made the request ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+In Experiment 2B, common ground information came in the form of novelty (Fig 1B, right).
+First, the speaker encountered one object on one of the tables.
 Later, a second object appeared.
-The second object was therefore new to the speaker.
-When the same speaker later used a novel word to requested an object (in a slightly excited way), participants could infer that it was the new object they are referring to.
-In contrast, when a different speaker, to whom both objects were equally new, made a request, no inference could be made based on the speaker's state of knowledge.
-In line with this reasoning, participants selected the new object above chance with the same speaker (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, see Fig.
-2), and more often compared to the different speaker ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-Taken together, experiment 1 and 2 showed that adults use general and speaker specific expectations to identify the referent of a novel word.
-In the following, we studied how these expectations are integrated when combined experimentally.
+When the same speaker then used a novel word to request an object, participants selected the new object above chance (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`), and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+Taken together, Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
 
@@
 
-We modeled the integration of general and common ground expectations as a process of probabilistic inference.
-We used the results of experiment 1 and 2 to inform key parameters in the model's architecture.
-Within the RSA framework, general expectations that speakers (or listeners) communicate in a cooperative and informative way are reflected in the model's recursive structure.
-When interpreting an utterance, the hypothetical listener imagines that it was generated by a pragmatic speaker whose goal is to produce the most informative utterance.
-The pragmatic speaker is modeled as reasoning about what the most informative utterance would be for a naive listener, who does not know the novel words.
-Importantly, the utterance in this case includes not just the novel word but also the turning to one of the tables.
-The conditional probability that the listener interprets an utterance as referring to a particular referent is defined as:
+We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of Experiments 1 and 2 to inform key parameters of a computational model.
+The Rational Speech Act (RSA) model architecture introduced by [@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
+The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents P(r) - with his generative model of how the utterance was produced: a speaker trying to convey information to him.
+To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) - a prior distribution over lexica P(L) [@bergen2016pragmatic].
 
-$$P_L(r_s|u)\propto P_S(u|r_s)P_S(r_s)$$
+$$P_{L}(r, \mathcal{L}|u)\propto P_{S}(u|r, \mathcal{L}) \cdot P( \mathcal{L}) \cdot P(r)$$
 
-Here, the term $P_S(u|r_s)$ denotes the likelihood that the pragmatic speaker will produce a particular utterance $u$ to refer to a referent $r$.
-It is defined in terms of a utility function $U_S(u;s)$ consisting of the surprisal of $u$ for a naive listener, who interprets $u$ according its literal semantics:
+In the above equation, the listener is trying to jointly resolve the speaker’s intended referent r and the meaning of words (thus learning the lexicon $\mathcal{L}$).
+He does this by imagining what a rational speaker would say, given the referent they are trying to communicate and a lexicon.
+The speaker is an approximately rational Bayesian actor (with degree of rationality alpha), who produces utterances as a function of their informativity.
+The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see SI Appendix for details):
 
-$$P_S(u|r_s)\propto exp(\alpha U_S(u;s))$$
+$$P_{S}(u|r,\mathcal{L})\propto Informativity(u;r)^\alpha \cdot P(u|\mathcal{L})$$
 
-This utility is maximized in order to decide which utterance to use to communicate about a particular referent, reflecting the expectation that the speaker communicates in an informative way.
-The absolute strength of $P_S(u|r_s)$ depends on a scalar value, $\alpha$, which can be interpreted as an indicator of how rational the speaker is in choosing utterances (i.e.
-as $\alpha$ increases, the speaker is more likely to choose the most informative utterance).
-We used the data from experiment 1 to specify how rational participants thought speakers were in the current setup.
-That is, we inferred which value of $\alpha$ would generate model predictions (assuming equal prior probability for each object) that corresponded to the average proportion of correct responses measured in experiment 1.
+The informativity of an utterance for a referent is taken to be the probability with which a naive listener, who only interprets utterances according to their literal semantics, would select a particular referent given an utterance.
 
-We treated common ground expectations as changes in the prior probability that a particular referent is being referred to ($P_S(r_s)$ in the first equation).
-For example, if the speaker expresses preference for object A, and the same speaker later requests an object, then A has a higher probability of being the referent of a subsequent utterance, regardless of any additional pragmatic considerations.
-We used the proportions measured in experiment 2 to specify the probability distribution across referents for the different common ground manipulations (novelty or preference, same or different speaker).
+$$Informativity(u; r) = P(r|u) \propto P(r) \cdot \mathcal{L}_{point}$$
 
-With $\alpha$ and $P_S(r_s)$ fixed based on experiment 1 and 2, we generated model predictions for situations in which general and common ground expectations had to be integrated (Fig.
-1C).
-Expectations could either be congruent or incongruent.
-If, for example, object A was the more informative object (unique to that table) and also the one the speaker expressed preference for, expectations were congruent.
-Next, the speaker who made the request could either be the same as the one in the previous interaction or a different one.
-Finally, common ground information could be manipulated in the form of preference or novelty.
-This resulted in a total of 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions for which we generated model predictions.
-In order to capture that behavioral data is to some extend noisy, all models included a noise parameter.
-Noise parameters ranged between 0 and 1 and reflect the proportion of responses that are estimated (based on the data) to be random instead of in line with model predictions.
+The speaker’s possible utterances are pairs of linguistic and non-linguistic signals, namely labels and points.
+Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point.
+Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see SI Appendix for modeling details).
+
+This computational model provides a natural avenue to formalize quantitatively how informativeness and common ground trade-off during word learning.
+As mentioned above, the common ground shared between speaker and listener plays the role of the listener’s prior distribution over meanings, or types of referents, that the speaker might be referring to and which we posit depends on prior interactions around the referents in the present context (e.g., preference or novelty; Experiment 2A and B).
+We use the results from Experiment 2 to specify this distribution.
+The in-the-moment, contextual informativeness of the utterance is captured in the likelihood term, whose value depends on the rationality parameter $\alpha$.
+Assumptions about rationality may change depending on context and we therefore used the data from Experiment 1 to specify $\alpha$ (see SI Appendix for details about these parameters).
+
+The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig.
+1C - see SI Appendix for additional details and a worked example of how predictions were generated).
+In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter to account for responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (Experiment 3).
 Including the noise parameter greatly improved the model fit to the data (see SI Appendix for details).
-We did not preregister the inclusion of a noise parameter for experiment 3 but did so for all subsequent experiments.
-
+We did not pre-register the inclusion of a noise parameter for Experiment 3 but did so for all subsequent experiments.
 ```{r ex3 GLMM, cache=F}
@@
 
-```
-
-In experiment 3, we collected new behavioral data for each of the eight conditions.
-Experimentally, we combined the procedures of experiment 1 and 2.
-The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig.
-1C).
-We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only general expectations are considered).
-Before comparing responses to model predictions we fit a generalized linear mixed model (GLMM) to the data to test if participant's responses varied across conditions.
-Participants distinguished between congruent and incongruent trials when the speaker remained the same (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
-
-```{r fig3, include = T, fig.align = "center", fig.cap = "Results from experiment 3 and 4 for adults.
-Data and model predictions by condition for experiment 3 (A).
-Transparent dots show data from individual participants, diamonds represent condition means.
-Corrrelation between model predictions and data in experiment 3 (B), between data in experiment 3 and data for the strong prior manipulation in experiment 4 (direct replication - C) and between model predictions and data in experiment 4 (D).
-Coefficients and p-values are based on Pearson correlation statistics.
-Error bars represent 95\\% HDIs.", out.width="450px"}
-knitr::include_graphics("./figures/fig3.png")
 ```
@@
 
-Model predictions were highly correlated with the average response in each condition (Fig.
-3A and B).
-We compared the fit of the pragmatics model described above to two alternative models: the *flat prior* model ignored the speaker specific expectation and the *prior only* model ignored the informativeness inference.
-This analysis tests whether the trade-off between expectations in the pragmatics model captured the structure in the data better compared to models that assume that participants only consider one type of expectation at a time.
-Model fit was much better for the pragmatic compared to the flat prior (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both types of expectations.
-The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)` ).
-This value was considerably lower for the pragmatics model, compared to the alternative models (see SI Appendix), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
+In Experiment 3, we combined the procedures of Experiment 1 and 2A or 2B.
+The test setup was identical to Experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig.
+1C).
+We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).
+Participants distinguished between congruent and incongruent trials when the speaker remained the same, as evidenced by the fit of a generalized linear mixed effects model (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
 
-## Replication and extension to different levels of speaker specific expectation (Experiment 4).
+Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig.
+2A).
+To test whether participants in fact balanced both information sources, we compared the pragmatics model to two alternative models: the *flat prior model*, which ignores common ground information and the *prior only model*, which ignores utterance information.
+Model fit was considerably better for the pragmatics model compared to the flat prior model (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
+The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
+This value was substantially lower for the pragmatics model compared to the alternative models (see SI Appendix), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
+Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.
 
-The goal of experiment 4 was twofold: First, to replicate the results of experiment 3 and second, to test the generalizability of the pragmatics model to a larger range of conditions.
-Compared to experiment 3, we manipulated the strength of the common ground expectations.
-For both, preference and novelty, we planned to have a strong, a medium and a weak manipulation.
-Expectation strength was manipulated by changing the way the speaker interacted with the objects prior to the request and measured as the proportion with which participants chose the preferred/novel object in the same speaker condition (see SI Appendix for results).
-For novelty, we succeeded in finding three qualitatively different manipulations.
-For preference, we piloted a number of manipulations but did not find a way to indicate only weak preference.
-Experiment 4 therefore included strong and medium manipulations for novelty and preference and a weak manipulation for novelty.
-The general expectation was the same as in experiment 3.
-For each level we crossed general and common ground expectations in the same way as in experiment 3, resulting in a total of 8 (strong) + 8 (medium) + 4 (weak) = 20 conditions.
-The strong manipulation was a direct replication of experiment 3.
-Model predictions were generated in the same way as in experiment 3.
-
-```{r ex4 GLMMs, cache=F}
-# strong
-
-lm_ex4_strong <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (speaker+alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "strong"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_strong)
-
-lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-
-lm_ex4_medium <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "medium"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_medium)
-
-lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-
-lm_ex4_weak <- glmer(correct_inf ~ speaker*alignment + (speaker+alignment|id), 
-              data = adult_ex4_data %>% filter(prior_manipulation == "weak"), family = binomial, 
-              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
-
-#summary(lm_ex4_weak)
-
-lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
-  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
-         std.error = round(std.error,2),
-         estimate = round(estimate,2))
-
+```{r fig2, include = T, fig.align = "center", fig.cap = "Correlation between model predictions and data.
+(A) Experiment 3, (B) Experiment 4, (C) 3-year-olds in Experiment 7 and (D) 4-year-olds in Experiment 7.
+Coefficients and p-values are based on Pearson correlation statistics.
+Error bars represent  95\\% HDIs.", out.width="450px"}
+knitr::include_graphics("./figures/fig2.png")
 ```
 
-Again, before evaluating model predictions, we fit GLMMs to the data for each level of common ground manipulation.
-Participants distinguished between congruent and incongruent trials when the speaker remained the same for the strong ($\beta$ = `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_strong%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`)\footnote{Here, this effect differed between novelty and preference: model term manipulation x alignment x speaker; $\beta$ = `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, p `r lm_ex4_r_strong%>%filter(term == "common_ground_manipulationpreference:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`} and medium ($\beta$ = `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_medium%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`), but not the weak manipulation ($\beta$ = `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex4_r_weak%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`, model term: `alignment x speaker` in all cases).
-This pattern validates our manipulations.
-If the speaker specific manipulation is weak, changing the speaker has no differential impact on the informativeness inference.
-Results from the strong manipulation in experiment 4 further replicated findings from experiment 3 (Fig.
-3C).
+## Replication and extension to different levels of common ground information (Experiment 4).
 
@@
   select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)
-
 ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
@@
 
+To test if our model makes accurate predictions for different combinations, we first replicated and then extended the results of Experiment 3 to a broader range of experimental conditions.
+Specifically, we manipulated the strength of the common ground information (strong, medium and weak manipulation) by changing  the way the speaker interacted with the objects prior to the request We ran a total of 20 conditions, including a direct replication of Experiment 3 (see SI Appendix for details).
+
 Model predictions from the pragmatics model were again highly correlated with the average response in each condition (Fig.
-3D).
-We evaluated model fit for the same models as in experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was again lower compared to the alternative models (see SI Appendix).
+2B).
+We evaluated model fit for the same models as in Experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
+The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to Experiment 3 and again lower compared to the alternative models (see SI Appendix).
 
-Summarizing experiment 3 and 4, we saw that adults flexibly integrated different expectations about a speaker in a word learning scenario.
-This process was best described by a model that treated information integration as a form of probabilistic inference.
-Next, we took a developmental perspective and studied if the same model could be used to describe children's word learning.
+# Do children integrate contextual information?
 
-# Children
+The previous section showed that competent language users flexibly integrate information during pragmatic word learning.
+Do children make use of multiple information sources during word learning as well?
+When does this integration emerge developmentally?
+While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described in detail nor tested.
+Here we provide an explanation in the form of our pragmatics model and test if it is able to capture children’s word learning.
+Embedded in the assumptions of the model is the idea that developmental change is change in the strength of the individual inferences, leading to a change in the strength of the integrated inference.
+As a starting point, our model assumes developmental continuity in the integration process itself, though this assumption could be called into question by a poor model fit.
 
-## Assessment of general and speaker specific expectations (Experiment 1 and 2)
+## Inferences based on utterance and common ground information (Experiment 5 and 6)
 
-We approached children's word learning in the same way as adults'.
-First, we measured the strength of general (informativeness) and common ground (preference) expectations and used these measurements to set model parameters.
-Then we generated model predictions for how expectations should be integrated.
-Finally, we compared model predictions to new behavioral data.
-In this, we took a truly developmental perspective.
-We sampled children continuously across the entire age range and generated model predictions for the average developmental trajectory in each condition.
-In all the following experiments, we tested children between 3.0 and 4.9 years of age.
-For experiment 1 and 2, we also tested two-year-olds but did not find sufficient evidence that they make general and/or common ground inferences in the tasks we used.
+The study for children followed the same general pattern as the one for adults.
+We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance (informativeness) and common ground (preference) information in isolation when making pragmatic inferences.
+We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive, frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition\footnote{For Experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.}.
 
@@
 
-summary(child_ex1_lm)
+#summary(child_ex1_lm)
 
@@
 
-child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (condition*age_num | agent), 
+child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (1 | agent), 
               data = child_ex2_lm_data, family = binomial, 
@@
 
-Children were only tested in the test condition in experiment 1.
-To compare children's performance to chance level, we binned age by year.
+Experiment 5 was analogous to Experiment 1 for adults.
+To compare children’s performance to chance level, we binned age by year.
 Four-year-olds selected the more informative object (i.e.
@@
 Three-year-olds, on the other hand, did not (t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`).
-Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig.
-4).
-Thus, children's expectation that speakers communicate in an informative way increased with age.
+Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`).
+Thus, children’s ability to use utterance information in a word learning context increased with age.
 
-In experiment 2, we assessed whether children use common ground information to identify the referent of a novel word.
+In Experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
 We tested children with the novelty as well as the preference manipulation but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
-We therefore dropped this manipulation and focused on preference for the remainder of the study.
-
-```{r fig4, include = T, fig.align = "center", fig.cap = "Results from experiment 1 and 2 for children For preference, control refers to to the different speaker condition (see Fig.
-1B).
-Transparent dots show data from individual participants, regression lines show fitted linear models with 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="250px"}
-knitr::include_graphics("./figures/fig4.png")
-```
+Since our focus was on how children selectively integrate the two sources of information, we therefore dropped this manipulation and focused on preference for the remainder of the study.
 
 For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`), whereas three-year-olds did not (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`).
-However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, Fig.
-4).
+However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`4).
 Thus, children across the age range used common ground information to infer the referent of a novel word.
 
-## Model predictions for information integration evaluated against new data (Experiment 3)
+## Developmental model predictions evaluated against new data (Experiment 7)
 
-We used the measurements from experiment 1 and 2 to specify $\alpha$ and $P_S(r_s)$ in the pragmatics model.
-However, instead of setting these parameters to a single value, we used the data to infer the intercept and slope that best described the developmental trajectory for each parameter.
-For $P_S(r_s)$, this was done separately for the same speaker and the different speaker condition (see SI Appendix for details).
+We used the measurements from Experiment 5 and 6 to specify the strength of informativity, $\alpha$, and common ground in the pragmatics model.
+Instead of inferring a single value we inferred the intercept and slope for each parameter that best described the developmental trajectory in the data of Experiment 5 and 6.
 These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions.
@@
 
-In experiment 3, we combined the procedures of experiment 1 and 2 and collected new data from children between 3.0 and 4.9 years of age in each of the four conditions (Fig.
+In Experiment 7, we combined the procedures of Experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig.
 1C).
-Before comparing the data to model predictions, we fit a GLMM to the data to test if children distinguished between conditions.
-Children's propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
-
-```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 3 for children.
-Purple lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants (A).
-Correlation between model predictions and condition means binned by year (B).
-Coefficent and p-value are based on Pearson correlation statistic.
-Error bars represent 95\\% HDIs.", out.width="450px"}
-knitr::include_graphics("./figures/fig5.png")
-```
+Children’s propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
 
@@
 
-Next, we evaluated the model predictions (Fig 5A).
+Our modeling results suggest that children flexibly integrate both common ground and informativity information, and that this integration process is accurately captured by the pragmatics model at least for four-year-olds.
 For the correlational analysis, we binned model predictions and data by year.
-There was a substantial correlation between the predicted and measured average response in each age bin (Fig.
-5B).
+There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig.
+2C and D).
+One of the reasons for the latter was the low variation between conditions.
 For the model comparison, we treated age continuously.
-As for adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (see SI Appendix).
-The high level of inferred noise moved the model predictions in all conditions close to chance level (Fig.
-5A).
-We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more.
-This analysis was not preregistered.
+As with adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see SI Appendix).
+
+The high level of inferred noise moved the model predictions for children in all conditions close to chance level.
+We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see SI Appendix).
+This analysis was not pre-registered.
 Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age.
 In each case, the pragmatics model provided a better fit compared to the alternative models (flat prior: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; prior only: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-Taken together, these results suggest that children's word learning is best described as a flexible integration of general and common ground expectations.
 
@@
 
-Integrating different sources of information is an integral part of human communication.
-To infer the intended meaning of an utterance, listeners combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
-When learning new words, social information is especially vital.
-But how are different social expectations integrated during word learning?
-Here we explored the hypothesis that information integration is a process of probabilistic inference.
-We studied how expectations that speakers communicate in an informative way are contextualized by expectations that follow from prior interactions with the speaker.
-Across development, participants' learning was best predicted by a Bayesian pragmatics model in which expectations were flexibly traded-off between one another in a probabilistic way.
-Alternative models, which considered only one type of expectation, made worse predictions.
+Integrating multiple sources of information is an integral part of human communication [@tanenhaus1995integration].
+To infer the intended meaning of an utterance, listeners must combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
+This integration is especially vital in early language learning, and the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive].
+But how are different cues integrated during word learning?
+Here we used a Bayesian pragmatics model to formalize this integration process.
+We studied how utterance-level (Gricean expectations) about informative communication are integrated with common ground information that follows from prior interactions with the speaker.
+Adults’ and children’s learning was best predicted by a model in which both sources of information traded-off flexibly.
+Alternative models that considered only one source of information made substantially worse predictions.
 
-The pragmatics model goes beyond simply weighing expectations by some ratio.
-It offers an explicit account about how integration may proceed: Because all objects are new and their labels unknown, the initial probability of each object depends entirely on common ground information.
-Now, the listener assumes the speaker to produce their utterance based on the expected effect that their utterance will have *in light of* this shared common ground.
-Thus, inferences are not computed separately but the result of an integrated process.
-
-In the current model, common ground information was treated in the same way as contextual salience [see e.g.
-@frank2012predicting].
-Interacting around an object changed the probability that this object will be communicated about.
-In theory, similar changes could be brought about by increasing the object's perceptual salience.
-Future work could try to explicitly model the social-cognitive processes that gave rise to common ground expectations and contrast social and perceptual salience.
+All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing expectations by some ratio.
+We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data.
+That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli.
+Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning].
 
@@
 That is, while the degree to which listeners expect speakers to be informative or follow common ground changes with age, the process by which expectations are integrated remains the same.
-This is a very parsimonious conception of developmental change and others, in which the integration process itself changes with age, are also plausible and worth exploring.
+However, other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
+Our model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
+But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (Experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
 
-Studying how multiple types of social information are balanced contributes to a comprehensive and ecologically valid model of word learning.
-In the current study, participants inferred the referent by integrating non-linguistic cues (speakers turning and looking to one table) with assumptions about speaker informativeness and common ground information.
-However, the real learning environment is much richer than the what we captured in our experimental design.
-In addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to the meaning of the words embedded therein [@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
+Studying how multiple types of pragmatic cues are balanced contributes to a more comprehensive understanding of word learning.
+In the current study, participants inferred the referent by integrating non-linguistic cues (speakers pointing to a table) with assumptions about speaker informativeness and common ground information, going beyond previous experimental work in measuring how these information sources were combined.
+The real learning environment is far richer than what we captured in our experimental design, however.
+For example, in addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to meaning [@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
 Across development, children learn to recruit these different sources of information and integrate them.
-Our studies show how computational models of language use and comprehension can be used as powerful tools to explicate and test hypothesis about how integration proceeds.
+RSA models allow for the inclusion of semantic information as part of the utterance [@bergen2016pragmatic] and it will be a fruitful avenue for future research to model the integration of linguistic and pragmatic information across development.
+
+More broadly, our work here shows how computational models of language comprehension can be used as powerful tools to explicate and test hypotheses about information integration.
+Furthermore, we took a first step towards integrating developmental change into this theoretical framework.
 
@@
 Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9.
-Experiment 1 and each manipulation of experiment 2 had *N* = 40 participants.
-Sample size in experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
+Experiment 1 and each manipulation of Experiment 2 had N = 40 participants.
+Sample size in Experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
 *N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations.
@@
 
-Children were recruited from the floor of the Children's Discovery Museum in San Jose, California, USA.
+Children were recruited from the floor of the Children’s Discovery Museum in San Jose, California, USA.
 Parents gave informed consent and provided demographic information.
-We collected data from a total of 243 children between 3.0 and 4.9 years of age.
-We excluded 15 due to less than 75% of reported exposure to English, five because they responded incorrect on 2/2 training trials, three because of equipment malfunction and two because they quit before half of the test trials were completed.
-The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in experiment 1, *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in experiment 2 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in experiment 3.
+We collected data from a total of 243 children between 3.0 and 5.0 years of age.
+We excluded 15 children due to less than 75% of reported exposure to English, five because they responded incorrectly on 2/2 training trials, three because of equipment malfunction, and two because they quit before half of the test trials were completed.
+The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in Experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in Experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in Experiment 7.
 
-## Experimental procedures
+## Materials
 
@@
 Adults were directed to the website via MTurk and responded by clicking objects.
-Children were guided through the game by an experimenter and responded by touching objects on the screen.
+Children were guided through the game by an experimenter and responded by touching objects on the screen of an iPad tablet [@frank2016using].
 For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests.
-All studies started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball).
+All experiments started with an introduction to the animals and two training trials.
 Subsequent test trials in each condition were presented in a random order.
-
-The setup of experiment 1 for adults is shown in Fig.
-1A.
-In the beginning of each trial, the animal introduced themselves (e.g.
-“Hi, I’m Dog”) and then turned towards the table with the two objects.
-The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”).
-In the test condition, there was one object on the other table whereas in the control condition there were two.
-Participants received six trials, three per condition.
-
-The setup for experiment 2 is shown in Fig.
-1B.
-In the preference manipulation, the animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
-Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
-This procedure was the strong preference manipulation.
-In the medium version, the animal only expressed preference and did so in a more subtle way (simply saying: "Oh, wow").
-
-In the novelty manipulation one of the tables was initially empty.
-The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm..., nothing there”) of an object before turning to the other side and commenting in a complementary way.
-After shortly disappearing, the same animal repeated the sequence above.
-When the animal left a second time, a new object appeared on the empty table.
-Next, either the same or a different animal returned and requested an object.
-This corresponded to the strong manipulation.
-For the medium manipulation, the animal turned to each table only once before the new object appeared.
-In the weak manipulation, the animal only commented on the present object once and never turned to the empty table.
-Participants always received six trials, three with the same and three with the different speaker.
-
-For experiment 3 and 4 we inserted the common ground manipulation before the request in the setup of experiment 1 (Fig.
-1C).
-For example, the animal turned to the table with one object and express that they liked object A, then turned to the other table and express that they did not like object B.
-Next, after quickly disappearing, the animal reappeared, turned to the table with two objects and make a request.
-To make it clear, which of the objects the speaker commented on while being turned to the table with the two objects during the common ground manipulation, the object was temporarily enlarged.
-Participants completed eight trials for one of the common ground manipulations with two  trials per condition (same/different speaker x congruent/incongruent).
-
-Experiment 1 for children was modeled after @frank2014inferring.
-Instead of on tables, objects were presented as hanging in trees.
-After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
-Next, the trees and the objects in them disappeared and new trees replaced them.
-The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced).
-While facing straight, the animal first said "Here are some more trees" and then asked the child to pick the tree with the object that corresponded to the novel word ("Which of these trees has a [non-word]").
-Children received six trials in a single test condition.
-
-Experiment 2 for children was identical to the strong preference manipulation for adults. Children received eight trials, four with the same and four with a different animal returning.
-
-In experiment 3 for children, we again inserted the preference manipulation into the setup of experiment 1.
-After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
-Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
-Next, the animal disappeared and either the same or a different animal returned.
-The rest of the trial was identical to the label and request phase of experiment 1.
-Children received eight trials, two per condition (same/different speaker x congruent/incongruent).
+Detailed experimental procedures for each experiment can be found in the SI Appendix.
 
@@
 
-All analysis were run in R [@R-base].
-GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4].
+All analyses were run in R [@R-base].
+GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
 Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
-The flat prior model had the same structure as the pragmatics model but used a uniform prior over objects.
-The prior only model predicted choice based on the prior probability for each object alone.
-Bayes Factors for model comparisons are based on marginal likelihoods of each model given the data.
-The corresponding model code can be found in the associated online repository.
+Bayes Factors for model comparisons were based on marginal likelihoods of each model given the data.
+Details on models can be found in the supplementary information.
+
+# Acknowledgements
+
+MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
 

### 2019-09-03 papers/full_paper/models.Rmd
migrate manuscript and complete SI

@@
 
+```
+
+```{r}
+# preparing datafiles (delete eventually)
+
+# d <- read_csv(file="../../stats/data/inf.data.csv") %>%
+#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
+#          trial = alltrial -2,
+#          experiment = "adult_ex1",
+#          condition = ifelse(control == TRUE, "control", "test") )%>%
+#   filter(trial_type == "test")%>%
+#   select(experiment, id,  trial,condition, agent, correct)
+# 
+# write_csv(d , path="../../stats/data/adult_ex1.csv")
+# 
+# d <- read_csv(file="../../stats/data/novel.data.csv") %>%
+#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
+#          experiment = "adult_ex2_novelty",
+#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
+#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
+#   filter(trial != "train")%>%
+#   select(experiment, id, trial,speaker, agent, correct)
+# 
+# write_csv(d , path="../../stats/data/adult_ex2_novelty.csv")
+# 
+# d <- read_csv(file="../../stats/data/pref.data.csv") %>%
+#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
+#          experiment = "adult_ex2_preference",
+#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
+#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
+#   filter(trial != "train")%>%
+#   select(experiment, id, trial,speaker, agent, correct)
+# 
+# write_csv(d , path="../../stats/data/adult_ex2_preference.csv")
+# 
+# d <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
+#                read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
+#   distinct(id, alltrial, .keep_all = TRUE) %>%
+#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+# 
+# exclude <- d %>%
+#   filter(trial_type == "train") %>%
+#   group_by(id)%>%
+#   summarise(correct_inf = mean(correct_inf)) %>%
+#   filter(correct_inf == 0)
+# 
+# d <- d%>%
+#   filter(!id %in% exclude$id)%>%
+#   mutate(agent = ifelse( change == "same", agent, altAgent),
+#          common_ground_manipulation = ifelse(experiment == "novel_inf","novelty", "preference"),
+#          experiment = "adult_ex3",
+#          trial = alltrial -2,
+#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"))%>%
+#   filter(trial_type == "test")%>%
+#   select(experiment, id,trial, common_ground_manipulation, speaker ,alignment, agent, correct_inf)
+# 
+# write_csv(d , path="../../stats/data/adult_ex3.csv")
+# 
+# 
+#
+# d <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
+#                read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
+#                read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
+#                read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
+#                read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
+#                ) %>%
+#   distinct(id, alltrial, .keep_all = TRUE) %>%
+#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
+#          
+# exclude <- d %>%
+#   filter(trial_type == "train") %>%
+#   group_by(id)%>%
+#   summarise(correct_inf = mean(correct_inf)) %>%
+#   filter(correct_inf == 0)
+# 
+# d <- d%>%
+#   filter(!id %in% exclude$id)%>%
+#   mutate(agent = ifelse( change == "same", agent, altAgent),
+#          common_ground_manipulation = ifelse(grepl("novel",experiment),"novelty", "preference"),
+#          trial = alltrial -2,
+#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"),
+#          prior_manipulation = prior,
+#          experiment = "adult_ex4")%>%
+#   filter(trial_type == "test")%>%
+#   select(experiment, id,trial, common_ground_manipulation, prior_manipulation, speaker, alignment, agent, correct_inf)
+# 
+# write_csv(d , path="../../stats/data/adult_ex4.csv")
+#
+# 
+# d <- bind_rows(read_csv(file="../../stats/data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
+#                        read_csv(file="../../stats/data/kids_pref_2_data.csv")%>% mutate(age = subage))%>%
+#   filter(trial != "train")%>%
+#   mutate(age_bin = factor(age),
+#          experiment = "child_ex2",
+#          condition = ifelse(speakerChange == F, "same_speaker", "different_speaker"),
+#          agent = ifelse( speakerChange == F, agent, altAgent),
+#          id = subid,
+#          minage = min(age_num))%>%
+#   filter(trial != "train")%>%
+#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)
+# 
+# write_csv(d , path="../../stats/data/child_ex2.csv")
+# 
+# d <- bind_rows(
+#   read_csv(file="../../stats/data/kids_inf_data.csv"),
+#   read_csv(file="../../stats/data/kids_inf_2_data.csv"))%>%
+#   filter(subage != "2",
+#          trial != "filler1",
+#          trial != "filler2")%>%
+#   mutate(age_bin = factor(subage),
+#          experiment = "child_ex1",
+#          id =subid,
+#          minage = min(age_num))%>%
+#   select(experiment,id,age_bin,age_num,sex,minage,trial,correct)
+# 
+# write_csv(d , path="../../stats/data/child_ex1.csv")
+#
+# d <- read_csv(file="../../stats/data/kids_ex3_data.csv")%>%
+#   mutate(experiment = "child_ex3",
+#          id = subid,
+#          age_bin = subage,
+#          speaker = Speaker,
+#          alignment = Alignment,
+#          minage = min(age_num))%>%
+#   filter(trial != "filler1",trial != "filler2")%>%
+#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)
+# 
+#  write_csv(d , path="../../stats/data/child_ex3.csv")
 ```
@@
 adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
+```
+
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
 ```

### 2019-09-05 papers/full_paper/manuscript.Rmd
add test folder

@@
 These models make quantitative predictions for different hypotheses about how integration proceeds.
-Across seven experiments, we find that the way in which preschoolers and adults integrate information is best described by a model that flexibly trades off between different sources of information.
+We find that the way in which preschoolers and adults integrate information is best described by a model that flexibly trades off between different sources of information.
 Taken together, this work presents an explicit theory of socially grounded language learning.

### 2019-09-05 stats/adults/data_preprocessing.R
clean repo

@@ -1,128 +1,0 @@
-
-library(rjson)
-library(tidyr)
-library(stringr)
-library(dplyr)
-library(data.table)
-
-
-##
-setwd("~/Work/MCC/git-mcc/mcc/stats/")
-
-############################
-######## novelty ###########
-################################################################################################################
-
-
-# select all files from individual workers
-#files <- dir("~/Work/MCC/git-mcc/cosub_novelty/anonymized-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak2/production-results")
-#files <- dir("~/Work/MCC/git-mcc/nosub_novelty_weak2/sandbox-results")
-
-#combine files into one dataframe
-raw <- data.frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/nosub_novelty_weak2/production-results/",f,sep="")
-  jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(workerid = jd$WorkerId, 
-                   data = jd$answers$data$data
-)
-  raw <- bind_rows(raw, id)
-}
-
-# convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("id","alltrial","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,73,str_length(novel.data$pick)-4)
-novel.data = novel.data[!duplicated(novel.data), ]
-novel.data = novel.data[order(id)]
-#novel.data$id = paste(novel.data$id,novel.data$condition,sep="_")
-# check resulting datafile
-str(novel.data)
-head(novel.data)
-# write csv file for further analysis
-write.csv(novel.data, file="novel.weak.data2.csv")
-
-################################################################################################################
-
-
-############################
-######## preference ###########
-################################################################################################################
-
-#files <- dir("~/Work/MCC/git-mcc/cosub_preference/anonymized-results")
-#files <- dir("~/Work/MCC/git-mcc/nosub_preference_weak/production-results")
[…]

### 2019-09-05 stats/adults/data_preprocessing_Ex3.R

@@ -1,104 +1,0 @@
-
-library(rjson)
-library(tidyr)
-library(stringr)
-library(dplyr)
-library(data.table)
-library("stringr")
-
-
-##
-setwd("~/Work/MCC/git-mcc/mcc/stats/")
-
-############################
-######## novelty ###########
-################################################################################################################
-
-
-# select all files from individual workers
-#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/sandbox-results")
-#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/production-results")
-#files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_medium/production-results")
-files <- dir("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/production-results")
-
-
-#combine files into one dataframe
-raw <- data.frame()
-for (f in files) {
-  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/sandbox-results/",f,sep="")
-  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_strong/production-results/",f,sep="")
-  #jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_medium/production-results/",f,sep="")
-  jf <- paste("~/Work/MCC/git-mcc/nosub_Ex3_novel_weak/production-results/",f,sep="")
-  jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(workerid = jd$WorkerId, 
-                   data = jd$answers$data$data
-)
-  raw <- bind_rows(raw, id)
-}
-
-# convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.experiment","^data.agent","^data.altAgent","^data.rightFruit","^data.leftFruit","^data.corrFruit_inf","^data.corrFruit_novel","^data.pick","^data.novel","^data.inf","^data.trial","^data.alignment","^data.speaker","^data.rt", "^data.correct_inf","^data.correct_novel"))
-names(novel.data) = c("id","alltrial","experiment","agent","altAgent","rightFruit","leftFruit","corObjInf","corObjPrior","pick","prior","inf","trial","alignment","change","rt","correct_inf","correct_prior") 
-novel.data$pick= str_sub(novel.data$pick,65,str_length(novel.data$pick)-4)
[…]

### 2019-09-05 stats/kids/data_preprocessing_kids.R

@@ -1,262 +1,0 @@
-
-library(rjson)
-library(tidyr)
-library(stringr)
-library(dplyr)
-library(data.table)
-library(readxl)
-library(lubridate)
-
-
-##
-setwd("~/Work/MCC/git-mcc/mcc/stats/")
-
-############################
-######## novelty ###########
-################################################################################################################
-
-
-# select all files from individual workers
-files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round1/")
-
-
-#combine files into one dataframe
-raw <- data.frame()
-for (f in files) {
-  jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round1/",f,sep="")
-  jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(test_date= jf,
-                   data = jd$data$data
-  )
-  raw <- bind_rows(raw, id)
-}
-
-# convert into short format, drop unnecessary columns, rename variables and sort by id
-novel.data= melt(setDT(raw), measure = patterns( "^data.subid","^data.subage","^data.condition","^data.agent","^data.altAgent","^data.leftFruit","^data.rightFruit","^data.pick","^data.novel","^data.trial","^data.speakerChange","^data.rt", "^data.correct"))
-names(novel.data) = c("test_date","alltrial","subid","age","condition","agent","altAgent","leftObject","rightObject","pick","target","trial","change","rt","correct") 
-novel.data$pick= str_sub(novel.data$pick,72,str_length(novel.data$pick)-4)
-novel.data = novel.data[!duplicated(novel.data), ]
-novel.data = novel.data[order(subid)]
-
-
-
-# calculating age
-novel.data $test_date = as.Date(str_sub(novel.data $test_date,51,str_length(novel.data $test_date)-11))
-
-
-# change subid for subjects so that they match the subject log file
-# also chnage age group for one child to match dob
-novel.data <- novel.data%>%
-  mutate(targetObj = ifelse(target == "left",leftObject, rightObject),
-         correct = ifelse(pick == targetObj, 1, 0))
-
-
-
-
-
-
-
-# load subject log file
-log <- read_excel("../../MCC-subject_log.xlsx", 1)%>%
-  filter(Condition == "nov")%>%
-  select(subid,experimenter,keep_drop,sex,dob)
-
-# koin datasets
-novel.data <- left_join(novel.data,log, by = "subid")%>%
[…]

### 2019-09-05 experiments/Ex3_2/_layout/custom.js
clean repo

@@ -1,31 +1,0 @@
-setTimeout(function() {
-
-  var getLineHeight = function(el) {
-    return parseInt(document
-                    .defaultView
-                    .getComputedStyle(el, null)["line-height"]
-                    .replace("px",""));
-  }
-  
-  $("li:has(.content) > .annotation")
-    .filter(function(i, a) {
-      var p = $(a).find("p")[0];
-      if (!p) {
-        return false;
-      }
-      
-      var c = $(this).parent().find(".content")[0];
-      return $(p).height() > $(c).outerHeight();
-    })
-    .addClass("folded")
-    .prepend($("<span class='ellipsis'>+</span>").click(function(e) {
-      $(this).parent().toggleClass("folded");
-
-      if ($(this).text() == "+") {
-        $(this).text("-")
-      } else {
-        $(this).text("+")
-      }
-    }))
-
-}, 200);

### 2019-09-05 experiments/Ex5_child/Ex5_child.js

@@ -1,0 +1,1076 @@
+// preload
+var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back10.jpg","back4.jpg","back6.jpg","empty.png"];
+//for critical trials and fillers
+var images = new Array();
+for (i = 0; i < preFruits.length; i++) {
+	images[i] = new Image();
+	images[i].src = "images/" + preFruits[i];
+    images[i].id = preFruits[i];
+}
+
+
+
+function showLeftFriend(id) {
+	$(".tree_l").hide();
+	$("#"+id+"_l").show();
+}
+
+function showRightFriend(id) {
+	$(".tree_r").hide();
+	$("#"+id+"_r").show();
+}
+
+
+function showLeftChoiceFriend(id) {
+    $(".tree_l").hide();
+	$("#"+id+"_l_c").show();
+}
+
+function showRightChoiceFriend(id) {
+	$(".tree_r").hide();
+	$("#"+id+"_r_c").show();
+}
+
+var preSounds = ["Frog_intro.mp3",
+                 "ticon_label.mp3", "ticon_which.mp3",
+                 "oscot_label.mp3","oscot_which.mp3",
+                 "zoyar_label.mp3","zoyar_which.mp3",
+                 "kepel_label.mp3","kepel_which.mp3",
+                 "glipsa_label.mp3","glipsa_which.mp3",
+                 "toma_label.mp3","toma_which.mp3",
+                 "zubi_label.mp3","zubi_which.mp3",
+                 "wiso_label.mp3","wiso_which.mp3",
+                 "end.mp3", "more_trees.mp3"];
+//for critical trials and fillers
+var sound = new Array();
+for (i = 0; i < preSounds.length; i++) {
+	sound[i] = new Audio();
+	sound[i].src = "sound/" + preSounds[i];
+    sound[i].id = preSounds[i];
+}
+
+// ## Helper functions
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+function showText(id) {
+  // Hide all slides
+	$(".text").hide();
+	// Show just the slide we want to show
[…]

### 2019-09-05 experiments/Ex5_child/mmturkey.js

@@ -1,0 +1,263 @@
+// Bundle in Crockford's JSON2.js
+var JSON;JSON||(JSON={});
+(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
+e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
+"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-09-05 experiments/kids_informativeness/mcc_informativeness.js

@@ -1,673 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png"];
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
-    images[i].id = preFruits[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
-}
-
-// ## Helper functions
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-  // Hide all slides
-	$(".text").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-	$("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-  // Hide all slides
-	$(".agent").hide();
-}
-
[…]

### 2019-09-05 experiments/kids_informativeness/mcc_informativeness2.js

@@ -1,837 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png","fence.png"];
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
-    images[i].id = preFruits[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Elephant_train.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
-    sound[i].id = preSounds[i];
-}
-
-// ## Helper functions
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-  // Hide all slides
-	$(".text").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-	$("#"+id+"_"+orient).show();
[…]

### 2019-09-05 experiments/kids_informativeness/mcc_informativeness4_text.js

@@ -1,863 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","back10.jpg","empty.png","fence.png"];
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
-    images[i].id = preFruits[i];
-}
-
-
-/*var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Pig_train.mp3","Elephant_choice.mp3","Elephant_train.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
-    sound[i].id = preSounds[i];
-}*/
-
-// ## Helper functions
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-  // Hide all slides
-	$(".text").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
[…]

### 2019-09-05 experiments/kids_informativeness/mmturkey.js

@@ -1,263 +1,0 @@
-// Bundle in Crockford's JSON2.js
-var JSON;JSON||(JSON={});
-(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
-e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
-"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-09-05 experiments/kids_novelty/mcc_novelty.js

@@ -1,679 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","empty.png"];
-
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3"];
-//for critical trials and fillers
-var sound = new Array();
-for (i = 0; i < preSounds.length; i++) {
-	sound[i] = new Audio();
-	sound[i].src = "sound/" + preSounds[i];
-}
-
-// ## Helper functions
-
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-function showText(id) {
-	$(".text").hide();
-	$("#"+id).show();
-}
-
-
-function showAgent(id, orient) {
-	$(".agent").hide();
-    $(".point_agent_l").hide();
-    $(".point_agent_r").hide();
-	$("#"+id+"_"+orient).show();
-}
-
-function hideAgent() {
-	$(".agent").hide();
-}
-
-
-function choiceAgent(id) {
-	$(".agent").hide();
-	$("#"+id+"_choice").show();
-}
-
-function sourceRightFruit(a) {
[…]

### 2019-09-05 experiments/kids_novelty/mcc_novelty2.js

@@ -1,699 +1,0 @@
-// preload
-var preFruits = ["duck.png","car.png","bear.png","ball.png","t1.png", "t2.png", "t3.png", "t4.png", "t5.png", "t6.png", "t7.png", "t8.png", "t9.png", "t10.png", "t11.png", "t12.png", "t13.png", "t14.png", "t15.png", "t16.png", "t17.png", "t18.png","back1.jpg","back2.jpg","back3.jpg","back4.jpg","back5.jpg","back6.jpg","back7.jpg","back8.jpg","back9.jpg","empty.png"];
-
-//for critical trials and fillers
-var images = new Array();
-for (i = 0; i < preFruits.length; i++) {
-	images[i] = new Image();
-	images[i].src = "images/" + preFruits[i];
-}
-
-
-var preSounds = ["Frog_choice.mp3", "Mouse_choice.mp3", "Bear_choice.mp3", "Beaver_choice.mp3", "Monkey_choice.mp3", "Dog_choice.mp3", "Cat_choice.mp3", "Bunny_choice.mp3", "Tiger_choice.mp3", "Sheep_choice.mp3","Pig_choice.mp3","Elephant_choice.mp3","Frog_hello.mp3", "Mouse_hello.mp3", "Bear_hello.mp3", "Monkey_hello.mp3", "Dog_hello.mp3", "Cat_hello.mp3", "Bunny_hello.mp3", "Tiger_hello.mp3", "Sheep_hello.mp3","Pig_hello.mp3","Elephant_hello.mp3", "Beaver_hello.mp3","end.mp3","Frog_point_nothing.mp3", "Mouse_point_nothing.mp3", "Bear_point_nothing.mp3", "Beaver_point_nothing.mp3", "Monkey_point_nothing.mp3", "Dog_point_nothing.mp3", "Cat_point_nothing.mp3", "Bunny_point_nothing.mp3", "Tiger_point_nothing.mp3", "Sheep_point_nothing.mp3","Pig_point_nothing.mp3","Pig_train.mp3","Elephant_point_nothing.mp3","Elephant_train.mp3","Frog_point_old1.mp3", "Mouse_point_old1.mp3", "Bear_point_old1.mp3", "Monkey_point_old1.mp3", "Dog_point_old1.mp3", "Cat_point_old1.mp3", "Bunny_point_old1.mp3", "Tiger_point_old1.mp3", "Sheep_point_old1.mp3","Pig_point_old1.mp3","Elephant_point_old1.mp3", "Beaver
[…]

### 2019-09-05 experiments/kids_novelty/mmturkey.js

@@ -1,263 +1,0 @@
-// Bundle in Crockford's JSON2.js
-var JSON;JSON||(JSON={});
-(function(){function k(a){return a<10?"0"+a:a}function o(a){p.lastIndex=0;return p.test(a)?'"'+a.replace(p,function(a){var c=r[a];return typeof c==="string"?c:"\\u"+("0000"+a.charCodeAt(0).toString(16)).slice(-4)})+'"':'"'+a+'"'}function l(a,j){var c,d,h,m,g=e,f,b=j[a];b&&typeof b==="object"&&typeof b.toJSON==="function"&&(b=b.toJSON(a));typeof i==="function"&&(b=i.call(j,a,b));switch(typeof b){case "string":return o(b);case "number":return isFinite(b)?String(b):"null";case "boolean":case "null":return String(b);case "object":if(!b)return"null";
-e+=n;f=[];if(Object.prototype.toString.apply(b)==="[object Array]"){m=b.length;for(c=0;c<m;c+=1)f[c]=l(c,b)||"null";h=f.length===0?"[]":e?"[\n"+e+f.join(",\n"+e)+"\n"+g+"]":"["+f.join(",")+"]";e=g;return h}if(i&&typeof i==="object"){m=i.length;for(c=0;c<m;c+=1)typeof i[c]==="string"&&(d=i[c],(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h))}else for(d in b)Object.prototype.hasOwnProperty.call(b,d)&&(h=l(d,b))&&f.push(o(d)+(e?": ":":")+h);h=f.length===0?"{}":e?"{\n"+e+f.join(",\n"+e)+"\n"+g+"}":"{"+f.join(",")+
-"}";e=g;return h}}if(typeof Date.prototype.toJSON!=="function")Date.prototype.toJSON=function(){return isFinite(this.valueOf())?this.getUTCFullYear()+"-"+k(this.getUTCMonth()+1)+"-"+k(this.getUTCDate())+"T"+k(this.getUTCHours())+":"+k(this.getUTCMinutes())+":"+k(this.getUTCSeconds())+"Z":null},String.prototype.toJSON=Number.prototype.toJSON=Boolean.prototype.toJSON=function(){return this.valueOf()};var q=/[\u0000\u00ad\u0600-\u0604\u070f\u17b4\u17b5\u200c-\u200f\u2028-\u202f\u2060-\u206f\ufeff\ufff0-\uffff]/g,
[…]

### 2019-10-04 papers/full_paper/Supplementary_information.Rmd
update manuscript

--- 2019-09-03 papers/full_paper/SI_appendix.Rmd
@@
 ---
-title             : "Supplementary information: Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
-shorttitle        : "Pragmatic cue integration: Supplementary information"
+title             : "Supplementary information: Predicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+shorttitle        : "Predicting pragmatic cue integration: Supplementary information"
 
@@
 ### Prior strength manipualtions
-
-```{r ex4 prior pre-tests data adults}
-# load data from prior strength manipulation experiments to set priors
-adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
-```
 

### 2019-10-04 papers/full_paper/manuscript.Rmd
update manuscript

@@
 ---
-title             : "Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+title             : "Predicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
 shorttitle        : "Pragmatic cue integration"
@@
   Language is learned in complex social settings where listeners must reconstruct speakers’ intentend meanings from context.
-To navigate this challenge, children can use contextual or pragmatic reasoning to learn the meaning of unfamiliar words.
-One important challenge for pragmatic reasoning is that it often requires integrating information about the current utterance with broader common ground built up over the course of an interaction.
+To navigate this challenge, children can use pragmatic reasoning to learn the meaning of unfamiliar words.
+One important challenge for pragmatic reasoning is that it requires integrating multiple information sources.
 Here we study this integration process.
-We isolate these two sources of pragmatic information and formalize both how they should be combined and how they might develop using a probabilistic model of conversational reasoning.
-We present a series of seven experiments with three- to five-year-old children and adults that suggest that these two information sources flexibly trade off with one another.
-A cue combination model accurately predicted empirical results for children and adults and provided a better fit compared with alternative models in which only one information source was considered.
+We isolate two sources of pragmatic information and, using a probabilistic model of conversational reasoning, formalize both how they should be combined and how this process might develop.
+We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children and adults in a series of pre-registered experiments.
+Results show close numerical alignment between model predictions and data.
 This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
@@
 keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling"
-wordcount         : "X"
 
@@
 
-csl               : pnas.csl
+csl               : nature.csl
 
@@
 
-# Significance statement
-
-In order to learn the meaning of a new word, children need to integrate multiple sources of information.
-Some information is provided by the utterance itself, but other contextual information accumulates over the course of a conversation and is stored in common ground.
-To understand how these sources are integrated with one another and how they might develop, we formalize this process using computational models of pragmatic reasoning.
-These models make quantitative predictions for different hypotheses about how integration proceeds.
-We find that the way in which preschoolers and adults integrate information is best described by a model that flexibly trades off between different sources of information.
-Taken together, this work presents an explicit theory of socially grounded language learning.
-
-# Introduction
-
 What someone means by an utterance is oftentimes not reducible to the words they used.
-It takes  pragmatic inference – context-sensitive reasoning about the speaker’s intentions - to recover the intended meaning [@grice1991studies, @levinson2000presumptive, @sperber2001relevance].
+It takes  pragmatic inference – context-sensitive reasoning about the speaker’s intentions - to recover the intended meaning [@grice1991studies; @levinson2000presumptive; @sperber2001relevance].
 Contextual information comes in many forms.
@@
 Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative.
-Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies, @clark1996using, @sperber2001relevance, @tomasello2008origins].
-On the other hand, there is information provided by common ground (the body of knowledge and beliefs shared between interlocutors; [@bohn2018common, @clark1996using, @clark2015common].
-Because utterances are embedded in a broader (ongoing) social interaction, common ground information serves as a background against which new utterances are interpreted, making some meanings for ambiguous terms more likely than others.
+Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins].
+On the other hand, there is information provided by common ground (the body of knowledge and beliefs shared between interlocutors)[@bohn2018common; @clark1996using; @clark2015common].
+Because utterances are embedded in common ground, pragmatic reasoning in context always requires information integration.
+But how does integration proceed?
+And how does it develop?
+Verbal theories assume that information is integrated and that this process develops but do not specify how.
+We bridge this gap by formalizing information integration and development in a probabilistic model of pragmatic reasoning.
 
-Children learning their first language make inferences about intended meanings based on utterance-level and common-ground information both for language understanding and language learning [@bohn2019pervasive, @clark2009first, @tomasello2008origins].
+Children learning their first language make inferences about intended meanings based on utterance-level and common-ground information both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins].
 Starting very early, infants expect adults to produce utterances in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve].
 By age two, children are sensitive to the informativeness of communication [@o2001two].
-By age three children can use this expectation to make pragmatic inferences [@stiller2015ad, @yoon2019role] and to infer novel word meanings [@frank2014inferring].
-And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children, @horowitz2018trouble, @barner2011accessing].
+By age three children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring].
+And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children; @horowitz2018trouble; @barner2011accessing].
 Thus, children’s ability to reason about utterance-level pragmatics is present at least by ages three to five, and possibly substantially younger.
 
-Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social, @saylor2011s].
-For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role, @diesendruck2004two, @saylor2009preschoolers, @sullivan2019discourse].
+Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers; @sullivan2019discourse].
 
@@
 While many theories of pragmatic reasoning presuppose that both information sources are integrated, the nature of their relationship has typically not been specified.
-We address this challenge here.
 
 Recent innovations in probabilistic models of pragmatic reasoning provide a quantitative method for addressing the problem of integrating multiple sources of contextual information.
-This class of computational models, which are referred to as Rational Speech Act (RSA) models [@frank2012predicting, @goodman2016pragmatic] formalize the problem of language understanding as a special case of Bayesian social reasoning.
+This class of computational models, which are referred to as Rational Speech Act (RSA) models [@frank2012predicting; @goodman2016pragmatic] formalize the problem of language understanding as a special case of Bayesian social reasoning.
 A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative.
@@
 Thus, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade off between the prior probability of a meaning and the informativeness of the utterance.
-This trade off between contextual factors during word learning is a unique aspect of the word learning problem that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic, @frank2009using] or describing generalizations about word meaning [@xu2007word].
+This trade off between contextual factors during word learning is a unique aspect of the word learning problem that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].
 
@@
 To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans] predictions about conditions in which they either coincide or conflict.
+Finally, we pre-register these quantitative predictions and test them against new data from adults and children.
 
@@
 Then we generate a priori model predictions and compare them to data from an experiment – parallel to Experiment 3 – in which both information sources have to be integrated (Experiment 7).
-To our knowledge, the strategy of independently estimating model parameters with separate groups and combining them via the model to make preregistered quantitative predictions about a new population has not been used before with children.
 
@@
 
-# How do adults integrate contextual sources of information?
+# Results
 
-## Inferences based on utterance and common ground information  (Experiments 1 and 2)
+## How do adults integrate contextual sources of information?
+
+### Inferences based on utterance and common ground information  (Experiments 1 and 2)
 
@@
 In Experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
-The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig.
-1A).
+The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}A).
 When the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them, participants could infer that the word referred to object B.
@@
 In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior.
-Participants selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`).
+Participants selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+
 ```{r ex2-results}
@@
 
-In Experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role, @saylor2009preschoolers].
-In Experiment 2A, the speaker expressed a preference for one of two objects (Fig.
-1B, left).
+In Experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @saylor2009preschoolers].
+In Experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}B, left).
 Later, the speaker used a novel word to request an object.
 Adults selected the preferred object above chance (t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`) and more so than in a control condition, where a different speaker, whose preferences were unknown, made the request ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-In Experiment 2B, common ground information came in the form of novelty (Fig 1B, right).
+In Experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}B, right).
 First, the speaker encountered one object on one of the tables.
 Later, a second object appeared.
-When the same speaker then used a novel word to request an object, participants selected the new object above chance (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`), and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+When the same speaker then used a novel word to request an object, participants selected the new object above chance (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`), and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
 Taken together, Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
 
-## Model predictions for information integration evaluated against new data (Experiment 3).
+```{r fig2, include = T, fig.align = "center", fig.cap = "Results from Experiments 1, 2A, and 2B for adults.
+For preference and novelty, control refers to a different speaker (see Fig 1B).
+Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", out.width="300px"}
+knitr::include_graphics("./figures/fig2.png")
+```
+
+### Model predictions for information integration evaluated against new data (Experiment 3)
 
@@
 The speaker is an approximately rational Bayesian actor (with degree of rationality alpha), who produces utterances as a function of their informativity.
-The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see SI Appendix for details):
+The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see supplementary information for details):
 
@@
 Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point.
-Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see SI Appendix for modeling details).
+Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see supplementary information for modeling details).
 
@@
 The in-the-moment, contextual informativeness of the utterance is captured in the likelihood term, whose value depends on the rationality parameter $\alpha$.
-Assumptions about rationality may change depending on context and we therefore used the data from Experiment 1 to specify $\alpha$ (see SI Appendix for details about these parameters).
+Assumptions about rationality may change depending on context and we therefore used the data from Experiment 1 to specify $\alpha$ (see supplementary information for details about these parameters).
 
-The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig.
-1C - see SI Appendix for additional details and a worked example of how predictions were generated).
+The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}C - see supplementary information for additional details and a worked example of how predictions were generated).
 In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter to account for responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (Experiment 3).
-Including the noise parameter greatly improved the model fit to the data (see SI Appendix for details).
+Including the noise parameter greatly improved the model fit to the data (see supplementary information for details).
 We did not pre-register the inclusion of a noise parameter for Experiment 3 but did so for all subsequent experiments.
@@
 In Experiment 3, we combined the procedures of Experiment 1 and 2A or 2B.
-The test setup was identical to Experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig.
-1C).
+The test setup was identical to Experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}C).
 We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).
@@
 
-Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig.
-2A).
+```{r fig3, include = T, fig.align = "center", fig.cap = "Results from Experiment 3 and 4 for adults.
+(A) Data and model predictions by condition for Experiment 3.
+Transparent dots show data from individual participants, diamonds represent condition means.
+(B) Correlation between model predictions and data in Experiment 3, (C) between data in Experiment 3 and data for the strong prior manipulation in Experiment 4 (direct replication) and (D) between model predictions and data in Experiment 4.
+Coefficients and p-values are based on Pearson correlation statistics.
+Error bars represent 95\\% HDIs." , out.width="400px"}
+
+knitr::include_graphics("./figures/fig3.png")
+```
+
+Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig \ref{fig:fig3}B).
 To test whether participants in fact balanced both information sources, we compared the pragmatics model to two alternative models: the *flat prior model*, which ignores common ground information and the *prior only model*, which ignores utterance information.
@@
 The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
-This value was substantially lower for the pragmatics model compared to the alternative models (see SI Appendix), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
+This value was substantially lower for the pragmatics model compared to the alternative models (see supplementary information), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
 Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "Correlation between model predictions and data.
-(A) Experiment 3, (B) Experiment 4, (C) 3-year-olds in Experiment 7 and (D) 4-year-olds in Experiment 7.
-Coefficients and p-values are based on Pearson correlation statistics.
-Error bars represent  95\\% HDIs.", out.width="450px"}
-knitr::include_graphics("./figures/fig2.png")
-```
-
-## Replication and extension to different levels of common ground information (Experiment 4).
+### Replication and extension to different levels of common ground information (Experiment 4)
 
@@
 To test if our model makes accurate predictions for different combinations, we first replicated and then extended the results of Experiment 3 to a broader range of experimental conditions.
-Specifically, we manipulated the strength of the common ground information (strong, medium and weak manipulation) by changing  the way the speaker interacted with the objects prior to the request We ran a total of 20 conditions, including a direct replication of Experiment 3 (see SI Appendix for details).
+Specifically, we manipulated the strength of the common ground information (strong, medium and weak manipulation) by changing the way the speaker interacted with the objects prior to the request We ran a total of 20 conditions, including a direct replication of Experiment 3 (see Fig \ref{fig:fig3}C).
 
-Model predictions from the pragmatics model were again highly correlated with the average response in each condition (Fig.
-2B).
+Model predictions from the pragmatics model were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}D).
 We evaluated model fit for the same models as in Experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to Experiment 3 and again lower compared to the alternative models (see SI Appendix).
+The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to Experiment 3 and again lower compared to the alternative models (see supplementary information).
 
-# Do children integrate contextual information?
+## Do children integrate contextual information?
 
@@
 
-## Inferences based on utterance and common ground information (Experiment 5 and 6)
+### Inferences based on utterance and common ground information (Experiment 5 and 6)
 
@@
 We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance (informativeness) and common ground (preference) information in isolation when making pragmatic inferences.
-We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive, frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition\footnote{For Experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.}.
+We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition\footnote{For Experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.}.
 
@@
 Three-year-olds, on the other hand, did not (t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`).
-Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`).
+Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
 Thus, children’s ability to use utterance information in a word learning context increased with age.
+
+```{r fig4, include = T, fig.align = "center", fig.cap = "Results from Experiment 5 and 6 for children.
+For preference, control refers to to the different speaker condition (see Fig.
+1B).
+Transparent dots show data from individual participants, regression lines show fitted linear models with 95\\% CIs.
+Dashed line indicates performance expected by chance.", out.width="300px"}
+knitr::include_graphics("./figures/fig4.png")
+```
 
@@
 For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`), whereas three-year-olds did not (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`).
-However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`4).
+However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
 Thus, children across the age range used common ground information to infer the referent of a novel word.
 
-## Developmental model predictions evaluated against new data (Experiment 7)
+### Developmental model predictions evaluated against new data (Experiment 7)
 
@@
 
-In Experiment 7, we combined the procedures of Experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig.
-1C).
+In Experiment 7, we combined the procedures of Experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}C).
 Children’s propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
@@
 For the correlational analysis, we binned model predictions and data by year.
-There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig.
-2C and D).
+There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig \ref{fig:fig5}B).
 One of the reasons for the latter was the low variation between conditions.
@@
 As with adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see SI Appendix).
+The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see supplementary information).
 
 The high level of inferred noise moved the model predictions for children in all conditions close to chance level.
-We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see SI Appendix).
+We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see supplementary information, see Fig \ref{fig:fig5}A).
 This analysis was not pre-registered.
@@
 In each case, the pragmatics model provided a better fit compared to the alternative models (flat prior: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; prior only: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+
+```{r fig5, include = T, fig.align = "center", fig.cap = "Results from Experiment 7 for children.
+(A) Model predictions and data across age in the four conditions.
+Colored lines show predictions from the pragmatics model with different noise parameters.
+Transparent black dots show data from individual participants and black lines show conditional means of the data.
+(B) Correlation between model predictions (with noise parameter) and condition means binned by year.
+Coefficients and p-values are based on Pearson correlation statistic.
+Error bars and shaded regions represent 95\\% HDIs.", out.width = "300px"}
+knitr::include_graphics("./figures/fig5.png")
+```
 
@@
 For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests.
-All experiments started with an introduction to the animals and two training trials.
+All experiments started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball).
 Subsequent test trials in each condition were presented in a random order.
-Detailed experimental procedures for each experiment can be found in the SI Appendix.
+
+The setup of Experiment 1 for adults is shown in Fig \ref{fig:fig1}A.
+In the beginning of each trial, the animal introduced themselves (e.g.
+“Hi, I’m Dog”) and then turned towards the table with the two objects.
+The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”).
+In the test condition, there was one object on the other table, whereas in the control condition, there were two.
+In the control condition, no inference was possible based on the speaker’s turning.
+The “correct” object in the control condition was randomly chosen from the two objects on the table.
+Technically, this condition did not control for any alternative explanations and we therefore did not run it for children (see below).
+Participants received six trials, three per condition.
+
+The setup for Experiment 2 is shown in Fig \ref{fig:fig1}B.
+In the preference manipulation, the animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
+Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
+This procedure was the strong preference manipulation.
+In the medium version, the animal only expressed preference and did so in a more subtle way (simply saying: “Oh, wow”).
+
+In the novelty manipulation one of the tables was initially empty.
+The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
+After shortly disappearing, the same animal repeated the sequence above.
+When the animal left a second time, a new object appeared on the empty table.
+Next, either the same or a different animal returned and requested an object.
+This corresponded to the strong manipulation.
+For the medium manipulation, the animal turned to each table only once before the new object appeared.
+In the weak manipulation, the animal only commented on the present object once and never turned to the empty table.
+Participants always received six trials, three with the same and three with the different speaker.
+
+For Experiment 3 and 4 we inserted the common ground manipulation before the request in the setup of Experiment 1 (Fig \ref{fig:fig1}C).
+For example, the animal turned to the table with one object and expressed that they liked object A, then turned to the other table and express that they did not like object B.
+Next, after quickly disappearing, the animal reappeared, turned to the table with two objects and make a request.
+To make it clear, which of the objects the speaker commented on while being turned to the table with the two objects during the common ground manipulation, the object was temporarily enlarged.
+Participants completed eight trials for one of the common ground manipulations with two trials per condition (same/different speaker x congruent/incongruent).
+
+Experiment 5 for children was modeled after @frank2014inferring.
+Instead of on tables, objects were presented as hanging in trees (to facilitate showing points to distinct locations).
+After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
+Next, the trees and the objects in them disappeared and new trees replaced them.
+The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced).
+While facing straight, the animal first said “Here are some more trees” and then asked the child to pick the tree with the object that corresponded to the novel word (“Which of these trees has a [non-word]?”).
+Children received six trials in a single test condition.
+
+Experiment 2 for children was identical to the strong preference manipulation for adults. Children received eight trials, four with the same and four with a different animal returning.
+
+In Experiment 3 for children, we again inserted the preference manipulation into the setup of Experiment 1.
+After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
+Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
+Next, the animal disappeared and either the same or a different animal returned.
+The rest of the trial was identical to the label and request phase of Experiment 1.
+Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
 
@@
 Details on models can be found in the supplementary information.
-
-# Acknowledgements
-
-MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
-749229.
-MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
-We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
 
@@
 \endgroup
+
+\newpage
+
+# Acknowledgements
+
+MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
+
+# Author Contributions
+
+MB and MCF conceptualized the study, MM collected the data, MB and MHT analyzed the data, MB, MHT and MCF wrote the manuscript, all authors approved the final version of the manuscript.
+
+# Competing Interests
+
+The authors declare no competing interests.

### 2019-10-12 papers/full_paper/manuscript.Rmd
update manuscript for ethics

@@
 library(readxl)
+library(lsr)
 
@@
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         mean = mean(unlist(correct)),
          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(condition,df,t_value,p_value)%>%
+         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
+         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
+         d = cohensD(unlist(correct), mu = 0.5)) %>%
+  select(condition,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
   mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
-
+         t_value = round(t_value,2),
+         t_lci = round(t_lci,2),
+         t_uci = round(t_uci,2),
+         d = round(d,2))
 # model
@@
 In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior.
-Participants selected object B above chance in the test condition (t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+Participants selected object B above chance in the test condition (mean = `r ex1t%>%filter(condition == "test")%>%pull(mean)`, 95% CI of mean = [`r ex1t%>%filter(condition == "test")%>%pull(t_lci)`; `r ex1t%>%filter(condition == "test")%>%pull(t_uci)`], t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, d = `r ex1t%>%filter(condition == "test")%>%pull(d)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
 
@@
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         mean = mean(unlist(correct)),
          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(condition,df,t_value,p_value)%>%
+         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
+         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
+         d = cohensD(unlist(correct), mu = 0.5)) %>%
+  select(condition,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
   mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
+         t_value = round(t_value,2),
+         t_lci = round(t_lci,2),
+         t_uci = round(t_uci,2),
+         d = round(d,2))
 
@@
 Later, the speaker used a novel word to request an object.
-Adults selected the preferred object above chance (t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`) and more so than in a control condition, where a different speaker, whose preferences were unknown, made the request ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+Adults selected the preferred object above chance (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so than in a control condition, where a different speaker, whose preferences were unknown, made the request ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
 In Experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}B, right).
@@
 Later, a second object appeared.
-When the same speaker then used a novel word to request an object, participants selected the new object above chance (t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`), and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+When the same speaker then used a novel word to request an object, participants selected the new object above chance (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) , and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
 Taken together, Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
@@
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         mean = mean(unlist(correct)),
          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(age_bin,df,t_value,p_value)%>%
+         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
+         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
+         d = cohensD(unlist(correct), mu = 0.5)) %>%
+  select(age_bin,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
   mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
+         t_value = round(t_value,2),
+         t_lci = round(t_lci,2),
+         t_uci = round(t_uci,2),
+         d = round(d,2))
 
@@
   mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
+         mean = mean(unlist(correct)),
          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-         p_value = t.test(unlist(correct), mu = 0.5)$p.value) %>%
-  select(age_bin,df,t_value,p_value)%>%
+         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
+         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
+         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
+         d = cohensD(unlist(correct), mu = 0.5)) %>%
+  select(condition,age_bin,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
   mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
-         t_value = round(t_value,2))
+         t_value = round(t_value,2),
+         t_lci = round(t_lci,2),
+         t_uci = round(t_uci,2),
+         d = round(d,2))
 
@@
 Four-year-olds selected the more informative object (i.e.
-the object that was unique to the location the speaker turned to) above chance (t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`).
-Three-year-olds, on the other hand, did not (t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`).
+the object that was unique to the location the speaker turned to) above chance (mean = `r child_ex1t%>%filter(age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="4")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="4")%>%pull(d)`).
+Three-year-olds, on the other hand, did not (mean = `r child_ex1t%>%filter(age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="3")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="3")%>%pull(d)`).
 Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
@@
 
-For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`), whereas three-year-olds did not (t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`).
+For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`).
 However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
@@
 
+The study was approved by the Stanford Institutional Review Board (protocol no.
+19960).
 All experimental procedures, sample sizes and statistical analysis were pre-registered (https://osf.io/u7kxe/).
@@
 Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9.
+Each participant contributed data to only one experiment.
 Experiment 1 and each manipulation of Experiment 2 had N = 40 participants.
@@
 Parents gave informed consent and provided demographic information.
+Each child contributed data to only one experiment.
 We collected data from a total of 243 children between 3.0 and 5.0 years of age.
@@
 All analyses were run in R [@R-base].
-GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
+All p-values are based on two sided analysis.
+Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests.
+Frequentist GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
 Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
 Bayes Factors for model comparisons were based on marginal likelihoods of each model given the data.
-Details on models can be found in the supplementary information.
+Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the supplementary information and the online repository.
 

### 2019-12-16 papers/full_paper/Supplementary_information.Rmd
update repo for submission

@@
 ---
-title             : "Supplementary information: Predicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
-shorttitle        : "Predicting pragmatic cue integration: Supplementary information"
+title             : "Supplementary information  \nPredicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
+shorttitle        : " "
 
@@
     affiliation   : "1,2"
-    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
-    email         : "bohn@stanford.edu"
   - name          : "Michael Henry Tessler"
@@
   \usepackage{caption}
+  \usepackage{setspace}\doublespacing
   \renewcommand{\thetable}{S\arabic{table}} 
@@
 library(exactRankTests)
+library(matrixStats)
+library(readxl)
 
@@
 
+We used `r cite_r("library.bib")` for all our analyses reported in the main manuscript and the supplementary material.
+
 ## Experiment 1
@@
 
-```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 1, 3 and 4.", out.width="400px"}
+```{r figS1, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 1, 3 and 4.", out.width="100%"}
 knitr::include_graphics("./figures/SI_setup_inf.png")
@@
 Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", fig.height = 3}
+Dashed line indicates performance expected by chance.", fig.align = "center", out.width="80%"}
 p1 <- bind_rows(
@@
 
-```{r figS2, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation in Experiment 2 for adults.", out.width="400px"}
+```{r figS2, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation in Experiment 2 for adults.", out.width="100%"}
 knitr::include_graphics("./figures/SI_setup_pref.png")
@@
 Empirical means are shonw in black and model predictions in pink.
-Error bars represent 95\\% HDIs.", fig.height = 4}
+Error bars represent 95\\% HDIs.", fig.align = "center", out.width="100%"}
 adult_ex3_data_summary <- adult_ex3_data %>%
@@
 In preference/medium the animal only turned to one side and expressed liking in a more subtle way (saying only: “Oh, wow”).
+We piloted several procedures but did not find a manipualtion that indicated only weak preference.
 
@@
 Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", fig.height = 4.5}
+Dashed line indicates performance expected by chance.", fig.align = "center", out.width="100%"}
 
@@
 
-```{r figS3, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 5 and 7.", out.width="400px"}
+```{r figS3, include = T, fig.align = "center", fig.cap = "Screenshot showing test situation Experiment 5 and 7.", out.width="100%"}
 knitr::include_graphics("./figures/SI_setup_inf_child.png")
@@
 Transparent dots show data from individual participants, regression lines shows smoothed conditional mean with 95\\% CI.
-Dashed line indicates performance expected by chance.", fig.height = 3.5}
+Dashed line indicates performance expected by chance.", fig.align = "center", out.width="70%"}
 p_child_ex12 <- bind_rows(
@@
   geom_jitter(alpha = 0.2, height = 0.02, width = 0)+
-  geom_smooth(aes(fill = condition),method = "loess", se = T, span = 2,  alpha = .5, size = .7)+
+  geom_smooth(aes(fill = condition),method = "glm",method.args = list(family = "binomial"), se = T, alpha = .5, size = .7)+
   labs(x="Age",y="Proportion correct")+
@@
 ```{r plotmodelpredex7, fig.cap = "Model predictions and data for Experiment 7 with children.
-Colored lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants and the black line with grey CI shows the smoothed conditional mean of the data in each condition.", fig.height = 4}
+Colored lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants and the black line with grey CI shows the smoothed conditional mean of the data in each condition.", fig.align = "center", out.width="100%"}
 child_model_predictions <- readRDS("../../stats/saves/child_ex3_model_predictions.rds")%>%
@@
   geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
-  geom_smooth(data = p_child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
+  geom_smooth(data = p_child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "glm",method.args = list(family = "binomial"),  se = T,  alpha = .5)+
   #geom_hline(yintercept = 0.5, lty=2)+
@@
 Dots represent condition modes.
-Error bars represent 95\\% HDIs.", fig.height=2.5}
+Error bars represent 95\\% HDIs.", fig.align = "center", out.width="100%"}
 
@@
 
-```{r ex3noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.height = 2}
+```{r ex3noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
 ex3_noise_parameters <- bind_rows(
@@
 Dots represent condition modes.
-Error bars represent 95\\% HDIs.", fig.height=3}
+Error bars represent 95\\% HDIs.", fig.align = "center", out.width="100%"}
 
@@
 
-```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.height = 2}
+```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
 ex4_noise_parameters <- bind_rows(
@@
 ```{r childnoise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 7.
-A: single noise parameter across age, B: Developmental noise parameter.", fig.height = 2.5}
+A: single noise parameter across age, B: Developmental noise parameter.", fig.align = "center", out.width="100%", fig.height=3}
 ggarrange(child_noise_plot,child_dev_noise_plot, nrow = 1, ncol = 2, common.legend = T, legend = "right", labels = c("A","B"))
@@
 Dots represent condition modes.
-Error bars represent 95\\% HDIs.", fig.height = 7}
+Error bars represent 95\\% HDIs.", fig.align = "center", out.width="100%", fig.height=7}
 # child_cor <- bind_rows(
@@
 In all cases, the pragmatics model outperformed the two alternative models, both for children as well as for adults.
-Interestingly, for adults but not for children, using a uniform prior $L_0$ yielded a lower estimate for the noise parameter in Experiment 3 and 4.
+Interestingly, for adults but not for children, using a uniform prior for $L_0$ yielded a lower estimate for the noise parameter in Experiment 3 and 4.
 

### 2019-12-16 papers/full_paper/manuscript.Rmd
update repo for submission

@@
 We isolate two sources of pragmatic information and, using a probabilistic model of conversational reasoning, formalize both how they should be combined and how this process might develop.
-We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children and adults in a series of pre-registered experiments.
+We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children (N = 243) and adults (N = 694).
 Results show close numerical alignment between model predictions and data.
@@
 
-keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling"
+keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
 
 bibliography      : ["library.bib"]
-
-csl               : nature.csl
 
@@
 
+# Introduction
+
 What someone means by an utterance is oftentimes not reducible to the words they used.
@@
 On the one hand, there is information provided by the utterance\footnote{We use the terms utterance, utterance-level information or utterance-level cues to capture all cues that the speaker provides for their intended meaning.
-This includes direct referential information in the form of actions such as pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.} itself.
+This includes direct referential information in the form of pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.} itself.
 Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative.
@@
 Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
-For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers; @sullivan2019discourse].
+For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @saylor2009preschoolers; @sullivan2019discourse].
 
@@
 
-Listeners and speakers also enter into a conversation with assumptions about what is likely to be talked about, a reflection of the common ground shared between them.
 RSA models capture common ground information as a shared prior distribution over possible intended meanings.
 Thus, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade off between the prior probability of a meaning and the informativeness of the utterance.
-This trade off between contextual factors during word learning is a unique aspect of the word learning problem that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].
+This trade off between contextual factors during word learning is a unique aspect that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].
 
 We make use of this framework to study pragmatic cue integration across development.
-To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans] predictions about conditions in which they either coincide or conflict.
+To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans]: we make independent measurements of each cue’s strength and then combine them using the RSA model described above to make independent predictions about conditions in which they either coincide or conflict.
 Finally, we pre-register these quantitative predictions and test them against new data from adults and children.
 
-We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (Experiment 1).
-In separate experiments, we then show that adults make inferences based on common ground information (Experiment 2A and 2B).
+We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (experiment 1).
+Then we show that adults make inferences based on common ground information (experiment 2A and 2B).
 We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance and common ground information should be integrated.
@@
 
-After successfully validating this approach with adults, we apply the same model-driven experimental procedure to children: We first show that they make pragmatic inferences based on utterance and common ground information separately (Experiment 5 and 6).
-Then we generate a priori model predictions and compare them to data from an experiment – parallel to Experiment 3 – in which both information sources have to be integrated (Experiment 7).
+After successfully validating this approach with adults in study 1, we apply the same model-driven experimental procedure to children (study 2): We first show that they make pragmatic inferences based on utterance and common ground information separately (experiment 5 and 6).
+Then we generate a priori model predictions and compare them to data from an experiment in which both information sources have to be integrated (experiment 7).
 
-Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level (Gricean) and common-ground information flexibly.
+Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level and common-ground information flexibly.
 Second, it uses Bayesian data analysis within the RSA framework to provide a model for understanding the multiple loci for developmental change in complex behaviors like contextual communication.
@@
 Participants clicked on the object they thought the speaker referred to.
-Informativeness (Experiment 1, left) translated to making one object less frequent in context.
-Common ground (Experiment 2, middle) was manipulated by making one object preferred by or new to the speaker.
+Speech bubbles represent pre-recorded utterances.
+Informativeness (a) translated to making one object less frequent in context.
+Common ground (b) was manipulated by making one object preferred by or new to the speaker.
 Green plus signs represent utterances that expressed preference and red minus signs represent utterances that expressed dispreference (see main text for details).
-Experiment 3 (right) combined manipulations.
-One condition of Experiment 3 is shown here: preference - same speaker - incongruent.", out.width="450px"}
+Integration (c) combined informativeness and common ground manipulations.
+One integration condition is shown here: preference - same speaker - incongruent.", out.width="100%"}
 knitr::include_graphics("./figures/fig1.png")
@@
 
-# Results
+# Study 1: Adults
 
-## How do adults integrate contextual sources of information?
+## Participants
 
-### Inferences based on utterance and common ground information  (Experiments 1 and 2)
+Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9.
+Each participant contributed data to only one experiment.
+Experiment 1 and each manipulation of experiment 2 had *N* = 40 participants.
+Sample size in experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
+*N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations that went into experiment 4.
+Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.
+Sample sizes in all adult experiments were chosen to yield at least 120 datapoints per cell.
+All studies were approved by the Stanford Institutional Review Board (protocol no.
+19960).
+
+## Materials
+
+All experimental procedures were pre-registered (see https://osf.io/u7kxe/registrations).
+Experimental stimuli are freely available in the following online repository: https://github.com/manuelbohn/mcc.
+All experiments were framed as games in which participants would learn words from animals.
+They were implemented in HTML/JavaScript as a website.
+Adults were directed to the website via MTurk and responded by clicking objects.
+For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests.
+All experiments started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball).
+Subsequent test trials in each condition were presented in a random order.
+
+## Analytic approach
+
+We preregistered sample sizes, inferential statistical analysis and computational models for all experiments.
+All deviations from the registered analysis plan are explicitly mentioned.
+All analyses were run in R [@R-base].
+All p-values are based on two sided analysis.
+Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests.
+Frequentist logistic GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
+Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material available online.
+Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl].
+In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors which were calculated from the marginal likelihoods of each model given the data.
+Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online.
+Code to run the models is available in the associated online repository.
+
+## Experiment 1
+
+### Methods
 
@@
 
-In Experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
-The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}A).
-When the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them, participants could infer that the word referred to object B.
-This follows from the counter-factual inferences that, if the (informative) speaker had wanted to refer to object A, they would have pointed to the table with the single object (this being the least ambiguous way to refer to that object).
+In experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
+The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}a).
+At test, the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them.
+The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”).
+Participants could infer that the word referred to object B via the counter-factual inferences that, if the (informative) speaker had wanted to refer to object A, they would have pointed to the table with the single object (this being the least ambiguous way to refer to that object).
 In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior.
+Participants received six trials, three per condition.
+
+### Results
+
 Participants selected object B above chance in the test condition (mean = `r ex1t%>%filter(condition == "test")%>%pull(mean)`, 95% CI of mean = [`r ex1t%>%filter(condition == "test")%>%pull(t_lci)`; `r ex1t%>%filter(condition == "test")%>%pull(t_uci)`], t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, d = `r ex1t%>%filter(condition == "test")%>%pull(d)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+This finding replicates earlier work showing that adult listeners expect speakers to communicate in an informative way.
+
+## Experiment 2
+
+### Methods
 
@@
 
-In Experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @saylor2009preschoolers].
-In Experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}B, left).
-Later, the speaker used a novel word to request an object.
-Adults selected the preferred object above chance (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so than in a control condition, where a different speaker, whose preferences were unknown, made the request ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-In Experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}B, right).
-First, the speaker encountered one object on one of the tables.
-Later, a second object appeared.
-When the same speaker then used a novel word to request an object, participants selected the new object above chance (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) , and more often compared to when a different speaker (to whom both objects were equally new) made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
-Taken together, Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
+In experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @saylor2009preschoolers].
+In experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}b, left).
+The animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
+Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
+Participants could use the speakers preference to identify the referent when the same speaker returned but not when a different speaker appeared whose preferences were unknown.
 
-```{r fig2, include = T, fig.align = "center", fig.cap = "Results from Experiments 1, 2A, and 2B for adults.
-For preference and novelty, control refers to a different speaker (see Fig 1B).
+In experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}b, right).
+The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
+Later, a second object appeared on the previously empty table.
+Then the speaker used a novel word to request one of the objects.
+The referent of the novel word could be identified by assuming that the speaker uses it to refer to the object that is new to them.
+This inference was not licensed when a different speaker returned to whom both objects were equally new.
+For both novelty and preference, participants received six trials, three with the same and three with the different speaker.
+
+### Results
+
+In experiment 2A, participants selected the preferred object above chance (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so than in the speaker change control condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+
+In experiment 2B, participants selected the novel object above chance (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) when the same speaker made the request and more often compared to when a different speaker made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+
+```{r fig2, include = T, fig.align = "center", fig.cap = "Results from experiments 1, 2A, and 2B for adults.
+For preference and novelty, control refers to a different speaker (see Fig 1b).
 Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="300px"}
+Dashed line indicates performance expected by chance.", out.width="60%"}
 knitr::include_graphics("./figures/fig2.png")
@@
 
-### Model predictions for information integration evaluated against new data (Experiment 3)
+## Modelling information integration
 
-We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of Experiments 1 and 2 to inform key parameters of a computational model.
+Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
+We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model.
 The Rational Speech Act (RSA) model architecture introduced by [@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
@@
 The speaker is an approximately rational Bayesian actor (with degree of rationality alpha), who produces utterances as a function of their informativity.
-The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see supplementary information for details):
+The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see Supplementary Material available online for details):
 
@@
 Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point.
-Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see supplementary information for modeling details).
+Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see Supplementary Material available online for modeling details).
 
 This computational model provides a natural avenue to formalize quantitatively how informativeness and common ground trade-off during word learning.
-As mentioned above, the common ground shared between speaker and listener plays the role of the listener’s prior distribution over meanings, or types of referents, that the speaker might be referring to and which we posit depends on prior interactions around the referents in the present context (e.g., preference or novelty; Experiment 2A and B).
-We use the results from Experiment 2 to specify this distribution.
+As mentioned above, the common ground shared between speaker and listener plays the role of the listener’s prior distribution over meanings, or types of referents, that the speaker might be referring to and which we posit depends on prior interactions around the referents in the present context (e.g., preference or novelty; experiment 2A and B).
+We use the results from experiment 2 to specify this distribution.
 The in-the-moment, contextual informativeness of the utterance is captured in the likelihood term, whose value depends on the rationality parameter $\alpha$.
-Assumptions about rationality may change depending on context and we therefore used the data from Experiment 1 to specify $\alpha$ (see supplementary information for details about these parameters).
+Assumptions about rationality may change depending on context and we therefore used the data from experiment 1 to specify $\alpha$ (see Supplementary Material available online for details about these parameters).
 
-The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}C - see supplementary information for additional details and a worked example of how predictions were generated).
-In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter to account for responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (Experiment 3).
-Including the noise parameter greatly improved the model fit to the data (see supplementary information for details).
-We did not pre-register the inclusion of a noise parameter for Experiment 3 but did so for all subsequent experiments.
+The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}c - see Supplementary Material available online for additional details and a worked example of how predictions were generated).
+In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter, which can be thought of as reflecting the cost that comes with handling and integrating multiple information sources.
+Technically it estimates the proportion of responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (experiment 3).
+Including the noise parameter greatly improved the model fit to the data (see Supplementary Material available online for details).
+We did not pre-register the inclusion of a noise parameter for experiment 3 but did so for all subsequent experiments.
+
+## Experiment 3
+
+### Methods
+
 ```{r ex3 GLMM, cache=F}
@@
 
-In Experiment 3, we combined the procedures of Experiment 1 and 2A or 2B.
-The test setup was identical to Experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}C).
+In experiment 3, we combined the procedures of experiment 1 and 2A or 2B.
+The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}c).
 We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).
+
+### Results
+
 Participants distinguished between congruent and incongruent trials when the speaker remained the same, as evidenced by the fit of a generalized linear mixed effects model (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "Results from Experiment 3 and 4 for adults.
-(A) Data and model predictions by condition for Experiment 3.
+```{r fig3, include = T, fig.align = "center", fig.cap = "Results from experiment 3 and 4 for adults.
+Data and model predictions by condition for experiment 3 (a).
 Transparent dots show data from individual participants, diamonds represent condition means.
-(B) Correlation between model predictions and data in Experiment 3, (C) between data in Experiment 3 and data for the strong prior manipulation in Experiment 4 (direct replication) and (D) between model predictions and data in Experiment 4.
+Correlation between model predictions and data in Experiment 3 (b), between data in Experiment 3 and the direct replication in experiment 4 (c) and between model predictions and data in experiment 4 (d).
 Coefficients and p-values are based on Pearson correlation statistics.
-Error bars represent 95\\% HDIs." , out.width="400px"}
+Error bars represent 95\\% HDIs." , out.width="100%"}
 
@@
 
-Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig \ref{fig:fig3}B).
+Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig \ref{fig:fig3}b).
 To test whether participants in fact balanced both information sources, we compared the pragmatics model to two alternative models: the *flat prior model*, which ignores common ground information and the *prior only model*, which ignores utterance information.
@@
 The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
-This value was substantially lower for the pragmatics model compared to the alternative models (see supplementary information), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
+This value was substantially lower for the pragmatics model compared to the alternative models (see Supplementary Material available online), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
 Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.
 
-### Replication and extension to different levels of common ground information (Experiment 4)
+## Experiment 4
+
+### Methods
 
@@
 
-To test if our model makes accurate predictions for different combinations, we first replicated and then extended the results of Experiment 3 to a broader range of experimental conditions.
-Specifically, we manipulated the strength of the common ground information (strong, medium and weak manipulation) by changing the way the speaker interacted with the objects prior to the request We ran a total of 20 conditions, including a direct replication of Experiment 3 (see Fig \ref{fig:fig3}C).
+To test if our model makes accurate predictions for different combinations, we first replicated and then extended the results of experiment 3 to a broader range of experimental conditions.
+Specifically, we manipulated the strength of the common ground information (3 levels - strong, medium and weak - for preference and 2 levels - strong and medium - for novelty) by changing the way the speaker interacted with the objects prior to the request.
+The procedural details and statistical analysis for these these manipulations are described in detail in the Supplementary Material available online.
+For experiment 4, we paired each level of prior strength manipulation with the informativeness inference in the same way as in experiment 3.
+This resulted in a total of 20 conditions, for which we generated a priori model predictions in the same way as in experiment 3.
+The strong prior manipulation in experiment 4 was a direct replication of experiment 3 (see Fig \ref{fig:fig3}c).
+Each participant was randomly assigned to a common ground manipulation and a level of prior strength and completed eight trials in total, two in each unique condition in that combination.
 
-Model predictions from the pragmatics model were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}D).
-We evaluated model fit for the same models as in Experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to Experiment 3 and again lower compared to the alternative models (see supplementary information).
+### Results
 
-## Do children integrate contextual information?
+GLMM results for experiment 4 can be found in the Supplementary Material available online.
+Here we focus on the analysis based on the probabilistic models.
+Model predictions from the pragmatics model were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d).
+We evaluated model fit for the same models as in experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
+The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (see Supplementary Material available online).
+
+# Study 2: Children
 
@@
 When does this integration emerge developmentally?
-While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described in detail nor tested.
+While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described nor tested in detail.
 Here we provide an explanation in the form of our pragmatics model and test if it is able to capture children’s word learning.
@@
 As a starting point, our model assumes developmental continuity in the integration process itself, though this assumption could be called into question by a poor model fit.
-
-### Inferences based on utterance and common ground information (Experiment 5 and 6)
-
 The study for children followed the same general pattern as the one for adults.
 We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance (informativeness) and common ground (preference) information in isolation when making pragmatic inferences.
-We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition\footnote{For Experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.}.
+We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; @frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition.
+
+## Participants
+
+Children were recruited from the floor of the Children’s Discovery Museum in San Jose, California, USA.
+Parents gave informed consent and provided demographic information.
+Each child contributed data to only one experiment.
+We collected data from a total of 243 children between 3.0 and 5.0 years of age.
+We excluded 15 children due to less than 75% of reported exposure to English, five because they responded incorrectly on 2/2 training trials, three because of equipment malfunction, and two because they quit before half of the test trials were completed.
+The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in experiment 7.
+For experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.
+Sample sizes in all experiments were chosen to yield at least 80 data points in each cell for each age group.
+
+## Materials
+
+Experiments were implemented in the same general way as for adults.
+Children were guided through the games by an experimenter and responded by touching objects on the screen of an iPad tablet [@frank2016using].
+
+## Experiment 5
+
+### Methods
 
@@
 
-Experiment 5 was analogous to Experiment 1 for adults.
+Experiment 5 for children was modeled after @frank2014inferring.
+Instead of on tables, objects were presented as hanging in trees (to facilitate showing points to distinct locations).
+After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
+Next, the trees and the objects in them disappeared and new trees replaced them.
+The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced).
+While facing straight, the animal first said “Here are some more trees” and then asked the child to pick the tree with the object that corresponded to the novel word (“Which of these trees has a [non-word]?”).
+Children received six trials in a single test condition.
+
+### Results
+
 To compare children’s performance to chance level, we binned age by year.
@@
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "Results from Experiment 5 and 6 for children.
+```{r fig4, include = T, fig.align = "center", fig.cap = "Results from experiment 5 and 6 for children.
 For preference, control refers to to the different speaker condition (see Fig.
@@
 Transparent dots show data from individual participants, regression lines show fitted linear models with 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="300px"}
+Dashed line indicates performance expected by chance.", out.width="60%"}
 knitr::include_graphics("./figures/fig4.png")
@@
 
-In Experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
+## Experiment 6
+
+### Methods
+
+In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
 We tested children with the novelty as well as the preference manipulation but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
 Since our focus was on how children selectively integrate the two sources of information, we therefore dropped this manipulation and focused on preference for the remainder of the study.
+The procedure for children was identical to the preference manipulation for adults.
+Children received eight trials, four with the same and four with a different animal returning.
 
-For preference, four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`).
+### Results
+
+Four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`).
 However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
@@
 
-### Developmental model predictions evaluated against new data (Experiment 7)
+## Modelling information integration in children
 
-We used the measurements from Experiment 5 and 6 to specify the strength of informativity, $\alpha$, and common ground in the pragmatics model.
-Instead of inferring a single value we inferred the intercept and slope for each parameter that best described the developmental trajectory in the data of Experiment 5 and 6.
+Model predictions for children were generated using the same model described above for adults.
+However, to incorporate developmental change in the model, we allowed the rationality parameter $\alpha$ and the prior distribution over objects to change with age.
+That is, instead of a single value, we inferred the intercept and slope for each parameter that best described the developmental trajectory in the data of experiment 5 and 6.
 These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions.
-As for adults, all models included a noise parameter, which was estimated based on the data.
+As for adults, all models included a noise parameter, which was estimated based on the data of experiment 7.
+
+## Experiment 7
+
+### Methods
 
@@
 
-In Experiment 7, we combined the procedures of Experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}C).
+In experiment 7, we combined the procedures of experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}c).
+We again inserted the preference manipulation into the setup of experiment 5.
+After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
+Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
+Next, the animal disappeared and either the same or a different animal returned.
+The rest of the trial was identical to the label and request phase of experiment 5.
+Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
+
+### Results
+
 Children’s propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
@@
 
-Our modeling results suggest that children flexibly integrate both common ground and informativity information, and that this integration process is accurately captured by the pragmatics model at least for four-year-olds.
+Analyses comparing the model predictions from the probabilistic model to the data suggest that children flexibly integrate both common ground and informativity information.
+Furthermore, this integration process is accurately captured by the pragmatics model at least for four-year-olds.
 For the correlational analysis, we binned model predictions and data by year.
-There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig \ref{fig:fig5}B).
+There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig \ref{fig:fig5}b).
 One of the reasons for the latter was the low variation between conditions.
@@
 As with adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see supplementary information).
+The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see Supplementary Material available online).
 
 The high level of inferred noise moved the model predictions for children in all conditions close to chance level.
-We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see supplementary information, see Fig \ref{fig:fig5}A).
+We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see Supplementary Material available online and Fig \ref{fig:fig5}a).
 This analysis was not pre-registered.
@@
 In each case, the pragmatics model provided a better fit compared to the alternative models (flat prior: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; prior only: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+The developmental noise parameter for the pragmatics model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig.
+S13 in Supplementary Material available online).
 
-```{r fig5, include = T, fig.align = "center", fig.cap = "Results from Experiment 7 for children.
-(A) Model predictions and data across age in the four conditions.
-Colored lines show predictions from the pragmatics model with different noise parameters.
-Transparent black dots show data from individual participants and black lines show conditional means of the data.
-(B) Correlation between model predictions (with noise parameter) and condition means binned by year.
+```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 7 for children.
+Model predictions and data across age in the four conditions (a).
+Transparent black dots show data from individual participants and black lines show conditional means of the data with 95\\% CI.
+Black diamonds show the mean of the data for age bins by year and error bars show 95\\% CIs.
+Correlation between model predictions (with noise parameter) and condition means binned by year (b).
 Coefficients and p-values are based on Pearson correlation statistic.
-Error bars and shaded regions represent 95\\% HDIs.", out.width = "300px"}
+Error bars and shaded regions represent 95\\% HDIs.
+For 4-year-olds, two conditions yielded the same data means and model predicitons and are thus plotted on top of each other.", out.width = "80%"}
 knitr::include_graphics("./figures/fig5.png")
@@
 Here we used a Bayesian pragmatics model to formalize this integration process.
-We studied how utterance-level (Gricean expectations) about informative communication are integrated with common ground information that follows from prior interactions with the speaker.
+We studied how utterance-level about informative communication are integrated with common ground information.
 Adults’ and children’s learning was best predicted by a model in which both sources of information traded-off flexibly.
@@
 Our model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
-But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (Experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
+But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
 
@@
 The real learning environment is far richer than what we captured in our experimental design, however.
-For example, in addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to meaning [@clark1973s; @abend2017bootstrapping; @gleitman1990structural].
+For example, in addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to meaning [@clark1973s; @gleitman1990structural].
 Across development, children learn to recruit these different sources of information and integrate them.
@@
 Furthermore, we took a first step towards integrating developmental change into this theoretical framework.
-
-# Methods
-
-The study was approved by the Stanford Institutional Review Board (protocol no.
-19960).
-All experimental procedures, sample sizes and statistical analysis were pre-registered (https://osf.io/u7kxe/).
-Experimental stimuli, data files and analysis scripts are freely available in an online repository (https://github.com/manuelbohn/mcc).
-
-## Participants
-
-Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9.
-Each participant contributed data to only one experiment.
-Experiment 1 and each manipulation of Experiment 2 had N = 40 participants.
-Sample size in Experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
-*N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations.
-Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.
-
-Children were recruited from the floor of the Children’s Discovery Museum in San Jose, California, USA.
-Parents gave informed consent and provided demographic information.
-Each child contributed data to only one experiment.
-We collected data from a total of 243 children between 3.0 and 5.0 years of age.
-We excluded 15 children due to less than 75% of reported exposure to English, five because they responded incorrectly on 2/2 training trials, three because of equipment malfunction, and two because they quit before half of the test trials were completed.
-The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in Experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in Experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in Experiment 7.
-
-## Materials
-
-All experiments were framed as games in which participants would learn words from animals.
-They were implemented in HTML/JavaScript as a website.
-Adults were directed to the website via MTurk and responded by clicking objects.
-Children were guided through the game by an experimenter and responded by touching objects on the screen of an iPad tablet [@frank2016using].
-For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests.
-All experiments started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball).
-Subsequent test trials in each condition were presented in a random order.
-
-The setup of Experiment 1 for adults is shown in Fig \ref{fig:fig1}A.
-In the beginning of each trial, the animal introduced themselves (e.g.
-“Hi, I’m Dog”) and then turned towards the table with the two objects.
-The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”).
-In the test condition, there was one object on the other table, whereas in the control condition, there were two.
-In the control condition, no inference was possible based on the speaker’s turning.
-The “correct” object in the control condition was randomly chosen from the two objects on the table.
-Technically, this condition did not control for any alternative explanations and we therefore did not run it for children (see below).
-Participants received six trials, three per condition.
-
-The setup for Experiment 2 is shown in Fig \ref{fig:fig1}B.
-In the preference manipulation, the animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
-Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
-This procedure was the strong preference manipulation.
-In the medium version, the animal only expressed preference and did so in a more subtle way (simply saying: “Oh, wow”).
-
-In the novelty manipulation one of the tables was initially empty.
-The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
-After shortly disappearing, the same animal repeated the sequence above.
-When the animal left a second time, a new object appeared on the empty table.
-Next, either the same or a different animal returned and requested an object.
-This corresponded to the strong manipulation.
-For the medium manipulation, the animal turned to each table only once before the new object appeared.
-In the weak manipulation, the animal only commented on the present object once and never turned to the empty table.
-Participants always received six trials, three with the same and three with the different speaker.
-
-For Experiment 3 and 4 we inserted the common ground manipulation before the request in the setup of Experiment 1 (Fig \ref{fig:fig1}C).
-For example, the animal turned to the table with one object and expressed that they liked object A, then turned to the other table and express that they did not like object B.
-Next, after quickly disappearing, the animal reappeared, turned to the table with two objects and make a request.
-To make it clear, which of the objects the speaker commented on while being turned to the table with the two objects during the common ground manipulation, the object was temporarily enlarged.
-Participants completed eight trials for one of the common ground manipulations with two trials per condition (same/different speaker x congruent/incongruent).
-
-Experiment 5 for children was modeled after @frank2014inferring.
-Instead of on tables, objects were presented as hanging in trees (to facilitate showing points to distinct locations).
-After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
-Next, the trees and the objects in them disappeared and new trees replaced them.
-The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced).
-While facing straight, the animal first said “Here are some more trees” and then asked the child to pick the tree with the object that corresponded to the novel word (“Which of these trees has a [non-word]?”).
-Children received six trials in a single test condition.
-
-Experiment 2 for children was identical to the strong preference manipulation for adults. Children received eight trials, four with the same and four with a different animal returning.
-
-In Experiment 3 for children, we again inserted the preference manipulation into the setup of Experiment 1.
-After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
-Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
-Next, the animal disappeared and either the same or a different animal returned.
-The rest of the trial was identical to the label and request phase of Experiment 1.
-Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
-
-## Analysis
-
-All analyses were run in R [@R-base].
-All p-values are based on two sided analysis.
-Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests.
-Frequentist GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
-Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the r package `rwebppl` [@R-rwebppl].
-Bayes Factors for model comparisons were based on marginal likelihoods of each model given the data.
-Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the supplementary information and the online repository.
 
@@
 
-# Acknowledgements
+# Author Contributions
 
-MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
-749229.
-MCF was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+M.
+Bohn and M.C.
+Frank conceptualized the study, M.
+Merrick collected the data, M.
+Bohn and M.H.
+Tessler analyzed the data, M.
+Bohn, M.
+H.
+Tessler and M.C.
+Frank wrote the manuscript, all authors approved the final version of the manuscript.
+
+# Acknowledgments
+
 We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
 
-# Author Contributions
+# Funding
 
-MB and MCF conceptualized the study, MM collected the data, MB and MHT analyzed the data, MB, MHT and MCF wrote the manuscript, all authors approved the final version of the manuscript.
-
-# Competing Interests
-
-The authors declare no competing interests.
+M.
+Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+M.
+C.
+Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.

### 2020-03-10 papers/full_paper/Supplementary_information.Rmd
update paper after revision

@@
   separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic")%>%
+  mutate(model="integration")%>%
   group_by(model,common_ground_manipulation,speaker,alignment)%>%
@@
 Figure\ref{fig:plotex3} shows the result in each of the eight conditions of Experiment 3.
-Results are plotted from  The plot also shows model predictions from the pragmatics model (including the noise parameter - see below).
+Results are plotted from  The plot also shows model predictions from the integration model (including the noise parameter - see below).
 
@@
 ```{r plotmodelpredex7, fig.cap = "Model predictions and data for Experiment 7 with children.
-Colored lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants and the black line with grey CI shows the smoothed conditional mean of the data in each condition.", fig.align = "center", out.width="100%"}
+Colored lines show model predictions with 95\\% HDIs, transparent dots show data from individual participants and the black line with grey CI shows the smoothed conditional mean of the data in each condition.
+Black diamonds with error bars show mean for age bined by year with 95\\% HDIs.", fig.align = "center", out.width="100%"}
 child_model_predictions <- readRDS("../../stats/saves/child_ex3_model_predictions.rds")%>%
@@
 
+p_child_ex3_data_binned <- child_ex3_data %>%
+  mutate(age = as.character(age_bin), 
+         model = "Data",
+         speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))%>%
+  group_by(model,age, alignment, speaker) %>%
+  summarize(k = sum(correct_inf), n = n())%>%
+  ungroup() %>%
+  mutate(a = 1 + k,
+         b = 1 + n - k,
+         mean = (a-1)/(a+b-2),
+         ci_lower  = qbeta(.025, a, b),
+         ci_upper = qbeta(.975, a, b))%>%
+  select(-a,-b,-n,-k)
+
 ggplot(child_model_predictions)+
@@
   geom_smooth(data = p_child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "glm",method.args = list(family = "binomial"),  se = T,  alpha = .5)+
-  #geom_hline(yintercept = 0.5, lty=2)+
+geom_pointrange(data = p_child_ex3_data_binned, aes(x = as.numeric(age)+0.5, y = mean, ymin = ci_lower, ymax = ci_upper), size = .6,  position = position_dodge(width = .5), pch = 5)+
   labs(y="Proportion more informative", x = "Age")+
@@
   scale_color_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     breaks=c("integration","integration_noise","integration_developmental_noise"),
                      values= c("#00afaf","#af6300","#6c71c4"))+
   scale_fill_manual(name="Model",
-                     breaks=c("pragmatic","pragmatic_noise","pragmatic_developmental_noise"),
+                     breaks=c("integration","integration_noise","integration_developmental_noise"),
                      values= c("#00afaf","#af6300","#6c71c4"))
@@
 Figure \ref{fig:plotmodelpredex7} shows the results for each condition plotted by age as a continuous variable.
-The same figure also shows model predictions from the pragmatics model with different noise parameters (see below).
+The same figure also shows model predictions from the integration model with different noise parameters (see below).
 
@@
 
-## Pragmatics model
+## Integration model
 
@@
 
-In this section, we work through a toy numerical example for how model predictions were generated for the pragmatics model.
+In this section, we work through a toy numerical example for how model predictions were generated for the integration model.
 The prediction will correspond to the parameter free model described above (excluding the noise parameter).
@@
 
-To conclude the example, according to the parameter free pragmatics model, the probability that $L_1$ thinks that $S_1$ is referring to a yellow-ish object when producing $u_3$ is 0.91.
+To conclude the example, according to the parameter free integration model, the probability that $L_1$ thinks that $S_1$ is referring to a yellow-ish object when producing $u_3$ is 0.91.
 Based on this model we thus expected that, on average, participants would select the yellow-ish object in 91% of cases in a condition with the prior distribution specified above.
 
-## Prior only model
-
-The prior only model ignored the information about the intended referent that was expressed by the utterance and instead only focused on common ground manipulation.
+## No informativeness model
+
+The No informativeness model ignored the information about the intended referent that was expressed by the utterance and instead only focused on common ground manipulation.
 The only information available to $L_1$ is the prior distribution over referents.
@@
 That is, the probability of the referent given the utterance is determined by the prior probability of the referent for a particular speaker.
-The prior distributions were set in the same way as for the pragmatics model.
-
-## Flat prior model
-
-This model was identical in structure to the pragmatics model with the exception that the prior distribution did not correspond to the measurements from Experiment 2 and did not vary with speaker identity.
+The prior distributions were set in the same way as for the integration model.
+
+## No common ground model
+
+This model was identical in structure to the integration model with the exception that the prior distribution did not correspond to the measurements from Experiment 2 and did not vary with speaker identity.
 That is, regardless of common ground manipulation and speaker identity the prior distribution was always uniform (i.e.
 [0.33,0.33,0.33]).
-The speaker optimality parameter $\alpha$ was set in the same way as in the pragmatics model.
+The speaker optimality parameter $\alpha$ was set in the same way as in the integration model.
 
@@
 For adults, we used the data from Experiment 1 to infer the value of $\alpha$.
-That is, we inferred which value of $\alpha$ would generate model predictions for the pragmatics model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
+That is, we inferred which value of $\alpha$ would generate model predictions for the integration model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
 This value for $\alpha$ was then used in Experiment 3 and 4.
@@
 Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
-As for adults, this was done via the pragmatics model with equal prior probability for each object.
+As for adults, this was done via the integration model with equal prior probability for each object.
 In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the overall intercept and adding the slope times the child's age (with age anchored at 0).
@@
 We did not pre-register the inclusion of the noise parameter for Experiment 3, but did so for all subsequent experiments for which we did model comparisons (4 and 7).
-The first row in Table \ref{tab:ex3_comp} compares the pragmatics model with noise parameter to the model without the noise parameter.
+The first row in Table \ref{tab:ex3_comp} compares the integration model with noise parameter to the model without the noise parameter.
 This comparison shows that including the noise parameter greatly improves model fit.
@@
   separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior_noise")%>%
+  mutate(model="no_common_ground_noise")%>%
   group_by(model,common_ground_manipulation,speaker,alignment)%>%
@@
   separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only_noise")%>%
+  mutate(model="no_informativeness_noise")%>%
   group_by(model,common_ground_manipulation,speaker,alignment)%>%
@@
   separate(Parameter, into = c("common_ground_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic_noise")%>%
+  mutate(model="integration_noise")%>%
   group_by(model,common_ground_manipulation,speaker,alignment)%>%
@@
   )%>%
-  mutate(model =  case_when(model == "pragmatic_noise" ~ "Pragmatics",
-                            model == "prior_only_noise" ~ "Prior only",
-                            model == "flat_prior_noise" ~ "Flat prior"
+  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
+                            model == "no_informativeness_noise" ~ "No informativeness",
+                            model == "no_common_ground_noise" ~ "No common ground"
                             ))
@@
 ```{r ex3_comp,results = "asis"}
-log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")
+log_like_pragmatic_ex3 <- readRDS("../../stats/saves/ex3_pragm_model_loglike.rds")%>%
+  mutate(model = "integration")
 
 ex3_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds")%>%
-  mutate(model = "pragmatic_noise")%>%
+  mutate(model = "integration_noise")%>%
   group_by(model)%>%
@@
 ex3_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds")%>%
-  mutate(model = "prior_only_noise")%>%
+  mutate(model = "no_informativeness_noise")%>%
   group_by(model)%>%
@@
 ex3_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds")%>%
-  mutate(model = "flat_prior_noise")%>%
+  mutate(model = "no_common_ground_noise")%>%
   group_by(model)%>%
@@
 ) %>% spread(model, logP) %>%
-  mutate("pragmatic_noise > pragmatic" = exp(pragmatic_noise - pragmatic),
-         "pragmatic_noise > prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
-         "pragmatic_noise > flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
-         "prior_only_noise > flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
-  select(-pragmatic,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
+  mutate("integration_noise > integration" = exp(integration_noise - integration),
+         "integration_noise > no_informativeness_noise" = exp(integration_noise - no_informativeness_noise),
+         "integration_noise > no_common_ground_noise" = exp(integration_noise - no_common_ground_noise),
+         "no_informativeness_noise > no_common_ground_noise" = exp(no_informativeness_noise - no_common_ground_noise)) %>%
+  select(-integration,-integration_noise, -no_informativeness_noise, -no_common_ground_noise)%>%
   gather(Comparison, BF)%>%
@@
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Pragmatics"),
+  mutate(Model = "Integration"),
   readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Prior only"),
+  mutate(Model = "No informativeness"),
   readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Flat prior")
+  mutate(Model = "No common ground")
   )
@@
   xlim(0,1)+
-  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                     values= c("#b58900","#6c71c4","#859900"))+
-  scale_fill_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                     values= c("#b58900","#6c71c4","#859900"))
@@
 Consequently, a model that makes predictions that are closer to the data is likely to have a lower noise parameter.
-The results corroborate the model comparison by showing that the pragmatics model has the lowest noise parameter.
+The results corroborate the model comparison by showing that the integration model has the lowest noise parameter.
 
@@
   separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="flat_prior_noise")%>%
+  mutate(model="no_common_ground")%>%
   group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
@@
   separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="prior_only_noise")%>%
+  mutate(model="no_informativeness")%>%
   group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
@@
   separate(Parameter, into = c("common_ground_manipulation","prior_manipulation","speaker", "alignment"), sep="/")%>%
-  mutate(model="pragmatic_noise")%>%
+  mutate(model="integration_noise")%>%
   group_by(model,common_ground_manipulation,prior_manipulation,speaker,alignment)%>%
@@
   )%>%
-  mutate(model =  case_when(model == "pragmatic_noise" ~ "Pragmatics",
-                            model == "prior_only_noise" ~ "Prior only",
-                            model == "flat_prior_noise" ~ "Flat prior"
+  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
+                            model == "no_informativeness" ~ "No informativeness",
+                            model == "no_common_ground" ~ "No common ground"
                             ))
@@
 ex4_pragm_model_noise_loglike <- readRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds")%>%
-  mutate(model = "pragmatic_noise")%>%
+  mutate(model = "integration_noise")%>%
   group_by(model)%>%
@@
 ex4_prior_only_model_noise_loglike <- readRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds")%>%
-  mutate(model = "prior_only_noise")%>%
+  mutate(model = "no_informativeness")%>%
   group_by(model)%>%
@@
 ex4_flat_prior_model_noise_loglike <- readRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds")%>%
-  mutate(model = "flat_prior_noise")%>%
+  mutate(model = "no_common_ground")%>%
   group_by(model)%>%
@@
 ) %>% spread(model, logP) %>%
-  mutate("Pragmatics > Prior only" = exp(pragmatic_noise - prior_only_noise),
-         "Pragmatics > Flat prior" = exp(pragmatic_noise - flat_prior_noise),
-         "Flat prior > Prior only" = exp(flat_prior_noise - prior_only_noise)) %>%
-  select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)%>%
+  mutate("Integration > No informativeness" = exp(integration_noise - no_informativeness),
+         "Integration > No common ground" = exp(integration_noise - no_common_ground),
+         "No common ground > No informativeness" = exp(no_common_ground - no_informativeness)) %>%
+  select(-integration_noise, -no_common_ground, -no_informativeness)%>%
   gather(Comparison, BF)%>%
@@
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Pragmatics"),
+  mutate(Model = "Integration"),
   readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Prior only"),
+  mutate(Model = "No informativeness"),
   readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Flat prior")
+  mutate(Model = "No common ground")
   )
@@
 Figure \ref{fig:ex4noise} shows the posterior distribution of the noise parameter for each model in Experiment 4.
-All results suggest that the pragmatics model captures the structure in the data better compared to the alternative models considered.
+All results suggest that the integration model captures the structure in the data better compared to the alternative models considered.
 
@@
 We added the additional model comparisons because the noise parameter was relatively high.
-The additional model comparisons allow us to see if the pragmatics model provides a better fit when more emphasis is put on the model structure itself (see Figure \ref{fig:plotmodelpredex7} for model predictions from the models with different noise parameters).
+The additional model comparisons allow us to see if the integration model provides a better fit when more emphasis is put on the model structure itself (see Figure \ref{fig:plotmodelpredex7} for model predictions from the models with different noise parameters).
 The results show that this was the case.
@@
 Noise was therefore a function of the child's age.
-Table \ref{tab:child_prag_bf} shows model comparisons for the pragmatics models using different noise parameters.
+Table \ref{tab:child_prag_bf} shows model comparisons for the integration models using different noise parameters.
 This shows that including a noise parameter improves model fit but that the type of noise parameter does not make much of a difference.
@@
   child_ex3_pragmatic_models_bf
-  , caption = "Model comparisons for pragmatics models in Experiment 7"
+  , caption = "Model comparisons for integration models in Experiment 7"
   , note = "BF = Bayes Factor"
@@
 Table \ref{tab:child_bf} shows results for model comparison for the different types of noise parameters.
-In all cases, the pragmatics model provides a substantially better fit to the data compared to the alternative models.
+In all cases, the integration model provides a substantially better fit to the data compared to the alternative models.
 
@@
   spread(model, logP) %>%
-  mutate("Pragmatics > Flat P." = formatC(exp(pragmatic - flat_prior),2),
-         "Pragmatics > P. only" = formatC(exp(pragmatic - prior_only),2),
-         "Flat P. > P. only" = formatC(exp(flat_prior - prior_only),2)) %>%
+  mutate("Integration > No common ground" = formatC(exp(pragmatic - flat_prior),2),
+         "Integration > No informativeness" = formatC(exp(pragmatic - prior_only),2),
+         "No common ground > No informativeness" = formatC(exp(flat_prior - prior_only),2)) %>%
   select(-pragmatic,-flat_prior, -prior_only)
@@
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Pragmatics"),
+  mutate(Model = "Integration"),
   readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Prior only"),
+  mutate(Model = "No informativeness"),
   readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "Flat prior")
+  mutate(Model = "No common ground")
   )
@@
   age = rep(seq(0,2, by = 0.05),3),
-  Model = c(rep("Pragmatics",41),
-            rep("Flat prior",41),
-            rep("Prior only",41)),
+  Model = c(rep("Integration",41),
+            rep("No common ground",41),
+            rep("No informativeness",41)),
   int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
@@
   theme_few()+
-  scale_color_manual(breaks=c("Pragmatics","Prior only","Flat prior"),
+  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                     values= c("#b58900","#6c71c4","#859900"))
@@
 Figure \ref{fig:childnoise} shows the different types of noise parameters for the each model.
-Figure \ref{fig:childnoise}A shows that the pragmatics model has the lowest estimated level of noise of all the models considered.
-Figure \ref{fig:childnoise}B shows that the the pragmatics model has the lowest level of estimated noise across the entire age range.
-It also shows that noise decreases with age for the pragmatics model, suggesting that older children behaved more in line with model predictions compared to younger children.
+Figure \ref{fig:childnoise}A shows that the integration model has the lowest estimated level of noise of all the models considered.
+Figure \ref{fig:childnoise}B shows that the the integration model has the lowest level of estimated noise across the entire age range.
+It also shows that noise decreases with age for the integration model, suggesting that older children behaved more in line with model predictions compared to younger children.
 
@@
 Across noise parameters, model predictions and data are closest aligned (i.e.
-closest to the dotted line) for the pragmatics model, thereby corroborating the conclusions drawn based on the model comparison and the evaluation of the noise parameters.
+closest to the dotted line) for the integration model, thereby corroborating the conclusions drawn based on the model comparison and the evaluation of the noise parameters.
 Correlations are also higher for 4yo compared to 3yo, supporting the interpretation based on the developmental noise parameter that children behaved more in line with the model predictions as they got older.
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Flat prior",
+#   mutate(model = "No common ground",
 #          noise = "Noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Prior only",
+#   mutate(model = "No informativeness",
 #          noise = "Noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Flat prior",
+#   mutate(model = "No common ground",
 #          noise = "Dev. noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Prior only",
+#   mutate(model = "No informativeness",
 #          noise = "Dev. noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Prior only",
+#   mutate(model = "No informativeness",
 #          noise = "Param. free")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "Flat prior",
+#   mutate(model = "No common ground",
 #          noise = "Param. free")%>%
@@
 
-p_child_ex3_data <- child_ex3_data %>%
-  mutate(age = as.character(age_bin), 
-         model = "Data")%>%
-  group_by(model,age, alignment, speaker) %>%
-  summarize(k = sum(correct_inf), n = n())%>%
-  ungroup() %>%
-  mutate(a = 1 + k,
-         b = 1 + n - k,
-         mean = (a-1)/(a+b-2),
-         ci_lower  = qbeta(.025, a, b),
-         ci_upper = qbeta(.975, a, b))%>%
-  select(-a,-b,-n,-k)
-
 p_child_cor<- readRDS("../../stats/saves/child_all_models_cor.rds") %>%
@@
   ungroup()%>%
-  mutate(data_mean = rep(p_child_ex3_data%>%pull(mean),9),
-         data_ci_upper = rep(p_child_ex3_data%>%pull(ci_upper),9),
-         data_ci_lower = rep(p_child_ex3_data%>%pull(ci_lower),9))
+  mutate(model = recode(model,
+                          "Pragmatic" = "Integration",
+                          "Flat prior" = "No common ground",
+                          "Prior only" = "No informativeness"),
+         data_mean = rep(p_child_ex3_data_binned%>%pull(mean),9),
+         data_ci_upper = rep(p_child_ex3_data_binned%>%pull(ci_upper),9),
+         data_ci_lower = rep(p_child_ex3_data_binned%>%pull(ci_lower),9))
+
 ggplot(p_child_cor, aes(x = mean, y = data_mean, col = age)) +
@@
 We also ran the entire analysis with this alternative approach and found no major changes in the results.
-In all cases, the pragmatics model outperformed the two alternative models, both for children as well as for adults.
+In all cases, the integration model outperformed the two alternative models, both for children as well as for adults.
 Interestingly, for adults but not for children, using a uniform prior for $L_0$ yielded a lower estimate for the noise parameter in Experiment 3 and 4.

### 2020-03-10 papers/full_paper/manuscript.Rmd
update paper after revision

@@
 We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance and common ground information should be integrated.
-We consider three models that make different assumptions about the integration process: In the pragmatics model, the two information sources are integrated with one another; according to the flat prior model, participants focus only on the utterance information and in the prior only model, only common ground information is considered.
+We consider three models that make different assumptions about the integration process: In the *integration model*, the two information sources are integrated with one another.
+The other two models are lesion models that assume that participants focus on one type of information and disregard the other whenever they are presented together.
+According to the *no common ground* model, participants focus only on the utterance information and in the *no informativeness* model, only common ground information is considered.
 We compare predictions from these models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).
@@
 Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.
-Sample sizes in all adult experiments were chosen to yield at least 120 datapoints per cell.
+Sample sizes in all adult experiments were chosen to yield at least 120 data points per cell.
 All studies were approved by the Stanford Institutional Review Board (protocol no.
@@
 We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model.
-The Rational Speech Act (RSA) model architecture introduced by [@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
+The Rational Speech Act (RSA) model architecture introduced by Frank and Goodman [-@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
 The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents P(r) - with his generative model of how the utterance was produced: a speaker trying to convey information to him.
@@
   round(digits = 2)
+
+ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  round(digits = 2)
+
+ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  round(digits = 2)
 ```
@@
 The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}c).
+This combination resulted in two ways in which the two information sources could be aligned with one another.
+In the congruent condition, the object that was the more informative referent was also the one that was preferred by or new to the speaker.
+In the incongruent condition, the other object was the one that was preferred by or new to the speaker.
+Taken together, there were 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions in experiment 3.
+For each of these eight conditions, we generated model predictions using the modelling framework introduced above.
+The test hypothesis about how information is integrated we compared the three models introduced in the introduction: The *integration model* in which both information sources are flexibly combined, the *no common ground model* that focused only on utterance-level information and the the *no informativeness model* that focused only on common ground information.
+
+Participants completed eight trials for one of the common ground manipulations with two trials per condition (same/different speaker x congruent/incongruent).
+Conditions were presented in a random order.
 We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).
@@
 
-Participants distinguished between congruent and incongruent trials when the speaker remained the same, as evidenced by the fit of a generalized linear mixed effects model (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
+As a first step, we used a GLMM to test whether participants were sensitive to the different ways in which information could be aligned.
+We found that participants distinguished between congruent and incongruent trials when the speaker remained the same (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
+Thus, participants were sensitive to the different combinations of manipulations.
 
@@
 
-Participants’ average responses were highly correlated with the model’s predictions in each condition (Fig \ref{fig:fig3}b).
-To test whether participants in fact balanced both information sources, we compared the pragmatics model to two alternative models: the *flat prior model*, which ignores common ground information and the *prior only model*, which ignores utterance information.
-Model fit was considerably better for the pragmatics model compared to the flat prior model (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
-The estimated proportion of random responses according to the pragmatics model was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
-This value was substantially lower for the pragmatics model compared to the alternative models (see Supplementary Material available online), lending additional support to the conclusion that the pragmatics model better captured the behavioral data.
+As a second step, we compared the model predictions to the data.
+Participants’ average responses were highly correlated with the  predictions from the *integration model* in each condition (Fig \ref{fig:fig3}b).
+When comparing model, we found that model fit was considerably better for the* integration model* compared to the *no common ground model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
+
+Finally, we examined the noise parameter for each model.
+The estimated proportion of random responses according to the *integration model* was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
+This parameter was substantially lower for the *integration model* compared to the alternative models (*no common ground model*: `r ex3_flat_prior_model_noise_param%>%pull(mean)` [`r ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex3_prior_only_model_noise_param%>%pull(mean)` [`r ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex3_prior_only_model_noise_param%>%pull(ci_upper)`]), lending additional support to the conclusion that the *integration model* better captured the behavioral data.
 Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.
@@
   select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)
+
 ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
@@
   round(digits = 2)
+
+ex4_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  round(digits = 2)
+
+ex4_prior_only_model_noise_param <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))%>%
+  round(digits = 2)
+
 ```
 
-To test if our model makes accurate predictions for different combinations, we first replicated and then extended the results of experiment 3 to a broader range of experimental conditions.
+To test if the *integration model* makes accurate predictions for different combinations, we first replicated and then extended the results of experiment 3 to a broader range of experimental conditions.
 Specifically, we manipulated the strength of the common ground information (3 levels - strong, medium and weak - for preference and 2 levels - strong and medium - for novelty) by changing the way the speaker interacted with the objects prior to the request.
-The procedural details and statistical analysis for these these manipulations are described in detail in the Supplementary Material available online.
+The procedural details and statistical analysis for these these manipulations are described in the Supplementary Material available online.
 For experiment 4, we paired each level of prior strength manipulation with the informativeness inference in the same way as in experiment 3.
@@
 
+The direct replication of experiment 3 within experiment 4 showed a very close correspondence between the two rounds of data collection (see Fig \ref{fig:fig3}c).
 GLMM results for experiment 4 can be found in the Supplementary Material available online.
 Here we focus on the analysis based on the probabilistic models.
-Model predictions from the pragmatics model were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d).
-We evaluated model fit for the same models as in experiment 3 and found again that the pragmatics model fit the data much better compared to the flat prior (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the prior only model (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (see Supplementary Material available online).
+Model predictions from the *integration model* were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d).
+We evaluated model fit for the same models as in experiment 3 and found again that the *integration model* fit the data much better compared to the *no common ground* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
+The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (*no common ground model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).
 
@@
 While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described nor tested in detail.
-Here we provide an explanation in the form of our pragmatics model and test if it is able to capture children’s word learning.
+Here we provide an explanation in the form of our *integration model* and test if it is able to capture children’s word learning.
 Embedded in the assumptions of the model is the idea that developmental change is change in the strength of the individual inferences, leading to a change in the strength of the integrated inference.
-As a starting point, our model assumes developmental continuity in the integration process itself, though this assumption could be called into question by a poor model fit.
+As a starting point, our model assumes developmental continuity in the integration process itself [@bohn2019pervasive], though this assumption could be called into question by a poor model fit.
 The study for children followed the same general pattern as the one for adults.
@@
 In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
-We tested children with the novelty as well as the preference manipulation but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
-Since our focus was on how children selectively integrate the two sources of information, we therefore dropped this manipulation and focused on preference for the remainder of the study.
+We tested children with the novelty as well as the preference manipulation.
+In both cases, we found that children made the basic inference in that they selected the object that was preferred by or new to the speaker, but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
+This finding contrasts with earlier work [diesendruck2004two].
+However, since our focus was on how children selectively integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.
 The procedure for children was identical to the preference manipulation for adults.
-Children received eight trials, four with the same and four with a different animal returning.
+Children received eight trials, four with the same and four with a different speaker.
 
@@
 Next, the animal disappeared and either the same or a different animal returned.
-The rest of the trial was identical to the label and request phase of experiment 5.
+The rest of the trial was identical to the request phase of experiment 5.
 Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
@@
 
+As a first step, we used a GLMM to test whether children were sensitive to the different ways in which information could be aligned.
 Children’s propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).
@@
             ci_upper = hdi_upper(value))
+
+child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
+child_ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
+  filter(Parameter %in% c("noise"))  %>%
+  summarise(mean = estimate_mode(value), 
+            ci_lower = hdi_lower(value),
+            ci_upper = hdi_upper(value))
+
 ```
 
-Analyses comparing the model predictions from the probabilistic model to the data suggest that children flexibly integrate both common ground and informativity information.
-Furthermore, this integration process is accurately captured by the pragmatics model at least for four-year-olds.
+Analyses comparing the model predictions from the probabilistic models to the data suggest that children flexibly integrate both common ground and informativity information.
+Furthermore, this integration process is accurately captured by the *integration model* at least for four-year-olds.
 For the correlational analysis, we binned model predictions and data by year.
@@
 For the model comparison, we treated age continuously.
-As with adults, we found a much better model fit for the pragmatics model compared to the flat prior (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the prior only model (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The inferred level of noise based on the data for the pragmatics model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered but numerically higher than that of adults (see Supplementary Material available online).
+As with adults, we found a much better model fit for the *integration model* compared to the *no common ground* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the *no informativeness model* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+
+The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (*no common ground model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults.
 
 The high level of inferred noise moved the model predictions for children in all conditions close to chance level.
-We therefore compared two additional sets of models with different parameterizations that emphasized differences between conditions in the model predictions more (see Supplementary Material available online and Fig \ref{fig:fig5}a).
+We therefore compared two additional sets of models with different parameterizations of the noise parameter that emphasized differences between conditions in the model predictions more (see Supplementary Material available online and Fig \ref{fig:fig5}a).
 This analysis was not pre-registered.
 Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age.
-In each case, the pragmatics model provided a better fit compared to the alternative models (flat prior: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; prior only: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The developmental noise parameter for the pragmatics model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig.
+In each case, the *integration model* provided a better fit compared to the alternative models (*no common ground*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; *no informativeness*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+The developmental noise parameter for the integration model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig.
 S13 in Supplementary Material available online).
@@
 But how are different cues integrated during word learning?
-Here we used a Bayesian pragmatics model to formalize this integration process.
-We studied how utterance-level about informative communication are integrated with common ground information.
+Here we used a Bayesian cognitive model to formalize this integration process.
+We studied how utterance-level (Gricean) expectations about informative communication are integrated with common ground information.
 Adults’ and children’s learning was best predicted by a model in which both sources of information traded-off flexibly.
@@
 
-All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing expectations by some ratio.
+All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing information sources by some ratio.
 We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data.
@@
 
-We conceptualized developmental change as age related changes in the propensity to make the individual inferences.
-That is, while the degree to which listeners expect speakers to be informative or follow common ground changes with age, the process by which expectations are integrated remains the same.
-However, other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
-Our model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
+How is information integrated in this context in this context?
+The *integration model* assumes that the informativeness of an utterance depends on the common ground shared between interlocutors.
+That is, the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
+As a consequence, when prior interactions strongly implicate one object as the more likely referent (for example in the preference - same speaker conditions in experiment 3, 4 and 7), the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
+Taken together, this model provides an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
+Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.
+
+The *integration model* also predicted information integration in four-year-olds.
+However, the model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
 But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
+It would therefore be important to follow up with a combination of tasks that produce stronger inferences in younger children.
+
+The primary source of developmental change in our model are age related changes in the propensity to make the individual inferences.
+As they get older, children expect speakers to be more informative and to be more likely to follow common ground, but the process by which the two information sources are integrated at any given age is assumed to be the same.
+The developmental noise model reported for experiment 7 offers a complimentary way to think about developmental change.
+We found that the estimated level of noise for the *integration model* dropped with age.
+That is, while, according to this model, young children's responses were best explained by random guessing, older children responded in line with the model structure.
+One way to interpret this would be to say that handling and integrating the two information sources poses a greater challenge to younger children.
+As soon as the necessary abilities are in place, children flexibly combine the two information sources as described by the *integration model*.
+This points to domain general processes as an additional locus of developmental but also assumes that the integration process itself is stable across age.
+Other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
 
@@
 
+# Declarations of interest
+
+None.
+
 # Author Contributions

### 2020-03-12 papers/full_paper/manuscript.Rmd
revise manuscript

@@
 
-In experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @saylor2009preschoolers].
+In experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers].
 In experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}b, left).
@@
 In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
-We tested children with the novelty as well as the preference manipulation.
-In both cases, we found that children made the basic inference in that they selected the object that was preferred by or new to the speaker, but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
-This finding contrasts with earlier work [diesendruck2004two].
-However, since our focus was on how children selectively integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.
+We tested children only with the preference manipulation\footnote{We initially tested children with the novelty as well as the preference manipulation.
+We found that children made the basic inference in that they selected the object that was preferred by or new to the speaker, but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
+This finding contrasts with earlier work (Diesendruck et al., 2004).
+However, since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study}.
 The procedure for children was identical to the preference manipulation for adults.
@@
 This integration is especially vital in early language learning, and the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive].
-But how are different cues integrated during word learning?
+But how are pragmatic cues integrated during word learning?
 Here we used a Bayesian cognitive model to formalize this integration process.
@@
 That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli.
-Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning].
+Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning; @cohn2018pragmatically; @monroe2017colors].
 
@@
 But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
-It would therefore be important to follow up with a combination of tasks that produce stronger inferences in younger children.
+As a consequence, there was not much variation in three-year-old's responses for the model to explain.
 
-The primary source of developmental change in our model are age related changes in the propensity to make the individual inferences.
+The primary source of developmental change in our model is age related changes in the propensity to make the individual inferences.
 As they get older, children expect speakers to be more informative and to be more likely to follow common ground, but the process by which the two information sources are integrated at any given age is assumed to be the same.
-The developmental noise model reported for experiment 7 offers a complimentary way to think about developmental change.
-We found that the estimated level of noise for the *integration model* dropped with age.
-That is, while, according to this model, young children's responses were best explained by random guessing, older children responded in line with the model structure.
-One way to interpret this would be to say that handling and integrating the two information sources poses a greater challenge to younger children.
-As soon as the necessary abilities are in place, children flexibly combine the two information sources as described by the *integration model*.
-This points to domain general processes as an additional locus of developmental but also assumes that the integration process itself is stable across age.
 Other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
+
+The developmental noise model reported for experiment 7 offers another way to address the question of what changes with development.
+This model estimates a developmental trajectory for the proportion of responses that are better explained by random guessing than by the model structure.
+If such a model would find that model fit is comparable for younger and older children but that the noise parameter through which this fit is achieved decreases with age, we might conclude that cognitive abilities that have to do with task demands are the major locus of change rather than abilities that have to do with integrating information.
+In the developmental noise model in experiment 7, we found that noise decreased with age but, at the same time, that the resulting model fit was substantially worse for younger children.
+However, rather than a difference in how information is integrated, we think that a lack of variation in children's responses is the reason for this poor model fit.
+The strongest evidence for developmental changes in integration would come in a case where younger children showed evidence of above/below-chance judgment in the combined task that was distinct from that predicted by the two above/below-chance component tasks.
+Such a comparison would require more precision (either via more trials or more participants) than our current experiment affords, however.
 
@@
 RSA models allow for the inclusion of semantic information as part of the utterance [@bergen2016pragmatic] and it will be a fruitful avenue for future research to model the integration of linguistic and pragmatic information across development.
-
-More broadly, our work here shows how computational models of language comprehension can be used as powerful tools to explicate and test hypotheses about information integration.
-Furthermore, we took a first step towards integrating developmental change into this theoretical framework.
+To conclude, our work here shows how computational models of language comprehension can be used as powerful tools to explicate and test hypotheses about information integration across development.
 

### 2020-08-07 papers/full_paper/manuscript.Rmd
advance revision

@@
 Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins].
-On the other hand, there is information provided by common ground (the body of knowledge and beliefs shared between interlocutors)[@bohn2018common; @clark1996using; @clark2015common].
+On the other hand, there is information provided by common ground (the body of mutually shared knowledge and beliefs between interlocutors)[@bohn2018common; @clark1996using; @clark2015common].
 Because utterances are embedded in common ground, pragmatic reasoning in context always requires information integration.
@@
 
-Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
-For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @saylor2009preschoolers; @sullivan2019discourse].
+Evidence for the use of common ground\footnote{Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
+Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner;@hanna2003effects; @mozuraitis2015privileged].
+Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested.
+However, most of this work is focused on online perspective taking.
+In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children [@matthews2006effect].
+We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [see also @bohn2018common]} information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
 
-All of these examples, however, highlight children’s use of a single pragmatic information source or cue.
+These examples, however, highlight children’s use of a single pragmatic information source or cue.
 Harnessing multiple – potentially competing – cues poses a separate challenge.
 One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance.
-Much less is known about whether and how children – or even adults – combine these types of information.
-While many theories of pragmatic reasoning presuppose that both information sources are integrated, the nature of their relationship has typically not been specified.
+Much less is known about whether and how children combine these types of information.
+Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers].
+For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see).
+However, the information sources to be integrated in these studies are not all pragmatic in nature.
+Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not their ability to reason about the speaker’s intention in context.
+As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information.
+Thus, while many theories of pragmatic reasoning presuppose that pragmatic information sources are integrated, the nature of their relationship has typically not been specified.
 
@@
 
-The *integration model* also predicted information integration in four-year-olds.
+The *integration model* predicted information integration in four-year-olds.
 However, the model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
@@
 As a consequence, there was not much variation in three-year-old's responses for the model to explain.
+
+We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically.
+As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g.
+in @frank2012predicting].
+Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
+A starting point for explicitly modeling common ground would be the work by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling].
+In their work, they focus on how listeners identify the referent of ambiguous referring expressions.
+Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them.
+In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could easily be combined with one another.
+However, because common ground in our study was established by a shared interaction and not by the online convergence of different perspectives, it would require a different experimental design to test the combined model.
 

### 2020-08-10 papers/full_paper/manuscript.Rmd
advance revision

@@
   - name          : "Manuel Bohn"
-    affiliation   : "1,2"
+    affiliation   : "1,2,3"
     corresponding : yes    # Define only one corresponding author
@@
   - name          : "Michael Henry Tessler"
-    affiliation   : "3"
+    affiliation   : "4"
   - name          : "Megan Merrick"
@@
   - id            : "3"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "4"
     institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
@@
 These examples, however, highlight children’s use of a single pragmatic information source or cue.
-Harnessing multiple – potentially competing – cues poses a separate challenge.
+Harnessing multiple – potentially competing – pragmatic cues poses a separate challenge.
 One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance.
 Much less is known about whether and how children combine these types of information.
-Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers].
+Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @grosse201021; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @ganea2007infants].
 For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see).
 However, the information sources to be integrated in these studies are not all pragmatic in nature.
-Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not their ability to reason about the speaker’s intention in context.
+Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not necessarily their ability to reason about the speaker’s intention in context.
 As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information.
@@
 As a consequence, when prior interactions strongly implicate one object as the more likely referent (for example in the preference - same speaker conditions in experiment 3, 4 and 7), the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
-Taken together, this model provides an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
+Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@brunder1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
 Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.

### 2020-08-13 papers/full_paper/Supplementary_information.Rmd
advance revision

@@
 That is, we inferred which value of $\alpha$ would generate model predictions for the integration model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
+Technically, we used MCMC to compute the posterior distribution for $\alpha$ and took the MAP.
 This value for $\alpha$ was then used in Experiment 3 and 4.
@@
 For children, the speaker optimality parameter changed with age.
-Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
+Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept (MAP values) for $\alpha$ that best described the developmental trajectory in the data.
 As for adults, this was done via the integration model with equal prior probability for each object.
 In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the overall intercept and adding the slope times the child's age (with age anchored at 0).
-The analysis code corresponding to these calculations can be found in the associated online repository.
+The analysis code corresponding to these calculations can be found in the associated online repository in the file `models.Rmd`.
 

### 2020-08-13 papers/full_paper/manuscript.Rmd
advance revision

@@
 Integration (c) combined informativeness and common ground manipulations.
-One integration condition is shown here: preference - same speaker - incongruent.", out.width="100%"}
+One integration condition is shown here: preference - same speaker - congruent.", out.width="100%"}
 knitr::include_graphics("./figures/fig1.png")
@@
 This resulted in a total of 20 conditions, for which we generated a priori model predictions in the same way as in experiment 3.
+That is, we conducted a separate experiment for each level of prior strength and common ground manipulation to estimate the prior probability of each object following this particular manipulation (analogous to experiment 2).
+This prior distribution was then passed through the model for the congruent and incongruent conditions, resulting in a unique prediction for each of the 20 condition.
+Given the graded nature of the prior manipulations, experiment 4 basically tests how well the model performs with different types of prior distributions.
+
 The strong prior manipulation in experiment 4 was a direct replication of experiment 3 (see Fig \ref{fig:fig3}c).
@@
 
-How is information integrated in this context in this context?
+How is information integrated in this context?
 The *integration model* assumes that the informativeness of an utterance depends on the common ground shared between interlocutors.
-That is, the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
-As a consequence, when prior interactions strongly implicate one object as the more likely referent (for example in the preference - same speaker conditions in experiment 3, 4 and 7), the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
+This conception of information integration explains the seemingly counterintuitive predictions of the model.
+For example, one might expect that the model predicts a performance at chance level in the same speaker -- incongruent conditions because the two cues "pull" the listener in opposite directions.
+Instead, the model predicts a performance below chance, favoring the object implicated by the prior (which also matches participants' responses).
+This is because the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
+As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
 Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@brunder1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.

### 2020-08-14 papers/full_paper/Supplementary_information.Rmd
revision pass1

--- 2020-03-10 papers/full_paper/Supplementary_information.Rmd
@@
 mask              : no
+toc               : yes
 
@@
 library(broom)
-library(exactRankTests)
+library(broom.mixed)
 library(matrixStats)
@@
 The following sections present details on the analyses used to evaluate whether the different experimental manipulations produced different responses.
-For all generalized linear mixed models (GLMM) we used the maximally converging random effects structure.
+For all generalized linear mixed models (GLMM), we included random intercepts for participant id (`id`) and the animal speaker (`agent` - representing the respective "item") with random slopes for condition (same speaker vs.
+different speaker), alignment (congruent vs.
+incongruent; experiment 3, 4 and 7) and age (experiment 5-7).
+We also included interactions between random effects.
+This maximal structure was reduced until the model converged.
+The formula of the final model is presented in the text.
+To access further details about GLMMS, including variance estimates for random effects, please download the online repository, open the file `papers/full_paper/Supplementary_information.Rmd` and run the command `summary()` on the respective object that stores the output of each model.
 
@@
 
-ex1_r <- tidy(lm_ex1, effects = "fixed")%>%
+ex1_r <- broom.mixed::tidy(lm_ex1, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
          estimate = round(estimate,2))
+
 ```
@@
 
-ex2pref_r <- tidy(lm_ex2pref, effects = "fixed")%>%
+ex2pref_r <- broom.mixed::tidy(lm_ex2pref, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
+ex2nov_r <- broom.mixed::tidy(lm_ex2nov, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-lm_ex3_r <- tidy(lm_ex3, effects = "fixed")%>%
+lm_ex3_r <- broom.mixed::tidy(lm_ex3, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
   group_by(common_ground_manipulation,prior_manipulation)%>%
-  do(models = glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))))
-
-ex4_prior_models_table <- tidy(ex4_prior_models, models)%>%
-  filter(group == "fixed")%>%
-  select(-statistic, -group)%>%
+  do(broom::tidy(glmer(correct ~ speaker + (1|id) + (1|agent),data = .,family=binomial,  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))))
+
+ex4_prior_models_table <- ex4_prior_models%>%
+  filter(effect == "fixed")%>%
+  select(-statistic, -group, -effect)%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-lm_ex4_r_strong <- tidy(lm_ex4_strong, effects = "fixed")%>%
+lm_ex4_r_strong <- broom.mixed::tidy(lm_ex4_strong, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-lm_ex4_r_medium <- tidy(lm_ex4_medium, effects = "fixed")%>%
+lm_ex4_r_medium <- broom.mixed::tidy(lm_ex4_medium, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-lm_ex4_r_weak <- tidy(lm_ex4_weak, effects = "fixed")%>%
+lm_ex4_r_weak <- broom.mixed::tidy(lm_ex4_weak, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-Results from Experiment 3 and 4 (strong prior manipulation) were highly correlated (r = `r cor_3_4$estimate`, *p* > .001).
+Results from Experiments 3 and 4 (strong prior manipulation) were highly correlated (r = `r cor_3_4$estimate`, *p* > .001).
 
@@
 )%>%
-  mutate(condition = factor(condition, levels = c("control","test")))%>%
+  mutate(condition = factor(condition, levels = c("test","control")))%>%
   group_by(experiment,condition,age_num, id) %>%
@@
   scale_colour_solarized(name = "Condition",
-                     labels=c("Control","Test"))+
+                     labels=c("Test","Control"))+
   scale_fill_solarized(name = "Condition",
-                    labels=c("Control","Test"))+
+                    labels=c("Test","Control"))+
   theme(legend.position = c(0.1, 0.15), 
@@
 
-child_lm_ex1_r <- tidy(child_ex1_lm, effects = "fixed")%>%
+child_lm_ex1_r <- broom.mixed::tidy(child_ex1_lm, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-child_lm_ex2_r <- tidy(child_ex2_lm, effects = "fixed")%>%
+child_lm_ex2_r <- broom.mixed::tidy(child_ex2_lm, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 
-```{r child_models, results = "asis"}
+```{r child_models, results = "asis", out.width="100%"}
 child_ex3_lm_data <- child_ex3_data%>%
@@
 
-child_lm_ex3_r <- tidy(child_ex3_lm, effects = "fixed")%>%
+child_lm_ex3_r <- broom.mixed::tidy(child_ex3_lm, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
   mutate(speaker = ifelse(speaker == "different_speaker", "Different speaker", "Same speaker"),
-         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))
+         alignment = ifelse(alignment == "congruent", "Congruent", "Incongruent"))%>%
+  mutate(model = recode(model, pragmatic = "Parameter free", pragmatic_developmental_noise = "Developmental noise", pragmatic_noise = "Noise"))
 
@@
   scale_color_manual(name="Model",
-                     breaks=c("integration","integration_noise","integration_developmental_noise"),
-                     values= c("#00afaf","#af6300","#6c71c4"))+
+                     breaks=c("Parameter free","Noise","Developmental noise"),
+                     values= c("#00afaf","#6c71c4","#af6300"))+
   scale_fill_manual(name="Model",
-                     breaks=c("integration","integration_noise","integration_developmental_noise"),
-                     values= c("#00afaf","#af6300","#6c71c4"))
+                     breaks=c("Parameter free","Noise","Developmental noise"),
+                     values= c("#00afaf","#6c71c4","#af6300"))
 
@@
 As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term.
-It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
-For adults, we used the data from Experiment 1 to infer the value of $\alpha$.
+It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular con    text.
+For adults, we used the data from Experiment 1 to infer $\alpha$.
 That is, we inferred which value of $\alpha$ would generate model predictions for the integration model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
-This value for $\alpha$ was then used in Experiment 3 and 4.
+Technically, we used MCMC to compute the posterior distribution for $\alpha$ and computed the maximum a posteriori (MAP).
+This value for $\alpha$ was then used in Experiments 3 and 4.
 
@@
 As for adults, this was done via the integration model with equal prior probability for each object.
-In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the overall intercept and adding the slope times the child's age (with age anchored at 0).
-The analysis code corresponding to these calculations can be found in the associated online repository.
+In this model, $\alpha$ for a given age was defined via a simple linear regression.
+We calculated the MAP for the intercept and the slope of this regression based on their posterior distributions.
+In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0).
 
@@
 \ref{fig:figS2}) and disliked the pink-ish object (left table in Fig.\ref{fig:figS2}), the average proportion with which participants chose the yellow-ish object  was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for the pink-ish object it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
-In Experiment 3 and 4, this measurement determined the prior distribution over objects in cases whenever the the same manipulation was used (preference/same speaker).
+In Experiments 3 and 4, this measurement determined the prior distribution over objects in cases whenever the same manipulation was used (preference/same speaker).
 Note that Experiment 3 involved three objects while Experiment 2 only involved two.
@@
 As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age.
+We used a simple logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6.
 In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition (same or different speaker), adding the slope times the child's age and then using a logistic transformation to convert the outcome into proportions.
+Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalized in the same way for adults.
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
-Model code for inferring the intercept and the slope for the child study can be found in the associated online repository.
+Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd`.
 
@@
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
-  geom_point(size = 2)+
+  geom_point(size = 2, pch = 1, stroke = 1)+
   geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
@@
 
-```{r child_bf, results = "asis"}
+```{r child_bf, results = "asis", out.width="100%"}
 child_ex3_bf <- child_ex3_model_comparison%>%
@@
   spread(model, logP) %>%
-  mutate("Integration > No common ground" = formatC(exp(pragmatic - flat_prior),2),
-         "Integration > No informativeness" = formatC(exp(pragmatic - prior_only),2),
-         "No common ground > No informativeness" = formatC(exp(flat_prior - prior_only),2)) %>%
+  mutate("Int > No CG" = formatC(exp(pragmatic - flat_prior),2),
+         "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
+         "No CG > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
   select(-pragmatic,-flat_prior, -prior_only)
+
 apa_table(
@@
   , caption = "Model comparisons in Experiment 7"
-  , note = "BF = Bayes Factor"
+  , note = "BF = Bayes Factor, Int = Integration, No CG = No common ground, No Inf = No informativeness "
   , escape = T
@@
   geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
-  geom_point(size = 3)+
+  geom_point(size = 2, pch = 1, stroke = 1)+
   geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
@@
 In all cases, the integration model outperformed the two alternative models, both for children as well as for adults.
-Interestingly, for adults but not for children, using a uniform prior for $L_0$ yielded a lower estimate for the noise parameter in Experiment 3 and 4.
+Interestingly, for adults but not for children, using a uniform prior for $L_0$ yielded a lower estimate for the noise parameter in Experiments 3 and 4.
 

### 2020-08-14 papers/full_paper/manuscript.Rmd
revision pass1

@@
 abstract: |
-  Language is learned in complex social settings where listeners must reconstruct speakers’ intentend meanings from context.
+  Language is learned in complex social settings where listeners must reconstruct speakers’ intended meanings from context.
 To navigate this challenge, children can use pragmatic reasoning to learn the meaning of unfamiliar words.
@@
 Here we study this integration process.
-We isolate two sources of pragmatic information and, using a probabilistic model of conversational reasoning, formalize both how they should be combined and how this process might develop.
+We isolate two sources of pragmatic information (common ground and expectations about informativeness) and -- using a probabilistic model of conversational reasoning -- formalize how they should be combined and how this process might develop.
 We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children (N = 243) and adults (N = 694).
 Results show close numerical alignment between model predictions and data.
+Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that children selectively ignore one information source.
 This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
@@
 library(broom)
+library(broom.mixed)
 library(readxl)
@@
 Contextual information comes in many forms.
-On the one hand, there is information provided by the utterance\footnote{We use the terms utterance, utterance-level information or utterance-level cues to capture all cues that the speaker provides for their intended meaning.
-This includes direct referential information in the form of pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.} itself.
+On the one hand, there is information provided by the utterance^[
+We use the terms utterance, utterance-level information or utterance-level cues to capture all cues that the speaker provides for their intended meaning.
+This includes direct referential information in the form of pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.] itself.
 Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative.
@@
 
-Evidence for the use of common ground\footnote{Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
-Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner;@hanna2003effects; @mozuraitis2015privileged].
+Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
+Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions ^[@brown2009partner; @hanna2003effects; @mozuraitis2015privileged].
 Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested.
 However, most of this work is focused on online perspective taking.
-In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children [@matthews2006effect].
-We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [see also @bohn2018common]} information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children ^[@matthews2006effect].
+We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [@bohn2018common].] information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
 For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
@@
 
-#summary(lm_ex2nov)
+summary(lm_ex2nov)
 
-ex2nov_r <- tidy(lm_ex2nov, effects = "fixed")%>%
+ex2nov_r <- broom.mixed::tidy(lm_ex2nov, effects = "fixed")%>%
   mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
@@
 For preference and novelty, control refers to a different speaker (see Fig 1b).
-Transparent dots show data from individual participants, diamonds represent condition means, error bars are 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="60%"}
+Transparent dots show data from individual participants (slightly jittered to avoid overplotting), diamonds represent condition means, error bars are 95\\% CIs.
+Dashed line indicates performance expected by chance.", out.width="70%"}
 knitr::include_graphics("./figures/fig2.png")
@@
 Data and model predictions by condition for experiment 3 (a).
-Transparent dots show data from individual participants, diamonds represent condition means.
+Transparent dots show data from individual participants (slightly jittered to avoid overplotting), diamonds represent condition means.
 Correlation between model predictions and data in Experiment 3 (b), between data in Experiment 3 and the direct replication in experiment 4 (c) and between model predictions and data in experiment 4 (d).
@@
 Participants’ average responses were highly correlated with the  predictions from the *integration model* in each condition (Fig \ref{fig:fig3}b).
-When comparing model, we found that model fit was considerably better for the* integration model* compared to the *no common ground model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
+When comparing model, we found that model fit was considerably better for the *integration model* compared to the *no common ground model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
 
@@
 1B).
-Transparent dots show data from individual participants, regression lines show fitted linear models with 95\\% CIs.
-Dashed line indicates performance expected by chance.", out.width="60%"}
+Transparent dots show data from individual participants (slightly jittered to avoid overplotting), regression lines show fitted linear models with 95\\% CIs.
+Dashed line indicates performance expected by chance.", out.width="70%"}
 knitr::include_graphics("./figures/fig4.png")
@@
 In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
-We tested children only with the preference manipulation\footnote{We initially tested children with the novelty as well as the preference manipulation.
+We tested children only with the preference manipulation^[We initially tested children with the novelty as well as the preference manipulation.
 We found that children made the basic inference in that they selected the object that was preferred by or new to the speaker, but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty.
-This finding contrasts with earlier work (Diesendruck et al., 2004).
-However, since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study}.
+This finding contrasts with earlier work [@diesendruck2004two].
+since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
 The procedure for children was identical to the preference manipulation for adults.

### 2020-08-14 papers/full_paper/manuscript.Rmd
revision pass1

@@
 Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
-Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions ^[@brown2009partner; @hanna2003effects; @mozuraitis2015privileged].
+Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @mozuraitis2015privileged].
 Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested.
 However, most of this work is focused on online perspective taking.
-In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children ^[@matthews2006effect].
+In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children [@matthews2006effect].
 We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [@bohn2018common].] information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].

### 2020-08-15 papers/full_paper/Supplementary_information.Rmd
update affilitations

@@
   - name          : "Manuel Bohn"
-    affiliation   : "1,2"
+    affiliation   : "1,2,3"
   - name          : "Michael Henry Tessler"
-    affiliation   : "3"
+    affiliation   : "4"
   - name          : "Megan Merrick"

### 2020-08-15 papers/full_paper/manuscript.Rmd
update affilitations

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Leipzig Research Center for Early Child Development, Jahnallee 59, 04109 Leipzig, Germany"
-    email         : "manuel.bohn@uni-leipzig.de"
+    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
+    email         : "manuel_bohn@eva.mpg.de"
   - name          : "Michael Henry Tessler"

### 2020-08-15 papers/full_paper/manuscript.Rmd
fix references

@@
 As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
-Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@brunder1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
+Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@bruner1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
 Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.

### 2020-09-21 papers/full_paper/Supplementary_information.Rmd
update revision

@@
 As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term.
-It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular con    text.
+It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
 For adults, we used the data from Experiment 1 to infer $\alpha$.
-That is, we inferred which value of $\alpha$ would generate model predictions for the integration model (assuming equal prior probability over referents) that corresponded to the average proportion of correct responses measured in Experiment 1.
-Technically, we used MCMC to compute the posterior distribution for $\alpha$ and computed the maximum a posteriori (MAP).
-This value for $\alpha$ was then used in Experiments 3 and 4.
-
-For children, the speaker optimality parameter changed with age.
+That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1.
+We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.
+
+For children, $\alpha$ changed with age.
 Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
@@
 In this model, $\alpha$ for a given age was defined via a simple linear regression.
-We calculated the MAP for the intercept and the slope of this regression based on their posterior distributions.
+Again, we performed a Bayesian analysis to compute a posterior distribution for the intercept and the slope of this regression.
 In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0).

### 2020-09-21 papers/full_paper/manuscript.Rmd
update revision

@@
 Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
-Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @mozuraitis2015privileged].
+Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged].
 Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested.
@@
 In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children [@matthews2006effect].
-We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [@bohn2018common].] information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [@bohn2018common].Our main focus is on how information that is part of common ground integrates with other pragmatic information sources.] information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
 For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
@@
 Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material available online.
-Probabilistic models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl].
-In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors which were calculated from the marginal likelihoods of each model given the data.
+
+Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian].
+All models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl].
+In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data.
 Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online.
@@
 This finding contrasts with earlier work [@diesendruck2004two].
-since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
+Since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
 The procedure for children was identical to the preference manipulation for adults.
@@
 However, to incorporate developmental change in the model, we allowed the rationality parameter $\alpha$ and the prior distribution over objects to change with age.
-That is, instead of a single value, we inferred the intercept and slope for each parameter that best described the developmental trajectory in the data of experiment 5 and 6.
+That is, instead of a single value, we used Bayesian data analysis to infer the intercept and slope for each parameter that best described the developmental trajectory in the data of experiment 5 and 6 (see Supplementary Material for details on how parameters were estimated).
 These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions.
@@
 The high level of inferred noise moved the model predictions for children in all conditions close to chance level.
-We therefore compared two additional sets of models with different parameterizations of the noise parameter that emphasized differences between conditions in the model predictions more (see Supplementary Material available online and Fig \ref{fig:fig5}a).
+We therefore compared two additional sets of models with different parameterizations of the noise parameter that emphasized differences between conditions in the model predictions more (see Supplementary Material and Fig \ref{fig:fig5}a).
 This analysis was not pre-registered.
@@
 
-Integrating multiple sources of information is an integral part of human communication [@tanenhaus1995integration].
+Integrating multiple sources of information is an integral part of human communication.
 To infer the intended meaning of an utterance, listeners must combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
@@
 
-All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing information sources by some ratio.
-We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data.
-That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli.
-Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning; @cohn2018pragmatically; @monroe2017colors].
+Cue integration is an integral part of language comprehension and learning.
+As such, it has been extensively studied in recent decades.
+The focus of this work has usually been on how adults combine perceptual, semantic or syntactic information [e.g.
+@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line].
+We extend the study of cue integration to pragmatics.
+Most importantly, however, we present a substantive theory of the integration process itself.
+Real world language comprehension and learning happens in socially dynamic and complex situations which inevitably require integrating multiple pragmatic information sources.
+The integration model provides a formal description of the (hypothetical) psychological representations that may underlie information integration.
+As such, our work complements theorizing about information integration in other domains of language [e.g.
+@fourtassi2020optimal; @mcclelland2006there; @smith2017multimodal].
 
@@
 
+All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing information sources by some ratio.
+We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data.
+That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli.
+Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning; @cohn2018pragmatically; @monroe2017colors].
+
 The *integration model* predicted information integration in four-year-olds.
@@
 Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
-A starting point for explicitly modeling common ground would be the work by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling].
+Our model also does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs.
+common ground.
+This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling].
 In their work, they focus on how listeners identify the referent of ambiguous referring expressions.
 Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them.
-In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could easily be combined with one another.
-However, because common ground in our study was established by a shared interaction and not by the online convergence of different perspectives, it would require a different experimental design to test the combined model.
+In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.
 

### 2020-09-21 papers/full_paper/manuscript.Rmd
update supplement for revision

@@
 Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
-Our model also does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs.
+Based on a process model of common ground, one could further specify how common ground information (i.e.
+social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm].
+Relatedly, our model does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs.
 common ground.

### 2020-09-22 papers/full_paper/models.Rmd
clean repo
update model algo

--- 2019-04-26 papers/full_paper/models.Rmd
@@
 
+```{r}
+child_ex3_pragm_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
+
+child_ex3_pragm_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+
+child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+
+child_ex3_flat_prior_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+
+child_ex3_flat_prior_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+
+child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+
+child_ex3_prior_only_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+
+child_ex3_prior_only_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+
+child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+
+```
+
 #### Pragmatic model
@@
 var steps = 5000
-var samples = 1
+var samples = 100
 var mll = AIS(model, {steps:steps, samples: samples})
@@
 ```{r}
-# child_ex3_pragm_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
+child_ex3_pragm_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
 
@@
 ```{r}
-# child_ex3_pragm_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+child_ex3_pragm_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
 
@@
 ```{r}
-# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
 
@@
 ```{r}
-# child_ex3_flat_prior_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+child_ex3_flat_prior_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
 
@@
 ```{r}
-# child_ex3_flat_prior_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+child_ex3_flat_prior_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
 
@@
 ```{r}
-# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
 
@@
 ```{r}
-# child_ex3_prior_only_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+child_ex3_prior_only_model_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
 
@@
 ```{r}
-# child_ex3_prior_only_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+child_ex3_prior_only_model_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
 
@@
 ```{r}
-# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 3,
+  cores = 3
+)%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
 

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
correct "it's" -> "its"
update supplement

@@
 As noted in the main text, the parameter $\alpha$ (speaker optimality parameter) in equation 2 determines the absolute strength of the likelihood term.
-It's interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
+Its interpretation is *how* rational $L_1$ thinks $S_1$ is in this particular context.
 For adults, we used the data from Experiment 1 to infer $\alpha$.
 That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1.
-We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.
+We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$.
+We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.
 
 For children, $\alpha$ changed with age.
-Instead of inferring a single value across age, we used the data from Experiment 5 to find the slope and intercept for $\alpha$ that best described the developmental trajectory in the data.
+Thus, $\alpha$ for a given age was defined via a simple linear regression and instead of inferring a single value across age, we used the data from Experiment 5 to find the intercept ($\beta^\alpha_0$) and slope ($\beta^\alpha_1$) that best described the developmental trajectory in the data.
 As for adults, this was done via the integration model with equal prior probability for each object.
-In this model, $\alpha$ for a given age was defined via a simple linear regression.
-Again, we performed a Bayesian analysis to compute a posterior distribution for the intercept and the slope of this regression.
-In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0).
+We performed a Bayesian analysis to compute a posterior distribution for the intercept and the slope of this regression.
+The prior distribution was $\beta^\alpha_0 \sim {\rm Cauchy }(1,2)$ for the intercept and $\beta^\alpha_1 \sim {\rm Cauchy }(0,2)$ for the slope.
+We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.
+In Experiment 7, the speaker optimality parameter for a given child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child's age (with age anchored at 0): $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$.
 
@@
 
-For children, we used the data from Experiment 6 to model the slope and intercept that best described the developmental trajectory in the data for each of the two conditions.
+For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the $j$ two conditions.
 As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age.
-We used a simple logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6.
-In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition (same or different speaker), adding the slope times the child's age and then using a logistic transformation to convert the outcome into proportions.
-Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalized in the same way for adults.
+We used a simple Bayesian logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6.
+The prior distribution was $\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ for the intercept and slope.
+We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.
+In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition ($j$), adding the slope times the child's age ($i$) and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$.
+Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalization in the same way as for adults.
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
-Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd`.
+Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd` starting line 1491.
 
@@
 Model fit was assessed based on marginal log-likelihoods of the data under each model.
-Bayes Factors were computed by first subtracting log-likelihoods for two models and then exponentiating the result.
+To compute the log-likelihood for models including a noise parameter, we used forward sampling on four independent chains to collect 5000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.
+
+Bayes Factors were then computed by first subtracting log-likelihoods for two models and then exponentiating the result.
 Table \ref{tab:ex3_comp} shows Bayes Factors for model comparisons in Experiment 3.

### 2020-09-22 papers/full_paper/manuscript.Rmd
update supplement

@@
 Frequentist logistic GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence.
-Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material available online.
+Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material.
 
-Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian].
 All models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl].
+Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in WebPPL.
 In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data.

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
fix forward sampling description

@@
 Model fit was assessed based on marginal log-likelihoods of the data under each model.
-To compute the log-likelihood for models including a noise parameter, we used forward sampling on four independent chains to collect 5000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.
+To compute the log-likelihood for models including a noise parameter, we used forward sampling to collect 20,000 samples from the prior distribution of the noise parameter, calculated the log-likelihood for each sample and then averaged over the resulting distribution.
 

### 2020-09-22 papers/full_paper/Supplementary_information.Rmd
Update Supplementary_information.Rmd

--- 2020-09-22 papers/full_paper/Supplementary_information.Rmd
@@
 For adults, we used the data from Experiment 1 to infer $\alpha$.
-That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1.
-We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the maximum a posteriori (MAP) and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$.
+That is, we performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents), with an unknown *a priori* value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1.
+We used MCMC to approximate the posterior distribution for $\alpha$ based on Experiment 1, computed the *maximum a posteriori* (MAP) estimate and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.	The prior distribution was $\alpha \sim {\rm Cauchy }(1,2)$.
 We collected samples from four independent MCMC chains, collecting 6000 samples from each chain and removing the first 2000 for burn-in.
@@
 The prior distribution over objects, $P(r)$, varied with the common ground manipulation, the identity of the speaker and the alignment of utterance and common ground information.
-Numerically, it depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children.
+Numerically, these probabilities depended on the measurement obtained in Experiment 2A and B for adults and Experiment 6 for children.
 Fig.
@@
 
-For adults, this worked in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker previously indicated that they liked the yellow-ish object (right table in Fig.
+For adults, the prior over objects was estimated in the following way: For example, in Experiment 2, for the preference/same speaker condition, when the speaker previously indicated that they liked the yellow-ish object (right table in Fig.
 \ref{fig:figS2}) and disliked the pink-ish object (left table in Fig.\ref{fig:figS2}), the average proportion with which participants chose the yellow-ish object  was `r adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` and for the pink-ish object it was `r 1-adult_ex2_preference_data %>% filter(condition == "same_speaker") %>% summarise(mean = mean(correct)) %>% pull(mean)` respectively.
@@
 Note that Experiment 3 involved three objects while Experiment 2 only involved two.
-We nevertheless used the exact proportions measured in Experiment 2 for each object to inform the prior.
-This approach spread out the absolute probability mass but conserved the relative relation between objects.
+We nevertheless used the exact proportions measured in Experiment 2 for each object as unnormalized probabilities in the prior.
+This approach  conserved the relative relation between object types.
 Thus, when utterance and common ground information were aligned (i.e.
@@
 
-For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the $j$ two conditions.
-As for the speaker optimality parameter, this allowed us to generate prior distributions that were sensitive to the child's age.
+For children, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectory in the data for each of the two ($j$) conditions.
+As for the speaker optimality parameter, this allowed us to generate object prior distributions in the cognitive model that were sensitive to the child's age.
 We used a simple Bayesian logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children's performance in the two conditions of experiment 6.
@@
 In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition ($j$), adding the slope times the child's age ($i$) and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$.
-Because these proportions corresponded to a two object scenario they were then converted to the three object scenario via normalization in the same way as for adults.
+Because these proportions corresponded to a two object scenario, they were then converted to the three object scenario via normalization in the same way as for adults.
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.

### 2020-09-23 papers/full_paper/Supplementary_information.Rmd
revision sent

@@
 
-## Model parameters
+# Model parameters
 
@@
 The overall distribution then depended on the alignment of information sources in the same way as it did for adults.
-Model code for inferring the intercept and the slope for the child study can be found in the associated online repository in the file `models.Rmd` starting line 1491.
+Model code for inferring the parameters can be found in the associated online repository in the file `models.Rmd` starting in line 213 (adults) 1464 (children).
 

### 2020-09-23 papers/full_paper/manuscript.Rmd
revision sent

@@
 Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins].
-On the other hand, there is information provided by common ground (the body of mutually shared knowledge and beliefs between interlocutors)[@bohn2018common; @clark1996using; @clark2015common].
+On the other hand, there is information provided by common ground [the body of mutually shared knowledge and beliefs between interlocutors; @bohn2018common; @clark1996using; @clark2015common].
 Because utterances are embedded in common ground, pragmatic reasoning in context always requires information integration.
@@
 
-Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
+Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
 Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged].
@@
 However, most of this work is focused on online perspective taking.
-In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is supposedly easier for children [@matthews2006effect].
-We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is not just known to both interlocutors but also assumed to be shared between them [@bohn2018common].Our main focus is on how information that is part of common ground integrates with other pragmatic information sources.] information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is likely easier for children [@matthews2006effect].
+We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground.
+Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.
+
+Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
 For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
 
-These examples, however, highlight children’s use of a single pragmatic information source or cue.
+The examples discussed above, however, highlight children’s use of a single pragmatic information source or cue.
 Harnessing multiple – potentially competing – pragmatic cues poses a separate challenge.
@@
 
-Cue integration is an integral part of language comprehension and learning.
+Cue integration is an integral part of language comprehension and learning [as well as perception more generally; @trommershauser2011sensory].
 As such, it has been extensively studied in recent decades.
@@
 @tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line].
-We extend the study of cue integration to pragmatics.
+We extend the study of linguistic cue integration to pragmatics.
 Most importantly, however, we present a substantive theory of the integration process itself.
@@
 The integration model provides a formal description of the (hypothetical) psychological representations that may underlie information integration.
-As such, our work complements theorizing about information integration in other domains of language [e.g.
+As such, our work complements theorizing about information integration in other domains of language comprehension [e.g.
 @fourtassi2020optimal; @mcclelland2006there; @smith2017multimodal].
@@
 
-We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically.
-As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g.
-in @frank2012predicting].
-Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
-Based on a process model of common ground, one could further specify how common ground information (i.e.
-social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm].
-Relatedly, our model does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs.
-common ground.
-This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling].
-In their work, they focus on how listeners identify the referent of ambiguous referring expressions.
-Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them.
-In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.
-
 The primary source of developmental change in our model is age related changes in the propensity to make the individual inferences.
@@
 Such a comparison would require more precision (either via more trials or more participants) than our current experiment affords, however.
+
+We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically.
+As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g.
+in @frank2012predicting].
+Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
+Based on a process model of common ground, one could further specify how common ground information (i.e.
+social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm].
+A further limitation of our work here is that we did not specify how common ground is integrated into the process of compositional interpretation at work in more complex sentences.
+This is an open challenge for future research on pragmatic inference.
+One possible approach would be to make inferences about relevant common ground at the level of individual lexical items and to propagate this uncertainty through compositions into larger sentences [as in e.g., @potts2016embedded].
+
+Our model also does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs.
+common ground.
+This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling].
+In their work, they focus on how listeners identify the referent of ambiguous referring expressions.
+Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them.
+In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.
+
+# Conclusion
 

### 2020-09-23 papers/full_paper/models.Rmd
revision sent

--- 2019-04-26 papers/full_paper/models.Rmd
@@
 ---
-title             : "Predicting information integration in pragmatic word learning across development"
-shorttitle        : "Supplementary Information"
-
-author: 
-  - name          : "Manuel Bohn"
-    affiliation   : "1,2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
-    email         : "bohn@stanford.edu"
-  - name          : "Michael Henry Tessler"
-    affiliation   : "3"
-  - name          : "Megan Merrick"
-    affiliation   : "1"
-  - name          : "Michael C. Frank"
-    affiliation   : "1"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
-  - id            : "3"
-    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
-
-bibliography      : ["library.bib"]
-
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-lineno            : no
-mask              : no
-
-class             : "man"
-output            : papaja::apa6_pdf
+title: "Predicting information integration in pragmatic word learning across development"
+subtitle: "Probabilistic Models"
+author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
+output: 
+  bookdown::html_document2:
+    toc: yes
+    toc_float: true
+    fig_caption: yes
+    code_folding: show
+    number_sections: false
+  bookdown::pdf_document2:
+    toc: yes 
+    number_sections: false  
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = F, warning = F, message = F, include = T)
+knitr::opts_chunk$set(echo = T, warning = F, message = F, include = T)
 
@@
 ```
+# Overview
+
+This file includes model code for the probabilistic models.
+The section [Model code](#model-code) gives the code for the basic integration model.
+Firs, we define the objects and locations that feature in the experiments along with some helper functions and then we specify the actual cognitive model.
+
+The section [Adults](#adults) presents the analysis code for Experiment 3 and 4.
+In the section [Inferring speaker optimality parameter and setting priors](#parameters), we estimated the speaker optimality parameter $\alpha$ based on the data from Experiment 1 and define the prior distribution over objects, $P(r)$, based on Experiment 2.
+
+Then follows the code with which we generated the model predictions for the models in Experiment 3, that is, the integration model (with and without a noise parameter), the no informativeness model and the no common ground model (Section: [Model predictions](#ex3-predictions)).
+Next, we evaluate the noise parameter for each model and plot the model predictions and correlate predictions and the data for each model (Section: [Compare model predictions to data](#ex3-correlations)).
+Finally, we compute the log-likelihoods for each model and the Bayes Factors for the model comparisons (Section: [Model comparison](#ex3-comparison)).
+
+We start the section on [Experiment 4](#experiment-4) with specifying $P(r)$ for each version of prior strength manipulations.
+Next, we generate predictions for the three models (Section: [Model predictions (including noise parameter)](#ex4-predictions), inspect the corresponding noise parameters, and correlate the model predictions with the data (Section: [Compare model predictions to data](#ex4-correlations)).
+Finally, we compute the log-likelihoods and Bayes Factors (Section: [Model comparison](#ex4-comparison)).
+
+The section [Children](#children) follows the same logic as the one for adults.
+We first present the code used to estimate the intercept and slope necessary to compute $\alpha$ (using the data from Experiment 5) and $P(r)$ (using the data from Experiment 6) in an age-sensitive way (Section: [Model parameters and data](#child-parameters)).
+Then we generate model predictions for the three models, each in three versions,: without a noise parameter, with a single noise parameter and with a developmentally changing noise parameter (Section: [Model predictions](#child-predictions)).
+Then we compare the different noise parameters and correlate model predictions with the data (Section: [Compare model predictions to data](#child-correlations)).
+Finally, we compute the log-likelihoods for the different models and compare them via Bayes Factors (Section: [Model comparison](#child-comparison)).
 
@@
 
-#### Inferring speaker optimality parameter and setting priors
+#### Inferring speaker optimality parameter and setting priors {#parameters}
 
@@
 
-### Model predictions
-
-#### Pragmatic model
+### Model predictions {#ex3-predictions}
+
+#### Integration model
 
@@
 
-```{r predictions pragmatic model ex 3 noise, include = FALSE}
+```{r predictions pragmatic model ex 3 noise, include = T}
 # ex3_pragm_model_noise <- webppl(
@@
 
-#### Prior only model
+#### No informativeness model
 
@@
 
-```{r model prior only noise ex3, include = FALSE}
+```{r model prior only noise ex3, include = T}
 predictions.prior.only.ex3.noise <-'
@@
 
-```{r predictions prior only model ex 3 noise, include = FALSE}
+```{r predictions prior only model ex 3 noise, include = T}
 # ex3_prior_only_model_noise <- webppl(
@@
 
-#### Flat prior model
+#### No common ground model
 
@@
 
-```{r predictions flat prior model ex 3 noise, include = FALSE}
+```{r predictions flat prior model ex 3 noise, include = T}
 # ex3_flat_prior_model_noise <- webppl(
@@
 
-#### Compare model predictions to data
+#### Compare model predictions to data {#ex3-correlations}
 
@@
 
-### Model comparison
+### Model comparison {#ex3-comparison}
 
@@
 
-##### Pragmatic model
+##### Integration model
 
@@
 
-```{r loglike rsa noise ex3, include = FALSE}
+```{r loglike rsa noise ex3, include = T}
 loglike.rsa.ex3.noise <-'
@@
 ```
-##### Prior only model
+##### No informativeness model
 
@@
 
-```{r loglike prior only noise ex3, include = FALSE}
+```{r loglike prior only noise ex3, include = T}
 loglike.prior.only.ex3.noise <-'
@@
 
-##### Flat prior model
+##### No common ground model
 
@@
 
-```{r loglike flat prior noise ex3, include = FALSE}
+```{r loglike flat prior noise ex3, include = T}
 loglike.flat.prior.ex3.noise <-'
@@
 
+```{r ex4 prior pre-tests data adults}
+# load data from prior strength manipulation experiments to set priors
+adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
+```
+
 ```{r model setup ex 4}
@@
 
-### Model predictions (including noise parameter)
-
-#### Pragmatic model
-
-```{r model rsa noise ex4, include = FALSE}
+### Model predictions (including noise parameter) {#ex4-predictions}
+
+#### Integration model
+
+```{r model rsa noise ex4, include = T}
 predictions.rsa.ex4.noise <-'
@@
 
-```{r predictions pragmatic model ex 4 noise, include = FALSE}
+```{r predictions pragmatic model ex 4 noise, include = T}
 # ex4_pragm_model_noise <- webppl(
@@
 
-#### Prior only model
-
-```{r model prior only noise ex4, include = FALSE}
+#### No informativeness model
+
+```{r model prior only noise ex4, include = T}
 predictions.prior.only.ex4.noise <-'
@@
 
-```{r predictions prior only model ex 4 noise, include = FALSE}
+```{r predictions prior only model ex 4 noise, include = T}
 # ex4_prior_only_model_noise <- webppl(
@@
 
-#### Flat prior model
-
-```{r model flat prior noise ex4, include = FALSE}
+#### No common ground model
+
+```{r model flat prior noise ex4, include = T}
 predictions.flat.prior.ex4.noise <-'
@@
 
-```{r predictions flat prior model ex 4 noise, include = FALSE}
+```{r predictions flat prior model ex 4 noise, include = T}
 # ex4_flat_prior_model_noise <- webppl(
@@
 
-### Compare model predictions to data
+### Compare model predictions to data {#ex4-correlations}
 
@@
 
-### Model comparison
+### Model comparison {#ex4-comparison}
 
@@
 
-##### Pragmatic model 
-```{r loglike rsa noise ex4, include = FALSE}
+##### Integration model 
+```{r loglike rsa noise ex4, include = T}
 loglike.rsa.ex4.noise <-'
@@
 
-##### Prior only model
-
-```{r loglike prior only noise ex4, include = FALSE}
+##### No informativeness model
+
+```{r loglike prior only noise ex4, include = T}
 loglike.prior.only.ex4.noise <-'
@@
 
-##### Flat prior model
-
-```{r loglike flat prior noise ex4, include = FALSE}
+##### No common ground model
+
+```{r loglike flat prior noise ex4, include = T}
 loglike.flat.prior.ex4.noise <-'
@@
 
-## Model parameters and data
+## Model parameters and data {#child-parameters}
 
@@
 ```
-## Model predictions
-
-### Pragmatic model
+## Model predictions {#child-predictions}
+
+### Integration model
 
@@
 
-### Prior only model
+### No informativeness model
 
@@
 
-### Flat prior model
+### No common ground model
 
@@
 
-## Compare model predictions to data
+## Compare model predictions to data {#child-correlations}
 
@@
 
-## Model comparison
+## Model comparison {#child-comparison}
 
@@
 
-#### Pragmatic model
+#### Integration model
 
@@
   spread(model, logP) %>%
-  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
-         "pragmatic > prior_only" = pragmatic - prior_only,
-         "flat_prior > prior_only" = flat_prior - prior_only) %>%
+  mutate("pragmatic > flat_prior" = exp(pragmatic - flat_prior),
+         "pragmatic > prior_only" = exp(pragmatic - prior_only),
+         "flat_prior > prior_only" = exp(flat_prior - prior_only)) %>%
   select(-pragmatic,-flat_prior, -prior_only)

### 2020-11-18 papers/full_paper/models.Rmd
save AIS samples to run on cluster

@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-
-'
-```
-
-```{r}
-# child_ex3_pragm_model_likelihood<- webppl(
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prag_param_free.csv"
+var modelVariant = "integration parameter free"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+
+'
+```
+
+```{r}
+# webppl(
 #   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+#   packages ="webppl-csv",
 #   data =list(allData = ex3_model_data),
 #   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
+#   mutate(model = "pragmatic",
+#          parameter = "parameter free")%>%
 #   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
 
-child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
-  as.tibble()%>%
-  mutate(model = "pragmatic",
-         parameter = "parameter free")%>%
+child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
+
+child_ex3_pragm_model_likelihood_marginal <- child_ex3_pragm_model_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
 
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_pragm_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
-
-child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prag_noise.csv"
+var modelVariant = "integration noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+// var mll = AIS(model, {steps:steps, samples: samples})
+// mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
   mutate(model = "pragmatic",
          parameter = "noise")%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+
+child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+
+child_ex3_pragm_model_noise_likelihood_marginal <- child_ex3_pragm_model_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
+  summarise(logP = mean(weight))
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
-
-child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prag_dev_noise.csv"
+var modelVariant = "integration dev noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
   mutate(model = "pragmatic",
          parameter = "developmental noise")%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+
+child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+
+child_ex3_pragm_model_developmental_noise_likelihood_marginal <- child_ex3_pragm_model_developmental_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
 
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
-
-child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_flat_prior_param_free.csv"
+var modelVariant = "flat prior parameter free"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
   mutate(model = "flat_prior",
          parameter = "parameter free")%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+
+child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+
+child_ex3_flat_prior_model_likelihood_marginal <- child_ex3_flat_prior_model_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
+
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
-
-child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_flat_prior_noise.csv"
+var modelVariant = "flat prior noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
   mutate(model = "flat_prior",
          parameter = "noise")%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+
+child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+
+child_ex3_flat_prior_model_noise_likelihood_marginal <- child_ex3_flat_prior_model_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
+
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
-
-child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_flat_prior_dev_noise.csv"
+var modelVariant = "flat prior dev noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
   mutate(model = "flat_prior",
          parameter = "developmental noise")%>%
+  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+
+child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+
+child_ex3_flat_prior_model_developmental_noise_likelihood_marginal <- child_ex3_flat_prior_model_developmental_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
-
+  summarise(logP = mean(weight))
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
-
-child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prior_only_param_free.csv"
+var modelVariant = "prior only parameter free"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
   mutate(model = "prior_only",
          parameter = "parameter free")%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+
+child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+
+child_ex3_prior_only_model_likelihood_marginal <- child_ex3_prior_only_model_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
-
-child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prior_only_noise.csv"
+var modelVariant = "prior only noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
   mutate(model = "prior_only",
          parameter = "noise")%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+
+child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+
+child_ex3_prior_only_model_noise_likelihood_marginal <- child_ex3_prior_only_model_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
 ```
@@
 
-var steps = 5000
-var samples = 100
-var mll = AIS(model, {steps:steps, samples: samples})
-mll
-'
-```
-
-```{r}
-# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 3,
-#   cores = 3
-# )%>%
-#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
-
-child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")%>%
-  as.tibble()%>%
+var steps = 10
+var samples = 10
+
+var resultsOutFile = "../../stats/data/llh_child_prior_only_dev_noise.csv"
+var modelVariant = "prior only developmental noise"
+ var fileHandle = webpplCsv.openFile(resultsOutFile)
+ var header_to_write = ["modelVariant", "steps", "iter", "weight"].join(",")
+ webpplCsv.writeLine(header_to_write,fileHandle)
+ var weights = map(function(i) {
+	 var weight = AIS(model, {samples: 1, steps: steps})
+	 var line_to_write = [modelVariant, steps, i, weight].join(",")
+ 	 webpplCsv.writeLine(line_to_write,fileHandle)
+ }, _.range(samples))
+
+//var mll = AIS(model, {steps:steps, samples: samples})
+//mll
+'
+```
+
+```{r}
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  packages ="webppl-csv",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
   mutate(model = "prior_only",
          parameter = "developmental noise")%>%
+  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+
+child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+
+child_ex3_prior_only_model_developmental_noise_likelihood_marginal <- child_ex3_prior_only_model_developmental_noise_likelihood%>%
   group_by(model,parameter)%>%
-  summarise(logP = mean(V1))
+  summarise(logP = mean(weight))
+
 ```
@@
 ```{r model loglike ex3 children}
-# calculating model log-likelihoods
-
-# child_ex3_model_comparison <- bind_rows(
-#   child_ex3_pragm_model_likelihood,
-#   child_ex3_pragm_model_noise_likelihood,
-#   child_ex3_pragm_model_developmental_noise_likelihood,
-#   child_ex3_flat_prior_model_noise_likelihood,
-#   child_ex3_flat_prior_model_likelihood,
-#   child_ex3_flat_prior_model_developmental_noise_likelihood,
-#   child_ex3_prior_only_model_noise_likelihood,
-#   child_ex3_prior_only_model_likelihood,
-#   child_ex3_prior_only_model_developmental_noise_likelihood
-# )%>%
-#   ungroup()%>%
-#   mutate(model = reorder(model,logP))%>%
-#   saveRDS("../../stats/saves/child_ex3_model_comparison.rds")
+# combining model log-likelihoods
+
+child_ex3_model_comparison <- bind_rows(
+  child_ex3_pragm_model_likelihood_marginal,
+  child_ex3_pragm_model_noise_likelihood_marginal,
+  child_ex3_pragm_model_developmental_noise_likelihood_marginal,
+  child_ex3_flat_prior_model_noise_likelihood_marginal,
+  child_ex3_flat_prior_model_likelihood_marginal,
+  child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
+  child_ex3_prior_only_model_noise_likelihood_marginal,
+  child_ex3_prior_only_model_likelihood_marginal,
+  child_ex3_prior_only_model_developmental_noise_likelihood_marginal
+)%>%
+  ungroup()%>%
+  mutate(model = reorder(model,logP))%>%
+  saveRDS("../../stats/saves/child_ex3_model_comparison.rds")
 
@@
 
+#### Means
 ```{r plot model loglikes ex3 children, include = T}
@@
   facet_grid(~parameter)+
-  ylim(-475,-400)+
+  ylim(-550,-400)+
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#859900","#b58900","#6c71c4"))
+
+```
+#### Likelihood distributions (noise models only)
+
+```{r}
+child_ex3_model_ll_dist <- bind_rows(
+  child_ex3_pragm_model_likelihood,
+  child_ex3_pragm_model_noise_likelihood,
+  child_ex3_pragm_model_developmental_noise_likelihood,
+  child_ex3_flat_prior_model_noise_likelihood,
+  child_ex3_flat_prior_model_likelihood,
+  child_ex3_flat_prior_model_developmental_noise_likelihood,
+  child_ex3_prior_only_model_noise_likelihood,
+  child_ex3_prior_only_model_likelihood,
+  child_ex3_prior_only_model_developmental_noise_likelihood
+)%>%
+  ungroup()%>%
+  mutate(model = reorder(model,weight))
+
+ggplot(child_ex3_model_ll_dist, aes(x = weight, col = model, fill = model))+
+  geom_histogram(alpha = .5)+
+  facet_wrap(~parameter)+
+  theme_few()+
+  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
+                    values= c("#859900","#b58900","#6c71c4"))+
+  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                     values= c("#859900","#b58900","#6c71c4"))

### 2020-11-19 papers/full_paper/models.Rmd
prag noise llh distribution kids

@@
 
-var steps = 10
-var samples = 10
+var steps = 5000
+var samples = 1
 
@@
 ```{r}
-# webppl(
-#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
-#   packages ="webppl-csv",
-#   data =list(allData = ex3_model_data),
-#   data_var = "dataFromR",
-#   chains = 1,
-#   cores = 1
-# )
-# 
-# read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
-#   mutate(model = "pragmatic",
-#          parameter = "parameter free")%>%
-#   saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
+webppl(
+  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.marginal.likelihood , sep='\n'),
+  packages ="webppl-csv",
+  data =list(allData = ex3_model_data),
+  data_var = "dataFromR",
+  chains = 1,
+  cores = 1
+)
+
+read_csv("../../stats/data/llh_child_prag_param_free.csv")%>%
+  mutate(model = "pragmatic",
+         parameter = "parameter free")%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")
 
@@
 
-var steps = 10
-var samples = 10
+var steps = 5000
+var samples = 100
 

### 2021-01-05 papers/cogsci2019/cogsci2019.Rmd
prep for re-submission

@@
 library(lme4)
-library(broom)
+library(broom.mixed)
 library(exactRankTests)
@@
 
-pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")
+pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")%>%ungroup()
 

### 2021-01-05 papers/full_paper/Supplementary_information.Rmd
prep for re-submission

@@
   scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
-                    values= c("#b58900","#6c71c4","#859900"))+
+                    values= c("#C5D86D","#86615C","#AFE0CE"))+
   scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
-                    values= c("#b58900","#6c71c4","#859900"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 ```
@@
 child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
+  select(-ci_lower, -ci_upper)%>%
   filter(model == "pragmatic")%>%
@@
   mutate(BF = formatC(BF,2))
+
 apa_table(
@@
 child_ex3_bf <- child_ex3_model_comparison%>%
+  select(-ci_lower, -ci_upper)%>%
   rename(Parameter = parameter)%>%
@@
   scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
-                    values= c("#b58900","#6c71c4","#859900"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 ```

### 2021-01-05 papers/full_paper/manuscript.Rmd
prep for re-submission

@@
 Here we study this integration process.
-We isolate two sources of pragmatic information (common ground and expectations about informativeness) and -- using a probabilistic model of conversational reasoning -- formalize how they should be combined and how this process might develop.
+We isolate two sources of pragmatic information and -- using a probabilistic model of conversational reasoning -- formalize how they should be combined and how this process might develop.
 We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children (N = 243) and adults (N = 694).
 Results show close numerical alignment between model predictions and data.
-Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that children selectively ignore one information source.
+Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that participnats selectively ignore one information source.
 This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
@@
 
-Children learning their first language make inferences about intended meanings based on utterance-level and common-ground information both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins].
+Children learning their first language make inferences about intended meanings based on utterance-level and common ground information -- both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins].
 Starting very early, infants expect adults to produce utterances in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve].
 By age two, children are sensitive to the informativeness of communication [@o2001two].
-By age three children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring].
+By age three, children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring].
 And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children; @horowitz2018trouble; @barner2011accessing].
@@
 
-Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
+Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
 Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged].
@@
 We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground.
-Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.
-
-Evidence for the use of common ground information by young children is even stronger: Common ground information guides how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.] information by young children is even stronger: SPeaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
 For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
@@
 
-RSA models capture common ground information as a shared prior distribution over possible intended meanings.
-Thus, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade off between the prior probability of a meaning and the informativeness of the utterance.
+Within the RSA framework, one way to incorporate common ground is to treat it as a conversational prior.
+That is, to assume that social interactions result in prior distributions over possible intended meanings which are specific to a particular speaker.
+Following this logic, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade-off between the prior probability of a meaning and the informativeness of the utterance.
 This trade off between contextual factors during word learning is a unique aspect that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].
@@
 Then we show that adults make inferences based on common ground information (experiment 2A and 2B).
-We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance and common ground information should be integrated.
+We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance information and conversational priors should be integrated.
 We consider three models that make different assumptions about the integration process: In the *integration model*, the two information sources are integrated with one another.
-The other two models are lesion models that assume that participants focus on one type of information and disregard the other whenever they are presented together.
-According to the *no common ground* model, participants focus only on the utterance information and in the *no informativeness* model, only common ground information is considered.
+The other two models are lesioned models which assume that participants focus on one type of information and disregard the other whenever they are presented together.
+According to the *no conversational prior* model, participants focus only on the utterance information and in the *no informativeness* model, only the conversational prior is considered.
 We compare predictions from these models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).
@@
 
-Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level and common-ground information flexibly.
+Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level information with conversational priors.
 Second, it uses Bayesian data analysis within the RSA framework to provide a model for understanding the multiple loci for developmental change in complex behaviors like contextual communication.
@@
 All deviations from the registered analysis plan are explicitly mentioned.
-All analyses were run in R [@R-base].
+All analyses were run in `R` [@R-base].
 All p-values are based on two sided analysis.
@@
 
-All models and model comparisons were implemented in WebPPL [@dippl] using the R package `rwebppl` [@R-rwebppl].
-Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in WebPPL.
+All models and model comparisons were implemented in `WebPPL` [@dippl] using the `R` package `rwebppl` [@R-rwebppl].
+Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in `WebPPL`.
 In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data.
@@
 Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
-We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model.
+We modeled the integration of utterance informativity and conversational priors (representing common ground) as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model.
 The Rational Speech Act (RSA) model architecture introduced by Frank and Goodman [-@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
-The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents P(r) - with his generative model of how the utterance was produced: a speaker trying to convey information to him.
-To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) - a prior distribution over lexica P(L) [@bergen2016pragmatic].
+The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents $P(r)$ - with his generative model of how the utterance was produced: a speaker trying to convey information to him.
+To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) - a prior distribution over lexica $P(L)$ [@bergen2016pragmatic].
 
@@
 
-In the above equation, the listener is trying to jointly resolve the speaker’s intended referent r and the meaning of words (thus learning the lexicon $\mathcal{L}$).
+In the above equation, the listener is trying to jointly resolve the speaker’s intended referent $r$ and the meaning of words (thus learning the lexicon $\mathcal{L}$).
 He does this by imagining what a rational speaker would say, given the referent they are trying to communicate and a lexicon.
-The speaker is an approximately rational Bayesian actor (with degree of rationality alpha), who produces utterances as a function of their informativity.
+The speaker is an approximately rational Bayesian actor (with degree of rationality $\alpha$), who produces utterances as a function of their informativity.
 The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see Supplementary Material available online for details):
@@
 
-This computational model provides a natural avenue to formalize quantitatively how informativeness and common ground trade-off during word learning.
-As mentioned above, the common ground shared between speaker and listener plays the role of the listener’s prior distribution over meanings, or types of referents, that the speaker might be referring to and which we posit depends on prior interactions around the referents in the present context (e.g., preference or novelty; experiment 2A and B).
+This computational model provides a natural avenue to formalize quantitatively how informativeness and conversational priors trade-off during word learning.
+As mentioned above, we treat common ground as a conversational prior over meanings, or types of referents, that the speaker might be referring to.
+That is, we assume that the interactions around the referents in the present context (e.g., preference or novelty; experiment 2A and B) result in a person-specific prior distribution over referents.
 We use the results from experiment 2 to specify this distribution.
@@
 Participants’ average responses were highly correlated with the  predictions from the *integration model* in each condition (Fig \ref{fig:fig3}b).
-When comparing model, we found that model fit was considerably better for the *integration model* compared to the *no common ground model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
+When comparing models, we found that model fit was considerably better for the *integration model* compared to the *no conversational prior model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
 
@@
 The estimated proportion of random responses according to the *integration model* was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
-This parameter was substantially lower for the *integration model* compared to the alternative models (*no common ground model*: `r ex3_flat_prior_model_noise_param%>%pull(mean)` [`r ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex3_prior_only_model_noise_param%>%pull(mean)` [`r ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex3_prior_only_model_noise_param%>%pull(ci_upper)`]), lending additional support to the conclusion that the *integration model* better captured the behavioral data.
+This parameter was substantially lower for the *integration model* compared to the alternative models (*no conversational prior model*: `r ex3_flat_prior_model_noise_param%>%pull(mean)` [`r ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex3_prior_only_model_noise_param%>%pull(mean)` [`r ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex3_prior_only_model_noise_param%>%pull(ci_upper)`]), lending additional support to the conclusion that the *integration model* better captured the behavioral data.
 Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.
@@
 That is, we conducted a separate experiment for each level of prior strength and common ground manipulation to estimate the prior probability of each object following this particular manipulation (analogous to experiment 2).
-This prior distribution was then passed through the model for the congruent and incongruent conditions, resulting in a unique prediction for each of the 20 condition.
+This prior distribution was then passed through the model for the congruent and incongruent conditions, resulting in a unique prediction for each of the 20 conditions.
 Given the graded nature of the prior manipulations, experiment 4 basically tests how well the model performs with different types of prior distributions.
@@
 Model predictions from the *integration model* were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d).
-We evaluated model fit for the same models as in experiment 3 and found again that the *integration model* fit the data much better compared to the *no common ground* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (*no common ground model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).
+We evaluated model fit for the same models as in experiment 3 and found again that the *integration model* fit the data much better compared to the *no conversational prior* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
+The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (*no conversational prior model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).
 
@@
 This finding contrasts with earlier work [@diesendruck2004two].
-Since our focus was on how children integrate informativeness and common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
+Since our focus was on how children integrate informativeness and conversational priors resulting from common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
 The procedure for children was identical to the preference manipulation for adults.
@@
   group_by(parameter)%>%
+  select(-ci_lower, -ci_upper)%>%
   spread(model, logP) %>%
@@
 
-Analyses comparing the model predictions from the probabilistic models to the data suggest that children flexibly integrate both common ground and informativity information.
+Analyses comparing the model predictions from the probabilistic models to the data suggest that children flexibly integrate conversational priors and informativity information.
 Furthermore, this integration process is accurately captured by the *integration model* at least for four-year-olds.
@@
 For the model comparison, we treated age continuously.
-As with adults, we found a much better model fit for the *integration model* compared to the *no common ground* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the *no informativeness model* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+As with adults, we found a much better model fit for the *integration model* compared to the *no conversational prior* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the *no informativeness model* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).
 
-The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (*no common ground model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults.
+The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (*no conversational prior model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults (see Fig \ref{fig:fig5}c).
 
@@
 Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age.
-In each case, the *integration model* provided a better fit compared to the alternative models (*no common ground*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; *no informativeness*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The developmental noise parameter for the integration model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig.
-S13 in Supplementary Material available online).
+In each case, the *integration model* provided a better fit compared to the alternative models (*no conversational prior*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; *no informativeness*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+The developmental noise parameter for the integration model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig \ref{fig:fig5}d).
 
 ```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 7 for children.
-Model predictions and data across age in the four conditions (a).
+(a) Model predictions (with 95\\% HDIs) and data across age in the four conditions.
 Transparent black dots show data from individual participants and black lines show conditional means of the data with 95\\% CI.
 Black diamonds show the mean of the data for age bins by year and error bars show 95\\% CIs.
-Correlation between model predictions (with noise parameter) and condition means binned by year (b).
-Coefficients and p-values are based on Pearson correlation statistic.
-Error bars and shaded regions represent 95\\% HDIs.
-For 4-year-olds, two conditions yielded the same data means and model predicitons and are thus plotted on top of each other.", out.width = "80%"}
+(b) Correlation between model predictions (with noise parameter) and condition means binned by year (with 95\\% HDIs).
+For 4-year-olds, two conditions yielded the same data means and model predicitons and are thus plotted on top of each other.
+(c) Posterior distribution of the noise parameter for the different models.
+(d) Developmental trajectory of the noise paramter for the three developmental noise models; trajectories are based on MAPs of the posterior distribution for the intercept and slope.", out.width = "100%"}
 knitr::include_graphics("./figures/fig5.png")
@@
 To infer the intended meaning of an utterance, listeners must combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
-This integration is especially vital in early language learning, and the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive].
+This integration is especially vital in early language learning, when the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive].
 But how are pragmatic cues integrated during word learning?
 Here we used a Bayesian cognitive model to formalize this integration process.
-We studied how utterance-level (Gricean) expectations about informative communication are integrated with common ground information.
+We studied how utterance-level (Gricean) expectations about informative communication are integrated with conversational priors (resulting from common ground).
 Adults’ and children’s learning was best predicted by a model in which both sources of information traded-off flexibly.
@@
 Real world language comprehension and learning happens in socially dynamic and complex situations which inevitably require integrating multiple pragmatic information sources.
-The integration model provides a formal description of the (hypothetical) psychological representations that may underlie information integration.
+The *integration model* provides a formal description of the (hypothetical) psychological representations that may underlie information integration.
 As such, our work complements theorizing about information integration in other domains of language comprehension [e.g.
@@
 How is information integrated in this context?
-The *integration model* assumes that the informativeness of an utterance depends on the common ground shared between interlocutors.
+The *integration model* assumes that the informativeness of an utterance depends on the person-specific conversational priors (resulting from common ground).
 This conception of information integration explains the seemingly counterintuitive predictions of the model.
 For example, one might expect that the model predicts a performance at chance level in the same speaker -- incongruent conditions because the two cues "pull" the listener in opposite directions.
-Instead, the model predicts a performance below chance, favoring the object implicated by the prior (which also matches participants' responses).
-This is because the listener assumes that the speaker takes the common ground shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
-As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of common ground.
+Instead, the model predicts a performance below chance, favoring the object implicated by the prior (which also matches adults' responses).
+This is because the listener assumes that the speaker takes the conversational prior shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
+As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of a conversational prior.
 Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@bruner1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
@@
 As a consequence, there was not much variation in three-year-old's responses for the model to explain.
+Future work in this direction should use tasks (or age groups) that show a clear and strong response for each information source.
 
 The primary source of developmental change in our model is age related changes in the propensity to make the individual inferences.
-As they get older, children expect speakers to be more informative and to be more likely to follow common ground, but the process by which the two information sources are integrated at any given age is assumed to be the same.
+As they get older, children expect speakers to be more informative and to be more likely to follow the conversational prior, but the process by which the two information sources are integrated at any given age is assumed to be the same.
 Other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
@@
 The developmental noise model reported for experiment 7 offers another way to address the question of what changes with development.
-This model estimates a developmental trajectory for the proportion of responses that are better explained by random guessing than by the model structure.
+This model estimates a developmental trajectory for the proportion of responses that are better explained by random guessing than by the model structure (see Fig \ref{fig:fig5}d).
 If such a model would find that model fit is comparable for younger and older children but that the noise parameter through which this fit is achieved decreases with age, we might conclude that cognitive abilities that have to do with task demands are the major locus of change rather than abilities that have to do with integrating information.
@@
 
-We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically.
-As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g.
+We did not model the social-cognitive processes that underlie common ground.
+Instead, we assumed that the interactions that preceded the utterance (and presumably constitute common ground) result in a person-specific conversational prior.
+From a modeling perspective, this approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g.
 in @frank2012predicting].
 Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful.
+Thus, evoking common ground in this context is largely backed-up by the experimental tasks: the fact that participants (children and adults) were sensitive to the identity of the speaker tells us that the contextual salience of the referents resulted from a process of social reasoning.
+Thus, we feel confident in saying that our results speak to how participants integrated different sources of pragmatic information.
 Based on a process model of common ground, one could further specify how common ground information (i.e.

### 2021-01-05 papers/full_paper/models.Rmd
add updated model file
add flat prior dev noise
add child prior only model llh
prep for re-submission

--- 2020-11-18 papers/full_paper/models.Rmd
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))+
+                    values= c("#C5D86D","#86615C","#AFE0CE"))+
   scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 ```
@@
                      breaks=c("data","pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("black","#859900","#00afaf","#6c71c4","#b58900"))+
+                     values= c("black","#859900","#C5D86D","#86615C","#AFE0CE"))+
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
@@
   scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
-                    values= c("#00afaf","#b58900","#859900","#6c71c4"))
+                    values= c("#00afaf","#C5D86D","#86615C","#AFE0CE"))
 ```
@@
                      breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
-                     values= c("black","#b58900","#6c71c4","#859900"))+
+                     values= c("black","#C5D86D","#86615C","#AFE0CE"))+
   theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 ```
@@
   data_var = "dataFromR"
-)
+)%>%
+  saveRDS("../../stats/saves/child_ex3_pragm_model.rds")
 
 # model predictions
-child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
+child_ex3_pragm_model_predictions <- readRDS("../../stats/saves/child_ex3_pragm_model.rds") %>%
   separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
@@
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#b58900","#6c71c4","#859900"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 ```
@@
   group_by(model,parameter)%>%
-  summarise(logP = mean(weight))
+  summarise(logP = mean(weight),
+            ci_lower = hdi_lower(weight),
+            ci_upper = hdi_upper(weight))
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
-  mutate(model = "pragmatic",
-         parameter = "noise")%>%
-  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
+#   mutate(model = "pragmatic",
+#          parameter = "noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")
 
@@
   group_by(model,parameter)%>%
-  summarise(logP = mean(weight))
+  summarise(logP = mean(weight),
+            ci_lower = hdi_lower(weight),
+            ci_upper = hdi_upper(weight))
 ```
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
-  mutate(model = "pragmatic",
-         parameter = "developmental noise")%>%
-  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
+#   mutate(model = "pragmatic",
+#          parameter = "developmental noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
-  mutate(model = "flat_prior",
-         parameter = "parameter free")%>%
-  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
+#   mutate(model = "flat_prior",
+#          parameter = "parameter free")%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
-  mutate(model = "flat_prior",
-         parameter = "noise")%>%
-  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
+#   mutate(model = "flat_prior",
+#          parameter = "noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
-  mutate(model = "flat_prior",
-         parameter = "developmental noise")%>%
-  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
+#   mutate(model = "flat_prior",
+#          parameter = "developmental noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
-  mutate(model = "prior_only",
-         parameter = "parameter free")%>%
-  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
+#   mutate(model = "prior_only",
+#          parameter = "parameter free")%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
-  mutate(model = "prior_only",
-         parameter = "noise")%>%
-  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
-
-child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
+#   mutate(model = "prior_only",
+#          parameter = "noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
+# 
+# child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
 
@@
 ```{r}
-webppl(
-  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
-  data =list(allData = ex3_model_data),
-  data_var = "dataFromR",
-  packages ="webppl-csv",
-  chains = 1,
-  cores = 1
-)
-
-read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
-  mutate(model = "prior_only",
-         parameter = "developmental noise")%>%
-  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
+# webppl(
+#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
+#   data =list(allData = ex3_model_data),
+#   data_var = "dataFromR",
+#   packages ="webppl-csv",
+#   chains = 1,
+#   cores = 1
+# )
+# 
+# read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
+#   mutate(model = "prior_only",
+#          parameter = "developmental noise")%>%
+#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")
 
@@
 
-child_ex3_model_comparison <- bind_rows(
-  child_ex3_pragm_model_likelihood_marginal,
-  child_ex3_pragm_model_noise_likelihood_marginal,
-  child_ex3_pragm_model_developmental_noise_likelihood_marginal,
-  child_ex3_flat_prior_model_noise_likelihood_marginal,
-  child_ex3_flat_prior_model_likelihood_marginal,
-  child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
-  child_ex3_prior_only_model_noise_likelihood_marginal,
-  child_ex3_prior_only_model_likelihood_marginal,
-  child_ex3_prior_only_model_developmental_noise_likelihood_marginal
-)%>%
-  ungroup()%>%
-  mutate(model = reorder(model,logP))%>%
-  saveRDS("../../stats/saves/child_ex3_model_comparison.rds")
+# child_ex3_model_comparison <- bind_rows(
+#   child_ex3_pragm_model_likelihood_marginal,
+#   child_ex3_pragm_model_noise_likelihood_marginal,
+#   child_ex3_pragm_model_developmental_noise_likelihood_marginal,
+#   child_ex3_flat_prior_model_noise_likelihood_marginal,
+#   child_ex3_flat_prior_model_likelihood_marginal,
+#   child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
+#   child_ex3_prior_only_model_noise_likelihood_marginal,
+#   child_ex3_prior_only_model_likelihood_marginal,
+#   child_ex3_prior_only_model_developmental_noise_likelihood_marginal
+# )%>%
+#   ungroup()%>%
+#   mutate(model = reorder(model,logP))%>%
+#   saveRDS("../../stats/saves/child_ex3_model_comparison.rds")
 
@@
   geom_point(size = 7)+
+  #geom_pointrange(aes(x = model, y = logP, ymin = ci_lower, ymax = ci_upper ), pch = 4)+
   theme_few()+ 
@@
   facet_grid(~parameter)+
-  ylim(-550,-400)+
+  #ylim(-550,-400)+
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 
@@
 ```{r}
-child_ex3_model_ll_dist <- bind_rows(
-  child_ex3_pragm_model_likelihood,
-  child_ex3_pragm_model_noise_likelihood,
-  child_ex3_pragm_model_developmental_noise_likelihood,
-  child_ex3_flat_prior_model_noise_likelihood,
-  child_ex3_flat_prior_model_likelihood,
-  child_ex3_flat_prior_model_developmental_noise_likelihood,
-  child_ex3_prior_only_model_noise_likelihood,
-  child_ex3_prior_only_model_likelihood,
-  child_ex3_prior_only_model_developmental_noise_likelihood
-)%>%
-  ungroup()%>%
-  mutate(model = reorder(model,weight))
+# child_ex3_model_ll_dist <- bind_rows(
+#   child_ex3_pragm_model_likelihood,
+#   child_ex3_pragm_model_noise_likelihood,
+#   child_ex3_pragm_model_developmental_noise_likelihood,
+#   child_ex3_flat_prior_model_noise_likelihood,
+#   child_ex3_flat_prior_model_likelihood,
+#   child_ex3_flat_prior_model_developmental_noise_likelihood,
+#   child_ex3_prior_only_model_noise_likelihood,
+#   child_ex3_prior_only_model_likelihood,
+#   child_ex3_prior_only_model_developmental_noise_likelihood
+# )%>%
+#   ungroup()%>%
+#   mutate(model = reorder(model,weight))%>%
+#   saveRDS("../../stats/saves/child_ex3_model_comparison_dist.rds")
+
+child_ex3_model_ll_dist <- readRDS("../../stats/saves/child_ex3_model_comparison_dist.rds")
 
@@
   geom_histogram(alpha = .5)+
-  facet_wrap(~parameter)+
+  facet_wrap(~parameter, scales = "free")+
   theme_few()+
   scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))+
+                    values= c("#C5D86D","#86615C","#AFE0CE"))+
   scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
-                    values= c("#859900","#b58900","#6c71c4"))
+                    values= c("#C5D86D","#86615C","#AFE0CE"))
 
@@
   filter(model == "pragmatic")%>%
+  select(-ci_lower, -ci_upper)%>%
   spread(parameter, logP) %>%

### 2021-01-05 papers/full_paper/Supplementary_information.Rmd
add new supp material

@@
 
-## No common ground model
+## No conversational prior model
 
@@
                             model == "no_informativeness_noise" ~ "No informativeness",
-                            model == "no_common_ground_noise" ~ "No common ground"
+                            model == "no_common_ground_noise" ~ "No conversational prior"
                             ))
@@
   filter(Parameter %in% c("noise"))  %>%
-  mutate(Model = "No common ground")
+  mutate(Model = "No conversational prior")
   )
@@
   xlim(0,1)+
-  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
+  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                     values= c("#C5D86D","#86615C","#AFE0CE"))+
-  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
+  scale_fill_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                     values= c("#C5D86D","#86615C","#AFE0CE"))
@@
                             model == "no_informativeness" ~ "No informativeness",
-                            model == "no_common_ground" ~ "No common ground"
+                            model == "no_common_ground" ~ "No conversational prior"
                             ))
@@
   mutate("Integration > No informativeness" = exp(integration_noise - no_informativeness),
-         "Integration > No common ground" = exp(integration_noise - no_common_ground),
-         "No common ground > No informativeness" = exp(no_common_ground - no_informativeness)) %>%
+         "Integration > No conversational prior" = exp(integration_noise - no_common_ground),
+         "No conversational prior > No informativeness" = exp(no_common_ground - no_informativeness)) %>%
   select(-integration_noise, -no_common_ground, -no_informativeness)%>%
@@
   spread(model, logP) %>%
-  mutate("Int > No CG" = formatC(exp(pragmatic - flat_prior),2),
+  mutate("Int > No CP" = formatC(exp(pragmatic - flat_prior),2),
          "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
-         "No CG > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
+         "No CP > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
   select(-pragmatic,-flat_prior, -prior_only)
@@
   , caption = "Model comparisons in Experiment 7"
-  , note = "BF = Bayes Factor, Int = Integration, No CG = No common ground, No Inf = No informativeness "
+  , note = "BF = Bayes Factor, Int = Integration, No CP = No conversational prior, No Inf = No informativeness "
   , escape = T
@@
   Model = c(rep("Integration",41),
-            rep("No common ground",41),
+            rep("No conversational prior",41),
             rep("No informativeness",41)),
@@
   theme_few()+
-  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
+  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                     values= c("#C5D86D","#86615C","#AFE0CE"))
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "No common ground",
+#   mutate(model = "No conversational prior",
 #          noise = "Noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "No common ground",
+#   mutate(model = "No conversational prior",
 #          noise = "Dev. noise")%>%
@@
 #   mutate(age = ifelse(age<4,"3-year-olds","4-year-olds"))%>%
-#   mutate(model = "No common ground",
+#   mutate(model = "No conversational prior",
 #          noise = "Param. free")%>%
@@
                           "Pragmatic" = "Integration",
-                          "Flat prior" = "No common ground",
+                          "Flat prior" = "No conversational prior",
                           "Prior only" = "No informativeness"),

### 2021-01-05 papers/full_paper/manuscript.Rmd
add word count

@@
   - name          : "Manuel Bohn"
-    affiliation   : "1,2,3"
+    affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
@@
   - name          : "Michael Henry Tessler"
-    affiliation   : "4"
+    affiliation   : "2"
   - name          : "Megan Merrick"
-    affiliation   : "1"
+    affiliation   : "3"
   - name          : "Michael C. Frank"
-    affiliation   : "1"
+    affiliation   : "3"
 
@@
   - id            : "1"
+    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
+  - id            : "2"
+    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
+  - id            : "3"
     institution   : "Department of Psychology, Stanford University"
-  - id            : "2"
-    institution   : "Leipzig Research Center for Early Child Development, Leipzig University"
-  - id            : "3"
-    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
-  - id            : "4"
-    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
 
@@
 keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
+wordcount         : "7708"
 
@@
 
-Evidence for the use of common ground^[Common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
+What about common ground information?
+Before reviewing the developmental literature, we want to briefly clarify how we use the term *common ground* in this paper.
+In the adult literature, common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using].
 Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged].
@@
 We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground.
-Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.] information by young children is even stronger: SPeaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.
+Construed this way, evidence for the use of common ground information by young children is strong already very early in life.
+For example, speaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
 For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].

### 2021-03-31 papers/full_paper/manuscript.Rmd
add first draft BDA figure

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
+    address       : "Max Planck Institute for Evolutionary Anthropology, Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig"
     email         : "manuel_bohn@eva.mpg.de"
@@
 keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
-wordcount         : "7708"
 
@@
 mask              : no
+numbersections    : false
 
@@
 
+# Authornote
+
+We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
+M.
+Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+749229.
+M.
+C.
+Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+All experiments and analyses were pre-registered (https://osf.io/u7kxe/).
+Stimuli, data, and analysis code are available in a public repository (https://github.com/manuelbohn/mcc).
+
 # Declarations of interest
@@
 Frank wrote the manuscript, all authors approved the final version of the manuscript.
-
-# Acknowledgments
-
-We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
-
-# Funding
-
-M.
-Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
-749229.
-M.
-C.
-Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.

### 2021-03-31 papers/full_paper/bda_fig.tex
add first draft BDA figure

\documentclass{article}
    % General document formatting
    \usepackage[margin=0.7in]{geometry}
    \usepackage[parfill]{parskip}
    \usepackage[utf8]{inputenc}

    % Related to math
    \usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{tikz}
\usepackage{subfigure}
\usetikzlibrary{bayesnet}

\begin{document}

\begin{figure}[ht]
\begin{center}
\begin{tabular}{cc}

\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{ij}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{INF}_{i}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

\node[det, above=of data_me](L1_me){$L'_{1_{i}}$};
\node[det, above=of data_comb](L1_comb){$L_{1_{i}}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

\edge{L1_me}{data_me};
\edge{L1_comb}{data_comb};
\edge{RSA}{L1_me};
\edge{RSA}{L1_comb};

% COMMON GROUND
\node[det, above=of data_cg, yshift=0.2cm](rho){$\rho_i$};
\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
\node[latent, right=of rho, yshift=-0.5cm](beta_rho_slope){$\beta^{\rho}_1$};

\edge{rho}{data_cg};
\edge{beta_rho_int}{rho};
\edge{beta_rho_slope}{rho};
\edge{rho}{L1_comb};

%% SPEAKER INFORMATIVITY

\node[det, above=of RSA, xshift=0cm](alpha){$\alpha_i$};
\node[latent, above=of alpha, xshift=-1.25cm](beta_alpha_int){$\beta^{\alpha}_0$};
\node[latent, above=of alpha, xshift=1.25cm](beta_alpha_slope){$\beta^{\alpha}_1$};

%	\edge{alpha}{L1_me};
\edge{beta_alpha_int}{alpha};
\edge{beta_alpha_slope}{alpha};
\edge{alpha}{RSA};

%% SEMANTIC KNOWLEDGE model

\

\plate{plate_condition}{(data_comb)(L1_comb)}{$j \in \text{alignments}$};

	\plate{plate_data_comb}{
	(data_comb)
	(data_cg)
	(data_me)
	(plate_condition)
	(rho)
	(alpha)
	(L1_me)
	(L1_comb)
%		(plate_items)
	}{$i \in \text{3 and 4 year olds}$}

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (7.5,5) { 
$\beta^\rho_0 ,\beta^\rho_1 \sim \text{Uniform}(-2,2)$ \\
 $\rho_i = \text{logistic}(\beta^\rho_0  + i \cdot \beta^\alpha_1)$ \\
 $d^{CG}_{i} \sim \text{Bernoulli}(\rho_i)$ \\
 \\
$\beta^\alpha_0 \sim \text{Uniform}(-3,3); \beta^\alpha_1 \sim \text{Uniform}(-0,4)$ \\
 $\alpha_i = \beta^\alpha_0  + i \cdot \beta^\alpha_1$ \\
 $d^{INF}_{ij} \sim L'_{ij},  d^{CM}_{ij} \sim L_{ijk}$
};

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ 
$P_{L_{1}}(r \mid u; \{\alpha_i,\rho_i\})\propto P_{S}(u \mid r; \{\alpha_i,\rho_i\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S}(u \mid r; \{\alpha_i, \rho_i\})\propto P(r \mid u; \{\rho_i\}) ^{\alpha_i} $\\
$P(r \mid u; \{\rho_i\}) \propto \mathcal{L}(u, r \mid \rho_i)$
};

\end{tikzpicture}

\\
\\
\\
\\
\\

%S2 represents the RSA speaker model defined by Eq. 1, which is used to predict the production responses dprod of each participant i, for each state s (number of hearts), for each utterance w, in each goal condition g. The RSA speaker model takes as input the literal meaning variables θ, which additionally are used to predict the literal meaning judgments dlit assuming a Bernoulli linking function. Additionally, the RSA model takes the speaker’s goal weights ω and intended presentational goal weight φ, which are inferred separately for each goal condition g. Finally, the RSA model uses two global free parameters: the cost of negation c and the speaker’s rationality parameter α.

\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{i,j}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{INF}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

\node[det, above=of data_me](L1_me){$L'_{1}$};
\node[det, above=of data_comb](L1_comb){$L_{1}$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

\edge{L1_me}{data_me};
\edge{L1_comb}{data_comb};
\edge{RSA}{L1_me};
\edge{RSA}{L1_comb};

% COMMON GROUND
\node[latent, above=of data_cg, yshift=0.1cm](rho){$\rho_{i}$};

\edge{rho}{data_cg};
\edge{rho}{L1_comb};

%% SPEAKER INFORMATIVITY

\node[latent, above=of RSA, xshift=0cm](alpha){$\alpha$};

%	\edge{alpha}{L1_me};
\edge{alpha}{RSA};

\

\plate{plate_condition}{(data_comb)(L1_comb)}{$j \in \text{alignments}$};

	\plate{plate_data_comb}{
	(data_comb)
	(data_cg)
	(plate_condition)
	(rho)
%		(plate_items)
	}{$i \in \text{preference and novelty}$}

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{2ex}] at (6,3.75) { 
$\alpha \sim \text{Cauchy}(1,2)$ \\
$d^{INF} \sim L',  d^{CM}_{ij} \sim L_{ij}$
};

\node[draw, align=left, execute at begin node=\setlength{\baselineskip}{3ex}] at (8,0) {Integration model\\ 
$P_{L_{1}}(r \mid u; \{\alpha,\rho_i\})\propto P_{S}(u \mid r; \{\alpha, \rho_i\}) \cdot P(r \mid \rho_i) $\\ 
$P_{S}(u \mid r; \{\alpha, \rho_i\})\propto P(r \mid u; \{\rho_i\}) ^{\alpha} $\\
$P(r \mid u; \{\rho_i\}) \propto \mathcal{L}(u, r \mid \rho_i)$
};

\end{tikzpicture}

  \end{tabular}
  \end{center}
  \label{fig:bayesnet}
\end{figure}

\end{document}

### 2021-08-09 papers/full_paper/manuscript.Rmd
update paper after R1

@@
 To navigate this challenge, children can use pragmatic reasoning to learn the meaning of unfamiliar words.
-One important challenge for pragmatic reasoning is that it requires integrating multiple information sources.
+A critical challenge for pragmatic reasoning is that it requires integrating multiple information sources, which have typically been studied separately.
 Here we study this integration process.
-We isolate two sources of pragmatic information and -- using a probabilistic model of conversational reasoning -- formalize how they should be combined and how this process might develop.
+We isolate two sources of pragmatic information and -- using a probabilistic model of conversational reasoning – formalize how they should be combined and how this process might develop.
 We use this model to generate quantitative predictions, which we test against new behavioral data from three- to five-year-old children (N = 243) and adults (N = 694).
-Results show close numerical alignment between model predictions and data.
-Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that participnats selectively ignore one information source.
-This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
+Results show close alignment between model predictions and data.
+Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that participants selectively ignore one information source.
+This work integrates distinct sets of findings regarding information sources for early language learning and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.
 
@@
 
-What someone means by an utterance is oftentimes not reducible to the words they used.
-It takes pragmatic inference – context-sensitive reasoning about the speaker’s intentions - to recover the intended meaning [@grice1991studies; @levinson2000presumptive; @sperber2001relevance].
+Successful communication often requires an understanding that extends beyond just the meaning of words.
+It takes pragmatic inference -- context-sensitive reasoning about the speaker’s intentions -- to recover a speaker’s intended meaning [@grice1991studies; @levinson2000presumptive; @sperber2001relevance].
 Contextual information comes in many forms.
@@
 Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative.
-Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins].
-On the other hand, there is information provided by common ground [the body of mutually shared knowledge and beliefs between interlocutors; @bohn2018common; @clark1996using; @clark2015common].
-Because utterances are embedded in common ground, pragmatic reasoning in context always requires information integration.
-But how does integration proceed?
-And how does it develop?
-Verbal theories assume that information is integrated and that this process develops but do not specify how.
-We bridge this gap by formalizing information integration and development in a probabilistic model of pragmatic reasoning.
-
-Children learning their first language make inferences about intended meanings based on utterance-level and common ground information -- both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins].
-Starting very early, infants expect adults to produce utterances in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve].
+Semantic ambiguity can be resolved by reasoning about why the speaker produced these particular behaviors [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins].
+On the other hand, there is information provided by common ground: Through interaction, interlocutors gradually build up a body of mutually shared knowledge and beliefs [@bohn2018common; @clark1996using; @clark2015common].
+Interlocutors expect each other to observe common ground and thus communicate in ways that are relevant to it.
+
+Common ground and utterance-level information operate on different timelines.
+Utterances allow for in-the-moment inferences because they are composed of behaviors that the speaker chooses to express their intention in the here and now.
+On the other hand, common ground is built up over time through interaction.
+Nevertheless, the two information sources are intimately related because utterances are embedded in common ground.
+As a consequence, pragmatic reasoning in context always requires information integration.
+But how does this integration proceed?
+Verbal theories assume that information is integrated but do not specify how.
+An even more important question is how this integration process develops?
+After all, young children have less knowledge of words and syntax than adults and therefore cannot rely on the linguistic context to infer what a new word means.
+Instead, they heavily rely on pragmatic inferences during language learning [@bohn2019pervasive; @clark2015common; @tomasello2008origins].
+
+In the current work, we try to answer these questions by formalizing information integration in a probabilistic model of pragmatic reasoning in development.
+In the remainder of this introduction, we describe the development of pragmatic inference and reasoning about common ground in childhood and then discuss the Rational Speech Act model, a formal framework that we use as the basis for our account of information integration.
+
+# Pragmatic Development in Childhood
+
+Children make pragmatic inferences about intended meanings based on utterance-level information, both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins].
+Starting very early, preverbal infants expect adults to produce utterances (in the form of pointing gestures) in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve].
 By age two, children are sensitive to the informativeness of communication [@o2001two].
-By age three, children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring].
-And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children; @horowitz2018trouble; @barner2011accessing].
-Thus, children’s ability to reason about utterance-level pragmatics is present at least by ages three to five, and possibly substantially younger.
-
-What about common ground information?
+By age three, children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring].In this, they are not restricted to linguistic utterances: three-year-olds also readily infer the referent of novel non-linguistic behaviors and gestures [@bohn2019natural; @moore2015two].
+And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about the semantic scope of quantifiers rather than pragmatic deficits [@skordos2016children; @horowitz2018trouble; @barner2011accessing].
+Thus, children’s ability to reason about utterance-level pragmatics is present at least by ages three to five, and possibly substantially younger.In the present study, we focused on how children (and adults) make pragmatic inferences about word meanings based on the non-verbal aspects of an utterance: gaze and pointing gestures that accompany an unknown word.
+We adapted the procedure from @frank2014inferring, in which adults and children learned a new word based on contrasting the pointing gesture a speaker produced with alternative gestures they could have produced but did not.
+
+What is the role of common ground information in language understanding and learning?
 Before reviewing the developmental literature, we want to briefly clarify how we use the term *common ground* in this paper.
@@
 Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested.
-However, most of this work is focused on online perspective taking.
-In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is likely easier for children [@matthews2006effect].
-We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground.
+Most of this work, however, is focused on online perspective-taking.
+In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction -- something that is likely easier for children [@matthews2006effect].
+
+In the discussion that follows, we assume that the consequence of a direct interaction (with matching perspectives) is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them and hence part of common ground [@bohn2018common].
 Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources.
 Construed this way, evidence for the use of common ground information by young children is strong already very early in life.
-For example, speaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
-For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
-
-The examples discussed above, however, highlight children’s use of a single pragmatic information source or cue.
+For example, speaker-specific expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s].
+For slightly older children, common ground also facilitates word comprehension and learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].
+
+In the present study, we will focus on two types of common ground information: discourse novelty and speaker preferences.
+Akhtar and colleagues [-@akhtar1996role; see also @diesendruck2004two] showed that 2-year-olds learn a new word by reasoning about which objects are new to the speaker in the unfolding discourse -- and thus the more likely to be referred to.
+Saylor and colleagues [-@saylor2009preschoolers] showed that 3- and 4-year-olds learn words by tracking the preference a speaker expressed during an ongoing interaction.
+
+# Information Integration in Pragmatic Language Learning
+
+The work discussed so far highlights children’s use of a single pragmatic information source or cue.
 Harnessing multiple – potentially competing – pragmatic cues poses a separate challenge.
-One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance.
+A central aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance.
 Much less is known about whether and how children combine these types of information.
 Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @grosse201021; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @ganea2007infants].
-For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see).
-However, the information sources to be integrated in these studies are not all pragmatic in nature.
-Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not necessarily their ability to reason about the speaker’s intention in context.
-As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information.
-Thus, while many theories of pragmatic reasoning presuppose that pragmatic information sources are integrated, the nature of their relationship has typically not been specified.
+
+To take one example of integration processes, in a classic study, @nadig2002evidence found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see).
+Integration is assumed to be occurring in that common ground constrains the later processing of language.
+However, how this constraining works is not specified -- for example, presumably, these constraints are not absolute, implying some sort of graded combination.
+Furthermore, the information sources to be integrated in these studies are not all pragmatic in nature.
+For example, children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not necessarily their ability to reason about the speaker’s intention in context.
+As a consequence, earlier work of this type – while providing important experimental evidence for information combination in childhood – still does not speak to the question of how (or even if) listeners integrate different forms of *pragmatic* information.
+
+# The Rational Speech Act Framework
 
@@
 Within the RSA framework, one way to incorporate common ground is to treat it as a conversational prior.
-That is, to assume that social interactions result in prior distributions over possible intended meanings which are specific to a particular speaker.
-Following this logic, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade-off between the prior probability of a meaning and the informativeness of the utterance.
-This trade off between contextual factors during word learning is a unique aspect that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].
+That is, previous social interactions result in a prior distribution over possible intended meanings for the current social interaction, in a manner specific to a particular speaker (i.e., Xs previous interactions with Y inform Xs current expectations about what Y is likely to talk about).
+Following this logic, a natural locus for information integration within probabilistic models of pragmatic reasoning is the combination of the prior probability of a particular meaning and the likelihood of the current utterance being used to express that meaning.
+This feature of RSA models allows them to capture situations in which different information sources (e.g., common ground vs.
+utterance information) point to different meanings.
+
+When integrated into variants of RSA that allow for uncertainty about word meaning [e.g., @frank2014inferring], this natural weighting of prior and likelihood allows for the modeling of information integration.
+Despite of the broad use of probabilistic models in understanding word learning, other computational models of word learning have focused primarily on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word] and do not provide a clear route for pragmatic information integration.
+
+# The Current Study
 
@@
 To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans]: we make independent measurements of each cue’s strength and then combine them using the RSA model described above to make independent predictions about conditions in which they either coincide or conflict.
-Finally, we pre-register these quantitative predictions and test them against new data from adults and children.
-
-We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (experiment 1).
-Then we show that adults make inferences based on common ground information (experiment 2A and 2B).
-We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance information and conversational priors should be integrated.
-We consider three models that make different assumptions about the integration process: In the *integration model*, the two information sources are integrated with one another.
-The other two models are lesioned models which assume that participants focus on one type of information and disregard the other whenever they are presented together.
-According to the *no conversational prior* model, participants focus only on the utterance information and in the *no informativeness* model, only the conversational prior is considered.
-We compare predictions from these models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).
-
-After successfully validating this approach with adults in study 1, we apply the same model-driven experimental procedure to children (study 2): We first show that they make pragmatic inferences based on utterance and common ground information separately (experiment 5 and 6).
-Then we generate a priori model predictions and compare them to data from an experiment in which both information sources have to be integrated (experiment 7).
-
-Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level information with conversational priors.
-Second, it uses Bayesian data analysis within the RSA framework to provide a model for understanding the multiple loci for developmental change in complex behaviors like contextual communication.
+We pre-register these quantitative predictions and test them against new data from adults and children.
+
+We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (Experiment 1).
+Then we show that adults make inferences based on common ground information (Experiment 2A and 2B).
+We use data from these experiments to estimate parameters and generate a priori predictions from RSA models about how utterance information and conversational priors should be integrated.
+
+Models are most useful in comparison to one another.
+By examining differences in model fit as a function of different assumptions, we can make inferences about how specific choices lead to success or failure in capturing data.
+Here we consider three models that make different assumptions about the integration process.
+In the *integration model*, common ground and utterance-level information are integrated with one another as prior and likelihood (as described above).
+Our comparison models are lesioned models that assume that participants focus on one type of information and disregard the other whenever they are presented together.
+According to the *no conversational prior model*^[We chose to refer to the alternative models by the information source they leave out a) to highlight that they are lesioned versions of the integration model and b) to avoid the impression that the integration model takes in qualitatively different information sources.], participants focus only on the utterance information and in the *no informativeness model*, only the conversational prior is considered.
+These models represent plausible alternative accounts; for example, @gagliardi2017modeling found that a model that selectively ignored parts of the input best captured children’s use of statistical information during word learning.
+We compare predictions from the three models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).
+
+After validating this approach with adults in Study 1, we apply the same model-driven experimental procedure to children (Study 2): We first show that children make pragmatic inferences based on utterance and common ground information separately (Experiments 5 and 6).
+Then we generate a priori model predictions and compare them to data from an experiment in which children are provided with both information sources (Experiment 7).
+
+Taken together, this work makes three primary contributions: first, it shows that both adults and children integrate utterance-level information with common ground to make graded inferences about word meaning.
+Second, it provides an explicit theory of how this integration process proceeds and develops.
+Third, it uses Bayesian data analysis within the RSA framework to make a quantitative comparison of the evidence for competing hypotheses.
+
+In a recent study, @bohn2021young used a similar approach to study information integration in children.
+Besides focusing on different information sources (Bohn and colleagues studied how children’s lexical knowledge integrates with discourse novelty), we extend this work in three critical ways.
+First, utterances in our study combine words, gestures, and gaze.
+With this, we capture the multimodal nature of human communication.
+Second, we probe the social nature of common ground by testing and modeling how the identity of the speaker influences the interpretation of the utterance.
+Third, by including adults in our study, we show that the same modeling framework can be used to predict the behavior of adults and children.
 
@@
 Integration (c) combined informativeness and common ground manipulations.
-One integration condition is shown here: preference - same speaker - congruent.", out.width="100%"}
+Here we only show two (out of eight) integration conditions: preference - same speaker - incongruent (left) and novelty - different speaker - congruent (right).", out.width="100%"}
 knitr::include_graphics("./figures/fig1.png")
@@
 Each participant contributed data to only one experiment.
-Experiment 1 and each manipulation of experiment 2 had *N* = 40 participants.
-Sample size in experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
-*N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations that went into experiment 4.
-Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.
+Experiment 1 and each manipulation of Experiment 2 had *N* = 40 participants.
+Sample size in Experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`.
+*N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations that went into Experiment 4.
+Finally, Experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants.
 Sample sizes in all adult experiments were chosen to yield at least 120 data points per cell.
@@
 
-All models and model comparisons were implemented in `WebPPL` [@dippl] using the `R` package `rwebppl` [@R-rwebppl].
+All cognitive models and model comparisons were implemented in `WebPPL` [@dippl] using the `R` package `rwebppl` [@R-rwebppl].
 Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in `WebPPL`.
-In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data.
+In Experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors -- the ratio of the marginal likelihoods of each model given the data.
 Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online.
@@
 
-In experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
-The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}a).
+In Experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring].
+The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}a; side counterbalanced).
 At test, the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them.
@@
 Participants could infer that the word referred to object B via the counter-factual inferences that, if the (informative) speaker had wanted to refer to object A, they would have pointed to the table with the single object (this being the least ambiguous way to refer to that object).
+This inference rests on the assumption that the speaker is communicating about an object category or type (object A or B) and not a particular object token (e.g.
+object A on the left table).
 In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior.
@@
 
-In experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers].
-In experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}b, left).
-The animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
+In Experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers].
+In Experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}b, left).
+There was an object on each table.
+The animal introduced themselves, then turned to one of the tables (left or right: counterbalanced) and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude.
 Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead.
@@
 
-In experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}b, right).
-The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
+In Experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}b, right).
+There was an object on one of the tables, while the other was initially empty (side counterbalanced).
+The animal turned to one of the tables (left or right: counterbalanced) and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way.
 Later, a second object appeared on the previously empty table.
@@
 
-In experiment 2A, participants selected the preferred object above chance (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so than in the speaker change control condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
-
-In experiment 2B, participants selected the novel object above chance (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) when the same speaker made the request and more often compared to when a different speaker made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
-
-```{r fig2, include = T, fig.align = "center", fig.cap = "Results from experiments 1, 2A, and 2B for adults.
+In Experiment 2A, participants selected the preferred object above chance when the same speaker returned (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`[`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so when a different speaker returned ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).
+
+In Experiment 2B, participants selected the novel object above chance when the same speaker made the request (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`[`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) and more often compared to when a different speaker made the request  ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).
+
+```{r fig2, include = T, fig.align = "center", fig.cap = "Results from Experiments 1, 2A, and 2B for adults.
 For preference and novelty, control refers to a different speaker (see Fig 1b).
@@
 Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model.
-We modeled the integration of utterance informativity and conversational priors (representing common ground) as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model.
+We modeled the integration of utterance informativity and common ground as a process of socially-guided probabilistic inference, using the results of Experiments 1 and 2 to inform key parameters of a computational model.
 The Rational Speech Act (RSA) model architecture introduced by Frank and Goodman [-@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun).
-The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents $P(r)$ - with his generative model of how the utterance was produced: a speaker trying to convey information to him.
-To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) - a prior distribution over lexica $P(L)$ [@bergen2016pragmatic].
+The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning -- a prior distribution over referents $P(r)$ -- with his generative model of how the utterance was produced: a speaker trying to convey information to him.
+To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) -- a prior distribution over lexica $P(L)$ [@bergen2016pragmatic].
 
@@
 
-The speaker’s possible utterances are pairs of linguistic and non-linguistic signals, namely labels and points.
-Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point.
-Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see Supplementary Material available online for modeling details).
-
-This computational model provides a natural avenue to formalize quantitatively how informativeness and conversational priors trade-off during word learning.
+The speaker’s possible utterances are pairs of linguistic and non-linguistic signals, namely labels,  points, and gaze.
+Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point and gaze, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point/gaze.
+Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to pointing and/or gazing at the location, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$.
+Importantly, we assume that each label in the lexicon refers to an object type (e.g., object A) and not an object token (e.g., object A on the left table) [@csibra2009natural] (see Supplementary Material for modeling details).
+
+This computational model provides a natural avenue to formalize quantitatively how the informativeness of an utterance and conversational priors trade-off during word learning.
 As mentioned above, we treat common ground as a conversational prior over meanings, or types of referents, that the speaker might be referring to.
-That is, we assume that the interactions around the referents in the present context (e.g., preference or novelty; experiment 2A and B) result in a person-specific prior distribution over referents.
-We use the results from experiment 2 to specify this distribution.
+That is, we assume that the interactions around the referents in the present context (i.e., preference or novelty; Experiment 2A and B) result in a speaker-specific prior distribution over referents.
+We use the results from Experiment 2 to specify this distribution: For example, in Experiment 2, for the preference/same speaker participants chose the object the speaker liked (e.g., object B) with a proportion of 0.97 and the object the speaker disliked (object A) with 0.03.
+In Experiments 3 and 4, this measurement determined the prior distribution over objects in cases whenever the same manipulation was used (preference/same speaker).
+Note that Experiment 3 involved three objects while Experiment 2 only involved two.
+We nevertheless used the exact proportions measured in Experiment 2 for each object as unnormalized probabilities in the prior.
+This approach conserved the relative relation between object types.
+Thus, when utterance and common ground information were aligned (i.e.
+object B was the more informative referent) the unnormalized distribution over objects was [$P(A_1)$ = 0.03, $P(B)$ = 0.97, $P(A_2)$ = 0.03] and after normalizing it was [0.03, 0.94, 0.03].
+When information sources were dis-aligned (i.e.
+object A was the more informative referent), the object distribution was [0.97, 0.03, 0.97] or [0.49, 0.02, 0.49] after normalizing.
+
 The in-the-moment, contextual informativeness of the utterance is captured in the likelihood term, whose value depends on the rationality parameter $\alpha$.
-Assumptions about rationality may change depending on context and we therefore used the data from experiment 1 to specify $\alpha$ (see Supplementary Material available online for details about these parameters).
-
-The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}c - see Supplementary Material available online for additional details and a worked example of how predictions were generated).
-In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter, which can be thought of as reflecting the cost that comes with handling and integrating multiple information sources.
-Technically it estimates the proportion of responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (experiment 3).
-Including the noise parameter greatly improved the model fit to the data (see Supplementary Material available online for details).
-We did not pre-register the inclusion of a noise parameter for experiment 3 but did so for all subsequent experiments.
+Assumptions about rationality may change depending on context and we therefore used the data from Experiment 1 to specify $\alpha$.
+We performed a Bayesian analysis in which we used the integration model (assuming equal prior probability over referents) with an unknown a priori value of $\alpha$, and conditioned on the data from Experiment 1 to compute a posterior distribution over $\alpha$; in turn, the model generates posterior predictions for the proportion of correct responses in Experiment 1.
+We computed the maximum a posteriori (MAP) estimate and used this value for $\alpha$ to generate model predictions for Experiment 3 and 4.
+For additional information on parameter estimation we ask the reader to consult the Supplementary Material.
+
+Based on these parameters, the model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}c).
+In the Supplementary Material, we include a worked example in which we walk the reader through the steps of computing model predictions from the parameters and the model equations.
+We recommend going through this example to get a better understanding of the model.
+
+In addition to the parameters fit to the data from previous experiments, we include a noise parameter, which can be thought of as reflecting the cost that comes with handling and integrating multiple information sources.
+Technically, the noise parameter represents the proportion of responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (Experiment 3).
+Including the noise parameter greatly improved the model fit to the data (see Supplementary Material for details).
+We did not pre-register the inclusion of a noise parameter for Experiment 3 but did so for all subsequent experiments.
 
@@
 
-In experiment 3, we combined the procedures of experiment 1 and 2A or 2B.
-The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}c).
+In Experiment 3, we combined the procedures of Experiment 1 and 2A or 2B.
+The test setup was identical to Experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}c).
 This combination resulted in two ways in which the two information sources could be aligned with one another.
-In the congruent condition, the object that was the more informative referent was also the one that was preferred by or new to the speaker.
-In the incongruent condition, the other object was the one that was preferred by or new to the speaker.
-Taken together, there were 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions in experiment 3.
-For each of these eight conditions, we generated model predictions using the modelling framework introduced above.
-The test hypothesis about how information is integrated we compared the three models introduced in the introduction: The *integration model* in which both information sources are flexibly combined, the *no common ground model* that focused only on utterance-level information and the the *no informativeness model* that focused only on common ground information.
+In the congruent condition, the object that was the more informative referent in the present context was also the one that was preferred by or new to the speaker.
+In the incongruent condition, the object that was the less informative referent in the present context was the one that was preferred by or new to the speaker.
+
+In the preference condition, the speaker turned to one table, pointed to the object and expressed either liking or disliking using the same utterances as in Experiment 2A.
+To make it clear which object the speaker was referring to while pointing to the table with two objects, the referred-to object was temporarily enlarged.
+Whether the speaker first turned to the table with a single object or to the one with the two objects was counterbalanced.
+In the congruent condition, the preferred object was also the one that was unique to the table with the two objects.
+In the incongruent condition, the preferred object was also present on the other table.
+
+In the novelty condition,  the scene began with only one object on one of the tables.
+After commenting on the presence and absence of objects in the same way as in Experiment 2B, the speaker disappeared and two additional objects appeared, one on the previously empty table and one on the other table.
+Whether the speaker first turned to the empty table or to the one with an object was counterbalanced.
+In the congruent condition, two different objects appeared so that the object that was unique to the table with the two objects was also new in context.
+In the incongruent condition, two identical objects appeared so that the object that was unique to the table was the one that was old in context.
+The test event was the same for preference and novelty: the speaker turned to the table with the two objects and used the same request as in Experiment 1.
+
+Taken together, there were 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions in Experiment 3.
+For each of these eight conditions, we generated model predictions using the modeling framework introduced above.
+To arbitrate between hypotheses about how information is integrated, we compared the three models introduced in the introduction: The *integration model* in which both information sources are flexibly combined, the *no conversational prior model* that focused only on utterance-level information and the *no informativeness model* that focused only on common ground information.
 
@@
 
-```{r fig3, include = T, fig.align = "center", fig.cap = "Results from experiment 3 and 4 for adults.
-Data and model predictions by condition for experiment 3 (a).
+```{r fig3, include = T, fig.align = "center", fig.cap = "Results from Experiment 3 and 4 for adults.
+Data and model predictions by condition for Experiment 3 (a).
 Transparent dots show data from individual participants (slightly jittered to avoid overplotting), diamonds represent condition means.
-Correlation between model predictions and data in Experiment 3 (b), between data in Experiment 3 and the direct replication in experiment 4 (c) and between model predictions and data in experiment 4 (d).
+Correlation between model predictions and data in Experiment 3 (b), between data in Experiment 3 and the direct replication in Experiment 4 (c) and between model predictions and data in Experiment 4 (d).
 Coefficients and p-values are based on Pearson correlation statistics.
@@
 
-As a second step, we compared the model predictions to the data.
-Participants’ average responses were highly correlated with the  predictions from the *integration model* in each condition (Fig \ref{fig:fig3}b).
-When comparing models, we found that model fit was considerably better for the *integration model* compared to the *no conversational prior model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
+As a second step, we compared the cognitive model predictions to the data.
+Participants’ average responses were highly correlated with the predictions from the integration model in each condition (Fig \ref{fig:fig3}b).
+When comparing models, we found that model fit was unambiguously better for the *integration model* compared to the *no conversational prior model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.
 
 Finally, we examined the noise parameter for each model.
-The estimated proportion of random responses according to the *integration model* was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`).
+The estimated proportion of random responses according to the *integration model* was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI) =  [`r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`]).
 This parameter was substantially lower for the *integration model* compared to the alternative models (*no conversational prior model*: `r ex3_flat_prior_model_noise_param%>%pull(mean)` [`r ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex3_prior_only_model_noise_param%>%pull(mean)` [`r ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex3_prior_only_model_noise_param%>%pull(ci_upper)`]), lending additional support to the conclusion that the *integration model* better captured the behavioral data.
@@
 
-To test if the *integration model* makes accurate predictions for different combinations, we first replicated and then extended the results of experiment 3 to a broader range of experimental conditions.
-Specifically, we manipulated the strength of the common ground information (3 levels - strong, medium and weak - for preference and 2 levels - strong and medium - for novelty) by changing the way the speaker interacted with the objects prior to the request.
-The procedural details and statistical analysis for these these manipulations are described in the Supplementary Material available online.
-For experiment 4, we paired each level of prior strength manipulation with the informativeness inference in the same way as in experiment 3.
-This resulted in a total of 20 conditions, for which we generated a priori model predictions in the same way as in experiment 3.
-That is, we conducted a separate experiment for each level of prior strength and common ground manipulation to estimate the prior probability of each object following this particular manipulation (analogous to experiment 2).
+To test the scope of the *integration model*, we first replicated and then extended the results of Experiment 3 to a broader range of experimental conditions.
+Specifically, we manipulated the strength of the common ground information (3 levels -- strong, medium and weak -- for preference and 2 levels -- strong and medium -- for novelty) by modifying the way the speaker interacted with the objects prior to the request.
+The procedural details and statistical analysis for these manipulations are described in the Supplementary Material.
+For Experiment 4, we paired each level of prior strength manipulation with the informativeness inference in the same way as in Experiment 3.
+This resulted in a total of 20 conditions, for which we generated a priori model predictions in the same way as in Experiment 3.
+That is, we conducted a separate experiment for each level of prior strength and common ground manipulation to estimate the prior probability of each object following this particular manipulation (analogous to Experiment 2).
 This prior distribution was then passed through the model for the congruent and incongruent conditions, resulting in a unique prediction for each of the 20 conditions.
-Given the graded nature of the prior manipulations, experiment 4 basically tests how well the model performs with different types of prior distributions.
-
-The strong prior manipulation in experiment 4 was a direct replication of experiment 3 (see Fig \ref{fig:fig3}c).
+Given the graded nature of the prior manipulations, Experiment 4 basically tests how well the model performs with different types of prior distributions.
+
+The strong prior manipulation in Experiment 4 was a direct replication of Experiment 3 (see Fig \ref{fig:fig3}c).
 Each participant was randomly assigned to a common ground manipulation and a level of prior strength and completed eight trials in total, two in each unique condition in that combination.
@@
 
-The direct replication of experiment 3 within experiment 4 showed a very close correspondence between the two rounds of data collection (see Fig \ref{fig:fig3}c).
-GLMM results for experiment 4 can be found in the Supplementary Material available online.
+The direct replication of Experiment 3 within Experiment 4 showed a very close correspondence between the two rounds of data collection (see Fig \ref{fig:fig3}c).
+GLMM results for Experiment 4 can be found in the Supplementary Material available online.
 Here we focus on the analysis based on the probabilistic models.
 Model predictions from the *integration model* were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d).
-We evaluated model fit for the same models as in experiment 3 and found again that the *integration model* fit the data much better compared to the *no conversational prior* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
-The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (*no conversational prior model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).
+We evaluated model fit for the same models as in Experiment 3 and found again that the *integration model* fit the data much better compared to the *no conversational prior* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`).
+The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)`[`r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`], which was similar to Experiment 3 and again lower compared to the alternative models (*no conversational prior model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).
 
@@
 Do children make use of multiple information sources during word learning as well?
-When does this integration emerge developmentally?
-While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described nor tested in detail.
+How does this integration emerge developmentally?
+While many verbal theories of language learning imply that such integration does occur, the actual process of integration has rarely been described nor tested in detail.
 Here we provide an explanation in the form of our *integration model* and test if it is able to capture children’s word learning.
-Embedded in the assumptions of the model is the idea that developmental change is change in the strength of the individual inferences, leading to a change in the strength of the integrated inference.
+Embedded in the assumptions of the model is the idea that developmental change occurs via  changes in the strengths of the individual inferences, which leads to a change in the strength of the integrated inference.
 As a starting point, our model assumes developmental continuity in the integration process itself [@bohn2019pervasive], though this assumption could be called into question by a poor model fit.
 The study for children followed the same general pattern as the one for adults.
-We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance (informativeness) and common ground (preference) information in isolation when making pragmatic inferences.
-We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; @frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition.
+We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance-level and common ground information in isolation when making pragmatic inferences.
+We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; @frank2014inferring] -- and generated model predictions for the average developmental trajectory in each condition.
 
@@
 We excluded 15 children due to less than 75% of reported exposure to English, five because they responded incorrectly on 2/2 training trials, three because of equipment malfunction, and two because they quit before half of the test trials were completed.
-The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in experiment 7.
-For experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.
+The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in Experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in Experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in Experiment 7.
+For Experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two.
 Sample sizes in all experiments were chosen to yield at least 80 data points in each cell for each age group.
@@
 
+All procedures, sample sizes and data analyses were again pre-registered; materials, data, and analysis code can be found in the associated repository (see Study1).
 Experiments were implemented in the same general way as for adults.
@@
 Experiment 5 for children was modeled after @frank2014inferring.
-Instead of on tables, objects were presented as hanging in trees (to facilitate showing points to distinct locations).
+Instead of appearing on tables, objects were presented as hanging in trees, which facilitated the depiction of a speaker pointing to distinct locations.
 After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”).
@@
 Four-year-olds selected the more informative object (i.e.
-the object that was unique to the location the speaker turned to) above chance (mean = `r child_ex1t%>%filter(age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="4")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="4")%>%pull(d)`).
-Three-year-olds, on the other hand, did not (mean = `r child_ex1t%>%filter(age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="3")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="3")%>%pull(d)`).
+the object that was unique to the location the speaker turned to) above chance (mean = `r child_ex1t%>%filter(age_bin =="4")%>%pull(mean)`[`r child_ex1t%>%filter(age_bin =="4")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="4")%>%pull(d)`).
+Three-year-olds, on the other hand, did not (mean = `r child_ex1t%>%filter(age_bin =="3")%>%pull(mean)`[`r child_ex1t%>%filter(age_bin =="3")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="3")%>%pull(d)`).
 Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
@@
 
-```{r fig4, include = T, fig.align = "center", fig.cap = "Results from experiment 5 and 6 for children.
+```{r fig4, include = T, fig.align = "center", fig.cap = "Results from Experiment 5 and 6 for children.
 For preference, control refers to to the different speaker condition (see Fig.
@@
 
-In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
+In Experiment 6, we assessed whether children use common ground information to identify the referent of a novel word.
 We tested children only with the preference manipulation^[We initially tested children with the novelty as well as the preference manipulation.
@@
 This finding contrasts with earlier work [@diesendruck2004two].
-Since our focus was on how children integrate informativeness and conversational priors resulting from common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.].
+Since our focus was on how children integrate informativeness and conversational priors resulting from common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.
+We studied information integration in children using the novelty manipulation in a different study [@bohn2021young]].
 The procedure for children was identical to the preference manipulation for adults.
@@
 
-Four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`).
-However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
+Four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`[`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`[`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`).
+When the different speaker made the request, performance was at chance level in both age groups (three-year-olds: mean = `r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="3")%>%pull(mean)`[`r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="3")%>%pull(t_uci)`]; four-year-olds: mean = `r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="4")%>%pull(mean)`[`r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "different_speaker" ,age_bin =="4")%>%pull(t_uci)`].
+When we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}).
 Thus, children across the age range used common ground information to infer the referent of a novel word.
@@
 Model predictions for children were generated using the same model described above for adults.
-However, to incorporate developmental change in the model, we allowed the rationality parameter $\alpha$ and the prior distribution over objects to change with age.
-That is, instead of a single value, we used Bayesian data analysis to infer the intercept and slope for each parameter that best described the developmental trajectory in the data of experiment 5 and 6 (see Supplementary Material for details on how parameters were estimated).
+To incorporate developmental change in the model, we allowed the rationality parameter $\alpha$ (which controls the degree of speaker informativeness) and the prior distribution over objects (a proxy for common ground) to change with age.
+
+We defined $\alpha$ for a given age via a simple linear regression.
+Thus, instead of inferring a single value across age, we used the data from Experiment 5 to find the intercept ($\beta^\alpha_0$) and slope ($\beta^\alpha_1$) that best described the developmental trajectory in those data.
+As for adults, we inferred  via the integration model with equal prior probabilities for each object.
+We computed a posterior distribution for the intercept and the slope of this regression function.
+In Experiment 7, the speaker optimality parameter for a child of a given age was computed by taking the MAP for the intercept and adding the MAP for the slope times the child’s age $i$: $\alpha_i = \beta^\alpha_0 + i \cdot \beta^\alpha_1$.
+
+To estimate the prior distribution over objects, we used the data from Experiment 6 to model the intercepts ($\beta^\rho_{0,j}$) and slopes ($\beta^\rho_{1,j}$) that best described the developmental trajectories in the data for each of the two ($j$) conditions.
+This allowed us to generate prior distributions over objects in the cognitive model that were sensitive to the child’s age.
+We used a simple logistic regression to find the intercept and slope (MAP of posterior distribution) that best described children’s performance in the two conditions of Experiment 6.
+In Experiment 7, the prior probability for an object was computed by taking the intercept for the respective condition $j$, adding the slope times the child’s age $i$ and then using a logistic transformation to convert the outcome into proportions: $\rho_{i,j} = \text{logistic}(\beta^\rho_{0,j} + i \cdot \beta^\rho_{1,j})$.
+Because these proportions corresponded to a two-object scenario, they were then converted to the three-object scenario by assuming equal probabilities for objects of the same type and normalizing.
+The overall distribution depended on the alignment of information sources in the same way as it did for adults.
+The Supplementary Material provides additional information on the parameter estimation.
+
 These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions.
-As for adults, all models included a noise parameter, which was estimated based on the data of experiment 7.
+As for adults, all models included a noise parameter, which was estimated based on the data of Experiment 7.
 
@@
 
-In experiment 7, we combined the procedures of experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}c).
-We again inserted the preference manipulation into the setup of experiment 5.
-After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking.
-Then the animal turned to the other tree and expressed the other attitude for the other kind of object.
+In Experiment 7, we combined the procedures of Experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}c).
+We again inserted the preference manipulation into the setup of Experiment 5.
+After greeting the child, the animal turned to one of the trees, pointed to an object -- which was temporarily enlarged and moved closer to the animal -- and expressed either liking or disliking.
+Then, the animal turned to the other tree and expressed the opposite attitude (disliking or liking) for the other kind of object.
 Next, the animal disappeared and either the same or a different animal returned.
-The rest of the trial was identical to the request phase of experiment 5.
+We counterbalanced whether the speaker first turned to the tree with the two objects or the tree with a single object.
+The remainder of the trial was identical to the request phase of Experiment 5.
 Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.
@@
 
-The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (*no conversational prior model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults (see Fig \ref{fig:fig5}c).
+The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` [`r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`], which was lower compared to the alternative models considered (*no conversational prior model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults (see Fig \ref{fig:fig5}c).
 
@@
 Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age.
-In each case, the *integration model* provided a better fit compared to the alternative models (*no conversational prior*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; *no informativeness*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
-The developmental noise parameter for the integration model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig \ref{fig:fig5}d).
-
-```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 7 for children.
+
+In each case, the integration model provided a better fit compared to the alternative models (parameter-free: integration vs.
+no conversational prior BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, integration vs.
+no informativeness BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`; developmental noise:  integration vs.
+no conversational prior BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`, integration vs.
+no informativeness BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`).
+The developmental noise parameter for the integration model decreased with age, suggesting that for younger children, the model explained the data by assuming a high rate of random guessing, whereas, for older children, the model explained the data by virtue of the processes that are implemented in its structure (see Fig \ref{fig:fig5}d).
+
+```{r fig5, include = T, fig.align = "center", fig.cap = "Results from Experiment 7 for children.
 (a) Model predictions (with 95\\% HDIs) and data across age in the four conditions.
@@
 
-# Discussion
+# General Discussion
 
@@
 To infer the intended meaning of an utterance, listeners must combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor.
-This integration is especially vital in early language learning, when the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive].
+This integration is especially vital in early language learning when the different varieties of pragmatic information are among the most important sources of information for learners who may not yet have mastered syntax and semantics [@bohn2019pervasive].
 But how are pragmatic cues integrated during word learning?
@@
 
-Cue integration is an integral part of language comprehension and learning [as well as perception more generally; @trommershauser2011sensory].
-As such, it has been extensively studied in recent decades.
-The focus of this work has usually been on how adults combine perceptual, semantic or syntactic information [e.g.
-@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line].
+We begin our discussion by contextualizing our modeling findings and then turn to the developmental implications of the modeling results.
+We end with some discussion of the limitations of our experimental tasks and our computational model.
+
+# Modeling Contributions
+
+Cue integration in language processing has been extensively studied in recent decades, but the focus of this work has usually been on how adults combine perceptual, semantic or syntactic information [@tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line].
 We extend the study of linguistic cue integration to pragmatics.
@@
 Real world language comprehension and learning happens in socially dynamic and complex situations which inevitably require integrating multiple pragmatic information sources.
-The *integration model* provides a formal description of the (hypothetical) psychological representations that may underlie information integration.
-As such, our work complements theorizing about information integration in other domains of language comprehension [e.g.
-@fourtassi2020optimal; @mcclelland2006there; @smith2017multimodal].
-
-How is information integrated in this context?
-The *integration model* assumes that the informativeness of an utterance depends on the person-specific conversational priors (resulting from common ground).
-This conception of information integration explains the seemingly counterintuitive predictions of the model.
-For example, one might expect that the model predicts a performance at chance level in the same speaker -- incongruent conditions because the two cues "pull" the listener in opposite directions.
-Instead, the model predicts a performance below chance, favoring the object implicated by the prior (which also matches adults' responses).
-This is because the listener assumes that the speaker takes the conversational prior shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
-As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of a conversational prior.
-Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@bruner1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning.
-Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.
+The *integration model* provides a formal description of the process of information integration, at least at the computational level of analysis [@marr1982vision].
+As such, our work complements theorizing about information integration in other domains of language comprehension [e.g., @fourtassi2020optimal; @mcclelland2006there; @smith2017multimodal].
 
 All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing information sources by some ratio.
-We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data.
+Predictions thus result from models of the task rather than simply models of the data.
 That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli.
@@
 
-The *integration model* predicted information integration in four-year-olds.
+What does the integration model tell us about the way in which information is integrated?
+The model assumes that the informativeness of an utterance depends on the person-specific conversational priors (resulting from common ground).
+Broadly speaking, it formalizes the view that common ground is the starting point to determine how informative a given utterance is.
+As such, the model gives an explicit and formal description of how common ground may constrain the processing of utterances -- something that was unspecified in earlier experimental work on information integration [e.g., @khu2020preschoolers; @nadig2002evidence].
+
+Our conception of information integration explains the seemingly counterintuitive predictions of the model.
+For example, one might expect the model to predict a chance level performance in the same speaker – incongruent conditions because the two cues “pull” the listener in opposite directions.
+Instead, the model predicts a performance below chance, favoring the object implicated by the prior -- which also matches adults’ responses.
+This subtle prediction emerges because the listener assumes that the speaker takes the conversational prior shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance.
+As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of a conversational prior.
+
+Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@bruner1983child; @tomasello2009constructing] by providing an explicit description of the integration process.
+The model thereby offers a computational description of how information may be integrated during pragmatic word learning.
+Future work will be required to understand if and how the RSA framework, which typically makes aggregate predictions at the group level, can be used to understand the moment-by-moment and trial-by-trial behavior of individuals.
+Individuals’ behavior could well result from a heuristic approximation to full RSA-type inference.
+New methods will likely need to be developed to evaluate this conjecture.
+
+# Developmental Findings
+
+The correlational analysis showed that the *integration model* accurately predicted information integration in four-year-olds.
 However, the model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources.
-But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses.
-As a consequence, there was not much variation in three-year-old's responses for the model to explain.
-Future work in this direction should use tasks (or age groups) that show a clear and strong response for each information source.
-
-The primary source of developmental change in our model is age related changes in the propensity to make the individual inferences.
-As they get older, children expect speakers to be more informative and to be more likely to follow the conversational prior, but the process by which the two information sources are integrated at any given age is assumed to be the same.
-Other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.
-
-The developmental noise model reported for experiment 7 offers another way to address the question of what changes with development.
+Our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (Experiments 5 and 6), combined with some noise in responding, led the younger age group to appear relatively random in their responses.
+As a consequence, there was not much variation in the group-level performance of three-year-olds for the model to explain.
+The results of the model comparison also support this interpretation.
+Here, we treated age continuously and found that the integration model provided the best fit across the entire age range.
+Taken together, we may say that as soon as children are sufficiently sensitive to the individual information sources, the integration model accurately describes the way that information is integrated.
+To strengthen this interpretation, future work should use tasks (or age groups) that show a clear and strong response for each information source.
+
+Our model presents a substantive theory of the development of information integration during word learning.
+The primary source of developmental change in our model is age-related changes in the propensity to make individual inferences.
+As they get older, children expect speakers to be more informative and more likely to observe common ground.
+Still, the process by which the two information sources are integrated at any given age is assumed to be the same.
+The alternative models we considered are plausible accounts of other ways in which information could be integrated, but they also share the assumption of developmental continuity with respect to the integration process.
+Thus, in future work, it would be important to explore alternative models for the development of the integration process; one possible candidate would be a model in which the integration process itself changes with age.
+
+Bohn and colleagues [-@bohn2021young] explored such an alternative integration model.
+They used a similar modeling framework but studied different information sources.
+In addition to an integration model that is structurally comparable to the one described here, they formulated a biased integration model which assumed that children are biased towards some information sources over others.
+In a developmental version of this biased model, they assumed that the strength of this bias changes with age, which represents an alternative view on development.
+However, when directly compared, the integration model explained their data better.
+
+The developmental noise model reported for Experiment 7 offers yet another way to address the question of developmental change.
 This model estimates a developmental trajectory for the proportion of responses that are better explained by random guessing than by the model structure (see Fig \ref{fig:fig5}d).
-If such a model would find that model fit is comparable for younger and older children but that the noise parameter through which this fit is achieved decreases with age, we might conclude that cognitive abilities that have to do with task demands are the major locus of change rather than abilities that have to do with integrating information.
-In the developmental noise model in experiment 7, we found that noise decreased with age but, at the same time, that the resulting model fit was substantially worse for younger children.
-However, rather than a difference in how information is integrated, we think that a lack of variation in children's responses is the reason for this poor model fit.
-The strongest evidence for developmental changes in integration would come in a case where younger children showed evidence of above/below-chance judgment in the combined task that was distinct from that predicted by the two above/below-chance component tasks.
+If such a data analytic model would find that model fit is comparable for younger and older children but that the noise parameter through which this fit is achieved decreases with age, we might conclude that cognitive abilities that pertain to task demands are the major locus of change rather than abilities that have to do with integrating information.
+In the developmental noise model in Experiment 7, we found that noise decreased with age but, at the same time, that the resulting model fit was substantially worse for three-year-old children.
+As mentioned in the previous paragraph, we think that a lack of sensitivity to the individual information sources, rather than a failure to integrate them, is the reason for this poor model fit in the younger age group.
+The strongest evidence for developmental changes in integration would come in a case where younger children showed evidence of above/below-chance judgment in the combined task (Experiment 7) that was distinct from that predicted by the two above/below-chance component tasks (Experiment 5 and 6).
 Such a comparison would require more precision (either via more trials or more participants) than our current experiment affords, however.
 
-We did not model the social-cognitive processes that underlie common ground.
+# Limitations
+
+An important limitation of our experimental work is that we studied a single population of American-English speaking children and adults using a computerized storybook task.
+It is therefore unclear how our results would transfer to different populations and/or different experimental methods.
+Regarding the first point, we expect substantial variation across cultures and languages in how sensitive children are to the different information sources.
+The few studies that investigated pragmatic inferences similar to the ones we observed in our study found substantial variation [@su2015interpretation; @zhao2021development; @fortier2018ad].
+Extending this work to study information integration will be a very valuable avenue for future research.
+Nevertheless, we think that our modeling framework provides an excellent tool to study universalities and differences in information integration.
+
+Our modeling work is limited in that we did not model the social-cognitive processes that underlie common ground.
 Instead, we assumed that the interactions that preceded the utterance (and presumably constitute common ground) result in a person-specific conversational prior.
@@
 social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm].
-A further limitation of our work here is that we did not specify how common ground is integrated into the process of compositional interpretation at work in more complex sentences.
-This is an open challenge for future research on pragmatic inference.
-One possible approach would be to make inferences about relevant common ground at the level of individual lexical items and to propagate this uncertainty through compositions into larger sentences [as in e.g., @potts2016embedded].
 
@@
 Studying how multiple types of pragmatic cues are balanced contributes to a more comprehensive understanding of word learning.
-In the current study, participants inferred the referent by integrating non-linguistic cues (speakers pointing to a table) with assumptions about speaker informativeness and common ground information, going beyond previous experimental work in measuring how these information sources were combined.
+In the current study, participants inferred the referent by integrating non-linguistic cues (gaze and pointing gestures) with assumptions about speaker informativeness and common ground information, going beyond previous experimental work in measuring how these information sources were combined.
 The real learning environment is far richer than what we captured in our experimental design, however.
@@
 We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.
-M.
-Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
+Manuel Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no.
 749229.
-M.
-C.
+Michael Henry Tessler was supported by a National Science Foundation SBE Postdoctoral Research Fellowship Grant No.
+1911790.
+Michael C.
 Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.
+Parts of Study 1 appeared in the proceedings of the 41st Annual Meeting of the Cognitive Science Society, Montreal, Canada, 2019.
 All experiments and analyses were pre-registered (https://osf.io/u7kxe/).
-Stimuli, data, and analysis code are available in a public repository (https://github.com/manuelbohn/mcc).
+Experiments, data, and analysis code are available in a public repository (https://github.com/manuelbohn/mcc).
 
